### 2023-08-21 Paper/draft.Rmd
rearrange folders

---
title: "Learning from Data Through Models"
date: '`r format(Sys.time(), "%B %d, %Y")`'
author: "Alberto Bisin, Guillaume Frechette and Jimena Galindo"
abstract: "TBW"
#classoption: pagebackref # passes pagebackref=true to hyperref before it is loaded, allowing backreferencing
output: 
    pdf_document:
        citation_package: natbib
        fig_width: 7
        fig_height: 6
        fig_caption: true
        number_sections: true

        template: NULL
        keep_tex: true
        extra_dependencies:
            footmisc: ["bottom"] # footnote management
            setspace: ["doublespacing"] # spacing of the paper
            caption: ["normal"]
            dsfont: null # indicator function 1
            booktabs: null
            makecell: null
            hyperref: null
        includes:
          in_header: extra_header.tex

bibliography: bibliography.bib
fontsize: 12pt
geometry: margin=2.5cm
---

```{r dependencies, include=FALSE}
source("../parameters_and_packages.R")
```

# Introduction

# Literature Review

# Framework
An agent is of type $\theta \in \{\theta_L, \theta_M, \theta_H\}$  with $\theta_H > \theta_M > \theta_L$ and they face an unknown 
exogenous state
$\omega \in \{\omega_L, \omega_M, \omega_H\}$ with $\omega_H>\omega_M>\omega_L$. 
Each of the values of $\omega$ is realized with equal probability. The agent knows the distribution of $\omega$ but not its value. 
They also hold some prior belief about $\theta$ which is potentially misspecified.\footnote{The particular types of misspecification
that are allowed are discussed below.}
The agent chooses a binary gamble $e in \{e_L, e_M, e_H\}$ and and observes whether the gamble is a success or a failure. '
If it is a success,
the agent gets a payoff of $1$ and if it is a failure, the agent gets a payoff of $0$. The probability of success is increasing in
both $\theta$ and $\omega$ and is fully described in the following table:

\begin{tabular}{ c|c|c|c|}

  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
  \cline{2-4}
  $e_H$ & 50 & 20 & 2 \\
  \cline{2-4}
  $e_M$ & 45 & 30 & 7 \\
  \cline{2-4}
  $e_L$ & 40 & 25 & 20 \\
  \cline{2-4}
  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_L$} & \multicolumn{1}{c}{}\\
\end{tabular}
\hspace{.3cm} % adjust this value to set the space between tables
\begin{tabular}{ c|c|c|c|}

  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
  \cline{2-4}
  $e_H$ & 80 & 50 & 5 \\
  \cline{2-4}
  $e_M$ & 69 & 65 & 30 \\
  \cline{2-4}
  $e_L$ & 65 & 45 & 40 \\
  \cline{2-4}
  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_M$} & \multicolumn{1}{c}{}\\
\end{tabular}
\hspace{.3cm} % adjust this value to set the space between tables
\begin{tabular}{ c|c|c|c|}

  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
  \cline{2-4}
  $e_H$ & 98 & 65 & 25 \\
  \cline{2-4}
  $e_M$ & 80 & 69 & 35 \\
  \cline{2-4}
  $e_L$ & 75 & 55 & 45 \\
  \cline{2-4}
  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_H$} & \multicolumn{1}{c}{}\\
\end{tabular}

Conditional on a type, the agent's flow payoff is maximized by choosing the gamble that 
matches the state. For example, if the value of $\omega$ is $\omega_H$, the agent's flow payoff is maximized by 
choosing $e_H$ and if the state is $\omega_L$ the flow payoff is maximized by choosing gamble $e_L$. The agent myopically chooses
gambles every period to maximize the flow payoff for $T<\infty$ periods, and the agent's payoff is the sum of the payoffs from 
each period.

After observing the aoutcome of each gamble, the agent updates their beliefs of both theta and omega in one of 4 differente ways: 
As a \emph{dogmatic} as in \cite ; as a \emph{switcher} as in \cite ; as a \emph{self-attribution} updater as in \cite ; 
or as a fully Bayesian agent. Each of these updating rules is described in detail in what follows.

## A Biased Agent
An agent that updates their beliefs with self-attribution bias will update their beliefs about the state $\omega$ and their type $\theta$
by over-attributing successes to a high value of $\theta$ and under-estimating the role of higher $\omega$. Similarly, after a 
failure, they will attribute it to a low state more than an unbiased agent would. The exact updating rule is as follows:
\begin{equation}

\end{equation}

# Experimental Design

# Analysis

# Conclusion

### 2023-08-21 overconfidence_otree/Questionnaire/__init__.py

@@ -14,6 +14,7 @@ class C(BaseConstants):
     NAME_IN_URL = 'Questionnaire'
     PLAYERS_PER_GROUP = None
     NUM_ROUNDS = 1
+    TASKS = ['Math', 'Verbal', 'Science and Technology', 'Sports and Video Games', 'US Geography', 'Pop-Culture and Art']
 
 
 class Subsession(BaseSubsession):
@@ -28,67 +29,6 @@ class Player(BasePlayer):
     gender = models.StringField(label='What best describes your gender identity: Male, Female, Other?',
                                 choices=['Male', 'Female', 'Non-binary'])
     nationality = models.StringField(label='What is your nationality?', choices=['US National', 'non-US National'])
-    major = models.StringField(label='What best describes your major?',
-                               choices=['Anthropology',
-                                        'Art',
-                                        'Art History',
-                                        'Biology ',
-                                        'Biomolecular Science',
-                                        'Business',
-                                        'Chemistry',
-                                        'Cinema',
-                                        'Civil Engineering',
-                                        'Classics',
-                                        'Computer Science',
-                                        'Data Science',
-                                        'Digital Art and Design',
-                                        'Digital Communications and Media',
-                                        'Digital Media',
-                                        'Drama',
-                                        'Education Studies',
-                                        'Electrical Engineering',
-                                        'Economics',
-                                        'English',
-                                        'Environmental Studies',
-                                        'European and Mediterranean Studies',
-                                        'Finance',
-                                        'Game Design',
-                                        'Global Affairs',
-                                        'Healthcare',
-                                        'History',
-                                        'Hotel and Tourism Management',
-                                        'International Relations',
-                                        'Journalism',
-                                        'Language Studies',
-                                        'Leadership and Management Studies',
-                                        'Literature',
-                                        'Management',
-                                        'Marketing',
-                                        'Mathematics',
-                                        'Mechanical Engineering',
-                                        'Medical Sciences',
-                                        'Music',
-                                        'Music Business',
-                                        'Nutrition and Food Studies',
-                                        'Other Humanities',
-                                        'Other Social Sciences',
-                                        'Performance',
-                                        'Philosophy',
-                                        'Photography',
[…]

### 2023-08-21 overconfidence_otree/Quizzes/__init__.py

@@ -52,7 +52,7 @@ class C(BaseConstants):
     NAME_IN_URL = 'Quizzes'
     PLAYERS_PER_GROUP = None
     # time limit for each quiz in seconds. the form submits when time runs out
-    TIME = 5
+    TIME = 120
     # List of the quizz titles
     TASKS = ['Math', 'Verbal', 'Science and Technology', 'Sports and Video Games', 'US Geography', 'Pop-Culture and Art']
     NUM_ROUNDS = len(TASKS)

### 2023-08-21 overconfidence_otree/Signals/__init__.py

@@ -13,7 +13,7 @@ class C(BaseConstants):
     PLAYERS_PER_GROUP = None
     TASKS = ['Math', 'Verbal', 'Science and Technology', 'Sports and Video Games', 'US Geography', 'Pop-Culture and Art']
     # number of effort/signal realizations per quizz
-    N = 15
+    N = 10
     # total number of rounds
     NUM_ROUNDS = len(TASKS)*N
     # the matrices for the DGP
@@ -21,7 +21,7 @@ class C(BaseConstants):
     mm = np.array([[.40, .45, .65], [.30, .65, .69], [.05, .50, .80]])
     mh = np.array([[.45, .55, .75], [.35, .69, .80], [.25, .65, .98]])
     M = [ml, mm, mh]
-    SEED = 3821
+    SEED = 388
     trials = 10
     # first value of bucket 2
     T1 = 6
@@ -66,17 +66,17 @@ class Player(BasePlayer):
                                         widget=widgets.RadioSelectHorizontal)
 
     math_certainty = models.IntegerField(min=0, max=100,
-                                         label='Between 0 and 100 how sure are you of your answer? (100 you are completely sure and 0 means your answer was a random guess)')
+                                         label='From 0 to 100 how sure are you of your answer? (100 you are completely sure and 0 means your answer was a random guess)')
     verbal_certainty = models.IntegerField(min=0, max=100,
-                                           label='Between 0 and 100 how sure are you of your answer? (100 you are completely sure and 0 means your answer was a random guess)')
+                                           label='From 0 to 100 how sure are you of your answer? (100 you are completely sure and 0 means your answer was a random guess)')
     pop_certainty = models.IntegerField(min=0, max=100,
-                                        label='Between 0 and 100 how sure are you of your answer? (100 you are completely sure and 0 means your answer was a random guess)')
+                                        label='From 0 to 100 how sure are you of your answer? (100 you are completely sure and 0 means your answer was a random guess)')
     science_certainty = models.IntegerField(min=0, max=100,
-                                            label='Between 0 and 100 how sure are you of your answer? (100 you are completely sure and 0 means your answer was a random guess)')
+                                            label='From 0 to 100 how sure are you of your answer? (100 you are completely sure and 0 means your answer was a random guess)')
     us_certainty = models.IntegerField(min=0, max=100,
[…]

### 2023-08-21 overconfidence_otree/SignalsOther/__init__.py

@@ -15,7 +15,8 @@ class C(BaseConstants):
     TASKS = ['Math', 'Verbal',
              'Science and Technology', 'Sports and Video Games', 'US Geography', 'Pop-Culture and Art']
     # number of effort/signal realizations per quizz
-    N = 5
+    N = 10
+    trials = 10
     # total number of rounds
     NUM_ROUNDS = len(TASKS)*N
     # the matrices for the DGP
@@ -23,7 +24,7 @@ class C(BaseConstants):
     mm = np.array([[.40, .45, .65], [.30, .65, .69], [.05, .50, .80]])
     mh = np.array([[.45, .55, .75], [.35, .69, .80], [.25, .65, .98]])
     M = [ml, mm, mh]
-    SEED = 3821
+    SEED = 388
     T1 = 6
     T2 = 16
 
@@ -39,27 +40,27 @@ class Group(BaseGroup):
 class Player(BasePlayer):
     topic = models.StringField()
 
-    math_belief_self = models.IntegerField(label='Guess your score',
+    math_belief_self = models.IntegerField(label='',
                                            choices=[[0, 'Between 0 and ' + str(C.T1 - 1)],
                                                     [1, 'Between ' + str(C.T1) + ' and ' + str(C.T2 - 1)],
                                                     [2, str(C.T2) + ' or more']],
                                            widget=widgets.RadioSelectHorizontal)
-    verbal_belief_self = models.IntegerField(label='Guess your score',
+    verbal_belief_self = models.IntegerField(label='',
                                              choices=[[0, 'Between 0 and ' + str(C.T1 - 1)],
                                                       [1, 'Between ' + str(C.T1) + ' and ' + str(C.T2 - 1)],
                                                       [2, str(C.T2) + ' or more']],
                                              widget=widgets.RadioSelectHorizontal)
-    pop_belief_self = models.IntegerField(label='Guess your score',
+    pop_belief_self = models.IntegerField(label='',
                                      choices=[[0, 'Between 0 and ' + str(C.T1 - 1)],
                                               [1, 'Between ' + str(C.T1) + ' and ' + str(C.T2 - 1)],
                                               [2, str(C.T2) + ' or more']],
                                      widget=widgets.RadioSelectHorizontal)
-    science_belief_self = models.IntegerField(label='Guess your score',
+    science_belief_self = models.IntegerField(label='',
                                          choices=[[0, 'Between 0 and ' + str(C.T1 - 1)],
[…]

### 2023-08-21 overconfidence_otree/settings.py

@@ -21,7 +21,7 @@ SESSION_CONFIGS = [
 # e.g. self.session.config['participation_fee']
 
 SESSION_CONFIG_DEFAULTS = dict(
-    real_world_currency_per_point=1.00, participation_fee=0.00, doc=""
+    real_world_currency_per_point=.20, participation_fee=10.00, doc=""
 )
 
 PARTICIPANT_FIELDS = [
@@ -43,7 +43,15 @@ PARTICIPANT_FIELDS = [
     'major',
     'nationality',
     'part1_score',
-    'part1_topic']
+    'part1_topic',
+    'part2_score',
+    'part2_topic',
+    'math_other',
+    'verbal_other',
+    'science_other',
+    'sports_other',
+    'us_other',
+    'pop_other']
 
 SESSION_FIELDS = ['seed',
                   'w_verbal',

### 2023-08-21 overconfidence_otree/Questionnaire/__init__.py
new seed draw

@@ -48,7 +48,6 @@ class Questionnaire(Page):
         participant = player.participant
         participant.gender = player.gender
         participant.nationality = player.nationality
-        participant.major = player.major
 
 
 class ResultsWaitPage(WaitPage):

### 2023-08-21 overconfidence_otree/Signals/__init__.py

@@ -21,7 +21,7 @@ class C(BaseConstants):
     mm = np.array([[.40, .45, .65], [.30, .65, .69], [.05, .50, .80]])
     mh = np.array([[.45, .55, .75], [.35, .69, .80], [.25, .65, .98]])
     M = [ml, mm, mh]
-    SEED = 388
+    SEED = 3452
     trials = 10
     # first value of bucket 2
     T1 = 6

### 2023-08-21 overconfidence_otree/SignalsOther/__init__.py

@@ -24,7 +24,7 @@ class C(BaseConstants):
     mm = np.array([[.40, .45, .65], [.30, .65, .69], [.05, .50, .80]])
     mh = np.array([[.45, .55, .75], [.35, .69, .80], [.25, .65, .98]])
     M = [ml, mm, mh]
-    SEED = 388
+    SEED = 3452
     T1 = 6
     T2 = 16
 

### 2023-08-21 overconfidence_otree/settings.py

@@ -38,9 +38,7 @@ PARTICIPANT_FIELDS = [
     'pop_questions',
     'us_questions',
     'sports_questions',
-    'age',
     'gender',
-    'major',
     'nationality',
     'part1_score',
     'part1_topic',

### 2023-08-22 overconfidence_otree/Quizzes/__init__.py
start cleaning demo data

@@ -196,19 +196,6 @@ class Player(BasePlayer):
 
     score = models.IntegerField(initial=0)
 
-    math_belief=models.IntegerField(min=0, max=20,
-                                    label='How many questions do you think you answered correctly in the Math Quiz')
-    verbal_belief = models.IntegerField(min=0, max=20,
-                                      label='How many questions do you think you answered correctly in the Verbal Quiz')
-    pop_belief = models.IntegerField(min=0, max=20,
-                                        label='How many questions do you think you answered correctly in the Pop Culture and Art Quiz')
-    science_belief = models.IntegerField(min=0, max=20,
-                                        label='How many questions do you think you answered correctly in the Science and Technology Quiz')
-    us_belief = models.IntegerField(min=0, max=20,
-                                        label='How many questions do you think you answered correctly in the US Geography Quiz')
-    sports_belief = models.IntegerField(min=0, max=20,
-                                        label='How many questions do you think you answered correctly in the Sports and Videogames Quiz')
-
 
 # FUNCTIONS
 def creating_session(subsession: Subsession):

### 2023-08-29 Paper/draft.Rmd
reshape simulation data to merge with data

@@
 date: '`r format(Sys.time(), "%B %d, %Y")`'
-author: "Alberto Bisin, Guillaume Frechette and Jimena Galindo"
+author: "Jimena Galindo"
 abstract: "TBW"
@@
 
-bibliography: bibliography.bib
+bibliography: references.bib
 fontsize: 12pt
@@
 ```{r dependencies, include=FALSE}
-source("../parameters_and_packages.R")
+source("../Paper/parameters_and_packages.R")
 ```
@@
 # Introduction
-
-# Literature Review
 
@@
 
-After observing the aoutcome of each gamble, the agent updates their beliefs of both theta and omega in one of 4 differente ways: 
-As a \emph{dogmatic} as in \cite ; as a \emph{switcher} as in \cite ; as a \emph{self-attribution} updater as in \cite ; 
-or as a fully Bayesian agent. Each of these updating rules is described in detail in what follows.
+After observing the outcome of each gamble, the agent updates their beliefs of both theta and omega in one of 4 differente ways: 
+As a \emph{dogmatic} as in @Heidhues2018 ; as a \emph{switcher} as in @Ba2023 ; as a \emph{self-attribution} updater as in @Coutts2020; 
+or as a fully Bayesian agent. Each of these updating rules is described in detail below.
+
+Notice that both \theta and \omega can be identified from the outcomes.
+However, under the assumption that the agent is myopic, the choices might not gererate sufficient variation in effort to 
+identify both. Such cases arise when the agent is either overconfident or underconfident about their type and the combination
+of their choices with the exogenous state are such that the data observed is consistent with the erroneous beliefs. Each of 
+the updating mecahnisms above will make different predicitons about the cases in which the agent is able to learn their true 
+type and when the misspecification persists.
+
+## The Bayesian Benchmark
+
+A fully rational agent updates their beliefs about $\theta$ and $\omega$ simultaneously by using Bayes' rule. 
+The agent's posterior beliefs about $\theta$ and $\omega$ after observing a success are given by:
+\begin{equation}
+p[\theta_j|\text{success}] = \frac{p[\text{success}|\theta_j]p[\theta_j]}{\sum_{k=1}^3 p[\text{success}|\theta_k]p[\theta_k]}
+\end{equation}
+and
+\begin{equation}
+p[\omega_i|\text{success}] = \frac{p[\text{success}|\omega_i]p[\omega_i]}{\sum_{k=1}^3 p[\text{success}|\omega_k]p[\omega_k]}
+\end{equation}
+
+where $p[\text{success}|\theta_j]$ is the probability of success conditional on type $\theta_j$ and $p[\text{success}|\omega_i]$ is the
+probability of success conditional on state $\omega_i$.
+
+Notice that since agents are myopic, even though all the parameters could be identified with enough variation in choices, even 
+a fully Bayesian agent might not learn their true type. This is because they do not internalize the tradeoff between flow payoff
+and learning.
 

### 2023-08-29 Paper/draft.tex
reshape simulation data to merge with data

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Learning from Data Through Models},
  pdfauthor={Jimena Galindo},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=2.5cm]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}

\setlength{\parindent}{25pt}
\setlength{\parskip}{0pt}
\setlength{\skip\footins}{0.25cm} % margin before footnotes
\definecolor{myblue}{RGB}{31, 61, 122}
\definecolor{mypink}{RGB}{204, 0, 82}
\newtheorem{assumption}{Assumption}
\newtheorem{proposition}{Proposition} % Use the 'proposition' counter for numbering

\newcommand{\EE}[1]{\mathbb{E}\left[#1\right]}
\newcommand{\PP}[1]{\mathbb{P}\left(#1\right)}
\newcommand{\CP}[2]{\mathbb{P}\left(#1 \,| \, #2 \right)}
\newcommand{\CE}[2]{\mathbb{E}\left[#1\,|\,#2 \right]}
\usepackage[bottom]{footmisc}
\usepackage[doublespacing]{setspace}
\usepackage[normal]{caption}
\usepackage{dsfont}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{hyperref}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{plainnat}

\title{Learning from Data Through Models}
\author{Jimena Galindo}
\date{August 28, 2023}

\begin{document}
\maketitle
\begin{abstract}
TBW
\end{abstract}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

\hypertarget{framework}{%
\section{Framework}\label{framework}}

An agent is of type \(\theta \in \{\theta_L, \theta_M, \theta_H\}\) with
\(\theta_H > \theta_M > \theta_L\) and they face an unknown exogenous
state \(\omega \in \{\omega_L, \omega_M, \omega_H\}\) with
\(\omega_H>\omega_M>\omega_L\). Each of the values of \(\omega\) is
realized with equal probability. The agent knows the distribution of
\(\omega\) but not its value. They also hold some prior belief about
\(\theta\) which is potentially
misspecified.\footnote{The particular types of misspecification
that are allowed are discussed below.} The agent chooses a binary gamble
\(e in \{e_L, e_M, e_H\}\) and and observes whether the gamble is a
success or a failure. ' If it is a success, the agent gets a payoff of
\(1\) and if it is a failure, the agent gets a payoff of \(0\). The
probability of success is increasing in both \(\theta\) and \(\omega\)
and is fully described in the following table:

\begin{tabular}{ c|c|c|c|}

  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
  \cline{2-4}
  $e_H$ & 50 & 20 & 2 \\
  \cline{2-4}
  $e_M$ & 45 & 30 & 7 \\
  \cline{2-4}
  $e_L$ & 40 & 25 & 20 \\
  \cline{2-4}
  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_L$} & \multicolumn{1}{c}{}\\
\end{tabular}
\hspace{.3cm}

\% adjust this value to set the space between tables

\begin{tabular}{ c|c|c|c|}

  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
  \cline{2-4}
  $e_H$ & 80 & 50 & 5 \\
  \cline{2-4}
  $e_M$ & 69 & 65 & 30 \\
  \cline{2-4}
  $e_L$ & 65 & 45 & 40 \\
  \cline{2-4}
  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_M$} & \multicolumn{1}{c}{}\\
\end{tabular}
\hspace{.3cm}

\% adjust this value to set the space between tables

\begin{tabular}{ c|c|c|c|}

  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
  \cline{2-4}
  $e_H$ & 98 & 65 & 25 \\
  \cline{2-4}
  $e_M$ & 80 & 69 & 35 \\
  \cline{2-4}
  $e_L$ & 75 & 55 & 45 \\
  \cline{2-4}
  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_H$} & \multicolumn{1}{c}{}\\
\end{tabular}

Conditional on a type, the agent's flow payoff is maximized by choosing
the gamble that matches the state. For example, if the value of
\(\omega\) is \(\omega_H\), the agent's flow payoff is maximized by
choosing \(e_H\) and if the state is \(\omega_L\) the flow payoff is
maximized by choosing gamble \(e_L\). The agent myopically chooses
gambles every period to maximize the flow payoff for \(T<\infty\)
periods, and the agent's payoff is the sum of the payoffs from each
period.

After observing the outcome of each gamble, the agent updates their
beliefs of both theta and omega in one of 4 differente ways: As a
\emph{dogmatic} as in \citet{Heidhues2018} ; as a \emph{switcher} as in
\citet{Ba2023} ; as a \emph{self-attribution} updater as in
\citet{Coutts2020}; or as a fully Bayesian agent. Each of these updating
rules is described in detail below.

Notice that both \theta and \omega can be identified from the outcomes.
However, under the assumption that the agent is myopic, the choices
might not gererate sufficient variation in effort to identify both. Such
cases arise when the agent is either overconfident or underconfident
about their type and the combination of their choices with the exogenous
state are such that the data observed is consistent with the erroneous
beliefs. Each of the updating mecahnisms above will make different
predicitons about the cases in which the agent is able to learn their
true type and when the misspecification persists.

\hypertarget{the-bayesian-benchmark}{%
\subsection{The Bayesian Benchmark}\label{the-bayesian-benchmark}}

A fully rational agent updates their beliefs about \(\theta\) and
\(\omega\) simultaneously by using Bayes' rule. The agent's posterior
beliefs about \(\theta\) and \(\omega\) after observing a success are
given by: \begin{equation}
p[\theta_j|\text{success}] = \frac{p[\text{success}|\theta_j]p[\theta_j]}{\sum_{k=1}^3 p[\text{success}|\theta_k]p[\theta_k]}
\end{equation} and \begin{equation}
p[\omega_i|\text{success}] = \frac{p[\text{success}|\omega_i]p[\omega_i]}{\sum_{k=1}^3 p[\text{success}|\omega_k]p[\omega_k]}
\end{equation}

where \(p[\text{success}|\theta_j]\) is the probability of success
conditional on type \(\theta_j\) and \(p[\text{success}|\omega_i]\) is
the probability of success conditional on state \(\omega_i\).

Notice that since

\hypertarget{a-biased-agent}{%
\subsection{A Biased Agent}\label{a-biased-agent}}

An agent that updates their beliefs with self-attribution bias will
update their beliefs about the state \(\omega\) and their type
\(\theta\) by over-attributing successes to a high value of \(\theta\)
and under-estimating the role of higher \(\omega\). Similarly, after a
failure, they will attribute it to a low state more than an unbiased
agent would. The exact updating rule is as follows: \begin{equation}

\end{equation}

\hypertarget{experimental-design}{%
\section{Experimental Design}\label{experimental-design}}

\hypertarget{analysis}{%
\section{Analysis}\label{analysis}}

\renewcommand\refname{Conclusion}
  \bibliography{references.bib}

\end{document}

### 2023-08-31 overconfidence_otree/Signals/__init__.py
11 rounds

@@ -13,7 +13,7 @@ class C(BaseConstants):
     PLAYERS_PER_GROUP = None
     TASKS = ['Math', 'Verbal', 'Science and Technology', 'Sports and Video Games', 'US Geography', 'Pop-Culture and Art']
     # number of effort/signal realizations per quizz
-    N = 10
+    N = 11
     # total number of rounds
     NUM_ROUNDS = len(TASKS)*N
     # the matrices for the DGP

### 2023-08-31 overconfidence_otree/SignalsOther/__init__.py

@@ -15,7 +15,7 @@ class C(BaseConstants):
     TASKS = ['Math', 'Verbal',
              'Science and Technology', 'Sports and Video Games', 'US Geography', 'Pop-Culture and Art']
     # number of effort/signal realizations per quizz
-    N = 10
+    N = 11
     trials = 10
     # total number of rounds
     NUM_ROUNDS = len(TASKS)*N

### 2023-09-01 Paper/draft.Rmd
11 rounds

@@
 ---
-title: "Learning from Data Through Models"
+title: "Learning from Data Through Models"  # nolint: Grammarly.
 date: '`r format(Sys.time(), "%B %d, %Y")`'
@@
 that are allowed are discussed below.}
-The agent chooses a binary gamble $e in \{e_L, e_M, e_H\}$ and and observes whether the gamble is a success or a failure. '
+The agent chooses a binary gamble $e in \{e_L, e_M, e_H\}$ and observes whether the gamble is a success or a failure. '
 If it is a success,
@@
 
-After observing the outcome of each gamble, the agent updates their beliefs of both theta and omega in one of 4 differente ways: 
+After observing the outcome of each gamble, the agent updates their beliefs of both theta and omega in one of 4 different ways: 
 As a \emph{dogmatic} as in @Heidhues2018 ; as a \emph{switcher} as in @Ba2023 ; as a \emph{self-attribution} updater as in @Coutts2020; 
@@
 Notice that both \theta and \omega can be identified from the outcomes.
-However, under the assumption that the agent is myopic, the choices might not gererate sufficient variation in effort to 
+However, under the assumption that the agent is myopic, the choices might not generate sufficient variation in effort to 
 identify both. Such cases arise when the agent is either overconfident or underconfident about their type and the combination
-of their choices with the exogenous state are such that the data observed is consistent with the erroneous beliefs. Each of 
-the updating mecahnisms above will make different predicitons about the cases in which the agent is able to learn their true 
+of their choices with the exogenous state is such that the data observed is consistent with the erroneous beliefs. Each of 
+the updating mechanisms above will make different predictions about the cases in which the agent can learn their true 
 type and when the misspecification persists.

### 2023-09-01 Paper/parameters_and_packages.R

@@ -10,7 +10,8 @@ library(car) # for linearHypothesis
 library(lmtest) # for coefTest
 library(sandwich) # for clustering errors
 
-invisible(capture.output(renv::snapshot())) # keep the packages synced with the lockfile
+# keep the packages synced with the lockfile
+invisible(capture.output(renv::snapshot()))
 
 # parameters
-params = list(date_of_exp = '2023-04-01')
+params <- list(date_of_exp = "2023-04-01")

### 2023-09-03 Paper/draft.Rmd
other data and writing models

@@
 # Framework
+
+REWRITE IN GENERAL TERMS WITH THE PROBABILITY BEING GIVEN BY A FUNCTION THAT SATIEFIES ALL THE PROPERTIES IN BA SO THAT I CAN 
+REFER TO HER RESULTS.
+THEN EXPAND ON THE EXAMPLE FOR THE LAB AND SAY WHY IT CAPTURES ALL THE FORCES WE WANT.
+
 An agent is of type $\theta \in \{\theta_L, \theta_M, \theta_H\}$  with $\theta_H > \theta_M > \theta_L$ and they face an unknown 
@@
 \end{tabular}
-\hspace{.3cm} % adjust this value to set the space between tables
+\hspace{.3cm} 
 \begin{tabular}{ c|c|c|c|}
@@
 
-Notice that both \theta and \omega can be identified from the outcomes.
-However, under the assumption that the agent is myopic, the choices might not generate sufficient variation in effort to 
-identify both. Such cases arise when the agent is either overconfident or underconfident about their type and the combination
-of their choices with the exogenous state is such that the data observed is consistent with the erroneous beliefs. Each of 
-the updating mechanisms above will make different predictions about the cases in which the agent can learn their true 
-type and when the misspecification persists.
+Notice that both $\theta$ and $\omega$ can be identified from the outcomes if enough variation in the effort choices exists.
+This can be seen by confirming that no two columns are the same. Therefore, the agent can learn both their type and the 
+state by observing enough outcomes of the gambles for different effort choices.
 
@@
 
-A fully rational agent updates their beliefs about $\theta$ and $\omega$ simultaneously by using Bayes' rule. 
-The agent's posterior beliefs about $\theta$ and $\omega$ after observing a success are given by:
+A Bayesian agent simultaneously updates their beliefs about $\theta$ and $\omega$ by using Bayes' rule. 
+The posterior odds at period t about $\theta$ after observing an outcome are given by:
 \begin{equation}
-p[\theta_j|\text{success}] = \frac{p[\text{success}|\theta_j]p[\theta_j]}{\sum_{k=1}^3 p[\text{success}|\theta_k]p[\theta_k]}
+\frac{p_{t}[\theta_H|\text{outcome}]}{p_{t}[\theta_M|\text{outcome}]} = 
+      \frac{p[\text{outcome}|\theta_H]p_{t-1}[\theta_H]}{p[\text{outcome}|\theta_M]p_{t-1}[\theta_M]}
 \end{equation}
@@
 \begin{equation}
-p[\omega_i|\text{success}] = \frac{p[\text{success}|\omega_i]p[\omega_i]}{\sum_{k=1}^3 p[\text{success}|\omega_k]p[\omega_k]}
+\frac{p_{t}[\theta_M|\text{outcome}]}{p_{t}[\theta_L|\text{outcome}]} = 
+      \frac{p[\text{outcome}|\theta_M]p_{t-1}[\theta_M]}{p[\text{outcome}|\theta_L]p_{t-1}[\theta_L]}
 \end{equation}
 
-where $p[\text{success}|\theta_j]$ is the probability of success conditional on type $\theta_j$ and $p[\text{success}|\omega_i]$ is the
-probability of success conditional on state $\omega_i$.
+Where $p_{t-1}$ is the prior at period $t$ and 
+$p[\text{outcome}|\theta] = \sum_{\omega} p[\text{outcome}|\theta, \omega, e]p_{t-1}(\omega)$
+is the probability of observing the outcome given the agent's type and the effort chosen. The update is symmetric for $\omega$.
 
-Notice that since agents are myopic, even though all the parameters could be identified with enough variation in choices, even 
-a fully Bayesian agent might not learn their true type. This is because they do not internalize the tradeoff between flow payoff
-and learning.
+Bayesian agents always choose the effort level that maximizes their flow payoff by taking expectations over
+their prior beliefs about $\theta$ and $\omega$. Since agents are myopic, even though all the parameters could be identified with enough variation in choices, 
+a fully Bayesian agent might not learn their true type. This happens because they do not internalize the tradeoff between flow payoff
+and learning and thus might not experiment enough to learn their type. An alternative to this approach is given 
+by @Hestermann2021 and is discussed with the results.
 
@@
 An agent that updates their beliefs with self-attribution bias will update their beliefs about the state $\omega$ and their type $\theta$
-by over-attributing successes to a high value of $\theta$ and under-estimating the role of higher $\omega$. Similarly, after a 
-failure, they will attribute it to a low state more than an unbiased agent would. The exact updating rule is as follows:
+by over-attributing successes to a high value of $\theta$ and under-estimating the role of higher $\omega$. Similarly,
+they will attribute failure to a low state more than an unbiased agent would. 
+To model the self-serving attribution bias, I take the approach of @benjamin2019, where a generalization of the Bayes rule above gives the update.
+
 \begin{equation}
+\frac{p_{t}[\theta_H|\text{outcome}]}{p_{t}[\theta_M|\text{outcome}]} = 
+      \left(\frac{p[\text{outcome}|\theta_H]}{p[\text{outcome}|\theta_M]}\right)^{c_s^{\theta}\mathbb{I}\{\text{success}\}+c_f^{\theta}\mathbb{I}\{\text{failure}\}}\frac{p_{t-1}[\theta_H]}{p_{t-1}[\theta_M]}
+\end{equation}
+and
+\begin{equation}
+\frac{p_{t}[\theta_M|\text{outcome}]}{p_{t}[\theta_L|\text{outcome}]} = 
+      \left(\frac{p[\text{outcome}|\theta_M]}{p[\text{outcome}|\theta_L]}\right)^{c_s^{\theta}\mathbb{I}\{\text{success}\}+c_f^{\theta}\mathbb{I}\{\text{failure}\}}\frac{p_{t-1}[\theta_M]}{p_{t-1}[\theta_L]}
+\end{equation}
 
+$c_s^{\theta}$ and $c_f^{\theta}$ are the self-serving attribution bias parameters for the agent's type $\theta$. 
+If $c_s^{\theta} = c_f^{\theta} = 1$, the agent is unbiased and the update is the same as the Bayesian update. On the other hand, 
+if $c_s^{\theta} > c_f{\theta}$ the agent over-attributes success to their type and under-attributes failure to their type\footnote{
+  notice that the values of $c_s^{\theta}$ and $c_f^{\theta}$ are not restricted to be greater than 1. If they are both equal to 
+  each other but less (more) than one, then the bias is simply underinference (overinference).}.
+
+The update for $\omega$ is analogous but with $c_f^{\omega}$ and $c_s^{\omega}$ instead of $c_f^{\theta}$ and $c_s^{\theta}$ and
+ the bias is present whenever $c_f^{\omega} > c_s^{\omega}$. That is, the agent over-attributes failure to a low state relative the 
+higher states and under-attributes success to a low state relative to the higher states.
+
+## The Dogmatic Agent
+
+A dogmatic agent does not update their beliefs about $\theta$; instead,
+they hold a degenerate belief that places probability one on being a particular type, $\hat{\theta}$. For instance, the dogmatic agent 
+might be of type $\hat{\theta} = \theta_M$ but holds a belief that places probability one on being of type $\theta_H$. In this case, no matter
+how much information he gathers against being of type $\theta_H$, he will not update his beliefs. Any discrepancies between the 
+observed outcomes are incorporated using the Bayes rule to update their beliefs about $\omega$. This results in the following
+posterior odds:
+
+\begin{equation}
+\frac{p_{t}[\omega_H|\text{outcome}]}{p_{t}[\omega_M|\text{outcome}]} = 
+      \frac{p[\text{outcome}|\omega_H, \hat{\theta}, e]p_{t-1}[\omega_H]}{p[\text{outcome}|\omega_M, \hat{\theta}, e]p_{t-1}[\omega_M]}
 \end{equation}
+and
+\begin{equation}
+\frac{p_{t}[\omega_M|\text{outcome}]}{p_{t}[\omega_L|\text{outcome}]} = 
+      \frac{p[\text{outcome}|\omega_M, \hat{\theta}, e]p_{t-1}[\omega_M]}{p[\text{outcome}|\omega_L, \hat{\theta}, e]p_{t-1}[\omega_L]}
+\end{equation}
+
+A crucial difference between the dogmatic agent and the Bayesian agent is that the dogmatic agent does not aggregate across 
+types when updating their beliefs about $\omega$. This means the dogmatic agent will never learn their true type if they are 
+misspecified.
+
+@Heidhues2018 show that in a setting such as ours, a dogmatic modeler will inevitably fall into a self-confirming equilibrium where
+the outcomes they observe reinforce their belief on $\omega$ in such a way that as $t\to\infty$ the agent will be certain that
+the state is some $\omega^*$ consistent with their believed type and the observed data.
+
+## The Switcher
+
+An agent is a \emph{switcher} if they behave as a dogmatic but is willing to entertain the possibility that they are of a different type.
+In particular, when they start off as a misspecified dogmatic, they are willing to switch to a different dogmatic belief if the data is
+convincing enough.
+
+In order to abandon their initial dogmatic belief, the agent needs to observe a sequence of outcomes that are sufficiently unlikely
+to have happened if they were of the type they initially believed. They do so by keeping track of the likelihood that each of the
+possible types generated the data. If the likelihood ratio is sufficiently large, the agent will switch to the alternative
+and behave as if they are dogmatic about the new type.
+
+In particular, for an agent that starts off with a dogmatic belief that they are of type $\hat{\theta}$ but is willing to consider
+the alternative explanation that they are of type $\tilde{\theta}$, the agent will switch to the alternative if:
+
+$$\frac{p[h^t|\tilde{\theta}]}{p[h^t|\hat{\theta}]} > \alpha$$
+
+Where $h^t$ is the history of outcomes up to time $t$ and $\alpha \geq 1$ is a threshold that determines how convincing the data needs to be
+for the agent to change their belief. Notice that if $\alpha \to \infty$, we get the dogmatic agent. In this sense, the 
+switcher is a generalization of the dogmatic type, just as the self-attribution agent is a generalization of the Bayesian agent.
+
+By allowing the agent to keep track of the likelihoods and switching to an alternative type, the switcher can avoid the 
+self-confirming equilibrium the dogmatic agent falls into. However, if the prior belief on $theta$ is sufficiently tight around
+a self-confirming equilibrium, the switcher might look identical to the dogmatic even in a case where $\alpha$ is not too large.
 

### 2023-09-03 Paper/draft.tex
other data and writing models

@@
 \author{Jimena Galindo}
-\date{August 28, 2023}
+\date{September 03, 2023}
 
@@
 
+REWRITE IN GENERAL TERMS WITH THE PROBABILITY BEING GIVEN BY A FUNCTION
+THAT SATIEFIES ALL THE PROPERTIES IN BA SO THAT I CAN REFER TO HER
+RESULTS. THEN EXPAND ON THE EXAMPLE FOR THE LAB AND SAY WHY IT CAPTURES
+ALL THE FORCES WE WANT.
+
 An agent is of type \(\theta \in \{\theta_L, \theta_M, \theta_H\}\) with
@@
 that are allowed are discussed below.} The agent chooses a binary gamble
-\(e in \{e_L, e_M, e_H\}\) and and observes whether the gamble is a
-success or a failure. ' If it is a success, the agent gets a payoff of
-\(1\) and if it is a failure, the agent gets a payoff of \(0\). The
-probability of success is increasing in both \(\theta\) and \(\omega\)
-and is fully described in the following table:
+\(e in \{e_L, e_M, e_H\}\) and observes whether the gamble is a success
+or a failure. ' If it is a success, the agent gets a payoff of \(1\) and
+if it is a failure, the agent gets a payoff of \(0\). The probability of
+success is increasing in both \(\theta\) and \(\omega\) and is fully
+described in the following table:
 
@@
 \hspace{.3cm} 
-
-\% adjust this value to set the space between tables
-
 \begin{tabular}{ c|c|c|c|}
@@
 After observing the outcome of each gamble, the agent updates their
-beliefs of both theta and omega in one of 4 differente ways: As a
+beliefs of both theta and omega in one of 4 different ways: As a
 \emph{dogmatic} as in \citet{Heidhues2018} ; as a \emph{switcher} as in
@@
 
-Notice that both \theta and \omega can be identified from the outcomes.
-However, under the assumption that the agent is myopic, the choices
-might not gererate sufficient variation in effort to identify both. Such
-cases arise when the agent is either overconfident or underconfident
-about their type and the combination of their choices with the exogenous
-state are such that the data observed is consistent with the erroneous
-beliefs. Each of the updating mecahnisms above will make different
-predicitons about the cases in which the agent is able to learn their
-true type and when the misspecification persists.
+Notice that both \(\theta\) and \(\omega\) can be identified from the
+outcomes if enough variation in the effort choices exists. This can be
+seen by confirming that no two columns are the same. Therefore, the
+agent can learn both their type and the state by observing enough
+outcomes of the gambles for different effort choices.
 
@@
 
-A fully rational agent updates their beliefs about \(\theta\) and
-\(\omega\) simultaneously by using Bayes' rule. The agent's posterior
-beliefs about \(\theta\) and \(\omega\) after observing a success are
-given by: \begin{equation}
-p[\theta_j|\text{success}] = \frac{p[\text{success}|\theta_j]p[\theta_j]}{\sum_{k=1}^3 p[\text{success}|\theta_k]p[\theta_k]}
+A Bayesian agent simultaneously updates their beliefs about \(\theta\)
+and \(\omega\) by using Bayes' rule. The posterior odds at period t
+about \(\theta\) after observing an outcome are given by:
+\begin{equation}
+\frac{p_{t}[\theta_H|\text{outcome}]}{p_{t}[\theta_M|\text{outcome}]} = 
+      \frac{p[\text{outcome}|\theta_H]p_{t-1}[\theta_H]}{p[\text{outcome}|\theta_M]p_{t-1}[\theta_M]}
 \end{equation} and \begin{equation}
-p[\omega_i|\text{success}] = \frac{p[\text{success}|\omega_i]p[\omega_i]}{\sum_{k=1}^3 p[\text{success}|\omega_k]p[\omega_k]}
+\frac{p_{t}[\theta_M|\text{outcome}]}{p_{t}[\theta_L|\text{outcome}]} = 
+      \frac{p[\text{outcome}|\theta_M]p_{t-1}[\theta_M]}{p[\text{outcome}|\theta_L]p_{t-1}[\theta_L]}
 \end{equation}
 
-where \(p[\text{success}|\theta_j]\) is the probability of success
-conditional on type \(\theta_j\) and \(p[\text{success}|\omega_i]\) is
-the probability of success conditional on state \(\omega_i\).
+Where \(p_{t-1}\) is the prior at period \(t\) and
+\(p[\text{outcome}|\theta] = \sum_{\omega} p[\text{outcome}|\theta, \omega, e]p_{t-1}(\omega)\)
+is the probability of observing the outcome given the agent's type and
+the effort chosen. The update is symmetric for \(\omega\).
 
-Notice that since
+Bayesian agents always choose the effort level that maximizes their flow
+payoff by taking expectations over their prior beliefs about \(\theta\)
+and \(\omega\). Since agents are myopic, even though all the parameters
+could be identified with enough variation in choices, a fully Bayesian
+agent might not learn their true type. This happens because they do not
+internalize the tradeoff between flow payoff and learning and thus might
+not experiment enough to learn their type. An alternative to this
+approach is given by \citet{Hestermann2021} and is discussed with the
+results.
 
@@
 \(\theta\) by over-attributing successes to a high value of \(\theta\)
-and under-estimating the role of higher \(\omega\). Similarly, after a
-failure, they will attribute it to a low state more than an unbiased
-agent would. The exact updating rule is as follows: \begin{equation}
+and under-estimating the role of higher \(\omega\). Similarly, they will
+attribute failure to a low state more than an unbiased agent would. To
+model the self-serving attribution bias, I take the approach of
+\citet{benjamin2019}, where a generalization of the Bayes rule above
+gives the update.
 
+\begin{equation}
+\frac{p_{t}[\theta_H|\text{outcome}]}{p_{t}[\theta_M|\text{outcome}]} = 
+      \left(\frac{p[\text{outcome}|\theta_H]}{p[\text{outcome}|\theta_M]}\right)^{c_s^{\theta}\mathbb{I}\{\text{success}\}+c_f^{\theta}\mathbb{I}\{\text{failure}\}}\frac{p_{t-1}[\theta_H]}{p_{t-1}[\theta_M]}
+\end{equation} and \begin{equation}
+\frac{p_{t}[\theta_M|\text{outcome}]}{p_{t}[\theta_L|\text{outcome}]} = 
+      \left(\frac{p[\text{outcome}|\theta_M]}{p[\text{outcome}|\theta_L]}\right)^{c_s^{\theta}\mathbb{I}\{\text{success}\}+c_f^{\theta}\mathbb{I}\{\text{failure}\}}\frac{p_{t-1}[\theta_M]}{p_{t-1}[\theta_L]}
 \end{equation}
+
+\(c_s^{\theta}\) and \(c_f^{\theta}\) are the self-serving attribution
+bias parameters for the agent's type \(\theta\). If
+\(c_s^{\theta} = c_f^{\theta} = 1\), the agent is unbiased and the
+update is the same as the Bayesian update. On the other hand, if
+\(c_s^{\theta} > c_f{\theta}\) the agent over-attributes success to
+their type and under-attributes failure to their type\footnote{
+  notice that the values of $c_s^{\theta}$ and $c_f^{\theta}$ are not restricted to be greater than 1. If they are both equal to 
+  each other but less (more) than one, then the bias is simply underinference (overinference).}.
+
+The update for \(\omega\) is analogous but with \(c_f^{\omega}\) and
+\(c_s^{\omega}\) instead of \(c_f^{\theta}\) and \(c_s^{\theta}\) and
+the bias is present whenever \(c_f^{\omega} > c_s^{\omega}\). That is,
+the agent over-attributes failure to a low state relative the higher
+states and under-attributes success to a low state relative to the
+higher states.
+
+\hypertarget{the-dogmatic-agent}{%
+\subsection{The Dogmatic Agent}\label{the-dogmatic-agent}}
+
+A dogmatic agent does not update their beliefs about \(\theta\);
+instead, they hold a degenerate belief that places probability one on
+being a particular type, \(\hat{\theta}\). For instance, the dogmatic
+agent might be of type \(\hat{\theta} = \theta_M\) but holds a belief
+that places probability one on being of type \(\theta_H\). In this case,
+no matter how much information he gathers against being of type
+\(\theta_H\), he will not update his beliefs. Any discrepancies between
+the observed outcomes are incorporated using the Bayes rule to update
+their beliefs about \(\omega\). This results in the following posterior
+odds:
+
+\begin{equation}
+\frac{p_{t}[\omega_H|\text{outcome}]}{p_{t}[\omega_M|\text{outcome}]} = 
+      \frac{p[\text{outcome}|\omega_H, \hat{\theta}, e]p_{t-1}[\omega_H]}{p[\text{outcome}|\omega_M, \hat{\theta}, e]p_{t-1}[\omega_M]}
+\end{equation} and \begin{equation}
+\frac{p_{t}[\omega_M|\text{outcome}]}{p_{t}[\omega_L|\text{outcome}]} = 
+      \frac{p[\text{outcome}|\omega_M, \hat{\theta}, e]p_{t-1}[\omega_M]}{p[\text{outcome}|\omega_L, \hat{\theta}, e]p_{t-1}[\omega_L]}
+\end{equation}
+
+A crucial difference between the dogmatic agent and the Bayesian agent
+is that the dogmatic agent does not aggregate across types when updating
+their beliefs about \(\omega\). This means the dogmatic agent will never
+learn their true type if they are misspecified.
+
+\citet{Heidhues2018} show that in a setting such as ours, a dogmatic
+modeler will inevitably fall into a self-confirming equilibrium where
+the outcomes they observe reinforce their belief on \(\omega\) in such a
+way that as \(t\to\infty\) the agent will be certain that the state is
+some \(\omega^*\) consistent with their believed type and the observed
+data.
+
+\hypertarget{the-switcher}{%
+\subsection{The Switcher}\label{the-switcher}}
+
+An agent is a \emph{switcher} if they behave as a dogmatic but is
+willing to entertain the possibility that they are of a different type.
+In particular, when they start off as a misspecified dogmatic, they are
+willing to switch to a different dogmatic belief if the data is
+convincing enough.
+
+In order to abandon their initial dogmatic belief, the agent needs to
+observe a sequence of outcomes that are sufficiently unlikely to have
+happened if they were of the type they initially believed. They do so by
+keeping track of the likelihood that each of the possible types
+generated the data. If the likelihood ratio is sufficiently large, the
+agent will switch to the alternative and behave as if they are dogmatic
+about the new type.
+
+In particular, for an agent that starts off with a dogmatic belief that
+they are of type \(\hat{\theta}\) but is willing to consider the
+alternative explanation that they are of type \(\tilde{\theta}\), the
+agent will switch to the alternative if:
+
+\[\frac{p[h^t|\tilde{\theta}]}{p[h^t|\hat{\theta}]} > \alpha\]
+
+Where \(h^t\) is the history of outcomes up to time \(t\) and
+\(\alpha \geq 1\) is a threshold that determines how convincing the data
+needs to be for the agent to change their belief. Notice that if
+\(\alpha \to \infty\), we get the dogmatic agent. In this sense, the
+switcher is a generalization of the dogmatic type, just as the
+self-attribution agent is a generalization of the Bayesian agent.
+
+By allowing the agent to keep track of the likelihoods and switching to
+an alternative type, the switcher can avoid the self-confirming
+equilibrium the dogmatic agent falls into. However, if the prior belief
+on \(theta\) is sufficiently tight around a self-confirming equilibrium,
+the switcher might look identical to the dogmatic even in a case where
+\(\alpha\) is not too large.
 

### 2023-09-03 Paper/compile_paper.R

@@ -1,0 +1,8 @@
+# install missing packages from the lockfile
+renv::restore()
+
+# paper options
+knitr::opts_chunk$set(eval=T, echo=F, warning=F, message=F, cache=F)
+
+# compile the paper
+rmarkdown::render("Paper/draft.Rmd", output_format = "pdf_document")

### 2023-09-04 Paper/draft.Rmd
experimental design

@@
 THEN EXPAND ON THE EXAMPLE FOR THE LAB AND SAY WHY IT CAPTURES ALL THE FORCES WE WANT.
-
-An agent is of type $\theta \in \{\theta_L, \theta_M, \theta_H\}$  with $\theta_H > \theta_M > \theta_L$ and they face an unknown 
-exogenous state
-$\omega \in \{\omega_L, \omega_M, \omega_H\}$ with $\omega_H>\omega_M>\omega_L$. 
-Each of the values of $\omega$ is realized with equal probability. The agent knows the distribution of $\omega$ but not its value. 
-They also hold some prior belief about $\theta$ which is potentially misspecified.\footnote{The particular types of misspecification
-that are allowed are discussed below.}
-The agent chooses a binary gamble $e in \{e_L, e_M, e_H\}$ and observes whether the gamble is a success or a failure. '
-If it is a success,
-the agent gets a payoff of $1$ and if it is a failure, the agent gets a payoff of $0$. The probability of success is increasing in
-both $\theta$ and $\omega$ and is fully described in the following table:
-
-\begin{tabular}{ c|c|c|c|}
-
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
-  \cline{2-4}
-  $e_H$ & 50 & 20 & 2 \\
-  \cline{2-4}
-  $e_M$ & 45 & 30 & 7 \\
-  \cline{2-4}
-  $e_L$ & 40 & 25 & 20 \\
-  \cline{2-4}
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_L$} & \multicolumn{1}{c}{}\\
-\end{tabular}
-\hspace{.3cm} 
-\begin{tabular}{ c|c|c|c|}
-
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
-  \cline{2-4}
-  $e_H$ & 80 & 50 & 5 \\
-  \cline{2-4}
-  $e_M$ & 69 & 65 & 30 \\
-  \cline{2-4}
-  $e_L$ & 65 & 45 & 40 \\
-  \cline{2-4}
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_M$} & \multicolumn{1}{c}{}\\
-\end{tabular}
-\hspace{.3cm} 
-\begin{tabular}{ c|c|c|c|}
-
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
-  \cline{2-4}
-  $e_H$ & 98 & 65 & 25 \\
-  \cline{2-4}
-  $e_M$ & 80 & 69 & 35 \\
-  \cline{2-4}
-  $e_L$ & 75 & 55 & 45 \\
-  \cline{2-4}
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_H$} & \multicolumn{1}{c}{}\\
-\end{tabular}
-
-Conditional on a type, the agent's flow payoff is maximized by choosing the gamble that 
-matches the state. For example, if the value of $\omega$ is $\omega_H$, the agent's flow payoff is maximized by 
-choosing $e_H$ and if the state is $\omega_L$ the flow payoff is maximized by choosing gamble $e_L$. The agent myopically chooses
-gambles every period to maximize the flow payoff for $T<\infty$ periods, and the agent's payoff is the sum of the payoffs from 
-each period.
-
-After observing the outcome of each gamble, the agent updates their beliefs of both theta and omega in one of 4 different ways: 
-As a \emph{dogmatic} as in @Heidhues2018 ; as a \emph{switcher} as in @Ba2023 ; as a \emph{self-attribution} updater as in @Coutts2020; 
-or as a fully Bayesian agent. Each of these updating rules is described in detail below.
-
-Notice that both $\theta$ and $\omega$ can be identified from the outcomes if enough variation in the effort choices exists.
-This can be seen by confirming that no two columns are the same. Therefore, the agent can learn both their type and the 
-state by observing enough outcomes of the gambles for different effort choices.
 
@@
 
-$$\frac{p[h^t|\tilde{\theta}]}{p[h^t|\hat{\theta}]} > \alpha$$
+$$\frac{p[h^t|\tilde{\theta}}{p[h^t|\hat{\theta}]} > \alpha$$
 
@@
 
+# A Simple Example
+The agent can be of one of 3 types: $\theta \in \{\theta_L, \theta_M, \theta_H\}$  with $\theta_H > \theta_M > \theta_L$.
+They face an unknown exogenous success rate
+$\omega \in \{\omega_L, \omega_M, \omega_H\}$ with $\omega_H>\omega_M>\omega_L$. Each of the values of $\omega$ is realized with equal probability. 
+The agent knows the distribution of $\omega$ but not its realized value. Let the true type be $\theta^*$ 
+and the true state be $\omega^*$.
+
+The agent holds some prior belief about $\theta$ \footnote{which is potentially misspecified as in the dogmatic and switcher cases discussed} 
+and chooses a binary gamble $e in \{e_L, e_M, e_H\}$. The agent observes whether the gamble is a success or a failure and 
+gets a payoff of $1$ and if it is a success. They get $0$ otherwise.
+
+The probability of success is increasing in
+both $\theta$ and $\omega$ and is fully described in the following table:
+
+\begin{tabular}{ c|c|c|c|}
+
+  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
+  \cline{2-4}
+  $e_H$ & 50 & 20 & 2 \\
+  \cline{2-4}
+  $e_M$ & 45 & 30 & 7 \\
+  \cline{2-4}
+  $e_L$ & 40 & 25 & 20 \\
+
+  \cline{2-4}
+  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_L$} & \multicolumn{1}{c}{}\\
+\end{tabular}
+\hspace{.3cm} 
+\begin{tabular}{ c|c|c|c|}
+
+  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
+  \cline{2-4}
+  $e_H$ & 80 & 50 & 5 \\
+  \cline{2-4}
+  $e_M$ & 69 & 65 & 30 \\
+  \cline{2-4}
+  $e_L$ & 65 & 45 & 40 \\
+  \cline{2-4}
+  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_M$} & \multicolumn{1}{c}{}\\
+\end{tabular}
+\hspace{.3cm} 
+\begin{tabular}{ c|c|c|c|}
+
+  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
+  \cline{2-4}
+  $e_H$ & 98 & 65 & 25 \\
+  \cline{2-4}
+  $e_M$ & 80 & 69 & 35 \\
+  \cline{2-4}
+  $e_L$ & 75 & 55 & 45 \\
+  \cline{2-4}
+  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_H$} & \multicolumn{1}{c}{}\\
+\end{tabular}
+
+Conditional on a type, the agent's flow payoff is maximized by choosing the gamble that 
+matches the state. For example, if the value of $\omega$ is $\omega_H$, the agent's flow payoff is maximized by 
+choosing $e_H$ and if the state is $\omega_L$ the flow payoff is maximized by choosing gamble $e_L$. The agent myopically chooses
+gambles every period to maximize the flow payoff for $T$ periods.
+
+After observing the outcome of each gamble, the agent updates their beliefs using some algorithm and moves on to the next period.
+
+Notice that both $\theta$ and $\omega$ can be identified from the outcomes if enough variation in the effort choices exists.
+This can be seen by confirming there is no pair of $\theta$ and $\omega$ such that the probability of success is the same for all effort 
+choices. Therefore, by changing the effort choice, the agent can learn both their type and the state if they observe enough outcomes.
+
+In this example, for an agent with a dogmatic belief about their type, a self-defeating equilibrium is one in which the agent 
+chooses an effort level that, under the true $\theta$, yields a frequency of success that is consistent with the agent's 
+misspecified belief. That is, the observed rate of success under the true type and the effort level chosen, 
+$P[\text{sucess}|\theta^*, e]$ is the same as the probability of success under the agent's belief, $P[\text{sucess}|\hat{\theta}, e]$.
+
+In the data-generating process described above, there are six such equilibria. For example, if the agent is of type $\theta_M$  but
+mistakenly believes that he is of type $\hat{\theta}=\theta_H$ and the 
+and $\omega^* = \omega_M$, when the effort chosen is $e_L$, the agent will observe a success with 45% chance. Because the agent 
+dogmatically believes that their type is high, they will erroneously conclude that the rate is $\omega_L$. Under this belief,
+the optimal action is $e_L$ which will continue to generate successes with $45%$ probability, further reinforcing
+the incorrect belief. If the agent were to learn the true type and rate, they would instead choose $e_M$, yielding a 
+success with $65%$ probability and strictly higher expected payoffs.
+
+From @Heidhues2018, we know that if $\theta^*$ and $\omega^*$ are such that there is a self-confirming equilibrium, a dogmatic agent will always
+fall into the trap and continue to make sub-optimal choices. On the other hand, a switcher will be able to learn the true type and state
+as long as their prior is diffused enough and their switching threshold is low enough as in @Ba2023.
+
+By including self-confirming equilibria, the example captures the forces from each of the updating mechanisms discussed in the 
+previous section and allows for direct comparison of all the theories. For realizations of $(\theta, \omega)$ for which there are 
+self-confirming equilibria, the dogmatic agent will fall into the 
+trap whereas the switcher will be able to escape it. Similarly, an agent with self-attribution bias will update their beliefs differently from an unbiased Bayesian, leading
+them to choose different gambles. I exploit such cases in order to test which model is a better fit for how subjects behave in a 
+laboratory experiment.
+
 # Experimental Design
+
+I recruited XXX undergraduate subjects from the CESS lab at NYU who participated in an in-person experiment. Sessions lasted approximately 
+XXX hours and subjects earned an average payment of XXX. The experiment was programmed using oTree [@chen2016otree].
+
+The experiment consisted of 2 treatments: the ego-relevant condition and the stereotype condition. Subjects participated in only one
+of them. Treatments were randomly assigned at the session level. The tasks were identical across treatments, but in the ego condition
+the probability of success was based on the subject's own performance in a quiz, while in the stereotype condition, the probability
+od success was based on the performance of a randomly selected subject from another session.
+
+The experiment had 3 parts. In Part 1 subjects had 2 minutes to answer as many multiple-choice questions as they could from a 
+20 question quiz in a particular topic. They did this for 6 different topics, one after the other. The topics were: Math, Verbal 
+Reasoning, Pop-culture and Art, Science and Technology, US Geography, and Sports and Video Games. The maximum number of questions 
+they could answer correctly was 20. However, they did not know how many questions were available and they were given no feedback.
+
+After taking all 6 quizzes, they proceeded to part 2 where they were asked to guess their score on each of them. In the stereotype 
+treatment they were additionally asked to guess the score of another participant. All they knew about the other participant was their
+gender identity and whether they were US nationals or not.
+For each guess they had three score options: 5 or fewer, between 6 and 15, 
+16 or more. Each of these correspond to $\theta_L$, $\theta_M$, and $\theta_H$ respectively. 
+They were also asked to say how confident they felt about their choices with 4 options: it was a random guess, there is another equally likely score, I am pretty sure, I am completely sure.
+These 4 answers are mapped to priors that place probabilities
+.33, .50, .75, and 1 to the chosen type. The remaining probability is split equally among the other two types. Questions in part 2
+were not incentivized, but subjects were told that providing an accurate answer would increase their chances of earning more money in 
+the last part of the experiment.
+
+In part 3 subjects completed a belief updating task for each of the quizzes. Before starting the task they were reminded of their guess
+for the score. In the ego treatment they were reminded of their guess about themselves and in the stereotype treatment they were reminded
+of their guess about the other participant. In the stereotype treatment, they were also reminded of the characteristics of the other participant.
+
+For one topic at a time and in random order,
+they were presented with the three gambles from the example and were asked to choose one of them. The probability of success was 
+determined by their own score in the ego-relevant condition and by the score of the other participant in the stereotype condition. 
+Subjects had access to the three probability
+tables in the printout on the instructions at all times and the meaning of each cell was explained in detail in the instructions. However, 
+on the screen they had to choose which of the 3 tables they wanted to see before entering their choice in it. This was done as 
+an alternative to a belief elicitation in each round. I take their choice of table to be a noisy measure of their beliefs about
+the underlying type.
+
+Once they have entered their choice, they observe a sample of 10 outcomes from the gamble they chose.
+After observing the outcomes, they returned to the choice screen and entered a new choice.
+In the choice screen
+subjects had access to the entire history of gambles and outcomes for that task. Once they entered 11 gambles (and observed 110 outcomes), they moved on to 
+the next topic and repeated the same procedure. They all did so for all 6 topics.
+
+At the end of the experiment, one of the 6 topics was randomly selected to determine the payment. They earned $\$.20$ for each 
+correct answer in the quiz and for each success in part 3.
 

### 2023-09-04 Paper/draft.Rmd
editing

@@
 # Introduction
+
+# Related Literature
 
@@
 
+EXPLAIN WHY THEY ARE ALWAYS DISAPPOINTED AND UPDATE DOWNWARDS ON OMEGA UNTIL THEY FALL INTO THE TRAP.
+
 ## The Switcher
@@
 
-$$\frac{p[h^t|\tilde{\theta}}{p[h^t|\hat{\theta}]} > \alpha$$
+$$\frac{p[h^t|\tilde{\theta}]}{p[h^t|\hat{\theta}]} > \alpha$$
 
@@
 a self-confirming equilibrium, the switcher might look identical to the dogmatic even in a case where $\alpha$ is not too large.
+
+EXPLAIN HOW THEY MIGHT GET OUT OF THE TRAP.
 
@@
 
+ILLUSTRATE THE DIFFERENT PATHS WITH THE SIMULATION.
+
 # Experimental Design
@@
 
+The answers of part 2 allow me to classify subjects into overconfident, underconfident and correctly specified. If a subject 
+guesses their score to be in a higher category than their true score, they are overconfident. On the contrary, if they guess their
+score to be in a lower category than their true score, they are underconfident. Finally, if they guess their score to be in the same
+category as their true score, they are correctly specified. This classification is done for each of the 6 topics separately.
+
 In part 3 subjects completed a belief updating task for each of the quizzes. Before starting the task they were reminded of their guess
@@
 
+The randomness is controlled throughout the experiment and sessions by setting a seed drawn randomly before the
+first session. By doing this I ensure that any two subjects who have the same type and face the same exogenous rate will observe
+the same outcomes and thus, if they use the same updating procedure, they should be choosing the same gambles.
+This design feature allows me to identify differences in updating procedures across subjects.
+
 # Analysis

### 2023-09-04 Paper/draft.tex
editing

@@
 \author{Jimena Galindo}
-\date{September 03, 2023}
+\date{September 04, 2023}
 
@@
 ALL THE FORCES WE WANT.
-
-An agent is of type \(\theta \in \{\theta_L, \theta_M, \theta_H\}\) with
-\(\theta_H > \theta_M > \theta_L\) and they face an unknown exogenous
-state \(\omega \in \{\omega_L, \omega_M, \omega_H\}\) with
-\(\omega_H>\omega_M>\omega_L\). Each of the values of \(\omega\) is
-realized with equal probability. The agent knows the distribution of
-\(\omega\) but not its value. They also hold some prior belief about
-\(\theta\) which is potentially
-misspecified.\footnote{The particular types of misspecification
-that are allowed are discussed below.} The agent chooses a binary gamble
-\(e in \{e_L, e_M, e_H\}\) and observes whether the gamble is a success
-or a failure. ' If it is a success, the agent gets a payoff of \(1\) and
-if it is a failure, the agent gets a payoff of \(0\). The probability of
-success is increasing in both \(\theta\) and \(\omega\) and is fully
-described in the following table:
-
-\begin{tabular}{ c|c|c|c|}
-
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
-  \cline{2-4}
-  $e_H$ & 50 & 20 & 2 \\
-  \cline{2-4}
-  $e_M$ & 45 & 30 & 7 \\
-  \cline{2-4}
-  $e_L$ & 40 & 25 & 20 \\
-  \cline{2-4}
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_L$} & \multicolumn{1}{c}{}\\
-\end{tabular}
-\hspace{.3cm} 
-\begin{tabular}{ c|c|c|c|}
-
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
-  \cline{2-4}
-  $e_H$ & 80 & 50 & 5 \\
-  \cline{2-4}
-  $e_M$ & 69 & 65 & 30 \\
-  \cline{2-4}
-  $e_L$ & 65 & 45 & 40 \\
-  \cline{2-4}
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_M$} & \multicolumn{1}{c}{}\\
-\end{tabular}
-\hspace{.3cm} 
-\begin{tabular}{ c|c|c|c|}
-
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
-  \cline{2-4}
-  $e_H$ & 98 & 65 & 25 \\
-  \cline{2-4}
-  $e_M$ & 80 & 69 & 35 \\
-  \cline{2-4}
-  $e_L$ & 75 & 55 & 45 \\
-  \cline{2-4}
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_H$} & \multicolumn{1}{c}{}\\
-\end{tabular}
-
-Conditional on a type, the agent's flow payoff is maximized by choosing
-the gamble that matches the state. For example, if the value of
-\(\omega\) is \(\omega_H\), the agent's flow payoff is maximized by
-choosing \(e_H\) and if the state is \(\omega_L\) the flow payoff is
-maximized by choosing gamble \(e_L\). The agent myopically chooses
-gambles every period to maximize the flow payoff for \(T<\infty\)
-periods, and the agent's payoff is the sum of the payoffs from each
-period.
-
-After observing the outcome of each gamble, the agent updates their
-beliefs of both theta and omega in one of 4 different ways: As a
-\emph{dogmatic} as in \citet{Heidhues2018} ; as a \emph{switcher} as in
-\citet{Ba2023} ; as a \emph{self-attribution} updater as in
-\citet{Coutts2020}; or as a fully Bayesian agent. Each of these updating
-rules is described in detail below.
-
-Notice that both \(\theta\) and \(\omega\) can be identified from the
-outcomes if enough variation in the effort choices exists. This can be
-seen by confirming that no two columns are the same. Therefore, the
-agent can learn both their type and the state by observing enough
-outcomes of the gambles for different effort choices.
 
@@
 
+EXPLAIN WHY THEY ARE ALWAYS DISAPPOINTED AND UPDATE DOWNWARDS ON OMEGA
+UNTIL THEY FALL INTO THE TRAP.
+
 \hypertarget{the-switcher}{%
@@
 
-\[\frac{p[h^t|\tilde{\theta}]}{p[h^t|\hat{\theta}]} > \alpha\]
+\[\frac{p[h^t|\tilde{\theta}}{p[h^t|\hat{\theta}]} > \alpha\]
 
@@
 
+EXPLAIN HOW THEY MIGHT GET OUT OF THE TRAP.
+
+\hypertarget{a-simple-example}{%
+\section{A Simple Example}\label{a-simple-example}}
+
+The agent can be of one of 3 types:
+\(\theta \in \{\theta_L, \theta_M, \theta_H\}\) with
+\(\theta_H > \theta_M > \theta_L\). They face an unknown exogenous
+success rate \(\omega \in \{\omega_L, \omega_M, \omega_H\}\) with
+\(\omega_H>\omega_M>\omega_L\). Each of the values of \(\omega\) is
+realized with equal probability. The agent knows the distribution of
+\(\omega\) but not its realized value. Let the true type be \(\theta^*\)
+and the true state be \(\omega^*\).
+
+The agent holds some prior belief about \(\theta\)
+\footnote{which is potentially misspecified as in the dogmatic and switcher cases discussed}
+and chooses a binary gamble \(e in \{e_L, e_M, e_H\}\). The agent
+observes whether the gamble is a success or a failure and gets a payoff
+of \(1\) and if it is a success. They get \(0\) otherwise.
+
+The probability of success is increasing in both \(\theta\) and
+\(\omega\) and is fully described in the following table:
+
+\begin{tabular}{ c|c|c|c|}
+
+  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
+  \cline{2-4}
+  $e_H$ & 50 & 20 & 2 \\
+  \cline{2-4}
+  $e_M$ & 45 & 30 & 7 \\
+  \cline{2-4}
+  $e_L$ & 40 & 25 & 20 \\
+
+  \cline{2-4}
+  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_L$} & \multicolumn{1}{c}{}\\
+\end{tabular}
+\hspace{.3cm} 
+\begin{tabular}{ c|c|c|c|}
+
+  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
+  \cline{2-4}
+  $e_H$ & 80 & 50 & 5 \\
+  \cline{2-4}
+  $e_M$ & 69 & 65 & 30 \\
+  \cline{2-4}
+  $e_L$ & 65 & 45 & 40 \\
+  \cline{2-4}
+  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_M$} & \multicolumn{1}{c}{}\\
+\end{tabular}
+\hspace{.3cm} 
+\begin{tabular}{ c|c|c|c|}
+
+  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
+  \cline{2-4}
+  $e_H$ & 98 & 65 & 25 \\
+  \cline{2-4}
+  $e_M$ & 80 & 69 & 35 \\
+  \cline{2-4}
+  $e_L$ & 75 & 55 & 45 \\
+  \cline{2-4}
+  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_H$} & \multicolumn{1}{c}{}\\
+\end{tabular}
+
+Conditional on a type, the agent's flow payoff is maximized by choosing
+the gamble that matches the state. For example, if the value of
+\(\omega\) is \(\omega_H\), the agent's flow payoff is maximized by
+choosing \(e_H\) and if the state is \(\omega_L\) the flow payoff is
+maximized by choosing gamble \(e_L\). The agent myopically chooses
+gambles every period to maximize the flow payoff for \(T\) periods.
+
+After observing the outcome of each gamble, the agent updates their
+beliefs using some algorithm and moves on to the next period.
+
+Notice that both \(\theta\) and \(\omega\) can be identified from the
+outcomes if enough variation in the effort choices exists. This can be
+seen by confirming there is no pair of \(\theta\) and \(\omega\) such
+that the probability of success is the same for all effort choices.
+Therefore, by changing the effort choice, the agent can learn both their
+type and the state if they observe enough outcomes.
+
+In this example, for an agent with a dogmatic belief about their type, a
+self-defeating equilibrium is one in which the agent chooses an effort
+level that, under the true \(\theta\), yields a frequency of success
+that is consistent with the agent's misspecified belief. That is, the
+observed rate of success under the true type and the effort level
+chosen, \(P[\text{sucess}|\theta^*, e]\) is the same as the probability
+of success under the agent's belief,
+\(P[\text{sucess}|\hat{\theta}, e]\).
+
+In the data-generating process described above, there are six such
+equilibria. For example, if the agent is of type \(\theta_M\) but
+mistakenly believes that he is of type \(\hat{\theta}=\theta_H\) and the
+and \(\omega^* = \omega_M\), when the effort chosen is \(e_L\), the
+agent will observe a success with 45\% chance. Because the agent
+dogmatically believes that their type is high, they will erroneously
+conclude that the rate is \(\omega_L\). Under this belief, the optimal
+action is \(e_L\) which will continue to generate successes with \(45%
+\) probability, further reinforcing the incorrect belief. If the agent
+were to learn the true type and rate, they would instead choose \(e_M\),
+yielding a success with \(65%
+\) probability and strictly higher expected payoffs.
+
+From \citet{Heidhues2018}, we know that if \(\theta^*\) and \(\omega^*\)
+are such that there is a self-confirming equilibrium, a dogmatic agent
+will always fall into the trap and continue to make sub-optimal choices.
+On the other hand, a switcher will be able to learn the true type and
+state as long as their prior is diffused enough and their switching
+threshold is low enough as in \citet{Ba2023}.
+
+By including self-confirming equilibria, the example captures the forces
+from each of the updating mechanisms discussed in the previous section
+and allows for direct comparison of all the theories. For realizations
+of \((\theta, \omega)\) for which there are self-confirming equilibria,
+the dogmatic agent will fall into the trap whereas the switcher will be
+able to escape it. Similarly, an agent with self-attribution bias will
+update their beliefs differently from an unbiased Bayesian, leading them
+to choose different gambles. I exploit such cases in order to test which
+model is a better fit for how subjects behave in a laboratory
+experiment.
+
+ILLUSTRATE THE DIFFERENT PATHS WITH THE SIMULATION.
+
 \hypertarget{experimental-design}{%
 \section{Experimental Design}\label{experimental-design}}
+
+I recruited XXX undergraduate subjects from the CESS lab at NYU who
+participated in an in-person experiment. Sessions lasted approximately
+XXX hours and subjects earned an average payment of XXX. The experiment
+was programmed using oTree \citep{chen2016otree}.
+
+The experiment consisted of 2 treatments: the ego-relevant condition and
+the stereotype condition. Subjects participated in only one of them.
+Treatments were randomly assigned at the session level. The tasks were
+identical across treatments, but in the ego condition the probability of
+success was based on the subject's own performance in a quiz, while in
+the stereotype condition, the probability od success was based on the
+performance of a randomly selected subject from another session.
+
+The experiment had 3 parts. In Part 1 subjects had 2 minutes to answer
+as many multiple-choice questions as they could from a 20 question quiz
+in a particular topic. They did this for 6 different topics, one after
+the other. The topics were: Math, Verbal Reasoning, Pop-culture and Art,
+Science and Technology, US Geography, and Sports and Video Games. The
+maximum number of questions they could answer correctly was 20. However,
+they did not know how many questions were available and they were given
+no feedback.
+
+After taking all 6 quizzes, they proceeded to part 2 where they were
+asked to guess their score on each of them. In the stereotype treatment
+they were additionally asked to guess the score of another participant.
+All they knew about the other participant was their gender identity and
+whether they were US nationals or not. For each guess they had three
+score options: 5 or fewer, between 6 and 15, 16 or more. Each of these
+correspond to \(\theta_L\), \(\theta_M\), and \(\theta_H\) respectively.
+They were also asked to say how confident they felt about their choices
+with 4 options: it was a random guess, there is another equally likely
+score, I am pretty sure, I am completely sure. These 4 answers are
+mapped to priors that place probabilities .33, .50, .75, and 1 to the
+chosen type. The remaining probability is split equally among the other
+two types. Questions in part 2 were not incentivized, but subjects were
+told that providing an accurate answer would increase their chances of
+earning more money in the last part of the experiment.
+
+The answers of part 2 allow me to classify subjects into overconfident,
+underconfident and correctly specified. If a subject guesses their score
+to be in a higher category than their true score, they are
+overconfident. On the contrary, if they guess their score to be in a
+lower category than their true score, they are underconfident. Finally,
+if they guess their score to be in the same category as their true
+score, they are correctly specified. This classification is done for
+each of the 6 topics separately.
+
+In part 3 subjects completed a belief updating task for each of the
+quizzes. Before starting the task they were reminded of their guess for
+the score. In the ego treatment they were reminded of their guess about
+themselves and in the stereotype treatment they were reminded of their
+guess about the other participant. In the stereotype treatment, they
+were also reminded of the characteristics of the other participant.
+
+For one topic at a time and in random order, they were presented with
+the three gambles from the example and were asked to choose one of them.
+The probability of success was determined by their own score in the
+ego-relevant condition and by the score of the other participant in the
+stereotype condition. Subjects had access to the three probability
+tables in the printout on the instructions at all times and the meaning
+of each cell was explained in detail in the instructions. However, on
+the screen they had to choose which of the 3 tables they wanted to see
+before entering their choice in it. This was done as an alternative to a
+belief elicitation in each round. I take their choice of table to be a
+noisy measure of their beliefs about the underlying type.
+
+Once they have entered their choice, they observe a sample of 10
+outcomes from the gamble they chose. After observing the outcomes, they
+returned to the choice screen and entered a new choice. In the choice
+screen subjects had access to the entire history of gambles and outcomes
+for that task. Once they entered 11 gambles (and observed 110 outcomes),
+they moved on to the next topic and repeated the same procedure. They
+all did so for all 6 topics.
+
+At the end of the experiment, one of the 6 topics was randomly selected
+to determine the payment. They earned \(\$.20\) for each correct answer
+in the quiz and for each success in part 3.
+
+The randomness is controlled throughout the experiment and sessions by
+setting a seed drawn randomly before the first session. By doing this I
+ensure that any two subjects who have the same type and face the same
+exogenous rate will observe the same outcomes and thus, if they use the
+same updating procedure, they should be choosing the same gambles. This
+design feature allows me to identify differences in updating procedures
+across subjects.
 

### 2023-09-04 Paper/draft.Rmd
framework start

@@
 
-REWRITE IN GENERAL TERMS WITH THE PROBABILITY BEING GIVEN BY A FUNCTION THAT SATIEFIES ALL THE PROPERTIES IN BA SO THAT I CAN 
-REFER TO HER RESULTS.
-THEN EXPAND ON THE EXAMPLE FOR THE LAB AND SAY WHY IT CAPTURES ALL THE FORCES WE WANT.
+An agent is of type $\theta \in \Theta$ and faces an unknown exogenous state $\omega$ drawn from some 
+density $f$ over $\Omega$. The agent knows the 
+distribution of $\omega$ but not its realized value. His prior belief about his type is $p_0(\theta)$ and his belief about the state
+state $p_0(\omega)$ coincides with the true distribution $f$. Let the agent's type be $\theta^*$ and the realized state be $\omega^*$.
+
+An agent has a \emph{misspecified} belief if the prior assigns probability zero to their true type. Furthermore, the agent is 
+\emph{dogmatic} if he holds a degenerate belief that places probability one on being a particular type, $\hat{\theta}$. A dogmatic 
+agent can be dogmatic and misspecified. That means that $\hat{\theta} \neq \theta^*$ and $p_0(\hat{\theta}) = 1$.
+
+The agent chooses an action $a\in A$ and observes an outcome $h\in H$. 
+The outcome is a function of the agent's type, the state, and
+the action. In particular $h(\theta^*, \omega^*, a)$ is increasing in both $\theta^*$ and $\omega^*$. And is such that Conditional
+on a pair of parameters $(\theta, \omega)$, there is a unique optimal action.
+
+## Example
+
+Set $A = \Omega = $ and $H = [0, \infty)$ and consider a student with intrinsic ability $\theta^*\geq 0$ who faces a grading procedure $\omega^*$ that is unknown to them. However, 
+they know that a higher $\omega^*$ is more likely to yield a higher grade. In particular, assume the grade is given by 
+$(\theta^*+a)\omega^*$.
+
+The student must choose an effort level $a$ which will
+determine their grade. For whatever the chosen effort level is, the agent must pay a cost $c(a) = \frac{1}{2}a^2$. Therefore, the 
+student's payoff is given by
+
+\begin{equation}
+u(a; \theta^*, \omega^*) = (\theta^*+a)\omega^* - \frac{1}{2}a^2
+\end{equation}
 
@@
 
-In the data-generating process described above, there are six such equilibria. For example, if the agent is of type $\theta_M$  but
+In the data-generating process described above, there are five such equilibria. For example, if the agent is of type $\theta_M$  but
 mistakenly believes that he is of type $\hat{\theta}=\theta_H$ and the 

### 2023-09-05 Paper/draft.Rmd
editing outline

@@
 
-# Framework
+# Setting 1
 
@@
 An agent has a \emph{misspecified} belief if the prior assigns probability zero to their true type. Furthermore, the agent is 
-\emph{dogmatic} if he holds a degenerate belief that places probability one on being a particular type, $\hat{\theta}$. A dogmatic 
-agent can be dogmatic and misspecified. That means that $\hat{\theta} \neq \theta^*$ and $p_0(\hat{\theta}) = 1$.
+\emph{dogmatic} if he holds a degenerate belief that places probability one on being a particular type, $\hat{\theta}$. An 
+agent can be dogmatic and misspecified; that means that $\hat{\theta} \neq \theta^*$ and $p_0(\hat{\theta}) = 1$.
 
-The agent chooses an action $a\in A$ and observes an outcome $h\in H$. 
+The agent chooses an action $a\in A$ and observes a noisy outcome $h\in H$. 
 The outcome is a function of the agent's type, the state, and
-the action. In particular $h(\theta^*, \omega^*, a)$ is increasing in both $\theta^*$ and $\omega^*$. And is such that Conditional
-on a pair of parameters $(\theta, \omega)$, there is a unique optimal action.
+the action. In particular $h = h(\theta^*, \omega^*, a) + \varepsilon$ with $h(\cdot)$ increasing in both $\theta^*$ and $\omega^*$, 
+and such that conditional on a pair of parameters $(\theta, \omega)$, there is a unique optimal action. 
+$\varepsilon\sim N(0, \sigma)$ is noise in the output.
 
-## Example
+After observing the outcome, the agent updates his beliefs about $\theta$ and $\omega$ using some algorithm and moves on to the next period.
+He repeats this process infinitely many times. I make the simplifying assumption that the agent is myopic and chooses the action 
+that maximizes the payoff in each period. This assumption is symplifies the analysis and plays a role on whether an agent who updates
+ their beliefs using bayes rule would learn the truth or not.
 
-Set $A = \Omega = $ and $H = [0, \infty)$ and consider a student with intrinsic ability $\theta^*\geq 0$ who faces a grading procedure $\omega^*$ that is unknown to them. However, 
+A key notion in this setting is that of a self-defeating equilibrium\footnote{This notion is an adaptation of the Berk-Nash equilibrium in 
+@Esponda2016 to this setting with only one agent}. 
+A \emph{self-defeating equilibrium} is a belief and action pair such that the agent's belief about their type is misspecified and the 
+outcome generated by the action is consistent with the misspecified belief. The average outcome under the true type and the true 
+state equals the average output the agent expects under the misspecified belief. In addition, the agent's belief is said to be 
+\emph{stable} when this happens.
+
+Within this framework, I consider two nested theories of belief updating. The first one is a dogmatic modeler from @Heidhues2018.
+The second one is a switcher, as in @Ba2023. The dogmatic modeler can be seen as a switcher with an infinitely sticky initial belief
+and this is the sense in which the two are nested. Both theories produce different predictions with respect to the equilibrium outcome.
+
+## The Dogmatic Modeler
+
+A dogmatic agent does not update their beliefs about $\theta$; instead he holds a degenerate belief that places probability one 
+on being a particular type, $\hat{\theta}$, which is potentially not his true type. 
+In this case, no matter
+how much information he gathers against being of type $\hat{\theta}$, he will not update his beliefs. Any discrepancies between the 
+observed outcomes and his believed type are incorporated using the Bayes rule to update their beliefs about $\omega$. 
+This means the dogmatic agent will never learn their true type if they startu off as being misspecified.
+
+@Heidhues2018 show that, under certain assumptions on the per-period utility,\footnote{The assumptions are that 
+$u$ is twice continuously differentiable with: (i)$u_{ee}<0$ and $u_e(\underline{e} \theta, \omega)>0>u_e(\Bar{e}, \theta, \omega)$, 
+(ii) $u_{\theta}, u_{\omega}>0$ and (iii) $u_{e\theta}<0$ and $u_{e\omega}>0$. The direction of the derivatives is a normalization
+and the results would hold even when the signs are reversed.} 
+a dogmatic modeler will inevitably fall into a self-defeating equilibrium. The equilibrium will be such that
+the outcomes they observe reinforce their belief on $\omega$ in such a way that as $t\to\infty$ the agent will be sure that
+the state is some $\omega^{'}$ consistent with their believed type and the observed data. In other words, 
+they will be in a self-defeating equilibrium whith a stable belief that places probability one on the incorrect
+parameters $(\hat{theta}, \omega_\infty)$
+
+The mechanism by which the dogmatic agent falls into the self-defeating equilibrium is the following: Suppose the agent holds the 
+misspecified belief that they are type $\hat{\theta}>\theta^*$. For any prior over $\omega$, the agent will be disappointed by the outcome.
+He expected a gain of $h(\hat{\theta}, \mathbb{E}(\omega), a)$ but instead observes  $h(\hat{\theta}, \omega^*, a)$. 
+There are two 
+possible sources for the disappointment, the first is that the realized state is lower than the expected state. The second source is that the
+agent is of type $\theta^*$ and therefore, for all possible states, his gain will be lower than what he expected. Because the agent is dogmatic,
+he will not update his beliefs about $\theta$ and as a consequence will attribute the disappointment to the state being lower than expected.
+He will continue to update in ths way until he converges to a belief about $\omega$ that is stable. Such a belief will 
+explain the observed utility perfectly and allow the agent to rationalize his dogmatic belief about $\theta$. 
+Under the assumptions of @Heidhues2018, there is a unique value of $\omega$ at which the belief is stable, I will refer to such value
+as $\omega_\infty$.
+This mechanism is further illustrated in Example 1.
+
+**Example 1: ** 
+_Set $A = \Omega$ and $H = [0, \infty)$ and consider a student with intrinsic ability $\theta^*\geq 0$ who faces a grading procedure 
+$\omega^*$ that is unknown to them. However, 
 they know that a higher $\omega^*$ is more likely to yield a higher grade. In particular, assume the grade is given by 
@@
 
-The student must choose an effort level $a$ which will
-determine their grade. For whatever the chosen effort level is, the agent must pay a cost $c(a) = \frac{1}{2}a^2$. Therefore, the 
-student's payoff is given by
+The student must choose an effort level $a$, which determines their grade. For whatever the chosen effort level, 
+the agent must pay a cost $c(a) = \frac{1}{2}a^2$. And he repeats this process for infinitely many periods. 
+Assume also that the student's prior is such that $mathbb{E}[\omega]= \omega^*$ and he is dogmatic about being of 
+type $\hat{\theta}>\theta^*. \footnote{The example is illustrated for an overconfident agent but the results are symmetric for a digmatic agent who initially 
+places probability one on some $\tilde{\theta}<\theta^*$.}
+Therefore, the student's payoff in period $t$ is given by
 
 \begin{equation}
-u(a; \theta^*, \omega^*) = (\theta^*+a)\omega^* - \frac{1}{2}a^2
+u_t(a_t; \theta^*, \omega^*) = (\theta^*+a_t)\omega^* - \frac{1}{2}a^2 + \varepsilon_t
 \end{equation}
 
-## The Bayesian Benchmark
+Under this specification, the myopic optimal effort level is $a_t^* = \omega^*$. Nonetheless, because the agent does not know $\omega^*$,
+he will choose $a_t = \mathbb{E}_t(\omega)$ where the expectation is taken with respect to the agent's belief at the beginning of
+period $t$. If he does not revise his effort choice for $k$ periods, he will receive 
+an average utility of 
+$(\theta^*+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}$ but he was expecting an average utility of 
+$(\hat{\theta}\theta+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}$. In response, he will apply bayes rule to update his beliefs about
+$\omega$ to get the posterior belief with $\mathbb_{t+k}[\omega] = \frac{(\theta^* + \omega^*)\omega^*}{(\hat{\theta} + \omega^*)}$
+which is lower than the initial belief. This will cause the agent to choose a lower effort at $t+k$. As a result, he will again
+receive an average utlitity that is lower than what he expected which will cause his belief to drift further down. This process will
+continue until the average utility equals his expected utility under the dogmatic belief that assigns probability 1 to $\hat{\theta}$. 
+At that point, the stundent will have reached a self-defeating equilibrium and he will continue to choose sub-optimal effort forever._
+
+Although the model of a dogmatic modeler is able to rationalize the prevalence of overconfident (underconfident) beliefs, the
+assumption that the agent has a degenerate belief and no mechanism through which he can update such belief is very restrictive. An
+alternative approach is proposed by @Ba2023. She proposes an extension of the dogmatic agent who is able to jump from one dogmatic 
+belief to another. By doing so, the agent might end up being dogmatic and correctly speciefied.
+
+## The Switcher
+
+An agent is a \emph{switcher} if they behave as a dogmatic, but is willing to entertain the possibility that they are of a different type.
+In particular, when they start off as a misspecified dogmatic, they are willing to switch to a different dogmatic belief if the data is
+convincing enough. Notice that their beliefs are still degenerate and assign probability one to a particular type, and zero to 
+all other types. This means that a bayesian update on $\theta$ would cause no change in their beliefs.
+However, they are willing to entertain two such beliefs and have a mechanism by which they decide which belief to adopt at any period $t$.
+
+In order to abandon their initial dogmatic belief, the agent needs to observe a sequence of outcomes that are sufficiently unlikely
+to have happened if they were of the type they initially believed. They do so by keeping track of the likelihood that each of the
+possible types generated the data. If the likelihood ratio is sufficiently large, the agent will switch to the alternative
+and behave as if they are dogmatic about the new type.
+
+In particular, for an agent that starts off with a dogmatic belief that they are of type $\hat{\theta}$ but is willing to consider
+the alternative explanation that they are of type $\tilde{\theta}$, the agent will switch to the alternative if:
+
+$$\frac{p[h^t|\tilde{\theta}]}{p[h^t|\hat{\theta}]} > \alpha$$
+
+Where $h^t$ is the history of outcomes up to time $t$ and $\alpha \geq 1$ is a threshold that determines how convincing the data needs to be
+for the agent to change their belief. Notice that if $\alpha \to \infty$, we get the dogmatic agent. In this sense, the 
+switcher is a generalization of the dogmatic type, just as the self-attribution agent is a generalization of the Bayesian agent.
+
+By allowing the agent to keep track of the likelihoods and switching to an alternative type, the switcher can avoid the 
+self-confirming equilibrium the dogmatic agent falls into. However, if the prior belief on $theta$ is sufficiently tight around
+a self-confirming equilibrium, the switcher might look identical to the dogmatic even in a case where $\alpha$ is not too large.
+
+** Example 1 (continued)** 
+_ Take the same student from the example and now add the possibility of switching beliefs. _
+
+# Seting 2
+
+## The Bayesian
 
@@
 their prior beliefs about $\theta$ and $\omega$. Since agents are myopic, even though all the parameters could be identified with enough variation in choices,
+
 a fully Bayesian agent might not learn their true type. This happens because they do not internalize the tradeoff between flow payoff
@@
 
-## A Biased Agent
+## The Biased Agent
 An agent that updates their beliefs with self-attribution bias will update their beliefs about the state $\omega$ and their type $\theta$
@@
 
-## The Dogmatic Agent
-
-A dogmatic agent does not update their beliefs about $\theta$; instead,
-they hold a degenerate belief that places probability one on being a particular type, $\hat{\theta}$. For instance, the dogmatic agent 
-might be of type $\hat{\theta} = \theta_M$ but holds a belief that places probability one on being of type $\theta_H$. In this case, no matter
-how much information he gathers against being of type $\theta_H$, he will not update his beliefs. Any discrepancies between the 
-observed outcomes are incorporated using the Bayes rule to update their beliefs about $\omega$. This results in the following
-posterior odds:
-
-\begin{equation}
-\frac{p_{t}[\omega_H|\text{outcome}]}{p_{t}[\omega_M|\text{outcome}]} = 
-      \frac{p[\text{outcome}|\omega_H, \hat{\theta}, e]p_{t-1}[\omega_H]}{p[\text{outcome}|\omega_M, \hat{\theta}, e]p_{t-1}[\omega_M]}
-\end{equation}
-and
-\begin{equation}
-\frac{p_{t}[\omega_M|\text{outcome}]}{p_{t}[\omega_L|\text{outcome}]} = 
-      \frac{p[\text{outcome}|\omega_M, \hat{\theta}, e]p_{t-1}[\omega_M]}{p[\text{outcome}|\omega_L, \hat{\theta}, e]p_{t-1}[\omega_L]}
-\end{equation}
-
-A crucial difference between the dogmatic agent and the Bayesian agent is that the dogmatic agent does not aggregate across 
-types when updating their beliefs about $\omega$. This means the dogmatic agent will never learn their true type if they are 
-misspecified.
-
-@Heidhues2018 show that in a setting such as ours, a dogmatic modeler will inevitably fall into a self-confirming equilibrium where
-the outcomes they observe reinforce their belief on $\omega$ in such a way that as $t\to\infty$ the agent will be certain that
-the state is some $\omega^*$ consistent with their believed type and the observed data.
-
-EXPLAIN WHY THEY ARE ALWAYS DISAPPOINTED AND UPDATE DOWNWARDS ON OMEGA UNTIL THEY FALL INTO THE TRAP.
-
-## The Switcher
-
-An agent is a \emph{switcher} if they behave as a dogmatic but is willing to entertain the possibility that they are of a different type.
-In particular, when they start off as a misspecified dogmatic, they are willing to switch to a different dogmatic belief if the data is
-convincing enough.
-
-In order to abandon their initial dogmatic belief, the agent needs to observe a sequence of outcomes that are sufficiently unlikely
-to have happened if they were of the type they initially believed. They do so by keeping track of the likelihood that each of the
-possible types generated the data. If the likelihood ratio is sufficiently large, the agent will switch to the alternative
-and behave as if they are dogmatic about the new type.
-
-In particular, for an agent that starts off with a dogmatic belief that they are of type $\hat{\theta}$ but is willing to consider
-the alternative explanation that they are of type $\tilde{\theta}$, the agent will switch to the alternative if:
-
-$$\frac{p[h^t|\tilde{\theta}]}{p[h^t|\hat{\theta}]} > \alpha$$
-
-Where $h^t$ is the history of outcomes up to time $t$ and $\alpha \geq 1$ is a threshold that determines how convincing the data needs to be
-for the agent to change their belief. Notice that if $\alpha \to \infty$, we get the dogmatic agent. In this sense, the 
-switcher is a generalization of the dogmatic type, just as the self-attribution agent is a generalization of the Bayesian agent.
-
-By allowing the agent to keep track of the likelihoods and switching to an alternative type, the switcher can avoid the 
-self-confirming equilibrium the dogmatic agent falls into. However, if the prior belief on $theta$ is sufficiently tight around
-a self-confirming equilibrium, the switcher might look identical to the dogmatic even in a case where $\alpha$ is not too large.
-
-EXPLAIN HOW THEY MIGHT GET OUT OF THE TRAP.
-
-# A Simple Example
+# A Unifying Framework
 The agent can be of one of 3 types: $\theta \in \{\theta_L, \theta_M, \theta_H\}$  with $\theta_H > \theta_M > \theta_L$.
@@
 The agent knows the distribution of $\omega$ but not its realized value. Let the true type be $\theta^*$ 
-and the true state be $\omega^*$.
+and let the true state be $\omega^*$.
 
@@
 
+## The Dogmatic Modeler
+
+A dogmatic modeler updates their beliefs about omega by using bayes rule. For the example, that means he ends up with the following
+posterior odds ratios:
+
+\begin{equation}
+\frac{p_{t}[\omega_H|\text{outcome}]}{p_{t}[\omega_M|\text{outcome}]} = 
+      \frac{p[\text{outcome}|\omega_H, \hat{\theta}, e]p_{t-1}[\omega_H]}{p[\text{outcome}|\omega_M, \hat{\theta}, e]p_{t-1}[\omega_M]}
+\end{equation}
+and
+\begin{equation}
+\frac{p_{t}[\omega_M|\text{outcome}]}{p_{t}[\omega_L|\text{outcome}]} = 
+      \frac{p[\text{outcome}|\omega_M, \hat{\theta}, e]p_{t-1}[\omega_M]}{p[\text{outcome}|\omega_L, \hat{\theta}, e]p_{t-1}[\omega_L]}
+\end{equation}
+
 # Experimental Design

### 2023-09-05 Paper/draft.tex
editing outline

@@
 \author{Jimena Galindo}
-\date{September 04, 2023}
+\date{September 05, 2023}
 
@@
 
-\hypertarget{framework}{%
-\section{Framework}\label{framework}}
+\hypertarget{related-literature}{%
+\section{Related Literature}\label{related-literature}}
 
-REWRITE IN GENERAL TERMS WITH THE PROBABILITY BEING GIVEN BY A FUNCTION
-THAT SATIEFIES ALL THE PROPERTIES IN BA SO THAT I CAN REFER TO HER
-RESULTS. THEN EXPAND ON THE EXAMPLE FOR THE LAB AND SAY WHY IT CAPTURES
-ALL THE FORCES WE WANT.
+\hypertarget{framework-1}{%
+\section{Framework 1}\label{framework-1}}
+
+An agent is of type \(\theta \in \Theta\) and faces an unknown exogenous
+state \(\omega\) drawn from some density \(f\) over \(\Omega\). The
+agent knows the distribution of \(\omega\) but not its realized value.
+His prior belief about his type is \(p_0(\theta)\) and his belief about
+the state state \(p_0(\omega)\) coincides with the true distribution
+\(f\). Let the agent's type be \(\theta^*\) and the realized state be
+\(\omega^*\).
+
+An agent has a \emph{misspecified} belief if the prior assigns
+probability zero to their true type. Furthermore, the agent is
+\emph{dogmatic} if he holds a degenerate belief that places probability
+one on being a particular type, \(\hat{\theta}\). A dogmatic agent can
+be dogmatic and misspecified. That means that
+\(\hat{\theta} \neq \theta^*\) and \(p_0(\hat{\theta}) = 1\).
+
+The agent chooses an action \(a\in A\) and observes a noisy outcome
+\(h\in H\). The outcome is a function of the agent's type, the state,
+and the action. In particular
+\(h = h(\theta^*, \omega^*, a) + \varepsilon\) with \(h(\cdot)\)
+increasing in both \(\theta^*\) and \(\omega^*\); and such that
+conditional on a pair of parameters \((\theta, \omega)\), there is a
+unique optimal action. \(\varepsilon\sim N(0, \sigma)\) is noise in the
+output.
+
+After observing the outcome, the agent updates his beliefs about
+\(\theta\) and \(\omega\) using some algorithm and moves on to the next
+period. He repeats this process infinitely many times. I make the
+simplifying assumption that the agent is myopic and chooses the action
+that maximizes the payoff in each period. This assumption is crucial for
+the results as the agent will not trade off the flow payoff for learning
+the truth as a forward-looking agent would.
+
+Within this framework, I consider two nested theories of belief
+updating. The first one is a dogmatic modeler from \citet{Heidhues2018}.
+The second one is a switcher, as in \citet{Ba2023}. The dogmatic modeler
+can be seen as a switcher with an infinitely sticky initial belief and
+this is the sense in which the two are nested.
+
+A key notion in this setting is that of a self-defeating
+equilibrium\footnote{This notion is an adaptation of the Berk-Nash equilibrium in 
+@Esponda2016}. A \emph{self-defeating equilibrium} is a belief and
+action pair such that the agent's belief about their type is
+misspecified and the outcome generated by the action is consistent with
+the misspecified belief. The average outcome under the true type and the
+true state equals the average output the agent expects under the
+misspecified belief. In addition, the agent's belief is said to be
+\emph{stable} when this happens.
+
+\hypertarget{the-dogmatic-modeler}{%
+\subsection{The Dogmatic Modeler}\label{the-dogmatic-modeler}}
+
+A dogmatic agent does not update their beliefs about \(\theta\); instead
+he holds a degenerate belief that places probability one on being a
+particular type, \(\hat{\theta}\), which is potentially not his true
+type. In this case, no matter how much information he gathers against
+being of type \(\hat{\theta}\), he will not update his beliefs. Any
+discrepancies between the observed outcomes and his believed type are
+incorporated using the Bayes rule to update their beliefs about
+\(\omega\).
+
+A key difference between the dogmatic agent and a fully Bayesian agent
+is that the dogmatic agent does not aggregate across types when updating
+their beliefs about \(\omega\). This means the dogmatic agent will never
+learn their true type if they are misspecified.
+
+\citet{Heidhues2018} show that, under certain assumptions on the
+per-period utility,\footnote{The assumptions are that 
+$u$ is twice continuously differentiable with: (i)$u_{ee}<0$ and $u_e(\underline{e} \theta, \omega)>0>u_e(\Bar{e}, \theta, \omega)$, 
+(ii) $u_{\theta}, u_{\omega}>0$ and (iii) $u_{e\theta}<0$ and $u_{e\omega}>0$. The direction of the derivatives is a normalization
+and the results would hold even when the signs are reversed.} about the
+outcome \(h\), a dogmatic modeler will inevitably fall into a
+self-defeating equilibrium where the outcomes they observe reinforce
+their belief on \(\omega\) in such a way that as \(t\to\infty\) the
+agent will be sure that the state is some \(\omega^{'}\) consistent with
+their believed type and the observed data.
+
+The mechanism by which the dogmatic agent falls into the self-defeating
+equilibrium is the following: Suppose the agent holds the misspecified
+belief that they are type \(\hat{\theta}>\theta^*\). For any prior over
+\(\omega\), the agent will be disappointed by the outcome; he expected a
+gain of \(h(\hat{\theta}, \mathbb{E}(\omega), a)\) but instead observes
+\(h(\hat{\theta}, \omega^*, a)\). There are two possible sources for the
+disappointment. The first is that the realized state is lower than the
+expected state. The second is that the agent is of type \(\theta^*\) and
+thus for all possible states, his gain will be lower than what he
+expected. Because the agent is dogmatic, he will not update his beliefs
+about \(\theta\) and thus will attribute the disappointment to the state
+being lower than expected. \citet{Heidhues2018} give sufficient
+conditions for the agent to fall into a self-confirming equilibrium
+where the agent will continue to choose an action that reinforces an
+incorrect belief about the state. This force is illustrated in Example
+1.
+
+\textbf{Example 1: } Set \(A = \Omega\) and \(H = [0, \infty)\) and
+consider a student with intrinsic ability \(\theta^*\geq 0\) who faces a
+grading procedure \(\omega^*\) that is unknown to them. However, they
+know that a higher \(\omega^*\) is more likely to yield a higher grade.
+In particular, assume the grade is given by \((\theta^*+a)\omega^*\).
+
+The student must choose an effort level \(a\), which determines their
+grade. For whatever the chosen effort level, the agent must pay a cost
+\(c(a) = \frac{1}{2}a^2\). And he repeats this process for infinitely
+many periods. Assume also that the student's prior is such that
+\(mathbb{E}[\omega]= \omega^*\). Therefore, the student's payoff in
+period \(t\) is given by
+
+\begin{equation}
+u_t(a_t; \theta^*, \omega^*) = (\theta^*+a_t)\omega^* - \frac{1}{2}a^2 + \varepsilon_t
+\end{equation}
+
+Under this specification, the myopic optimal effort level is
+\(a_t^* = \omega^*\). Nonetheless, because the agent does not know
+\(\omega^*\), he will choose \(a_t = \mathbb{E}_t(\omega)\) where the
+expectation is taken with respect to the agent's belief at the beginning
+of period \(t\). If he does not revise his effort choice for multiple
+periods, he will observe an average grade of
+\((\theta^*+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}\) but he was expecting
+an average grade of
+\((\hat{\theta}\theta+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}\)
 
@@
 and \(\omega\). Since agents are myopic, even though all the parameters
-could be identified with enough variation in choices, a fully Bayesian
-agent might not learn their true type. This happens because they do not
-internalize the tradeoff between flow payoff and learning and thus might
-not experiment enough to learn their type. An alternative to this
-approach is given by \citet{Hestermann2021} and is discussed with the
-results.
+could be identified with enough variation in choices,
 
-\hypertarget{a-biased-agent}{%
-\subsection{A Biased Agent}\label{a-biased-agent}}
+\hypertarget{the-switcher}{%
+\subsection{The Switcher}\label{the-switcher}}
+
+An agent is a \emph{switcher} if they behave as a dogmatic but is
+willing to entertain the possibility that they are of a different type.
+In particular, when they start off as a misspecified dogmatic, they are
+willing to switch to a different dogmatic belief if the data is
+convincing enough.
+
+In order to abandon their initial dogmatic belief, the agent needs to
+observe a sequence of outcomes that are sufficiently unlikely to have
+happened if they were of the type they initially believed. They do so by
+keeping track of the likelihood that each of the possible types
+generated the data. If the likelihood ratio is sufficiently large, the
+agent will switch to the alternative and behave as if they are dogmatic
+about the new type.
+
+In particular, for an agent that starts off with a dogmatic belief that
+they are of type \(\hat{\theta}\) but is willing to consider the
+alternative explanation that they are of type \(\tilde{\theta}\), the
+agent will switch to the alternative if:
+
+\[\frac{p[h^t|\tilde{\theta}]}{p[h^t|\hat{\theta}]} > \alpha\]
+
+Where \(h^t\) is the history of outcomes up to time \(t\) and
+\(\alpha \geq 1\) is a threshold that determines how convincing the data
+needs to be for the agent to change their belief. Notice that if
+\(\alpha \to \infty\), we get the dogmatic agent. In this sense, the
+switcher is a generalization of the dogmatic type, just as the
+self-attribution agent is a generalization of the Bayesian agent.
+
+By allowing the agent to keep track of the likelihoods and switching to
+an alternative type, the switcher can avoid the self-confirming
+equilibrium the dogmatic agent falls into. However, if the prior belief
+on \(theta\) is sufficiently tight around a self-confirming equilibrium,
+the switcher might look identical to the dogmatic even in a case where
+\(\alpha\) is not too large.
+
+EXPLAIN HOW THEY MIGHT GET OUT OF THE TRAP.
+
+\hypertarget{the-bayesian-agent}{%
+\subsection{The Bayesian Agent}\label{the-bayesian-agent}}
+
+a fully Bayesian agent might not learn their true type. This happens
+because they do not internalize the tradeoff between flow payoff and
+learning and thus might not experiment enough to learn their type. An
+alternative to this approach is given by \citet{Hestermann2021} and is
+discussed with the results.
+
+\hypertarget{the-biased-agent}{%
+\subsection{The Biased Agent}\label{the-biased-agent}}
 
@@
 
-\hypertarget{the-dogmatic-agent}{%
-\subsection{The Dogmatic Agent}\label{the-dogmatic-agent}}
-
-A dogmatic agent does not update their beliefs about \(\theta\);
-instead, they hold a degenerate belief that places probability one on
-being a particular type, \(\hat{\theta}\). For instance, the dogmatic
-agent might be of type \(\hat{\theta} = \theta_M\) but holds a belief
-that places probability one on being of type \(\theta_H\). In this case,
-no matter how much information he gathers against being of type
-\(\theta_H\), he will not update his beliefs. Any discrepancies between
-the observed outcomes are incorporated using the Bayes rule to update
-their beliefs about \(\omega\). This results in the following posterior
-odds:
-
-\begin{equation}
-\frac{p_{t}[\omega_H|\text{outcome}]}{p_{t}[\omega_M|\text{outcome}]} = 
-      \frac{p[\text{outcome}|\omega_H, \hat{\theta}, e]p_{t-1}[\omega_H]}{p[\text{outcome}|\omega_M, \hat{\theta}, e]p_{t-1}[\omega_M]}
-\end{equation} and \begin{equation}
-\frac{p_{t}[\omega_M|\text{outcome}]}{p_{t}[\omega_L|\text{outcome}]} = 
-      \frac{p[\text{outcome}|\omega_M, \hat{\theta}, e]p_{t-1}[\omega_M]}{p[\text{outcome}|\omega_L, \hat{\theta}, e]p_{t-1}[\omega_L]}
-\end{equation}
-
-A crucial difference between the dogmatic agent and the Bayesian agent
-is that the dogmatic agent does not aggregate across types when updating
-their beliefs about \(\omega\). This means the dogmatic agent will never
-learn their true type if they are misspecified.
-
-\citet{Heidhues2018} show that in a setting such as ours, a dogmatic
-modeler will inevitably fall into a self-confirming equilibrium where
-the outcomes they observe reinforce their belief on \(\omega\) in such a
-way that as \(t\to\infty\) the agent will be certain that the state is
-some \(\omega^*\) consistent with their believed type and the observed
-data.
-
-EXPLAIN WHY THEY ARE ALWAYS DISAPPOINTED AND UPDATE DOWNWARDS ON OMEGA
-UNTIL THEY FALL INTO THE TRAP.
-
-\hypertarget{the-switcher}{%
-\subsection{The Switcher}\label{the-switcher}}
-
-An agent is a \emph{switcher} if they behave as a dogmatic but is
-willing to entertain the possibility that they are of a different type.
-In particular, when they start off as a misspecified dogmatic, they are
-willing to switch to a different dogmatic belief if the data is
-convincing enough.
-
-In order to abandon their initial dogmatic belief, the agent needs to
-observe a sequence of outcomes that are sufficiently unlikely to have
-happened if they were of the type they initially believed. They do so by
-keeping track of the likelihood that each of the possible types
-generated the data. If the likelihood ratio is sufficiently large, the
-agent will switch to the alternative and behave as if they are dogmatic
-about the new type.
-
-In particular, for an agent that starts off with a dogmatic belief that
-they are of type \(\hat{\theta}\) but is willing to consider the
-alternative explanation that they are of type \(\tilde{\theta}\), the
-agent will switch to the alternative if:
-
-\[\frac{p[h^t|\tilde{\theta}}{p[h^t|\hat{\theta}]} > \alpha\]
-
-Where \(h^t\) is the history of outcomes up to time \(t\) and
-\(\alpha \geq 1\) is a threshold that determines how convincing the data
-needs to be for the agent to change their belief. Notice that if
-\(\alpha \to \infty\), we get the dogmatic agent. In this sense, the
-switcher is a generalization of the dogmatic type, just as the
-self-attribution agent is a generalization of the Bayesian agent.
-
-By allowing the agent to keep track of the likelihoods and switching to
-an alternative type, the switcher can avoid the self-confirming
-equilibrium the dogmatic agent falls into. However, if the prior belief
-on \(theta\) is sufficiently tight around a self-confirming equilibrium,
-the switcher might look identical to the dogmatic even in a case where
-\(\alpha\) is not too large.
-
-EXPLAIN HOW THEY MIGHT GET OUT OF THE TRAP.
-
 \hypertarget{a-simple-example}{%
@@
 \(\omega\) but not its realized value. Let the true type be \(\theta^*\)
-and the true state be \(\omega^*\).
+and let the true state be \(\omega^*\).
 
@@
 
-In the data-generating process described above, there are six such
+In the data-generating process described above, there are five such
 equilibria. For example, if the agent is of type \(\theta_M\) but
@@
 ILLUSTRATE THE DIFFERENT PATHS WITH THE SIMULATION.
+
+\hypertarget{the-dogmatic-modeler-1}{%
+\subsection{The Dogmatic Modeler}\label{the-dogmatic-modeler-1}}
+
+A dogmatic modeler updates their beliefs about omega by using bayes
+rule. For the example, that means he ends up with the following
+posterior odds ratios:
+
+\begin{equation}
+\frac{p_{t}[\omega_H|\text{outcome}]}{p_{t}[\omega_M|\text{outcome}]} = 
+      \frac{p[\text{outcome}|\omega_H, \hat{\theta}, e]p_{t-1}[\omega_H]}{p[\text{outcome}|\omega_M, \hat{\theta}, e]p_{t-1}[\omega_M]}
+\end{equation} and \begin{equation}
+\frac{p_{t}[\omega_M|\text{outcome}]}{p_{t}[\omega_L|\text{outcome}]} = 
+      \frac{p[\text{outcome}|\omega_M, \hat{\theta}, e]p_{t-1}[\omega_M]}{p[\text{outcome}|\omega_L, \hat{\theta}, e]p_{t-1}[\omega_L]}
+\end{equation}
 

### 2023-09-07 Paper/draft.Rmd
editing text + fixing plots

@@
 
-# Setting 1
+# Framework 1
 
@@
 
-$$\frac{p[h^t|\tilde{\theta}]}{p[h^t|\hat{\theta}]} > \alpha$$
+$$\frac{p[h^t|\tilde{\theta}]}{p[h^t|\hat{\theta}]} > \alpha\geq 1$$
 
-Where $h^t$ is the history of outcomes up to time $t$ and $\alpha \geq 1$ is a threshold that determines how convincing the data needs to be
-for the agent to change their belief. Notice that if $\alpha \to \infty$, we get the dogmatic agent. In this sense, the 
-switcher is a generalization of the dogmatic type, just as the self-attribution agent is a generalization of the Bayesian agent.
+Where $h^t$ is the history of outcomes up to time $t$ and $\alpha$ is the switching threshold. By keeping track of the 
+likelihood ratio, the agent can perform a \emph{Bayesian hypothesis test} and adopt the Dogmatic belief that best fits 
+the data.\footnote{In a related problem @schwarstein proposes a similar updating procedure wich relies on the Bayesian 
+hypothesis test and results in similar updating outcomes.}
+Notice that if $\alpha \to \infty$, the behavior of the switcher will be indistinguishable from that of the Dogmatic modeler. 
+In this sense, the switcher is a generalization of the dogmatic type.
 
 By allowing the agent to keep track of the likelihoods and switching to an alternative type, the switcher can avoid the 
-self-confirming equilibrium the dogmatic agent falls into. However, if the prior belief on $theta$ is sufficiently tight around
-a self-confirming equilibrium, the switcher might look identical to the dogmatic even in a case where $\alpha$ is not too large.
+self-confirming equilibrium. However, if the prior belief on $omega$ is sufficiently tight around
+a self-defeating equilibrium, the switcher might look identical to the dogmatic even in a case where $\alpha$ is not too large.
+This happens because under the agent's prior, the likelihood ratio is unlikely to grow as fast as it is needed to escape 
+the self-defeating equilibrium. In this cases we say that the misspecified belief is persistent. Hence, in order to be able 
+to determine which of these two models provides a better explanation of the observed behaviors, we must focus on cases 
+in which the prior is diffused enough and the sequence of realized outcomes is such that
+the self-defeating equilibrium would not persist.
 
-** Example 1 (continued)** 
-_ Take the same student from the example and now add the possibility of switching beliefs. _
-
-# Seting 2
+# Framework 2
 
@@
 Bayesian agents always choose the effort level that maximizes their flow payoff by taking expectations over
-their prior beliefs about $\theta$ and $\omega$. Since agents are myopic, even though all the parameters could be identified with enough variation in choices,
-
-a fully Bayesian agent might not learn their true type. This happens because they do not internalize the tradeoff between flow payoff
+their prior beliefs about $\theta$ and $\omega$. Since agents are myopic, even though all the parameters 
+could be identified with enough variation in choices, a fully Bayesian agent might not learn their true type. This happens because they do not internalize the tradeoff between flow payoff
 and learning and thus might not experiment enough to learn their type. An alternative to this approach is given 
@@
 
-# A Unifying Framework
+# A Unifying Example
 The agent can be of one of 3 types: $\theta \in \{\theta_L, \theta_M, \theta_H\}$  with $\theta_H > \theta_M > \theta_L$.
 They face an unknown exogenous success rate
-$\omega \in \{\omega_L, \omega_M, \omega_H\}$ with $\omega_H>\omega_M>\omega_L$. Each of the values of $\omega$ is realized with equal probability. 
-The agent knows the distribution of $\omega$ but not its realized value. Let the true type be $\theta^*$ 
-and let the true state be $\omega^*$.
+$\omega \in \{\omega_L, \omega_M, \omega_H\}$ with $\omega_H>\omega_M>\omega_L$. Each of the values of $\omega$ is realized with 
+equal probability. 
+The agent knows the distribution of $\omega$ but not its realized value.
 
-The agent holds some prior belief about $\theta$ \footnote{which is potentially misspecified as in the dogmatic and switcher cases discussed} 
+Denote the true type by $\theta^*$ and the true state by $\omega^*$. The agent holds some prior belief about $\theta$ 
+\footnote{which is potentially misspecified as in the dogmatic and switcher cases discussed above} 
 and chooses a binary gamble $e in \{e_L, e_M, e_H\}$. The agent observes whether the gamble is a success or a failure and 
-gets a payoff of $1$ and if it is a success. They get $0$ otherwise.
+gets a payoff of $1$ and if it is a success; they get $0$ otherwise.
 
-The probability of success is increasing in
-both $\theta$ and $\omega$ and is fully described in the following table:
+The probability of success is increasing in both $\theta$ and $\omega$ and is fully described by the following table:
 
@@
 matches the state. For example, if the value of $\omega$ is $\omega_H$, the agent's flow payoff is maximized by 
-choosing $e_H$ and if the state is $\omega_L$ the flow payoff is maximized by choosing gamble $e_L$. The agent myopically chooses
-gambles every period to maximize the flow payoff for $T$ periods.
+choosing $e_H$ and if the state is $\omega_L$ the flow payoff is maximized by choosing gamble $e_L$, regardless of the value of $\theta$. 
+The agent myopically chooses gambles every period to maximize the flow payoff for $T<\infty$ periods.
 
-After observing the outcome of each gamble, the agent updates their beliefs using some algorithm and moves on to the next period.
+After observing the outcome of each gamble, the agent updates their beliefs using some procedure and moves on to the next period.
 
 Notice that both $\theta$ and $\omega$ can be identified from the outcomes if enough variation in the effort choices exists.
-This can be seen by confirming there is no pair of $\theta$ and $\omega$ such that the probability of success is the same for all effort 
-choices. Therefore, by changing the effort choice, the agent can learn both their type and the state if they observe enough outcomes.
+This can be seen by confirming that there is no pair of $\theta$ and $\omega$ such that the probability of success is the same for all effort 
+choices. Thus, by changing the effort choice, the agent can learn both their type and the state if they observe enough outcomes.
 
@@
 chooses an effort level that, under the true $\theta$, yields a frequency of success that is consistent with the agent's 
-misspecified belief. That is, the observed rate of success under the true type and the effort level chosen, 
-$P[\text{sucess}|\theta^*, e]$ is the same as the probability of success under the agent's belief, $P[\text{sucess}|\hat{\theta}, e]$.
+misspecified belief. That is $P[\text{sucess}|\theta^*, e^*] = P[\text{sucess}|\hat{\theta}, e^*]$ where $e^*$ is the agent's 
+myopic optimal choice.
 
@@
 the optimal action is $e_L$ which will continue to generate successes with $45%$ probability, further reinforcing
-the incorrect belief. If the agent were to learn the true type and rate, they would instead choose $e_M$, yielding a 
-success with $65%$ probability and strictly higher expected payoffs.
-
-From @Heidhues2018, we know that if $\theta^*$ and $\omega^*$ are such that there is a self-confirming equilibrium, a dogmatic agent will always
-fall into the trap and continue to make sub-optimal choices. On the other hand, a switcher will be able to learn the true type and state
-as long as their prior is diffused enough and their switching threshold is low enough as in @Ba2023.
+the incorrect belief. By doing so, the agent forgoes the payoff from gamble $e_M$ which would yield a success with $65\%$ chance.
 
@@
 them to choose different gambles. I exploit such cases in order to test which model is a better fit for how subjects behave in a 
-laboratory experiment.
+laboratory experiment. \footnote{because the setting does not match that of @Heidhues2018, there will be situationf for which the theory 
+does not provie a prediction. If such cases arise in the lab, they will not be used for the analysis.}
 
-ILLUSTRATE THE DIFFERENT PATHS WITH THE SIMULATION.
-
-## The Dogmatic Modeler
-
-A dogmatic modeler updates their beliefs about omega by using bayes rule. For the example, that means he ends up with the following
-posterior odds ratios:
-
-\begin{equation}
-\frac{p_{t}[\omega_H|\text{outcome}]}{p_{t}[\omega_M|\text{outcome}]} = 
-      \frac{p[\text{outcome}|\omega_H, \hat{\theta}, e]p_{t-1}[\omega_H]}{p[\text{outcome}|\omega_M, \hat{\theta}, e]p_{t-1}[\omega_M]}
-\end{equation}
-and
-\begin{equation}
-\frac{p_{t}[\omega_M|\text{outcome}]}{p_{t}[\omega_L|\text{outcome}]} = 
-      \frac{p[\text{outcome}|\omega_M, \hat{\theta}, e]p_{t-1}[\omega_M]}{p[\text{outcome}|\omega_L, \hat{\theta}, e]p_{t-1}[\omega_L]}
-\end{equation}
+For this particular example,
 

### 2023-09-07 Data/script_cleaning.py

@@ -1,0 +1,516 @@
+import csv
+import numpy as np
+import matplotlib.pyplot as plt
+import pandas as pd
+import scipy as sp
+import seaborn as sns
+import random
+
+# Read in the data from the ego treatment sessions
+# import the data in wide format for each session
+session1 = pd.read_csv("../Data/ego_demo_data.csv")
+session2 = pd.read_csv("../Data/all_apps_wide-2023-09-01.csv")
+
+# concatenate the sessions
+ego_wide = pd.concat([session1, session2], axis=0, sort=False)
+
+ego_wide['treatment'] = 'ego'
+ego_wide.reset_index(inplace=True)
+
+# Read in the data from the stereotype treatment sessions
+# import the data in wide format
+stereo_wide = pd.read_csv("../Data/stereo_demo_data.csv")
+stereo_wide['treatment'] = 'stereotype'
+
+# from the data frame ego_wide, select all the columns that have names that start with 'Quizzes' and append the column 'participant.code
+quiz_cols = [col for col in ego_wide.columns if 'Quizzes' in col]+['participant.code', 'treatment']
+
+
+# from the data frame ego_wide, select all the columns that have names that start with 'participant.'
+participant_cols = [col for col in ego_wide.columns if 'participant' in col]+['participant.code']
+
+# from the data frame ego_wide, select all the columns that have names that start with 'session.'
+session_cols = [col for col in ego_wide.columns if 'session' in col]+['participant.code']
+
+# from the data frame ego_wide, select all the columns that have names that start with 'Signals.'
+signal_cols = [col for col in ego_wide.columns if 'Signals' in col]+['participant.code']
+
+# from the data frame ego_wide, select all the columns that have names that start with 'SignalsOther.'
+signal_other_cols = [col for col in ego_wide.columns if 'SignalsOther' in col]+['participant.code']
+
+# from the data frame ego_wide, select all the columns that have names that start with 'Questionnaire.'
+questionnaire_cols = [col for col in ego_wide.columns if 'Questionnaire' in col]+['participant.code']
+
+# split the data frame ego_wide into 6 data frames using the columns we just selected
+ego_quiz = ego_wide[quiz_cols]
+ego_participant = ego_wide[participant_cols]
+ego_session = ego_wide[session_cols]
+ego_signal = ego_wide[signal_cols]
[…]

### 2023-09-07 overconfidence_otree/Signals/__init__.py

@@ -458,7 +458,7 @@ class VerbalFeedback(Page):
     @staticmethod
     def vars_for_template(player):
         participant = player.participant
-        score = player.participant.verbal_score
+        score = int(player.participant.verbal_score)
         player.verbal_score = score
         session = player.session
         e = player.effort
@@ -568,7 +568,7 @@ class MathFeedback(Page):
     @staticmethod
     def vars_for_template(player):
         participant = player.participant
-        score = player.participant.math_score
+        score = int(player.participant.math_score)
         player.math_score = score
         e = player.effort
         session = player.session
@@ -678,7 +678,7 @@ class PopFeedback(Page):
     @staticmethod
     def vars_for_template(player):
         participant = player.participant
-        score = participant.pop_score
+        score = int(participant.pop_score)
         player.pop_score = score
         session = player.session
         e = player.effort
@@ -789,7 +789,7 @@ class ScienceFeedback(Page):
     def vars_for_template(player):
         participant = player.participant
         session = player.session
-        score = player.participant.science_score
+        score = int(player.participant.science_score)
         player.science_score = score
         e = player.effort
         if score < C.T1:
@@ -899,7 +899,7 @@ class SportsFeedback(Page):
     def vars_for_template(player):
         participant = player.participant
         session = player.session
-        score = player.participant.sports_score
+        score = int(player.participant.sports_score)
         player.sports_score = score
         e = player.effort
         if score < C.T1:
@@ -1010,7 +1010,7 @@ class UsFeedback(Page):
     def vars_for_template(player):
         participant = player.participant
         session = player.session
-        score = player.participant.us_score
+        score = int(player.participant.us_score)
         player.us_score = score
         e = player.effort
         if score < C.T1:

### 2023-09-07 overconfidence_otree/SignalsOther/__init__.py

@@ -133,18 +133,36 @@ class Player(BasePlayer):
                                                       [2, str(C.T2) + ' or more']],
                                              widget=widgets.RadioSelectHorizontal)
 
-    math_certainty_other = models.IntegerField(min=0, max=100,
-                                              label='From 0 to 100 how sure are you of your answer? (100 means you are completely sure and 0 means your answer was a random guess)')
-    verbal_certainty_other = models.IntegerField(min=0, max=100,
-                                                label='From 0 to 100 how sure are you of your answer? (100 means you are completely sure and 0 means your answer was a random guess)')
-    pop_certainty_other = models.IntegerField(min=0, max=100,
-                                             label='From 0 to 100 how sure are you of your answer? (100 means you are completely sure and 0 means your answer was a random guess)')
-    science_certainty_other = models.IntegerField(min=0, max=100,
-                                                 label='From 0 to 100 how sure are you of your answer? (100 means you are completely sure and 0 means your answer was a random guess)')
-    us_certainty_other = models.IntegerField(min=0, max=100,
-                                            label='From 0 to 100 how sure are you of your answer? (100 means you are completely sure and 0 means your answer was a random guess)')
-    sports_certainty_other = models.IntegerField(min=0, max=100,
-                                                label='From 0 to 100 how sure are you of your answer? (100 means you are completely sure and 0 means your answer was a random guess)')
+    math_certainty_other = models.IntegerField(label='How sure are you of your answer?',
+                                              choices=[[33, 'It is a random guess'],
+                                                       [50, 'There is another choice that is equally likely'],
+                                                       [75, 'Somewhat sure'],
+                                                       [100, 'Completely sure']])
+    verbal_certainty_other = models.IntegerField(label='How sure are you of your answer?',
+                                                choices=[[33, 'It is a random guess'],
+                                                         [50, 'There is another choice that is equally likely'],
+                                                         [75, 'Somewhat sure'],
+                                                         [100, 'Completely sure']])
+    pop_certainty_other = models.IntegerField(label='how sure are you of your answer?',
+                                             choices=[[33, 'It is a random guess'],
+                                                      [50, 'There is another choice that is equally likely'],
+                                                      [75, 'Somewhat sure'],
+                                                      [100, 'Completely sure']])
+    science_certainty_other = models.IntegerField(label='how sure are you of your answer?',
+                                                 choices=[[33, 'It is a random guess'],
[…]

### 2023-09-07 Paper/draft.Rmd
editing text

@@
 ---
-title: "Learning from Data Through Models"  # nolint: Grammarly.
+title: "Learning with misspecified models: Overconfidence and Stereotypes"  # nolint: Grammarly.
 date: '`r format(Sys.time(), "%B %d, %Y")`'
@@
 they will be in a self-defeating equilibrium whith a stable belief that places probability one on the incorrect
-parameters $(\hat{theta}, \omega_\infty)$
+parameters $(\hat{\theta}, \omega_{\infty})$
 
@@
 they know that a higher $\omega^*$ is more likely to yield a higher grade. In particular, assume the grade is given by 
-$(\theta^*+a)\omega^*$.
+$(\theta^*+a)\omega^*$._
 
-The student must choose an effort level $a$, which determines their grade. For whatever the chosen effort level, 
+_The student must choose an effort level $a$, which determines their grade. For whatever the chosen effort level, 
 the agent must pay a cost $c(a) = \frac{1}{2}a^2$. And he repeats this process for infinitely many periods. 
 Assume also that the student's prior is such that $mathbb{E}[\omega]= \omega^*$ and he is dogmatic about being of 
-type $\hat{\theta}>\theta^*. \footnote{The example is illustrated for an overconfident agent but the results are symmetric for a digmatic agent who initially 
+type $\hat{\theta}>\theta^*$. \footnote{The example is illustrated for an overconfident agent but the results are symmetric for a digmatic agent who initially 
 places probability one on some $\tilde{\theta}<\theta^*$.}
-Therefore, the student's payoff in period $t$ is given by
+Therefore, the student's payoff in period $t$ is given by _
 
@@
 
-Under this specification, the myopic optimal effort level is $a_t^* = \omega^*$. Nonetheless, because the agent does not know $\omega^*$,
+_Under this specification, the myopic optimal effort level is $a_t^* = \omega^*$. Nonetheless, because the agent does not know $\omega^*$,
 he will choose $a_t = \mathbb{E}_t(\omega)$ where the expectation is taken with respect to the agent's belief at the beginning of
@@
 $(\hat{\theta}\theta+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}$. In response, he will apply bayes rule to update his beliefs about
-$\omega$ to get the posterior belief with $\mathbb_{t+k}[\omega] = \frac{(\theta^* + \omega^*)\omega^*}{(\hat{\theta} + \omega^*)}$
+$\omega$ to get the posterior belief with $\mathbb{E}_{t+k}[\omega] = \frac{(\theta^{*} + \omega^{*})\omega^{*}}{\hat{\theta} + \omega^{*}}$
 which is lower than the initial belief. This will cause the agent to choose a lower effort at $t+k$. As a result, he will again
@@
 continue until the average utility equals his expected utility under the dogmatic belief that assigns probability 1 to $\hat{\theta}$. 
-At that point, the stundent will have reached a self-defeating equilibrium and he will continue to choose sub-optimal effort forever._
+At that point, the stundent will have reached a self-defeating equilibrium and he will continue to choose sub-optimal effort forever. _
 
@@
 likelihood ratio, the agent can perform a \emph{Bayesian hypothesis test} and adopt the Dogmatic belief that best fits 
-the data.\footnote{In a related problem @schwarstein proposes a similar updating procedure wich relies on the Bayesian 
-hypothesis test and results in similar updating outcomes.}
+the data.\footnote{In a related problem @Schwarstein2021 proposes a similar updating procedure wich relies on the Bayesian 
+hypothesis test.}
 Notice that if $\alpha \to \infty$, the behavior of the switcher will be indistinguishable from that of the Dogmatic modeler. 
@@
 
+The agent is still of some type $\theta^* \in \Theta$ and the state is $\omega \sim F$. In this case the agent chooses an action 
+$a\in A$
+and observes a binary outcome that is either a success or a failure. Denote the outcome by $o \in {s,f}$. The probability of 
+observing a success is ingreasing in $\theta^*$ and in $\omega$. Whenever the agent observes a succes, he gets a payoff $v>0$ and
+whenever the outcome is a failure, normalize the payoff to 0.  In addition, the probability of success is such that for each state, 
+there is a unique optimal action that maximizes the agent's expected payoff.
+
+Two nested theories that have been widely studied fall within this framework: Fully Bayesian updating and self-serving attribution 
+bias. I explain each of these classical models of belief updating in what follows
+
 ## The Bayesian
@@
 The posterior odds at period t about $\theta$ after observing an outcome are given by:
-\begin{equation}
+$$
 \frac{p_{t}[\theta_H|\text{outcome}]}{p_{t}[\theta_M|\text{outcome}]} = 
       \frac{p[\text{outcome}|\theta_H]p_{t-1}[\theta_H]}{p[\text{outcome}|\theta_M]p_{t-1}[\theta_M]}
-\end{equation}
+$$
 and
-\begin{equation}
+$$
 \frac{p_{t}[\theta_M|\text{outcome}]}{p_{t}[\theta_L|\text{outcome}]} = 
       \frac{p[\text{outcome}|\theta_M]p_{t-1}[\theta_M]}{p[\text{outcome}|\theta_L]p_{t-1}[\theta_L]}
-\end{equation}
+$$
 
@@
 their prior beliefs about $\theta$ and $\omega$. Since agents are myopic, even though all the parameters 
-could be identified with enough variation in choices, a fully Bayesian agent might not learn their true type. This happens because they do not internalize the tradeoff between flow payoff
-and learning and thus might not experiment enough to learn their type. An alternative to this approach is given 
+could be identified with enough variation in choices, although the Bayesian agent is the closest to a fully rational agent discussed here, 
+they might not learn their true type. This happens because, by being myopic, they do not internalize the tradeoff between flow payoff
+and learning. This can result in too little experimentation to learn their true type. An alternative to this approach is given 
 by @Hestermann2021 and is discussed with the results.
 
-## The Biased Agent
-An agent that updates their beliefs with self-attribution bias will update their beliefs about the state $\omega$ and their type $\theta$
+## The Self-Serving Bayesian
+
+A self-serving bayesian is an agent who uses a biased version of Bayes rule to update his beliefs.He will update his beliefs 
+about the state $\omega$ and his type $\theta$
 by over-attributing successes to a high value of $\theta$ and under-estimating the role of higher $\omega$. Similarly,
-they will attribute failure to a low state more than an unbiased agent would. 
-To model the self-serving attribution bias, I take the approach of @benjamin2019, where a generalization of the Bayes rule above gives the update.
+he will attribute failure to a low state to a greter degree than an unbiased agent would. 
+To model the self-serving attribution bias, I take the approach of @benjamin2019, where the posterior is given by:
 
-\begin{equation}
-\frac{p_{t}[\theta_H|\text{outcome}]}{p_{t}[\theta_M|\text{outcome}]} = 
-      \left(\frac{p[\text{outcome}|\theta_H]}{p[\text{outcome}|\theta_M]}\right)^{c_s^{\theta}\mathbb{I}\{\text{success}\}+c_f^{\theta}\mathbb{I}\{\text{failure}\}}\frac{p_{t-1}[\theta_H]}{p_{t-1}[\theta_M]}
-\end{equation}
-and
-\begin{equation}
-\frac{p_{t}[\theta_M|\text{outcome}]}{p_{t}[\theta_L|\text{outcome}]} = 
-      \left(\frac{p[\text{outcome}|\theta_M]}{p[\text{outcome}|\theta_L]}\right)^{c_s^{\theta}\mathbb{I}\{\text{success}\}+c_f^{\theta}\mathbb{I}\{\text{failure}\}}\frac{p_{t-1}[\theta_M]}{p_{t-1}[\theta_L]}
-\end{equation}
+$$
+p_{t}[\theta_H|\text{outcome}] = 
+\frac{p[\text{outcome}|\theta]^{c_s^{\theta}\mathbb{I}\{\text{success}\}+c_f^{\theta}\mathbb{I}\{\text{failure}\}}p_{t-1}[\theta]}
+{\sum_{\theta'\in\Theta}p[\text{outcome}|\theta']^{c_s^{\theta}\mathbb{I}\{\text{success}\}+c_f^{\theta}\mathbb{I}\{\text{failure}\}}p_{t-1}[\theta']}
+$$
 
@@
 laboratory experiment. \footnote{because the setting does not match that of @Heidhues2018, there will be situationf for which the theory 
-does not provie a prediction. If such cases arise in the lab, they will not be used for the analysis.}
-
-For this particular example,
+does not provie a prediction. If such cases arise in the lab, they will not be used for the analysis. However, whether a misspecified 
+belief persists or not for the switcher, depends highly on the realized history of signals that he gets.} In what follows I explain 
+the details of how this example was implemented in the lab.
 
@@
 
-The experiment consisted of 2 treatments: the ego-relevant condition and the stereotype condition. Subjects participated in only one
-of them. Treatments were randomly assigned at the session level. The tasks were identical across treatments, but in the ego condition
-the probability of success was based on the subject's own performance in a quiz, while in the stereotype condition, the probability
-od success was based on the performance of a randomly selected subject from another session.
+The experiment consisted of 2 treatments: the \emph{ego-relevant} condition and the \emph{stereotype} condition. Subjects participated 
+in only one of the treatments. Treatments were randomly assigned at the session level. The tasks were identical across treatments, 
+except for parameter $\theta$. In the ego-relevant condition $\theta$ is the subject's own performance in a quiz, while in the 
+stereotype condition, it is the performance of a randomly selected subject from another session.
 
 The experiment had 3 parts. In Part 1 subjects had 2 minutes to answer as many multiple-choice questions as they could from a 
-20 question quiz in a particular topic. They did this for 6 different topics, one after the other. The topics were: Math, Verbal 
-Reasoning, Pop-culture and Art, Science and Technology, US Geography, and Sports and Video Games. The maximum number of questions 
-they could answer correctly was 20. However, they did not know how many questions were available and they were given no feedback.
+20-question quiz. They did this for quizzes on 6 different topics. The topics were: Math, Verbal 
+Reasoning, Pop-culture and Art, Science and Technology, US Geography, and Sports and Video Games. 
+In this part, they did not know how many questions were available and they were given no feedback.
 
 After taking all 6 quizzes, they proceeded to part 2 where they were asked to guess their score on each of them. In the stereotype 
-treatment they were additionally asked to guess the score of another participant. All they knew about the other participant was their
-gender identity and whether they were US nationals or not.
-For each guess they had three score options: 5 or fewer, between 6 and 15, 
-16 or more. Each of these correspond to $\theta_L$, $\theta_M$, and $\theta_H$ respectively. 
-They were also asked to say how confident they felt about their choices with 4 options: it was a random guess, there is another equally likely score, I am pretty sure, I am completely sure.
+treatment they were additionally asked to guess the score of a randomly drawn participant from a previous session. 
+All they knew about the other participant was their gender identity and whether they were US nationals or not.
+For each guess they had three score options: Low-Score (5 or fewer correct answers), Mid-Score (between 6 and 15 correct answers), 
+High-Score (16 or more). Each of the score categories correspond to $\theta_L$, $\theta_M$, and $\theta_H$ respectively. 
+They were also asked to say how confident they felt about their choices. They had 4 possible answers: "it was a random guess", 
+"there is another equally likely score", "I am pretty sure", "I am completely sure". 
 These 4 answers are mapped to priors that place probabilities 
-.33, .50, .75, and 1 to the chosen type. The remaining probability is split equally among the other two types. Questions in part 2
+.33, .50, .75, and 1 to the chosen type. The remaining probability is split equally among the other two types. 
+Questions in part 2
 were not incentivized, but subjects were told that providing an accurate answer would increase their chances of earning more money in 
@@
 
-The answers of part 2 allow me to classify subjects into overconfident, underconfident and correctly specified. If a subject 
-guesses their score to be in a higher category than their true score, they are overconfident. On the contrary, if they guess their
-score to be in a lower category than their true score, they are underconfident. Finally, if they guess their score to be in the same
-category as their true score, they are correctly specified. This classification is done for each of the 6 topics separately.
+The purpose of part 2 is to classify subjects into overconfident, underconfident and correctly specified. If a subject 
+guesses their score to be in a higher (lower) category than their true score, they are overconfident (underconfident); if they 
+guess their score to be in the same category as their true score, they are correctly specified. 
+This classification is done for each of the 6 topics separately.
 
-In part 3 subjects completed a belief updating task for each of the quizzes. Before starting the task they were reminded of their guess
+Finally, in part 3 subjects completed a belief updating task for each of the quizzes. Before starting the task they were reminded of their guess
 for the score. In the ego treatment they were reminded of their guess about themselves and in the stereotype treatment they were reminded
@@
 For one topic at a time and in random order,
-they were presented with the three gambles from the example and were asked to choose one of them. The probability of success was 
-determined by their own score in the ego-relevant condition and by the score of the other participant in the stereotype condition. 
+they were presented with the three gambles from the example above, and were asked to choose one of them. 
+The probability of success was 
+determined by their own score in the ego-relevant condition, and by the score of the other participant in the stereotype condition. 
 Subjects had access to the three probability
-tables in the printout on the instructions at all times and the meaning of each cell was explained in detail in the instructions. However, 
-on the screen they had to choose which of the 3 tables they wanted to see before entering their choice in it. This was done as 
-an alternative to a belief elicitation in each round. I take their choice of table to be a noisy measure of their beliefs about
-the underlying type.
+tables in the printout of the instructions at all times and the meaning of each cell was explained in detail.
 
-Once they have entered their choice, they observe a sample of 10 outcomes from the gamble they chose.
-After observing the outcomes, they returned to the choice screen and entered a new choice.
-In the choice screen
-subjects had access to the entire history of gambles and outcomes for that task. Once they entered 11 gambles (and observed 110 outcomes), they moved on to 
-the next topic and repeated the same procedure. They all did so for all 6 topics.
+In the interphase, they had to choose which of the 3 tables they wanted to see before entering their choice in it. This was done as 
+an alternative to a belief elicitation in each round. I take their choice of table to be a signal for their beliefs about
+the underlying type. I chose not to elicit the beliefs at each round to stay true to the forces in framework 1.
 
-At the end of the experiment, one of the 6 topics was randomly selected to determine the payment. They earned $\$.20$ for each 
-correct answer in the quiz and for each success in part 3.
+Once they have entered their choice, they observe a sample of 10 outcomes from the gamble they chose. After observing the outcomes, 
+they returned to the choice screen and entered a new choice. In the choice screen 
+subjects had access to the entire history of gambles and outcomes for that task as well as a summary of the outcomes so far. 
+Once they entered 11 gambles (and observed 110 outcomes), they moved on to 
+the next topic and repeated the same procedure. They all did this for all 6 topics.
 
-The randomness is controlled throughout the experiment and sessions by setting a seed drawn randomly before the
-first session. By doing this I ensure that any two subjects who have the same type and face the same exogenous rate will observe
+At the end of the experiment, one of the 6 topics was randomly selected to determine the payment. They earned $\$0.20$ for each 
+correct answer in the quiz, and for each success in part 3.
+
+Randomness is controlled throughout the experiment and sessions by setting a seed at the beggining of the
+first session. The seed was drawn at random and remained fixed for all sessions. 
+By doing this I ensure that any two subjects who have the same type and face the same exogenous rate will observe
 the same outcomes and thus, if they use the same updating procedure, they should be choosing the same gambles. 

### 2023-09-07 Paper/draft.tex
editing text

@@
 \hypersetup{
-  pdftitle={Learning from Data Through Models},
+  pdftitle={Learning with misspecified models: Overconfidence and Stereotypes},
   pdfauthor={Jimena Galindo},
@@
 
-\title{Learning from Data Through Models}
+\title{Learning with misspecified models: Overconfidence and
+Stereotypes}
 \author{Jimena Galindo}
-\date{September 05, 2023}
+\date{September 07, 2023}
 
@@
 \emph{dogmatic} if he holds a degenerate belief that places probability
-one on being a particular type, \(\hat{\theta}\). A dogmatic agent can
-be dogmatic and misspecified. That means that
+one on being a particular type, \(\hat{\theta}\). An agent can be
+dogmatic and misspecified; that means that
 \(\hat{\theta} \neq \theta^*\) and \(p_0(\hat{\theta}) = 1\).
@@
 \(h = h(\theta^*, \omega^*, a) + \varepsilon\) with \(h(\cdot)\)
-increasing in both \(\theta^*\) and \(\omega^*\); and such that
+increasing in both \(\theta^*\) and \(\omega^*\), and such that
 conditional on a pair of parameters \((\theta, \omega)\), there is a
@@
 simplifying assumption that the agent is myopic and chooses the action
-that maximizes the payoff in each period. This assumption is crucial for
-the results as the agent will not trade off the flow payoff for learning
-the truth as a forward-looking agent would.
+that maximizes the payoff in each period. This assumption is symplifies
+the analysis and plays a role on whether an agent who updates their
+beliefs using bayes rule would learn the truth or not.
+
+A key notion in this setting is that of a self-defeating
+equilibrium\footnote{This notion is an adaptation of the Berk-Nash equilibrium in 
+@Esponda2016 to this setting with only one agent}. A
+\emph{self-defeating equilibrium} is a belief and action pair such that
+the agent's belief about their type is misspecified and the outcome
+generated by the action is consistent with the misspecified belief. The
+average outcome under the true type and the true state equals the
+average output the agent expects under the misspecified belief. In
+addition, the agent's belief is said to be \emph{stable} when this
+happens.
 
@@
 can be seen as a switcher with an infinitely sticky initial belief and
-this is the sense in which the two are nested.
-
-A key notion in this setting is that of a self-defeating
-equilibrium\footnote{This notion is an adaptation of the Berk-Nash equilibrium in 
-@Esponda2016}. A \emph{self-defeating equilibrium} is a belief and
-action pair such that the agent's belief about their type is
-misspecified and the outcome generated by the action is consistent with
-the misspecified belief. The average outcome under the true type and the
-true state equals the average output the agent expects under the
-misspecified belief. In addition, the agent's belief is said to be
-\emph{stable} when this happens.
+this is the sense in which the two are nested. Both theories produce
+different predictions with respect to the equilibrium outcome.
 
@@
 incorporated using the Bayes rule to update their beliefs about
-\(\omega\).
-
-A key difference between the dogmatic agent and a fully Bayesian agent
-is that the dogmatic agent does not aggregate across types when updating
-their beliefs about \(\omega\). This means the dogmatic agent will never
-learn their true type if they are misspecified.
+\(\omega\). This means the dogmatic agent will never learn their true
+type if they startu off as being misspecified.
 
@@
 (ii) $u_{\theta}, u_{\omega}>0$ and (iii) $u_{e\theta}<0$ and $u_{e\omega}>0$. The direction of the derivatives is a normalization
-and the results would hold even when the signs are reversed.} about the
-outcome \(h\), a dogmatic modeler will inevitably fall into a
-self-defeating equilibrium where the outcomes they observe reinforce
-their belief on \(\omega\) in such a way that as \(t\to\infty\) the
-agent will be sure that the state is some \(\omega^{'}\) consistent with
-their believed type and the observed data.
+and the results would hold even when the signs are reversed.} a dogmatic
+modeler will inevitably fall into a self-defeating equilibrium. The
+equilibrium will be such that the outcomes they observe reinforce their
+belief on \(\omega\) in such a way that as \(t\to\infty\) the agent will
+be sure that the state is some \(\omega^{'}\) consistent with their
+believed type and the observed data. In other words, they will be in a
+self-defeating equilibrium whith a stable belief that places probability
+one on the incorrect parameters \((\hat{\theta}, \omega_{\infty})\)
 
@@
 belief that they are type \(\hat{\theta}>\theta^*\). For any prior over
-\(\omega\), the agent will be disappointed by the outcome; he expected a
+\(\omega\), the agent will be disappointed by the outcome. He expected a
 gain of \(h(\hat{\theta}, \mathbb{E}(\omega), a)\) but instead observes
 \(h(\hat{\theta}, \omega^*, a)\). There are two possible sources for the
-disappointment. The first is that the realized state is lower than the
-expected state. The second is that the agent is of type \(\theta^*\) and
-thus for all possible states, his gain will be lower than what he
-expected. Because the agent is dogmatic, he will not update his beliefs
-about \(\theta\) and thus will attribute the disappointment to the state
-being lower than expected. \citet{Heidhues2018} give sufficient
-conditions for the agent to fall into a self-confirming equilibrium
-where the agent will continue to choose an action that reinforces an
-incorrect belief about the state. This force is illustrated in Example
-1.
+disappointment, the first is that the realized state is lower than the
+expected state. The second source is that the agent is of type
+\(\theta^*\) and therefore, for all possible states, his gain will be
+lower than what he expected. Because the agent is dogmatic, he will not
+update his beliefs about \(\theta\) and as a consequence will attribute
+the disappointment to the state being lower than expected. He will
+continue to update in ths way until he converges to a belief about
+\(\omega\) that is stable. Such a belief will explain the observed
+utility perfectly and allow the agent to rationalize his dogmatic belief
+about \(\theta\). Under the assumptions of \citet{Heidhues2018}, there
+is a unique value of \(\omega\) at which the belief is stable, I will
+refer to such value as \(\omega_\infty\). This mechanism is further
+illustrated in Example 1.
 
-\textbf{Example 1: } Set \(A = \Omega\) and \(H = [0, \infty)\) and
-consider a student with intrinsic ability \(\theta^*\geq 0\) who faces a
-grading procedure \(\omega^*\) that is unknown to them. However, they
-know that a higher \(\omega^*\) is more likely to yield a higher grade.
-In particular, assume the grade is given by \((\theta^*+a)\omega^*\).
+\textbf{Example 1: } \emph{Set \(A = \Omega\) and \(H = [0, \infty)\)
+and consider a student with intrinsic ability \(\theta^*\geq 0\) who
+faces a grading procedure \(\omega^*\) that is unknown to them. However,
+they know that a higher \(\omega^*\) is more likely to yield a higher
+grade. In particular, assume the grade is given by
+\((\theta^*+a)\omega^*\).}
 
-The student must choose an effort level \(a\), which determines their
-grade. For whatever the chosen effort level, the agent must pay a cost
-\(c(a) = \frac{1}{2}a^2\). And he repeats this process for infinitely
-many periods. Assume also that the student's prior is such that
-\(mathbb{E}[\omega]= \omega^*\). Therefore, the student's payoff in
-period \(t\) is given by
+\emph{The student must choose an effort level \(a\), which determines
+their grade. For whatever the chosen effort level, the agent must pay a
+cost \(c(a) = \frac{1}{2}a^2\). And he repeats this process for
+infinitely many periods. Assume also that the student's prior is such
+that \(mathbb{E}[\omega]= \omega^*\) and he is dogmatic about being of
+type \(\hat{\theta}>\theta^*\).
+\footnote{The example is illustrated for an overconfident agent but the results are symmetric for a digmatic agent who initially 
+places probability one on some $\tilde{\theta}<\theta^*$.} Therefore,
+the student's payoff in period \(t\) is given by }
 
@@
 
-Under this specification, the myopic optimal effort level is
+\emph{Under this specification, the myopic optimal effort level is
 \(a_t^* = \omega^*\). Nonetheless, because the agent does not know
@@
 expectation is taken with respect to the agent's belief at the beginning
-of period \(t\). If he does not revise his effort choice for multiple
-periods, he will observe an average grade of
+of period \(t\). If he does not revise his effort choice for \(k\)
+periods, he will receive an average utility of
 \((\theta^*+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}\) but he was expecting
-an average grade of
-\((\hat{\theta}\theta+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}\)
+an average utility of
+\((\hat{\theta}\theta+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}\). In
+response, he will apply bayes rule to update his beliefs about
+\(\omega\) to get the posterior belief with
+\(\mathbb{E}_{t+k}[\omega] = \frac{(\theta^{*} + \omega^{*})\omega^{*}}{\hat{\theta} + \omega^{*}}\)
+which is lower than the initial belief. This will cause the agent to
+choose a lower effort at \(t+k\). As a result, he will again receive an
+average utlitity that is lower than what he expected which will cause
+his belief to drift further down. This process will continue until the
+average utility equals his expected utility under the dogmatic belief
+that assigns probability 1 to \(\hat{\theta}\). At that point, the
+stundent will have reached a self-defeating equilibrium and he will
+continue to choose sub-optimal effort forever. }
 
-\hypertarget{the-bayesian-benchmark}{%
-\subsection{The Bayesian Benchmark}\label{the-bayesian-benchmark}}
-
-A Bayesian agent simultaneously updates their beliefs about \(\theta\)
-and \(\omega\) by using Bayes' rule. The posterior odds at period t
-about \(\theta\) after observing an outcome are given by:
-\begin{equation}
-\frac{p_{t}[\theta_H|\text{outcome}]}{p_{t}[\theta_M|\text{outcome}]} = 
-      \frac{p[\text{outcome}|\theta_H]p_{t-1}[\theta_H]}{p[\text{outcome}|\theta_M]p_{t-1}[\theta_M]}
-\end{equation} and \begin{equation}
-\frac{p_{t}[\theta_M|\text{outcome}]}{p_{t}[\theta_L|\text{outcome}]} = 
-      \frac{p[\text{outcome}|\theta_M]p_{t-1}[\theta_M]}{p[\text{outcome}|\theta_L]p_{t-1}[\theta_L]}
-\end{equation}
-
-Where \(p_{t-1}\) is the prior at period \(t\) and
-\(p[\text{outcome}|\theta] = \sum_{\omega} p[\text{outcome}|\theta, \omega, e]p_{t-1}(\omega)\)
-is the probability of observing the outcome given the agent's type and
-the effort chosen. The update is symmetric for \(\omega\).
-
-Bayesian agents always choose the effort level that maximizes their flow
-payoff by taking expectations over their prior beliefs about \(\theta\)
-and \(\omega\). Since agents are myopic, even though all the parameters
-could be identified with enough variation in choices,
+Although the model of a dogmatic modeler is able to rationalize the
+prevalence of overconfident (underconfident) beliefs, the assumption
+that the agent has a degenerate belief and no mechanism through which he
+can update such belief is very restrictive. An alternative approach is
+proposed by \citet{Ba2023}. She proposes an extension of the dogmatic
+agent who is able to jump from one dogmatic belief to another. By doing
+so, the agent might end up being dogmatic and correctly speciefied.
 
@@
 
-An agent is a \emph{switcher} if they behave as a dogmatic but is
+An agent is a \emph{switcher} if they behave as a dogmatic, but is
 willing to entertain the possibility that they are of a different type.
@@
 willing to switch to a different dogmatic belief if the data is
-convincing enough.
+convincing enough. Notice that their beliefs are still degenerate and
+assign probability one to a particular type, and zero to all other
+types. This means that a bayesian update on \(\theta\) would cause no
+change in their beliefs. However, they are willing to entertain two such
+beliefs and have a mechanism by which they decide which belief to adopt
+at any period \(t\).
 
@@
 
-\[\frac{p[h^t|\tilde{\theta}]}{p[h^t|\hat{\theta}]} > \alpha\]
+\[\frac{p[h^t|\tilde{\theta}]}{p[h^t|\hat{\theta}]} > \alpha\geq 1\]
 
-Where \(h^t\) is the history of outcomes up to time \(t\) and
-\(\alpha \geq 1\) is a threshold that determines how convincing the data
-needs to be for the agent to change their belief. Notice that if
-\(\alpha \to \infty\), we get the dogmatic agent. In this sense, the
-switcher is a generalization of the dogmatic type, just as the
-self-attribution agent is a generalization of the Bayesian agent.
+Where \(h^t\) is the history of outcomes up to time \(t\) and \(\alpha\)
+is the switching threshold. By keeping track of the likelihood ratio,
+the agent can perform a \emph{Bayesian hypothesis test} and adopt the
+Dogmatic belief that best fits the
+data.\footnote{In a related problem @Schwarstein2021 proposes a similar updating procedure wich relies on the Bayesian 
+hypothesis test.} Notice that if \(\alpha \to \infty\), the behavior of
+the switcher will be indistinguishable from that of the Dogmatic
+modeler. In this sense, the switcher is a generalization of the dogmatic
+type.
 
@@
 an alternative type, the switcher can avoid the self-confirming
-equilibrium the dogmatic agent falls into. However, if the prior belief
-on \(theta\) is sufficiently tight around a self-confirming equilibrium,
-the switcher might look identical to the dogmatic even in a case where
-\(\alpha\) is not too large.
+equilibrium. However, if the prior belief on \(omega\) is sufficiently
+tight around a self-defeating equilibrium, the switcher might look
+identical to the dogmatic even in a case where \(\alpha\) is not too
+large. This happens because under the agent's prior, the likelihood
+ratio is unlikely to grow as fast as it is needed to escape the
+self-defeating equilibrium. In this cases we say that the misspecified
+belief is persistent. Hence, in order to be able to determine which of
+these two models provides a better explanation of the observed
+behaviors, we must focus on cases in which the prior is diffused enough
+and the sequence of realized outcomes is such that the self-defeating
+equilibrium would not persist.
 
-EXPLAIN HOW THEY MIGHT GET OUT OF THE TRAP.
+\hypertarget{framework-2}{%
+\section{Framework 2}\label{framework-2}}
 
-\hypertarget{the-bayesian-agent}{%
-\subsection{The Bayesian Agent}\label{the-bayesian-agent}}
+The agent is still of some type \(\theta^* \in \Theta\) and the state is
+\(\omega \sim F\). In this case the agent chooses an action \(a\in A\)
+and observes a binary outcome that is either a success or a failure.
+Denote the outcome by \(o \in {s,f}\). The probability of observing a
+success is ingreasing in \(\theta^*\) and in \(\omega\). Whenever the
+agent observes a succes, he gets a payoff \(v>0\) and whenever the
+outcome is a failure, normalize the payoff to 0. In addition, the
+probability of success is such that for each state, there is a unique
+optimal action that maximizes the agent's expected payoff.
 
-a fully Bayesian agent might not learn their true type. This happens
-because they do not internalize the tradeoff between flow payoff and
-learning and thus might not experiment enough to learn their type. An
-alternative to this approach is given by \citet{Hestermann2021} and is
-discussed with the results.
+Two nested theories that have been widely studied fall within this
+framework: Fully Bayesian updating and self-serving attribution bias. I
+explain each of these classical models of belief updating in what
+follows
 
-\hypertarget{the-biased-agent}{%
-\subsection{The Biased Agent}\label{the-biased-agent}}
+\hypertarget{the-bayesian}{%
+\subsection{The Bayesian}\label{the-bayesian}}
 
-An agent that updates their beliefs with self-attribution bias will
-update their beliefs about the state \(\omega\) and their type
-\(\theta\) by over-attributing successes to a high value of \(\theta\)
-and under-estimating the role of higher \(\omega\). Similarly, they will
-attribute failure to a low state more than an unbiased agent would. To
-model the self-serving attribution bias, I take the approach of
-\citet{benjamin2019}, where a generalization of the Bayes rule above
-gives the update.
+A Bayesian agent simultaneously updates their beliefs about \(\theta\)
+and \(\omega\) by using Bayes' rule. The posterior odds at period t
+about \(\theta\) after observing an outcome are given by: \[
+\frac{p_{t}[\theta_H|\text{outcome}]}{p_{t}[\theta_M|\text{outcome}]} = 
+      \frac{p[\text{outcome}|\theta_H]p_{t-1}[\theta_H]}{p[\text{outcome}|\theta_M]p_{t-1}[\theta_M]}
+\] and \[
+\frac{p_{t}[\theta_M|\text{outcome}]}{p_{t}[\theta_L|\text{outcome}]} = 
+      \frac{p[\text{outcome}|\theta_M]p_{t-1}[\theta_M]}{p[\text{outcome}|\theta_L]p_{t-1}[\theta_L]}
+\]
 
-\begin{equation}
-\frac{p_{t}[\theta_H|\text{outcome}]}{p_{t}[\theta_M|\text{outcome}]} = 
-      \left(\frac{p[\text{outcome}|\theta_H]}{p[\text{outcome}|\theta_M]}\right)^{c_s^{\theta}\mathbb{I}\{\text{success}\}+c_f^{\theta}\mathbb{I}\{\text{failure}\}}\frac{p_{t-1}[\theta_H]}{p_{t-1}[\theta_M]}
-\end{equation} and \begin{equation}
-\frac{p_{t}[\theta_M|\text{outcome}]}{p_{t}[\theta_L|\text{outcome}]} = 
-      \left(\frac{p[\text{outcome}|\theta_M]}{p[\text{outcome}|\theta_L]}\right)^{c_s^{\theta}\mathbb{I}\{\text{success}\}+c_f^{\theta}\mathbb{I}\{\text{failure}\}}\frac{p_{t-1}[\theta_M]}{p_{t-1}[\theta_L]}
-\end{equation}
+Where \(p_{t-1}\) is the prior at period \(t\) and
+\(p[\text{outcome}|\theta] = \sum_{\omega} p[\text{outcome}|\theta, \omega, e]p_{t-1}(\omega)\)
+is the probability of observing the outcome given the agent's type and
+the effort chosen. The update is symmetric for \(\omega\).
+
+Bayesian agents always choose the effort level that maximizes their flow
+payoff by taking expectations over their prior beliefs about \(\theta\)
+and \(\omega\). Since agents are myopic, even though all the parameters
+could be identified with enough variation in choices, although the
+Bayesian agent is the closest to a fully rational agent discussed here,
+they might not learn their true type. This happens because, by being
+myopic, they do not internalize the tradeoff between flow payoff and
+learning. This can result in too little experimentation to learn their
+true type. An alternative to this approach is given by
+\citet{Hestermann2021} and is discussed with the results.
+
+\hypertarget{the-self-serving-bayesian}{%
+\subsection{The Self-Serving Bayesian}\label{the-self-serving-bayesian}}
+
+A self-serving bayesian is an agent who uses a biased version of Bayes
+rule to update his beliefs.He will update his beliefs about the state
+\(\omega\) and his type \(\theta\) by over-attributing successes to a
+high value of \(\theta\) and under-estimating the role of higher
+\(\omega\). Similarly, he will attribute failure to a low state to a
+greter degree than an unbiased agent would. To model the self-serving
+attribution bias, I take the approach of \citet{benjamin2019}, where the
+posterior is given by:
+
+\[
+p_{t}[\theta_H|\text{outcome}] = 
+\frac{p[\text{outcome}|\theta]^{c_s^{\theta}\mathbb{I}\{\text{success}\}+c_f^{\theta}\mathbb{I}\{\text{failure}\}}p_{t-1}[\theta]}
+{\sum_{\theta'\in\Theta}p[\text{outcome}|\theta']^{c_s^{\theta}\mathbb{I}\{\text{success}\}+c_f^{\theta}\mathbb{I}\{\text{failure}\}}p_{t-1}[\theta']}
+\]
 
@@
 
-\hypertarget{a-simple-example}{%
-\section{A Simple Example}\label{a-simple-example}}
+\hypertarget{a-unifying-example}{%
+\section{A Unifying Example}\label{a-unifying-example}}
 
@@
 realized with equal probability. The agent knows the distribution of
-\(\omega\) but not its realized value. Let the true type be \(\theta^*\)
-and let the true state be \(\omega^*\).
+\(\omega\) but not its realized value.
 
+Denote the true type by \(\theta^*\) and the true state by \(\omega^*\).
 The agent holds some prior belief about \(\theta\)
-\footnote{which is potentially misspecified as in the dogmatic and switcher cases discussed}
+\footnote{which is potentially misspecified as in the dogmatic and switcher cases discussed above}
 and chooses a binary gamble \(e in \{e_L, e_M, e_H\}\). The agent
 observes whether the gamble is a success or a failure and gets a payoff
-of \(1\) and if it is a success. They get \(0\) otherwise.
+of \(1\) and if it is a success; they get \(0\) otherwise.
 
 The probability of success is increasing in both \(\theta\) and
-\(\omega\) and is fully described in the following table:
+\(\omega\) and is fully described by the following table:
 
@@
 choosing \(e_H\) and if the state is \(\omega_L\) the flow payoff is
-maximized by choosing gamble \(e_L\). The agent myopically chooses
-gambles every period to maximize the flow payoff for \(T\) periods.
+maximized by choosing gamble \(e_L\), regardless of the value of
+\(\theta\). The agent myopically chooses gambles every period to
+maximize the flow payoff for \(T<\infty\) periods.
 
 After observing the outcome of each gamble, the agent updates their
-beliefs using some algorithm and moves on to the next period.
+beliefs using some procedure and moves on to the next period.
 
@@
 outcomes if enough variation in the effort choices exists. This can be
-seen by confirming there is no pair of \(\theta\) and \(\omega\) such
-that the probability of success is the same for all effort choices.
-Therefore, by changing the effort choice, the agent can learn both their
-type and the state if they observe enough outcomes.
+seen by confirming that there is no pair of \(\theta\) and \(\omega\)
+such that the probability of success is the same for all effort choices.
+Thus, by changing the effort choice, the agent can learn both their type
+and the state if they observe enough outcomes.
 
@@
 level that, under the true \(\theta\), yields a frequency of success
-that is consistent with the agent's misspecified belief. That is, the
-observed rate of success under the true type and the effort level
-chosen, \(P[\text{sucess}|\theta^*, e]\) is the same as the probability
-of success under the agent's belief,
-\(P[\text{sucess}|\hat{\theta}, e]\).
+that is consistent with the agent's misspecified belief. That is
+\(P[\text{sucess}|\theta^*, e^*] = P[\text{sucess}|\hat{\theta}, e^*]\)
+where \(e^*\) is the agent's myopic optimal choice.
 
@@
 action is \(e_L\) which will continue to generate successes with \(45%
-\) probability, further reinforcing the incorrect belief. If the agent
-were to learn the true type and rate, they would instead choose \(e_M\),
-yielding a success with \(65%
-\) probability and strictly higher expected payoffs.
-
-From \citet{Heidhues2018}, we know that if \(\theta^*\) and \(\omega^*\)
-are such that there is a self-confirming equilibrium, a dogmatic agent
-will always fall into the trap and continue to make sub-optimal choices.
-On the other hand, a switcher will be able to learn the true type and
-state as long as their prior is diffused enough and their switching
-threshold is low enough as in \citet{Ba2023}.
+\) probability, further reinforcing the incorrect belief. By doing so,
+the agent forgoes the payoff from gamble \(e_M\) which would yield a
+success with \(65\%\) chance.
 
@@
 experiment.
-
-ILLUSTRATE THE DIFFERENT PATHS WITH THE SIMULATION.
-
-\hypertarget{the-dogmatic-modeler-1}{%
-\subsection{The Dogmatic Modeler}\label{the-dogmatic-modeler-1}}
-
-A dogmatic modeler updates their beliefs about omega by using bayes
-rule. For the example, that means he ends up with the following
-posterior odds ratios:
-
-\begin{equation}
-\frac{p_{t}[\omega_H|\text{outcome}]}{p_{t}[\omega_M|\text{outcome}]} = 
-      \frac{p[\text{outcome}|\omega_H, \hat{\theta}, e]p_{t-1}[\omega_H]}{p[\text{outcome}|\omega_M, \hat{\theta}, e]p_{t-1}[\omega_M]}
-\end{equation} and \begin{equation}
-\frac{p_{t}[\omega_M|\text{outcome}]}{p_{t}[\omega_L|\text{outcome}]} = 
-      \frac{p[\text{outcome}|\omega_M, \hat{\theta}, e]p_{t-1}[\omega_M]}{p[\text{outcome}|\omega_L, \hat{\theta}, e]p_{t-1}[\omega_L]}
-\end{equation}
+\footnote{because the setting does not match that of @Heidhues2018, there will be situationf for which the theory 
+does not provie a prediction. If such cases arise in the lab, they will not be used for the analysis. However, whether a misspecified 
+belief persists or not for the switcher, depends highly on the realized history of signals that he gets.}
+In what follows I explain the details of how this example was
+implemented in the lab.
 
@@
 
-The experiment consisted of 2 treatments: the ego-relevant condition and
-the stereotype condition. Subjects participated in only one of them.
-Treatments were randomly assigned at the session level. The tasks were
-identical across treatments, but in the ego condition the probability of
-success was based on the subject's own performance in a quiz, while in
-the stereotype condition, the probability od success was based on the
-performance of a randomly selected subject from another session.
+The experiment consisted of 2 treatments: the \emph{ego-relevant}
+condition and the \emph{stereotype} condition. Subjects participated in
+only one of the treatments. Treatments were randomly assigned at the
+session level. The tasks were identical across treatments, except for
+parameter \(\theta\). In the ego-relevant condition \(\theta\) is the
+subject's own performance in a quiz, while in the stereotype condition,
+it is the performance of a randomly selected subject from another
+session.
 
 The experiment had 3 parts. In Part 1 subjects had 2 minutes to answer
-as many multiple-choice questions as they could from a 20 question quiz
-in a particular topic. They did this for 6 different topics, one after
-the other. The topics were: Math, Verbal Reasoning, Pop-culture and Art,
-Science and Technology, US Geography, and Sports and Video Games. The
-maximum number of questions they could answer correctly was 20. However,
-they did not know how many questions were available and they were given
-no feedback.
+as many multiple-choice questions as they could from a 20-question quiz.
+They did this for quizzes on 6 different topics. The topics were: Math,
+Verbal Reasoning, Pop-culture and Art, Science and Technology, US
+Geography, and Sports and Video Games. In this part, they did not know
+how many questions were available and they were given no feedback.
 
@@
 asked to guess their score on each of them. In the stereotype treatment
-they were additionally asked to guess the score of another participant.
-All they knew about the other participant was their gender identity and
-whether they were US nationals or not. For each guess they had three
-score options: 5 or fewer, between 6 and 15, 16 or more. Each of these
-correspond to \(\theta_L\), \(\theta_M\), and \(\theta_H\) respectively.
-They were also asked to say how confident they felt about their choices
-with 4 options: it was a random guess, there is another equally likely
-score, I am pretty sure, I am completely sure. These 4 answers are
-mapped to priors that place probabilities .33, .50, .75, and 1 to the
-chosen type. The remaining probability is split equally among the other
-two types. Questions in part 2 were not incentivized, but subjects were
-told that providing an accurate answer would increase their chances of
-earning more money in the last part of the experiment.
+they were additionally asked to guess the score of a randomly drawn
+participant from a previous session. All they knew about the other
+participant was their gender identity and whether they were US nationals
+or not. For each guess they had three score options: Low-Score (5 or
+fewer correct answers), Mid-Score (between 6 and 15 correct answers),
+High-Score (16 or more). Each of the score categories correspond to
+\(\theta_L\), \(\theta_M\), and \(\theta_H\) respectively. They were
+also asked to say how confident they felt about their choices. They had
+4 possible answers: ``it was a random guess'', ``there is another
+equally likely score'', ``I am pretty sure'', ``I am completely sure''.
+These 4 answers are mapped to priors that place probabilities .33, .50,
+.75, and 1 to the chosen type. The remaining probability is split
+equally among the other two types. Questions in part 2 were not
+incentivized, but subjects were told that providing an accurate answer
+would increase their chances of earning more money in the last part of
+the experiment.
 
-The answers of part 2 allow me to classify subjects into overconfident,
+The purpose of part 2 is to classify subjects into overconfident,
 underconfident and correctly specified. If a subject guesses their score
-to be in a higher category than their true score, they are
-overconfident. On the contrary, if they guess their score to be in a
-lower category than their true score, they are underconfident. Finally,
-if they guess their score to be in the same category as their true
-score, they are correctly specified. This classification is done for
-each of the 6 topics separately.
+to be in a higher (lower) category than their true score, they are
+overconfident (underconfident); if they guess their score to be in the
+same category as their true score, they are correctly specified. This
+classification is done for each of the 6 topics separately.
 
-In part 3 subjects completed a belief updating task for each of the
-quizzes. Before starting the task they were reminded of their guess for
-the score. In the ego treatment they were reminded of their guess about
-themselves and in the stereotype treatment they were reminded of their
-guess about the other participant. In the stereotype treatment, they
-were also reminded of the characteristics of the other participant.
+Finally, in part 3 subjects completed a belief updating task for each of
+the quizzes. Before starting the task they were reminded of their guess
+for the score. In the ego treatment they were reminded of their guess
+about themselves and in the stereotype treatment they were reminded of
+their guess about the other participant. In the stereotype treatment,
+they were also reminded of the characteristics of the other participant.
 
 For one topic at a time and in random order, they were presented with
-the three gambles from the example and were asked to choose one of them.
-The probability of success was determined by their own score in the
-ego-relevant condition and by the score of the other participant in the
-stereotype condition. Subjects had access to the three probability
-tables in the printout on the instructions at all times and the meaning
-of each cell was explained in detail in the instructions. However, on
-the screen they had to choose which of the 3 tables they wanted to see
-before entering their choice in it. This was done as an alternative to a
-belief elicitation in each round. I take their choice of table to be a
-noisy measure of their beliefs about the underlying type.
+the three gambles from the example above, and were asked to choose one
+of them. The probability of success was determined by their own score in
+the ego-relevant condition, and by the score of the other participant in
+the stereotype condition. Subjects had access to the three probability
+tables in the printout of the instructions at all times and the meaning
+of each cell was explained in detail.
+
+In the interphase, they had to choose which of the 3 tables they wanted
+to see before entering their choice in it. This was done as an
+alternative to a belief elicitation in each round. I take their choice
+of table to be a signal for their beliefs about the underlying type. I
+chose not to elicit the beliefs at each round to stay true to the forces
+in framework 1.
 
@@
 screen subjects had access to the entire history of gambles and outcomes
-for that task. Once they entered 11 gambles (and observed 110 outcomes),
-they moved on to the next topic and repeated the same procedure. They
-all did so for all 6 topics.
+for that task as well as a summary of the outcomes so far. Once they
+entered 11 gambles (and observed 110 outcomes), they moved on to the
+next topic and repeated the same procedure. They all did this for all 6
+topics.
 
 At the end of the experiment, one of the 6 topics was randomly selected
-to determine the payment. They earned \(\$.20\) for each correct answer
-in the quiz and for each success in part 3.
+to determine the payment. They earned \(\$0.20\) for each correct answer
+in the quiz, and for each success in part 3.
 
-The randomness is controlled throughout the experiment and sessions by
-setting a seed drawn randomly before the first session. By doing this I
-ensure that any two subjects who have the same type and face the same
-exogenous rate will observe the same outcomes and thus, if they use the
-same updating procedure, they should be choosing the same gambles. This
+Randomness is controlled throughout the experiment and sessions by
+setting a seed at the beggining of the first session. The seed was drawn
+at random and remained fixed for all sessions. By doing this I ensure
+that any two subjects who have the same type and face the same exogenous
+rate will observe the same outcomes and thus, if they use the same
+updating procedure, they should be choosing the same gambles. This
 design feature allows me to identify differences in updating procedures

### 2023-09-07 overconfidence_otree/Quizzes/__init__.py

@@ -209,6 +209,11 @@ def creating_session(subsession: Subsession):
 
 
 #PAGES
+class Welcome(Page):
+    @staticmethod
+    def is_displayed(player):
+        return player.round_number == 1
+
 class Instructions(Page):
     @staticmethod
     def is_displayed(player):
@@ -225,6 +230,7 @@ class Start(Page):
         position = val_list.index(player.round_number)
         player.topic = key_list[position]
         return dict(topic=player.topic)
+
 
 class MathQuiz(Page):
     @staticmethod
@@ -639,4 +645,4 @@ class ResultsWaitPage(WaitPage):
     pass
 
 
-page_sequence = [Instructions, Start, VerbalQuiz, MathQuiz, PopQuiz, SportsQuiz, ScienceQuiz, USQuiz, Transition]
+page_sequence = [Welcome, Instructions, Start, VerbalQuiz, MathQuiz, PopQuiz, SportsQuiz, ScienceQuiz, USQuiz, Transition]

### 2023-09-11 Paper/draft.Rmd
alpha estimate

@@
 them to choose different gambles. I exploit such cases in order to test which model is a better fit for how subjects behave in a 
-laboratory experiment. \footnote{because the setting does not match that of @Heidhues2018, there will be situationf for which the theory 
+laboratory experiment. \footnote{because the setting does not match that of Heidhues et al. [2018], there will be situationf for which the theory 
 does not provie a prediction. If such cases arise in the lab, they will not be used for the analysis. However, whether a misspecified 
@@
 
+# Predictions
+
+In the example and for the seed that was drawn and fixed throughout, the models make different predictions.
+
 # Analysis

### 2023-09-12 Paper/draft.Rmd
session1

@@
 
-## The Self-Serving Bayesian
+## The Self-Serving Updater
 
@@
 
-In the example and for the seed that was drawn and fixed throughout, the models make different predictions.
+Because the different models apply only under certain conditions, I split the predictions into two groups; the dogmatic and the 
+switcher constitute the first group, and the bayesian and self-serving updater are the second group. the predictions of group 1
+apply only in cases where $(\theta, \omega)$ are such that there is a self-defeating equilibrium. This is because whenever 
+there is no self defeating equilibria, the dogmatic model does not apply. On the other hand, the theories of group 2 apply to all
+possible combinations of the parameters. Hence, these theories can be tested and differentiated within a broader set of 
+observations.
+
+It is also important to note that since the predictions of the model are asymptotic and probabilistic, the predictions that are made 
+for the particular example that was taken to the lab depend strongly on the realized sequence of signals. Because the randomness has 
+been controlled for and kept fixed across sessions, for every parametrization $(\theta, \omega)$ there is a unique optimal path 
+for each of the models. I present the predictions made by this particular realization of the seed.\footnote{The seed that was drawn 
+at the beginning of session 1 was 3452. The same seed was used for all sessions. It is used both for drawing $\omega$ for each of 
+the tasks in the experiment, as well as for drawing the outcomes from the gambles.}
+
+## Dogmatic and Switcher
+
+The cases in which we can apply these two theories are the five self-defeating equilibria from the data generating process in the 
+example. From these and with the seed that was drawn, the models make different predictions in 4 cases. \footnote{the fifth 
+self-defeating equilibrum is such that the likelihood ratio does not go above 1 and thus the switcher is indistinguishable from 
+the dogmatic agent.}
+
+## Bayesian and self-attribution updater
 

### 2023-09-12 Paper/draft.tex
session1

@@
 \author{Jimena Galindo}
-\date{September 07, 2023}
+\date{September 12, 2023}
 
@@
 
-\hypertarget{the-self-serving-bayesian}{%
-\subsection{The Self-Serving Bayesian}\label{the-self-serving-bayesian}}
+\hypertarget{the-self-serving-updater}{%
+\subsection{The Self-Serving Updater}\label{the-self-serving-updater}}
 
@@
 experiment.
-\footnote{because the setting does not match that of @Heidhues2018, there will be situationf for which the theory 
+\footnote{because the setting does not match that of Heidhues et al. [2018], there will be situationf for which the theory 
 does not provie a prediction. If such cases arise in the lab, they will not be used for the analysis. However, whether a misspecified 
@@
 
+\hypertarget{predictions}{%
+\section{Predictions}\label{predictions}}
+
+Because the different models apply only under certain conditions, I
+split the predictions into two groups; the dogmatic and the switcher
+constitute the first group, and the bayesian and self-serving updater
+are the second group. the predictions of group 1 apply only in cases
+where \((\theta, \omega)\) are such that there is a self-defeating
+equilibrium. This is because whenever there is no self defeating
+equilibria, the dogmatic model does not apply. On the other hand, the
+theories of group 2 apply to all possible combinations of the
+parameters. Hence, these theories can be tested and differentiated
+within a broader set of observations.
+
+It is also important to note that since the predictions of the model are
+asymptotic and probabilistic, the predictions that are made for the
+particular example that was taken to the lab depend strongly on the
+realized sequence of signals. Because the randomness has been controlled
+for and kept fixed across sessions, for every parametrization
+\((\theta, \omega)\) there is a unique optimal path for each of the
+models. I present the predictions made by this particular realization of
+the seed.\footnote{The seed that was drawn 
+at the beginning of session 1 was 3452. The same seed was used for all sessions. It is used both for drawing $\omega$ for each of 
+the tasks in the experiment, as well as for drawing the outcomes from the gambles.}
+
+\hypertarget{dogmatic-and-switcher}{%
+\subsection{Dogmatic and Switcher}\label{dogmatic-and-switcher}}
+
+The cases in which we can apply these two theories are the five
+self-defeating equilibria from the data generating process in the
+example. From these and with the seed that was drawn, the models make
+different predictions in 4 cases. \footnote{the fifth 
+self-defeating equilibrum is such that the likelihood ratio does not go above 1 and thus the switcher is indistinguishable from 
+the dogmatic agent.}
+
+\hypertarget{bayesian-and-self-attribution-updater}{%
+\subsection{Bayesian and self-attribution
+updater}\label{bayesian-and-self-attribution-updater}}
+
 \hypertarget{analysis}{%

### 2023-09-29 Slides/overconfident_beliefs/ExpSeminar_spring23.tex
slides setup

\documentclass[aspectratio=169]{beamer}

\usepackage{geometry}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{theorem}
\usepackage{natbib}
\usepackage{mathtools}
\usepackage{cite}
\usepackage{natbib}
\usepackage{setspace}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{xcolor}
\usepackage{array}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[normalem]{ulem}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{calc}
\usepackage{tabularx}
\usepackage{threeparttable}
\usepackage{wrapfig}
\usepackage{adjustbox}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage[table]{xcolor}

\title{Models of Belief Updating:\\ The Case of Overconfidence}
\author{Jimena Galindo}

\begin{document}

\frame{\titlepage}

\begin{frame}{Motivation}
    We often observe beliefs and behaviors that are inconsistent with the fully Bayesian benchmark:\\
    \bigskip
    \begin{itemize} 
        \item Overconfidence  
        \item Polarization 
    \end{itemize}

    \bigskip
    Recent theoretical literature has sought to explain these phenomena (and others) with the notion of \bf{Misspecified Mental Models}
\end{frame}

\begin{frame}{Motivation}
    We often observe beliefs and behaviors that are inconsistent with the fully Bayesian benchmark:\\
    \bigskip
    \begin{itemize} 
        \item Overconfidence \textbf{(today)}  
        \item Polarization \textbf{(next time)}
    \end{itemize}

    \bigskip
    Recent theoretical literature has sought to explain these phenomena (and others) with the notion of \bf{Misspecified Mental Models}
\end{frame}

\begin{frame}{Mental Models}

A prior on unknown parameters/states and an updating procedure\\
\bigskip
\begin{itemize}
    \item Bayesian 
    \item Dogmatic 
    \item Motivated Beliefs
\end{itemize}

\end{frame}

\begin{frame}{Overconfidence}
    Belief that my type is higher than it truly is (``overestimation'' as in Moore and Healy, 2008)\\
    \bigskip

    Overconfidence seems to be persistent in various settings. Ultimately it leads to sub-optimal choices:
    \begin{itemize} 
        \item Excess entry of entrepreneurs (Camerer and Lovallo, 1999)
        \item Suboptimal genetic testing (Oster et al. 2013)
        \item  Workers overestimate their productivity (Hoffman and Burks, 2020)
    \end{itemize}

\end{frame}

\begin{frame}{An Example}
    An entrepreneur has \textbf{unknown intrinsic ability} $\theta^*$ and chooses a level of effort $e\geq 0.$ \\
    \bigskip
    Effort and ability are transformed into output at an exogenous and \textbf{unknown rate} $\omega.$\\
    \bigskip 
    An overconfident entrepreneur believes he is of type $\hat\theta>\theta^*$\\
    \bigskip

    The entrepreneur wants to maximize their utility\\
        $$y = (\theta^* + e)\omega-\frac{1}{2}e^2 +\varepsilon$$\\
    \pause
    \bigskip
    Regardless of their own type (or their beliefs about it), they should choose $e^*(\omega)=\omega$\\
\end{frame}

\begin{frame}{Learning is Possible}
    This exercise is repeated for $t=0, 1, ...$
        $$y_t = (\theta^* + e_t)\omega-\frac{1}{2}e_t^2 +\varepsilon_t$$

    Note that both parameters are identified in this setting:\\
    \bigskip

    \begin{itemize}
        \item Choosing $\hat{e}$ and $\hat{e}+1$ over multiple periods allows identification of $\omega$\\
        \bigskip
        \item Once $\omega$ is known, $\theta$ can be backed out\\
     \end{itemize}
    \bigskip
    How come people don't learn the true $\theta$?
\end{frame}

\begin{frame}{The Literature}
Settings with two or more unknowns allow for different explanations of the bias:\\
\bigskip
\begin{enumerate}
\item Self-defeating equilibrium (Heidhues et al., 2018): 
    \begin{itemize}
        \item Bayesian on $\omega$
        \item Dogmatic about $\theta$

    \end{itemize}
    \bigskip
    \item Bayesian Likelihood Ratio test (Ba, 2022 JMP):
    \begin{itemize}
        \item Bayesian on $\omega$ 
        \item Hypothesis testing on $\theta$
    \end{itemize}
    \bigskip
    \item Self-Serving Attribution Bias with two unknowns (Brunnermeier and Parker, 2005; Coutts et al. 2022wp): 
    \begin{itemize}
        \item Good news are attributed to high $\theta$ bad news are attributed to low $\omega$
    \end{itemize}

\end{enumerate}
\end{frame}

\begin{frame}{The Research Questions}
    We know people fall somewhere between Bayesian Learning and the very extreme Heidhues et al. setting.\\
    \bigskip
    \begin{itemize}
        \item To what extent do the different theories explain the data?\\
        \begin{itemize}
            \item Is there heterogeneity in the way people update beliefs?\\
        \end{itemize}
    \end{itemize}
    \pause
    \bigskip
    Misspecified mental models lead to incorrect beliefs even in settings where there are no ego-relevant parameters
    \bigskip
    \begin{itemize}
        \item How do the models perform in a setting with two parameters that are NOT ego-relevant?\\
    \end{itemize}
\end{frame}

\begin{frame}{Roadmap}
    \begin{enumerate}
        \item Theory 1 --- Further Motivation\\
        \bigskip
        \item Theory 2\\
        \bigskip
        \item Theory 3\\
        \bigskip
        \item Unifying framework\\
        \bigskip
        \item Experimental Design
    \end{enumerate}
\end{frame}

\begin{frame}{Theory 1: Dogmatic Modelers (HKS)}
    \Large\textbf{Unrealistic Expectations and Misguided Learning \\}
    (Heidhues, Köszegi, and Strack, 2018)
\end{frame}

\begin{frame}{The Setting}

$\omega$ is drawn from density $g_0$ with $\omega^*=E_{g_0}(\omega).$\\
\bigskip
The entrepreneur's true ability is $\theta^*$, they believe with certainty that it is $\hat\theta>\theta^*.$ \\
\bigskip
At $t=0$, the entrepreneur has the prior $g_0.$\\
\bigskip
They correctly choose $e_0 = \omega^*.$\\
\bigskip
\pause
Suppose they don't update their beliefs or their choice for a long time.
\end{frame}

\begin{frame}{Updating the Beliefs}

For their chosen effort $\omega^*$, they observe an average output of 
$$ y_0=(\theta^* + \omega^*)\omega^*-\frac{1}{2}(\omega^*)^2 $$

But were expecting
$$ (\hat\theta + \omega^*)\omega^*-\frac{1}{2}(\omega^*)^2 > y_0$$\\
\bigskip
\pause
So they conclude that $\omega_1$ must be such that:
$$(\hat \theta + \omega^*)\omega_1-\frac{1}{2}(\omega^*)^2 = (\theta^* + \omega^*)\omega^*-\frac{1}{2}(\omega^*)^2 $$\\
\bigskip 
Which gives $\omega_1 = \frac{(\theta^* + \omega^*)\omega^*}{(\hat \theta + \omega^*)}<\omega^*$

\end{frame}

\begin{frame}{Bayesian updating}
    Updating choices every period (myopically) the belief will drift even further:\\
    \bigskip
    A lower choice of $e$ still gives a lower output than expected. \\
    \bigskip
    So $\omega_{t+1}$ must be lower than they believed in period $t$.\\
    \bigskip
    Heidhues et al. show that this process converges to a belief $\omega_\infty<\omega_1<\omega^*.$\\
    \bigskip
    The result is symmetric for underconfident subjects.

\end{frame}

\begin{frame}{In the Lab}
\label{Figure1}

Götte and Kozakiewicz (2022) test the predictions in a lab experiment:

\begin{figure}
    \centering
    \includegraphics[scale=0.5]{figures/GK_experiment.png}
\end{figure}
    \hyperlink{Other Figures}{\beamerbutton{Other Figures}}

\end{frame}

\begin{frame}{Results}
    Biased updating in the same direction as the theoretical predictions.\\
    \bigskip
    The bias is not as large as the theory predicts.\\
    \bigskip
    Some agents do update their belief of $\theta$ in the right direction.\\
\end{frame}

\begin{frame}{Theory 2: Switchers}
    \Large\textbf{ Robust Misspecified Models and Paradigm Shifts \\}
    (Ba, 2022 JMP)
\end{frame}

\begin{frame}{The Setting}
    Same as HKS but with finite $\Omega$ and finite $A$\\
    \bigskip
    Now the entrepreneur is willing to switch to an alternative level of ability $\theta'$ (assume $\theta' = \theta^*$).\\
    \bigskip
    Instead of updating $P[\theta]$ every period, they perform a Bayesian hypothesis test:\\
    \bigskip
    Adopt model $\theta'$ at time t iff \\
    $$\frac{\ell_t (\theta')}{\ell_t(\theta)}>\alpha\geq1$$

    Where $$\ell_t(\theta) := \sum_{\omega}g_0(\omega)\prod_{\tau=0}^{t-1}\pi^\theta(y_\tau|a_\tau, \omega)$$

\end{frame}

\begin{frame}{Results}

    The self-defeating trap is difficult to escape when the entrepreneur is overconfident.\\
    \bigskip
    Underconfident agents escape the trap at a higher rate than overconfident and learn the true parameter.\\
    \bigskip
    Explains why underconfidence is less prevalent in the data.\\
    \bigskip
    Overconfident agents can escape the trap if their prior is not too ``tight'' around a self confirming equilibrium.

\end{frame}

\begin{frame}{Theory 3: Motivated Beliefs}
    \Large\textbf{Optimal Expectations}\\
    (Brunnermeier and Parker, 2005)\\
    \bigskip
    \Large\textbf{What to blame? Self-serving attribution bias with
multi-dimensional uncertainty}\\
    (Coutts et al., 2022 wp)
\end{frame}

\begin{frame}{The Setting}
    A fixed effort $e$, $\theta \in \{\theta_H, \theta_L\}$ and $\omega \in \{\omega_H, \omega_L\}$ generate binary signals (success/failure)\\
    \bigskip
    After a success the agent updates their belief about $\theta$ with distortions $\gamma_\theta$ and $\gamma_\omega$, $p_{t+1}(\theta_H|success)$ is given by:\\
    \begin{center}
        \small
        $\frac{\gamma^s_\theta\gamma^s_\omega\pi_t(\theta_H) g_t(\omega_H) q_t(\theta_H, \omega_H) + \gamma^s_\theta\pi_t(\theta_H) g_t(\omega_L) q_t(\theta_H, \omega_L)}{\gamma^s_\theta\gamma^s_\omega\pi_t(\theta_H) g_t(\omega_H) q_t(\theta_H, \omega_H) + \gamma^s_\theta\pi_t(\theta_H) g_t(\omega_L) q_t(\theta_H, \omega_L) + \gamma^s_\omega\pi_t(\theta_L) g_t(\omega_H) q_t(\theta_L, \omega_H) + \pi_t(\theta_L) g_t(\omega_L) q_t(\theta_L, \omega_L)}$\\
    \end{center}
    \bigskip
    with $q_t(\theta, \omega):=Pr[\text{success}|\theta, \omega]$ increasing in $\omega$ and $\theta$
\end{frame}

\begin{frame}{Predictions and Evidence (Coutts et al. 2022)}
    Prediction: Even unbiased agents will overweight $\theta_H$ after a success and end up being biased.\\
    \bigskip
    Experiment: Evidence of biased updating when $\theta$ is ego-relevant.\\
    \bigskip
    The framework does not allow direct comparisons with the other two theoretical predictions.\\
    \bigskip
    It gives an alternative rationalization for the persistence of overconfidence.

\end{frame}

\begin{frame}{A framework where we can compare}

Finite type space: $\theta \in \{\theta_H, \theta_M, \theta_L\}$\\
\bigskip
Finite state space: $\omega \in \{\omega_H, \omega_M, \omega_L\}$
with $p(\omega_k)=1/3$ \\
\bigskip
Finite action space: $e \in \{e_H, e_M, e_L\}$\\
\bigskip
Binary signal: Success/Failure with $P\left[Success|e, \omega, \theta\right]$ satisfying the assumptions of HKS

\end{frame}

\begin{frame}{The Data Generating Process}
The probability of success is given by:\\
\bigskip
\centering
\begin{tabular}{ c|c|c|c|}

  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
  \cline{2-4}
  $e_H$ & 50 & 20 & 2 \\
  \cline{2-4}
  $e_M$ & 45 & 30 & 7 \\
  \cline{2-4}
  $e_L$ & 40 & 25 & 20 \\
  \cline{2-4}
  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_L$} & \multicolumn{1}{c}{}\\
\end{tabular}
\hspace{.3cm} % adjust this value to set the space between tables
\begin{tabular}{ c|c|c|c|}

  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
  \cline{2-4}
  $e_H$ & 80 & 50 & 5 \\
  \cline{2-4}
  $e_M$ & 69 & 65 & 30 \\
  \cline{2-4}
  $e_L$ & 65 & 45 & 40 \\
  \cline{2-4}
  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_M$} & \multicolumn{1}{c}{}\\
\end{tabular}
\hspace{.3cm} % adjust this value to set the space between tables
\begin{tabular}{ c|c|c|c|}

  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
  \cline{2-4}
  $e_H$ & 98 & 65 & 25 \\
  \cline{2-4}
  $e_M$ & 80 & 69 & 35 \\
  \cline{2-4}
  $e_L$ & 75 & 55 & 45 \\
  \cline{2-4}
  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_H$} & \multicolumn{1}{c}{}\\
\end{tabular}

\end{frame}

\begin{frame}{The Data Generating Process}
    \centering
\begin{tabular}{ c|c|c|c|}

  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
  \cline{2-4}
  $e_H$ & \cellcolor{blue!25}50 & 20 & 2 \\
  \cline{2-4}
  $e_M$ & 45 & \cellcolor{blue!25}30 & 7 \\
  \cline{2-4}
  $e_L$ & 40 & 25 & \cellcolor{blue!25}20 \\
  \cline{2-4}
  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_L$} & \multicolumn{1}{c}{}\\
\end{tabular}
\hspace{.3cm} % adjust this value to set the space between tables
\begin{tabular}{ c|c|c|c|}

  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
  \cline{2-4}
  $e_H$ & \cellcolor{blue!25}80 & 50 & 5 \\
  \cline{2-4}
  $e_M$ & 69 & \cellcolor{blue!25}65 & 30 \\
  \cline{2-4}
  $e_L$ & 65 & 45 & \cellcolor{blue!25}40 \\
  \cline{2-4}
  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_M$} & \multicolumn{1}{c}{}\\
\end{tabular}
\hspace{.3cm} % adjust this value to set the space between tables
\begin{tabular}{ c|c|c|c|}

  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
  \cline{2-4}
  $e_H$ & \cellcolor{blue!25}98 & 65 & 25 \\
  \cline{2-4}
  $e_M$ & 80 & \cellcolor{blue!25}69 & 35 \\
  \cline{2-4}
  $e_L$ & 75 & 55 & \cellcolor{blue!25}45 \\
  \cline{2-4}
  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_H$} & \multicolumn{1}{c}{}\\
\end{tabular}
\end{frame}

\begin{frame}{The Data Generating Process}
\begin{center}
\begin{tikzpicture}
  \draw[<-] (1,0) -- (3,0);
  \draw[<-] (5,0) -- (7,0);
  \draw[<-] (9,0) -- (11,0);
\end{tikzpicture}
\end{center}
\\
\bigskip
\centering
\begin{tabular}{ c|c|c|c|}

  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
  \cline{2-4}
  $e_H$ & \cellcolor{blue!25}50 & 20 & 2 \\
  \cline{2-4}
  $e_M$ & 45 & \cellcolor{blue!25}30 & 7 \\
  \cline{2-4}
  $e_L$ & 40 & 25 & \cellcolor{blue!25}20 \\
  \cline{2-4}
  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_L$} & \multicolumn{1}{c}{}\\
\end{tabular}
\hspace{.3cm} % adjust this value to set the space between tables
\begin{tabular}{ c|c|c|c|}

  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
  \cline{2-4}
  $e_H$ & \cellcolor{blue!25}80 & 50 & 5 \\
  \cline{2-4}
  $e_M$ & 69 & \cellcolor{blue!25}65 & 30 \\
  \cline{2-4}
  $e_L$ & 65 & 45 & \cellcolor{blue!25}40 \\
  \cline{2-4}
  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_M$} & \multicolumn{1}{c}{}\\
\end{tabular}
\hspace{.3cm} % adjust this value to set the space between tables
\begin{tabular}{ c|c|c|c|}

  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
  \cline{2-4}
  $e_H$ & \cellcolor{blue!25}98 & 65 & 25 \\
  \cline{2-4}
  $e_M$ & 80 & \cellcolor{blue!25}69 & 35 \\
  \cline{2-4}
  $e_L$ & 75 & 55 & \cellcolor{blue!25}45 \\
  \cline{2-4}
  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_H$} & \multicolumn{1}{c}{}\\
\end{tabular}

\begin{center}
    \resizebox{0.6\linewidth}{!}{\vector(1,0){300}}
  \end{center}

\end{frame}

\begin{frame}{A Self-Confirming Equilibrium}

\centering
\begin{tabular}{ c|c|c|c|}

  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
  \cline{2-4}
  $e_H$ & \cellcolor[HTML]{b84f79}50 & 20 & 2 \\
  \cline{2-4}
  $e_M$ & 45 & 30 & 7 \\
  \cline{2-4}
  $e_L$ & 40 & 25 & 20 \\
  \cline{2-4}
  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_L$} & \multicolumn{1}{c}{}\\
\end{tabular}
\hspace{.3cm} % adjust this value to set the space between tables
\begin{tabular}{ c|c|c|c|}

  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
  \cline{2-4}
  $e_H$ & 80 & \cellcolor[HTML]{b84f79}50 & 5 \\
  \cline{2-4}
  $e_M$ & 69 &\cellcolor[HTML]{f09ebe}65 & 30 \\
  \cline{2-4}
  $e_L$ & 65 & \cellcolor[HTML]{f09ebe}45 & 40 \\
  \cline{2-4}
  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_M$} & \multicolumn{1}{c}{}\\
\end{tabular}
\hspace{.3cm} % adjust this value to set the space between tables
\begin{tabular}{ c|c|c|c|}

  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
  \cline{2-4}
  $e_H$ & 98 & 65 & 25 \\
  \cline{2-4}
  $e_M$ & 80 & 69 & 35 \\
  \cline{2-4}
  $e_L$ & 75 & 55 & 45 \\
  \cline{2-4}
  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_H$} & \multicolumn{1}{c}{}\\
\end{tabular}
\end{frame}

\begin{frame}{The Self-Confirming Equilibria}

\centering
\begin{tabular}{ c|c|c|c|}

  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
  \cline{2-4}
  $e_H$ & \cellcolor[HTML]{b84f79}50 & 20 & 2 \\
  \cline{2-4}
  $e_M$ & 45 & \cellcolor[HTML]{5f94b8}30 & 7 \\
  \cline{2-4}
  $e_L$ & \cellcolor[HTML]{69a35b}40 & 25 & 20 \\
  \cline{2-4}
  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_L$} & \multicolumn{1}{c}{}\\
\end{tabular}
\hspace{.3cm} % adjust this value to set the space between tables
\begin{tabular}{ c|c|c|c|}

  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
  \cline{2-4}
  $e_H$ & 80 & \cellcolor[HTML]{b84f79}50 & 5 \\
  \cline{2-4}
  $e_M$ & \cellcolor[HTML]{fab143}69 & 65 & \cellcolor[HTML]{5f94b8}30 \\
  \cline{2-4}
  $e_L$ & 65 & \cellcolor[HTML]{9662f0}45 & \cellcolor[HTML]{69a35b}40 \\
  \cline{2-4}
  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_M$} & \multicolumn{1}{c}{}\\
\end{tabular}
\hspace{.3cm} % adjust this value to set the space between tables
\begin{tabular}{ c|c|c|c|}

  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
  \cline{2-4}
  $e_H$ & 98 & 65 & 25 \\
  \cline{2-4}
  $e_M$ & 80 & \cellcolor[HTML]{fab143}69 & 35 \\
  \cline{2-4}
  $e_L$ & 75 & 55 & \cellcolor[HTML]{9662f0}45 \\
  \cline{2-4}
  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_H$} & \multicolumn{1}{c}{}\\
\end{tabular}
\end{frame}

\begin{frame}{An Example}
\begin{itemize}
    \item True type is $\theta_M$ \\
    \bigskip
    \item True exchange rate is $\omega_M$ $\rightarrow$ The entrepreneur believes it is uniformly distributed\\
    \end{itemize}

    \centering
\begin{tabular}{ c|c|c|c|}

  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
  \cline{2-4}
  $e_H$ & 50 & 20 & 2 \\
  \cline{2-4}
  $e_M$ & 45 & 30 & 7 \\
  \cline{2-4}
  $e_L$ & 40 & 25 & 20 \\
  \cline{2-4}
  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_L$} & \multicolumn{1}{c}{}\\
\end{tabular}
\hspace{.3cm} % adjust this value to set the space between tables
\begin{tabular}{ c|c|c|c|}

  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
  \cline{2-4}
  $e_H$ & 80 & \cellcolor{blue!25}50 & 5 \\
  \cline{2-4}
  $e_M$ & 69 & \cellcolor{blue!25}65 & 30 \\
  \cline{2-4}
  $e_L$ & 65 & \cellcolor{blue!25}45 & 40 \\
  \cline{2-4}
  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_M$} & \multicolumn{1}{c}{}\\
\end{tabular}
\hspace{.3cm} % adjust this value to set the space between tables
\begin{tabular}{ c|c|c|c|}

  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
  \cline{2-4}
  $e_H$ & 98 & 65 & 25 \\
  \cline{2-4}
  $e_M$ & 80 & 69 & 35 \\
  \cline{2-4}
  $e_L$ & 75 & 55 & 45 \\
  \cline{2-4}
  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_H$} & \multicolumn{1}{c}{}\\
\end{tabular}

\end{frame}

\begin{frame}{Example: Dogmatic Modeler}
\begin{itemize}
    \item Theory 1: for an entrepreneur who believes he is $\theta_H$
    \end{itemize}
    \bigskip
    \begin{enumerate}
        \item Chooses $e_H$ and is disappointed $\rightarrow$ adjust belief about $\omega$ downward\\
        \bigskip
        \item Eventually chooses $e_M$ and is disappointed as well $\rightarrow$ adjust belief about $\omega$\\
        \bigskip
        \item Eventually chooses $e_L$ and falls into a self-confirming equilibrium
    \end{enumerate}

\end{frame}

\begin{frame}{Dogmatic Overconfident}
    \begin{figure}
        \centering
        \includegraphics[trim=0 20 0 0, clip]{figures/dogmatic.png}
        \caption{$\theta^*=\theta_M$, $\hat\theta=\theta_H$, $\omega^*=\omega_M$}
    \end{figure}
\end{frame}

\begin{frame}{Example: Likelihood Testing}
\begin{itemize}
    \item Theory 2: for the same initial belief
    \item Keeping track of the likelihood of each $\theta$
    \end{itemize}
    \bigskip
    \begin{enumerate}
        \item Chooses $e_H$ and is disappointed $\rightarrow$ adjust belief about $\omega$ downward\\
        \bigskip
        \item Eventually chooses $e_M$ and is disappointed as well $\rightarrow$ adjust belief about $\omega$\\
        \bigskip
        \item Eventually chooses $e_L$ and falls into a self-confirming equilibrium\\
        \bigskip
        \item At some point, the likelihood of $\theta_M$ becomes much larger than that of $\theta_H$ and the agent updates their belief
    \end{enumerate}

\end{frame}

\begin{frame}{Switcher Overconfident}
    \begin{figure}
        \centering
        \includegraphics{figures/switch.png}
        \caption{$\theta^*=\theta_M$, $\hat\theta=\theta_H$, $\omega^*=\omega_M$, $\alpha= 1.1$}
    \end{figure}
\end{frame}

\begin{frame}{Example: Self-Serving Beliefs}
\begin{itemize}
    \item Theory 3: Start with a diffused prior over $\theta$
    \end{itemize}
    \bigskip
    \begin{enumerate}
        \item Chooses $e$ that maximizes utility according to priors
        \bigskip
        \item Success $\rightarrow$ overweight $\theta_H$ and underweight $\omega_H$\\
        \item Failure $\rightarrow$ overweight $\omega_L$ underweight $\theta_L$\\
        \bigskip
        \item Belief on $\omega$ deteriorates a lot after failure streaks
        \item Belief on $\theta$ increases a lot after success streaks\\
    \end{enumerate}

\end{frame}

\begin{frame}{Dogmatic Overconfident}
    \begin{figure}
        \centering
        \includegraphics{figures/SS.png}
        \caption{$\gamma^s_\theta=1.2$, $\gamma^s_\omega = .8$}
    \end{figure}
\end{frame}

\begin{frame}{The Simulation}
\label{Figure2}
    \begin{figure}
    \centering
    \includegraphics[scale=0.43]{figures/all_1_1.png}
\end{figure}

\hyperlink{WorstCase}{\beamerreturnbutton{Other Cases}}

\end{frame}

\begin{frame}{The Experiment:}
Brief Questionnaire: Age, Gender, Nationality, Major\\
\bigskip
Part 1: Set Types\\
\bigskip
\begin{itemize}
    \item Quiz: Answer as many questions as you can in 2 minutes:\\
    \begin{itemize}
        \item Math, Verbal, Pop-Culture, Science, Us Geography, Sports and Videogames\\
    \end{itemize}
    \bigskip
    \item How many questions do you think you answered correctly in each quiz?\\
    \begin{itemize}
        \item[o] Bin1, Bin2, Bin3
    \end{itemize}
\end{itemize}

\end{frame}

\begin{frame}{The Experiment: Ego-relevant condition}
Belief updating and effort choice (One topic at a time)\\
\bigskip
\begin{itemize}
    \item Choose an effort
    \item Receive a signal realization
\end{itemize}
\bigskip
25 rounds per topic

\end{frame}

\begin{frame}{Eliciting Beliefs?}
\begin{itemize}
    \item $E[\omega]$ is revealed by their choice of effort\\
    \bigskip
    \item Eliciting beliefs for $\theta$ can incentivize learning in a way that is not consistent with the model\\
    \bigskip
\end{itemize}

Allow them to see the success rate matrix for only one type. 
\begin{itemize}
    \item Track the matrices they choose to see in each round
\end{itemize}

\end{frame}

\begin{frame}{The Experiment: Ego-irrelevant condition}

Observe the characteristics of a participant. 
\begin{itemize}
    \item ``What score do you think this participant got in the (topic) quiz?'' 
    \item Bin1, Bin2, Bin3 
\end{itemize}

Belief updating and effort choice\\
\bigskip
\begin{itemize}
    \item Choose an effort
    \item Receive a signal realization
    \begin{itemize}
        \item[o] The DGP is that of the observed participant
    \end{itemize}
\end{itemize}
\bigskip
25 rounds (per topic/participant)

\end{frame}

\begin{frame}{Conclusion}
What I hope to get from this design:\\
\bigskip
    \begin{itemize}
        \item A classification of subjects into one of the models based on their behavior\\
        \bigskip
        \item If subjects are switchers: what is the switching threshold $\alpha$\\
        \bigskip
        \item Insight into the role of ego-relevant parameters in belief misspecification
    \end{itemize}
\end{frame}

\begin{frame}{The end}
    \large\textbf{Thank you!}
\end{frame}

\begin{frame}{Götte and Kozakiewicz (2022) }
\label{Other Figures}
    \begin{figure}
    \centering
    \includegraphics[scale=0.45]{figures/GK_under-unbiased.png}
\end{figure}

\hyperlink{Figure1}{\beamerreturnbutton{Back}}

\end{frame}

\begin{frame}{A Bad Case}
\label{WorstCase}
    \begin{figure}
    \centering
    \includegraphics[scale=0.4]{figures/all_2_2.png}
\end{figure}

\hyperlink{Figure2}{\beamerreturnbutton{Back}}

\end{frame}

\end{document}

### 2023-09-29 Slides/overconfident_beliefs/Sept23_choaching.tex
slides setup

--- 2023-09-29 Slides/overconfident_beliefs/ExpSeminar_spring23.tex
@@
 \usepackage[table]{xcolor}
+\usepackage{xcolor}
 
-\title{Models of Belief Updating:\\ The Case of Overconfidence}
+\title{Learning with Misspecified Models:\\  overconfidence and stereotypes}
 \author{Jimena Galindo}
@@
 \begin{frame}{Motivation}
-    We often observe beliefs and behaviors that are inconsistent with the fully Bayesian benchmark:\\
+    Updating beliefs is a difficult task\\
     \bigskip
-    \begin{itemize} 
-        \item Overconfidence  
-        \item Polarization 
-    \end{itemize}
+    Mounting evidence of biases\\
+\documentclass[aspectratio=169]{beamer}
 
+\usepackage{geometry}
+\usepackage{amsmath}
+\usepackage{graphicx}
+\usepackage{amsfonts}
+\usepackage{amssymb}
+\usepackage{setspace}
+\usepackage{theorem}
+\usepackage{natbib}
+\usepackage{mathtools}
+\usepackage{cite}
+\usepackage{natbib}
+\usepackage{setspace}
+\usepackage[utf8]{inputenc}
+\usepackage[english]{babel}
+\usepackage{xcolor}
+\usepackage{array}
+\usepackage{caption}
+\usepackage{graphicx}
+\usepackage{siunitx}
+\usepackage[normalem]{ulem}
+\usepackage{colortbl}
+\usepackage{multirow}
+\usepackage{hhline}
+\usepackage{calc}
+\usepackage{tabularx}
+\usepackage{threeparttable}
+\usepackage{wrapfig}
+\usepackage{adjustbox}
+\usepackage{hyperref}
+\usepackage{tikz}
+\usepackage[table]{xcolor}
+\usepackage{xcolor}
+
+\title{Learning with Misspecified Models:\\  overconfidence and stereotypes}
+\author{Jimena Galindo}
+
+\begin{document}
+
+\frame{\titlepage}
+
+\begin{frame}{Motivation}
+    Updating beliefs is a difficult task\\
     \bigskip
-    Recent theoretical literature has sought to explain these phenomena (and others) with the notion of \bf{Misspecified Mental Models}
+    Mounting evidence of biases\\
+\documentclass[aspectratio=169]{beamer}
+
+\usepackage{geometry}
+\usepackage{amsmath}
+\usepackage{graphicx}
+\usepackage{amsfonts}
+\usepackage{amssymb}
+\usepackage{setspace}
+\usepackage{theorem}
+\usepackage{natbib}
+\usepackage{mathtools}
+\usepackage{cite}
+\usepackage{natbib}
+\usepackage{setspace}
+\usepackage[utf8]{inputenc}
+\usepackage[english]{babel}
+\usepackage{xcolor}
+\usepackage{array}
+\usepackage{caption}
+\usepackage{graphicx}
+\usepackage{siunitx}
+\usepackage[normalem]{ulem}
+\usepackage{colortbl}
+\usepackage{multirow}
+\usepackage{hhline}
+\usepackage{calc}
+\usepackage{tabularx}
+\usepackage{threeparttable}
+\usepackage{wrapfig}
+\usepackage{adjustbox}
+\usepackage{hyperref}
+\usepackage{tikz}
+\usepackage[table]{xcolor}
+\usepackage{xcolor}
+
+\title{Learning with Misspecified Models:\\  overconfidence and stereotypes}
+\author{Jimena Galindo}
+
+\begin{document}
+
+\frame{\titlepage}
+
+\begin{frame}{Motivation}
+    Updating beliefs is a difficult task\\
+    \bigskip
+    Mounting evidence of biases\\
+    \bigskip
+    Economic theory developed models that rationalize biased behaviors
 \end{frame}
 
-\begin{frame}{Motivation}
-    We often observe beliefs and behaviors that are inconsistent with the fully Bayesian benchmark:\\
-    \bigskip
-    \begin{itemize} 
-        \item Overconfidence \textbf{(today)}  
-        \item Polarization \textbf{(next time)}
-    \end{itemize}
+\begin{frame}{Prevalence of Overconfidence}
 
-    \bigskip
-    Recent theoretical literature has sought to explain these phenomena (and others) with the notion of \bf{Misspecified Mental Models}
-\end{frame}
-
-\begin{frame}{Mental Models}
-
-A prior on unknown parameters/states and an updating procedure\\
-\bigskip
-\begin{itemize}
-    \item Bayesian 
-    \item Dogmatic 
-    \item Motivated Beliefs
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}{Overconfidence}
-    Belief that my type is higher than it truly is (``overestimation'' as in Moore and Healy, 2008)\\
+   \textbf{OVERCONFIDENCE}: Belief that my type is higher than it truly is (``overestimation'' as in Moore and Healy, 2008)\\
     \bigskip
@@
         \item Excess entry of entrepreneurs (Camerer and Lovallo, 1999)
-        \item Suboptimal genetic testing (Oster et al. 2013)
+        \item Suboptimal genetic testing and healthcare (Oster et al. 2013)
         \item  Workers overestimate their productivity (Hoffman and Burks, 2020)
@@
 \begin{frame}{An Example}
-    An entrepreneur has \textbf{unknown intrinsic ability} $\theta^*$ and chooses a level of effort $e\geq 0.$ \\
+    A student has \textbf{unknown intrinsic ability} $\theta^*$ and chooses a level of effort $e\geq 0$. \\
     \bigskip
-    Effort and ability are transformed into output at an exogenous and \textbf{unknown rate} $\omega.$\\
+    Effort and ability are transformed into a noisy output at an exogenous and \textbf{unknown rate} $\omega.$\\
     \bigskip 
-    An overconfident entrepreneur believes he is of type $\hat\theta>\theta^*$\\
+    An overconfident student believes he is of type $\hat\theta>\theta^*$\\
     \bigskip
 
-    The entrepreneur wants to maximize their utility\\
+    And wants to maximize utility\\
         $$y = (\theta^* + e)\omega-\frac{1}{2}e^2 +\varepsilon$$\\
@@
     \bigskip
-    Regardless of their own type (or their beliefs about it), they should choose $e^*(\omega)=\omega$\\
+   {\textbf{Regardless of their own type, they should choose $e^*(\omega)=\omega$\\}}
 \end{frame}
@@
     \bigskip
-    How come people don't learn the true $\theta$?
+    How come people don't learn their true type and don't choose the optimal effort?
 \end{frame}
 
-\begin{frame}{The Literature}
+\begin{frame}{Mental Models}
+
+A prior belief over parameters/states/types and an updating procedure\\
+\bigskip
+\begin{itemize}
+    \item Bayesian 
+    \item Dogmatic 
+    \item Motivated Beliefs/Self-attribution
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Research Questions}
+    To what extent do the different theories explain observed behavior?\\
+    \begin{itemize}
+        \item Do we observe heterogeneity in the use of mental models?
+    \end{itemize}
+    \bigskip
+    Is ego-relevance of the type a key feature for the misspecification?
+    \begin{itemize}
+        \item Can the same theories be used to explain the prevalence of stereotypes?
+    \end{itemize}
+\end{frame}
+
+\begin{frame}{Road-map}
+    \begin{enumerate}
+        \item Three Theories of Overconfidence\\
+        \bigskip
+        \item Mechanisms and Predictions\\
+        \bigskip
+        \item Unifying Framework\\
+        \bigskip
+        \item Experimental Design\\
+        \bigskip
+        \item Results (coming soon)
+    \end{enumerate}
+\end{frame}
+
+\begin{frame}{The Theories}
 Settings with two or more unknowns allow for different explanations of the bias:\\
@@
 
-\begin{frame}{The Research Questions}
-    We know people fall somewhere between Bayesian Learning and the very extreme Heidhues et al. setting.\\
-    \bigskip
-    \begin{itemize}
-        \item To what extent do the different theories explain the data?\\
-        \begin{itemize}
-            \item Is there heterogeneity in the way people update beliefs?\\
-        \end{itemize}
-    \end{itemize}
-    \pause
-    \bigskip
-    Misspecified mental models lead to incorrect beliefs even in settings where there are no ego-relevant parameters
-    \bigskip
-    \begin{itemize}
-        \item How do the models perform in a setting with two parameters that are NOT ego-relevant?\\
-    \end{itemize}
-\end{frame}
-
-\begin{frame}{Roadmap}
-    \begin{enumerate}
-        \item Theory 1 --- Further Motivation\\
-        \bigskip
-        \item Theory 2\\
-        \bigskip
-        \item Theory 3\\
-        \bigskip
-        \item Unifying framework\\
-        \bigskip
-        \item Experimental Design
-    \end{enumerate}
-\end{frame}
-
 \begin{frame}{Theory 1: Dogmatic Modelers (HKS)}
@@
 
-$\omega$ is drawn from density $g_0$ with $\omega^*=E_{g_0}(\omega).$\\
+The student's true ability is $\theta^*$, they believe with certainty that it is $\hat\theta>\theta^*.$ \\
 \bigskip
-The entrepreneur's true ability is $\theta^*$, they believe with certainty that it is $\hat\theta>\theta^*.$ \\
+The rate $\omega$ is drawn from density $g_0$ with $\omega^*=E_{g_0}(\omega).$\\
+
 \bigskip
-At $t=0$, the entrepreneur has the prior $g_0.$\\
+At $t=0$, the student has the prior $g_0.$\\
 \bigskip
@@
 \pause
-Suppose they don't update their beliefs or their choice for a long time.
+\textbf{Suppose they don't update their beliefs or their choice for a number of periods.}
 \end{frame}
@@
 
-\begin{frame}{Bayesian updating}
+\begin{frame}{Updating the Beliefs}
     Updating choices every period (myopically) the belief will drift even further:\\
@@
     \bigskip
-    Heidhues et al. show that this process converges to a belief $\omega_\infty<\omega_1<\omega^*.$\\
+    \textbf{Prediction:} convergence to a self-confirming equilibrium with $\omega_\infty<\omega_1<\omega^*.$\\
     \bigskip
@@
 
-\end{frame}
-
-\begin{frame}{In the Lab}
-\label{Figure1}
-
-Götte and Kozakiewicz (2022) test the predictions in a lab experiment:
-
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.5]{figures/GK_experiment.png}
-\end{figure}
-    \hyperlink{Other Figures}{\beamerbutton{Other Figures}}
-
-\end{frame}
-
-\begin{frame}{Results}
-    Biased updating in the same direction as the theoretical predictions.\\
-    \bigskip
-    The bias is not as large as the theory predicts.\\
-    \bigskip
-    Some agents do update their belief of $\theta$ in the right direction.\\
 \end{frame}
@@
     Adopt model $\theta'$ at time t iff \\
-    $$\frac{\ell_t (\theta')}{\ell_t(\theta)}>\alpha\geq1$$
+    $$\frac{\ell_t (\theta')}{\ell_t(\hat{\theta})}>\alpha\geq1$$
 
@@
 
-    The self-defeating trap is difficult to escape when the entrepreneur is overconfident.\\
-    \bigskip
-    Underconfident agents escape the trap at a higher rate than overconfident and learn the true parameter.\\
-    \bigskip
-    Explains why underconfidence is less prevalent in the data.\\
-    \bigskip
-    Overconfident agents can escape the trap if their prior is not too ``tight'' around a self confirming equilibrium.
+    \textbf{Prediction:} Misspecified agents escape the trap as long as their prior is not too ``tight'' around a self-confirming equilibrium.
 
@@
 \begin{frame}{Theory 3: Motivated Beliefs}
-    \Large\textbf{Optimal Expectations}\\
-    (Brunnermeier and Parker, 2005)\\
-    \bigskip
-    \Large\textbf{What to blame? Self-serving attribution bias with
-multi-dimensional uncertainty}\\
-    (Coutts et al., 2022 wp)
+
+    \Large\textbf{Errors in probabilistic reasoning and judgment biases}\\
+    (Benjamin, 2019)\\
+
 \end{frame}
@@
 \begin{frame}{The Setting}
-    A fixed effort $e$, $\theta \in \{\theta_H, \theta_L\}$ and $\omega \in \{\omega_H, \omega_L\}$ generate binary signals (success/failure)\\
+    Fixed effort $e$, $\theta \in \{\theta_H, \theta_L\}$ and $\omega \in \{\omega_H, \omega_L\}$ generate binary signals (\textbf{s}/\textbf{f})\\
     \bigskip
-    After a success the agent updates their belief about $\theta$ with distortions $\gamma_\theta$ and $\gamma_\omega$, $p_{t+1}(\theta_H|success)$ is given by:\\
-    \begin{center}
-        \small
-        $\frac{\gamma^s_\theta\gamma^s_\omega\pi_t(\theta_H) g_t(\omega_H) q_t(\theta_H, \omega_H) + \gamma^s_\theta\pi_t(\theta_H) g_t(\omega_L) q_t(\theta_H, \omega_L)}{\gamma^s_\theta\gamma^s_\omega\pi_t(\theta_H) g_t(\omega_H) q_t(\theta_H, \omega_H) + \gamma^s_\theta\pi_t(\theta_H) g_t(\omega_L) q_t(\theta_H, \omega_L) + \gamma^s_\omega\pi_t(\theta_L) g_t(\omega_H) q_t(\theta_L, \omega_H) + \pi_t(\theta_L) g_t(\omega_L) q_t(\theta_L, \omega_L)}$\\
-    \end{center}
+    After a signal realization $m$, the agent updates their belief about $\theta$ with distortions $c_m^\theta$ and $c_m^\omega$, so that:\\
+
+        $$\frac{p_{t+1}[\theta_H]}{p_{t+1}[\theta_L]} = \left(\frac{p[\text{m}|\theta_H]}{p[\text{m}|\theta_L]}\right)^{c_m^\theta}\frac{p_t[\theta_H]}{p_t[\theta_L]}$$
+
+    and
+        $$\frac{p_{t+1}[\omega_H]}{p_{t+1}[\omega_L]} = \left(\frac{p[\text{m}|\omega_H]}{p[\text{m}|\omega_L]}\right)^{c_m^\omega}\frac{p_t[\omega_H]}{p_t[\omega_L]}$$
+
     \bigskip
-    with $q_t(\theta, \omega):=Pr[\text{success}|\theta, \omega]$ increasing in $\omega$ and $\theta$
+    The agent suffers from self-attribution bias if $c_s^\theta >c_f^\theta$ and $c_s^\omega < c_f^\omega$.
 \end{frame}
 
-\begin{frame}{Predictions and Evidence (Coutts et al. 2022)}
-    Prediction: Even unbiased agents will overweight $\theta_H$ after a success and end up being biased.\\
+\begin{frame}{Predictions}
+    \textbf{Prediction:} Even unbiased agents will overweight $\theta_H$ after a success and end up being biased.\\
     \bigskip
-    Experiment: Evidence of biased updating when $\theta$ is ego-relevant.\\
+    When $c^\theta = c^\omega = 1$, the updating procedure coincides with the unbiased Bayesian.\\
+
     \bigskip
-    The framework does not allow direct comparisons with the other two theoretical predictions.\\
-    \bigskip
-    It gives an alternative rationalization for the persistence of overconfidence.
+    The framework does not allow direct comparisons with the other two theories.\\
 
@@
 
-\begin{frame}{A framework where we can compare}
+\begin{frame}{A Unifying Framework}
 
@@
 \begin{itemize}
-    \item Theory 1: for an entrepreneur who believes he is $\theta_H$
+    \item Theory 1: for a student who believes he is $\theta_H$
     \end{itemize}
@@
         \centering
-        \includegraphics[trim=0 20 0 0, clip]{figures/dogmatic.png}
+        \includegraphics[scale=.5]{figures2/dogmatic_over_11.png}
         \caption{$\theta^*=\theta_M$, $\hat\theta=\theta_H$, $\omega^*=\omega_M$}
@@
         \centering
-        \includegraphics{figures/switch.png}
+        \includegraphics[scale=.5]{figures2/switcher_over_11.png}
         \caption{$\theta^*=\theta_M$, $\hat\theta=\theta_H$, $\omega^*=\omega_M$, $\alpha= 1.1$}
@@
 
-\begin{frame}{Dogmatic Overconfident}
+\begin{frame}{Self-Serving Bias}
     \begin{figure}
         \centering
-        \includegraphics{figures/SS.png}
-        \caption{$\gamma^s_\theta=1.2$, $\gamma^s_\omega = .8$}
+        \includegraphics[scale=.5]{figures2/self-serving_11.png}
+
     \end{figure}
@@
     \centering
-    \includegraphics[scale=0.43]{figures/all_1_1.png}
+    \includegraphics[scale=0.2]{figures2/all_11.png}
 \end{figure}
-
-\hyperlink{WorstCase}{\beamerreturnbutton{Other Cases}}
 
@@
 \begin{frame}{The Experiment:}
-Brief Questionnaire: Age, Gender, Nationality, Major\\
-\bigskip
+
 Part 1: Set Types\\
@@
     \begin{itemize}
-        \item Math, Verbal, Pop-Culture, Science, Us Geography, Sports and Videogames\\
+        \item Math, Verbal, Pop-Culture, Science, Us Geography, Sports and Video games\\
     \end{itemize}
@@
     \item Choose an effort
-    \item Receive a signal realization
+    \item Receive a sample of 10 signal realizations
 \end{itemize}
 \bigskip
-25 rounds per topic
+11 rounds per topic
 
@@
 
-\begin{frame}{The Experiment: Ego-irrelevant condition}
+\begin{frame}{The Experiment: Stereotype condition}
 
-Observe the characteristics of a participant. 
+Observe the characteristics of a participant (Gender, US National or not). \\
 \begin{itemize}
-    \item ``What score do you think this participant got in the (topic) quiz?'' 
-    \item Bin1, Bin2, Bin3 
+    \item ``What score do you think this participant got in the (topic) quiz?'' \\
+    \item Bin1, Bin2, Bin3 \\
 \end{itemize}
+\bigskip
+Belief updating and effort choice\\
 
-Belief updating and effort choice\\
-\bigskip
 \begin{itemize}
@@
 \bigskip
-25 rounds (per topic/participant)
+11 rounds (per topic/participant)
 
+\end{frame}
+
+\begin{frame}{Screen}
+    \begin{figure}
+        \centering
+        \includegraphics[scale=.4]{figures2/screen1.png}
+    \end{figure}
+\end{frame}
+
+\begin{frame}{Screen}
+    \begin{figure}
+        \centering
+        \includegraphics[scale=.4]{figures2/screen2.png}
+    \end{figure}
 \end{frame}
@@
 
-\begin{frame}{Götte and Kozakiewicz (2022) }
-\label{Other Figures}
-    \begin{figure}
-    \centering
-    \includegraphics[scale=0.45]{figures/GK_under-unbiased.png}
-\end{figure}
-
-\hyperlink{Figure1}{\beamerreturnbutton{Back}}
-
-\end{frame}
-
-\begin{frame}{A Bad Case}
-\label{WorstCase}
-    \begin{figure}
-    \centering
-    \includegraphics[scale=0.4]{figures/all_2_2.png}
-\end{figure}
-
-\hyperlink{Figure2}{\beamerreturnbutton{Back}}
-
-\end{frame}
-
 \end{document}

### 2023-09-29 Slides/overconfident_beliefs/TheoryLunch_fall22.tex
slides setup

--- 2023-09-29 Slides/overconfident_beliefs/ExpSeminar_spring23.tex
@@
 \usepackage{hyperref}
-\usepackage{tikz}
-\usepackage[table]{xcolor}
 
-\title{Models of Belief Updating:\\ The Case of Overconfidence}
-\author{Jimena Galindo}
+\title{Testing the Overconfidence Trap}
 
@@
 \begin{frame}{Motivation}
-    We often observe beliefs and behaviors that are inconsistent with the fully Bayesian benchmark:\\
-    \bigskip
-    \begin{itemize} 
-        \item Overconfidence  
-        \item Polarization 
-    \end{itemize}
-
-    \bigskip
-    Recent theoretical literature has sought to explain these phenomena (and others) with the notion of \bf{Misspecified Mental Models}
-\end{frame}
-
-\begin{frame}{Motivation}
-    We often observe beliefs and behaviors that are inconsistent with the fully Bayesian benchmark:\\
-    \bigskip
-    \begin{itemize} 
-        \item Overconfidence \textbf{(today)}  
-        \item Polarization \textbf{(next time)}
-    \end{itemize}
-
-    \bigskip
-    Recent theoretical literature has sought to explain these phenomena (and others) with the notion of \bf{Misspecified Mental Models}
-\end{frame}
-
-\begin{frame}{Mental Models}
-
-A prior on unknown parameters/states and an updating procedure\\
-\bigskip
-\begin{itemize}
-    \item Bayesian 
-    \item Dogmatic 
-    \item Motivated Beliefs
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}{Overconfidence}
-    Belief that my type is higher than it truly is (``overestimation'' as in Moore and Healy, 2008)\\
-    \bigskip
-
-    Overconfidence seems to be persistent in various settings. Ultimately it leads to sub-optimal choices:
+    Overconfidence seems to be persistent in various settings. Ultimately it leads to suboptimal choices:
     \begin{itemize} 
         \item Excess entry of entrepreneurs (Camerer and Lovallo, 1999)
-        \item Suboptimal genetic testing (Oster et al. 2013)
+        \item Suboptimal genetic testing and healthcare (Oster et al. 2013)
         \item  Workers overestimate their productivity (Hoffman and Burks, 2020)
     \end{itemize}
+    \bigskip
 
@@
 \begin{frame}{An Example}
-    An entrepreneur has \textbf{unknown intrinsic ability} $\theta^*$ and chooses a level of effort $e\geq 0.$ \\
+    An entrepreneur has \textbf{unknown intrinsic ability} $\theta$ and chooses a level of effort $e\geq 0.$ \\
+    \bigskip
+    An overconfident entrepreneur believes $\theta$ is larger than the true value.\\
     \bigskip
@@
     \bigskip 
-    An overconfident entrepreneur believes he is of type $\hat\theta>\theta^*$\\
-    \bigskip
-
-    The entrepreneur wants to maximize their utility\\
-        $$y = (\theta^* + e)\omega-\frac{1}{2}e^2 +\varepsilon$$\\
+    So the entrepreneur wants to maximize \\
+        $$y = (\theta + e)\omega-\frac{1}{2}e^2 +\varepsilon$$
     \pause
-    \bigskip
-    Regardless of their own type (or their beliefs about it), they should choose $e^*(\omega)=\omega$\\
+    Regardless of their own type (or their beliefs about it), they should choose $e^*.(\omega)=\omega$\\
 \end{frame}
@@
 \begin{frame}{Learning is Possible}
-    This exercise is repeated for $t=0, 1, ...$
-        $$y_t = (\theta^* + e_t)\omega-\frac{1}{2}e_t^2 +\varepsilon_t$$
-
+    This exercise is myopically repeated for $t=0, 1, ...$
+        $$y_t = (\theta + e_t)\omega-\frac{1}{2}e_t^2 +\varepsilon_t$$
     Note that both parameters are identified in this setting:\\
     \bigskip
-
     \begin{itemize}
-        \item Choosing $\hat{e}$ and $\hat{e}+1$ over multiple periods allows identification of $\omega$\\
+        \item Choosing $\hat{e}$ and $\hat{e}+1$ allows identification of $\omega$\\
         \bigskip
@@
 \begin{enumerate}
-\item Self-defeating equilibrium (Heidhues et al., 2018): 
+    \item Self-attribution bias with two unknowns (Coutts et al. 2022 wp): 
     \begin{itemize}
-        \item Bayesian on $\omega$
-        \item Dogmatic about $\theta$
-
+        \item Good news are attributed to high $\theta$ bad news are attributed to low $\omega$
     \end{itemize}
     \bigskip
-    \item Bayesian Likelihood Ratio test (Ba, 2022 JMP):
+    \item Bayesian factor test (Ba, 2022 JMP):
     \begin{itemize}
-        \item Bayesian on $\omega$ 
+        \item Bayesian updating on $\omega$ 
         \item Hypothesis testing on $\theta$
@@
     \bigskip
-    \item Self-Serving Attribution Bias with two unknowns (Brunnermeier and Parker, 2005; Coutts et al. 2022wp): 
+    \item Self-defeating equilibrium (Heidhues et al., 2018): 
     \begin{itemize}
-        \item Good news are attributed to high $\theta$ bad news are attributed to low $\omega$
+        \item Never updates beliefs about $\theta$
+        \item Bayesian on $\omega$
     \end{itemize}
@@
 
-\begin{frame}{The Research Questions}
-    We know people fall somewhere between Bayesian Learning and the very extreme Heidhues et al. setting.\\
-    \bigskip
-    \begin{itemize}
-        \item To what extent do the different theories explain the data?\\
-        \begin{itemize}
-            \item Is there heterogeneity in the way people update beliefs?\\
-        \end{itemize}
-    \end{itemize}
-    \pause
-    \bigskip
-    Misspecified mental models lead to incorrect beliefs even in settings where there are no ego-relevant parameters
-    \bigskip
-    \begin{itemize}
-        \item How do the models perform in a setting with two parameters that are NOT ego-relevant?\\
-    \end{itemize}
-\end{frame}
-
-\begin{frame}{Roadmap}
-    \begin{enumerate}
-        \item Theory 1 --- Further Motivation\\
-        \bigskip
-        \item Theory 2\\
-        \bigskip
-        \item Theory 3\\
-        \bigskip
-        \item Unifying framework\\
-        \bigskip
-        \item Experimental Design
-    \end{enumerate}
-\end{frame}
-
-\begin{frame}{Theory 1: Dogmatic Modelers (HKS)}
+\begin{frame}{Theory 1}
     \Large\textbf{Unrealistic Expectations and Misguided Learning \\}
@@
 
-$\omega$ is drawn from density $g_0$ with $\omega^*=E_{g_0}(\omega).$\\
+$\omega$ is drawn from density $g_0$. And the realized value is $\omega^*=E_{g_0}(\omega).$\\
 \bigskip
@@
 
-For their chosen effort $\omega^*$, they observe an average output of 
+They observe an average output of 
 $$ y_0=(\theta^* + \omega^*)\omega^*-\frac{1}{2}(\omega^*)^2 $$
@@
 \begin{frame}{In the Lab}
-\label{Figure1}
 
@@
     \centering
-    \includegraphics[scale=0.5]{figures/GK_experiment.png}
+    \includegraphics[scale=0.7]{figures/GK_experiment.png}
 \end{figure}
-    \hyperlink{Other Figures}{\beamerbutton{Other Figures}}
 
@@
     \bigskip
-    Some agents do update their belief of $\theta$ in the right direction.\\
+    They argue that some agents do update their belief in the ability parameter.\\
+    \bigskip
+    How are people updating their beliefs on two parameters?
 \end{frame}
 
-\begin{frame}{Theory 2: Switchers}
+\begin{frame}{The Research Question}
+    We know people fall somewhere between Bayesian Learning and the very extreme Heidhues et al. setting.\\
+    \bigskip
+    \begin{itemize}
+        \item Do the existing alternative theories explain the behavior well?\\
+        \begin{itemize}
+            \item Is there heterogeneity in how people update their beliefs? (Bayesian, self-attribution, hypothesis testing, self-defeating)
+        \end{itemize}
+    \bigskip
+        \item Can we design an intervention that will help people learn their true type?\\
+    \end{itemize}
+\end{frame}
+
+\begin{frame}{Theory 2}
     \Large\textbf{ Robust Misspecified Models and Paradigm Shifts \\}
@@
 \begin{frame}{The Setting}
-    Same as HKS but with finite $\Omega$ and finite $A$\\
+    Same as Theory 1\\
     \bigskip
-    Now the entrepreneur is willing to switch to an alternative level of ability $\theta'$ (assume $\theta' = \theta^*$).\\
+    Now the entrepreneur entertains an alternative level of ability $\theta'$ (assume $\theta' = \theta^*$).\\
     \bigskip
@@
     \bigskip
-    Overconfident agents can escape the trap if their prior is not too ``tight'' around a self confirming equilibrium.
+    Overconfident agents can escape the trap if their prior is not too "tight" around a self confirming equilibrium.
 
@@
 \begin{frame}{The Setting}
-    A fixed effort $e$, $\theta \in \{\theta_H, \theta_L\}$ and $\omega \in \{\omega_H, \omega_L\}$ generate binary signals (success/failure)\\
+    Assume $e$ is fixed and $\theta \in \{\underline{\theta}, \Bar{\theta}\}$ \\
     \bigskip
-    After a success the agent updates their belief about $\theta$ with distortions $\gamma_\theta$ and $\gamma_\omega$, $p_{t+1}(\theta_H|success)$ is given by:\\
-    \begin{center}
-        \small
-        $\frac{\gamma^s_\theta\gamma^s_\omega\pi_t(\theta_H) g_t(\omega_H) q_t(\theta_H, \omega_H) + \gamma^s_\theta\pi_t(\theta_H) g_t(\omega_L) q_t(\theta_H, \omega_L)}{\gamma^s_\theta\gamma^s_\omega\pi_t(\theta_H) g_t(\omega_H) q_t(\theta_H, \omega_H) + \gamma^s_\theta\pi_t(\theta_H) g_t(\omega_L) q_t(\theta_H, \omega_L) + \gamma^s_\omega\pi_t(\theta_L) g_t(\omega_H) q_t(\theta_L, \omega_H) + \pi_t(\theta_L) g_t(\omega_L) q_t(\theta_L, \omega_L)}$\\
-    \end{center}
-    \bigskip
-    with $q_t(\theta, \omega):=Pr[\text{success}|\theta, \omega]$ increasing in $\omega$ and $\theta$
+    Let the probability of success be increasing in $\theta$ and $\omega$ and denote it by by
+    $$q(\theta, \omega):=Pr[success|\theta, \omega]$$
+    After a success the agent updates their belief about $\theta$ with distortion $\gamma_\theta$:
+    $$p_{t+1}(\Bar{\theta}|success)= \frac{\gamma_\theta\pi_t(\Bar{\theta})\sum_\omega g_t(\omega) q_t(\Bar\theta, \omega)}{\gamma_\theta\pi_t(\Bar{\theta})\sum_\omega g_t(\omega)q_t(\Bar{\theta}, \omega)+ \pi_t(\underline {\theta})\sum_\omega g_t(\omega) q_t(\underline{\theta}, \omega)}$$
+
 \end{frame}
@@
 \begin{frame}{Predictions and Evidence (Coutts et al. 2022)}
-    Prediction: Even unbiased agents will overweight $\theta_H$ after a success and end up being biased.\\
+    Prediction: Even unbiased agents will overweight $\theta
+_H$ after a success and end up being biased.\\
     \bigskip
@@
     \bigskip
-    It gives an alternative rationalization for the persistence of overconfidence.
+    It rationalizes the formation of overconfident beliefs.
 
@@
 \begin{frame}{A framework where we can compare}
-
-Finite type space: $\theta \in \{\theta_H, \theta_M, \theta_L\}$\\
+    Theories 1 and 2 draw conclusions within the same setting already.\\
     \bigskip
-Finite state space: $\omega \in \{\omega_H, \omega_M, \omega_L\}$
-with $p(\omega_k)=1/3$ \\
-\bigskip
-Finite action space: $e \in \{e_H, e_M, e_L\}$\\
-\bigskip
-Binary signal: Success/Failure with $P\left[Success|e, \omega, \theta\right]$ satisfying the assumptions of HKS
-
+    Can we bring the self-serving attribution bias into that setting?\\
+    \begin{enumerate}
+        \item A larger $\alpha$ in Theory 2 is consistent with self-serving beliefs when the update is done by evaluating the likelihood ratio.
+        \item We can write out the fully Bayesian update within the setting and introduce the bias as in Theory 3.
+        \item If some subject starts out with the correct belief $\theta$ and ends up being overconfident, it is evidence of a self-serving bias.
+    \end{enumerate}
 \end{frame}
 
-\begin{frame}{The Data Generating Process}
-The probability of success is given by:\\
+\begin{frame}{A Theory-Inspired intervention}
+    The parameters in this setting are identified. Allowing for a trade-off between exploitation and experimentation is sufficient for learning. \\
     \bigskip
-\centering
-\begin{tabular}{ c|c|c|c|}
-
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
-  \cline{2-4}
-  $e_H$ & 50 & 20 & 2 \\
-  \cline{2-4}
-  $e_M$ & 45 & 30 & 7 \\
-  \cline{2-4}
-  $e_L$ & 40 & 25 & 20 \\
-  \cline{2-4}
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_L$} & \multicolumn{1}{c}{}\\
-\end{tabular}
-\hspace{.3cm} % adjust this value to set the space between tables
-\begin{tabular}{ c|c|c|c|}
-
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
-  \cline{2-4}
-  $e_H$ & 80 & 50 & 5 \\
-  \cline{2-4}
-  $e_M$ & 69 & 65 & 30 \\
-  \cline{2-4}
-  $e_L$ & 65 & 45 & 40 \\
-  \cline{2-4}
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_M$} & \multicolumn{1}{c}{}\\
-\end{tabular}
-\hspace{.3cm} % adjust this value to set the space between tables
-\begin{tabular}{ c|c|c|c|}
-
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
-  \cline{2-4}
-  $e_H$ & 98 & 65 & 25 \\
-  \cline{2-4}
-  $e_M$ & 80 & 69 & 35 \\
-  \cline{2-4}
-  $e_L$ & 75 & 55 & 45 \\
-  \cline{2-4}
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_H$} & \multicolumn{1}{c}{}\\
-\end{tabular}
-
+    There are two ways in which experimentation can lead to correct learning:\\
+    \begin{enumerate}
+        \item Experimentation on $e$:
+        \begin{itemize}
+            \item Götte and Kozakiewicz show that some agents do learn (are they experimenting?)
+            \item Would overconfident/underconfident subjects choose to experiment if the option is made explicitly available to them?
+        \end{itemize}
+        \bigskip
+        \item Allowing experimentation over $\omega$ (switching environments): 
+        \begin{itemize}
+            \item Hesterman and Le Yaouanq (2021) show that in a model with fixed $e$ and the possibility to experiment in different environments, overconfident subjects learn $\theta$ faster than unbiased/underconfident subjects
+        \end{itemize}
+    \end{enumerate}
 \end{frame}
 
-\begin{frame}{The Data Generating Process}
-    \centering
-\begin{tabular}{ c|c|c|c|}
+\begin{frame}{Testing in the lab}
 
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
-  \cline{2-4}
-  $e_H$ & \cellcolor{blue!25}50 & 20 & 2 \\
-  \cline{2-4}
-  $e_M$ & 45 & \cellcolor{blue!25}30 & 7 \\
-  \cline{2-4}
-  $e_L$ & 40 & 25 & \cellcolor{blue!25}20 \\
-  \cline{2-4}
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_L$} & \multicolumn{1}{c}{}\\
-\end{tabular}
-\hspace{.3cm} % adjust this value to set the space between tables
-\begin{tabular}{ c|c|c|c|}
-
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
-  \cline{2-4}
-  $e_H$ & \cellcolor{blue!25}80 & 50 & 5 \\
-  \cline{2-4}
-  $e_M$ & 69 & \cellcolor{blue!25}65 & 30 \\
-  \cline{2-4}
-  $e_L$ & 65 & 45 & \cellcolor{blue!25}40 \\
-  \cline{2-4}
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_M$} & \multicolumn{1}{c}{}\\
-\end{tabular}
-\hspace{.3cm} % adjust this value to set the space between tables
-\begin{tabular}{ c|c|c|c|}
-
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
-  \cline{2-4}
-  $e_H$ & \cellcolor{blue!25}98 & 65 & 25 \\
-  \cline{2-4}
-  $e_M$ & 80 & \cellcolor{blue!25}69 & 35 \\
-  \cline{2-4}
-  $e_L$ & 75 & 55 & \cellcolor{blue!25}45 \\
-  \cline{2-4}
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_H$} & \multicolumn{1}{c}{}\\
-\end{tabular}
-\end{frame}
-
-\begin{frame}{The Data Generating Process}
-\begin{center}
-\begin{tikzpicture}
-  \draw[<-] (1,0) -- (3,0);
-  \draw[<-] (5,0) -- (7,0);
-  \draw[<-] (9,0) -- (11,0);
-\end{tikzpicture}
-\end{center}
-\\
-\bigskip
-\centering
-\begin{tabular}{ c|c|c|c|}
-
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
-  \cline{2-4}
-  $e_H$ & \cellcolor{blue!25}50 & 20 & 2 \\
-  \cline{2-4}
-  $e_M$ & 45 & \cellcolor{blue!25}30 & 7 \\
-  \cline{2-4}
-  $e_L$ & 40 & 25 & \cellcolor{blue!25}20 \\
-  \cline{2-4}
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_L$} & \multicolumn{1}{c}{}\\
-\end{tabular}
-\hspace{.3cm} % adjust this value to set the space between tables
-\begin{tabular}{ c|c|c|c|}
-
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
-  \cline{2-4}
-  $e_H$ & \cellcolor{blue!25}80 & 50 & 5 \\
-  \cline{2-4}
-  $e_M$ & 69 & \cellcolor{blue!25}65 & 30 \\
-  \cline{2-4}
-  $e_L$ & 65 & 45 & \cellcolor{blue!25}40 \\
-  \cline{2-4}
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_M$} & \multicolumn{1}{c}{}\\
-\end{tabular}
-\hspace{.3cm} % adjust this value to set the space between tables
-\begin{tabular}{ c|c|c|c|}
-
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
-  \cline{2-4}
-  $e_H$ & \cellcolor{blue!25}98 & 65 & 25 \\
-  \cline{2-4}
-  $e_M$ & 80 & \cellcolor{blue!25}69 & 35 \\
-  \cline{2-4}
-  $e_L$ & 75 & 55 & \cellcolor{blue!25}45 \\
-  \cline{2-4}
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_H$} & \multicolumn{1}{c}{}\\
-\end{tabular}
-
-\begin{center}
-    \resizebox{0.6\linewidth}{!}{\vector(1,0){300}}
-  \end{center}
-
-\end{frame}
-
-\begin{frame}{A Self-Confirming Equilibrium}
-
-\centering
-\begin{tabular}{ c|c|c|c|}
-
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
-  \cline{2-4}
-  $e_H$ & \cellcolor[HTML]{b84f79}50 & 20 & 2 \\
-  \cline{2-4}
-  $e_M$ & 45 & 30 & 7 \\
-  \cline{2-4}
-  $e_L$ & 40 & 25 & 20 \\
-  \cline{2-4}
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_L$} & \multicolumn{1}{c}{}\\
-\end{tabular}
-\hspace{.3cm} % adjust this value to set the space between tables
-\begin{tabular}{ c|c|c|c|}
-
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
-  \cline{2-4}
-  $e_H$ & 80 & \cellcolor[HTML]{b84f79}50 & 5 \\
-  \cline{2-4}
-  $e_M$ & 69 &\cellcolor[HTML]{f09ebe}65 & 30 \\
-  \cline{2-4}
-  $e_L$ & 65 & \cellcolor[HTML]{f09ebe}45 & 40 \\
-  \cline{2-4}
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_M$} & \multicolumn{1}{c}{}\\
-\end{tabular}
-\hspace{.3cm} % adjust this value to set the space between tables
-\begin{tabular}{ c|c|c|c|}
-
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
-  \cline{2-4}
-  $e_H$ & 98 & 65 & 25 \\
-  \cline{2-4}
-  $e_M$ & 80 & 69 & 35 \\
-  \cline{2-4}
-  $e_L$ & 75 & 55 & 45 \\
-  \cline{2-4}
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_H$} & \multicolumn{1}{c}{}\\
-\end{tabular}
-\end{frame}
-
-\begin{frame}{The Self-Confirming Equilibria}
-
-\centering
-\begin{tabular}{ c|c|c|c|}
-
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
-  \cline{2-4}
-  $e_H$ & \cellcolor[HTML]{b84f79}50 & 20 & 2 \\
-  \cline{2-4}
-  $e_M$ & 45 & \cellcolor[HTML]{5f94b8}30 & 7 \\
-  \cline{2-4}
-  $e_L$ & \cellcolor[HTML]{69a35b}40 & 25 & 20 \\
-  \cline{2-4}
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_L$} & \multicolumn{1}{c}{}\\
-\end{tabular}
-\hspace{.3cm} % adjust this value to set the space between tables
-\begin{tabular}{ c|c|c|c|}
-
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
-  \cline{2-4}
-  $e_H$ & 80 & \cellcolor[HTML]{b84f79}50 & 5 \\
-  \cline{2-4}
-  $e_M$ & \cellcolor[HTML]{fab143}69 & 65 & \cellcolor[HTML]{5f94b8}30 \\
-  \cline{2-4}
-  $e_L$ & 65 & \cellcolor[HTML]{9662f0}45 & \cellcolor[HTML]{69a35b}40 \\
-  \cline{2-4}
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_M$} & \multicolumn{1}{c}{}\\
-\end{tabular}
-\hspace{.3cm} % adjust this value to set the space between tables
-\begin{tabular}{ c|c|c|c|}
-
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
-  \cline{2-4}
-  $e_H$ & 98 & 65 & 25 \\
-  \cline{2-4}
-  $e_M$ & 80 & \cellcolor[HTML]{fab143}69 & 35 \\
-  \cline{2-4}
-  $e_L$ & 75 & 55 & \cellcolor[HTML]{9662f0}45 \\
-  \cline{2-4}
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_H$} & \multicolumn{1}{c}{}\\
-\end{tabular}
-\end{frame}
-
-\begin{frame}{An Example}
+Part 1: Test\\
 \begin{itemize}
-    \item True type is $\theta_M$ \\
-    \bigskip
-    \item True exchange rate is $\omega_M$ $\rightarrow$ The entrepreneur believes it is uniformly distributed\\
+    \item Get the ego-relevant parameter
+    \item Elicit beliefs
 \end{itemize}
-
-    \centering
-\begin{tabular}{ c|c|c|c|}
-
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
-  \cline{2-4}
-  $e_H$ & 50 & 20 & 2 \\
-  \cline{2-4}
-  $e_M$ & 45 & 30 & 7 \\
-  \cline{2-4}
-  $e_L$ & 40 & 25 & 20 \\
-  \cline{2-4}
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_L$} & \multicolumn{1}{c}{}\\
-\end{tabular}
-\hspace{.3cm} % adjust this value to set the space between tables
-\begin{tabular}{ c|c|c|c|}
-
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
-  \cline{2-4}
-  $e_H$ & 80 & \cellcolor{blue!25}50 & 5 \\
-  \cline{2-4}
-  $e_M$ & 69 & \cellcolor{blue!25}65 & 30 \\
-  \cline{2-4}
-  $e_L$ & 65 & \cellcolor{blue!25}45 & 40 \\
-  \cline{2-4}
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_M$} & \multicolumn{1}{c}{}\\
-\end{tabular}
-\hspace{.3cm} % adjust this value to set the space between tables
-\begin{tabular}{ c|c|c|c|}
-
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
-  \cline{2-4}
-  $e_H$ & 98 & 65 & 25 \\
-  \cline{2-4}
-  $e_M$ & 80 & 69 & 35 \\
-  \cline{2-4}
-  $e_L$ & 75 & 55 & 45 \\
-  \cline{2-4}
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_H$} & \multicolumn{1}{c}{}\\
-\end{tabular}
-
-\end{frame}
-
-\begin{frame}{Example: Dogmatic Modeler}
+\pause
+Part 2: Investment game (N rounds)\\
 \begin{itemize}
-    \item Theory 1: for an entrepreneur who believes he is $\theta_H$
+    \item Treatment is paid according to their own score as $\theta$ 
+    \item Control is paid according to an ego-neutral parameter 
 \end{itemize}
-    \bigskip
 \begin{enumerate}
-        \item Chooses $e_H$ and is disappointed $\rightarrow$ adjust belief about $\omega$ downward\\
-        \bigskip
-        \item Eventually chooses $e_M$ and is disappointed as well $\rightarrow$ adjust belief about $\omega$\\
-        \bigskip
-        \item Eventually chooses $e_L$ and falls into a self-confirming equilibrium
+    \item Choose an amount e to invest
+    \item Returns are $\theta \omega + e(\omega-\frac{1}{2}e) + \varepsilon_t$
+    \item Belief elicitation
 \end{enumerate}
-
-\end{frame}
-
-\begin{frame}{Dogmatic Overconfident}
-    \begin{figure}
-        \centering
-        \includegraphics[trim=0 20 0 0, clip]{figures/dogmatic.png}
-        \caption{$\theta^*=\theta_M$, $\hat\theta=\theta_H$, $\omega^*=\omega_M$}
-    \end{figure}
-\end{frame}
-
-\begin{frame}{Example: Likelihood Testing}
+\pause
+Part 3: Explicitly allow experimentation
 \begin{itemize}
-    \item Theory 2: for the same initial belief
-    \item Keeping track of the likelihood of each $\theta$
-    \end{itemize}
-    \bigskip
-    \begin{enumerate}
-        \item Chooses $e_H$ and is disappointed $\rightarrow$ adjust belief about $\omega$ downward\\
-        \bigskip
-        \item Eventually chooses $e_M$ and is disappointed as well $\rightarrow$ adjust belief about $\omega$\\
-        \bigskip
-        \item Eventually chooses $e_L$ and falls into a self-confirming equilibrium\\
-        \bigskip
-        \item At some point, the likelihood of $\theta_M$ becomes much larger than that of $\theta_H$ and the agent updates their belief
-    \end{enumerate}
-
-\end{frame}
-
-\begin{frame}{Switcher Overconfident}
-    \begin{figure}
-        \centering
-        \includegraphics{figures/switch.png}
-        \caption{$\theta^*=\theta_M$, $\hat\theta=\theta_H$, $\omega^*=\omega_M$, $\alpha= 1.1$}
-    \end{figure}
-\end{frame}
-
-\begin{frame}{Example: Self-Serving Beliefs}
-\begin{itemize}
-    \item Theory 3: Start with a diffused prior over $\theta$
-    \end{itemize}
-    \bigskip
-    \begin{enumerate}
-        \item Chooses $e$ that maximizes utility according to priors
-        \bigskip
-        \item Success $\rightarrow$ overweight $\theta_H$ and underweight $\omega_H$\\
-        \item Failure $\rightarrow$ overweight $\omega_L$ underweight $\theta_L$\\
-        \bigskip
-        \item Belief on $\omega$ deteriorates a lot after failure streaks
-        \item Belief on $\theta$ increases a lot after success streaks\\
-    \end{enumerate}
-
-\end{frame}
-
-\begin{frame}{Dogmatic Overconfident}
-    \begin{figure}
-        \centering
-        \includegraphics{figures/SS.png}
-        \caption{$\gamma^s_\theta=1.2$, $\gamma^s_\omega = .8$}
-    \end{figure}
-\end{frame}
-
-\begin{frame}{The Simulation}
-\label{Figure2}
-    \begin{figure}
-    \centering
-    \includegraphics[scale=0.43]{figures/all_1_1.png}
-\end{figure}
-
-\hyperlink{WorstCase}{\beamerreturnbutton{Other Cases}}
-
-\end{frame}
-
-\begin{frame}{The Experiment:}
-Brief Questionnaire: Age, Gender, Nationality, Major\\
-\bigskip
-Part 1: Set Types\\
-\bigskip
-\begin{itemize}
-    \item Quiz: Answer as many questions as you can in 2 minutes:\\
-    \begin{itemize}
-        \item Math, Verbal, Pop-Culture, Science, Us Geography, Sports and Videogames\\
-    \end{itemize}
-    \bigskip
-    \item How many questions do you think you answered correctly in each quiz?\\
-    \begin{itemize}
-        \item[o] Bin1, Bin2, Bin3
-    \end{itemize}
+    \item Draw a random $e$ for the next $n$ rounds
+    \item Draw a new return parameter $\omega$
 \end{itemize}
@@
 
-\begin{frame}{The Experiment: Ego-relevant condition}
-Belief updating and effort choice (One topic at a time)\\
+\begin{frame}{What needs to be done}
+    \begin{enumerate}
+        \item Define self-serving attribution bias in the framework of theories 1 and 2 (??)\\
         \bigskip
+        \item Get predictions in a simplified environment (finite parameter sets).
+        \bigskip
+        \item Parameters should be such that there are differences among models:
         \begin{itemize}
-    \item Choose an effort
-    \item Receive a signal realization
+            \item Subjects update in Theory 2 but fall into self-defeating eq. in Theory 1
+            \item Self-serving beliefs make the default model more sticky in Theory 2 
+            \item Self serving bias over weights high $\theta$ relative to the Bayesian
+            \item Under self serving bias, unbiased subjects become biased. And overconfident subjects become more confident after a success
         \end{itemize}
-\bigskip
-25 rounds per topic
-
-\end{frame}
-
-\begin{frame}{Eliciting Beliefs?}
-\begin{itemize}
-    \item $E[\omega]$ is revealed by their choice of effort\\
-    \bigskip
-    \item Eliciting beliefs for $\theta$ can incentivize learning in a way that is not consistent with the model\\
-    \bigskip
-\end{itemize}
-
-Allow them to see the success rate matrix for only one type. 
-\begin{itemize}
-    \item Track the matrices they choose to see in each round
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}{The Experiment: Ego-irrelevant condition}
-
-Observe the characteristics of a participant. 
-\begin{itemize}
-    \item ``What score do you think this participant got in the (topic) quiz?'' 
-    \item Bin1, Bin2, Bin3 
-\end{itemize}
-
-Belief updating and effort choice\\
-\bigskip
-\begin{itemize}
-    \item Choose an effort
-    \item Receive a signal realization
-    \begin{itemize}
-        \item[o] The DGP is that of the observed participant
-    \end{itemize}
-\end{itemize}
-\bigskip
-25 rounds (per topic/participant)
-
-\end{frame}
-
-\begin{frame}{Conclusion}
-What I hope to get from this design:\\
-\bigskip
-    \begin{itemize}
-        \item A classification of subjects into one of the models based on their behavior\\
-        \bigskip
-        \item If subjects are switchers: what is the switching threshold $\alpha$\\
-        \bigskip
-        \item Insight into the role of ego-relevant parameters in belief misspecification
-    \end{itemize}
+    \end{enumerate}
 \end{frame}

### 2023-10-01 Paper/draft.Rmd
New bias model

@@
 
-A self-serving bayesian is an agent who uses a biased version of Bayes rule to update his beliefs.He will update his beliefs 
-about the state $\omega$ and his type $\theta$
+A self-serving bayesian is an agent who uses a biased version of Bayes rule to update their beliefs. 
+They will update their beliefs 
+about the state $\omega$ and his type $\theta$ simultaneously
 by over-attributing successes to a high value of $\theta$ and under-estimating the role of higher $\omega$. Similarly,
 he will attribute failure to a low state to a greter degree than an unbiased agent would. 
-To model the self-serving attribution bias, I take the approach of @benjamin2019, where the posterior is given by:
+To model the self-serving attribution bias, I take the approach of @benjamin2019, where the posterior odds are given by:
 
 $$
-p_{t}[\theta_H|\text{outcome}] = 
-\frac{p[\text{outcome}|\theta]^{c_s^{\theta}\mathbb{I}\{\text{success}\}+c_f^{\theta}\mathbb{I}\{\text{failure}\}}p_{t-1}[\theta]}
-{\sum_{\theta'\in\Theta}p[\text{outcome}|\theta']^{c_s^{\theta}\mathbb{I}\{\text{success}\}+c_f^{\theta}\mathbb{I}\{\text{failure}\}}p_{t-1}[\theta']}
+p_{t+1}[\theta, \omega|s_t] =\left(
+\frac{p_t[s_t|\theta, \omega]}
+{p_t[s_t|\theta', \omega']}\right)^{c(\theta, \omega, s_t)}
 $$
 
-$c_s^{\theta}$ and $c_f^{\theta}$ are the self-serving attribution bias parameters for the agent's type $\theta$. 
-If $c_s^{\theta} = c_f^{\theta} = 1$, the agent is unbiased and the update is the same as the Bayesian update. On the other hand, 
-if $c_s^{\theta} > c_f{\theta}$ the agent over-attributes success to their type and under-attributes failure to their type\footnote{
-  notice that the values of $c_s^{\theta}$ and $c_f^{\theta}$ are not restricted to be greater than 1. If they are both equal to 
-  each other but less (more) than one, then the bias is simply underinference (overinference).}.
+Whith $c(\theta, \omega, s_t)$ such that   
+c(\theta, \omega, \s_t) > c(\theta', \omega').
 
-The update for $\omega$ is analogous but with $c_f^{\omega}$ and $c_s^{\omega}$ instead of $c_f^{\theta}$ and $c_s^{\theta}$ and
-the bias is present whenever $c_f^{\omega} > c_s^{\omega}$. That is, the agent over-attributes failure to a low state relative the 
-higher states and under-attributes success to a low state relative to the higher states.
-
-# A Unifying Example
+# A Unifying Framework
 The agent can be of one of 3 types: $\theta \in \{\theta_L, \theta_M, \theta_H\}$  with $\theta_H > \theta_M > \theta_L$.

### 2023-10-06 Paper/draft.Rmd
learners and not learners

@@
 
-# Related Literature
+## Related literature
 
-# Framework 1
+# Theoretical Framework
+
+I consider multiple theories of belief updating that have been proposed in the literature and that are able to rationalize
+the prevalence of misspecified beliefs. I focus on two different frameworks and develop a unifying example that allows me to
+compare the predictions of all the theories. In this section, I outline the theories within each of the frameworks.
+
+## Framework 1
 
@@
 density $f$ over $\Omega$. The agent knows the 
-distribution of $\omega$ but not its realized value. His prior belief about his type is $p_0(\theta)$ and his belief about the state
-state $p_0(\omega)$ coincides with the true distribution $f$. Let the agent's type be $\theta^*$ and the realized state be $\omega^*$.
+distribution of $\omega$ but not its realized value. His prior belief about his type is $p_0(\theta)$ and his belief about the state, 
+$p_0(\omega)$, coincides with the true distribution. Let the agent's true type be $\theta^{*}$,  and the realized state be $\omega^{*}$.
 
@@
 \emph{dogmatic} if he holds a degenerate belief that places probability one on being a particular type, $\hat{\theta}$. An 
-agent can be dogmatic and misspecified; that means that $\hat{\theta} \neq \theta^*$ and $p_0(\hat{\theta}) = 1$.
+agent can be dogmatic and misspecified. If the agent is both, $\hat{\theta} \neq \theta^*$ and $p_0(\hat{\theta}) = 1$.
 
@@
 He repeats this process infinitely many times. I make the simplifying assumption that the agent is myopic and chooses the action 
-that maximizes the payoff in each period. This assumption is symplifies the analysis and plays a role on whether an agent who updates
- their beliefs using bayes rule would learn the truth or not.
+that maximizes the payoff in each period. This assumption simplifies the analysis and plays a role in whether an agent who updates
+ their beliefs using Bayes rule would learn the truth or not. The behavior of a forward-looking agent is discussed in the conclusion.
 
@@
 A \emph{self-defeating equilibrium} is a belief and action pair such that the agent's belief about their type is misspecified and the 
-outcome generated by the action is consistent with the misspecified belief. The average outcome under the true type and the true 
-state equals the average output the agent expects under the misspecified belief. In addition, the agent's belief is said to be 
+outcome generated by the action is consistent with the misspecified belief. This means that the average outcome under the true type and the true 
+state equals the average output the agent expects under the misspecified belief. The agent's belief is said to be 
 \emph{stable} when this happens.
 
-Within this framework, I consider two nested theories of belief updating. The first one is a dogmatic modeler from @Heidhues2018.
+Within this framework, I consider two nested theories of belief updating: the first one is a dogmatic modeler from @Heidhues2018,
 The second one is a switcher, as in @Ba2023. The dogmatic modeler can be seen as a switcher with an infinitely sticky initial belief
-and this is the sense in which the two are nested. Both theories produce different predictions with respect to the equilibrium outcome.
+and this is the sense in which the two are nested. Both theories produce different predictions about the agent's behavior. I discuss both 
+in what follows.
 
-## The Dogmatic Modeler
+### The Dogmatic Modeler
 
-A dogmatic agent does not update their beliefs about $\theta$; instead he holds a degenerate belief that places probability one 
-on being a particular type, $\hat{\theta}$, which is potentially not his true type. 
+A dogmatic agent does not update their beliefs about $\theta$, instead, he holds a degenerate belief that places probability on 
+$\hat{\theta}$, which is potentially misspecified. 
 In this case, no matter
-how much information he gathers against being of type $\hat{\theta}$, he will not update his beliefs. Any discrepancies between the 
+how much information he gathers against being of type $\hat{\theta}$, he will not update his beliefs about $\theta$. 
+Any discrepancies between the 
 observed outcomes and his believed type are incorporated using the Bayes rule to update their beliefs about $\omega$.
-This means the dogmatic agent will never learn their true type if they startu off as being misspecified.
-
 @Heidhues2018 show that, under certain assumptions on the per-period utility,\footnote{The assumptions are that 
@@
 a dogmatic modeler will inevitably fall into a self-defeating equilibrium. The equilibrium will be such that
-the outcomes they observe reinforce their belief on $\omega$ in such a way that as $t\to\infty$ the agent will be sure that
+the outcomes they observe reinforce their belief on $\omega$ in such a way that as $t\to\infty$ the agent will 
+be sure that
 the state is some $\omega^{'}$ consistent with their believed type and the observed data. In other words, 
-they will be in a self-defeating equilibrium whith a stable belief that places probability one on the incorrect
+they will be in a self-defeating equilibrium with a stable belief that places probability one on the incorrect
 parameters $(\hat{\theta}, \omega_{\infty})$
@@
 he will not update his beliefs about $\theta$ and as a consequence will attribute the disappointment to the state being lower than expected.
-He will continue to update in ths way until he converges to a belief about $\omega$ that is stable. Such a belief will 
+He will continue to update in this way until he converges to a belief about $\omega$ that is stable. Such a belief will 
 explain the observed utility perfectly and allow the agent to rationalize his dogmatic belief about $\theta$. 
@@
 $(\theta^*+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}$ but he was expecting an average utility of 
-$(\hat{\theta}\theta+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}$. In response, he will apply bayes rule to update his beliefs about
+$(\hat{\theta}\theta+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}$. In response, he will apply Bayes rule to update his beliefs about
 $\omega$ to get the posterior belief with $\mathbb{E}_{t+k}[\omega] = \frac{(\theta^{*} + \omega^{*})\omega^{*}}{\hat{\theta} + \omega^{*}}$
 which is lower than the initial belief. This will cause the agent to choose a lower effort at $t+k$. As a result, he will again
-receive an average utlitity that is lower than what he expected which will cause his belief to drift further down. This process will
+receive an average utility that is lower than what he expected which will cause his belief to drift further down. This process will
 continue until the average utility equals his expected utility under the dogmatic belief that assigns probability 1 to $\hat{\theta}$. 
-At that point, the stundent will have reached a self-defeating equilibrium and he will continue to choose sub-optimal effort forever. _
+At that point, the student will have reached a self-defeating equilibrium and he will continue to choose sub-optimal effort forever. _
 
-Although the model of a dogmatic modeler is able to rationalize the prevalence of overconfident (underconfident) beliefs, the
+Although the model of a dogmatic modeler rationalizes the prevalence of overconfident (underconfident) beliefs, the
 assumption that the agent has a degenerate belief and no mechanism through which he can update such belief is very restrictive. An
 alternative approach is proposed by @Ba2023. She proposes an extension of the dogmatic agent who is able to jump from one dogmatic 
-belief to another. By doing so, the agent might end up being dogmatic and correctly speciefied.
+belief to another. By doing so, the agent might end up being dogmatic and correctly specified.
 
-## The Switcher
+### The Switcher
 
@@
 In particular, when they start off as a misspecified dogmatic, they are willing to switch to a different dogmatic belief if the data is
-convincing enough. Notice that their beliefs are still degenerate and assign probability one to a particular type, and zero to 
-all other types. This means that a bayesian update on $\theta$ would cause no change in their beliefs.
+convincing enough. Their prior is still degenerate and assigns probability one to a particular type, and zero to 
+all other types. This means that a Bayesian update on $\theta$ does not change their beliefs about the type.
 However, they are willing to entertain two such beliefs and have a mechanism by which they decide which belief to adopt at any period $t$.
 
-In order to abandon their initial dogmatic belief, the agent needs to observe a sequence of outcomes that are sufficiently unlikely
-to have happened if they were of the type they initially believed. They do so by keeping track of the likelihood that each of the
+In order to abandon their initial dogmatic belief, the agent needs to observe a sequence of outcomes 
+that are sufficiently unlikely
+to have happened if they were of the type they initially believed. In order to evaluate if the evidence is convincing enough, 
+they keep track of the likelihood that each of the
 possible types generated the data. If the likelihood ratio is sufficiently large, the agent will switch to the alternative
@@
 
-In particular, for an agent that starts off with a dogmatic belief that they are of type $\hat{\theta}$ but is willing to consider
+In particular, for an agent that starts with a dogmatic belief that they are of type $\hat{\theta}$ but is willing to consider
 the alternative explanation that they are of type $\tilde{\theta}$, the agent will switch to the alternative if:
@@
 likelihood ratio, the agent can perform a \emph{Bayesian hypothesis test} and adopt the Dogmatic belief that best fits 
-the data.\footnote{In a related problem @Schwarstein2021 proposes a similar updating procedure wich relies on the Bayesian 
-hypothesis test.}
+the data.\footnote{In a related problem @Schwarstein2021 proposes a similar updating procedure which relies on the Bayesian 
+hypothesis test. However, in their model there is a sender who optimally chooses to propose a model that fits the data}
 Notice that if $\alpha \to \infty$, the behavior of the switcher will be indistinguishable from that of the Dogmatic modeler. 
@@
 This happens because under the agent's prior, the likelihood ratio is unlikely to grow as fast as it is needed to escape 
-the self-defeating equilibrium. In this cases we say that the misspecified belief is persistent. Hence, in order to be able 
-to determine which of these two models provides a better explanation of the observed behaviors, we must focus on cases 
-in which the prior is diffused enough and the sequence of realized outcomes is such that
-the self-defeating equilibrium would not persist.
+the self-defeating equilibrium. In such situations, we say that the misspecified belief is persistent.
 
-# Framework 2
+## Framework 2
 
-The agent is still of some type $\theta^* \in \Theta$ and the state is $\omega \sim F$. In this case the agent chooses an action 
+As in framework 1, the agent is of some type $\theta^* \in \Theta$ and the state is $\omega \sim F$. 
+In this case, the agent chooses an action 
 $a\in A$
 and observes a binary outcome that is either a success or a failure. Denote the outcome by $o \in {s,f}$. The probability of 
-observing a success is ingreasing in $\theta^*$ and in $\omega$. Whenever the agent observes a succes, he gets a payoff $v>0$ and
-whenever the outcome is a failure, normalize the payoff to 0.  In addition, the probability of success is such that for each state, 
+observing a success is increasing in $\theta^*$ and in $\omega$. Whenever the agent observes a success, he gets a payoff $v>0$ and
+whenever the outcome is a failure, the payoff is 0.  In addition, the probability of success is such that for each state, 
 there is a unique optimal action that maximizes the agent's expected payoff.
 
-Two nested theories that have been widely studied fall within this framework: Fully Bayesian updating and self-serving attribution 
+I focus on two nested theories that have been widely studied within this framework: Full Bayesian updating and self-serving attribution 
 bias. I explain each of these classical models of belief updating in what follows
 
-## The Bayesian
+### The Bayesian
 
@@
 
-## The Self-Serving Updater
+### The Self-Serving Updater
 
@@
 
-# A Unifying Framework
+# A Unifying Example
 The agent can be of one of 3 types: $\theta \in \{\theta_L, \theta_M, \theta_H\}$  with $\theta_H > \theta_M > \theta_L$.

### 2023-10-07 Paper/draft.Rmd
trap behavior

@@
 source("../Paper/parameters_and_packages.R")
+```
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 7, fig.height = 6, fig.align = "center")
+```
+
+```{r data, include=FALSE}
+updates <- fread("../Clean/updates_post.csv")
 ```
@@
 
-As in framework 1, the agent is of some type $\theta^* \in \Theta$ and the state is $\omega \sim F$. 
+As in framework 1, the agent is of some type $\theta^* \in \Theta$ and the state is $\omega \sim F(\Omega)$. 
 In this case, the agent chooses an action 
@@
 whenever the outcome is a failure, the payoff is 0.  In addition, the probability of success is such that for each state, 
-there is a unique optimal action that maximizes the agent's expected payoff.
+there is a unique optimal action that maximizes the agent's expected payoff. Therefore, the probability 
+of success can be seen as a monotone transformation of the utility from Framework 1.
 
@@
 A Bayesian agent simultaneously updates their beliefs about $\theta$ and $\omega$ by using Bayes' rule. 
-The posterior odds at period t about $\theta$ after observing an outcome are given by:
+The posterior at period t+1 about $\theta$ after observing a history of outcomes $h^t$ is given by:
 $$
-\frac{p_{t}[\theta_H|\text{outcome}]}{p_{t}[\theta_M|\text{outcome}]} = 
-      \frac{p[\text{outcome}|\theta_H]p_{t-1}[\theta_H]}{p[\text{outcome}|\theta_M]p_{t-1}[\theta_M]}
-$$
-and
-$$
-\frac{p_{t}[\theta_M|\text{outcome}]}{p_{t}[\theta_L|\text{outcome}]} = 
-      \frac{p[\text{outcome}|\theta_M]p_{t-1}[\theta_M]}{p[\text{outcome}|\theta_L]p_{t-1}[\theta_L]}
+p_{t+1}(\theta, \omega| h^t) = \frac{p[h^t|\theta, \omega]p_t(\theta, \omega)}{\sum_{(\theta', \omega')}p[h^t|\theta', \omega']p_t(\theta', \omega')}
 $$
 
-Where $p_{t-1}$ is the prior at period $t$ and 
-$p[\text{outcome}|\theta] = \sum_{\omega} p[\text{outcome}|\theta, \omega, e]p_{t-1}(\omega)$
-is the probability of observing the outcome given the agent's type and the effort chosen. The update is symmetric for $\omega$.
+Where $p_{t}$ is the belief at the start of period $t+1$. The update is symmetric for $\omega$.
 
-Bayesian agents always choose the effort level that maximizes their flow payoff by taking expectations over
+Bayesian agents choose the effort level that maximizes their expected flow payoff by taking expectations over
 their prior beliefs about $\theta$ and $\omega$. Since agents are myopic, even though all the parameters 
-could be identified with enough variation in choices, although the Bayesian agent is the closest to a fully rational agent discussed here, 
-they might not learn their true type. This happens because, by being myopic, they do not internalize the tradeoff between flow payoff
+could be identified with enough variation in choices. Although the Bayesian agent is the closest to a 
+fully rational agent discussed here, 
+they might not learn their true type. This happens because, by being myopic, they do not internalize 
+the tradeoff between flow payoff
 and learning. This can result in too little experimentation to learn their true type. An alternative to this approach is given 
-by @Hestermann2021 and is discussed with the results.
+by @Hestermann2021 and is discussed in the concluding remarks.
+
+Also notice that if a fully Bayesian agent has a dogmatic prior, they will never update their beliefs 
+about the parameter that they are dogmatic about. This will imply that they are prone to the same types 
+of errors as the dogmatic modeler in framework 1.
 
@@
 
-A self-serving bayesian is an agent who uses a biased version of Bayes rule to update their beliefs. 
+A self-serving Bayesian is an agent who uses a biased version of Bayes rule to update their beliefs. 
 They will update their beliefs 
@@
 by over-attributing successes to a high value of $\theta$ and under-estimating the role of higher $\omega$. Similarly,
-he will attribute failure to a low state to a greter degree than an unbiased agent would. 
+he will attribute failure to a low state to a greater degree than an unbiased agent would. 
 To model the self-serving attribution bias, I take the approach of @benjamin2019, where the posterior odds are given by:
@@
 $$
-p_{t+1}[\theta, \omega|s_t] =\left(
-\frac{p_t[s_t|\theta, \omega]}
-{p_t[s_t|\theta', \omega']}\right)^{c(\theta, \omega, s_t)}
+p_{t+1}(\theta, \omega| h^t) = \frac{p[h^t|\theta, \omega]^{c(\theta, \omega, o_t)}p_t(\theta, \omega)}{\sum_{(\theta', \omega')}p[h^t|\theta', \omega']^{c(\theta, \omega, o_t)}p_t(\theta', \omega')}
 $$
 
-Whith $c(\theta, \omega, s_t)$ such that   
-c(\theta, \omega, \s_t) > c(\theta', \omega').
+with $c(\theta_H, \omega, o)<c(\theta_M, \omega, o)<c(\theta_L, \omega, o)\leq 1$
+and $c(\theta, \omega_L, o)<c(\theta, \omega_M, o)<c(\theta, \omega_H, o)\leq 1$.
+
+This formulation of the bias means that the agent will over-attribute successes to a high type and 
+under-attribute them to a low type. Whereas they will over-attribute failures to a low state and
+under-attribute them to a high state. The parameter $c$ determines the degree of bias and the restriction on the 
+order ensures that the model is still falsifiable.
 
 # A Unifying Example
+
+In order to compare the predictions of the theories discussed above, I develop a unifying example that allows me to
+isolate the forces behind each of the theories. The example is a modification of the one in @Heidhues2018 and is adapeted to 
+be easier to implement in the lab.
+
 The agent can be of one of 3 types: $\theta \in \{\theta_L, \theta_M, \theta_H\}$  with $\theta_H > \theta_M > \theta_L$.
@@
 The probability of success is increasing in both $\theta$ and $\omega$ and is fully described by the following table:
+
+\begin{table}[htbp]
 
@@
 
+\caption{Probability of success for each type, gamble and effort level}
+\label{tab:table1}
+\end{table}
+
 Conditional on a type, the agent's flow payoff is maximized by choosing the gamble that 
@@
 By including self-confirming equilibria, the example captures the forces from each of the updating mechanisms discussed in the 
-previous section and allows for direct comparison of all the theories. For realizations of $(\theta, \omega)$ for which there are 
+previous section and allows for the comparison of the main forces behind the theories. For realizations of $(\theta, \omega)$ for which there are 
 self-confirming equilibria, the dogmatic agent will fall into the 
@@
 laboratory experiment. \footnote{because the setting does not match that of Heidhues et al. [2018], there will be situationf for which the theory 
-does not provie a prediction. If such cases arise in the lab, they will not be used for the analysis. However, whether a misspecified 
+does not provide a prediction. If such cases arise in the lab, they will not be used for the analysis. However, whether a misspecified 
 belief persists or not for the switcher, depends highly on the realized history of signals that he gets.} In what follows I explain 
@@
 
-I recruited XXX undergraduate subjects from the CESS lab at NYU who participated in an in-person experiment. Sessions lasted approximately 
-XXX hours and subjects earned an average payment of XXX. The experiment was programmed using oTree [@chen2016otree].
+I recruited `r print(unique(updates$code))` undergraduate subjects from the CESS lab at NYU who participated in an in-person experiment. 
+Sessions lasted approximately 
+45 minutes and subjects earned an average payment of $\$22.6$. The experiment was programmed using oTree [@chen2016otree].
 
 The experiment consisted of 2 treatments: the \emph{ego-relevant} condition and the \emph{stereotype} condition. Subjects participated 
-in only one of the treatments. Treatments were randomly assigned at the session level. The tasks were identical across treatments, 
+in only one of the treatments. All subjects within a session participated in the same treatment and the 
+first 4 treatments were assigned the ego-relevant condition; the rest were assigned to the stereotype treatment. 
+The tasks were identical across treatments, 
 except for parameter $\theta$. In the ego-relevant condition $\theta$ is the subject's own performance in a quiz, while in the 
@@
 
-After taking all 6 quizzes, they proceeded to part 2 where they were asked to guess their score on each of them. In the stereotype 
+After taking all 6 quizzes, they proceeded to part 2 where they were asked to guess their score on each of them. 
+In the stereotype 
 treatment they were additionally asked to guess the score of a randomly drawn participant from a previous session. 
 All they knew about the other participant was their gender identity and whether they were US nationals or not.
-For each guess they had three score options: Low-Score (5 or fewer correct answers), Mid-Score (between 6 and 15 correct answers), 
-High-Score (16 or more). Each of the score categories correspond to $\theta_L$, $\theta_M$, and $\theta_H$ respectively. 
+For each guess, they had three score options: Low-Score (5 or fewer correct answers), Mid-Score (between 6 and 15 correct answers), 
+High-Score (16 or more). Each of the score categories corresponded to $\theta_L$, $\theta_M$, and $\theta_H$ respectively. 
 They were also asked to say how confident they felt about their choices. They had 4 possible answers: "it was a random guess", 
@@
 .33, .50, .75, and 1 to the chosen type. The remaining probability is split equally among the other two types. 
-Questions in part 2
+Questions in Part 2
 were not incentivized, but subjects were told that providing an accurate answer would increase their chances of earning more money in 
@@
 
-The purpose of part 2 is to classify subjects into overconfident, underconfident and correctly specified. If a subject 
+The purpose of Part 2 is to classify subjects into overconfident, underconfident and correctly specified. If a subject 
 guesses their score to be in a higher (lower) category than their true score, they are overconfident (underconfident); if they 
@@
 
-Finally, in part 3 subjects completed a belief updating task for each of the quizzes. Before starting the task they were reminded of their guess
-for the score. In the ego treatment they were reminded of their guess about themselves and in the stereotype treatment they were reminded
+Finally, in Part 3, subjects completed a belief updating task for each of the quizzes. Before starting the task they were reminded of their guess
+for the score. In the ego-relevant treatment, they were reminded of their guess about themselves and in the stereotype treatment they were reminded
 of their guess about the other participant. In the stereotype treatment, they were also reminded of the characteristics of the other participant.
@@
 For one topic at a time and in random order,
-they were presented with the three gambles from the example above, and were asked to choose one of them. 
+they were presented with the three gambles from the example above and were asked to choose one of them. 
 The probability of success was 
@@
 In the interphase, they had to choose which of the 3 tables they wanted to see before entering their choice in it. This was done as 
-an alternative to a belief elicitation in each round. I take their choice of table to be a signal for their beliefs about
+an alternative to a belief elicitation in each round. I take their choice of table to be indicative of their beliefs about
 the underlying type. I chose not to elicit the beliefs at each round to stay true to the forces in framework 1.
@@
 
-At the end of the experiment, one of the 6 topics was randomly selected to determine the payment. They earned $\$0.20$ for each 
-correct answer in the quiz, and for each success in part 3.
+At the end of the experiment, one of the 6 topics was randomly selected to determine the payment. 
+They earned $\$0.20$ for each 
+correct answer in the quiz, and for each success in the task in Part 3 for the selected topic.
 
-Randomness is controlled throughout the experiment and sessions by setting a seed at the beggining of the
-first session. The seed was drawn at random and remained fixed for all sessions. 
+Randomness is controlled throughout the experiment and sessions by setting a seed at the beginning of the
+first session. The seed was drawn at random and remained fixed for all sessions. \footnote{The seed that was drawn 
+at the beginning of session 1 was 3452. The same seed was used for all sessions. It is used both for drawing $\omega$ for each of 
+the tasks in the experiment, as well as for drawing the outcomes from the gambles.}
 By doing this I ensure that any two subjects who have the same type and face the same exogenous rate will observe
@@
 
-Because the different models apply only under certain conditions, I split the predictions into two groups; the dogmatic and the 
-switcher constitute the first group, and the bayesian and self-serving updater are the second group. the predictions of group 1
-apply only in cases where $(\theta, \omega)$ are such that there is a self-defeating equilibrium. This is because whenever 
-there is no self defeating equilibria, the dogmatic model does not apply. On the other hand, the theories of group 2 apply to all
-possible combinations of the parameters. Hence, these theories can be tested and differentiated within a broader set of 
-observations.
+In this section, I outline the behavior that is predicted by each of the theories discussed above. I start with the dogmatic modeler.
 
-It is also important to note that since the predictions of the model are asymptotic and probabilistic, the predictions that are made 
-for the particular example that was taken to the lab depend strongly on the realized sequence of signals. Because the randomness has 
-been controlled for and kept fixed across sessions, for every parametrization $(\theta, \omega)$ there is a unique optimal path 
-for each of the models. I present the predictions made by this particular realization of the seed.\footnote{The seed that was drawn 
-at the beginning of session 1 was 3452. The same seed was used for all sessions. It is used both for drawing $\omega$ for each of 
-the tasks in the experiment, as well as for drawing the outcomes from the gambles.}
+## Dogmatic Modeler
 
-## Dogmatic and Switcher
+Since the domain of the problem is discrete and finite in the example, the predictions of the original theory apply only to 
+the combinations of parameters and initial beliefs for which there is a self-defeating equilibrium. In the example, there are 5 such 
+combinations. For each of them, the dogmatic modeler predicts that the agent will fall into the self-defeating equilibrium and will 
+be able to sustain the misspecified belief forever.
 
-The cases in which we can apply these two theories are the five self-defeating equilibria from the data generating process in the 
-example. From these and with the seed that was drawn, the models make different predictions in 4 cases. \footnote{the fifth 
-self-defeating equilibrum is such that the likelihood ratio does not go above 1 and thus the switcher is indistinguishable from 
-the dogmatic agent.}
+Table \ref{tab:table-dog} describes the 5 self-defeating equilibria and the effort choices that sustain them. The first columns describe the
+combination of parameters and initial beliefs. The last column describes the effort choice that the agent will make in the long run. It is 
+only for these combinations of parameter values and beliefs that the dogmatic model makes predictions within the Unifying example.
 
-## Bayesian and self-attribution updater
+**Prediction 1D:** _Whenever an agent is of a type $\theta^*$ but mistakenly believes that they are of a type $\hat{\theta}$, 
+and $(\theta^*, \omega^*, \hat{\theta})$ are such that there is s self-defeating equilibrium, the agent will fall into the
+trap and choose the effort level that sustains the misspecified belief forever._
 
-# Analysis
+The model 
+does not make predictions about what happens in cases where there is no stable belief. I assume that because there is 
+no stable belief, the agent will eventually
+have to use some procedure to revise their belief about $\theta$. In such cases, I aim to determine which of the alternative 
+explanations provided by the other theories is a better fit for the data.
+
+\begin{table}[htbp]
+
+    \centering
+    \begin{tabular}{|c|c|c|c|c|}
+        \hline
+        \textbf{True Type ($\theta^*$)} & \textbf{True State ($\omega^*$)} & \textbf{Believed Type ($\hat{\theta}$)} & \textbf{Believed state ($\hat{\omega}$)} & \textbf{Effort} \\
+        \hline
+        \hline
+        $\theta_L$ & $\omega_H$ & $\theta_M$ & $\omega_L$ & $e_L$ \\
+        \hline
+        $\theta_M$ & $\omega_L$ & $\theta_L$ & $\omega_M$ & $e_M$ \\
+        \hline
+        $\theta_M$ & $\omega_M$ & $\theta_H$ & $\omega_L$ & $e_L$ \\
+        \hline
+        $\theta_M$ & $\omega_M$ & $\theta_L$ & $\omega_H$ & $e_H$ \\
+        \hline
+        $\theta_M$ & $\omega_H$ & $\theta_H$ & $\omega_M$ & $e_M$ \\
+        \hline
+
+    \end{tabular}
+    \caption{Stable beliefs and the effort choices that support them for the unifying example}
+    \label{tab:table-dog}
+\end{table}
+
+Although the dogmatic model does not apply to all possible parametrizations and beliefs, whether subjects
+fall into the self-defeating equilibria or not is still informative of the updating procedure that they are using.
+Understanding if the presence of traps is a key feature preventing subjects from learning the optimal action is important
+for understanding the prevalence of overconfidence. Similarly, gaining insight into what happens 
+when there are no traps is important for understanding what are the other reasons why overconfidence 
+might arise and prevail.
+
+## Switcher
+
+Since the switcher starts as the same dogmatic agent, the initial behavior of both types of agents is identical, 
+however, because the switcher is keeping track of the likelihood ratio, they will be able to escape the self-defeating
+equilibrium if the evidence is convincing enough. Therefore there is a positive probability that the switcher will
+adjust their initially misspecified belief about $\theta$ and learn the true state.
+
+**Prediction 1S:** With positive probability, the switcher will escape the self-defeating equilibrium and learn the true state.
+
+One caveat is that when the switcher and the dogmatic agent both start with a correctly specified belief, neither of them 
+will fall into the self-defeating equilibria and thus will look identical even in the long run. This means that
+in order to distinguish between the two theories, I need to look at cases where the agent starts with a misspecified belief.
+
+The probability that the switcher will escape the self-defeating equilibrium depends on the prior belief about $\omega$.
+If the prior is sufficiently tight around the self-defeating equilibrium, the likelihood ratio will not grow fast enough, however, 
+in the example above, the prior is uniform over the states and therefore, the likelihood ratio is more likely to grow fast enough.
+
+## Self-Attribution Bias
+
+The key feature of Self-attribution bias is the asymmetric treatment of good news and bad news. 
+In particular, the agent will over-attribute successes to a high type and under-attribute them to a low type.
+Similarly, they will over-attribute failures to a low state and under-attribute them to a high state.
+This implies that, after observing a failure, the agent will adjust their effort downwards by more than 
+what an unbiased Bayesian would have done. In contrast, after observing a success, the agent will adjust 
+their effort upwards by less than a Bayesian would have done and if the bias is large enough, it could
+be that the agent will not adjust their effort upwards at all, or even decrease their effort in response to a success.
+
+This is in stark contrast with what a Dogmatic modeler would do. A dogmatic modeler always attributes
+any variation in the outcome to the state and never updates their beliefs about $\theta$. Therefore,
+they will always increase their effort choices after a surprising success and decrease it after a failure.
+
+On the other hand, the biased behavior can be in line with the behavior of a switcher. In particular,
+if the agent starts with a misspecified belief on $\hat{\theta}$, and is willing to switch to a belief with 
+$\theta'>\hat{\theta}$, whenever the paradigm shift happens, it will likely be in response to a surprising 
+streak of successes. In this case, when they adjust their belief about $\theta$, they will also 
+adjust their effort choice. Since they were initially underconfident, they had been choosing an effort that was
+too high relative to the true state, and therefore, the effort is likely to fall in response to a 
+surprising streak of success.
+
+**Prediction 1A:** _After observing a failure, the agent will adjust their effort downwards by more than a Bayesian would have done.
+After observing a success, the agent will adjust their effort upwards by less than a Bayesian would have done. If the bias is large enough,
+the agent might not adjust their effort upwards at all, or even decrease their effort in response to a success._
+
+Prediction 1A helps distinguish between the self-attribution bias and the dogmatic modeler. However, it does not help distinguish between
+the self-attribution bias and the switcher. In order to do so, I need to look at cases where the agent starts with a correctly specified belief.
+In these cases, the switcher is very unlikely to switch to a different belief and therefore, the behavior of the switcher will mostly change
+in the same direction as the information he receives. \footnote{If they get a streak of failures they are likely to 
+adjust their effort downwards and if they get a streak of successes they are likely to adjust their effort upwards.} Instead, 
+the self-attribution bias will lead to a different behavior. In particular, even for agents who have a belief 
+that is correctly specified and place a lot of weight on the correct values of $\theta$, the bias will 
+cause these agents to become overconfident after a sequence of successes. This force is not present in the switcher or the dogmatic
+and it is the key feature that allows me to identify a biased updating procedure.
+
+**Prediction 2A:** _After observing a streak of successes, the agent will update their belief about $\theta$ upwards. This will lead to the 
+possibility of observing subjects who start correctly specified and become overconfident._
+
+## The Bayesian
+
+The Bayesian serves as the closest benchmark to a fully rational agent. However, as discussed above, 
+they are still vulnerable to falling into self-defeating equilibria, in which case, their long-run behavior
+will be identical to that of the dogmatic modeler. The main distinguishing feature is that when they do 
+fall into a self-defeating equilibrium, there is no bias in the direction of the misspecification that they 
+end up being trapped in. In contrast, the dogmatic modeler will always be trapped in a misspecified belief
+that they started with and the self-attribution updater will always become overconfident.
+
+**Prediction 1B:** _When an agent starts with a diffused prior and falls into a self-defeating equilibrium,
+they will be equally likely to fall into the underconfident trap as the overconfident trap._
+
+**Prediction 2B:** _Bayesian agents always update their effort choices in the same direction as the information they receive. 
+That is, if they see successes, they would only increase their effort; and if they see failures they would 
+only decrease their effort._
+
+# Stereotypes
+
+So far I have focused only on the case of overconfidence. However, each of the models can also be used to explain the prevalence
+of underconfidence. An agent can have a dogmatic belief about the ability of a particular group of people and either under or overestimate
+the associated parameter. Similarly, they can be willing to switch between two dogmatic beliefs about their ability as a switcher would.
+Finally, they can have a biased updating procedure in which they treat good news and bad news asymmetrically.
+
+As such, all the predictions discussed above apply to the case of Stereotypes as well. My analysis of 
+stereotypes will focus only on the degree to which ego-relevance of the type affects the updating procedure and not on the 
+motivations behind the bias. I am particularly interested in whether the explanatory power of the models 
+differs with the degree of ego-relevance of the type.
+
+# Results
+
+## Initial Beliefs and misspecifications
+
+As mentioned in the predictions section, the dogmatic modeler and the switcher are only distinguishable 
+when the agent starts with a misspecified belief. Figure \ref{fig:misspecification-hist} shows the 
+distribution of misspecifications by treatment. The histogram considers the difference between the subject's 
+true score in the quiz and their guess about their score. If their guess is in a higher category than their true score,
+they are overconfident; if it is in a lower category, they are underconfident; and if it is in the same category, 
+they are correctly specified. Overall, `r round(sum(updates$misspecification != 'correct')/nrow(updates), 2)` of the 
+guesses made in the questionnaire were misspecified. The rest of the guesses coincided with the true score. 
+And the distribution of misspecifications is similar across treatments.
+
+![Initial misspecifications by treatment](../figures/misspecification_hist.png){#fig:misspecification-hist}
+
+Although the overall distribution is similar for both treatments, the misspecifications arise for different 
+combinations of characteristics in each treatment. Figure \ref{fig:misspecification-by-treatment} shows a heatmap 
+of the misspecifications that arose in each treatment. In the stereotype treatment, subjects are most underconfident 
+about the performance 
+of other non-American females in Sports and Video Games. In contrast, they are most overconfident about the performance 
+of American men in Verbal Reasoning. In the ego-relevant treatment, subjects are most underconfident about their own
+performance in pop culture and art, while most overconfident about their performance in Verbal Reasoning.
+
+![Initial misspecifications by treatment and characteristics](../figures/misspecifications_characteristics_treatment.png){#fig:misspecification-by-treatment}
+
+Having widespread misspecifications in both treatments is important for the analysis because it allows me to distinguish between the
+dogmatic modeler and the switcher. If there were no misspecifications, the two models would be indistinguishable.
+
+## Learning
+
+In this section, I analyze the learning behavior of subjects in the experiment. There are two parameters 
+that subjects can be learning about: the exogenous parameter $\omega$ and the type $\theta$. 
+Their belief about the exogenous parameter is tracked by their choice of effort, while their belief about the 
+type is tracked by their choice of a matrix in which to enter their effort.
+
+### Learning about the state
+
+In order to analyze the learning about the state, I look at the share of optimal choices that are made at each round.
+I find that although subjects seem to be improving in their choices overall, the last choice coincided 
+with the true state only in 52% of the choices in the last round of each task. This is statistically 
+greater than the initial share of optimal choices of 30% ($p<0.01$). However, it is still far from 
+complete learning. It is also important to note that learning is similar across treatments. The 
+share of choices that were consistent with the true state for each round is reported in Figure \ref{fig:optimal-choices-by-round}.
+
+![Share of optimal choices by round](../figures/effort_learning.png){#fig:optimal-choices-by-round}
+
+A closer look at whether people learned or not reveals that there is a good amount of heterogeneity in the
+sample. Figure \ref{fig:learning-by-groups} shows the share of optimal choices by round for 
+subjects that chose an effort that matched the state in 3 out of the last 4 rounds. It also shows the 
+share of optimal choices for subjects who chose an effort that matched the state in fewer than 3 out of 
+the last 4 rounds. I label the former as learners and the latter as non-learners, with learners making up
+`r round(sum(updates$learner)/nrow(updates), 2)*100`% of the sample.
+
+![Share of optimal choices by round for subjects who learned (their effort in at least 3 out of tha last 4 choices matched the state), and subjects who did not learn](../figures/learning_groups.png){#fig:learning-by-groups}
+
+In what follows I will try to disentangle the reasons for the lack of learning. I will argue that 
+it is not due to the presence of traps, but rather due to biased updating. According to the theories, 
+the main reason why subjects might not learn is that they have an incorrect belief about the type or 
+they develop an incorrect belief about the type.
+
+### Learning about the type
+
+![Matrix choices by round](../figures/last_button_consistency.png){#fig:matrix-choices-by-round}
+
+Since the elicitation of the belief about the type was not incentivized and not elicited in a standard way, 
+I first need to confirm that subjects were not just randomly choosing a matrix in which to enter their effort.
+The left panel of Figure \ref{fig:matrix-choices-by-round} shows the share of subjects who chose a matrix 
+consistent with their initial reported belief. In round 1, `r round(nrow(updates[round_number == 1 & last_button_consistent == 1])/ nrow(updates[round_number==1]), 2)*100`% 
+of the subjects chose a matrix that was consistent with their initial belief. This indicates that subjects
+were not just randomly choosing a matrix in which to enter their effort. From round 2 onwards, the share
+steadily declines, but still not as far as to indicate a random choice of matrices. This is consistent with
+the subjects moving away from their starting belief through some updating procedure.
+
+On the right panel of Figure \ref{fig:matrix-choices-by-round} I show the share of subjects who chose a matrix
+that is consistent with their true type. Unlike the left panel, there is no clear trend, which indicates that
+although they are moving away from their initial belief, they are not moving towards their true type, which 
+means that overall, misspecification is not decreasing. A closer look at the data reveals a good amount of
+heterogeneity in the underlying behavior.
+
+Figure \ref{fig:transitions} shows the transition matrix for subjects who started in each of the 
+3 possible starting specifications and the specifications that they ended up in at the end of the updating task.
+The two things to note are that the initial belief is the most likely end belief. This is consistent with 
+some degree of stickiness of the misspecifications as the switcher and dogmatic models would predict. However, 
+the data also presents a lot of subjects who started with a correct belief of the type and ended up 
+overestimating it. This is consistent only with the self-attribution bias. Lastly, the subjects who
+initially overestimate the score, are the least likely to learn their true type.
+
+![Transition matrix for subjects who started in each of the 3 possible starting specifications and the specification that they ended up in at the end of the updating task](../figures/misspecification_transitions.png){#fig:transitions}
+
+The transition matrix points towards the presence of self-attribution bias in the data. However, it is
+still possible that there is heterogeneity in the updating procedure across subjects. In the next section
+I will look at the role of self-defeating equilibria in preventing learning. I find that the presence of
+self-defeating equilibria does not seem to be the main deterrent to learning.
+
+## Learning traps
+
+As described above, the presence of stable misspecified beliefs act as learning traps. If an agent falls 
+into one of these traps, bayesian updating will lead them to choose the same effort forever. These self-defeating 
+equilibria allow me to distinguish between the dogmatic modeler and the switcher. If the agent falls into a
+trap and stays there forever, they are more likely to be a dogmatic modeler. If they escape the trap, they
+are more likely to be a switcher or to be updating with some attribution bias.
+
+I look at the subjects who are updating in a task where the combination of $\theta$ and $\omega$ is such that
+there is a self-defeating equilibrium. I then look at how often
+
+## Reactions to good and bad news
 
 # Conclusion
+
+# References

### 2023-10-07 Paper/draft.tex
trap behavior

--- 2023-09-07 Paper/draft.tex
@@
 \usepackage[margin=2.5cm]{geometry}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 \setlength{\emergencystretch}{3em} % prevent overfull lines
@@
 \author{Jimena Galindo}
-\date{September 07, 2023}
+\date{October 07, 2023}
 
@@
 \hypertarget{related-literature}{%
-\section{Related Literature}\label{related-literature}}
+\subsection{Related literature}\label{related-literature}}
+
+\hypertarget{theoretical-framework}{%
+\section{Theoretical Framework}\label{theoretical-framework}}
+
+I consider multiple theories of belief updating that have been proposed
+in the literature and that are able to rationalize the prevalence of
+misspecified beliefs. I focus on two different frameworks and develop a
+unifying example that allows me to compare the predictions of all the
+theories. In this section, I outline the theories within each of the
+frameworks.
 
 \hypertarget{framework-1}{%
-\section{Framework 1}\label{framework-1}}
+\subsection{Framework 1}\label{framework-1}}
 
@@
 His prior belief about his type is \(p_0(\theta)\) and his belief about
-the state state \(p_0(\omega)\) coincides with the true distribution
-\(f\). Let the agent's type be \(\theta^*\) and the realized state be
-\(\omega^*\).
+the state, \(p_0(\omega)\), coincides with the true distribution. Let
+the agent's true type be \(\theta^{*}\), and the realized state be
+\(\omega^{*}\).
 
@@
 one on being a particular type, \(\hat{\theta}\). An agent can be
-dogmatic and misspecified; that means that
+dogmatic and misspecified. If the agent is both,
 \(\hat{\theta} \neq \theta^*\) and \(p_0(\hat{\theta}) = 1\).
@@
 simplifying assumption that the agent is myopic and chooses the action
-that maximizes the payoff in each period. This assumption is symplifies
-the analysis and plays a role on whether an agent who updates their
-beliefs using bayes rule would learn the truth or not.
+that maximizes the payoff in each period. This assumption simplifies the
+analysis and plays a role in whether an agent who updates their beliefs
+using Bayes rule would learn the truth or not. The behavior of a
+forward-looking agent is discussed in the conclusion.
 
@@
 the agent's belief about their type is misspecified and the outcome
-generated by the action is consistent with the misspecified belief. The
-average outcome under the true type and the true state equals the
-average output the agent expects under the misspecified belief. In
-addition, the agent's belief is said to be \emph{stable} when this
+generated by the action is consistent with the misspecified belief. This
+means that the average outcome under the true type and the true state
+equals the average output the agent expects under the misspecified
+belief. The agent's belief is said to be \emph{stable} when this
 happens.
@@
 Within this framework, I consider two nested theories of belief
-updating. The first one is a dogmatic modeler from \citet{Heidhues2018}.
+updating: the first one is a dogmatic modeler from \citet{Heidhues2018},
 The second one is a switcher, as in \citet{Ba2023}. The dogmatic modeler
@@
 this is the sense in which the two are nested. Both theories produce
-different predictions with respect to the equilibrium outcome.
+different predictions about the agent's behavior. I discuss both in what
+follows.
 
 \hypertarget{the-dogmatic-modeler}{%
-\subsection{The Dogmatic Modeler}\label{the-dogmatic-modeler}}
+\subsubsection{The Dogmatic Modeler}\label{the-dogmatic-modeler}}
 
-A dogmatic agent does not update their beliefs about \(\theta\); instead
-he holds a degenerate belief that places probability one on being a
-particular type, \(\hat{\theta}\), which is potentially not his true
-type. In this case, no matter how much information he gathers against
-being of type \(\hat{\theta}\), he will not update his beliefs. Any
+A dogmatic agent does not update their beliefs about \(\theta\),
+instead, he holds a degenerate belief that places probability on
+\(\hat{\theta}\), which is potentially misspecified. In this case, no
+matter how much information he gathers against being of type
+\(\hat{\theta}\), he will not update his beliefs about \(\theta\). Any
 discrepancies between the observed outcomes and his believed type are
 incorporated using the Bayes rule to update their beliefs about
-\(\omega\). This means the dogmatic agent will never learn their true
-type if they startu off as being misspecified.
-
-\citet{Heidhues2018} show that, under certain assumptions on the
-per-period utility,\footnote{The assumptions are that 
+\(\omega\). \citet{Heidhues2018} show that, under certain assumptions on
+the per-period utility,\footnote{The assumptions are that 
 $u$ is twice continuously differentiable with: (i)$u_{ee}<0$ and $u_e(\underline{e} \theta, \omega)>0>u_e(\Bar{e}, \theta, \omega)$, 
@@
 believed type and the observed data. In other words, they will be in a
-self-defeating equilibrium whith a stable belief that places probability
+self-defeating equilibrium with a stable belief that places probability
 one on the incorrect parameters \((\hat{\theta}, \omega_{\infty})\)
@@
 the disappointment to the state being lower than expected. He will
-continue to update in ths way until he converges to a belief about
+continue to update in this way until he converges to a belief about
 \(\omega\) that is stable. Such a belief will explain the observed
@@
 \((\hat{\theta}\theta+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}\). In
-response, he will apply bayes rule to update his beliefs about
+response, he will apply Bayes rule to update his beliefs about
 \(\omega\) to get the posterior belief with
@@
 choose a lower effort at \(t+k\). As a result, he will again receive an
-average utlitity that is lower than what he expected which will cause
-his belief to drift further down. This process will continue until the
+average utility that is lower than what he expected which will cause his
+belief to drift further down. This process will continue until the
 average utility equals his expected utility under the dogmatic belief
 that assigns probability 1 to \(\hat{\theta}\). At that point, the
-stundent will have reached a self-defeating equilibrium and he will
+student will have reached a self-defeating equilibrium and he will
 continue to choose sub-optimal effort forever. }
 
-Although the model of a dogmatic modeler is able to rationalize the
-prevalence of overconfident (underconfident) beliefs, the assumption
-that the agent has a degenerate belief and no mechanism through which he
-can update such belief is very restrictive. An alternative approach is
-proposed by \citet{Ba2023}. She proposes an extension of the dogmatic
-agent who is able to jump from one dogmatic belief to another. By doing
-so, the agent might end up being dogmatic and correctly speciefied.
+Although the model of a dogmatic modeler rationalizes the prevalence of
+overconfident (underconfident) beliefs, the assumption that the agent
+has a degenerate belief and no mechanism through which he can update
+such belief is very restrictive. An alternative approach is proposed by
+\citet{Ba2023}. She proposes an extension of the dogmatic agent who is
+able to jump from one dogmatic belief to another. By doing so, the agent
+might end up being dogmatic and correctly specified.
 
 \hypertarget{the-switcher}{%
-\subsection{The Switcher}\label{the-switcher}}
+\subsubsection{The Switcher}\label{the-switcher}}
 
@@
 willing to switch to a different dogmatic belief if the data is
-convincing enough. Notice that their beliefs are still degenerate and
-assign probability one to a particular type, and zero to all other
-types. This means that a bayesian update on \(\theta\) would cause no
-change in their beliefs. However, they are willing to entertain two such
-beliefs and have a mechanism by which they decide which belief to adopt
-at any period \(t\).
+convincing enough. Their prior is still degenerate and assigns
+probability one to a particular type, and zero to all other types. This
+means that a Bayesian update on \(\theta\) does not change their beliefs
+about the type. However, they are willing to entertain two such beliefs
+and have a mechanism by which they decide which belief to adopt at any
+period \(t\).
 
@@
 observe a sequence of outcomes that are sufficiently unlikely to have
-happened if they were of the type they initially believed. They do so by
-keeping track of the likelihood that each of the possible types
-generated the data. If the likelihood ratio is sufficiently large, the
-agent will switch to the alternative and behave as if they are dogmatic
-about the new type.
+happened if they were of the type they initially believed. In order to
+evaluate if the evidence is convincing enough, they keep track of the
+likelihood that each of the possible types generated the data. If the
+likelihood ratio is sufficiently large, the agent will switch to the
+alternative and behave as if they are dogmatic about the new type.
 
-In particular, for an agent that starts off with a dogmatic belief that
-they are of type \(\hat{\theta}\) but is willing to consider the
-alternative explanation that they are of type \(\tilde{\theta}\), the
-agent will switch to the alternative if:
+In particular, for an agent that starts with a dogmatic belief that they
+are of type \(\hat{\theta}\) but is willing to consider the alternative
+explanation that they are of type \(\tilde{\theta}\), the agent will
+switch to the alternative if:
 
@@
 Dogmatic belief that best fits the
-data.\footnote{In a related problem @Schwarstein2021 proposes a similar updating procedure wich relies on the Bayesian 
-hypothesis test.} Notice that if \(\alpha \to \infty\), the behavior of
-the switcher will be indistinguishable from that of the Dogmatic
-modeler. In this sense, the switcher is a generalization of the dogmatic
-type.
+data.\footnote{In a related problem @Schwarstein2021 proposes a similar updating procedure which relies on the Bayesian 
+hypothesis test. However, in their model there is a sender who optimally chooses to propose a model that fits the data}
+Notice that if \(\alpha \to \infty\), the behavior of the switcher will
+be indistinguishable from that of the Dogmatic modeler. In this sense,
+the switcher is a generalization of the dogmatic type.
 
@@
 ratio is unlikely to grow as fast as it is needed to escape the
-self-defeating equilibrium. In this cases we say that the misspecified
-belief is persistent. Hence, in order to be able to determine which of
-these two models provides a better explanation of the observed
-behaviors, we must focus on cases in which the prior is diffused enough
-and the sequence of realized outcomes is such that the self-defeating
-equilibrium would not persist.
+self-defeating equilibrium. In such situations, we say that the
+misspecified belief is persistent.
 
 \hypertarget{framework-2}{%
-\section{Framework 2}\label{framework-2}}
+\subsection{Framework 2}\label{framework-2}}
 
-The agent is still of some type \(\theta^* \in \Theta\) and the state is
-\(\omega \sim F\). In this case the agent chooses an action \(a\in A\)
-and observes a binary outcome that is either a success or a failure.
-Denote the outcome by \(o \in {s,f}\). The probability of observing a
-success is ingreasing in \(\theta^*\) and in \(\omega\). Whenever the
-agent observes a succes, he gets a payoff \(v>0\) and whenever the
-outcome is a failure, normalize the payoff to 0. In addition, the
-probability of success is such that for each state, there is a unique
-optimal action that maximizes the agent's expected payoff.
+As in framework 1, the agent is of some type \(\theta^* \in \Theta\) and
+the state is \(\omega \sim F(\Omega)\). In this case, the agent chooses
+an action \(a\in A\) and observes a binary outcome that is either a
+success or a failure. Denote the outcome by \(o \in {s,f}\). The
+probability of observing a success is increasing in \(\theta^*\) and in
+\(\omega\). Whenever the agent observes a success, he gets a payoff
+\(v>0\) and whenever the outcome is a failure, the payoff is 0. In
+addition, the probability of success is such that for each state, there
+is a unique optimal action that maximizes the agent's expected payoff.
+Therefore, the probability of success can be seen as a monotone
+transformation of the utility from Framework 1.
 
-Two nested theories that have been widely studied fall within this
-framework: Fully Bayesian updating and self-serving attribution bias. I
+I focus on two nested theories that have been widely studied within this
+framework: Full Bayesian updating and self-serving attribution bias. I
 explain each of these classical models of belief updating in what
@@
 \hypertarget{the-bayesian}{%
-\subsection{The Bayesian}\label{the-bayesian}}
+\subsubsection{The Bayesian}\label{the-bayesian}}
 
 A Bayesian agent simultaneously updates their beliefs about \(\theta\)
-and \(\omega\) by using Bayes' rule. The posterior odds at period t
-about \(\theta\) after observing an outcome are given by: \[
-\frac{p_{t}[\theta_H|\text{outcome}]}{p_{t}[\theta_M|\text{outcome}]} = 
-      \frac{p[\text{outcome}|\theta_H]p_{t-1}[\theta_H]}{p[\text{outcome}|\theta_M]p_{t-1}[\theta_M]}
-\] and \[
-\frac{p_{t}[\theta_M|\text{outcome}]}{p_{t}[\theta_L|\text{outcome}]} = 
-      \frac{p[\text{outcome}|\theta_M]p_{t-1}[\theta_M]}{p[\text{outcome}|\theta_L]p_{t-1}[\theta_L]}
+and \(\omega\) by using Bayes' rule. The posterior at period t+1 about
+\(\theta\) after observing a history of outcomes \(h^t\) is given by: \[
+p_{t+1}(\theta, \omega| h^t) = \frac{p[h^t|\theta, \omega]p_t(\theta, \omega)}{\sum_{(\theta', \omega')}p[h^t|\theta', \omega']p_t(\theta', \omega')}
 \]
 
-Where \(p_{t-1}\) is the prior at period \(t\) and
-\(p[\text{outcome}|\theta] = \sum_{\omega} p[\text{outcome}|\theta, \omega, e]p_{t-1}(\omega)\)
-is the probability of observing the outcome given the agent's type and
-the effort chosen. The update is symmetric for \(\omega\).
+Where \(p_{t}\) is the belief at the start of period \(t+1\). The update
+is symmetric for \(\omega\).
 
-Bayesian agents always choose the effort level that maximizes their flow
-payoff by taking expectations over their prior beliefs about \(\theta\)
-and \(\omega\). Since agents are myopic, even though all the parameters
-could be identified with enough variation in choices, although the
-Bayesian agent is the closest to a fully rational agent discussed here,
-they might not learn their true type. This happens because, by being
-myopic, they do not internalize the tradeoff between flow payoff and
-learning. This can result in too little experimentation to learn their
-true type. An alternative to this approach is given by
-\citet{Hestermann2021} and is discussed with the results.
+Bayesian agents choose the effort level that maximizes their expected
+flow payoff by taking expectations over their prior beliefs about
+\(\theta\) and \(\omega\). Since agents are myopic, even though all the
+parameters could be identified with enough variation in choices.
+Although the Bayesian agent is the closest to a fully rational agent
+discussed here, they might not learn their true type. This happens
+because, by being myopic, they do not internalize the tradeoff between
+flow payoff and learning. This can result in too little experimentation
+to learn their true type. An alternative to this approach is given by
+\citet{Hestermann2021} and is discussed in the concluding remarks.
 
-\hypertarget{the-self-serving-bayesian}{%
-\subsection{The Self-Serving Bayesian}\label{the-self-serving-bayesian}}
+Also notice that if a fully Bayesian agent has a dogmatic prior, they
+will never update their beliefs about the parameter that they are
+dogmatic about. This will imply that they are prone to the same types of
+errors as the dogmatic modeler in framework 1.
 
-A self-serving bayesian is an agent who uses a biased version of Bayes
-rule to update his beliefs.He will update his beliefs about the state
-\(\omega\) and his type \(\theta\) by over-attributing successes to a
-high value of \(\theta\) and under-estimating the role of higher
-\(\omega\). Similarly, he will attribute failure to a low state to a
-greter degree than an unbiased agent would. To model the self-serving
-attribution bias, I take the approach of \citet{benjamin2019}, where the
-posterior is given by:
+\hypertarget{the-self-serving-updater}{%
+\subsubsection{The Self-Serving
+Updater}\label{the-self-serving-updater}}
+
+A self-serving Bayesian is an agent who uses a biased version of Bayes
+rule to update their beliefs. They will update their beliefs about the
+state \(\omega\) and his type \(\theta\) simultaneously by
+over-attributing successes to a high value of \(\theta\) and
+under-estimating the role of higher \(\omega\). Similarly, he will
+attribute failure to a low state to a greater degree than an unbiased
+agent would. To model the self-serving attribution bias, I take the
+approach of \citet{benjamin2019}, where the posterior odds are given by:
 
 \[
-p_{t}[\theta_H|\text{outcome}] = 
-\frac{p[\text{outcome}|\theta]^{c_s^{\theta}\mathbb{I}\{\text{success}\}+c_f^{\theta}\mathbb{I}\{\text{failure}\}}p_{t-1}[\theta]}
-{\sum_{\theta'\in\Theta}p[\text{outcome}|\theta']^{c_s^{\theta}\mathbb{I}\{\text{success}\}+c_f^{\theta}\mathbb{I}\{\text{failure}\}}p_{t-1}[\theta']}
+p_{t+1}(\theta, \omega| h^t) = \frac{p[h^t|\theta, \omega]^{c(\theta, \omega, o_t)}p_t(\theta, \omega)}{\sum_{(\theta', \omega')}p[h^t|\theta', \omega']^{c(\theta, \omega, o_t)}p_t(\theta', \omega')}
 \]
 
-\(c_s^{\theta}\) and \(c_f^{\theta}\) are the self-serving attribution
-bias parameters for the agent's type \(\theta\). If
-\(c_s^{\theta} = c_f^{\theta} = 1\), the agent is unbiased and the
-update is the same as the Bayesian update. On the other hand, if
-\(c_s^{\theta} > c_f{\theta}\) the agent over-attributes success to
-their type and under-attributes failure to their type\footnote{
-  notice that the values of $c_s^{\theta}$ and $c_f^{\theta}$ are not restricted to be greater than 1. If they are both equal to 
-  each other but less (more) than one, then the bias is simply underinference (overinference).}.
+with
+\(c(\theta_H, \omega, o)<c(\theta_M, \omega, o)<c(\theta_L, \omega, o)\leq 1\)
+and
+\(c(\theta, \omega_L, o)<c(\theta, \omega_M, o)<c(\theta, \omega_H, o)\leq 1\).
 
-The update for \(\omega\) is analogous but with \(c_f^{\omega}\) and
-\(c_s^{\omega}\) instead of \(c_f^{\theta}\) and \(c_s^{\theta}\) and
-the bias is present whenever \(c_f^{\omega} > c_s^{\omega}\). That is,
-the agent over-attributes failure to a low state relative the higher
-states and under-attributes success to a low state relative to the
-higher states.
+This formulation of the bias means that the agent will over-attribute
+successes to a high type and under-attribute them to a low type. Whereas
+they will over-attribute failures to a low state and under-attribute
+them to a high state. The parameter \(c\) determines the degree of bias
+and the restriction on the order ensures that the model is still
+falsifiable.
 
@@
 \section{A Unifying Example}\label{a-unifying-example}}
+
+In order to compare the predictions of the theories discussed above, I
+develop a unifying example that allows me to isolate the forces behind
+each of the theories. The example is a modification of the one in
+\citet{Heidhues2018} and is adapeted to be easier to implement in the
+lab.
 
@@
 \(\omega\) and is fully described by the following table:
+
+\begin{table}[htbp]
 
@@
 
+\caption{Probability of success for each type, gamble and effort level}
+\label{tab:table1}
+\end{table}
+
 Conditional on a type, the agent's flow payoff is maximized by choosing
@@
 from each of the updating mechanisms discussed in the previous section
-and allows for direct comparison of all the theories. For realizations
-of \((\theta, \omega)\) for which there are self-confirming equilibria,
-the dogmatic agent will fall into the trap whereas the switcher will be
-able to escape it. Similarly, an agent with self-attribution bias will
-update their beliefs differently from an unbiased Bayesian, leading them
-to choose different gambles. I exploit such cases in order to test which
-model is a better fit for how subjects behave in a laboratory
-experiment.
-\footnote{because the setting does not match that of @Heidhues2018, there will be situationf for which the theory 
-does not provie a prediction. If such cases arise in the lab, they will not be used for the analysis. However, whether a misspecified 
+and allows for the comparison of the main forces behind the theories.
+For realizations of \((\theta, \omega)\) for which there are
+self-confirming equilibria, the dogmatic agent will fall into the trap
+whereas the switcher will be able to escape it. Similarly, an agent with
+self-attribution bias will update their beliefs differently from an
+unbiased Bayesian, leading them to choose different gambles. I exploit
+such cases in order to test which model is a better fit for how subjects
+behave in a laboratory experiment.
+\footnote{because the setting does not match that of Heidhues et al. [2018], there will be situationf for which the theory 
+does not provide a prediction. If such cases arise in the lab, they will not be used for the analysis. However, whether a misspecified 
 belief persists or not for the switcher, depends highly on the realized history of signals that he gets.}
@@
 
-I recruited XXX undergraduate subjects from the CESS lab at NYU who
+I recruited undergraduate subjects from the CESS lab at NYU who
 participated in an in-person experiment. Sessions lasted approximately
-XXX hours and subjects earned an average payment of XXX. The experiment
-was programmed using oTree \citep{chen2016otree}.
+45 minutes and subjects earned an average payment of \(\$22.6\). The
+experiment was programmed using oTree \citep{chen2016otree}.
 
@@
 condition and the \emph{stereotype} condition. Subjects participated in
-only one of the treatments. Treatments were randomly assigned at the
-session level. The tasks were identical across treatments, except for
+only one of the treatments. All subjects within a session participated
+in the same treatment and the first 4 treatments were assigned the
+ego-relevant condition; the rest were assigned to the stereotype
+treatment. The tasks were identical across treatments, except for
 parameter \(\theta\). In the ego-relevant condition \(\theta\) is the
@@
 participant was their gender identity and whether they were US nationals
-or not. For each guess they had three score options: Low-Score (5 or
+or not. For each guess, they had three score options: Low-Score (5 or
 fewer correct answers), Mid-Score (between 6 and 15 correct answers),
-High-Score (16 or more). Each of the score categories correspond to
+High-Score (16 or more). Each of the score categories corresponded to
 \(\theta_L\), \(\theta_M\), and \(\theta_H\) respectively. They were
@@
 .75, and 1 to the chosen type. The remaining probability is split
-equally among the other two types. Questions in part 2 were not
+equally among the other two types. Questions in Part 2 were not
 incentivized, but subjects were told that providing an accurate answer
@@
 
-The purpose of part 2 is to classify subjects into overconfident,
+The purpose of Part 2 is to classify subjects into overconfident,
 underconfident and correctly specified. If a subject guesses their score
@@
 
-Finally, in part 3 subjects completed a belief updating task for each of
-the quizzes. Before starting the task they were reminded of their guess
-for the score. In the ego treatment they were reminded of their guess
-about themselves and in the stereotype treatment they were reminded of
-their guess about the other participant. In the stereotype treatment,
-they were also reminded of the characteristics of the other participant.
+Finally, in Part 3, subjects completed a belief updating task for each
+of the quizzes. Before starting the task they were reminded of their
+guess for the score. In the ego-relevant treatment, they were reminded
+of their guess about themselves and in the stereotype treatment they
+were reminded of their guess about the other participant. In the
+stereotype treatment, they were also reminded of the characteristics of
+the other participant.
 
 For one topic at a time and in random order, they were presented with
-the three gambles from the example above, and were asked to choose one
-of them. The probability of success was determined by their own score in
+the three gambles from the example above and were asked to choose one of
+them. The probability of success was determined by their own score in
 the ego-relevant condition, and by the score of the other participant in
@@
 alternative to a belief elicitation in each round. I take their choice
-of table to be a signal for their beliefs about the underlying type. I
+of table to be indicative of their beliefs about the underlying type. I
 chose not to elicit the beliefs at each round to stay true to the forces
@@
 to determine the payment. They earned \(\$0.20\) for each correct answer
-in the quiz, and for each success in part 3.
+in the quiz, and for each success in the task in Part 3 for the selected
+topic.
 
 Randomness is controlled throughout the experiment and sessions by
-setting a seed at the beggining of the first session. The seed was drawn
-at random and remained fixed for all sessions. By doing this I ensure
-that any two subjects who have the same type and face the same exogenous
-rate will observe the same outcomes and thus, if they use the same
-updating procedure, they should be choosing the same gambles. This
-design feature allows me to identify differences in updating procedures
-across subjects.
+setting a seed at the beginning of the first session. The seed was drawn
+at random and remained fixed for all sessions.
+\footnote{The seed that was drawn 
+at the beginning of session 1 was 3452. The same seed was used for all sessions. It is used both for drawing $\omega$ for each of 
+the tasks in the experiment, as well as for drawing the outcomes from the gambles.}
+By doing this I ensure that any two subjects who have the same type and
+face the same exogenous rate will observe the same outcomes and thus, if
+they use the same updating procedure, they should be choosing the same
+gambles. This design feature allows me to identify differences in
+updating procedures across subjects.
 
-\hypertarget{analysis}{%
-\section{Analysis}\label{analysis}}
+\hypertarget{predictions}{%
+\section{Predictions}\label{predictions}}
 
-\renewcommand\refname{Conclusion}
+In this section, I outline the behavior that is predicted by each of the
+theories discussed above. I start with the dogmatic modeler.
+
+\hypertarget{dogmatic-modeler}{%
+\subsection{Dogmatic Modeler}\label{dogmatic-modeler}}
+
+Since the domain of the problem is discrete and finite in the example,
+the predictions of the original theory apply only to the combinations of
+parameters and initial beliefs for which there is a self-defeating
+equilibrium. In the example, there are 5 such combinations. For each of
+them, the dogmatic modeler predicts that the agent will fall into the
+self-defeating equilibrium and will be able to sustain the misspecified
+belief forever.
+
+Table \ref{tab:table-dog} describes the 5 self-defeating equilibria and
+the effort choices that sustain them. The first columns describe the
+combination of parameters and initial beliefs. The last column describes
+the effort choice that the agent will make in the long run. It is only
+for these combinations of parameter values and beliefs that the dogmatic
+model makes predictions within the Unifying example.
+
+\textbf{Prediction 1D:} \emph{Whenever an agent is of a type
+\(\theta^*\) but mistakenly believes that they are of a type
+\(\hat{\theta}\), and \((\theta^*, \omega^*, \hat{\theta})\) are such
+that there is s self-defeating equilibrium, the agent will fall into the
+trap and choose the effort level that sustains the misspecified belief
+forever.}
+
+The model does not make predictions about what happens in cases where
+there is no stable belief. I assume that because there is no stable
+belief, the agent will eventually have to use some procedure to revise
+their belief about \(\theta\). In such cases, I aim to determine which
+of the alternative explanations provided by the other theories is a
+better fit for the data.
+
+\begin{table}[htbp]
+
+    \centering
+    \begin{tabular}{|c|c|c|c|c|}
+        \hline
+        \textbf{True Type ($\theta^*$)} & \textbf{True State ($\omega^*$)} & \textbf{Believed Type ($\hat{\theta}$)} & \textbf{Believed state ($\hat{\omega}$)} & \textbf{Effort} \\
+        \hline
+        \hline
+        $\theta_L$ & $\omega_H$ & $\theta_M$ & $\omega_L$ & $e_L$ \\
+        \hline
+        $\theta_M$ & $\omega_L$ & $\theta_L$ & $\omega_M$ & $e_M$ \\
+        \hline
+        $\theta_M$ & $\omega_M$ & $\theta_H$ & $\omega_L$ & $e_L$ \\
+        \hline
+        $\theta_M$ & $\omega_M$ & $\theta_L$ & $\omega_H$ & $e_H$ \\
+        \hline
+        $\theta_M$ & $\omega_H$ & $\theta_H$ & $\omega_M$ & $e_M$ \\
+        \hline
+
+    \end{tabular}
+    \caption{Stable beliefs and the effort choices that support them for the unifying example}
+    \label{tab:table-dog}
+\end{table}
+
+Although the dogmatic model does not apply to all possible
+parametrizations and beliefs, whether subjects fall into the
+self-defeating equilibria or not is still informative of the updating
+procedure that they are using. Understanding if the presence of traps is
+a key feature preventing subjects from learning the optimal action is
+important for understanding the prevalence of overconfidence. Similarly,
+gaining insight into what happens when there are no traps is important
+for understanding what are the other reasons why overconfidence might
+arise and prevail.
+
+\hypertarget{switcher}{%
+\subsection{Switcher}\label{switcher}}
+
+Since the switcher starts as the same dogmatic agent, the initial
+behavior of both types of agents is identical, however, because the
+switcher is keeping track of the likelihood ratio, they will be able to
+escape the self-defeating equilibrium if the evidence is convincing
+enough. Therefore there is a positive probability that the switcher will
+adjust their initially misspecified belief about \(\theta\) and learn
+the true state.
+
+\textbf{Prediction 1S:} With positive probability, the switcher will
+escape the self-defeating equilibrium and learn the true state.
+
+One caveat is that when the switcher and the dogmatic agent both start
+with a correctly specified belief, neither of them will fall into the
+self-defeating equilibria and thus will look identical even in the long
+run. This means that in order to distinguish between the two theories, I
+need to look at cases where the agent starts with a misspecified belief.
+
+The probability that the switcher will escape the self-defeating
+equilibrium depends on the prior belief about \(\omega\). If the prior
+is sufficiently tight around the self-defeating equilibrium, the
+likelihood ratio will not grow fast enough, however, in the example
+above, the prior is uniform over the states and therefore, the
+likelihood ratio is more likely to grow fast enough.
+
+\hypertarget{self-attribution-bias}{%
+\subsection{Self-Attribution Bias}\label{self-attribution-bias}}
+
+The key feature of Self-attribution bias is the asymmetric treatment of
+good news and bad news. In particular, the agent will over-attribute
+successes to a high type and under-attribute them to a low type.
+Similarly, they will over-attribute failures to a low state and
+under-attribute them to a high state. This implies that, after observing
+a failure, the agent will adjust their effort downwards by more than
+what an unbiased Bayesian would have done. In contrast, after observing
+a success, the agent will adjust their effort upwards by less than a
+Bayesian would have done and if the bias is large enough, it could be
+that the agent will not adjust their effort upwards at all, or even
+decrease their effort in response to a success.
+
+This is in stark contrast with what a Dogmatic modeler would do. A
+dogmatic modeler always attributes any variation in the outcome to the
+state and never updates their beliefs about \(\theta\). Therefore, they
+will always increase their effort choices after a surprising success and
+decrease it after a failure.
+
+On the other hand, the biased behavior can be in line with the behavior
+of a switcher. In particular, if the agent starts with a misspecified
+belief on \(\hat{\theta}\), and is willing to switch to a belief with
+\(\theta'>\hat{\theta}\), whenever the paradigm shift happens, it will
+likely be in response to a surprising streak of successes. In this case,
+when they adjust their belief about \(\theta\), they will also adjust
+their effort choice. Since they were initially underconfident, they had
+been choosing an effort that was too high relative to the true state,
+and therefore, the effort is likely to fall in response to a surprising
+streak of success.
+
+\textbf{Prediction 1A:} \emph{After observing a failure, the agent will
+adjust their effort downwards by more than a Bayesian would have done.
+After observing a success, the agent will adjust their effort upwards by
+less than a Bayesian would have done. If the bias is large enough, the
+agent might not adjust their effort upwards at all, or even decrease
+their effort in response to a success.}
+
+Prediction 1A helps distinguish between the self-attribution bias and
+the dogmatic modeler. However, it does not help distinguish between the
+self-attribution bias and the switcher. In order to do so, I need to
+look at cases where the agent starts with a correctly specified belief.
+In these cases, the switcher is very unlikely to switch to a different
+belief and therefore, the behavior of the switcher will mostly change in
+the same direction as the information he receives.
+\footnote{If they get a streak of failures they are likely to 
+adjust their effort downwards and if they get a streak of successes they are likely to adjust their effort upwards.}
+Instead, the self-attribution bias will lead to a different behavior. In
+particular, even for agents who have a belief that is correctly
+specified and place a lot of weight on the correct values of \(\theta\),
+the bias will cause these agents to become overconfident after a
+sequence of successes. This force is not present in the switcher or the
+dogmatic and it is the key feature that allows me to identify a biased
+updating procedure.
+
+\textbf{Prediction 2A:} \emph{After observing a streak of successes, the
+agent will update their belief about \(\theta\) upwards. This will lead
+to the possibility of observing subjects who start correctly specified
+and become overconfident.}
+
+\hypertarget{the-bayesian-1}{%
+\subsection{The Bayesian}\label{the-bayesian-1}}
+
+The Bayesian serves as the closest benchmark to a fully rational agent.
+However, as discussed above, they are still vulnerable to falling into
+self-defeating equilibria, in which case, their long-run behavior will
+be identical to that of the dogmatic modeler. The main distinguishing
+feature is that when they do fall into a self-defeating equilibrium,
+there is no bias in the direction of the misspecification that they end
+up being trapped in. In contrast, the dogmatic modeler will always be
+trapped in a misspecified belief that they started with and the
+self-attribution updater will always become overconfident.
+
+\textbf{Prediction 1B:} \emph{When an agent starts with a diffused prior
+and falls into a self-defeating equilibrium, they will be equally likely
+to fall into the underconfident trap as the overconfident trap.}
+
+\textbf{Prediction 2B:} \emph{Bayesian agents always update their effort
+choices in the same direction as the information they receive. That is,
+if they see successes, they would only increase their effort; and if
+they see failures they would only decrease their effort.}
+
+\hypertarget{stereotypes}{%
+\section{Stereotypes}\label{stereotypes}}
+
+So far I have focused only on the case of overconfidence. However, each
+of the models can also be used to explain the prevalence of
+underconfidence. An agent can have a dogmatic belief about the ability
+of a particular group of people and either under or overestimate the
+associated parameter. Similarly, they can be willing to switch between
+two dogmatic beliefs about their ability as a switcher would. Finally,
+they can have a biased updating procedure in which they treat good news
+and bad news asymmetrically.
+
+As such, all the predictions discussed above apply to the case of
+Stereotypes as well. My analysis of stereotypes will focus only on the
+degree to which ego-relevance of the type affects the updating procedure
+and not on the motivations behind the bias. I am particularly interested
+in whether the explanatory power of the models differs with the degree
+of ego-relevance of the type.
+
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
+\hypertarget{initial-beliefs-and-misspecifications}{%
+\subsection{Initial Beliefs and
+misspecifications}\label{initial-beliefs-and-misspecifications}}
+
+As mentioned in the predictions section, the dogmatic modeler and the
+switcher are only distinguishable when the agent starts with a
+misspecified belief. Figure \ref{fig:misspecification-hist} shows the
+distribution of misspecifications by treatment. The histogram considers
+the difference between the subject's true score in the quiz and their
+guess about their score. If their guess is in a higher category than
+their true score, they are overconfident; if it is in a lower category,
+they are underconfident; and if it is in the same category, they are
+correctly specified. Overall, 0.43 of the guesses made in the
+questionnaire were misspecified. The rest of the guesses coincided with
+the true score. And the distribution of misspecifications is similar
+across treatments.
+
+\begin{figure}
+\hypertarget{fig:misspecification-hist}{%
+\centering
+\includegraphics{../figures/misspecification_hist.png}
+\caption{Initial misspecifications by
+treatment}\label{fig:misspecification-hist}
+}
+\end{figure}
+
+Although the overall distribution is similar for both treatments, the
+misspecifications arise for different combinations of characteristics in
+each treatment. Figure \ref{fig:misspecification-by-treatment} shows a
+heatmap of the misspecifications that arose in each treatment. In the
+stereotype treatment, subjects are most underconfident about the
+performance of other non-American females in Sports and Video Games. In
+contrast, they are most overconfident about the performance of American
+men in Verbal Reasoning. In the ego-relevant treatment, subjects are
+most underconfident about their own performance in pop culture and art,
+while most overconfident about their performance in Verbal Reasoning.
+
+\begin{figure}
+\hypertarget{fig:misspecification-by-treatment}{%
+\centering
+\includegraphics{../figures/misspecifications_characteristics_treatment.png}
+\caption{Initial misspecifications by treatment and
+characteristics}\label{fig:misspecification-by-treatment}
+}
+\end{figure}
+
+Having widespread misspecifications in both treatments is important for
+the analysis because it allows me to distinguish between the dogmatic
+modeler and the switcher. If there were no misspecifications, the two
+models would be indistinguishable.
+
+\hypertarget{learning}{%
+\subsection{Learning}\label{learning}}
+
+In this section, I analyze the learning behavior of subjects in the
+experiment. There are two parameters that subjects can be learning
+about: the exogenous parameter \(\omega\) and the type \(\theta\). Their
+belief about the exogenous parameter is tracked by their choice of
+effort, while their belief about the type is tracked by their choice of
+a matrix in which to enter their effort.
+
+\hypertarget{learning-about-the-state}{%
+\subsubsection{Learning about the
+state}\label{learning-about-the-state}}
+
+In order to analyze the learning about the state, I look at the share of
+optimal choices that are made at each round. I find that although
+subjects seem to be improving in their choices overall, the last choice
+coincided with the true state only in 52\% of the choices in the last
+round of each task. This is statistically greater than the initial share
+of optimal choices of 30\% (\(p<0.01\)). However, it is still far from
+complete learning. It is also important to note that learning is similar
+across treatments. The share of choices that were consistent with the
+true state for each round is reported in Figure
+\ref{fig:optimal-choices-by-round}.
+
+\begin{figure}
+\hypertarget{fig:optimal-choices-by-round}{%
+\centering
+\includegraphics{../figures/effort_learning.png}
+\caption{Share of optimal choices by
+round}\label{fig:optimal-choices-by-round}
+}
+\end{figure}
+
+A closer look at whether people learned or not reveals that there is a
+good amount of heterogeneity in the sample. Figure
+\ref{fig:learning-by-groups} shows the share of optimal choices by round
+for subjects that chose an effort that matched the state in 3 out of the
+last 4 rounds. It also shows the share of optimal choices for subjects
+who chose an effort that matched the state in fewer than 3 out of the
+last 4 rounds. I label the former as learners and the latter as
+non-learners, with learners making up 0\% of the sample.
+
+\begin{figure}
+\hypertarget{fig:learning-by-groups}{%
+\centering
+\includegraphics{../figures/learning_groups.png}
+\caption{Share of optimal choices by round for subjects who learned
+(their effort in at least 3 out of tha last 4 choices matched the
+state), and subjects who did not learn}\label{fig:learning-by-groups}
+}
+\end{figure}
+
+In what follows I will try to disentangle the reasons for the lack of
+learning. I will argue that it is not due to the presence of traps, but
+rather due to biased updating. According to the theories, the main
+reason why subjects might not learn is that they have an incorrect
+belief about the type or they develop an incorrect belief about the
+type.
+
+\hypertarget{learning-about-the-type}{%
+\subsubsection{Learning about the type}\label{learning-about-the-type}}
+
+\begin{figure}
+\hypertarget{fig:matrix-choices-by-round}{%
+\centering
+\includegraphics{../figures/last_button_consistency.png}
+\caption{Matrix choices by round}\label{fig:matrix-choices-by-round}
+}
+\end{figure}
+
+Since the elicitation of the belief about the type was not incentivized
+and not elicited in a standard way, I first need to confirm that
+subjects were not just randomly choosing a matrix in which to enter
+their effort. The left panel of Figure \ref{fig:matrix-choices-by-round}
+shows the share of subjects who chose a matrix consistent with their
+initial reported belief. In round 1, 71\% of the subjects chose a matrix
+that was consistent with their initial belief. This indicates that
+subjects were not just randomly choosing a matrix in which to enter
+their effort. From round 2 onwards, the share steadily declines, but
+still not as far as to indicate a random choice of matrices. This is
+consistent with the subjects moving away from their starting belief
+through some updating procedure.
+
+On the right panel of Figure \ref{fig:matrix-choices-by-round} I show
+the share of subjects who chose a matrix that is consistent with their
+true type. Unlike the left panel, there is no clear trend, which
+indicates that although they are moving away from their initial belief,
+they are not moving towards their true type, which means that overall,
+misspecification is not decreasing. A closer look at the data reveals a
+good amount of heterogeneity in the underlying behavior.
+
+Figure \ref{fig:transitions} shows the transition matrix for subjects
+who started in each of the 3 possible starting specifications and the
+specifications that they ended up in at the end of the updating task.
+The two things to note are that the initial belief is the most likely
+end belief. This is consistent with some degree of stickiness of the
+misspecifications as the switcher and dogmatic models would predict.
+However, the data also presents a lot of subjects who started with a
+correct belief of the type and ended up overestimating it. This is
+consistent only with the self-attribution bias. Lastly, the subjects who
+initially overestimate the score, are the least likely to learn their
+true type.
+
+\begin{figure}
+\hypertarget{fig:transitions}{%
+\centering
+\includegraphics{../figures/misspecification_transitions.png}
+\caption{Transition matrix for subjects who started in each of the 3
+possible starting specifications and the specification that they ended
+up in at the end of the updating task}\label{fig:transitions}
+}
+\end{figure}
+
+This transition matrix
+
+\hypertarget{reactions-to-good-and-bad-news}{%
+\subsection{Reactions to good and bad
+news}\label{reactions-to-good-and-bad-news}}
+
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
+
+\renewcommand\refname{References}
   \bibliography{references.bib}

### 2023-10-09 Paper/draft.Rmd
lab slides

@@
 \begin{table}[htbp]
+\centering
 
@@
 Sessions lasted approximately 
-45 minutes and subjects earned an average payment of $\$22.6$. The experiment was programmed using oTree [@chen2016otree].
+45 minutes and subjects earned an average payment of $\$22.6$. The experiment was programmed using oTree [@otree].
 
@@
 with the true state only in 52% of the choices in the last round of each task. This is statistically 
-greater than the initial share of optimal choices of 30% ($p<0.01$). However, it is still far from 
+greater than the initial share of optimal choices ($p<0.01$). However, it is still far from 
 complete learning. It is also important to note that learning is similar across treatments. The 
@@
 the last 4 rounds. I label the former as learners and the latter as non-learners, with learners making up
-`r round(sum(updates$learner)/nrow(updates), 2)*100`% of the sample.
+`r round(sum(updates$learned)/nrow(updates), 2)*100`% of the sample.
 
@@
 
-I look at the subjects who are updating in a task where the combination of $\theta$ and $\omega$ is such that
-there is a self-defeating equilibrium. I then look at how often
+Overall, it does not seem to be the presence of traps that is preventing learning. Figure \ref{fig:traps}
+shows that the share of subjects who learned in cases where there was a trap is larger than the share of
+subjects who learned in cases where there was no trap. This is true for both treatments. This indicates
+that even in the presence of traps, some people learn.
+
+![Share of subjects who learned in cases where there was a trap and in cases where there was no trap](../figures/learning_trap_presence.png){#fig:traps}
+
+A closer look at the behavior of only the cases in which there were traps reveals that among those who did not
+learn, the choices that support stable beliefs were chosen much more often than among subjects who learned. 
+Figure \ref{fig:traps-choice} shows the share of choices that were consistent with a stable belief for the
+learners and the non-learners. The difference is statistically significant ($p<0.01$). Thus, although the 
+presence of self-defeating equilibria is not the main deterrent to learning, it does seem to be a factor
+in the behavior of those who do not learn.
+
+![Share of choices that were consistent with a stable belief for the learners and the non-learners](../figures/trap_choice.png){#fig:traps-choice}
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+share_trapped <- round(sum(updates$trapped) / length(updates$trapped),2)
+```
+
+When looking a the behavior in the last 4 rounds of each task, only `r print(share_trapped)*100`% 
+of the subjects  
+were trapped\footnote{I consider a subject to be trapped if 3 out of the last 4 choices were consistent 
+with the self-defeating equilibrium} in a self-defeating equilibrium. These subjects could have been
+dogmatic, switchers for whom the likelihood did not grow fast enough, or Bayesian agents who fell into 
+a self-defeating equilibrium. The rest of the subjects were either updating their beliefs with a bias
+or were switchers.
+
+So far I have accounted for `r share_trapped*100`% subjects as being trapped, and 
+`r round(sum(updates$learned)/nrow(updates), 2)*100`%
+having learned the state correctly. From the remaining `r (1 - share_trapped - round(sum(updates$learned)/nrow(updates), 2))*100`%, 
+`r round(sum(updates$categorized=='neither' & updates$trap==1)/sum(updates$categorized=='neither'), 2)*100`% were prone to traps
+but did not fall into them, therefore they could not have been dogmatic modelers. Alternative explanations
+are that they were switchers who considered an incorrect alternative model, or that they were updating with a bias so large that their effort
+choices were far from optimal.
+
+In the following section, I look at indications of biased updating among all the groups identified so far.
 
@@
 
+One of the key features of the self-attribution bias is that the agent will react differently to good news and bad news.
+In particular, they will overreact to bad news and underreact to good news. I define good news to be any sample of outcomes
+for which the realized number of successes is greater than the average number of successes so far. Similarly, I define bad news to be
+any sample of outcomes for which the realized number of successes is smaller than the average number of successes so far.
+In addition, I calculate the difference between the realized number of successes and the average number of successes so far and
+call it the news differential.
+Figure \ref{fig:good-bad-news} shows the correlation between change in effort and the news differential, separately for 
+good and bad news.
+
+The overall pattern is that bad news are associated with a decrease in effort, and a 
+more negative news differential is associated with a larger decrease in effort. On the contrary, good news are associated with 
+a small decrease in effort. As mentioned in the predictions section, this is consistent with the self-attribution bias as well
+as with a change of paradigm. It is not consistent with the dogmatic modeler or the Bayesian. Because 
+I do not directly elicit beliefs, it is not possible to distinguish between the self-attribution bias and the change of 
+paradigm with this data alone.
+Nevertheless, the fact that about a third of the subjects started with a correctly specified belief and ended up overconfident
+is consistent only with the self-attribution bias. Therefore, I conclude that the self-attribution bias is the most likely
+explanation for the behavior of the subjects in the experiment.
+
+![Change in effort by news differential](../figures/effort_change_news.png){#fig:good-bad-news}
+
+A regression analysis of this same data reveals that indeed, the slopes are different for the two types 
+of news and that the difference is statistically significant ($p<0.01$). The regression results are reported in Table \ref{tab:regression}.
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE }
+reg <- lm(effort_change ~ good_news + news_diff + news_diff:good_news, data=updates[round_number>1,])
+robust_se <- sqrt(diag(vcovHC(reg)))
+
+# Attach the robust standard errors to the coefficient estimates
+coefs <- coef(reg)
+coefs <- cbind(coefs, robust_se)
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# run the regression only for treatment  = ego
+reg_ego <- lm(effort_change ~ good_news + news_diff + news_diff:good_news, data=updates[round_number>1 & treatment == 'ego',])
+
+# Attach the robust standard errors to the coefficient estimates
+coefs_ego <- coef(reg_ego)
+coefs_ego <- cbind(coefs_ego, robust_se)
+
+# run the regression only for treatment  = stereotype
+reg_stereotype <- lm(effort_change ~ good_news + news_diff + news_diff:good_news, data=updates[round_number>1 & treatment == 'stereotype',])
+
+# Attach the robust standard errors to the coefficient estimates
+coefs_stereotype <- coef(reg_stereotype)
+coefs_stereotype <- cbind(coefs_stereotype, robust_se)
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+# report reg, reg_ego, reg_stereotype in different columns using stargazer
+
+stargazer(reg, reg_ego, reg_stereotype, 
+title='Regression of effort change on news differential', 
+          dep.var.labels='Change in effort', 
+          covariate.labels=c('Good News', 'News differential', 'News Differential * Good News'),
+          column.labels=c('All', 'Ego-relevant', 'Stereotype'), 
+          omit.stat=c('f', 'ser'), 
+          digits=2, 
+          label='tab:regression', 
+          header=FALSE, 
+          se = list(coefs[, 2], coefs_ego[, 2], coefs_stereotype[, 2]))
+```
+
+# Structural estimation
+
+## Model fit
+
 # Conclusion
 
+I  designed a setting in which I can distinguish between the forces of dogmatism, paradigm shifts, and optimal expectations.
+Through a laboratory experiment, I collected data on behavior and infer beliefs from it. I find that 
+the behavior of the subjects is consistent with the self-attribution bias. In particular, I find that 
+subjects decrease their effort in response to bad news as well as to bad news, although the latter decrease 
+is smaller. This is consistent with the self-attribution bias as well as with a change of paradigm. However,
+I also observe that about a third of the subjects started with a correctly specified belief and ended up
+overconfident. This is consistent only with the self-attribution bias. Therefore, I conclude that the
+model that best explains the data is that of optimal expectations.
+
+I have small or no effects throughout on the ego-relevance of the type. Although the motivation behind the 
+theories does not directly apply to the case of stereotypes, the lack of stark differences suggest that 
+biases arise due to an incorrect updating procedure and not necessarily due to the self-serving motivation 
+behind the bias. The lack of differences in the behavior of the subjects across treatments could also 
+be due to self-censoring of the subjects. In particular, subjects might be initially reluctant to 
+express their true belief about a particular group of people. In addition, as they learn and realize 
+that their beliefs might be incorrect, they might overreact to signals to try to compensate for the initial 
+bias. Such an updating procedure would be consistent with the self-attribution bias for the case of sterotypes.
+I remain agnostic about whether that is truly the case or whether the lack of differences is due to other 
+factors.
+
+Another bias that has been studied and suggested in the literature is the confirmation bias. In particular,
+it has been suggested that subjects who are overestimate $\theta$ in their prior, will over-attribute 
+successes to a high type and under-attribute them to a low type. Symmetrically, subjects who initially 
+underestimate $\theta$ will over-attribute failures to a low type and under-attribute them to a high type.
+I do not find evidence of such a bias in the data. This is consistent with what @Mobius2022 find in their
+experiment.
+
+I further investigate possible heterogeneity in the underlying models being used by estimating the 
+structural parameters of the models.
+
 # References

### 2023-10-09 Paper/draft.tex
lab slides

@@
 \author{Jimena Galindo}
-\date{October 07, 2023}
+\date{October 08, 2023}
 
@@
 45 minutes and subjects earned an average payment of \(\$22.6\). The
-experiment was programmed using oTree \citep{chen2016otree}.
+experiment was programmed using oTree \citep{otree}.
 
@@
 round of each task. This is statistically greater than the initial share
-of optimal choices of 30\% (\(p<0.01\)). However, it is still far from
-complete learning. It is also important to note that learning is similar
-across treatments. The share of choices that were consistent with the
-true state for each round is reported in Figure
+of optimal choices (\(p<0.01\)). However, it is still far from complete
+learning. It is also important to note that learning is similar across
+treatments. The share of choices that were consistent with the true
+state for each round is reported in Figure
 \ref{fig:optimal-choices-by-round}.
@@
 last 4 rounds. I label the former as learners and the latter as
-non-learners, with learners making up 0\% of the sample.
+non-learners, with learners making up 39\% of the sample.
 
@@
 
-This transition matrix
+The transition matrix points towards the presence of self-attribution
+bias in the data. However, it is still possible that there is
+heterogeneity in the updating procedure across subjects. In the next
+section I will look at the role of self-defeating equilibria in
+preventing learning. I find that the presence of self-defeating
+equilibria does not seem to be the main deterrent to learning.
+
+\hypertarget{learning-traps}{%
+\subsection{Learning traps}\label{learning-traps}}
+
+As described above, the presence of stable misspecified beliefs act as
+learning traps. If an agent falls into one of these traps, bayesian
+updating will lead them to choose the same effort forever. These
+self-defeating equilibria allow me to distinguish between the dogmatic
+modeler and the switcher. If the agent falls into a trap and stays there
+forever, they are more likely to be a dogmatic modeler. If they escape
+the trap, they are more likely to be a switcher or to be updating with
+some attribution bias.
+
+Overall, it does not seem to be the presence of traps that is preventing
+learning. Figure \ref{fig:traps} shows that the share of subjects who
+learned in cases where there was a trap is larger than the share of
+subjects who learned in cases where there was no trap. This is true for
+both treatments. This indicates that even in the presence of traps, some
+people learn.
+
+\begin{figure}
+\hypertarget{fig:traps}{%
+\centering
+\includegraphics{../figures/learning_trap_presence.png}
+\caption{Share of subjects who learned in cases where there was a trap
+and in cases where there was no trap}\label{fig:traps}
+}
+\end{figure}
+
+A closer look at the behavior of only the cases in which there were
+traps reveals that among those who did not learn, the choices that
+support stable beliefs were chosen much more often than among subjects
+who learned. Figure \ref{fig:traps-choice} shows the share of choices
+that were consistent with a stable belief for the learners and the
+non-learners. The difference is statistically significant (\(p<0.01\)).
+Thus, although the presence of self-defeating equilibria is not the main
+deterrent to learning, it does seem to be a factor in the behavior of
+those who do not learn.
+
+\begin{figure}
+\hypertarget{fig:traps-choice}{%
+\centering
+\includegraphics{../figures/trap_choice.png}
+\caption{Share of choices that were consistent with a stable belief for
+the learners and the non-learners}\label{fig:traps-choice}
+}
+\end{figure}
+
+When looking a the behavior in the last 4 rounds of each task, only 16\%
+of the subjects\\
+were
+trapped\footnote{I consider a subject to be trapped if 3 out of the last 4 choices were consistent 
+with the self-defeating equilibrium} in a self-defeating equilibrium.
+These subjects could have been dogmatic, switchers for whom the
+likelihood did not grow fast enough, or Bayesian agents who fell into a
+self-defeating equilibrium. The rest of the subjects were either
+updating their beliefs with a bias or were switchers.
+
+So far I have accounted for 16\% subjects as being trapped, and 39\%
+having learned the state correctly. From the remaining 45\%, 60\% were
+prone to traps but did not fall into them, therefore they could not have
+been dogmatic modelers. Alternative explanations are that they were
+switchers who considered an incorrect alternative model, or that they
+were updating with a bias so large that their effort choices were far
+from optimal.
+
+In the following section, I look at indications of biased updating among
+all the groups identified so far.
 
@@
 
+One of the key features of the self-attribution bias is that the agent
+will react differently to good news and bad news. In particular, they
+will overreact to bad news and underreact to good news. I define good
+news to be any sample of outcomes for which the realized number of
+successes is greater than the average number of successes so far.
+Similarly, I define bad news to be any sample of outcomes for which the
+realized number of successes is smaller than the average number of
+successes so far. In addition, I calculate the difference between the
+realized number of successes and the average number of successes so far
+and call it the news differential. Figure \ref{fig:good-bad-news} shows
+the correlation between change in effort and the news differential,
+separately for good and bad news.
+
+The overall pattern is that bad news are associated with a decrease in
+effort, and a more negative news differential is associated with a
+larger decrease in effort. On the contrary, good news are associated
+with a small decrease in effort. As mentioned in the predictions
+section, this is consistent with the self-attribution bias as well as
+with a change of paradigm. It is not consistent with the dogmatic
+modeler or the Bayesian. Because I do not directly elicit beliefs, it is
+not possible to distinguish between the self-attribution bias and the
+change of paradigm with this data alone. Nevertheless, the fact that
+about a third of the subjects started with a correctly specified belief
+and ended up overconfident is consistent only with the self-attribution
+bias. Therefore, I conclude that the self-attribution bias is the most
+likely explanation for the behavior of the subjects in the experiment.
+
+\begin{figure}
+\hypertarget{fig:good-bad-news}{%
+\centering
+\includegraphics{../figures/effort_change_news.png}
+\caption{Change in effort by news differential}\label{fig:good-bad-news}
+}
+\end{figure}
+
+A regression analysis of this same data reveals that indeed, the slopes
+are different for the two types of news and that the difference is
+statistically significant (\(p<0.01\)). The regression results are
+reported in Table \ref{tab:regression}.
+
+\begin{table}[!htbp] \centering 
+  \caption{Regression of effort change on news differential} 
+  \label{tab:regression} 
+\begin{tabular}{@{\extracolsep{5pt}}lccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-4} 
+\\[-1.8ex] & \multicolumn{3}{c}{Change in effort} \\ 
+ & All & Ego-relevant & Stereotype \\ 
+\\[-1.8ex] & (1) & (2) & (3)\\ 
+\hline \\[-1.8ex] 
+ Good News & $-$0.12$^{**}$ & $-$0.16$^{***}$ & $-$0.05 \\ 
+  & (0.05) & (0.05) & (0.05) \\ 
+  & & & \\ 
+ News differential & 0.22$^{***}$ & 0.22$^{***}$ & 0.21$^{***}$ \\ 
+  & (0.02) & (0.02) & (0.02) \\ 
+  & & & \\ 
+ News Differential * Good News & $-$0.27$^{***}$ & $-$0.25$^{***}$ & $-$0.29$^{***}$ \\ 
+  & (0.02) & (0.02) & (0.02) \\ 
+  & & & \\ 
+ Constant & 0.31$^{***}$ & 0.31$^{***}$ & 0.30$^{***}$ \\ 
+  & (0.04) & (0.04) & (0.04) \\ 
+  & & & \\ 
+\hline \\[-1.8ex] 
+Observations & 4,680 & 2,700 & 1,980 \\ 
+R$^{2}$ & 0.04 & 0.04 & 0.04 \\ 
+Adjusted R$^{2}$ & 0.04 & 0.04 & 0.04 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
+
+\hypertarget{structural-estimation}{%
+\section{Structural estimation}\label{structural-estimation}}
+
+\hypertarget{model-fit}{%
+\subsection{Model fit}\label{model-fit}}
+
 \hypertarget{conclusion}{%
@@
 
+I designed a setting in which I can distinguish between the forces of
+dogmatism, paradigm shifts, and optimal expectations. Through a
+laboratory experiment, I collected data on behavior and infer beliefs
+from it. I find that the behavior of the subjects is consistent with the
+self-attribution bias. In particular, I find that subjects decrease
+their effort in response to bad news as well as to bad news, although
+the latter decrease is smaller. This is consistent with the
+self-attribution bias as well as with a change of paradigm. However, I
+also observe that about a third of the subjects started with a correctly
+specified belief and ended up overconfident. This is consistent only
+with the self-attribution bias. Therefore, I conclude that the model
+that best explains the data is that of optimal expectations.
+
+I have small or no effects throughout on the ego-relevance of the type.
+Although the motivation behind the theories does not directly apply to
+the case of stereotypes, the lack of stark differences suggest that
+biases arise due to an incorrect updating procedure and not necessarily
+due to the self-serving motivation behind the bias. The lack of
+differences in the behavior of the subjects across treatments could also
+be due to self-censoring of the subjects. In particular, subjects might
+be initially reluctant to express their true belief about a particular
+group of people. In addition, as they learn and realize that their
+beliefs might be incorrect, they might overreact to signals to try to
+compensate for the initial bias. Such an updating procedure would be
+consistent with the self-attribution bias for the case of sterotypes. I
+remain agnostic about whether that is truly the case or whether the lack
+of differences is due to other factors.
+
+Another bias that has been studied and suggested in the literature is
+the confirmation bias. In particular, it has been suggested that
+subjects who are overestimate \(\theta\) in their prior, will
+over-attribute successes to a high type and under-attribute them to a
+low type. Symmetrically, subjects who initially underestimate \(\theta\)
+will over-attribute failures to a low type and under-attribute them to a
+high type. I do not find evidence of such a bias in the data. This is
+consistent with what \citet{Mobius2022} find in their experiment.
+
+I further investigate possible heterogeneity in the underlying models
+being used by estimating the structural parameters of the models.
+
 \renewcommand\refname{References}

### 2023-10-09 Paper/parameters_and_packages.R

@@ -9,6 +9,7 @@ library(reticulate)
 library(car) # for linearHypothesis
 library(lmtest) # for coefTest
 library(sandwich) # for clustering errors
+library(stargazer) # for regression tables
 
 # keep the packages synced with the lockfile
 invisible(capture.output(renv::snapshot()))

### 2023-10-10 Paper/draft.Rmd
corrections in slides

@@
 
-## Related literature
+Overconfidence has been documented in a wide range of settings and has been shown to have important economic consequences:
+@Camerer1999 find that overconfidence can explain the excessive entry of entrepreneurs into the market; @Hoffman2020 show that
+workers who overestimate their productivity within a firm are less likely to look for a new job; @Oster2013 determine that 
+people at high risk of Huntington's disease make saving decisions as if they were not at risk.
+
+Although the bias has been widely studied by economists, the settings in which 
+the the belief updating procedure has been studied is narrow in scope. In particular, the literature has focused on
+the cases in which the agent updates their beliefs about a single characteristic that they might care about.
+For instance, @Eil2011 study the case in which the agent updates their beliefs about their own ability, and their 
+own beauty in two separate experiments. Similarly, @Benoit2015 study the case in which the agent updates their 
+beliefs about their own IQ.
 
@@
 
-I consider multiple theories of belief updating that have been proposed in the literature and that are able to rationalize
+I consider multiple theories of belief updating that have been proposed in the literature to rationalize
 the prevalence of misspecified beliefs. I focus on two different frameworks and develop a unifying example that allows me to
-compare the predictions of all the theories. In this section, I outline the theories within each of the frameworks.
+compare the predictions of all the theories. In framework 1 I consider a setting in which the an agent observes
+a continuous output and infers the underlying state. In framework 2, the agent observes a binary outcome and infers the
+underlying probability of success. In both frameworks, I consider two nested theories of belief updating.
 
@@
 density $f$ over $\Omega$. The agent knows the 
-distribution of $\omega$ but not its realized value. His prior belief about his type is $p_0(\theta)$ and his belief about the state, 
-$p_0(\omega)$, coincides with the true distribution. Let the agent's true type be $\theta^{*}$,  and the realized state be $\omega^{*}$.
+distribution of $\omega$ but not its realized value. His belief about the state, 
+$p_0(\omega)$, coincide with the true distribution, $f$; and his belief about the type is $p_0(\theta)$. 
+Let the agent's true type be $\theta^{*}$,  and the realized state be $\omega^{*}$.
 
-An agent has a \emph{misspecified} belief if the prior assigns probability zero to their true type. Furthermore, the agent is 
-\emph{dogmatic} if he holds a degenerate belief that places probability one on being a particular type, $\hat{\theta}$. An 
-agent can be dogmatic and misspecified. If the agent is both, $\hat{\theta} \neq \theta^*$ and $p_0(\hat{\theta}) = 1$.
+An agent's belief about the type is \emph{misspecified} if it assigns probability zero to their true type. Furthermore, the agent is 
+\emph{dogmatic} if he holds a degenerate belief that places probability one on being of type $\hat{\theta}$. An 
+agent can be dogmatic and misspecified, in which case $\hat{\theta} \neq \theta^*$ and $p_0(\hat{\theta}) = 1$.
 
-The agent chooses an action $a\in A$ and observes a noisy outcome $h\in H$. 
+The agent chooses an action $a\in A$ and observes a noisy outcome $h$. 
 The outcome is a function of the agent's type, the state, and
@@
 and such that conditional on a pair of parameters $(\theta, \omega)$, there is a unique optimal action. 
-$\varepsilon\sim N(0, \sigma)$ is noise in the output.
+additionally, $\varepsilon\sim N(0, \sigma)$ is noise in the output.
 
@@
 that maximizes the payoff in each period. This assumption simplifies the analysis and plays a role in whether an agent who updates
- their beliefs using Bayes rule would learn the truth or not. The behavior of a forward-looking agent is discussed in the conclusion.
+ their beliefs using Bayes rule would learn the truth or not, however, for the main theory discussed in this section, the results hold
+ even when relaxing this assumption. The behavior of a forward-looking agent is further discussed in the conclusion.
 
 A key notion in this setting is that of a self-defeating equilibrium\footnote{This notion is an adaptation of the Berk-Nash equilibrium in 
-@Esponda2016 to this setting with only one agent}. 
+\citet{Esponda2016} to this setting with only one agent}. 
 A \emph{self-defeating equilibrium} is a belief and action pair such that the agent's belief about their type is misspecified and the 
@@
 The second one is a switcher, as in @Ba2023. The dogmatic modeler can be seen as a switcher with an infinitely sticky initial belief
-and this is the sense in which the two are nested. Both theories produce different predictions about the agent's behavior. I discuss both 
-in what follows.
+so the two theories are nested. However, outside of the limiting case, they produce different 
+predictions about the agent's behavior. I discuss each of them separately in what follows.
 
 ### The Dogmatic Modeler
+
+Take the action space to be the same as the state space $\Omega$ and  $\Omega =A=[\underline{a}, \infty)$.
 
@@
 In this case, no matter
-how much information he gathers against being of type $\hat{\theta}$, he will not update his beliefs about $\theta$. 
+how much information he gathers against being of type $\hat{\theta}$, he will not update his beliefs about it. 
 Any discrepancies between the 
-observed outcomes and his believed type are incorporated using the Bayes rule to update their beliefs about $\omega$.
+observed outcomes and his believed type are incorporated using the Bayes rule to update his beliefs about $\omega$.
 @Heidhues2018 show that, under certain assumptions on the per-period utility,\footnote{The assumptions are that 
-$u$ is twice continuously differentiable with: (i)$u_{ee}<0$ and $u_e(\underline{e} \theta, \omega)>0>u_e(\Bar{e}, \theta, \omega)$, 
-(ii) $u_{\theta}, u_{\omega}>0$ and (iii) $u_{e\theta}<0$ and $u_{e\omega}>0$. The direction of the derivatives is a normalization
+$u$ is twice continuously differentiable with: (i)$u_{aa}<0$ and $u_a(\underline{a},  \theta, \omega)>0>u_a(\Bar{a}, \theta, \omega)$, 
+(ii) $u_{\theta}, u_{\omega}>0$ and (iii) $u_{a\theta}<0$ and $u_{a\omega}>0$. Where $\underline{a}$ is the
+minimal action and $\Bar{a}$ is the maximal one. 
+ The direction of the derivatives is a normalization
 and the results would hold even when the signs are reversed.} 
@@
 There are two 
-possible sources for the disappointment, the first is that the realized state is lower than the expected state. The second source is that the
+possible sources for the disappointment: the first is that the realized state is lower than the expected state; the second source is that the
 agent is of type $\theta^*$ and therefore, for all possible states, his gain will be lower than what he expected. Because the agent is dogmatic,
@@
 as $\omega_\infty$.
-This mechanism is further illustrated in Example 1.
+This mechanism is illustrated in Example 1.
 
 **Example 1: ** 
-_Set $A = \Omega$ and $H = [0, \infty)$ and consider a student with intrinsic ability $\theta^*\geq 0$ who faces a grading procedure 
-$\omega^*$ that is unknown to them. However, 
-they know that a higher $\omega^*$ is more likely to yield a higher grade. In particular, assume the grade is given by 
+_Set $A = \Omega=[\underline{a}, \infty)$ and consider a student with intrinsic ability $\theta^*\geq 0$ who faces a grading procedure 
+$\omega^*$ that is unknown to them. 
+The student knows that a higher $\omega^*$ is more likely to yield a higher grade. In particular, she knows the grade is given by 
 $(\theta^*+a)\omega^*$._
 
-_The student must choose an effort level $a$, which determines their grade. For whatever the chosen effort level, 
-the agent must pay a cost $c(a) = \frac{1}{2}a^2$. And he repeats this process for infinitely many periods. 
-Assume also that the student's prior is such that $mathbb{E}[\omega]= \omega^*$ and he is dogmatic about being of 
-type $\hat{\theta}>\theta^*$. \footnote{The example is illustrated for an overconfident agent but the results are symmetric for a digmatic agent who initially 
+_The student must choose an effort level $a$, which determines her grade. For whatever the chosen effort level, 
+the student must pay a cost $c(a) = \frac{1}{2}a^2$ and receives a grade of $(\theta^*+a)\omega^*$. She repeats 
+this process for infinitely many periods. 
+Assume also that the student's prior is such that $\mathbb{E}[\omega]= \omega^*$ and she is dogmatic 
+about being of 
+type $\hat{\theta}>\theta^*$.\footnote{The example is illustrated for an overconfident student but 
+the results are symmetric for a dogmatic student who initially 
 places probability one on some $\tilde{\theta}<\theta^*$.}
@@
 
-_Under this specification, the myopic optimal effort level is $a_t^* = \omega^*$. Nonetheless, because the agent does not know $\omega^*$,
-he will choose $a_t = \mathbb{E}_t(\omega)$ where the expectation is taken with respect to the agent's belief at the beginning of
-period $t$. If he does not revise his effort choice for $k$ periods, he will receive 
+_Under this specification, the myopic optimal effort level is $a_t^* = \omega^*$. 
+Because the student does not know $\omega^*$,
+he will choose $a_t = \mathbb{E}_t(\omega)$ where the expectation is taken with respect to the 
+student's belief at the beginning of
+period $t$. If she does not revise his effort choice for $k$ periods, she will receive 
 an average utility of 
 $(\theta^*+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}$ but he was expecting an average utility of 
-$(\hat{\theta}\theta+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}$. In response, he will apply Bayes rule to update his beliefs about
-$\omega$ to get the posterior belief with $\mathbb{E}_{t+k}[\omega] = \frac{(\theta^{*} + \omega^{*})\omega^{*}}{\hat{\theta} + \omega^{*}}$
-which is lower than the initial belief. This will cause the agent to choose a lower effort at $t+k$. As a result, he will again
-receive an average utility that is lower than what he expected which will cause his belief to drift further down. This process will
-continue until the average utility equals his expected utility under the dogmatic belief that assigns probability 1 to $\hat{\theta}$. 
-At that point, the student will have reached a self-defeating equilibrium and he will continue to choose sub-optimal effort forever. _
+$(\hat{\theta}\theta+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}$. In response, she will apply Bayes 
+rule to update his beliefs about
+$\omega$ to get the posterior belief with 
+$\mathbb{E}_{t+k}[\omega] = \frac{(\theta^{*} + \omega^{*})\omega^{*}}{\hat{\theta} + \omega^{*}}$
+which is lower than the initial belief. This will cause the student to choose a lower effort at $t+k$. As a result, she will again
+receive an average utility that is lower than what he expected which will cause her belief to drift further down. This process will
+continue until the average utility equals her expected utility under the dogmatic belief that assigns probability 1 to $\hat{\theta}$. 
+At that point, the student will have reached a self-defeating equilibrium and she will continue to choose sub-optimal effort forever. _
 
 Although the model of a dogmatic modeler rationalizes the prevalence of overconfident (underconfident) beliefs, the
-assumption that the agent has a degenerate belief and no mechanism through which he can update such belief is very restrictive. An
-alternative approach is proposed by @Ba2023. She proposes an extension of the dogmatic agent who is able to jump from one dogmatic 
-belief to another. By doing so, the agent might end up being dogmatic and correctly specified.
+assumption that the agent has a degenerate belief and no mechanism through which he can update such 
+belief is very restrictive. An
+alternative approach is proposed by @Ba2023. She proposes an extension of the dogmatic agent who 
+is able to swithch from one dogmatic 
+belief to another. By doing so, the agent can avoid the self-defeating equilibria and end up being dogmatic and correctly specified.
 
@@
 
-An agent is a \emph{switcher} if they behave as a dogmatic, but is willing to entertain the possibility that they are of a different type.
+An agent is a \emph{switcher} if they behave as a dogmatic, but are willing to entertain the possibility that they are of a different type.
 In particular, when they start off as a misspecified dogmatic, they are willing to switch to a different dogmatic belief if the data is
@@
 
-Where $h^t$ is the history of outcomes up to time $t$ and $\alpha$ is the switching threshold. By keeping track of the 
+Where $h^t$ is the history of outcomes up to time $t$ and $\alpha$ is the switching threshold.\footnote{Notice that if $\alpha \to \infty$, the behavior of the switcher will be indistinguishable from that of the Dogmatic modeler.
+In this sense, the switcher is a generalization of the dogmatic type.} By keeping track of the 
 likelihood ratio, the agent can perform a \emph{Bayesian hypothesis test} and adopt the Dogmatic belief that best fits 
-the data.\footnote{In a related problem @Schwarstein2021 proposes a similar updating procedure which relies on the Bayesian 
+the data.\footnote{In a related problem \citet{Schwarstein2021} proposes a similar updating procedure which relies on the Bayesian 
 hypothesis test. However, in their model there is a sender who optimally chooses to propose a model that fits the data}
-Notice that if $\alpha \to \infty$, the behavior of the switcher will be indistinguishable from that of the Dogmatic modeler. 
-In this sense, the switcher is a generalization of the dogmatic type.
 
 By allowing the agent to keep track of the likelihoods and switching to an alternative type, the switcher can avoid the 
-self-confirming equilibrium. However, if the prior belief on $omega$ is sufficiently tight around
+self-confirming equilibria. However, if the prior belief on $omega$ is sufficiently tight around
 a self-defeating equilibrium, the switcher might look identical to the dogmatic even in a case where $\alpha$ is not too large.
@@
 $a\in A$
-and observes a binary outcome that is either a success or a failure. Denote the outcome by $o \in {s,f}$. The probability of 
-observing a success is increasing in $\theta^*$ and in $\omega$. Whenever the agent observes a success, he gets a payoff $v>0$ and
+and observes a binary outcome that is either a success or a failure. Denote the outcome by $o \in \{s,f\}$. The probability of 
+observing a success is increasing in $\theta$ and in $\omega$. Whenever the agent observes a success, he gets a payoff $v>0$ and
 whenever the outcome is a failure, the payoff is 0.  In addition, the probability of success is such that for each state, 
@@
 A Bayesian agent simultaneously updates their beliefs about $\theta$ and $\omega$ by using Bayes' rule. 
-The posterior at period t+1 about $\theta$ after observing a history of outcomes $h^t$ is given by:
+The posterior at period t+1 about $\theta$ after observing outcom $o$ is given by:
 $$
-p_{t+1}(\theta, \omega| h^t) = \frac{p[h^t|\theta, \omega]p_t(\theta, \omega)}{\sum_{(\theta', \omega')}p[h^t|\theta', \omega']p_t(\theta', \omega')}
+p_{t+1}(\theta, \omega| h^t) = \frac{p[o|\theta, \omega]p_t(\theta, \omega)}{\sum_{(\theta', \omega')}p[o|\theta', \omega']p_t(\theta', \omega')}
 $$
 
-Where $p_{t}$ is the belief at the start of period $t+1$. The update is symmetric for $\omega$.
+Where $p_{t}$ is the belief at the start of period $t+1$ and includes all the information gathered so far.
 
@@
 their prior beliefs about $\theta$ and $\omega$. Since agents are myopic, even though all the parameters 
-could be identified with enough variation in choices. Although the Bayesian agent is the closest to a 
-fully rational agent discussed here, 
-they might not learn their true type. This happens because, by being myopic, they do not internalize 
+could be identified with enough variation in choices, there will be instances in which the Bayesian will not
+learn even with infinite amounts of data. This happens because, by being myopic, they do not internalize 
 the tradeoff between flow payoff
 and learning. This can result in too little experimentation to learn their true type. An alternative to this approach is given 
-by @Hestermann2021 and is discussed in the concluding remarks.
+by @Hestermann2021 and is discussed in the concluding remarks. Regardless, this approach is useful as a 
+benchamrk for the other theories discussed in this paper.
 
@@
 
-A self-serving Bayesian is an agent who uses a biased version of Bayes rule to update their beliefs. 
+A Self-Serving Bayesian is an agent who uses a biased version of Bayes rule to update their beliefs. 
 They will update their beliefs 
@@
 This formulation of the bias means that the agent will over-attribute successes to a high type and 
-under-attribute them to a low type. Whereas they will over-attribute failures to a low state and
-under-attribute them to a high state. The parameter $c$ determines the degree of bias and the restriction on the 
-order ensures that the model is still falsifiable.
+under-attribute them to a low type Whereas they will over-attribute failures to a low state and
+under-attribute them to a high state. The bias is introduced by distorting the perceived likelihood 
+that the signal was generated by either high values of $\theta$ when it is a success, or by low 
+values of $\omega$ when it is a failure.  The parameter $c$ determines the degree of bias and imposes
+enough restrictions to ensure that the model is still falsifiable.
 
@@
 In order to compare the predictions of the theories discussed above, I develop a unifying example that allows me to
-isolate the forces behind each of the theories. The example is a modification of the one in @Heidhues2018 and is adapeted to 
-be easier to implement in the lab.
+isolate the forces behind each of the theories. The example is a modification of the one in @Heidhues2018 and is adapted to 
+implementable in the lab.
 
@@
 
-Denote the true type by $\theta^*$ and the true state by $\omega^*$. The agent holds some prior belief about $\theta$ 
-\footnote{which is potentially misspecified as in the dogmatic and switcher cases discussed above} 
+Denote the true type by $\theta^*$ and the true state by $\omega^*$. The agent holds some prior belief about 
+$\theta$\footnote{which is potentially misspecified as in the dogmatic and switcher cases discussed above} 
 and chooses a binary gamble $e in \{e_L, e_M, e_H\}$. The agent observes whether the gamble is a success or a failure and 
@@
 
-The probability of success is increasing in both $\theta$ and $\omega$ and is fully described by the following table:
+The probability of success is increasing in both $\theta$ and $\omega$ and is fully described by the Table \ref{tab:DGP}
 
@@
 \caption{Probability of success for each type, gamble and effort level}
-\label{tab:table1}
+\label{tab:DGP}
 \end{table}
@@
 them to choose different gambles. I exploit such cases in order to test which model is a better fit for how subjects behave in a 
-laboratory experiment. \footnote{because the setting does not match that of Heidhues et al. [2018], there will be situationf for which the theory 
+laboratory experiment.\footnote{because the setting does not match that of @Heidhues2018, there will be situations for which the theory 
 does not provide a prediction. If such cases arise in the lab, they will not be used for the analysis. However, whether a misspecified 
@@
 
-I recruited `r print(unique(updates$code))` undergraduate subjects from the CESS lab at NYU who participated in an in-person experiment. 
+I recruited `r length(unique(updates$code))` undergraduate subjects from the CESS lab at NYU who participated in an in-person experiment. 
 Sessions lasted approximately 
@@
 Randomness is controlled throughout the experiment and sessions by setting a seed at the beginning of the
-first session. The seed was drawn at random and remained fixed for all sessions. \footnote{The seed that was drawn 
+first session. The seed was drawn at random and remained fixed for all sessions.\footnote{The seed that was drawn 
 at the beginning of session 1 was 3452. The same seed was used for all sessions. It is used both for drawing $\omega$ for each of 
@@
 By doing this I ensure that any two subjects who have the same type and face the same exogenous rate will observe
-the same outcomes and thus, if they use the same updating procedure, they should be choosing the same gambles. 
-This design feature allows me to identify differences in updating procedures across subjects.
+the same outcomes. This feature allows me to identify differences across subjects in updating procedures since if they use the same 
+updating procedure, they should be choosing the same gambles.
 
@@
 
-In this section, I outline the behavior that is predicted by each of the theories discussed above. I start with the dogmatic modeler.
+In this section, I outline the behavior that is predicted by each of the theories discussed above.
 
@@
 
-So far I have focused only on the case of overconfidence. However, each of the models can also be used to explain the prevalence
-of underconfidence. An agent can have a dogmatic belief about the ability of a particular group of people and either under or overestimate
+So far I have focused only on the case of overconfidence about an ego-relevant parameter. 
+However, each of the models can also be used to explain the prevalence
+of stereotypes. An agent can have a dogmatic belief about the ability of a particular group of people and either under or overestimate
 the associated parameter. Similarly, they can be willing to switch between two dogmatic beliefs about their ability as a switcher would.
@@
 complete learning. It is also important to note that learning is similar across treatments. The 
-share of choices that were consistent with the true state for each round is reported in Figure \ref{fig:optimal-choices-by-round}.
-
-![Share of optimal choices by round](../figures/effort_learning.png){#fig:optimal-choices-by-round}
+share of choices that were consistent with the true state for each round is reported in panel A of 
+Figure \ref{fig:learning-by-groups}.
 
 A closer look at whether people learned or not reveals that there is a good amount of heterogeneity in the
-sample. Figure \ref{fig:learning-by-groups} shows the share of optimal choices by round for 
+sample. Panel B of Figure \ref{fig:learning-by-groups} shows the share of optimal choices by round for 
 subjects that chose an effort that matched the state in 3 out of the last 4 rounds. It also shows the 
@@
 
-Overall, it does not seem to be the presence of traps that is preventing learning. Figure \ref{fig:traps}
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+numerator <- length(unique(updates$player_code[updates$trap == 1 & updates$learned == 1]))
+
+# Calculate the denominator
+denominator <- length(unique(updates$player_code[updates$trap == 1]))
+
+# Calculate the ratio
+share_learned <- round(numerator / denominator, 2)
+
+numerator <- length(unique(updates$player_code[updates$trap == 1 & updates$trapped == 1]))
+
+# Calculate the denominator
+denominator <- length(unique(updates$player_code[updates$trap == 1]))
+
+# Calculate the ratio
+share_trapped <- round(numerator / denominator, 2)
+```
+
+Overall, it does not seem to be the presence of traps that is preventing learning. Panel A of Figure \ref{fig:traps-choice}
 shows that the share of subjects who learned in cases where there was a trap is larger than the share of
 subjects who learned in cases where there was no trap. This is true for both treatments. This indicates
-that even in the presence of traps, some people learn.
-
-![Share of subjects who learned in cases where there was a trap and in cases where there was no trap](../figures/learning_trap_presence.png){#fig:traps}
+that even in the presence of traps, `r share_learned*100`% of subjects learn. From the share that 
+did not learn when there was a trap. A remaining `r share_trapped*100`% can be accounted for as being 
+trapped.\footnote{A subject is considered trapped when 3 out of their last 4 choices are consistent with 
+a self-defeating equilibrium.} 
+While the rest of the subjects neither learned nor were trapped.
 
@@
 
-![Share of choices that were consistent with a stable belief for the learners and the non-learners](../figures/trap_choice.png){#fig:traps-choice}
+![Panel A: Share of subjects who learned in cases where there was a trap and in cases where there was no trap.
+Panel B: Share of choices that were consistent with a stable belief for the learners, those who are in a trap and others](../figures/trap_choice.png){#fig:traps-choice}
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-share_trapped <- round(sum(updates$trapped) / length(updates$trapped),2)
-```
-
-When looking a the behavior in the last 4 rounds of each task, only `r print(share_trapped)*100`% 
-of the subjects  
-were trapped\footnote{I consider a subject to be trapped if 3 out of the last 4 choices were consistent 
-with the self-defeating equilibrium} in a self-defeating equilibrium. These subjects could have been
-dogmatic, switchers for whom the likelihood did not grow fast enough, or Bayesian agents who fell into 
-a self-defeating equilibrium. The rest of the subjects were either updating their beliefs with a bias
-or were switchers.
-
-So far I have accounted for `r share_trapped*100`% subjects as being trapped, and 
+So far I have accounted for `r round(sum(updates$trapped)/nrow(updates), 2)*100`% subjects as being trapped, and 
 `r round(sum(updates$learned)/nrow(updates), 2)*100`%
-having learned the state correctly. From the remaining `r (1 - share_trapped - round(sum(updates$learned)/nrow(updates), 2))*100`%, 
+having learned the state correctly. From the remaining `r (1 - round(sum(updates$trapped)/nrow(updates), 2) - round(sum(updates$learned)/nrow(updates), 2))*100`%, 
 `r round(sum(updates$categorized=='neither' & updates$trap==1)/sum(updates$categorized=='neither'), 2)*100`% were prone to traps
@@
 are that they were switchers who considered an incorrect alternative model, or that they were updating with a bias so large that their effort
-choices were far from optimal.
+choices were far from optimal. Behavior that is not consistent with either of these falls outside of the 
+scope of the theories discussed above.
 
-In the following section, I look at indications of biased updating among all the groups identified so far.
+My results are consistent with the findings of @Hestermann2021. In a laboratory experiment that
+stays true to Framework 1, they test the predictions of the dogmatic modeler. They find that the average
+pattern in behavior is in the direction of the dogmatic modeler, however, subjects do not fully act as dogmatics as
+their actions do not go as far as to fully support the self-defeating equilibrium. A lot of 
+the differences between the observed behavior in their experiment and the model can be attributed 
+to subjects avoiding the self-defeating equilibria and learning the true state. In contrast to their study, I can 
+provide more insight into the reasons why subjects avoid the self-defeating equilibria.
 
@@
 call it the news differential.
-Figure \ref{fig:good-bad-news} shows the correlation between change in effort and the news differential, separately for 
+Figure \ref{fig:reaction-news} shows the correlation between change in effort and the news differential, separately for 
 good and bad news.
@@
 
-![Change in effort by news differential](../figures/effort_change_news.png){#fig:good-bad-news}
+![Change in effort by news differential](../figures/effort_change_news.png){#fig:reaction-news}
 
@@
 of news and that the difference is statistically significant ($p<0.01$). The regression results are reported in Table \ref{tab:regression}.
+columns 2 and 3 of the table consider the model for each treatment separately. I find no significant differences in 
+the parameters across treatment. This is consistent with the fact that the bias is not driven by the ego-relevance 
+of $\theta$.\footnote{The ego-relevance of $\theta$ is the motivation behind the self-attribution bias, 
+however, the bias itself is due to an incorrect updating procedure in response to good and bad news. The presence of 
+asymmetric updating in the stereotype condition can be due to self-censoring of the subjects. In particular, subjects 
+who initially underestimated the performance of the other participant might have realized their mistake and 
+by overestimating it after good news. This is consistent with the data presented here as well as with 
+the data observed in the transition matrix for stereotypes which is reported in the Appendix}
 
@@
 
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+
+bayesian <- updates[, .(round_number, good_news_bay, signal_bay_diff, effort_change_bay)]
+
+setnames(bayesian, c('good_news_bay', 'signal_bay_diff', 'effort_change_bay'), c('good_news', 'news_diff', 'effort_change'))
+
+# run the regression for the bayesian simulation
+reg_bayesian <- lm(effort_change ~ good_news + news_diff + news_diff:good_news, data=bayesian[round_number>1])
+
+# Attach the robust standard errors to the coefficient estimates
+coefs_bayesian <- coef(reg_bayesian)
+coefs_bayesian <- cbind(coefs_bayesian, robust_se)
+```
+
 ```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 
-stargazer(reg, reg_ego, reg_stereotype, 
-title='Regression of effort change on news differential', 
+stargazer(reg, reg_ego, reg_stereotype, reg_bayesian,  
+          title='Regression of effort change on news difference with robust standard errors', 
           dep.var.labels='Change in effort', 
-          covariate.labels=c('Good News', 'News differential', 'News Differential * Good News'),
-          column.labels=c('All', 'Ego-relevant', 'Stereotype'), 
+          covariate.labels=c('Good news', 'News difference', 'News difference * Good news'),
+          column.labels=c('All', 'Ego-relevant', 'Stereotype', 'Bayesian Simulation'), 
           omit.stat=c('f', 'ser'), 
@@
           header=FALSE, 
-          se = list(coefs[, 2], coefs_ego[, 2], coefs_stereotype[, 2]))
+          se = list(coefs[, 2], coefs_ego[, 2], coefs_stereotype[, 2], coefs_bayesian[, 2]))
+
 ```
 
+More convincing evidence against the Switching model is the lack of inverse or attenuated correlation between 
+the change in effort and the news differential. In particular, if the switcher were the underlying model,
+I would expect overconfident subjects who start with an overestimation of $\theta$ to increase their effort
+in response to bad news that were very surprising. This would flatten the slope of the regression line 
+for bad news relative to what a Bayesian would do. \ref{tab:regression} shows that the slope for bad news for
+the simulation\footnote{The details on how the data was simulated are explained in the Appendix} 
+of the Bayesian updates is much flatter than the slope in the data.
+
+## Stereotypes and ego-relevance
+
+Throughout the experiment, there is little difference in the behavior of subjects across treatments.
+Two of the main differences are that subjects in the ego-relevant treatment are more likely to become 
+overconfident when they start with a correct belief. And that subjects in the stereotype treatment are
+more likely to overreact to good news when they start by underestimating the performance of the other
+participant.
+
+These two differences present as consistent with the self-attribution bias. However, the pattern in the
+stereotype treatment could also be due to self-censoring of the subjects. In particular, subjects who
+initially underestimated the performance of the other participant might have realized their mistake and
+over-compensated their mistake by overestimating it after good news. This is consistent with the data
+and offers a more intuitive explanation for why this pattern arises in the stereotype treatment.
+
+Furthermore, I find no evidence of confirmation bias which is something that has been suggested in the
+literature of biased udating.\footnote{See \citet{benjamin2019} for a review of the literature in this and 
+other biases.} In particular, I find no evidence that subjects who overestimate the score of the other 
+participant are more likely to over-attribute successes to a high type and under-attribute them to a low type.
+Symmetrically, I find no evidence that subjects who underestimate the score of the other participant are
+more likely to over-attribute failures to a low type and under-attribute them to a high type. This is 
+consistent with what @Mobius2022 find in their experiment in a less complex updating task.
+
 # Structural estimation
+I have discussed two models that are consistent with the data: the self-attribution bias and the switcher.
+Although the data seems to point more convincingly towards the self-attribution bias, I cannot rule out
+the possibility that the switcher is the underlying model. In this section, I estimate the structural
+parameters of the two models and try to classify subjects into each of the models to assess how 
+much of the data is explained by each of the two likely theories.
+
+## Estimation of the switching threshold
+
+## Estimation of the self-attribution bias
 
@@
 
+# Appendix
+
+## Transition matrix by treatment
+
+Figure \ref{fig:transitions-treatment} shows the transition matrix for each of the treatments separately.
+It shows that initial misspecifications are more sticky in the ego treatment and that subjects who 
+underestimate the score of the other participant in the stereotype treatment are more likely to end up 
+overestimating it than in the ego treatment. This may signal some sort of self-censoring or overreaction 
+in the stereotype treatment.
+
+![Transition matrix for subjects who started in each of the 3 possible starting specifications and the specification that they ended up in at the end of the updating task](../figures/misspecification_transitions_treatment.png){#fig:transitions-treatment}
+
+## Model simulation
+
+In order to simulate the data for each of the models and asses their fit, I simulated the path that each
+type of agent would have taken given each possible realization of $(\theta, \omega)$. I fixed 
+the seed of the random number generator to 3452\footnote{this is the seed that was drawn at random for the experiment} and fixed the signals that would be shown in each round
+after each choice by drawing them before simulating. This way, the signals that the simulation 
+uses coincide exactly with the signals that a subject would have seen in the experiment. 
+I then use each of the algorithms defined by the models to simulate the path that the agent would have taken
+given the signal and given an initial belief. For the dogmatic modeler and the switcher, I use each possible
+dogmatic belief. For the Bayesian and the self-attribution bias, I use a uniform belief on theta.
+
+# Experiment Instructions
+
+You are about to participate in an experiment on decision-making.
+What you earn depends partly on your decisions and partly on chance.
+Please turn off cell phones and similar devices now.
+Please do not talk or in any way try to communicate with other participants.
+We will start with a brief instruction period. If you have any questions during this period, raise your hand, and your question will be answered so everyone can hear.
+
+**General Instructions**
+
+The experiment is separated into two parts. You will be given instructions for each part when it is reached.
+
+**Part 1:**
+
+In part 1, you will be asked to solve a series of quizzes.
+In each quiz, you will answer multiple choice questions on one of 6 topics: Math, Verbal Reasoning, US Geography, Science and Technology, Pop Culture, and Sports and Video Games.
+
+The order of the topics will be determined randomly.
+
+You will see only one question at a time. Select an answer and then click the “Next” button to move on to the following question.
+
+If you leave a question unanswered, it will be marked as incorrect. You will not be able to go back to that question once you click the “Next” button.
+
+You will have 2 minutes for each quiz. Once the time runs out, your answers will be submitted automatically.
+
+At the end of the experiment, the computer will randomly select one topic (each chosen with equal probability), and you will be paid $0.20 for each correct answer.
+
+Your score on the quizzes will also affect how much you earn in part 2. The higher your score, the more likely you will be to make more money.
+
+When you finish all six quizzes, there will be a short questionnaire that will not affect your payoff.
+Please answer all the questions as accurately as you can.
+You will have access to your answers from Part 1 when in Part 2, which can help you make better choices.
+
+We will move on to Part 2 once everyone completes Part 1.
+
+ **Part 2 (Ego):**
+
+The task in this part will be repeated once for each topic from Part 1. For each task, you will make 11 choices.
+
+In this part, you will choose one of 3 gambles and see 10 outcomes for the one you choose.
+Each outcome will be either a success or a failure, and the probability with which each of them is a success is determined by 3 factors:
+
+Your score on the quiz for the corresponding topic,
+
+A randomly chosen success rate,
+
+Your choice of a gamble.
+
+Your score is either Low (if it is 5 or less), Mid (if it is between 6 and 15), or High (if it is 16 or more).
+You will not know your actual score, but you will be reminded of the guess you made in part 1.
+
+The success rate will be chosen randomly by the computer, and it can be Rate A, B, or C.
+Each is drawn with an equal chance (1⁄3 chance each), but you will not know which one was drawn.
+The rate is drawn once, at the beginning of the task, and stays fixed throughout.
+
+To maximize the chance of success, you should choose the gamble that matches the underlying success rate:
+- Gamble A maximizes the probability of a success when the rate is A,
+- Gamble B maximizes the probability of success when the rate is B and
+- Gamble C maximizes the probability of success when the rate is C.
+
+After 11 gamble choices, the task will change to the next topic. This means that the probability of success for this new task will be determined by the following:
+- The score you received on the quiz for the corresponding topic and 
+- a new draw of the rate (A, B, or C)
+
+At the end of the experiment, the computer will randomly pick one of the topics, and you will be paid $0.20 for each success.
+(For each topic, there will be 110 outcomes: 10 outcomes for each of the 11 choices you made).
+
+We will now go over the details of the probability of success. They are described by the tables in the back.
+
+Three tables describe the probabilities. Each table corresponds to one of the score levels: Low, Mid, and High.
+
+Each of the columns within the matrix corresponds to one of the success rates. You do not know which was drawn, but the gambles' outcomes can help you determine the rate.
+
+You will choose a Row.
+
+In order to enter your choice of a gamble, you will first need to choose which matrix you want to see.
+If you choose a matrix that does not correspond to your score, the probabilities in the table will not match the probabilities with which the outcomes are successful.
+
+The outcomes will be generated using:
+- your actual score (table), which you do not know for certain,
+- the gamble (row) that you chose, and
+- the rate (column), which you also don’t know.
+
+**Part 2 (stereotype):**
+
+The task in this part will be repeated once for each topic from Part 1. For each task, you will make 11 choices.
+
+In this part, you will choose one of 3 gambles and see 10 outcomes for the one you choose.
+Each outcome will be either a success or a failure, and the probability with which each of them is a success is determined by 3 factors:
+- The score of another participant on the quiz for the corresponding topic,
+- A randomly chosen success rate,
+- Your choice of a gamble.
+
+The other participant’s score is either Low (if it is 5 or less), Mid (if it is between 6 and 15), or High (if it is 16 or more).
+You will not know the score but will be reminded of your guess in part 1.
+
+The success rate will be chosen randomly by the computer, and it can be Rate A, B, or C.
+Each is drawn with an equal chance (1⁄3 chance each), but you will not know which one was drawn.
+The rate is drawn once, at the beginning of the task, and stays fixed throughout.
+
+To maximize the chance of success, you should choose the gamble that matches the underlying success rate:
+- Gamble A maximizes the probability of a success when the rate is A,
+- Gamble B maximizes the probability of success when the rate is B and
+- Gamble C maximizes the probability of success when the rate is C.
+
+After 11 gamble choices, the task will change to the next topic. This means that the probability of success for this new task will be determined by the following:
+ - The score the other participant got on the quiz for the corresponding topic 
+ - A new draw of the rate(A, B, or C)
+
+At the end of the experiment, the computer will randomly pick one of the topics, and you will be paid $0.20 for each success.
+(For each topic, there will be 110 outcomes: 10 outcomes for each of the 11 choices you made).
+
+We will now go over the details of the probability of success. They are described by the tables in the back.
+
+Three tables describe the probabilities. Each table corresponds to one of the score levels: Low, Mid, and High.
+
+Each of the columns within the matrix corresponds to one of the success rates. You do not know which one was drawn, but the gambles' outcomes can help you determine the rate.
+
+You will choose a Row.
+
+In order to enter your choice of a gamble, you will first need to choose which matrix you want to see.
+If you choose a matrix that does not correspond to the score, the probabilities in the table will not match the probabilities with which the outcomes are successful.
+
+Once you enter a choice, the 10 outcomes will be generated using the following:
+- the actual score (matrix), which you do not know for certain,
+- the gamble (row) that you chose, and
+- the rate (column), which you also don’t know.
+
+_the full data generating process is printed in the rear side of the instructions and always available to the subjects the matrices are labeled with "if your/the other participant's score is" depending on the treatment_
+
+**Screen walk-through script:**
+
+This is the screen where you will enter your choices of gambles.
+First, you must choose the matrix that you want to see. Whatever matrix you choose to see does not change the probabilities with which the gables are a success.
+Then, you must choose a gamble (which corresponds to a row).
+The computer will draw 10 outcomes for that gamble using the probability in the chosen row and the column corresponding to the rate for this task.
+On the right, you can choose to see either the total count of successes and failures for each gamble or the detailed history. That is the number of successes and failures for each of your choices.
+The rate will be drawn again for the next task, corresponding to the next quiz topic. And you will repeat this process.
+
 # References

### 2023-10-10 Paper/draft.tex
corrections in slides

@@
 \author{Jimena Galindo}
-\date{October 08, 2023}
+\date{October 09, 2023}
 
@@
 
-\hypertarget{related-literature}{%
-\subsection{Related literature}\label{related-literature}}
+Overconfidence has been documented in a wide range of settings and has
+been shown to have important economic consequences: \citet{Camerer1999}
+find that overconfidence can explain the excessive entry of
+entrepreneurs into the market; \citet{Hoffman2020} show that workers who
+overestimate their productivity within a firm are less likely to look
+for a new job; \citet{Oster2013} determine that people at high risk of
+Huntington's disease make saving decisions as if they were not at risk.
+
+Although the bias has been widely studied by economists, the settings in
+which the the belief updating procedure has been studied is narrow in
+scope. In particular, the literature has focused on the cases in which
+the agent updates their beliefs about a single characteristic that they
+might care about. For instance, \citet{Eil2011} study the case in which
+the agent updates their beliefs about their own ability, and their own
+beauty in two separate experiments. Similarly, \citet{Benoit2015} study
+the case in which the agent updates their beliefs about their own IQ.
 
@@
 I consider multiple theories of belief updating that have been proposed
-in the literature and that are able to rationalize the prevalence of
-misspecified beliefs. I focus on two different frameworks and develop a
-unifying example that allows me to compare the predictions of all the
-theories. In this section, I outline the theories within each of the
-frameworks.
+in the literature to rationalize the prevalence of misspecified beliefs.
+I focus on two different frameworks and develop a unifying example that
+allows me to compare the predictions of all the theories. In framework 1
+I consider a setting in which the an agent observes a continuous output
+and infers the underlying state. In framework 2, the agent observes a
+binary outcome and infers the underlying probability of success. In both
+frameworks, I consider two nested theories of belief updating.
 
@@
 agent knows the distribution of \(\omega\) but not its realized value.
-His prior belief about his type is \(p_0(\theta)\) and his belief about
-the state, \(p_0(\omega)\), coincides with the true distribution. Let
-the agent's true type be \(\theta^{*}\), and the realized state be
+His belief about the state, \(p_0(\omega)\), coincide with the true
+distribution, \(f\); and his belief about the type is \(p_0(\theta)\).
+Let the agent's true type be \(\theta^{*}\), and the realized state be
 \(\omega^{*}\).
 
-An agent has a \emph{misspecified} belief if the prior assigns
+An agent's belief about the type is \emph{misspecified} if it assigns
 probability zero to their true type. Furthermore, the agent is
 \emph{dogmatic} if he holds a degenerate belief that places probability
-one on being a particular type, \(\hat{\theta}\). An agent can be
-dogmatic and misspecified. If the agent is both,
-\(\hat{\theta} \neq \theta^*\) and \(p_0(\hat{\theta}) = 1\).
+one on being of type \(\hat{\theta}\). An agent can be dogmatic and
+misspecified, in which case \(\hat{\theta} \neq \theta^*\) and
+\(p_0(\hat{\theta}) = 1\).
 
 The agent chooses an action \(a\in A\) and observes a noisy outcome
-\(h\in H\). The outcome is a function of the agent's type, the state,
-and the action. In particular
-\(h = h(\theta^*, \omega^*, a) + \varepsilon\) with \(h(\cdot)\)
-increasing in both \(\theta^*\) and \(\omega^*\), and such that
-conditional on a pair of parameters \((\theta, \omega)\), there is a
-unique optimal action. \(\varepsilon\sim N(0, \sigma)\) is noise in the
-output.
+\(h\). The outcome is a function of the agent's type, the state, and the
+action. In particular \(h = h(\theta^*, \omega^*, a) + \varepsilon\)
+with \(h(\cdot)\) increasing in both \(\theta^*\) and \(\omega^*\), and
+such that conditional on a pair of parameters \((\theta, \omega)\),
+there is a unique optimal action. additionally,
+\(\varepsilon\sim N(0, \sigma)\) is noise in the output.
 
@@
 analysis and plays a role in whether an agent who updates their beliefs
-using Bayes rule would learn the truth or not. The behavior of a
-forward-looking agent is discussed in the conclusion.
+using Bayes rule would learn the truth or not, however, for the main
+theory discussed in this section, the results hold even when relaxing
+this assumption. The behavior of a forward-looking agent is further
+discussed in the conclusion.
 
@@
 equilibrium\footnote{This notion is an adaptation of the Berk-Nash equilibrium in 
-@Esponda2016 to this setting with only one agent}. A
+\citet{Esponda2016} to this setting with only one agent}. A
 \emph{self-defeating equilibrium} is a belief and action pair such that
@@
 The second one is a switcher, as in \citet{Ba2023}. The dogmatic modeler
-can be seen as a switcher with an infinitely sticky initial belief and
-this is the sense in which the two are nested. Both theories produce
-different predictions about the agent's behavior. I discuss both in what
-follows.
+can be seen as a switcher with an infinitely sticky initial belief so
+the two theories are nested. However, outside of the limiting case, they
+produce different predictions about the agent's behavior. I discuss each
+of them separately in what follows.
 
@@
 \subsubsection{The Dogmatic Modeler}\label{the-dogmatic-modeler}}
+
+Take the action space to be the same as the state space \(\Omega\) and
+\(\Omega =A=[\underline{a}, \infty)\).
 
@@
 matter how much information he gathers against being of type
-\(\hat{\theta}\), he will not update his beliefs about \(\theta\). Any
+\(\hat{\theta}\), he will not update his beliefs about it. Any
 discrepancies between the observed outcomes and his believed type are
-incorporated using the Bayes rule to update their beliefs about
+incorporated using the Bayes rule to update his beliefs about
 \(\omega\). \citet{Heidhues2018} show that, under certain assumptions on
 the per-period utility,\footnote{The assumptions are that 
-$u$ is twice continuously differentiable with: (i)$u_{ee}<0$ and $u_e(\underline{e} \theta, \omega)>0>u_e(\Bar{e}, \theta, \omega)$, 
-(ii) $u_{\theta}, u_{\omega}>0$ and (iii) $u_{e\theta}<0$ and $u_{e\omega}>0$. The direction of the derivatives is a normalization
+$u$ is twice continuously differentiable with: (i)$u_{aa}<0$ and $u_a(\underline{a},  \theta, \omega)>0>u_a(\Bar{a}, \theta, \omega)$, 
+(ii) $u_{\theta}, u_{\omega}>0$ and (iii) $u_{a\theta}<0$ and $u_{a\omega}>0$. Where $\underline{a}$ is the
+minimal action and $\Bar{a}$ is the maximal one. 
+ The direction of the derivatives is a normalization
 and the results would hold even when the signs are reversed.} a dogmatic
@@
 \(h(\hat{\theta}, \omega^*, a)\). There are two possible sources for the
-disappointment, the first is that the realized state is lower than the
-expected state. The second source is that the agent is of type
+disappointment: the first is that the realized state is lower than the
+expected state; the second source is that the agent is of type
 \(\theta^*\) and therefore, for all possible states, his gain will be
@@
 is a unique value of \(\omega\) at which the belief is stable, I will
-refer to such value as \(\omega_\infty\). This mechanism is further
-illustrated in Example 1.
-
-\textbf{Example 1: } \emph{Set \(A = \Omega\) and \(H = [0, \infty)\)
+refer to such value as \(\omega_\infty\). This mechanism is illustrated
+in Example 1.
+
+\textbf{Example 1: } \emph{Set \(A = \Omega=[\underline{a}, \infty)\)
 and consider a student with intrinsic ability \(\theta^*\geq 0\) who
-faces a grading procedure \(\omega^*\) that is unknown to them. However,
-they know that a higher \(\omega^*\) is more likely to yield a higher
-grade. In particular, assume the grade is given by
+faces a grading procedure \(\omega^*\) that is unknown to them. The
+student knows that a higher \(\omega^*\) is more likely to yield a
+higher grade. In particular, she knows the grade is given by
 \((\theta^*+a)\omega^*\).}
@@
 \emph{The student must choose an effort level \(a\), which determines
-their grade. For whatever the chosen effort level, the agent must pay a
-cost \(c(a) = \frac{1}{2}a^2\). And he repeats this process for
-infinitely many periods. Assume also that the student's prior is such
-that \(mathbb{E}[\omega]= \omega^*\) and he is dogmatic about being of
-type \(\hat{\theta}>\theta^*\).
-\footnote{The example is illustrated for an overconfident agent but the results are symmetric for a digmatic agent who initially 
+her grade. For whatever the chosen effort level, the student must pay a
+cost \(c(a) = \frac{1}{2}a^2\) and receives a grade of
+\((\theta^*+a)\omega^*\). She repeats this process for infinitely many
+periods. Assume also that the student's prior is such that
+\(\mathbb{E}[\omega]= \omega^*\) and she is dogmatic about being of type
+\(\hat{\theta}>\theta^*\).\footnote{The example is illustrated for an overconfident student but 
+the results are symmetric for a dogmatic student who initially 
 places probability one on some $\tilde{\theta}<\theta^*$.} Therefore,
@@
 \emph{Under this specification, the myopic optimal effort level is
-\(a_t^* = \omega^*\). Nonetheless, because the agent does not know
-\(\omega^*\), he will choose \(a_t = \mathbb{E}_t(\omega)\) where the
-expectation is taken with respect to the agent's belief at the beginning
-of period \(t\). If he does not revise his effort choice for \(k\)
-periods, he will receive an average utility of
+\(a_t^* = \omega^*\). Because the student does not know \(\omega^*\), he
+will choose \(a_t = \mathbb{E}_t(\omega)\) where the expectation is
+taken with respect to the student's belief at the beginning of period
+\(t\). If she does not revise his effort choice for \(k\) periods, she
+will receive an average utility of
 \((\theta^*+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}\) but he was expecting
@@
 \((\hat{\theta}\theta+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}\). In
-response, he will apply Bayes rule to update his beliefs about
+response, she will apply Bayes rule to update his beliefs about
 \(\omega\) to get the posterior belief with
 \(\mathbb{E}_{t+k}[\omega] = \frac{(\theta^{*} + \omega^{*})\omega^{*}}{\hat{\theta} + \omega^{*}}\)
-which is lower than the initial belief. This will cause the agent to
-choose a lower effort at \(t+k\). As a result, he will again receive an
-average utility that is lower than what he expected which will cause his
+which is lower than the initial belief. This will cause the student to
+choose a lower effort at \(t+k\). As a result, she will again receive an
+average utility that is lower than what he expected which will cause her
 belief to drift further down. This process will continue until the
-average utility equals his expected utility under the dogmatic belief
+average utility equals her expected utility under the dogmatic belief
 that assigns probability 1 to \(\hat{\theta}\). At that point, the
-student will have reached a self-defeating equilibrium and he will
+student will have reached a self-defeating equilibrium and she will
 continue to choose sub-optimal effort forever. }
@@
 \citet{Ba2023}. She proposes an extension of the dogmatic agent who is
-able to jump from one dogmatic belief to another. By doing so, the agent
-might end up being dogmatic and correctly specified.
+able to swithch from one dogmatic belief to another. By doing so, the
+agent can avoid the self-defeating equilibria and end up being dogmatic
+and correctly specified.
 
@@
 
-An agent is a \emph{switcher} if they behave as a dogmatic, but is
+An agent is a \emph{switcher} if they behave as a dogmatic, but are
 willing to entertain the possibility that they are of a different type.
@@
 Where \(h^t\) is the history of outcomes up to time \(t\) and \(\alpha\)
-is the switching threshold. By keeping track of the likelihood ratio,
-the agent can perform a \emph{Bayesian hypothesis test} and adopt the
-Dogmatic belief that best fits the
-data.\footnote{In a related problem @Schwarstein2021 proposes a similar updating procedure which relies on the Bayesian 
+is the switching
+threshold.\footnote{Notice that if $\alpha \to \infty$, the behavior of the switcher will be indistinguishable from that of the Dogmatic modeler. 
+In this sense, the switcher is a generalization of the dogmatic type.}
+By keeping track of the likelihood ratio, the agent can perform a
+\emph{Bayesian hypothesis test} and adopt the Dogmatic belief that best
+fits the
+data.\footnote{In a related problem \citet{Schwarstein2021} proposes a similar updating procedure which relies on the Bayesian 
 hypothesis test. However, in their model there is a sender who optimally chooses to propose a model that fits the data}
-Notice that if \(\alpha \to \infty\), the behavior of the switcher will
-be indistinguishable from that of the Dogmatic modeler. In this sense,
-the switcher is a generalization of the dogmatic type.
 
@@
 an alternative type, the switcher can avoid the self-confirming
-equilibrium. However, if the prior belief on \(omega\) is sufficiently
+equilibria. However, if the prior belief on \(omega\) is sufficiently
 tight around a self-defeating equilibrium, the switcher might look
@@
 an action \(a\in A\) and observes a binary outcome that is either a
-success or a failure. Denote the outcome by \(o \in {s,f}\). The
-probability of observing a success is increasing in \(\theta^*\) and in
+success or a failure. Denote the outcome by \(o \in \{s,f\}\). The
+probability of observing a success is increasing in \(\theta\) and in
 \(\omega\). Whenever the agent observes a success, he gets a payoff
@@
 and \(\omega\) by using Bayes' rule. The posterior at period t+1 about
-\(\theta\) after observing a history of outcomes \(h^t\) is given by: \[
-p_{t+1}(\theta, \omega| h^t) = \frac{p[h^t|\theta, \omega]p_t(\theta, \omega)}{\sum_{(\theta', \omega')}p[h^t|\theta', \omega']p_t(\theta', \omega')}
+\(\theta\) after observing outcom \(o\) is given by: \[
+p_{t+1}(\theta, \omega| h^t) = \frac{p[o|\theta, \omega]p_t(\theta, \omega)}{\sum_{(\theta', \omega')}p[o|\theta', \omega']p_t(\theta', \omega')}
 \]
 
-Where \(p_{t}\) is the belief at the start of period \(t+1\). The update
-is symmetric for \(\omega\).
+Where \(p_{t}\) is the belief at the start of period \(t+1\) and
+includes all the information gathered so far.
 
@@
 \(\theta\) and \(\omega\). Since agents are myopic, even though all the
-parameters could be identified with enough variation in choices.
-Although the Bayesian agent is the closest to a fully rational agent
-discussed here, they might not learn their true type. This happens
-because, by being myopic, they do not internalize the tradeoff between
-flow payoff and learning. This can result in too little experimentation
-to learn their true type. An alternative to this approach is given by
-\citet{Hestermann2021} and is discussed in the concluding remarks.
+parameters could be identified with enough variation in choices, there
+will be instances in which the Bayesian will not learn even with
+infinite amounts of data. This happens because, by being myopic, they do
+not internalize the tradeoff between flow payoff and learning. This can
+result in too little experimentation to learn their true type. An
+alternative to this approach is given by \citet{Hestermann2021} and is
+discussed in the concluding remarks. Regardless, this approach is useful
+as a benchamrk for the other theories discussed in this paper.
 
@@
 
-A self-serving Bayesian is an agent who uses a biased version of Bayes
+A Self-Serving Bayesian is an agent who uses a biased version of Bayes
 rule to update their beliefs. They will update their beliefs about the
@@
 This formulation of the bias means that the agent will over-attribute
-successes to a high type and under-attribute them to a low type. Whereas
+successes to a high type and under-attribute them to a low type Whereas
 they will over-attribute failures to a low state and under-attribute
-them to a high state. The parameter \(c\) determines the degree of bias
-and the restriction on the order ensures that the model is still
+them to a high state. The bias is introduced by distorting the perceived
+likelihood that the signal was generated by either high values of
+\(\theta\) when it is a success, or by low values of \(\omega\) when it
+is a failure. The parameter \(c\) determines the degree of bias and
+imposes enough restrictions to ensure that the model is still
 falsifiable.
@@
 each of the theories. The example is a modification of the one in
-\citet{Heidhues2018} and is adapeted to be easier to implement in the
-lab.
+\citet{Heidhues2018} and is adapted to implementable in the lab.
 
@@
 Denote the true type by \(\theta^*\) and the true state by \(\omega^*\).
-The agent holds some prior belief about \(\theta\)
-\footnote{which is potentially misspecified as in the dogmatic and switcher cases discussed above}
+The agent holds some prior belief about
+\(\theta\)\footnote{which is potentially misspecified as in the dogmatic and switcher cases discussed above}
 and chooses a binary gamble \(e in \{e_L, e_M, e_H\}\). The agent
@@
 The probability of success is increasing in both \(\theta\) and
-\(\omega\) and is fully described by the following table:
+\(\omega\) and is fully described by the Table \ref{tab:DGP}
 
 \begin{table}[htbp]
+\centering
 
@@
 such cases in order to test which model is a better fit for how subjects
-behave in a laboratory experiment.
-\footnote{because the setting does not match that of Heidhues et al. [2018], there will be situationf for which the theory 
+behave in a laboratory
+experiment.\footnote{because the setting does not match that of @Heidhues2018, there will be situations for which the theory 
 does not provide a prediction. If such cases arise in the lab, they will not be used for the analysis. However, whether a misspecified 
@@
 
-I recruited undergraduate subjects from the CESS lab at NYU who
+I recruited 0m2xzxgv, 0zs7j0mw, 13f4qqvo, 1c7v4nh9, 1gu1vzgk, 1yeajno3,
+28arcsnx, 32k6klan, 49lqkk00, 72o8c5bk, 73pn8n63, 78jeza78, 7ebbfqqg,
+7h604tn3, 83tbxcch, 8yvmba6x, 9lzz0jai, 9om8jvev, 9rpnegmp, 9w15nflu,
+bj048c8i, d37p2ydy, dxfg6c2i, e44vpjp5, fpvdnkq8, g2yvlu4k, hp19zqeh,
+inak0r18, iomh77xp, j6ftwuzj, nxd05o0f, p1b4dbgv, p1k5rpou, pxz3760k,
+q9icrsb2, qoio0y3d, rp5nv7ut, sfi4nrq8, su9at1s5, szq917jn, vybvjxs2,
+xvmd7coq, y71ca1at, z6bycrw5, zap4p51l, 0kxsrg73, 1zb27tea, 36b7nxpg,
+3cv0gsso, 4d7lvql9, 4kecnisx, 56op1uib, 6sybrxjn, 6zd6yym2, 78sdphga,
+a22g0du7, byf6tjt0, cioxyqvq, cl0818oa, dk93ewke, ffd2bxk4, g2p53iqv,
+idzf7yro, ilooy3i8, j3r6tuv8, jk70axat, jka2nr9v, k43107gm, ko3jhnbj,
+lmiiifw0, n86dcmzu, ncvtgyzn, oqf1d07l, q9jar1of, uz5m20q1, v3yunf9n,
+wursesku, zwzznpo6 undergraduate subjects from the CESS lab at NYU who
 participated in an in-person experiment. Sessions lasted approximately
@@
 setting a seed at the beginning of the first session. The seed was drawn
-at random and remained fixed for all sessions.
-\footnote{The seed that was drawn 
+at random and remained fixed for all
+sessions.\footnote{The seed that was drawn 
 at the beginning of session 1 was 3452. The same seed was used for all sessions. It is used both for drawing $\omega$ for each of 
@@
 By doing this I ensure that any two subjects who have the same type and
-face the same exogenous rate will observe the same outcomes and thus, if
-they use the same updating procedure, they should be choosing the same
-gambles. This design feature allows me to identify differences in
-updating procedures across subjects.
+face the same exogenous rate will observe the same outcomes. This
+feature allows me to identify differences across subjects in updating
+procedures since if they use the same updating procedure, they should be
+choosing the same gambles.
 
@@
 In this section, I outline the behavior that is predicted by each of the
-theories discussed above. I start with the dogmatic modeler.
+theories discussed above.
 
@@
 
-So far I have focused only on the case of overconfidence. However, each
-of the models can also be used to explain the prevalence of
-underconfidence. An agent can have a dogmatic belief about the ability
-of a particular group of people and either under or overestimate the
-associated parameter. Similarly, they can be willing to switch between
-two dogmatic beliefs about their ability as a switcher would. Finally,
-they can have a biased updating procedure in which they treat good news
-and bad news asymmetrically.
+So far I have focused only on the case of overconfidence about an
+ego-relevant parameter. However, each of the models can also be used to
+explain the prevalence of stereotypes. An agent can have a dogmatic
+belief about the ability of a particular group of people and either
+under or overestimate the associated parameter. Similarly, they can be
+willing to switch between two dogmatic beliefs about their ability as a
+switcher would. Finally, they can have a biased updating procedure in
+which they treat good news and bad news asymmetrically.
 
@@
 treatments. The share of choices that were consistent with the true
-state for each round is reported in Figure
-\ref{fig:optimal-choices-by-round}.
-
-\begin{figure}
-\hypertarget{fig:optimal-choices-by-round}{%
-\centering
-\includegraphics{../figures/effort_learning.png}
-\caption{Share of optimal choices by
-round}\label{fig:optimal-choices-by-round}
-}
-\end{figure}
+state for each round is reported in panel A of Figure
+\ref{fig:learning-by-groups}.
 
 A closer look at whether people learned or not reveals that there is a
-good amount of heterogeneity in the sample. Figure
+good amount of heterogeneity in the sample. Panel B of Figure
 \ref{fig:learning-by-groups} shows the share of optimal choices by round
@@
 Overall, it does not seem to be the presence of traps that is preventing
-learning. Figure \ref{fig:traps} shows that the share of subjects who
-learned in cases where there was a trap is larger than the share of
-subjects who learned in cases where there was no trap. This is true for
-both treatments. This indicates that even in the presence of traps, some
-people learn.
-
-\begin{figure}
-\hypertarget{fig:traps}{%
-\centering
-\includegraphics{../figures/learning_trap_presence.png}
-\caption{Share of subjects who learned in cases where there was a trap
-and in cases where there was no trap}\label{fig:traps}
-}
-\end{figure}
+learning. Panel A of Figure \ref{fig:traps-choice} shows that the share
+of subjects who learned in cases where there was a trap is larger than
+the share of subjects who learned in cases where there was no trap. This
+is true for both treatments. This indicates that even in the presence of
+traps, 44\% of subjects learn. From the share that did not learn when
+there was a trap. A remaining 21\% can be accounted for as being
+trapped.\footnote{A subject is considered trapped when 3 out of their last 4 choices are consistent with 
+a self-defeating equilibrium.} While the rest of the subjects neither
+learned nor were trapped.
 
@@
 \includegraphics{../figures/trap_choice.png}
-\caption{Share of choices that were consistent with a stable belief for
-the learners and the non-learners}\label{fig:traps-choice}
+\caption{Panel A: Share of subjects who learned in cases where there was
+a trap and in cases where there was no trap. Panel B: Share of choices
+that were consistent with a stable belief for the learners, those who
+are in a trap and others}\label{fig:traps-choice}
 }
@@
 
-When looking a the behavior in the last 4 rounds of each task, only 16\%
-of the subjects\\
-were
-trapped\footnote{I consider a subject to be trapped if 3 out of the last 4 choices were consistent 
-with the self-defeating equilibrium} in a self-defeating equilibrium.
-These subjects could have been dogmatic, switchers for whom the
-likelihood did not grow fast enough, or Bayesian agents who fell into a
-self-defeating equilibrium. The rest of the subjects were either
-updating their beliefs with a bias or were switchers.
-
-So far I have accounted for 16\% subjects as being trapped, and 39\%
-having learned the state correctly. From the remaining 45\%, 60\% were
+So far I have accounted for 21\% subjects as being trapped, and 39\%
+having learned the state correctly. From the remaining 35\%, 60\% were
 prone to traps but did not fall into them, therefore they could not have
@@
 were updating with a bias so large that their effort choices were far
-from optimal.
-
-In the following section, I look at indications of biased updating among
-all the groups identified so far.
+from optimal. Behavior that is not consistent with either of these falls
+outside of the scope of the theories discussed above.
+
+My results are consistent with the findings of \citet{Hestermann2021}.
+In a laboratory experiment that stays true to Framework 1, they test the
+predictions of the dogmatic modeler. They find that the average pattern
+in behavior is in the direction of the dogmatic modeler, however,
+subjects do not fully act as dogmatics as their actions do not go as far
+as to fully support the self-defeating equilibrium. A lot of the
+differences between the observed behavior in their experiment and the
+model can be attributed to subjects avoiding the self-defeating
+equilibria and learning the true state. In contrast to their study, I
+can provide more insight into the reasons why subjects avoid the
+self-defeating equilibria.
 
@@
 realized number of successes and the average number of successes so far
-and call it the news differential. Figure \ref{fig:good-bad-news} shows
+and call it the news differential. Figure \ref{fig:reaction-news} shows
 the correlation between change in effort and the news differential,
@@
 \begin{figure}
-\hypertarget{fig:good-bad-news}{%
+\hypertarget{fig:reaction-news}{%
 \centering
 \includegraphics{../figures/effort_change_news.png}
-\caption{Change in effort by news differential}\label{fig:good-bad-news}
+\caption{Change in effort by news differential}\label{fig:reaction-news}
 }
@@
 statistically significant (\(p<0.01\)). The regression results are
-reported in Table \ref{tab:regression}.
+reported in Table \ref{tab:regression}. columns 2 and 3 of the table
+consider the model for each treatment separately. I find no significant
+differences in the parameters across treatment. This is consistent with
+the fact that the bias is not driven by the ego-relevance of
+\(\theta\).\footnote{The ego-relevance of $\theta$ is the motivation behind the self-attribution bias, 
+however, the bias itself is due to an incorrect updating procedure in response to good and bad news. The presence of 
+asymmetric updating in the stereotype condition can be due to self-censoring of the subjects. In particular, subjects 
+who initially underestimated the performance of the other participant might have realized their mistake and 
+by overestimating it after good news. This is consistent with the data presented here as well as with 
+the data observed in the transition matrix for stereotypes which is reported in the Appendix}
 
 \begin{table}[!htbp] \centering 
-  \caption{Regression of effort change on news differential} 
+  \caption{Regression of effort change on news differential with robust standard errors} 
   \label{tab:regression} 
-\begin{tabular}{@{\extracolsep{5pt}}lccc} 
+\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
 \\[-1.8ex]\hline 
 \hline \\[-1.8ex] 
- & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-4} 
-\\[-1.8ex] & \multicolumn{3}{c}{Change in effort} \\ 
- & All & Ego-relevant & Stereotype \\ 
-\\[-1.8ex] & (1) & (2) & (3)\\ 
+ & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-5} 
+\\[-1.8ex] & \multicolumn{4}{c}{Change in effort} \\ 
+ & All & Ego-relevant & Stereotype & Bayesian Simulation \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
 \hline \\[-1.8ex] 
- Good News & $-$0.12$^{**}$ & $-$0.16$^{***}$ & $-$0.05 \\ 
-  & (0.05) & (0.05) & (0.05) \\ 
-  & & & \\ 
- News differential & 0.22$^{***}$ & 0.22$^{***}$ & 0.21$^{***}$ \\ 
-  & (0.02) & (0.02) & (0.02) \\ 
-  & & & \\ 
- News Differential * Good News & $-$0.27$^{***}$ & $-$0.25$^{***}$ & $-$0.29$^{***}$ \\ 
-  & (0.02) & (0.02) & (0.02) \\ 
-  & & & \\ 
- Constant & 0.31$^{***}$ & 0.31$^{***}$ & 0.30$^{***}$ \\ 
-  & (0.04) & (0.04) & (0.04) \\ 
-  & & & \\ 
+ Good News & $-$0.12$^{**}$ & $-$0.16$^{***}$ & $-$0.05 & 0.08 \\ 
+  & (0.05) & (0.05) & (0.05) & (0.05) \\ 
+  & & & & \\ 
+ News differential & 0.22$^{***}$ & 0.22$^{***}$ & 0.21$^{***}$ & 0.06$^{***}$ \\ 
+  & (0.02) & (0.02) & (0.02) & (0.02) \\ 
+  & & & & \\ 
+ News Differential * Good News & $-$0.27$^{***}$ & $-$0.25$^{***}$ & $-$0.29$^{***}$ & $-$0.04 \\ 
+  & (0.02) & (0.02) & (0.02) & (0.02) \\ 
+  & & & & \\ 
+ Constant & 0.31$^{***}$ & 0.31$^{***}$ & 0.30$^{***}$ & $-$0.08$^{*}$ \\ 
+  & (0.04) & (0.04) & (0.04) & (0.04) \\ 
+  & & & & \\ 
 \hline \\[-1.8ex] 
-Observations & 4,680 & 2,700 & 1,980 \\ 
-R$^{2}$ & 0.04 & 0.04 & 0.04 \\ 
-Adjusted R$^{2}$ & 0.04 & 0.04 & 0.04 \\ 
+Observations & 4,680 & 2,700 & 1,980 & 4,680 \\ 
+R$^{2}$ & 0.04 & 0.04 & 0.04 & 0.05 \\ 
+Adjusted R$^{2}$ & 0.04 & 0.04 & 0.04 & 0.05 \\ 
 \hline 
 \hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 \end{tabular} 
@@
 
+More convincing evidence against the Switching model is the lack of
+inverse or attenuated correlation between the change in effort and the
+news differential. In particular, if the switcher were the underlying
+model, I would expect overconfident subjects who start with an
+overestimation of \(\theta\) to increase their effort in response to bad
+news that were very surprising. This would flatten the slope of the
+regression line for bad news relative to what a Bayesian would do.
+\ref{tab:regression} shows that the slope for bad news for the
+simulation\footnote{The details on how the data was simulated are explained in the Appendix}
+of the Bayesian updates is much flatter than the slope in the data.
+
+\hypertarget{stereotypes-and-ego-relevance}{%
+\subsection{Stereotypes and
+ego-relevance}\label{stereotypes-and-ego-relevance}}
+
+Throughout the experiment, there is little difference in the behavior of
+subjects across treatments. Two of the main differences are that
+subjects in the ego-relevant treatment are more likely to become
+overconfident when they start with a correct belief. And that subjects
+in the stereotype treatment are more likely to overreact to good news
+when they start by underestimating the performance of the other
+participant.
+
+These two differences present as consistent with the self-attribution
+bias. However, the pattern in the stereotype treatment could also be due
+to self-censoring of the subjects. In particular, subjects who initially
+underestimated the performance of the other participant might have
+realized their mistake and over-compensated their mistake by
+overestimating it after good news. This is consistent with the data and
+offers a more intuitive explanation for why this pattern arises in the
+stereotype treatment.
+
+Furthermore, I find no evidence of confirmation bias which is something
+that has been suggested in the literature of biased
+udating.\footnote{See \citet{benjamin2019} for a review of the literature in this and 
+other biases.} In particular, I find no evidence that subjects who
+overestimate the score of the other participant are more likely to
+over-attribute successes to a high type and under-attribute them to a
+low type. Symmetrically, I find no evidence that subjects who
+underestimate the score of the other participant are more likely to
+over-attribute failures to a low type and under-attribute them to a high
+type. This is consistent with what \citet{Mobius2022} find in their
+experiment in a less complex updating task.
+
 \hypertarget{structural-estimation}{%
 \section{Structural estimation}\label{structural-estimation}}
+
+I have discussed two models that are consistent with the data: the
+self-attribution bias and the switcher. Although the data seems to point
+more convincingly towards the self-attribution bias, I cannot rule out
+the possibility that the switcher is the underlying model. In this
+section, I estimate the structural parameters of the two models and try
+to classify subjects into each of the models to assess how much of the
+data is explained by each of the two likely theories.
+
+\hypertarget{estimation-of-the-switching-threshold}{%
+\subsection{Estimation of the switching
+threshold}\label{estimation-of-the-switching-threshold}}
+
+\hypertarget{estimation-of-the-self-attribution-bias}{%
+\subsection{Estimation of the self-attribution
+bias}\label{estimation-of-the-self-attribution-bias}}
 
@@
 
+\hypertarget{appendix}{%
+\section{Appendix}\label{appendix}}
+
+\hypertarget{transition-matrix-by-treatment}{%
+\subsection{Transition matrix by
+treatment}\label{transition-matrix-by-treatment}}
+
+Figure \ref{fig:transitions-treatment} shows the transition matrix for
+each of the treatments separately. It shows that initial
+misspecifications are more sticky in the ego treatment and that subjects
+who underestimate the score of the other participant in the stereotype
+treatment are more likely to end up overestimating it than in the ego
+treatment. This may signal some sort of self-censoring or overreaction
+in the stereotype treatment.
+
+\begin{figure}
+\hypertarget{fig:transitions-treatment}{%
+\centering
+\includegraphics{../figures/misspecification_transitions_treatment.png}
+\caption{Transition matrix for subjects who started in each of the 3
+possible starting specifications and the specification that they ended
+up in at the end of the updating task}\label{fig:transitions-treatment}
+}
+\end{figure}
+
+\hypertarget{model-simulation}{%
+\subsection{Model simulation}\label{model-simulation}}
+
+In order to simulate the data for each of the models and asses their
+fit, I simulated the path that each type of agent would have taken given
+each possible realization of \((\theta, \omega)\). I fixed the seed of
+the random number generator to
+3452\footnote{this is the seed that was drawn at random for the experiment}
+and fixed the signals that would be shown in each round after each
+choice by drawing them before simulating. This way, the signals that the
+simulation uses coincide exactly with the signals that a subject would
+have seen in the experiment. I then use each of the algorithms defined
+by the models to simulate the path that the agent would have taken given
+the signal and given an initial belief. For the dogmatic modeler and the
+switcher, I use each possible dogmatic belief. For the Bayesian and the
+self-attribution bias, I use a uniform belief on theta.
+
+\hypertarget{experiment-instructions}{%
+\section{Experiment Instructions}\label{experiment-instructions}}
+
+You are about to participate in an experiment on decision-making. What
+you earn depends partly on your decisions and partly on chance. Please
+turn off cell phones and similar devices now. Please do not talk or in
+any way try to communicate with other participants. We will start with a
+brief instruction period. If you have any questions during this period,
+raise your hand, and your question will be answered so everyone can
+hear.
+
+\textbf{General Instructions}
+
+The experiment is separated into two parts. You will be given
+instructions for each part when it is reached.
+
+\textbf{Part 1:}
+
+In part 1, you will be asked to solve a series of quizzes. In each quiz,
+you will answer multiple choice questions on one of 6 topics: Math,
+Verbal Reasoning, US Geography, Science and Technology, Pop Culture, and
+Sports and Video Games.
+
+The order of the topics will be determined randomly.
+
+You will see only one question at a time. Select an answer and then
+click the ``Next'' button to move on to the following question.
+
+If you leave a question unanswered, it will be marked as incorrect. You
+will not be able to go back to that question once you click the ``Next''
+button.
+
+You will have 2 minutes for each quiz. Once the time runs out, your
+answers will be submitted automatically.
+
+At the end of the experiment, the computer will randomly select one
+topic (each chosen with equal probability), and you will be paid \$0.20
+for each correct answer.
+
+Your score on the quizzes will also affect how much you earn in part 2.
+The higher your score, the more likely you will be to make more money.
+
+When you finish all six quizzes, there will be a short questionnaire
+that will not affect your payoff. Please answer all the questions as
+accurately as you can. You will have access to your answers from Part 1
+when in Part 2, which can help you make better choices.
+
+We will move on to Part 2 once everyone completes Part 1.
+
+\textbf{Part 2 (Ego):}
+
+The task in this part will be repeated once for each topic from Part 1.
+For each task, you will make 11 choices.
+
+In this part, you will choose one of 3 gambles and see 10 outcomes for
+the one you choose. Each outcome will be either a success or a failure,
+and the probability with which each of them is a success is determined
+by 3 factors:
+
+Your score on the quiz for the corresponding topic,
+
+A randomly chosen success rate,
+
+Your choice of a gamble.
+
+Your score is either Low (if it is 5 or less), Mid (if it is between 6
+and 15), or High (if it is 16 or more). You will not know your actual
+score, but you will be reminded of the guess you made in part 1.
+
+The success rate will be chosen randomly by the computer, and it can be
+Rate A, B, or C. Each is drawn with an equal chance (1⁄3 chance each),
+but you will not know which one was drawn. The rate is drawn once, at
+the beginning of the task, and stays fixed throughout.
+
+To maximize the chance of success, you should choose the gamble that
+matches the underlying success rate: - Gamble A maximizes the
+probability of a success when the rate is A, - Gamble B maximizes the
+probability of success when the rate is B and - Gamble C maximizes the
+probability of success when the rate is C.
+
+After 11 gamble choices, the task will change to the next topic. This
+means that the probability of success for this new task will be
+determined by the following: - The score you received on the quiz for
+the corresponding topic and - a new draw of the rate (A, B, or C)
+
+At the end of the experiment, the computer will randomly pick one of the
+topics, and you will be paid \$0.20 for each success. (For each topic,
+there will be 110 outcomes: 10 outcomes for each of the 11 choices you
+made).
+
+We will now go over the details of the probability of success. They are
+described by the tables in the back.
+
+Three tables describe the probabilities. Each table corresponds to one
+of the score levels: Low, Mid, and High.
+
+Each of the columns within the matrix corresponds to one of the success
+rates. You do not know which was drawn, but the gambles' outcomes can
+help you determine the rate.
+
+You will choose a Row.
+
+In order to enter your choice of a gamble, you will first need to choose
+which matrix you want to see. If you choose a matrix that does not
+correspond to your score, the probabilities in the table will not match
+the probabilities with which the outcomes are successful.
+
+The outcomes will be generated using: - your actual score (table), which
+you do not know for certain, - the gamble (row) that you chose, and -
+the rate (column), which you also don't know.
+
+\textbf{Part 2 (stereotype):}
+
+The task in this part will be repeated once for each topic from Part 1.
+For each task, you will make 11 choices.
+
+In this part, you will choose one of 3 gambles and see 10 outcomes for
+the one you choose. Each outcome will be either a success or a failure,
+and the probability with which each of them is a success is determined
+by 3 factors: - The score of another participant on the quiz for the
+corresponding topic, - A randomly chosen success rate, - Your choice of
+a gamble.
+
+The other participant's score is either Low (if it is 5 or less), Mid
+(if it is between 6 and 15), or High (if it is 16 or more). You will not
+know the score but will be reminded of your guess in part 1.
+
+The success rate will be chosen randomly by the computer, and it can be
+Rate A, B, or C. Each is drawn with an equal chance (1⁄3 chance each),
+but you will not know which one was drawn. The rate is drawn once, at
+the beginning of the task, and stays fixed throughout.
+
+To maximize the chance of success, you should choose the gamble that
+matches the underlying success rate: - Gamble A maximizes the
+probability of a success when the rate is A, - Gamble B maximizes the
+probability of success when the rate is B and - Gamble C maximizes the
+probability of success when the rate is C.
+
+After 11 gamble choices, the task will change to the next topic. This
+means that the probability of success for this new task will be
+determined by the following: - The score the other participant got on
+the quiz for the corresponding topic - A new draw of the rate(A, B, or
+C)
+
+At the end of the experiment, the computer will randomly pick one of the
+topics, and you will be paid \$0.20 for each success. (For each topic,
+there will be 110 outcomes: 10 outcomes for each of the 11 choices you
+made).
+
+We will now go over the details of the probability of success. They are
+described by the tables in the back.
+
+Three tables describe the probabilities. Each table corresponds to one
+of the score levels: Low, Mid, and High.
+
+Each of the columns within the matrix corresponds to one of the success
+rates. You do not know which one was drawn, but the gambles' outcomes
+can help you determine the rate.
+
+You will choose a Row.
+
+In order to enter your choice of a gamble, you will first need to choose
+which matrix you want to see. If you choose a matrix that does not
+correspond to the score, the probabilities in the table will not match
+the probabilities with which the outcomes are successful.
+
+Once you enter a choice, the 10 outcomes will be generated using the
+following: - the actual score (matrix), which you do not know for
+certain, - the gamble (row) that you chose, and - the rate (column),
+which you also don't know.
+
+\emph{the full data generating process is printed in the rear side of
+the instructions and always available to the subjects the matrices are
+labeled with ``if your/the other participant's score is'' depending on
+the treatment}
+
+\textbf{Screen walk-through script:}
+
+This is the screen where you will enter your choices of gambles. First,
+you must choose the matrix that you want to see. Whatever matrix you
+choose to see does not change the probabilities with which the gables
+are a success. Then, you must choose a gamble (which corresponds to a
+row). The computer will draw 10 outcomes for that gamble using the
+probability in the chosen row and the column corresponding to the rate
+for this task. On the right, you can choose to see either the total
+count of successes and failures for each gamble or the detailed history.
+That is the number of successes and failures for each of your choices.
+The rate will be drawn again for the next task, corresponding to the
+next quiz topic. And you will repeat this process.
+
 \renewcommand\refname{References}

### 2023-10-11 Paper/draft.Rmd
intro start

@@
 geometry: margin=2.5cm
+
 ---
@@
 
-Overconfidence has been documented in a wide range of settings and has been shown to have important economic consequences:
-@Camerer1999 find that overconfidence can explain the excessive entry of entrepreneurs into the market; @Hoffman2020 show that
-workers who overestimate their productivity within a firm are less likely to look for a new job; @Oster2013 determine that 
-people at high risk of Huntington's disease make saving decisions as if they were not at risk.
-
-Although the bias has been widely studied by economists, the settings in which 
-the the belief updating procedure has been studied is narrow in scope. In particular, the literature has focused on
-the cases in which the agent updates their beliefs about a single characteristic that they might care about.
-For instance, @Eil2011 study the case in which the agent updates their beliefs about their own ability, and their 
-own beauty in two separate experiments. Similarly, @Benoit2015 study the case in which the agent updates their 
-beliefs about their own IQ.
+A growing body of literature in economics studies the mechanisms through which economic agents come to 
+hold incorrect beliefs about a fundamental. Most of this literature focuses on the case in which agents
+are passive observers of the world and incorrectly incorporate the information they receive into their 
+beliefs\footnote{See \citet{benjamin2019} for a review of error in probabilistic thinking}.
+However, in many situations, agents are active participants in the process of generating information.
+In such cases, the information they receive is affected by their actions and the way they process it
+can affect their future behavior. I refer to this as an \emph{endogenous information} setting.
+This sort of setting, has been shown to explain pehnomena that
+cannot be rationalized with the classical models of biased belief updating (e.g. @Nyarko1991 and 
+@Levy2022). Settings with endogenous information and misspecified learning also offer alternative explanations 
+for why certain well known biases might persist. I focus on a group of theories that aim to explain 
+the prevalence of overconfidence.
+
+Overconfidence has been shown to be a prevalent bias in a variety of settongs. @Oster2013 shows that 
+subjects who are at high risk of having Huntingtons disease underestimate their probability of 
+having the disease and make retirement decisions as if they were not sick. Relating to investment 
+decisions, @Hoffman2020 show that workers overestimate their productivity in their 
+current employment and are unlikely to look for other oportunities. @Camerer1999 find that 
+entrepreneurs are overconfident about the quiality of their enterprise, 
+which leads to excessive entry and early exit from markets. These are only some examples of how 
+holding an incorrect belief about a fundamental can lead to costly decisions \footnote{Other examples 
+of overconfidence are }.
+
+I isolate the main forces from 3 different theories of misspecified learning. Each of the theories 
+rationalizes the prevalence of overconfidence in frameworks where the agents are learning about 
+an ego-relevant parameter and an exogenously determined state. The interaction between these two 
+parameters together with an endogenous information process give rise to two explanaitions
+for the presistence of overconfidence. On one hand, even with bayesian updating, the agent 
+may fall into learning traps. Learning traps are misspecified beliefs and optimal actions 
+that induce signals that confirm the misspecified belief. Once an agent finds themselves in 
+such a situation, the belief will be stable and even with a correctly speficified model of learning, 
+they will not be able to abandon their icorrect beliefs. On the other hand a setting with two variables allows the agent to engage in asymmetric updating 
+with respect to good and bad news. When the outcome depends on an ego-relevant parameter as well
+as a state, the agent can attribute good news to a high value of the parameter while attributing 
+failures to a low value of the exogenous parameter\footnote{This is in line with the well known theory 
+in behavioral science of self-attribution bias of which \citet{kelley1980} provides a review.}.
+
+@Heidhues2018 shows 
+that under certain assumptions on the output function, learning traps can rationalize the 
+existance of misspecified beliefs when agents are dogmatic about the ego-relevant parameter. 
+In a more general model @Ba2023 further analyzes this setting 
+and characterizes the stuations in which even agents who are not dogmatic might become trapped.
+She allows initi dogmatic agents to consider alternative theories and adopt whichever is a 
+better explanation of the observed data. They do so by performing Bayesian hypothesis tests
+that compare the likelihood of having observed the outcome under alternative paradigms\footnote{A 
+similar mechanism is proposed by \citet{Schwarstein2021} in a setting with persuasion}. Although
+this learning mechanism allows agents to avoid the learning traps, there are still situations under
+which misspecified beliefs may persist.
 
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+dogmatic <- updates[, .(round_number, good_news_dogmatic, signal_dogmatic_diff, effort_change_dogmatic)]
+setnames(dogmatic, c('good_news_dogmatic', 'signal_dogmatic_diff', 'effort_change_dogmatic'), c('good_news', 'news_diff', 'effort_change'))
+
+# run the regression for the dogmatic simulation
+reg_dogmatic <- lm(effort_change ~ good_news + news_diff + news_diff:good_news, data=dogmatic[round_number>1])
+
+# Attach the robust standard errors to the coefficient estimates
+coefs_dogmatic <- coef(reg_dogmatic)
+coefs_dogmatic <- cbind(coefs_dogmatic, robust_se)
+
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
 # report reg, reg_ego, reg_stereotype in different columns using stargazer
 
-stargazer(reg, reg_ego, reg_stereotype, reg_bayesian,  
+stargazer(reg, reg_ego, reg_stereotype, reg_bayesian, reg_dogmatic,  
           title='Regression of effort change on news difference with robust standard errors', 
@@
           covariate.labels=c('Good news', 'News difference', 'News difference * Good news'),
-          column.labels=c('All', 'Ego-relevant', 'Stereotype', 'Bayesian Simulation'), 
+          column.labels=c('All', 'Ego-relevant', 'Stereotype', 'Bayesian Simulation', 'Dogmatic Simulation'), 
           omit.stat=c('f', 'ser'), 
@@
           header=FALSE,
-          se = list(coefs[, 2], coefs_ego[, 2], coefs_stereotype[, 2], coefs_bayesian[, 2]))
+          float.env='sidewaystable', 
+          se = list(coefs[, 2], coefs_ego[, 2], coefs_stereotype[, 2], coefs_bayesian[, 2], coefs_dogmatic[, 2]))
 
@@
 
+# References
+
 # Appendix
@@
 The rate will be drawn again for the next task, corresponding to the next quiz topic. And you will repeat this process.
-
-# References

### 2023-10-11 Paper/draft.tex
intro start

@@
 \newtheorem{proposition}{Proposition} % Use the 'proposition' counter for numbering
+\usepackage{rotating, graphicx}
 
@@
 \author{Jimena Galindo}
-\date{October 09, 2023}
+\date{October 10, 2023}
 
@@
 
-Overconfidence has been documented in a wide range of settings and has
-been shown to have important economic consequences: \citet{Camerer1999}
-find that overconfidence can explain the excessive entry of
-entrepreneurs into the market; \citet{Hoffman2020} show that workers who
-overestimate their productivity within a firm are less likely to look
-for a new job; \citet{Oster2013} determine that people at high risk of
-Huntington's disease make saving decisions as if they were not at risk.
-
-Although the bias has been widely studied by economists, the settings in
-which the the belief updating procedure has been studied is narrow in
-scope. In particular, the literature has focused on the cases in which
-the agent updates their beliefs about a single characteristic that they
-might care about. For instance, \citet{Eil2011} study the case in which
-the agent updates their beliefs about their own ability, and their own
-beauty in two separate experiments. Similarly, \citet{Benoit2015} study
-the case in which the agent updates their beliefs about their own IQ.
+A growing body of literature in economics studies the mechanisms through
+which economic agents come to hold incorrect beliefs about a
+fundamental. Most of this literature focuses on the case in which agents
+are passive observers of the world and incorrectly incorporate the
+information they receive into their
+beliefs\footnote{See \citet{benjamin2019} for a review of error in probabilistic thinking}.
+However, in many situations, agents are active participants in the
+process of generating information. In such cases, the information they
+receive is affected by their actions and the way they process it can
+affect their future behavior. I refer to this as an
+\emph{endogenous information} setting. This sort of setting, has been
+shown to explain pehnomena that cannot be rationalized with the
+classical models of biased belief updating (e.g. \citet{Nyarko1991} and
+\citet{Levy2022}). Settings with endogenous information and misspecified
+learning also offer alternative explanations for why certain well known
+biases might persist. I focus on a group of theories that aim to explain
+the prevalence of overconfidence.
+
+Overconfidence has been shown to be a prevalent bias in a variety of
+settongs. \citet{Oster2013} shows that subjects who are at high risk of
+having Huntingtons disease underestimate their probability of having the
+disease and make retirement decisions as if they were not sick. Relating
+to investment decisions, \citet{Hoffman2020} show that workers
+overestimate their productivity in their current employment and are
+unlikely to look for other oportunities. \citet{Camerer1999} find that
+entrepreneurs are overconfident about the quiality of their enterprise,
+which leads to excessive entry and early exit from markets. These are
+only some examples of how holding an incorrect belief about a
+fundamental can lead to costly decisions \footnote{Other examples 
+of overconfidence are }.
+
+I isolate the main forces from 3 different theories of misspecified
+learning. Each of the theories rationalizes the prevalence of
+overconfidence in frameworks where the agents are learning about an
+ego-relevant parameter and an exogenously determined state. The
+interaction between these two parameters together with an endogenous
+information process give rise to two explanaitions for the presistence
+of overconfidence. On one hand, even with bayesian updating, the agent
+may fall into learning traps. Learning traps are misspecified beliefs
+and optimal actions that induce signals that confirm the misspecified
+belief. Once an agent finds themselves in such a situation, the belief
+will be stable and even with a correctly speficified model of learning,
+they will not be able to abandon their icorrect beliefs. On the other
+hand a setting with two variables allows the agent to engage in
+asymmetric updating with respect to good and bad news. When the outcome
+depends on an ego-relevant parameter as well as a state, the agent can
+attribute good news to a high value of the parameter while attributing
+failures to a low value of the exogenous
+parameter\footnote{This is in line with the well known theory 
+in behavioral science of self-attribution bias of which \citet{kelley1980} provides a review.}.
+
+\citet{Heidhues2018} shows that under certain assumptions on the output
+function, learning traps can rationalize the existance of misspecified
+beliefs when agents are dogmatic about the ego-relevant parameter. In a
+more general model \citet{Ba2023} further analyzes this setting and
+characterizes the stuations in which even agents who are not dogmatic
+might become trapped. She allows initi dogmatic agents to consider
+alternative theories and adopt whichever is a better explanation of the
+observed data. They do so by performing Bayesian hypothesis tests that
+compare the likelihood of having observed the outcome under alternative
+paradigms\footnote{A 
+similar mechanism is proposed by \citet{Schwarstein2021} in a setting with persuasion}.
+Although this learning mechanism allows agents to avoid the learning
+traps, there are still situations under which misspecified beliefs may
+persist.
 
@@
 
-I recruited 0m2xzxgv, 0zs7j0mw, 13f4qqvo, 1c7v4nh9, 1gu1vzgk, 1yeajno3,
-28arcsnx, 32k6klan, 49lqkk00, 72o8c5bk, 73pn8n63, 78jeza78, 7ebbfqqg,
-7h604tn3, 83tbxcch, 8yvmba6x, 9lzz0jai, 9om8jvev, 9rpnegmp, 9w15nflu,
-bj048c8i, d37p2ydy, dxfg6c2i, e44vpjp5, fpvdnkq8, g2yvlu4k, hp19zqeh,
-inak0r18, iomh77xp, j6ftwuzj, nxd05o0f, p1b4dbgv, p1k5rpou, pxz3760k,
-q9icrsb2, qoio0y3d, rp5nv7ut, sfi4nrq8, su9at1s5, szq917jn, vybvjxs2,
-xvmd7coq, y71ca1at, z6bycrw5, zap4p51l, 0kxsrg73, 1zb27tea, 36b7nxpg,
-3cv0gsso, 4d7lvql9, 4kecnisx, 56op1uib, 6sybrxjn, 6zd6yym2, 78sdphga,
-a22g0du7, byf6tjt0, cioxyqvq, cl0818oa, dk93ewke, ffd2bxk4, g2p53iqv,
-idzf7yro, ilooy3i8, j3r6tuv8, jk70axat, jka2nr9v, k43107gm, ko3jhnbj,
-lmiiifw0, n86dcmzu, ncvtgyzn, oqf1d07l, q9jar1of, uz5m20q1, v3yunf9n,
-wursesku, zwzznpo6 undergraduate subjects from the CESS lab at NYU who
+I recruited 78 undergraduate subjects from the CESS lab at NYU who
 participated in an in-person experiment. Sessions lasted approximately
@@
 
-So far I have accounted for 21\% subjects as being trapped, and 39\%
-having learned the state correctly. From the remaining 35\%, 60\% were
+So far I have accounted for 16\% subjects as being trapped, and 39\%
+having learned the state correctly. From the remaining 45\%, 60\% were
 prone to traps but did not fall into them, therefore they could not have
@@
 
-\begin{table}[!htbp] \centering 
-  \caption{Regression of effort change on news differential with robust standard errors} 
+\begin{sidewaystable}[!htbp] \centering 
+  \caption{Regression of effort change on news difference with robust standard errors} 
   \label{tab:regression} 
-\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
+\begin{tabular}{@{\extracolsep{5pt}}lccccc} 
 \\[-1.8ex]\hline 
 \hline \\[-1.8ex] 
- & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-5} 
-\\[-1.8ex] & \multicolumn{4}{c}{Change in effort} \\ 
- & All & Ego-relevant & Stereotype & Bayesian Simulation \\ 
-\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
+ & \multicolumn{5}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-6} 
+\\[-1.8ex] & \multicolumn{5}{c}{Change in effort} \\ 
+ & All & Ego-relevant & Stereotype & Bayesian Simulation & Dogmatic Simulation \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5)\\ 
 \hline \\[-1.8ex] 
- Good News & $-$0.12$^{**}$ & $-$0.16$^{***}$ & $-$0.05 & 0.08 \\ 
-  & (0.05) & (0.05) & (0.05) & (0.05) \\ 
-  & & & & \\ 
- News differential & 0.22$^{***}$ & 0.22$^{***}$ & 0.21$^{***}$ & 0.06$^{***}$ \\ 
-  & (0.02) & (0.02) & (0.02) & (0.02) \\ 
-  & & & & \\ 
- News Differential * Good News & $-$0.27$^{***}$ & $-$0.25$^{***}$ & $-$0.29$^{***}$ & $-$0.04 \\ 
-  & (0.02) & (0.02) & (0.02) & (0.02) \\ 
-  & & & & \\ 
- Constant & 0.31$^{***}$ & 0.31$^{***}$ & 0.30$^{***}$ & $-$0.08$^{*}$ \\ 
-  & (0.04) & (0.04) & (0.04) & (0.04) \\ 
-  & & & & \\ 
+ Good news & $-$0.12$^{**}$ & $-$0.16$^{***}$ & $-$0.05 & 0.08 & $-$0.08 \\ 
+  & (0.05) & (0.05) & (0.05) & (0.05) & (0.05) \\ 
+  & & & & & \\ 
+ News difference & 0.22$^{***}$ & 0.22$^{***}$ & 0.21$^{***}$ & 0.06$^{***}$ & 0.10$^{***}$ \\ 
+  & (0.02) & (0.02) & (0.02) & (0.02) & (0.02) \\ 
+  & & & & & \\ 
+ News difference * Good news & $-$0.27$^{***}$ & $-$0.25$^{***}$ & $-$0.29$^{***}$ & $-$0.04 & $-$0.06$^{***}$ \\ 
+  & (0.02) & (0.02) & (0.02) & (0.02) & (0.02) \\ 
+  & & & & & \\ 
+ Constant & 0.31$^{***}$ & 0.31$^{***}$ & 0.30$^{***}$ & $-$0.08$^{*}$ & 0.05 \\ 
+  & (0.04) & (0.04) & (0.04) & (0.04) & (0.04) \\ 
+  & & & & & \\ 
 \hline \\[-1.8ex] 
-Observations & 4,680 & 2,700 & 1,980 & 4,680 \\ 
-R$^{2}$ & 0.04 & 0.04 & 0.04 & 0.05 \\ 
-Adjusted R$^{2}$ & 0.04 & 0.04 & 0.04 & 0.05 \\ 
+Observations & 4,680 & 2,700 & 1,980 & 4,680 & 4,680 \\ 
+R$^{2}$ & 0.04 & 0.04 & 0.04 & 0.05 & 0.06 \\ 
+Adjusted R$^{2}$ & 0.04 & 0.04 & 0.04 & 0.05 & 0.06 \\ 
 \hline 
 \hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\textit{Note:}  & \multicolumn{5}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 \end{tabular} 
-\end{table}
+\end{sidewaystable}
 
@@
 
+\hypertarget{references}{%
+\section{References}\label{references}}
+
 \hypertarget{appendix}{%
@@
 
-\renewcommand\refname{References}
   \bibliography{references.bib}

### 2023-10-14 Paper/draft.Rmd
smm

--- 2023-10-10 Paper/draft.Rmd
@@
 ---
-title: "Learning with misspecified models: Overconfidence and Stereotypes"  # nolint: Grammarly.
+title: "Learning with misspecified models: the case of overestimation"  
 date: '`r format(Sys.time(), "%B %d, %Y")`'
 author: "Jimena Galindo"
-abstract: "TBW"
+abstract: "I design a framework and laboratory experiment that allows for the comparison of multiple theories of misspecified learning.
+I focus on a framework with endogenous information and two a data generating process ruled by two fundamentals: an ego-relevant parameter and a state.
+Within this framework I study three forces that can lead to misspecified beliefs: initial misspecifications, learning traps and biased updating.
+I find that biased updating is the main driver of misspecifications.
+In addition, I vary the degree of ego-relevance of the parameter by introducing a stereotype treatment.
+The data is consistent with biased updating in both cases but for potentially different reasons: In the ego-relevant treatment subjects attribute successes to their own ability and failures to luck; in the stereotype treatment they over-compensate for initial negative biases by over-attributing positive signals to the ability of others.
+This translates into similar observed choices but different dynamic in beliefs."
 #classoption: pagebackref # passes pagebackref=true to hyperref before it is loaded, allowing backreferencing
@@
             hyperref: null
+
         includes:
@@
 
+\newpage
 # Introduction
 
-Overconfidence has been documented in a wide range of settings and has been shown to have important economic consequences:
-@Camerer1999 find that overconfidence can explain the excessive entry of entrepreneurs into the market; @Hoffman2020 show that
-workers who overestimate their productivity within a firm are less likely to look for a new job; @Oster2013 determine that 
-people at high risk of Huntington's disease make saving decisions as if they were not at risk.
-
-Although the bias has been widely studied by economists, the settings in which 
-the the belief updating procedure has been studied is narrow in scope. In particular, the literature has focused on
-the cases in which the agent updates their beliefs about a single characteristic that they might care about.
-For instance, @Eil2011 study the case in which the agent updates their beliefs about their own ability, and their 
-own beauty in two separate experiments. Similarly, @Benoit2015 study the case in which the agent updates their 
-beliefs about their own IQ.
+A growing body of literature in economics explores how people develop incorrect beliefs 
+about fundamentals. Most of this research centers on scenarios where agents 
+passively observe the world, and incorrectly integrate the received information into their 
+beliefs.\footnote{See \citet{benjamin2019} for a review of the literature on errors of 
+probabilistic thinking}
+However, many real-world situations cast agents as active participants in the generation of 
+information. In these cases, the information they acquire is influenced by their actions and 
+subsequent behavior is in turn determined by how they incorporate the information 
+into their beliefs.
+
+Consider a student who needs to decide how much effort to put into 
+studying for an exam. 
+Their decision will depend on two factors: their belief about their intrinsic 
+ability, and their belief about how difficult the exam will be. The outcome 
+they observe will be affected by how much they decide to study. Imagine that the student 
+puts in a moderate amout of effort and gets a surprisingly good grade. Did they get a good grade because 
+they are smarter than they thought? Or because the exam was easier than they had anticipated? 
+Their future exam preparation strategy will depend fundamentally on which line of reasoning they 
+take. This feedback loop is refered to as an \emph{endogenous information 
+process}.
+
+I compare a set of theories that model learning in an endogenous information setting and 
+which can rationalize 
+the persistence of misspecified beliefs. I describe a unifying framework that nests multiple 
+theories of model learning and generates testable predictions for each of them. 
+I cast this framework in a laboratory experiment design and test these predictions to identify which 
+of these theories are consistent with the behavior I observe in the lab.
+The framework features an agent who needs to 
+learn two parameters: one that regards their own characteristics 
+(an \emph{ego-relevant} parameter), 
+and an exogenously determined state. In the context of the student preparing for exams, 
+the two parameters  would be their intrinsic ability and the difficulty of the exam.
+
+Misspecified beliefs about an ego-relevant parameter are often referred to as overconfidence 
+(or underconfidence) and 
+have been documented by behavioral scientists\footnote{\citet{kelley1980} 
+provides a review of the psychology literature.} and economists\footnote{See \citet{benjamin2019} 
+for a review of the literature in economics.} in a variety of settings.  @Oster2013 find that 
+subjects who are at high risk of having Huntington's disease overestimate their probability of 
+being healthy and make retirement decisions as if they were healthy. @Hoffman2020 show that workers 
+overestimate the quality of their match to their 
+current employment and are unlikely to look for other opportunities. @Camerer1999 find that 
+entrepreneurs are overconfident about the quality of their enterprise, 
+which leads to excessive entry and early exit from markets.
+
+In all of these examples,
+holding an incorrect belief about a fundamental leads to suboptimal choices with 
+potentially high costs. In spite of the abundance of evidence, the scope of the existing research 
+is limited in terms of the frameworks it considers. Most of the experimental evidence 
+documenting the bias is collected in settings where subject are passive learners.\footnote{
+\citet{Gotte2022} and \citet{Ozyilmaz2022} are exceptions that study settings with endogenous information processes.} They 
+observe a noisy signal and report their beliefs over subsequent rounds.\footnote{\citet{Bracha2012} and 
+\citet{Mobius2022} are some examples}. Although these studies provide important insights, they are 
+not flexible enough 
+to incorporate the richer theories that have been proposed more recently. In particular, they 
+do not allow the studies of endogenous learning or for learning about multiple parameters at once.\footnote{\citet{Coutts2020} 
+studies an environment with an ego-relevant parameter and an exogenous state but does not 
+incorporate the endogenous information process.}
+
+In my experiment, I move away from the standard framework to study a richer set of 
+underlying mechanisms. In particular, 
+the interaction between the two parameters, together with an endogenous information process, 
+give rise to three possible explanations
+for the persistence of incorrect beliefs: dogmatism, the existence of learning traps and misattribution bias.
+
+Within the first explanation, even with perfect Bayesian updating the agent 
+may fall into learning traps.\footnote{Conditions under which this happens are detailed in \citet{Hestermann2021}} 
+These traps are characterized by a 
+combination of misspecified beliefs and 
+optimal actions which produce information that confirms the misspecified belief---this is a 
+\emph{self-defeating equilibrium}. 
+Once an agent falls into it, the belief will be stable and even with 
+a correctly specified model of learning, they will not be able to abandon their misspecified beliefs. 
+If, in addition the agent is 
+dogmatic about their belief, @Heidhues2018 show that they will inevitably fall into a trap
+and thus will be able to rationalize and sustein their initial dogmatically overconfident 
+(or underconfident) belief.\footnote{\citet{Gotte2022} study the case of agents with dogmatic initial beliefs in a 
+laboratory experiment.}
+
+@Ba2023 moves away from dogmatism and endows the agents with a mechanism through which 
+they can abandon misspecified beliefs; this allows them to avoid falling into learning traps. 
+To do so agents perform Bayesian hypothesis tests to evaluate which is the more 
+likely parameter out of two possibilities. By doing this, she characterizes the set of situations 
+in which, even agents who consider alternative paradigms, may become trapped.\footnote{A 
+similar mechanism is proposed by \citet{Schwarstein2021} in a setting with persuasion.}
+
+Lastly, misattribution bias is the more classical explanation which has been widely studied in 
+behavioral science.\footnote{see \citet{kelley1980} for a review.}
+Agents who suffer from misattribution bias will attribute successes to their own ability---the 
+ego-relevant parameter---and failures to bad luck---the state. 
+Under this model of learning, even an agent who initially has a correct initial 
+belief may become overconfident if they observe a sequence of successes. In this case, 
+the main driver of the bias is not an initial misspecification or the presence of learning traps, 
+it is the updating procedure itself.\footnote{A more general framework that can be used to model 
+this bias has also been proposed by \citet{Brunnermeier2005} and empirically studied by \citet{Bracha2012}.}
+
+These theories provide the main building blocks for a simplified framework that can be directly 
+implemented in a laboratory experiment. The goal is to 
+identify the which of the 3 forces---the presence of learning traps, mispecified initial beliefs, or missatribution 
+bias---better explains the observed behavior. To determine the fit of the models, I compare the behavior
+predicted by each theory to the benchmark given by the fully Bayesian updating procedure.
+
+I also study whether the misspecification is inherently linked to the ego-relevance the parameters 
+or a more general phenomenon. I vary the degree of ego-relevance by introducing a 
+treatment in which subjects learn about the ability of another participant.
+In this treatment, the participants know only the gender and nationality of the other, which can 
+induce stereotypes---a different type of misspecification.  
+If correct learning about the parameters happens at higher rates in the stereotype treatment, 
+it would suggest that the 
+bias is intrinsically linked to the ego-relevance of the parameter. In contrast, if similar 
+biased behavior arises in both treatments, it is more likely that the main driver of these types 
+of misspecified beliefs is the updating procedure itself or the endogenous information process.
+
+Although some agents do fall into learning traps, I find that the behavior of most 
+subjects is better explained by misattribution bias. I also find that misattribution is 
+no more prevalent in the ego-relevant than in the stereotype condition. This suggests 
+that the main driver of the misspecification is the updating proceduce. However, the underlying 
+mechanism by which the bias is generated may be 
+different in both treatments: While in the ego-relevant condition, the intuitive explanation behind the
+bias is that the agent prefers to hold themselves in high esteem, in the stereotype condition
+it seems to be driven by some sort of self-censoring---when subjects realize that they underestimated 
+the ability of another participant based on their gender and nationality, they over-compensate by
+overestimating their ability.
+
+Finally, I estimate the structural parameters of the models to study model-heterogeneity in the sample.
+I find that even at an individual level the behavior is better explained by misattribution bias for most
+subjects. There is a smaller group of subjects that can be better explained through dogmatic beliefs
+and hypothesis testing and none of them behave in line with the fully Bayesian benchmark.
+
+In what follows I first discuss the theoretical framework and the predictions of each of the theories.
+Then I introduce a unifying example and my hypotheses. I then describe the experimental
+design and the results, as well as the estimation of the parameters.
 
@@
 
-I consider multiple theories of belief updating that have been proposed in the literature to rationalize
-the prevalence of misspecified beliefs. I focus on two different frameworks and develop a unifying example that allows me to
-compare the predictions of all the theories. In framework 1 I consider a setting in which the an agent observes
-a continuous output and infers the underlying state. In framework 2, the agent observes a binary outcome and infers the
-underlying probability of success. In both frameworks, I consider two nested theories of belief updating.
+The theories that I consider make predictions in two distinct frameworks. I first detail each theory 
+within their original framework and then develop a unifying example that allows me to
+compare the predictions of all of them. In framework 1 I consider a setting in which the an agent observes
+a continuous output and infers the underlying state. In framework 2, the agent observes a binary 
+outcome and infers the underlying probability of success. In both frameworks, I consider two nested theories 
+of learning.
 
@@
 _The student must choose an effort level $a$, which determines her grade. For whatever the chosen effort level, 
-the student must pay a cost $c(a) = \frac{1}{2}a^2$ and receives a grade of $(\theta^*+a)\omega^*$. She repeats 
+the student must pay a cost $c(a) = \frac{1}{2}a^2$ and observes a grade of $(\theta^*+a)\omega^*$. She repeats 
 this process for infinitely many periods. 
@@
 $(\theta^*+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}$ but he was expecting an average utility of 
-$(\hat{\theta}\theta+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}$. In response, she will apply Bayes 
+$(\hat{\theta}+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}$. In response, she will apply Bayes 
 rule to update his beliefs about
@@
 Nevertheless, the fact that about a third of the subjects started with a correctly specified belief and ended up overconfident
-is consistent only with the self-attribution bias. Therefore, I conclude that the self-attribution bias is the most likely
-explanation for the behavior of the subjects in the experiment.
+is consistent only with the self-attribution bias. this points towards the fact that 
+misattribution bias is the most likely explanation for the behavior of the subjects in the experiment.
 
@@
 
-A regression analysis of this same data reveals that indeed, the slopes are different for the two types 
-of news and that the difference is statistically significant ($p<0.01$). The regression results are reported in Table \ref{tab:regression}.
+A regression analysis of this same data reveals that indeed, the slopes are different for godd and bad
+news and that the difference is statistically significant.\footnote{I run a robustness check where I define
+good news to be a net-positive sample (half or more of the outcomes observed in the sample received in that round
+were successful) and bad news to be net-negative sample. I find the same pattern in this alternative regression model
+and the results are reported in the appendix.} 
+The regression results are reported in Table \ref{tab:regression}.
 columns 2 and 3 of the table consider the model for each treatment separately. I find no significant differences in 
@@
 I would expect overconfident subjects who start with an overestimation of $\theta$ to increase their effort
-in response to bad news that were very surprising. This would flatten the slope of the regression line 
+in response to surprising bad news. This would flatten the slope of the regression line 
 for bad news relative to what a Bayesian would do. \ref{tab:regression} shows that the slope for bad news for
@@
 
+The switching threshold is the parameter that determines the likelihood ratio at which the switcher
+abandons the status quo paradigm and adopts the alternative. In order to estimate this parameter, I
+assume that all subjects are switchers and look at the rounds in which they chose to reveal a probability
+matrix that was different from the one they revealed in the previous round. I then calculate the likelihood
+ratio for the alternative paradigm to the status quo. I average across all such 
+likelihood ratios and use the average as an estimate of the switching threshold.
+
+In detail, Let $b_{t}^\theta$ be the belief about $\theta$ in period $t$.\footnote{in the experimental data, 
+I use the revealed matrix as a proxy for the belief. I take the matrix revealed in the previous period 
+to be the status-quo and the matrix revealed in period $t$ to be the alternative}. 
+And consider a subject for whom $b_{\tau-1}^\theta \neq b_{\tau}^\theta$, 
+where $b_{t}^\theta$. That is, in period $\tau-1$ they chose to reveal a matrix that was different from the one they
+revealed in period $\tau$. The matrix revealed in period $\tau-1$ is the status quo paradigm and the matrix revealed in
+period $\tau$ is the alternative paradigm. The likelihood ratio for the alternative paradigm to the status quo is
+$$
+\ell = \frac{L(\theta | b_{\tau}^\theta)}{L(\theta | b_{\tau-1}^\theta)}=\frac{p_\tau(o_t|b_{\tau}^\theta)}{p_{\tau}(o_t|b_{\tau-1}^\theta)} 
+$$
+
+where $p_\tau(o_t|b_{\tau}^\theta)$ is the probability of observing the signal $o_t$ when the agent is of type $b_{\tau}^\theta$.
+
+The estimate of the switching threshold, $\alpha$, is the average of the likelihood ratios across all subjects who switched
+in the experiment, which is given by
+
+$$\hat{\alpha} = \frac{1}{N}\sum_{i=1}^N \ell_{i\tau}$$
+
+Where $N$ is the number of switches observed in the experiment.
+
+Because the feedback that subjects receive is the equivalent of 10 signal realizations, the estimate 
+of the parameter is an upper bound of the true parameter. A lower bound would be given by the
+average likelihood ratio in the round before the switch happens. I choose to estimate the upper bound
+to impose a harsher test on the theory.
+
+Because the likelihood ratio is a function of the signal, it depends on the sequence of signals that 
+subjects observe. This means that in some cases, the likelihood ratio increases by a large amount from 
+one period to another. Although such cases are not common\footnote{In the data, only 1.8% of the 
+observations have a likelihood ratio that exceeds 5.}, a few very large values can skew the average. 
+To avoid a biased parameter, I restrict my sample to those observations for which the likelihood ratio
+is less than 5.\footnote{The full distribution of likelihood ratios is reported in the appendix}
+Under these assumptions, the estimate of the switching threshold is `r round(mean(updates[lr < 5 & change_indicator==1, lr]), 2)`.
+
+This means that the evidence supporting the alternative paradigm needs to be approximately 10% more
+compelling than the evidence supporting the status quo paradigm in order for the agent to switch.
+The estimation treatment by treatment is slightly larger for the Ego condition than for the Stereotype
+condition. However, the difference is not statistically significant (p-value=0.96).
+
+I then use this estimate to simulate the behavior of the switcher to assess the fit of the model.
+Which is discussed in the next section.
+
 ## Estimation of the self-attribution bias
 
-## Model fit
+Estimation of the parameters of the self-attribution bias is more involved than estimation of the switching
+threshold. In this case, there is no obvious identification strategy that provides a simple estimate 
+of the parameters. Instead, I use the simulated method of moments to estimate the parameters of the model.
+
+In particular, I simulate the behavior of the self-attribution bias for each possible prior and over 
+a grid of parameters. I make the simplifying assumption that the distortion is symmetric across good and bad news.
+That is, I assume that $c(\theta_H, \omega, \text{good news})=c(\theta, \omega_L, \text{bad news})=:c_g$ and that 
+$c(\theta_M, \omega, \text{bad news})=c(\theta, \omega_M, \text{good news})=:c_b$. In addition, I normalize the 
+remaining cases to be equal to 1. This leaves me with only 2 parameters to estimate.
+
+The moments that I match in the data are the reaction to good news and the reaction to bad news. In particular,
+I match the average change in effort in response to good news and the average change in effort in response to bad news.
+That is I match the following moments:
+
+$$
+\bar{G} = \frac{1}{N}\sum_{i=1}^N \frac{1}{T}\sum_{t=1}^T \mathbb{I}\{o_t > \bar{o}\} \cdot (e_t - e_{t-1}) 
+$$
+$$
+\bar{B} = \frac{1}{N}\sum_{i=1}^N \frac{1}{T}\sum_{t=1}^T \mathbb{I}\{o_t < \bar{o}\} \cdot (e_t - e_{t-1})
+$$
+where $N$ is the number of subjects in the sample, $T$ is the number of rounds in the experiment.
+
+I then use the simulated method of moments to estimate the parameters of the model. In particular, I
+simulate the behavior of the model for each possible prior and over a grid of parameters. I then
+calculate the average change in effort in response to good news and the average change in effort in
+response to bad news for each possible prior and over the grid of parameters and across $I$ simulated 
+indiviaduals. 
+I then minimize the objective function given by the sum of squared differences between the simulated
+moments and the empirical moments. That is, I solve the following problem
+
+# Model fit
 
@@
 I have small or no effects throughout on the ego-relevance of the type. Although the motivation behind the 
-theories does not directly apply to the case of stereotypes, the lack of stark differences suggest that 
+theories does not directly apply to the case of stereotypes, the lack of stark differences suggests that 
 biases arise due to an incorrect updating procedure and not necessarily due to the self-serving motivation 
@@
 that their beliefs might be incorrect, they might overreact to signals to try to compensate for the initial 
-bias. Such an updating procedure would be consistent with the self-attribution bias for the case of sterotypes.
+bias. Such an updating procedure would be consistent with the self-attribution bias for the case of stereotypes.
 I remain agnostic about whether that is truly the case or whether the lack of differences is due to other 
@@
 
-# Appendix
-
+\newpage
+\appendix
+
+# appendix
 ## Transition matrix by treatment
@@
 ![Transition matrix for subjects who started in each of the 3 possible starting specifications and the specification that they ended up in at the end of the updating task](../figures/misspecification_transitions_treatment.png){#fig:transitions-treatment}
+
+## Full distribution of likelihood ratios
+The likelihood ratios at rounds in which I observe a change in the belief about $\theta$ presents a
+long right-tail. In particular, 1.8% of the observations have a likelihood ratio that exceeds 5 
+which would mean that the agent requires evidence that is 5 times more compelling in favor 
+of the alternative paradigm in order to switch. Figure \ref{fig:lr-hist} shows the distribution of
+likelihood ratios for all observations.
+
+![Distribution of likelihood ratios for all observed belief changes](../figures/lr_hist.png){#fig:lr-hist}
 
@@
 
-# Experiment Instructions
+## Reaction to good and bad news (robustness check)
+
+I use an alternate definition for good and bad news and check whether the results are robust to this. 
+I define a signal to be a net positive if the number of successes is equal to or greater than the number of failures.
+I define a signal to be a net negative if the number of failures is greater than the number of successes.
+I now treat net positive signals as good news and net negative signals as bad news. I then rerun the regression 
+analysis and find that the results are robust to this alternative definition. In particular, net negative 
+signals are associated with a stark decrease in effort for both treatments. Net positive signals are
+associated with a small decrease in effort for both treatments. The results are reported in Table \ref{tab:regression-net}.
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE }
+reg2 <- lm(effort_change ~ positive_signal + signal_prev + signal_prev:positive_signal, data=updates[round_number>1,])
+robust_se <- sqrt(diag(vcovHC(reg)))
+
+# Attach the robust standard errors to the coefficient estimates
+coefs2 <- coef(reg2)
+coefs2 <- cbind(coefs2, robust_se)
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# run the regression only for treatment  = ego
+reg2_ego <- lm(effort_change ~ positive_signal + signal_prev + signal_prev:positive_signal, data=updates[round_number>1 & treatment == 'ego',])
+
+# Attach the robust standard errors to the coefficient estimates
+coefs2_ego <- coef(reg2_ego)
+coefs2_ego <- cbind(coefs2_ego, robust_se)
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# run the regression only for treatment  = stereotype
+reg2_stereotype <- lm(effort_change ~ positive_signal + signal_prev + signal_prev:positive_signal, data=updates[round_number>1 & treatment == 'stereotype',])
+
+# Attach the robust standard errors to the coefficient estimates
+coefs2_stereotype <- coef(reg2_stereotype)
+coefs2_stereotype <- cbind(coefs2_stereotype, robust_se)
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+# report reg, reg_ego, reg_stereotype in different columns using stargazer
+
+stargazer(reg2, reg2_ego, reg2_stereotype,  
+          title='Regression of effort change on news difference with robust standard errors', 
+          dep.var.labels='Change in effort', 
+          covariate.labels=c('Net-positive signal', 'Signal value', 'Signal value * Net-Positive signal'),
+          column.labels=c('All', 'Ego-relevant', 'Stereotype'), 
+          omit.stat=c('f', 'ser'), 
+          digits=2, 
+          label='tab:regression-net', 
+          header=FALSE, 
+          se = list(coefs2[, 2], coefs2_ego[, 2], coefs2_stereotype[, 2]))
+
+```
+
+# Experimental Instructions
 
@@
 
-_the full data generating process is printed in the rear side of the instructions and always available to the subjects the matrices are labeled with "if your/the other participant's score is" depending on the treatment_
+_The full data generating process is printed on the rear side of the instructions and always available to the subjects throughout part 2._
+_Each of the matrices is labeled with "if your/the other participant's score is..." depending on the treatment_
 
@@
 
+\newpage
 # References

### 2023-10-14 Paper/draft.tex
smm

@@
 \hypersetup{
-  pdftitle={Learning with misspecified models: Overconfidence and Stereotypes},
+  pdftitle={Learning with misspecified models: the case of overestimation},
   pdfauthor={Jimena Galindo},
@@
 
-\title{Learning with misspecified models: Overconfidence and
-Stereotypes}
+\title{Learning with misspecified models: the case of overestimation}
 \author{Jimena Galindo}
-\date{October 10, 2023}
+\date{October 13, 2023}
 
@@
 \begin{abstract}
-TBW
+I design a framework and laboratory experiment that allows for the
+comparison of multiple theories of misspecified learning. I focus on a
+framework with endogenous information and two complementary
+fundamentals: an ego-relevant parameter and a state. Within this
+framework I study three forces that can lead to misspecified beliefs:
+dogmatism, learning traps and biased updating. I find that biased
+updating is the main driver of misspecifications. In addition, I vary
+the degree of ego-relevance of the parameter by introducing a stereotype
+treatment. The data is consistent with biased updating in both cases but
+for potentially different reasons: subjects attribute successes to their
+own ability and failures to luck. In the stereotype treatment they
+over-compensate for initial negative biases by over-attributing positive
+signals to the ability of others. This translates into similar observed
+choices but different dynamisc in beliefs.
 \end{abstract}
+
+\newpage
 
@@
 
-A growing body of literature in economics studies the mechanisms through
-which economic agents come to hold incorrect beliefs about a
-fundamental. Most of this literature focuses on the case in which agents
-are passive observers of the world and incorrectly incorporate the
-information they receive into their
-beliefs\footnote{See \citet{benjamin2019} for a review of error in probabilistic thinking}.
-However, in many situations, agents are active participants in the
-process of generating information. In such cases, the information they
-receive is affected by their actions and the way they process it can
-affect their future behavior. I refer to this as an
-\emph{endogenous information} setting. This sort of setting, has been
-shown to explain pehnomena that cannot be rationalized with the
-classical models of biased belief updating (e.g. \citet{Nyarko1991} and
-\citet{Levy2022}). Settings with endogenous information and misspecified
-learning also offer alternative explanations for why certain well known
-biases might persist. I focus on a group of theories that aim to explain
-the prevalence of overconfidence.
-
-Overconfidence has been shown to be a prevalent bias in a variety of
-settongs. \citet{Oster2013} shows that subjects who are at high risk of
-having Huntingtons disease underestimate their probability of having the
-disease and make retirement decisions as if they were not sick. Relating
-to investment decisions, \citet{Hoffman2020} show that workers
-overestimate their productivity in their current employment and are
-unlikely to look for other oportunities. \citet{Camerer1999} find that
-entrepreneurs are overconfident about the quiality of their enterprise,
-which leads to excessive entry and early exit from markets. These are
-only some examples of how holding an incorrect belief about a
-fundamental can lead to costly decisions \footnote{Other examples 
-of overconfidence are }.
-
-I isolate the main forces from 3 different theories of misspecified
-learning. Each of the theories rationalizes the prevalence of
-overconfidence in frameworks where the agents are learning about an
-ego-relevant parameter and an exogenously determined state. The
-interaction between these two parameters together with an endogenous
-information process give rise to two explanaitions for the presistence
-of overconfidence. On one hand, even with bayesian updating, the agent
-may fall into learning traps. Learning traps are misspecified beliefs
-and optimal actions that induce signals that confirm the misspecified
-belief. Once an agent finds themselves in such a situation, the belief
-will be stable and even with a correctly speficified model of learning,
-they will not be able to abandon their icorrect beliefs. On the other
-hand a setting with two variables allows the agent to engage in
-asymmetric updating with respect to good and bad news. When the outcome
-depends on an ego-relevant parameter as well as a state, the agent can
-attribute good news to a high value of the parameter while attributing
-failures to a low value of the exogenous
-parameter\footnote{This is in line with the well known theory 
-in behavioral science of self-attribution bias of which \citet{kelley1980} provides a review.}.
-
-\citet{Heidhues2018} shows that under certain assumptions on the output
-function, learning traps can rationalize the existance of misspecified
-beliefs when agents are dogmatic about the ego-relevant parameter. In a
-more general model \citet{Ba2023} further analyzes this setting and
-characterizes the stuations in which even agents who are not dogmatic
-might become trapped. She allows initi dogmatic agents to consider
-alternative theories and adopt whichever is a better explanation of the
-observed data. They do so by performing Bayesian hypothesis tests that
-compare the likelihood of having observed the outcome under alternative
-paradigms\footnote{A 
-similar mechanism is proposed by \citet{Schwarstein2021} in a setting with persuasion}.
-Although this learning mechanism allows agents to avoid the learning
-traps, there are still situations under which misspecified beliefs may
-persist.
+A growing body of literature in economics explores how people develop
+incorrect beliefs about fundamentals. Most of this research centers on
+scenarios where agents passively observe the world, and incorrectly
+integrate the received information into their
+beliefs\footnote{See \citet{benjamin2019} for a review of the literature on errors of 
+probabilistic thinking}. However, many real-world situations cast agents
+as active participants in the generation of information. In these cases,
+the information they acquire is influenced by their actions and their
+subsequent behavior is in turn determined by how they incorporate the
+information into their beliefs. This further affects the information
+generating process.
+
+Consider a student who needs to decide how much effort to put into
+studying for an exam. Their decision will depend on two different
+factors: their belief about their intrinsic ability, and their belief
+about how difficult the exam will be. The outcome that they observe will
+be affected by how much they decide to study. Imagine that the student
+puts in a moderate amout of effort and gets a surprisingly good grade.
+Did they get a good grade because they are smarter than they thought? Or
+because the exam was easier than they had anticipated? Their future exam
+preparation strategy will depend fundamentally on which line of
+reasoning they take; in turn, their performance in the next exam will
+further affect the outcome they observe. This type of feedback loop is
+what I call and \emph{endogenous information 
+setting} and is at the center of the forces that I study.
+
+I compare a set of theories that model learning in an endogenous
+information setting and which can rationalize the persistence of
+misspecified beliefs. To do so, I first come up with a unifying
+framework in which each of the theories makes different predictions. I
+then implement this framework in a laboratory experiment. The framework
+that I use features an agent who, in order to make optimal decisions,
+needs to learn a parameter that regards their own characteristics (an
+\emph{ego-relevant} parameter), as well as an exogenously determined
+state---in the case of the student it would be their intrinsic ability
+and the difficulty of the exam.
+
+Misspecified beliefs about an ego-relevant parameter are often referred
+to as overconfidence and have been documented by behavioral
+science\footnote{\citet{kelley1980} 
+provides a review of the psychology literature.} and
+economics\footnote{See \citet{benjamin2019} 
+for a review of the literature in economics.} in a variety of settings.
+\citet{Oster2013} find that subjects who are at high risk of having
+Huntington's disease overestimate their probability of being healthy and
+make retirement decisions as if they were. \citet{Hoffman2020} show that
+workers overestimate the quality of their match to their current
+employment and are unlikely to look for other opportunities.
+\citet{Camerer1999} find that entrepreneurs are overconfident about the
+quality of their enterprise, which leads to excessive entry and early
+exit from markets.
+
+In all of these examples, holding an incorrect belief about a
+fundamental leads to suboptimal choices with potentially high costs. In
+spite of the abundance of evidence, the scope of the existing research
+is limited in terms of the frameworks it considers. Most of the
+experimental evidence documenting the bias is collected in settings
+where subject are passive learners.\footnote{
+\citet{Gotte2022} and \citet{Ozyilmaz2022} are exceptions that study settings with endogenous information processes.}
+They observe a noisy signal and report their beliefs over subsequent
+rounds.\footnote{\citet{Bracha2012} and 
+\citet{Mobius2022} are some examples}. Although these studies provide
+important insights, they are not flexible enough to incorporate the
+richer theories that have been proposed more recently. In particular,
+they do not allow the studies of endogenous learning or for learning
+about multiple parameters at once.\footnote{\citet{Coutts2020} 
+studies an environment with an ego-relevant parameter and an exogenous state but does not 
+incorporate the endogenous information process.}
+
+In my experiment, I move away from the standard framework to study a
+richer set of underlying mechanisms. In particular, the interaction
+between the two parameters, together with an endogenous information
+process, give rise to three possible explanations for the persistence of
+incorrect beliefs: dogmatism, the existence of learning traps and
+misattribution bias.
+
+Within the first explanation, even with perfect Bayesian updating the
+agent may fall into learning
+traps.\footnote{Conditions under which this happens are detailed in \citet{Hestermann2021}}
+These traps are characterized by a combination of misspecified beliefs
+and optimal actions which produce information that confirms the
+misspecified belief---this is a \emph{self-defeating equilibrium}. Once
+an agent falls into it, the belief will be stable and even with a
+correctly specified model of learning, they will not be able to abandon
+their misspecified beliefs. If, in addition the agent is dogmatic about
+their belief, \citet{Heidhues2018} show that they will inevitably fall
+into a trap and thus will be able to rationalize and sustein their
+initial dogmatically overconfident (or underconfident)
+belief.\footnote{\citet{Gotte2022} study the case of agents with dogmatic initial beliefs in a 
+laboratory experiment.}
+
+\citet{Ba2023} moves away from dogmatism and endows the agents with a
+mechanism through which they can abandon misspecified beliefs; this
+allows them to avoid falling into learning traps. To do so agents
+perform Bayesian hypothesis tests to evaluate which is the more likely
+parameter out of two possibilities. By doing this, she characterizes the
+set of situations in which, even agents who consider alternative
+paradigms, may become trapped.\footnote{A 
+similar mechanism is proposed by \citet{Schwarstein2021} in a setting with persuasion.}
+
+Lastly, misattribution bias is the more classical explanation which has
+been widely studied in behavioral
+science.\footnote{see \citet{kelley1980} for a review.} Agents who
+suffer from misattribution bias will attribute successes to their own
+ability---the ego-relevant parameter---and failures to bad luck---the
+state. Under this model of learning, even an agent who initially has a
+correct initial belief may become overconfident if they observe a
+sequence of successes. In this case, the main driver of the bias is not
+an initial misspecification or the presence of learning traps, it is the
+updating procedure
+itself.\footnote{A more general framework that can be used to model 
+this bias has also been proposed by \citet{Brunnermeier2005} and empirically studied by \citet{Bracha2012}.}
+
+These theories provide the main building blocks for a simplified
+framework that can be directly implemented in a laboratory experiment.
+The goal is primarily to identify the which of the 3 forces---dogmatism,
+the presence of learning traps or missatribution bias---better explains
+the observed behavior. To do so, I compare the behavior predicted by
+each theory to the benchmark given by the fully Bayesian updating
+procedure.
+
+On a secondary level, I also aim to understand if the misspecification
+is inherently linked to the ego-relevance of one of the parameters or if
+it is a more general phenomenon. To do so I vary the degree of
+ego-relevance by introducing a treatment in which subjects learn about
+the ability of another participant. In this treatment, the participants
+know only the gender and nationality of the other, which can induce
+stereotypes---a different type of misspecification.\\
+If correct learning about the parameters happens at higher rates in the
+stereotype treatment, it would suggest that the bias is intrinsically
+linked to the ego-relevance of the parameter. In contrast, if similar
+biased behavior arises in both treatments, it is more likely that the
+main driver of these types of misspecified beliefs is the updating
+procedure itself or the endogenous information process.
+
+I find that, although some agents do fall into learning traps, the
+behavior of most subjects is better explained by misattribution bias. I
+also find that misattribution is no more prevalent in the ego-relevant
+than in the stereotype condition. This suggests that the main driver of
+the misspecification is the updating proceduce. However, the underlying
+mechanism by which the bias is generated may be different in both
+treatments: While in the ego-relevant condition, the intuitive
+explanation behind the bias is that the agent prefers to hold themselves
+in high esteem, in the stereotype condition it seems to be driven by
+some sort of self-censoring---when subjects realize that they
+underestimated the ability of another participant based on their gender
+and nationality, they over-compensate by overestimating their ability.
+
+Finally, I structurally estimate the parameters of the models to study
+heterogeneity in the sample. I find that even at an individual level the
+behavior is better explained by misattribution bias for most subjects.
+There is a smaller group of subjects that can be better explained
+through dogmatic beliefs and hypothesis testing and none of them behave
+in line with the fully Bayesian benchmark.
+
+In what follows I first discuss the theoretical framework and the
+predictions of each of the theories. Then I introduce a unifying example
+and my hypotheses. I then describe the experimental design and the
+results, as well as the estimation of the parameters.
 
@@
 
-I consider multiple theories of belief updating that have been proposed
-in the literature to rationalize the prevalence of misspecified beliefs.
-I focus on two different frameworks and develop a unifying example that
-allows me to compare the predictions of all the theories. In framework 1
-I consider a setting in which the an agent observes a continuous output
-and infers the underlying state. In framework 2, the agent observes a
-binary outcome and infers the underlying probability of success. In both
-frameworks, I consider two nested theories of belief updating.
+The theories that I consider make predictions in two distinct
+frameworks. I first detail each theory within their original framework
+and then develop a unifying example that allows me to compare the
+predictions of all of them. In framework 1 I consider a setting in which
+the an agent observes a continuous output and infers the underlying
+state. In framework 2, the agent observes a binary outcome and infers
+the underlying probability of success. In both frameworks, I consider
+two nested theories of learning.
 
@@
 her grade. For whatever the chosen effort level, the student must pay a
-cost \(c(a) = \frac{1}{2}a^2\) and receives a grade of
+cost \(c(a) = \frac{1}{2}a^2\) and observes a grade of
 \((\theta^*+a)\omega^*\). She repeats this process for infinitely many
@@
 an average utility of
-\((\hat{\theta}\theta+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}\). In
-response, she will apply Bayes rule to update his beliefs about
-\(\omega\) to get the posterior belief with
+\((\hat{\theta}+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}\). In response, she
+will apply Bayes rule to update his beliefs about \(\omega\) to get the
+posterior belief with
 \(\mathbb{E}_{t+k}[\omega] = \frac{(\theta^{*} + \omega^{*})\omega^{*}}{\hat{\theta} + \omega^{*}}\)
@@
 A regression analysis of this same data reveals that indeed, the slopes
-are different for the two types of news and that the difference is
-statistically significant (\(p<0.01\)). The regression results are
-reported in Table \ref{tab:regression}. columns 2 and 3 of the table
+are different for godd and bad news and that the difference is
+statistically
+significant.\footnote{I run a robustness check where I define
+good news to be a net-positive sample (half or more of the outcomes observed in the sample received in that round
+were successful) and bad news to be net-negative sample. I find the same pattern in this alternative regression model
+and the results are reported in the appendix.} The regression results
+are reported in Table \ref{tab:regression}. columns 2 and 3 of the table
 consider the model for each treatment separately. I find no significant
@@
 model, I would expect overconfident subjects who start with an
-overestimation of \(\theta\) to increase their effort in response to bad
-news that were very surprising. This would flatten the slope of the
-regression line for bad news relative to what a Bayesian would do.
-\ref{tab:regression} shows that the slope for bad news for the
+overestimation of \(\theta\) to increase their effort in response to
+surprising bad news. This would flatten the slope of the regression line
+for bad news relative to what a Bayesian would do. \ref{tab:regression}
+shows that the slope for bad news for the
 simulation\footnote{The details on how the data was simulated are explained in the Appendix}
@@
 
+The switching threshold is the parameter that determines the likelihood
+ratio at which the switcher abandons the status quo paradigm and adopts
+the alternative. In order to estimate this parameter, I assume that all
+subjects are switchers and look at the rounds in which they chose to
+reveal a probability matrix that was different from the one they
+revealed in the previous round. I then calculate the likelihood ratio
+for the alternative paradigm to the status quo. I average across all
+such likelihood ratios and use the average as an estimate of the
+switching threshold.
+
+In detail, Let \(b_{t}^\theta\) be the belief about \(\theta\) in period
+\(t\).\footnote{in the experimental data, 
+I use the revealed matrix as a proxy for the belief. I take the matrix revealed in the previous period 
+to be the status-quo and the matrix revealed in period $t$ to be the alternative}.
+And consider a subject for whom
+\(b_{\tau-1}^\theta \neq b_{\tau}^\theta\), where \(b_{t}^\theta\). That
+is, in period \(\tau-1\) they chose to reveal a matrix that was
+different from the one they revealed in period \(\tau\). The matrix
+revealed in period \(\tau-1\) is the status quo paradigm and the matrix
+revealed in period \(\tau\) is the alternative paradigm. The likelihood
+ratio for the alternative paradigm to the status quo is \[
+\ell = \frac{L(\theta | b_{\tau}^\theta)}{L(\theta | b_{\tau-1}^\theta)}=\frac{p_\tau(o_t|b_{\tau}^\theta)}{p_{\tau}(o_t|b_{\tau-1}^\theta)} 
+\]
+
+where \(p_\tau(o_t|b_{\tau}^\theta)\) is the probability of observing
+the signal \(o_t\) when the agent is of type \(b_{\tau}^\theta\).
+
+The estimate of the switching threshold, \(\alpha\), is the average of
+the likelihood ratios across all subjects who switched in the
+experiment, which is given by
+
+\[\hat{\alpha} = \frac{1}{N}\sum_{i=1}^N \ell_{i\tau}\]
+
+Where \(N\) is the number of switches observed in the experiment.
+
+Because the feedback that subjects receive is the equivalent of 10
+signal realizations, the estimate of the parameter is an upper bound of
+the true parameter. A lower bound would be given by the average
+likelihood ratio in the round before the switch happens. I choose to
+estimate the upper bound to impose a harsher test on the theory.
+
+Because the likelihood ratio is a function of the signal, it depends on
+the sequence of signals that subjects observe. This means that in some
+cases, the likelihood ratio increases by a large amount from one period
+to another. Although such cases are not
+common\footnote{In the data, only 1.8% of the 
+observations have a likelihood ratio that exceeds 5.}, a few very large
+values can skew the average. To avoid a biased parameter, I restrict my
+sample to those observations for which the likelihood ratio is less than
+5.\footnote{The full distribution of likelihood ratios is reported in the appendix}
+Under these assumptions, the estimate of the switching threshold is
+1.09.
+
+This means that the evidence supporting the alternative paradigm needs
+to be approximately 10\% more compelling than the evidence supporting
+the status quo paradigm in order for the agent to switch. The estimation
+treatment by treatment is slightly larger for the Ego condition than for
+the Stereotype condition. However, the difference is not statistically
+significant (p-value=0.96).
+
+I then use this estimate to simulate the behavior of the switcher to
+assess the fit of the model. Which is discussed in the next section.
+
 \hypertarget{estimation-of-the-self-attribution-bias}{%
@@
 
+Estimation of the parameters of the self-attribution bias is more
+involved than estimation of the switching threshold. In this case, there
+is no obvious identification strategy that provides a simple estimate of
+the parameters. Instead, I use the simulated method of moments to
+estimate the parameters of the model.
+
+In particular, I simulate the behavior of the self-attribution bias for
+each possible prior and over a grid of parameters. I make the
+simplifying assumption that the distortion is symmetric across good and
+bad news. That is, I assume that
+\(c(\theta_H, \omega, \text{good news})=c(\theta, \omega_L, \text{bad news})=:c_g\)
+and that
+\(c(\theta_M, \omega, \text{bad news})=c(\theta, \omega_M, \text{good news})=:c_b\).
+In addition, I normalize the remaining cases to be equal to 1. This
+leaves me with only 2 parameters to estimate.
+
+The moments that I match in the data are the reaction to good news and
+the reaction to bad news. In particular, I match the average change in
+effort in response to good news and the average change in effort in
+response to bad news. That is I match the following moments:
+
+\[
+\bar{G} = \frac{1}{N}\sum_{i=1}^N \frac{1}{T}\sum_{t=1}^T \mathbb{I}\{o_t > \bar{o}\} \cdot (e_t - e_{t-1}) 
+\] \[
+\bar{B} = \frac{1}{N}\sum_{i=1}^N \frac{1}{T}\sum_{t=1}^T \mathbb{I}\{o_t < \bar{o}\} \cdot (e_t - e_{t-1})
+\] where \(N\) is the number of subjects in the sample, \(T\) is the
+number of rounds in the experiment.
+
+I then use the simulated method of moments to estimate the parameters of
+the model. In particular, I simulate the behavior of the model for each
+possible prior and over a grid of parameters. I then calculate the
+average change in effort in response to good news and the average change
+in effort in response to bad news for each possible prior and over the
+grid of parameters and across \(I\) simulated indiviaduals. I then
+minimize the objective function given by the sum of squared differences
+between the simulated moments and the empirical moments. That is, I
+solve the following problem
+
 \hypertarget{model-fit}{%
-\subsection{Model fit}\label{model-fit}}
+\section{Model fit}\label{model-fit}}
 
@@
 Although the motivation behind the theories does not directly apply to
-the case of stereotypes, the lack of stark differences suggest that
+the case of stereotypes, the lack of stark differences suggests that
 biases arise due to an incorrect updating procedure and not necessarily
@@
 compensate for the initial bias. Such an updating procedure would be
-consistent with the self-attribution bias for the case of sterotypes. I
+consistent with the self-attribution bias for the case of stereotypes. I
 remain agnostic about whether that is truly the case or whether the lack
@@
 
-\hypertarget{references}{%
-\section{References}\label{references}}
+\newpage
+\appendix
 
 \hypertarget{appendix}{%
-\section{Appendix}\label{appendix}}
+\section{appendix}\label{appendix}}
 
@@
 up in at the end of the updating task}\label{fig:transitions-treatment}
+}
+\end{figure}
+
+\hypertarget{full-distribution-of-likelihood-ratios}{%
+\subsection{Full distribution of likelihood
+ratios}\label{full-distribution-of-likelihood-ratios}}
+
+The likelihood ratios at rounds in which I observe a change in the
+belief about \(\theta\) presents a long right-tail. In particular, 1.8\%
+of the observations have a likelihood ratio that exceeds 5 which would
+mean that the agent requires evidence that is 5 times more compelling in
+favor of the alternative paradigm in order to switch. Figure
+\ref{fig:lr-hist} shows the distribution of likelihood ratios for all
+observations.
+
+\begin{figure}
+\hypertarget{fig:lr-hist}{%
+\centering
+\includegraphics{../figures/lr_hist.png}
+\caption{Distribution of likelihood ratios for all observed belief
+changes}\label{fig:lr-hist}
 }
@@
 
-\hypertarget{experiment-instructions}{%
-\section{Experiment Instructions}\label{experiment-instructions}}
+\hypertarget{reaction-to-good-and-bad-news-robustness-check}{%
+\subsection{Reaction to good and bad news (robustness
+check)}\label{reaction-to-good-and-bad-news-robustness-check}}
+
+I use an alternate definition for good and bad news and check whether
+the results are robust to this. I define a signal to be a net positive
+if the number of successes is equal to or greater than the number of
+failures. I define a signal to be a net negative if the number of
+failures is greater than the number of successes. I now treat net
+positive signals as good news and net negative signals as bad news. I
+then rerun the regression analysis and find that the results are robust
+to this alternative definition. In particular, net negative signals are
+associated with a stark decrease in effort for both treatments. Net
+positive signals are associated with a small decrease in effort for both
+treatments. The results are reported in Table \ref{tab:regression-net}.
+
+\begin{table}[!htbp] \centering 
+  \caption{Regression of effort change on news difference with robust standard errors} 
+  \label{tab:regression-net} 
+\begin{tabular}{@{\extracolsep{5pt}}lccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-4} 
+\\[-1.8ex] & \multicolumn{3}{c}{Change in effort} \\ 
+ & All & Ego-relevant & Stereotype \\ 
+\\[-1.8ex] & (1) & (2) & (3)\\ 
+\hline \\[-1.8ex] 
+ Net-positive signal & 0.99$^{***}$ & 0.80$^{***}$ & 1.24$^{***}$ \\ 
+  & (0.05) & (0.05) & (0.05) \\ 
+  & & & \\ 
+ Signal value & 0.21$^{***}$ & 0.22$^{***}$ & 0.21$^{***}$ \\ 
+  & (0.02) & (0.02) & (0.02) \\ 
+  & & & \\ 
+ Signal value * Net-Positive signal & $-$0.28$^{***}$ & $-$0.26$^{***}$ & $-$0.31$^{***}$ \\ 
+  & (0.02) & (0.02) & (0.02) \\ 
+  & & & \\ 
+ Constant & $-$0.49$^{***}$ & $-$0.48$^{***}$ & $-$0.50$^{***}$ \\ 
+  & (0.04) & (0.04) & (0.04) \\ 
+  & & & \\ 
+\hline \\[-1.8ex] 
+Observations & 4,680 & 2,700 & 1,980 \\ 
+R$^{2}$ & 0.05 & 0.05 & 0.05 \\ 
+Adjusted R$^{2}$ & 0.05 & 0.04 & 0.05 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
+
+\hypertarget{experimental-instructions}{%
+\section{Experimental Instructions}\label{experimental-instructions}}
 
@@
 
-\emph{the full data generating process is printed in the rear side of
-the instructions and always available to the subjects the matrices are
-labeled with ``if your/the other participant's score is'' depending on
-the treatment}
+\emph{The full data generating process is printed on the rear side of
+the instructions and always available to the subjects throughout part
+2.} \emph{Each of the matrices is labeled with ``if your/the other
+participant's score is\ldots{}'' depending on the treatment}
 
@@
 
+\newpage
+
+\renewcommand\refname{References}
   \bibliography{references.bib}

### 2023-10-14 Data/script_cleaning.py
Remove unwanted files

@@ -1,597 +1,0 @@
-
-
-import numpy as np
-import matplotlib.pyplot as plt
-import pandas as pd
-import scipy as sp
-import seaborn as sns
-
-# Read in the data from the ego treatment sessions
-# import the data in wide format for each session
-session1 = pd.read_csv("Data/session1_ego.csv")
-session2 = pd.read_csv("Data/session2_ego.csv")
-session3 = pd.read_csv("Data/session3_ego.csv")
-session4 = pd.read_csv("Data/session4_ego.csv")
-
-# concatenate the sessions
-ego_wide = pd.concat([session1, session2, session3, session4], axis=0, sort=False)
-
-ego_wide['treatment'] = 'ego'
-ego_wide.reset_index(inplace=True)
-
-######## Read in the data from the stereotype treatment sessions
-# import the data in wide format
-stereo_wide = pd.read_csv("Simulations/demo/data/stereo_demo_data.csv")
-stereo_wide['treatment'] = 'stereotype'
-
-# from the data frame ego_wide, select all the columns that have names that start with 'Quizzes' and append the column 'participant.code
-quiz_cols = [col for col in ego_wide.columns if 'Quizzes' in col]+['participant.code', 'treatment']
-
-
-# from the data frame ego_wide, select all the columns that have names that start with 'participant.'
-participant_cols = [col for col in ego_wide.columns if 'participant' in col]+['participant.code']
-
-# from the data frame ego_wide, select all the columns that have names that start with 'session.'
-session_cols = [col for col in ego_wide.columns if 'session' in col]+['participant.code']
-
-# from the data frame ego_wide, select all the columns that have names that start with 'Signals.'
-signal_cols = [col for col in ego_wide.columns if 'Signals' in col]+['participant.code']
-
-# from the data frame ego_wide, select all the columns that have names that start with 'SignalsOther.'
-signal_other_cols = [col for col in ego_wide.columns if 'SignalsOther' in col]+['participant.code']
-
-# from the data frame ego_wide, select all the columns that have names that start with 'Questionnaire.'
-questionnaire_cols = [col for col in ego_wide.columns if 'Questionnaire' in col]+['participant.code']
-
-# split the data frame ego_wide into 6 data frames using the columns we just selected
-ego_quiz = ego_wide[quiz_cols]
-ego_participant = ego_wide[participant_cols]
-ego_session = ego_wide[session_cols]
[…]

### 2023-10-14 Paper/draft.tex
recompile draft

@@
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else
+  % xetex/luatex font selection
 \fi
@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Learning with misspecified models: the case of overestimation},
-  pdfauthor={Jimena Galindo},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage[margin=2.5cm]{geometry}
@@
 \bibliographystyle{plainnat}
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same}
+\hypersetup{
+  pdftitle={Learning with misspecified models: the case of overestimation},
+  pdfauthor={Jimena Galindo},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
@@
 \author{Jimena Galindo}
-\date{October 13, 2023}
+\date{October 14, 2023}
 
@@
 comparison of multiple theories of misspecified learning. I focus on a
-framework with endogenous information and two complementary
-fundamentals: an ego-relevant parameter and a state. Within this
-framework I study three forces that can lead to misspecified beliefs:
-dogmatism, learning traps and biased updating. I find that biased
-updating is the main driver of misspecifications. In addition, I vary
-the degree of ego-relevance of the parameter by introducing a stereotype
-treatment. The data is consistent with biased updating in both cases but
-for potentially different reasons: subjects attribute successes to their
-own ability and failures to luck. In the stereotype treatment they
-over-compensate for initial negative biases by over-attributing positive
-signals to the ability of others. This translates into similar observed
-choices but different dynamisc in beliefs.
+framework with endogenous information and two a data generating process
+ruled by two fundamentals: an ego-relevant parameter and a state. Within
+this framework I study three forces that can lead to misspecified
+beliefs: initial misspecifications, learning traps and biased updating.
+I find that biased updating is the main driver of misspecifications. In
+addition, I vary the degree of ego-relevance of the parameter by
+introducing a stereotype treatment. The data is consistent with biased
+updating in both cases but for potentially different reasons: In the
+ego-relevant treatment subjects attribute successes to their own ability
+and failures to luck; in the stereotype treatment they over-compensate
+for initial negative biases by over-attributing positive signals to the
+ability of others. This translates into similar observed choices but
+different dynamic in beliefs.
 \end{abstract}
@@
 integrate the received information into their
-beliefs\footnote{See \citet{benjamin2019} for a review of the literature on errors of 
-probabilistic thinking}. However, many real-world situations cast agents
+beliefs.\footnote{See \citet{benjamin2019} for a review of the literature on errors of 
+probabilistic thinking} However, many real-world situations cast agents
 as active participants in the generation of information. In these cases,
-the information they acquire is influenced by their actions and their
+the information they acquire is influenced by their actions and
 subsequent behavior is in turn determined by how they incorporate the
-information into their beliefs. This further affects the information
-generating process.
+information into their beliefs.
 
 Consider a student who needs to decide how much effort to put into
-studying for an exam. Their decision will depend on two different
-factors: their belief about their intrinsic ability, and their belief
-about how difficult the exam will be. The outcome that they observe will
-be affected by how much they decide to study. Imagine that the student
-puts in a moderate amout of effort and gets a surprisingly good grade.
-Did they get a good grade because they are smarter than they thought? Or
-because the exam was easier than they had anticipated? Their future exam
+studying for an exam. Their decision will depend on two factors: their
+belief about their intrinsic ability, and their belief about how
+difficult the exam will be. The outcome they observe will be affected by
+how much they decide to study. Imagine that the student puts in a
+moderate amout of effort and gets a surprisingly good grade. Did they
+get a good grade because they are smarter than they thought? Or because
+the exam was easier than they had anticipated? Their future exam
 preparation strategy will depend fundamentally on which line of
-reasoning they take; in turn, their performance in the next exam will
-further affect the outcome they observe. This type of feedback loop is
-what I call and \emph{endogenous information 
-setting} and is at the center of the forces that I study.
+reasoning they take. This feedback loop is refered to as an
+\emph{endogenous information 
+process}.
 
@@
 information setting and which can rationalize the persistence of
-misspecified beliefs. To do so, I first come up with a unifying
-framework in which each of the theories makes different predictions. I
-then implement this framework in a laboratory experiment. The framework
-that I use features an agent who, in order to make optimal decisions,
-needs to learn a parameter that regards their own characteristics (an
-\emph{ego-relevant} parameter), as well as an exogenously determined
-state---in the case of the student it would be their intrinsic ability
-and the difficulty of the exam.
+misspecified beliefs. I describe a unifying framework that nests
+multiple theories of model learning and generates testable predictions
+for each of them. I cast this framework in a laboratory experiment
+design and test these predictions to identify which of these theories
+are consistent with the behavior I observe in the lab. The framework
+features an agent who needs to learn two parameters: one that regards
+their own characteristics (an \emph{ego-relevant} parameter), and an
+exogenously determined state. In the context of the student preparing
+for exams, the two parameters would be their intrinsic ability and the
+difficulty of the exam.
 
 Misspecified beliefs about an ego-relevant parameter are often referred
-to as overconfidence and have been documented by behavioral
-science\footnote{\citet{kelley1980} 
+to as overconfidence (or underconfidence) and have been documented by
+behavioral scientists\footnote{\citet{kelley1980} 
 provides a review of the psychology literature.} and
-economics\footnote{See \citet{benjamin2019} 
+economists\footnote{See \citet{benjamin2019} 
 for a review of the literature in economics.} in a variety of settings.
@@
 Huntington's disease overestimate their probability of being healthy and
-make retirement decisions as if they were. \citet{Hoffman2020} show that
-workers overestimate the quality of their match to their current
-employment and are unlikely to look for other opportunities.
+make retirement decisions as if they were healthy. \citet{Hoffman2020}
+show that workers overestimate the quality of their match to their
+current employment and are unlikely to look for other opportunities.
 \citet{Camerer1999} find that entrepreneurs are overconfident about the
@@
 framework that can be directly implemented in a laboratory experiment.
-The goal is primarily to identify the which of the 3 forces---dogmatism,
-the presence of learning traps or missatribution bias---better explains
-the observed behavior. To do so, I compare the behavior predicted by
-each theory to the benchmark given by the fully Bayesian updating
-procedure.
-
-On a secondary level, I also aim to understand if the misspecification
-is inherently linked to the ego-relevance of one of the parameters or if
-it is a more general phenomenon. To do so I vary the degree of
-ego-relevance by introducing a treatment in which subjects learn about
-the ability of another participant. In this treatment, the participants
-know only the gender and nationality of the other, which can induce
-stereotypes---a different type of misspecification.\\
+The goal is to identify the which of the 3 forces---the presence of
+learning traps, mispecified initial beliefs, or missatribution
+bias---better explains the observed behavior. To determine the fit of
+the models, I compare the behavior predicted by each theory to the
+benchmark given by the fully Bayesian updating procedure.
+
+I also study whether the misspecification is inherently linked to the
+ego-relevance the parameters or a more general phenomenon. I vary the
+degree of ego-relevance by introducing a treatment in which subjects
+learn about the ability of another participant. In this treatment, the
+participants know only the gender and nationality of the other, which
+can induce stereotypes---a different type of misspecification.\\
 If correct learning about the parameters happens at higher rates in the
@@
 
-I find that, although some agents do fall into learning traps, the
+Although some agents do fall into learning traps, I find that the
 behavior of most subjects is better explained by misattribution bias. I
@@
 
-Finally, I structurally estimate the parameters of the models to study
-heterogeneity in the sample. I find that even at an individual level the
-behavior is better explained by misattribution bias for most subjects.
-There is a smaller group of subjects that can be better explained
-through dogmatic beliefs and hypothesis testing and none of them behave
-in line with the fully Bayesian benchmark.
+Finally, I estimate the structural parameters of the models to study
+model-heterogeneity in the sample. I find that even at an individual
+level the behavior is better explained by misattribution bias for most
+subjects. There is a smaller group of subjects that can be better
+explained through dogmatic beliefs and hypothesis testing and none of
+them behave in line with the fully Bayesian benchmark.
 
@@
 and ended up overconfident is consistent only with the self-attribution
-bias. Therefore, I conclude that the self-attribution bias is the most
+bias. this points towards the fact that misattribution bias is the most
 likely explanation for the behavior of the subjects in the experiment.

### 2023-10-14 Paper/draft.Rmd
Edit intro and abstract

@@
 ---
-title: "Learning with misspecified models: the case of overestimation"  
+title: "Learning with Misspecified Models: the case of overestimation"  
 date: '`r format(Sys.time(), "%B %d, %Y")`'
 author: "Jimena Galindo"
-abstract: "I design a framework and laboratory experiment that allows for the comparison of multiple theories of misspecified learning.
-I focus on a framework with endogenous information and two a data generating process ruled by two fundamentals: an ego-relevant parameter and a state.
+abstract: "I design a framework and a laboratory experiment that allows for the comparison of multiple theories of misspecified learning.
+I focus on a framework with endogenous information and a data-generating process ruled by two fundamentals: an ego-relevant parameter and a state.
 Within this framework I study three forces that can lead to misspecified beliefs: initial misspecifications, learning traps and biased updating.
-I find that biased updating is the main driver of misspecifications.
+I find that biased updating is the main driver of misspecified beliefs in the lab.
 In addition, I vary the degree of ego-relevance of the parameter by introducing a stereotype treatment.
-The data is consistent with biased updating in both cases but for potentially different reasons: In the ego-relevant treatment subjects attribute successes to their own ability and failures to luck; in the stereotype treatment they over-compensate for initial negative biases by over-attributing positive signals to the ability of others.
-This translates into similar observed choices but different dynamic in beliefs."
+The data is consistent with biased updating in both cases but for potentially different reasons: when learning about themselves, subjects attribute successes to their own ability and failures to luck.
+Instead, in the stereotype treatment, they compensate for initial negative biases by over-attributing positive signals to the ability of others.
+This translates into similar observed choices but different dynamics in beliefs."
+
 #classoption: pagebackref # passes pagebackref=true to hyperref before it is loaded, allowing backreferencing
@@
 beliefs.\footnote{See \citet{benjamin2019} for a review of the literature on errors of 
-probabilistic thinking}
+probabilistic thinking.}
 However, many real-world situations cast agents as active participants in the generation of 
-information. In these cases, the information they acquire is influenced by their actions and 
+information. In these cases, the information they observe is influenced by their actions and 
 subsequent behavior is in turn determined by how they incorporate the information 
@@
 
-Consider a student who needs to decide how much effort to put into 
-studying for an exam. 
-Their decision will depend on two factors: their belief about their intrinsic 
+As an example consider a student who needs to decide how much effort to put into 
+studying for an exam. Their decision will depend on two factors: their belief about their intrinsic 
 ability, and their belief about how difficult the exam will be. The outcome 
 they observe will be affected by how much they decide to study. Imagine that the student 
-puts in a moderate amout of effort and gets a surprisingly good grade. Did they get a good grade because 
+puts in a moderate amount of effort and gets a surprisingly good grade. Did they get a good grade because 
 they are smarter than they thought? Or because the exam was easier than they had anticipated? 
 Their future exam preparation strategy will depend fundamentally on which line of reasoning they 
-take. This feedback loop is refered to as an \emph{endogenous information 
-process}.
-
-I compare a set of theories that model learning in an endogenous information setting and 
-which can rationalize 
-the persistence of misspecified beliefs. I describe a unifying framework that nests multiple 
-theories of model learning and generates testable predictions for each of them. 
-I cast this framework in a laboratory experiment design and test these predictions to identify which 
-of these theories are consistent with the behavior I observe in the lab.
-The framework features an agent who needs to 
-learn two parameters: one that regards their own characteristics 
+take. This feedback loop is referred to as an \emph{endogenous information 
+process} and is at the center of the forces I study.
+
+To understand what the main forces at play are, I compare a set of theories that model learning in settings with 
+endogenous information, and which can rationalize the persistence of misspecified beliefs. I develop a unifying framework that nests multiple 
+theories of learning and generates testable predictions for each of them. 
+Then I cast this framework in a laboratory experiment and test the predictions to identify which 
+of the theories are consistent with the behavior I observe in the lab.
+The experiment features an agent who needs to 
+learn two parameters: one that pertains their own characteristics 
 (an \emph{ego-relevant} parameter), 
-and an exogenously determined state. In the context of the student preparing for exams, 
+and an exogenously determined state---in the context of the student preparing for exams, 
 the two parameters  would be their intrinsic ability and the difficulty of the exam.
@@
 observe a noisy signal and report their beliefs over subsequent rounds.\footnote{\citet{Bracha2012} and 
-\citet{Mobius2022} are some examples}. Although these studies provide important insights, they are 
+\citet{Mobius2022} are some examples.} Although these studies provide important insights, they are 
 not flexible enough 
 to incorporate the richer theories that have been proposed more recently. In particular, they 
-do not allow the studies of endogenous learning or for learning about multiple parameters at once.\footnote{\citet{Coutts2020} 
+do not allow the study of endogenous learning or for learning about multiple parameters at once.\footnote{\citet{Coutts2020} 
 studies an environment with an ego-relevant parameter and an exogenous state but does not 
@@
 
-In my experiment, I move away from the standard framework to study a richer set of 
-underlying mechanisms. In particular, 
-the interaction between the two parameters, together with an endogenous information process, 
-give rise to three possible explanations
-for the persistence of incorrect beliefs: dogmatism, the existence of learning traps and misattribution bias.
-
-Within the first explanation, even with perfect Bayesian updating the agent 
-may fall into learning traps.\footnote{Conditions under which this happens are detailed in \citet{Hestermann2021}} 
-These traps are characterized by a 
-combination of misspecified beliefs and 
-optimal actions which produce information that confirms the misspecified belief---this is a 
-\emph{self-defeating equilibrium}. 
-Once an agent falls into it, the belief will be stable and even with 
+In my experiment, I move away from the standard framework of passive learning to analyze a richer set of learning mechanisms. In particular, 
+the interaction between the two parameters together with an endogenous information process 
+gives rise to three possible mechanisms that allow
+for the persistence of incorrect beliefs: the presence of learning traps, incorrect initial beliefs, and misattribution bias.
+The theories that I consider incorporate different combinations of these mechanisms.
+
+When the setting features learning traps, even an agent who incorporates all information correctly, 
+may fall into learning traps as outlined by @Hestermann2021. These traps are characterized by a 
+combination of an incorrect belief and an
+optimal action which produce information that confirms the incorrect belief. 
+Once an agent falls into a trap, the belief will be stable and even with 
 a correctly specified model of learning, they will not be able to abandon their misspecified beliefs. 
-If, in addition the agent is 
-dogmatic about their belief, @Heidhues2018 show that they will inevitably fall into a trap
-and thus will be able to rationalize and sustein their initial dogmatically overconfident 
-(or underconfident) belief.\footnote{\citet{Gotte2022} study the case of agents with dogmatic initial beliefs in a 
+If, the agent is 
+dogmatic about their initial belief, @Heidhues2018 show that they will inevitably fall into a trap
+and thus will be able to rationalize and sustain their initial misspecification belief.\footnote{\citet{Gotte2022} study the case of agents with dogmatic initial beliefs in a 
 laboratory experiment.}
@@
 @Ba2023 moves away from dogmatism and endows the agents with a mechanism through which 
-they can abandon misspecified beliefs; this allows them to avoid falling into learning traps. 
-To do so agents perform Bayesian hypothesis tests to evaluate which is the more 
+they can abandon incorrect beliefs; this allows them to avoid falling into learning traps. 
+To do so agents perform Bayesian hypothesis tests that evaluate which is the more 
 likely parameter out of two possibilities. By doing this, she characterizes the set of situations 
@@
 
-Lastly, misattribution bias is the more classical explanation which has been widely studied in 
-behavioral science.\footnote{see \citet{kelley1980} for a review.}
+Lastly, misattribution bias is the more classical explanation and has been widely studied in 
+behavioral science.\footnote{See \citet{kelley1980} for a review.}
 Agents who suffer from misattribution bias will attribute successes to their own ability---the 
@@
 These theories provide the main building blocks for a simplified framework that can be directly 
-implemented in a laboratory experiment. The goal is to 
-identify the which of the 3 forces---the presence of learning traps, mispecified initial beliefs, or missatribution 
+implemented in a laboratory experiment.
+In the experiment subjects make choices and receive feedback that depends on their own ability, an exogenous parameter and the choice they made.
+I track their choices as well as their beliefs about their own ability.
+The goal is to
+identify which of the 3 forces---the presence of learning traps, misspecified initial beliefs, or missatribution 
 bias---better explains the observed behavior. To determine the fit of the models, I compare the behavior
@@
 
-I also study whether the misspecification is inherently linked to the ego-relevance the parameters 
-or a more general phenomenon. I vary the degree of ego-relevance by introducing a 
+I also study whether the learning mechanism is inherently linked to the ego-relevance the parameters 
+or if it is a more general phenomenon. I vary the degree of ego-relevance by introducing a 
 treatment in which subjects learn about the ability of another participant.
-In this treatment, the participants know only the gender and nationality of the other, which can 
+In this treatment, the participants know only the gender and nationality of the other, and thus can 
 induce stereotypes---a different type of misspecification.  
@@
 Although some agents do fall into learning traps, I find that the behavior of most 
-subjects is better explained by misattribution bias. I also find that misattribution is 
+subjects is better explained by misattribution bias: good news are treated as signaling high ability, while bad news are attributed to a low state. I also find that misattribution is 
 no more prevalent in the ego-relevant than in the stereotype condition. This suggests 
-that the main driver of the misspecification is the updating proceduce. However, the underlying 
+that the main driver of the misspecification is the updating proceduce; however, the underlying 
 mechanism by which the bias is generated may be 
-different in both treatments: While in the ego-relevant condition, the intuitive explanation behind the
-bias is that the agent prefers to hold themselves in high esteem, in the stereotype condition
-it seems to be driven by some sort of self-censoring---when subjects realize that they underestimated 
-the ability of another participant based on their gender and nationality, they over-compensate by
+different in both treatments: While in the ego-relevant condition subjects prefer to hold themselves in high esteem, in the stereotype condition
+updating seems to be driven by some sort of bias overcorrection---when subjects realize that they underestimated 
+the ability of another participant based on their gender and nationality, they compensate by
 overestimating their ability.
@@
 Finally, I estimate the structural parameters of the models to study model-heterogeneity in the sample.
-I find that even at an individual level the behavior is better explained by misattribution bias for most
+I find that even at an individual level the behavior is better explained by a general model of 
+misattribution bias for most
 subjects. There is a smaller group of subjects that can be better explained through dogmatic beliefs
@@
 In what follows I first discuss the theoretical framework and the predictions of each of the theories.
-Then I introduce a unifying example and my hypotheses. I then describe the experimental
-design and the results, as well as the estimation of the parameters.
+Then I introduce a unifying example and my hypotheses. In section 4 I describe the experimental
+design and in section 5 I present the data and the results. Section 6 outlines the estimation of the parameters
+and the model fit analysis.
 

### 2023-10-14 Paper/draft.tex
Edit intro and abstract

@@
 \hypersetup{
-  pdftitle={Learning with misspecified models: the case of overestimation},
+  pdftitle={Learning with Misspecified Models: the case of overestimation},
   pdfauthor={Jimena Galindo},
@@
 
-\title{Learning with misspecified models: the case of overestimation}
+\title{Learning with Misspecified Models: the case of overestimation}
 \author{Jimena Galindo}
@@
 \begin{abstract}
-I design a framework and laboratory experiment that allows for the
+I design a framework and a laboratory experiment that allows for the
 comparison of multiple theories of misspecified learning. I focus on a
-framework with endogenous information and two a data generating process
+framework with endogenous information and a data-generating process
 ruled by two fundamentals: an ego-relevant parameter and a state. Within
@@
 beliefs: initial misspecifications, learning traps and biased updating.
-I find that biased updating is the main driver of misspecifications. In
-addition, I vary the degree of ego-relevance of the parameter by
-introducing a stereotype treatment. The data is consistent with biased
-updating in both cases but for potentially different reasons: In the
-ego-relevant treatment subjects attribute successes to their own ability
-and failures to luck; in the stereotype treatment they over-compensate
-for initial negative biases by over-attributing positive signals to the
-ability of others. This translates into similar observed choices but
-different dynamic in beliefs.
+I find that biased updating is the main driver of misspecified beliefs
+in the lab. In addition, I vary the degree of ego-relevance of the
+parameter by introducing a stereotype treatment. The data is consistent
+with biased updating in both cases but for potentially different
+reasons: when learning about themselves, subjects attribute successes to
+their own ability and failures to luck. Instead, in the stereotype
+treatment, they compensate for initial negative biases by
+over-attributing positive signals to the ability of others. This
+translates into similar observed choices but different dynamics in
+beliefs.
 \end{abstract}
@@
 beliefs.\footnote{See \citet{benjamin2019} for a review of the literature on errors of 
-probabilistic thinking} However, many real-world situations cast agents
+probabilistic thinking.} However, many real-world situations cast agents
 as active participants in the generation of information. In these cases,
-the information they acquire is influenced by their actions and
+the information they observe is influenced by their actions and
 subsequent behavior is in turn determined by how they incorporate the
@@
 
-Consider a student who needs to decide how much effort to put into
-studying for an exam. Their decision will depend on two factors: their
-belief about their intrinsic ability, and their belief about how
-difficult the exam will be. The outcome they observe will be affected by
-how much they decide to study. Imagine that the student puts in a
-moderate amout of effort and gets a surprisingly good grade. Did they
-get a good grade because they are smarter than they thought? Or because
-the exam was easier than they had anticipated? Their future exam
+As an example consider a student who needs to decide how much effort to
+put into studying for an exam. Their decision will depend on two
+factors: their belief about their intrinsic ability, and their belief
+about how difficult the exam will be. The outcome they observe will be
+affected by how much they decide to study. Imagine that the student puts
+in a moderate amount of effort and gets a surprisingly good grade. Did
+they get a good grade because they are smarter than they thought? Or
+because the exam was easier than they had anticipated? Their future exam
 preparation strategy will depend fundamentally on which line of
-reasoning they take. This feedback loop is refered to as an
+reasoning they take. This feedback loop is referred to as an
 \emph{endogenous information 
-process}.
-
-I compare a set of theories that model learning in an endogenous
-information setting and which can rationalize the persistence of
-misspecified beliefs. I describe a unifying framework that nests
-multiple theories of model learning and generates testable predictions
-for each of them. I cast this framework in a laboratory experiment
-design and test these predictions to identify which of these theories
-are consistent with the behavior I observe in the lab. The framework
-features an agent who needs to learn two parameters: one that regards
-their own characteristics (an \emph{ego-relevant} parameter), and an
-exogenously determined state. In the context of the student preparing
-for exams, the two parameters would be their intrinsic ability and the
-difficulty of the exam.
+process} and is at the center of the forces I study.
+
+To understand what the main forces at play are, I compare a set of
+theories that model learning in settings with endogenous information,
+and which can rationalize the persistence of misspecified beliefs. I
+develop a unifying framework that nests multiple theories of learning
+and generates testable predictions for each of them. Then I cast this
+framework in a laboratory experiment and test the predictions to
+identify which of the theories are consistent with the behavior I
+observe in the lab. The experiment features an agent who needs to learn
+two parameters: one that pertains their own characteristics (an
+\emph{ego-relevant} parameter), and an exogenously determined state---in
+the context of the student preparing for exams, the two parameters would
+be their intrinsic ability and the difficulty of the exam.
 
@@
 rounds.\footnote{\citet{Bracha2012} and 
-\citet{Mobius2022} are some examples}. Although these studies provide
+\citet{Mobius2022} are some examples.} Although these studies provide
 important insights, they are not flexible enough to incorporate the
 richer theories that have been proposed more recently. In particular,
-they do not allow the studies of endogenous learning or for learning
-about multiple parameters at once.\footnote{\citet{Coutts2020} 
+they do not allow the study of endogenous learning or for learning about
+multiple parameters at once.\footnote{\citet{Coutts2020} 
 studies an environment with an ego-relevant parameter and an exogenous state but does not 
@@
 
-In my experiment, I move away from the standard framework to study a
-richer set of underlying mechanisms. In particular, the interaction
-between the two parameters, together with an endogenous information
-process, give rise to three possible explanations for the persistence of
-incorrect beliefs: dogmatism, the existence of learning traps and
-misattribution bias.
-
-Within the first explanation, even with perfect Bayesian updating the
-agent may fall into learning
-traps.\footnote{Conditions under which this happens are detailed in \citet{Hestermann2021}}
-These traps are characterized by a combination of misspecified beliefs
-and optimal actions which produce information that confirms the
-misspecified belief---this is a \emph{self-defeating equilibrium}. Once
-an agent falls into it, the belief will be stable and even with a
-correctly specified model of learning, they will not be able to abandon
-their misspecified beliefs. If, in addition the agent is dogmatic about
-their belief, \citet{Heidhues2018} show that they will inevitably fall
-into a trap and thus will be able to rationalize and sustein their
-initial dogmatically overconfident (or underconfident)
+In my experiment, I move away from the standard framework of passive
+learning to analyze a richer set of learning mechanisms. In particular,
+the interaction between the two parameters together with an endogenous
+information process gives rise to three possible mechanisms that allow
+for the persistence of incorrect beliefs: the presence of learning
+traps, incorrect initial beliefs, and misattribution bias. The theories
+that I consider incorporate different combinations of these mechanisms.
+
+When the setting features learning traps, even an agent who incorporates
+all information correctly, may fall into learning traps as outlined by
+\citet{Hestermann2021}. These traps are characterized by a combination
+of an incorrect belief and an optimal action which produce information
+that confirms the incorrect belief. Once an agent falls into a trap, the
+belief will be stable and even with a correctly specified model of
+learning, they will not be able to abandon their misspecified beliefs.
+If, the agent is dogmatic about their initial belief,
+\citet{Heidhues2018} show that they will inevitably fall into a trap and
+thus will be able to rationalize and sustain their initial
+misspecification
 belief.\footnote{\citet{Gotte2022} study the case of agents with dogmatic initial beliefs in a 
@@
 \citet{Ba2023} moves away from dogmatism and endows the agents with a
-mechanism through which they can abandon misspecified beliefs; this
-allows them to avoid falling into learning traps. To do so agents
-perform Bayesian hypothesis tests to evaluate which is the more likely
+mechanism through which they can abandon incorrect beliefs; this allows
+them to avoid falling into learning traps. To do so agents perform
+Bayesian hypothesis tests that evaluate which is the more likely
 parameter out of two possibilities. By doing this, she characterizes the
@@
 
-Lastly, misattribution bias is the more classical explanation which has
+Lastly, misattribution bias is the more classical explanation and has
 been widely studied in behavioral
-science.\footnote{see \citet{kelley1980} for a review.} Agents who
+science.\footnote{See \citet{kelley1980} for a review.} Agents who
 suffer from misattribution bias will attribute successes to their own
@@
 framework that can be directly implemented in a laboratory experiment.
-The goal is to identify the which of the 3 forces---the presence of
-learning traps, mispecified initial beliefs, or missatribution
+In the experiment subjects make choices and receive feedback that
+depends on their own ability, an exogenous parameter and the choice they
+made. I track their choices as well as their beliefs about their own
+ability. The goal is to identify which of the 3 forces---the presence of
+learning traps, misspecified initial beliefs, or missatribution
 bias---better explains the observed behavior. To determine the fit of
@@
 
-I also study whether the misspecification is inherently linked to the
-ego-relevance the parameters or a more general phenomenon. I vary the
-degree of ego-relevance by introducing a treatment in which subjects
-learn about the ability of another participant. In this treatment, the
-participants know only the gender and nationality of the other, which
-can induce stereotypes---a different type of misspecification.\\
+I also study whether the learning mechanism is inherently linked to the
+ego-relevance the parameters or if it is a more general phenomenon. I
+vary the degree of ego-relevance by introducing a treatment in which
+subjects learn about the ability of another participant. In this
+treatment, the participants know only the gender and nationality of the
+other, and thus can induce stereotypes---a different type of
+misspecification.\\
 If correct learning about the parameters happens at higher rates in the
@@
 Although some agents do fall into learning traps, I find that the
-behavior of most subjects is better explained by misattribution bias. I
-also find that misattribution is no more prevalent in the ego-relevant
-than in the stereotype condition. This suggests that the main driver of
-the misspecification is the updating proceduce. However, the underlying
-mechanism by which the bias is generated may be different in both
-treatments: While in the ego-relevant condition, the intuitive
-explanation behind the bias is that the agent prefers to hold themselves
-in high esteem, in the stereotype condition it seems to be driven by
-some sort of self-censoring---when subjects realize that they
-underestimated the ability of another participant based on their gender
-and nationality, they over-compensate by overestimating their ability.
+behavior of most subjects is better explained by misattribution bias:
+good news are treated as signaling high ability, while bad news are
+attributed to a low state. I also find that misattribution is no more
+prevalent in the ego-relevant than in the stereotype condition. This
+suggests that the main driver of the misspecification is the updating
+proceduce; however, the underlying mechanism by which the bias is
+generated may be different in both treatments: While in the ego-relevant
+condition subjects prefer to hold themselves in high esteem, in the
+stereotype condition updating seems to be driven by some sort of bias
+overcorrection---when subjects realize that they underestimated the
+ability of another participant based on their gender and nationality,
+they compensate by overestimating their ability.
 
@@
 model-heterogeneity in the sample. I find that even at an individual
-level the behavior is better explained by misattribution bias for most
-subjects. There is a smaller group of subjects that can be better
-explained through dogmatic beliefs and hypothesis testing and none of
-them behave in line with the fully Bayesian benchmark.
+level the behavior is better explained by a general model of
+misattribution bias for most subjects. There is a smaller group of
+subjects that can be better explained through dogmatic beliefs and
+hypothesis testing and none of them behave in line with the fully
+Bayesian benchmark.
 
@@
 predictions of each of the theories. Then I introduce a unifying example
-and my hypotheses. I then describe the experimental design and the
-results, as well as the estimation of the parameters.
+and my hypotheses. In section 4 I describe the experimental design and
+in section 5 I present the data and the results. Section 6 outlines the
+estimation of the parameters and the model fit analysis.
 

### 2023-10-15 Paper/draft.Rmd
Smm estimation, write section and rerun

@@
 ---
-title: "Learning with Misspecified Models: the case of overestimation"  
+title: "Learning with Mental Models: the case of overestimation"  
 date: '`r format(Sys.time(), "%B %d, %Y")`'
@@
 The goal is to
-identify which of the 3 forces---the presence of learning traps, misspecified initial beliefs, or missatribution 
+identify which of the 3 forces---the presence of learning traps, misspecified initial beliefs, or misatribution 
 bias---better explains the observed behavior. To determine the fit of the models, I compare the behavior
@@
 
-I also study whether the learning mechanism is inherently linked to the ego-relevance the parameters 
+I also study whether the learning mechanism is inherently linked to the ego-relevance of the parameters 
 or if it is a more general phenomenon. I vary the degree of ego-relevance by introducing a 
@@
 no more prevalent in the ego-relevant than in the stereotype condition. This suggests 
-that the main driver of the misspecification is the updating proceduce; however, the underlying 
+that the main driver of the misspecification is the updating procedure; however, the underlying 
 mechanism by which the bias is generated may be 
@@
 
-Estimation of the parameters of the self-attribution bias is more involved than estimation of the switching
-threshold. In this case, there is no obvious identification strategy that provides a simple estimate 
-of the parameters. Instead, I use the simulated method of moments to estimate the parameters of the model.
-
-In particular, I simulate the behavior of the self-attribution bias for each possible prior and over 
-a grid of parameters. I make the simplifying assumption that the distortion is symmetric across good and bad news.
-That is, I assume that $c(\theta_H, \omega, \text{good news})=c(\theta, \omega_L, \text{bad news})=:c_g$ and that 
-$c(\theta_M, \omega, \text{bad news})=c(\theta, \omega_M, \text{good news})=:c_b$. In addition, I normalize the 
-remaining cases to be equal to 1. This leaves me with only 2 parameters to estimate.
-
-The moments that I match in the data are the reaction to good news and the reaction to bad news. In particular,
-I match the average change in effort in response to good news and the average change in effort in response to bad news.
-That is I match the following moments:
-
-$$
-\bar{G} = \frac{1}{N}\sum_{i=1}^N \frac{1}{T}\sum_{t=1}^T \mathbb{I}\{o_t > \bar{o}\} \cdot (e_t - e_{t-1}) 
-$$
-$$
-\bar{B} = \frac{1}{N}\sum_{i=1}^N \frac{1}{T}\sum_{t=1}^T \mathbb{I}\{o_t < \bar{o}\} \cdot (e_t - e_{t-1})
-$$
-where $N$ is the number of subjects in the sample, $T$ is the number of rounds in the experiment.
-
-I then use the simulated method of moments to estimate the parameters of the model. In particular, I
-simulate the behavior of the model for each possible prior and over a grid of parameters. I then
-calculate the average change in effort in response to good news and the average change in effort in
-response to bad news for each possible prior and over the grid of parameters and across $I$ simulated 
-indiviaduals. 
-I then minimize the objective function given by the sum of squared differences between the simulated
-moments and the empirical moments. That is, I solve the following problem
+I use the simulated method of moments to estimate the distortion parameters of the misattribution bias model.
+There is a toltal of 6 parameters in the model, however, I assume that the distortion is symmetric for good and bad news.
+Formally, I assume that
+$c(\theta_H, \omega, \text{good news})=c(\theta, \omega_L, \text{bad news})$, $c(\theta_M, \omega, \text{good news})=c(\theta, \omega_M, \text{bad news})$ and $c(\theta_L, \omega, \text{good news})=c(\theta, \omega_H, \text{bad news})$.
+
+To estimate them I use 4 moment conditions.
+The moments that I use are the regression coefficients from the reaction to good and bad news.
+That is: the slope and intercept of the relationship between the number of successes in the last signal sample and the change in effort as a consequence.
+The slope and intercept are different for good and bad news, which gives 4 moment conditions.
+To determine good news are samples for which there are more successes than failures.
+Bad news are outcome samples for which there are more failures than successes.
+The sample moments are reported in \ref{tab:regression-net} and correspond to the following regression model:
+
+$$ \Delta effort_{it} = \beta_0 + \beta_1 signal_{i t-1} + \beta_2\mathbb{I}\{good \:news_{i t-1}\} + \beta_3{I}\{good\:news\}*signal_{i t-1} $$
+where $i$ is an individual and task level index (each subject in each of the six tasks in the experiment represents a single observed path) and $t$ is a round_number index that ranges from 1 to 11.
+The variable $signal_{i t-1}$ is the number of successes observed in round $t-1$, and the change in effort is $\Delta effort_{it}=effort_{it}-effort_{it-1}$.
+The coefficients $\beta_0$ and $\beta_1$ are the moments that rule the interaction between bad news and effort change, while $\beta_0+\beta_2$ and $\beta_1 +\beta_3$ are the intercept and the slope for the relation between effort change and good news.
+
+In order to find the parameters that correspond to the observed moments I rely on simulation.
+Rather than theoretically deriving the moments, I simulate what a large number of subjects would have done conditional on parameter values.
+I do this for a large number of parameter combinations that statisfy the restrictions on them.
+For each set of parameter values, I compute
+the simulated moments.
+These simulations are meant to approximate the population moments conditional on parameters.
+I then look for the set of parameters that minimize the weighted quadratic distance between the sample moments and the population moments.
+The weight I place on each of the moments is the inverse of the variance of the moment in the sample.
+
+The model makes deterministic predictions about the choices subjects should make after each possible history of signals.
+However, in the data I observe significant variation.
+In order to account for variation in the simulation I introduce a noise parameter $\varepsilon_{it}\sim U[0, 1]$ which introduces a tremble in the choice of subject $i$ in period $t$.
+If $\varepsilon_{it}<0.1$ the subject chooses an effort level at random.
+Otherwise they choose the optimal effort as predicted by the model.
+More details on the simulation can be found in the Appendix.
+While the estimated parameters are all interior solutions with $\hat{c} = (0.4, 0.7, 1.5)$.
+
+Using the estimated parameters I proceed to simulate the deterministic choice paths for each of the models.
 
 # Model fit
+
+I simulate each of the models for each possible combination of type and state $(\theta, \omega)$.
+I then compute te distance from the observed paths of each subject to each of the simulated paths that match the subjects type and state.
+I average across all paths for a single subject (each subject participated in 6 distinct effort tasks) and determine which model is a better
+explanation for that subject's behavior by finding the one that gives the minimal average distance between the observed behavior and the simulation.
+
+In detail, let $e_{ikt}$ be the effort chosen by subject $i$ in task $k$ at round $t$. And let $\tilde{e}_{t}(\theta, \omega, j)$
+be the simulated choices using model $j$ for a subject of type $\theta$ in state $\omega$.
+And let $j$ be dogmatic, switcher, attribution or Bayesian.
+I solve the following problem to determine the best fitting model for each subject $i$.
+
+$$ arg\min_j \sum_k \frac{1}{T}\sum_t{\left[e_{ikt}-\tilde{e}_{t}(\theta, \omega, j)\right]} $$
+The histogram in Figure \ref{fig:best-models} shows the distribution of the best fitting models in the sample. The average fit of each model is reported in the Appendix.
+
+![Distribution of the best fitting models at a subject level in each treatment](../figures/model_fit_histogram.png){#fig:best-models}
 
@@
 
+## Simulated Method of Moments
+
+I simulate the model on a grid with 3 parameters: $c_1$, $c_2$ and $c_3$ such that $c_1<c_2<c_3$.
+All parameters on the grid take values between 0.1 and 2 with a distance of 0.1 between them.
+I simulate 1000 paths of choices of length 11 for each of the possible combinations of parameters.
+For each set of parameters I compute the moments by estimating the regression model described in section 8.2.
+Represent the simulated models for parameter vector $c$ by $\tilde{m}(c)$ and the sample moments by $m$.
+The estimates of the parameters are given by
+
+$$ \hat{c} = arg\min_c (\tilde{m}(c)-m)^T W(\tilde{m}(c)-m)$$
+It is also worth noting that since the randomness if fixed in the experimental data by setting a seed, I do the same in the simulation and use the same seed as in the experimental environment to account for the correlation in observed signals that exists in the sample.
+
+To determine the parameters $\theta$ and $\omega$ in the simulated individuals, I draw from the empirical distribution.
+
 ## Model simulation
@@
 dogmatic belief. For the Bayesian and the self-attribution bias, I use a uniform belief on theta.
+
+## Model fit
+
+The average model fit for each of the simulated models is reported in Figure \ref{fig:model-fit}.
+
+![Average distance of subject behavior to the best fitting model](../figures/model_min_distance.png){#fig:model-fit}
 

### 2023-10-15 Paper/draft.tex
Smm estimation, write section and rerun

@@
 \hypersetup{
-  pdftitle={Learning with Misspecified Models: the case of overestimation},
+  pdftitle={Learning with Mental Models: the case of overestimation},
   pdfauthor={Jimena Galindo},
@@
 
-\title{Learning with Misspecified Models: the case of overestimation}
+\title{Learning with Mental Models: the case of overestimation}
 \author{Jimena Galindo}
-\date{October 14, 2023}
+\date{October 15, 2023}
 
@@
 ability. The goal is to identify which of the 3 forces---the presence of
-learning traps, misspecified initial beliefs, or missatribution
+learning traps, misspecified initial beliefs, or misatribution
 bias---better explains the observed behavior. To determine the fit of
@@
 I also study whether the learning mechanism is inherently linked to the
-ego-relevance the parameters or if it is a more general phenomenon. I
+ego-relevance of the parameters or if it is a more general phenomenon. I
 vary the degree of ego-relevance by introducing a treatment in which
@@
 suggests that the main driver of the misspecification is the updating
-proceduce; however, the underlying mechanism by which the bias is
+procedure; however, the underlying mechanism by which the bias is
 generated may be different in both treatments: While in the ego-relevant
@@
 
-Estimation of the parameters of the self-attribution bias is more
-involved than estimation of the switching threshold. In this case, there
-is no obvious identification strategy that provides a simple estimate of
-the parameters. Instead, I use the simulated method of moments to
-estimate the parameters of the model.
-
-In particular, I simulate the behavior of the self-attribution bias for
-each possible prior and over a grid of parameters. I make the
-simplifying assumption that the distortion is symmetric across good and
-bad news. That is, I assume that
-\(c(\theta_H, \omega, \text{good news})=c(\theta, \omega_L, \text{bad news})=:c_g\)
-and that
-\(c(\theta_M, \omega, \text{bad news})=c(\theta, \omega_M, \text{good news})=:c_b\).
-In addition, I normalize the remaining cases to be equal to 1. This
-leaves me with only 2 parameters to estimate.
-
-The moments that I match in the data are the reaction to good news and
-the reaction to bad news. In particular, I match the average change in
-effort in response to good news and the average change in effort in
-response to bad news. That is I match the following moments:
-
-\[
-\bar{G} = \frac{1}{N}\sum_{i=1}^N \frac{1}{T}\sum_{t=1}^T \mathbb{I}\{o_t > \bar{o}\} \cdot (e_t - e_{t-1}) 
-\] \[
-\bar{B} = \frac{1}{N}\sum_{i=1}^N \frac{1}{T}\sum_{t=1}^T \mathbb{I}\{o_t < \bar{o}\} \cdot (e_t - e_{t-1})
-\] where \(N\) is the number of subjects in the sample, \(T\) is the
-number of rounds in the experiment.
-
-I then use the simulated method of moments to estimate the parameters of
-the model. In particular, I simulate the behavior of the model for each
-possible prior and over a grid of parameters. I then calculate the
-average change in effort in response to good news and the average change
-in effort in response to bad news for each possible prior and over the
-grid of parameters and across \(I\) simulated indiviaduals. I then
-minimize the objective function given by the sum of squared differences
-between the simulated moments and the empirical moments. That is, I
-solve the following problem
+I use the simulated method of moments to estimate the distortion
+parameters of the misattribution bias model. There is a toltal of 6
+parameters in the model, however, I assume that the distortion is
+symmetric for good and bad news. Formally, I assume that
+\(c(\theta_H, \omega, \text{good news})=c(\theta, \omega_L, \text{bad news})\),
+\(c(\theta_M, \omega, \text{good news})=c(\theta, \omega_M, \text{bad news})\)
+and
+\(c(\theta_L, \omega, \text{good news})=c(\theta, \omega_H, \text{bad news})\).
+
+To estimate them I use 4 moment conditions. The moments that I use are
+the regression coefficients from the reaction to good and bad news. That
+is: the slope and intercept of the relationship between the number of
+successes in the last signal sample and the change in effort as a
+consequence. The slope and intercept are different for good and bad
+news, which gives 4 moment conditions. To determine good news are
+samples for which there are more successes than failures. Bad news are
+outcome samples for which there are more failures than successes. The
+sample moments are reported in \ref{tab:regression-net} and correspond
+to the following regression model:
+
+\[ \Delta effort_{it} = \beta_0 + \beta_1 signal_{i t-1} + \beta_2\mathbb{I}\{good \:news_{i t-1}\} + \beta_3{I}\{good\:news\}*signal_{i t-1} \]
+where \(i\) is an individual and task level index (each subject in each
+of the six tasks in the experiment represents a single observed path)
+and \(t\) is a round\_number index that ranges from 1 to 11. The
+variable \(signal_{i t-1}\) is the number of successes observed in round
+\(t-1\), and the change in effort is
+\(\Delta effort_{it}=effort_{it}-effort_{it-1}\). The coefficients
+\(\beta_0\) and \(\beta_1\) are the moments that rule the interaction
+between bad news and effort change, while \(\beta_0+\beta_2\) and
+\(\beta_1 +\beta_3\) are the intercept and the slope for the relation
+between effort change and good news.
+
+In order to find the parameters that correspond to the observed moments
+I rely on simulation. Rather than theoretically deriving the moments, I
+simulate what a large number of subjects would have done conditional on
+parameter values. I do this for a large number of parameter combinations
+that statisfy the restrictions on them. For each set of parameter
+values, I compute the simulated moments. These simulations are meant to
+approximate the population moments conditional on parameters. I then
+look for the set of parameters that minimize the weighted quadratic
+distance between the sample moments and the population moments. The
+weight I place on each of the moments is the inverse of the variance of
+the moment in the sample.
+
+The model makes deterministic predictions about the choices subjects
+should make after each possible history of signals. However, in the data
+I observe significant variation. In order to account for variation in
+the simulation I introduce a noise parameter
+\(\varepsilon_{it}\sim U[0, 1]\) which introduces a tremble in the
+choice of subject \(i\) in period \(t\). If \(\varepsilon_{it}<0.1\) the
+subject chooses an effort level at random. Otherwise they choose the
+optimal effort as predicted by the model. More details on the simulation
+can be found in the Appendix.
+
+Using the estimated parameters I proceed to simulate the deterministic
+choice paths for each of the models.
 
@@
 \section{Model fit}\label{model-fit}}
+
+I simulate each of the models for each possible combination of type and
+state \((\theta, \omega)\). I then compute te distance from the observed
+paths of each subject to each of the simulated paths that match the
+subjects type and state. I average across all paths for a single subject
+(each subject participated in 6 distinct effort tasks) and determine
+which model is a better explanation for that subject's behavior by
+finding the one that gives the minimal average distance between the
+observed behavior and the simulation.
+
+In detail, let \(e_{ikt}\) be the effort chosen by subject \(i\) in task
+\(k\) at round \(t\). And let \(\tilde{e}_{t}(\theta, \omega, j)\) be
+the simulated choices using model \(j\) for a subject of type \(\theta\)
+in state \(\omega\). And let \(j\) be dogmatic, switcher, attribution or
+Bayesian. I solve the following problem to determine the best fitting
+model for each subject \(i\).
+
+\[ arg\min_j \sum_k \frac{1}{T}\sum_t{\left[e_{ikt}-\tilde{e}_{t}(\theta, \omega, j)\right]} \]
+The histogram in Figure \ref{fig:best-models} shows the distribution of
+the best fitting models in the sample. The average fit of each model is
+reported in the Appendix.
+
+\begin{figure}
+\hypertarget{fig:best-models}{%
+\centering
+\includegraphics{../figures/model_fit_histogram.png}
+\caption{Distribution of the best fitting models at a subject level in
+each treatment}\label{fig:best-models}
+}
+\end{figure}
 
@@
 
+\hypertarget{simulated-method-of-moments}{%
+\subsection{Simulated Method of
+Moments}\label{simulated-method-of-moments}}
+
+I simulate the model on a grid with 3 parameters: \(c_1\), \(c_2\) and
+\(c_3\) such that \(c_1<c_2<c_3\). All parameters on the grid take
+values between 0.1 and 2 with a distance of 0.1 between them. I simulate
+1000 paths of choices of length 11 for each of the possible combinations
+of parameters. For each set of parameters I compute the moments by
+estimating the regression model described in section 8.2. Represent the
+simulated models for parameter vector \(c\) by \(\tilde{m}(c)\) and the
+sample moments by \(m\). The estimates of the parameters arw given by
+
+\[ \hat{c} = arg\min_c (\tilde{m}(c)-m)^T W(\tilde{m}(c)-m)\] It is also
+worth noting that since the randomness if fixed in the experimental data
+by setting a seed, I do the same in the simulation and use the same seed
+as in the experimental environment to account for the correlation in
+observed signals that exists in the sample.
+
 \hypertarget{model-simulation}{%
@@
 self-attribution bias, I use a uniform belief on theta.
+
+\hypertarget{model-fit-1}{%
+\subsection{Model fit}\label{model-fit-1}}
+
+The average model fit for each of the simulated models is reported in
+Figure \ref{fig:model-fit}.
+
+\begin{figure}
+\hypertarget{fig:model-fit}{%
+\centering
+\includegraphics{../figures/model_min_distance.png}
+\caption{Average distance of subject behavior to the best fitting
+model}\label{fig:model-fit}
+}
+\end{figure}
 

### 2023-10-15 Paper/compile_paper.R

@@ -6,3 +6,8 @@ knitr::opts_chunk$set(eval=T, echo=F, warning=F, message=F, cache=F)
 
 # compile the paper
 rmarkdown::render("Paper/draft.Rmd", output_format = "pdf_document")
+
+rmarkdown::render("Paper/Intro.Rmd", output_format = "pdf_document")
+
+
+

### 2023-10-15 Paper/Intro.Rmd
Separate file with only intro

--- 2023-10-14 Paper/draft.Rmd
@@
 and the model fit analysis.
-
-# Theoretical Framework
-
-The theories that I consider make predictions in two distinct frameworks. I first detail each theory 
-within their original framework and then develop a unifying example that allows me to
-compare the predictions of all of them. In framework 1 I consider a setting in which the an agent observes
-a continuous output and infers the underlying state. In framework 2, the agent observes a binary 
-outcome and infers the underlying probability of success. In both frameworks, I consider two nested theories 
-of learning.
-
-## Framework 1
-
-An agent is of type $\theta \in \Theta$ and faces an unknown exogenous state $\omega$ drawn from some 
-density $f$ over $\Omega$. The agent knows the 
-distribution of $\omega$ but not its realized value. His belief about the state, 
-$p_0(\omega)$, coincide with the true distribution, $f$; and his belief about the type is $p_0(\theta)$. 
-Let the agent's true type be $\theta^{*}$,  and the realized state be $\omega^{*}$.
-
-An agent's belief about the type is \emph{misspecified} if it assigns probability zero to their true type. Furthermore, the agent is 
-\emph{dogmatic} if he holds a degenerate belief that places probability one on being of type $\hat{\theta}$. An 
-agent can be dogmatic and misspecified, in which case $\hat{\theta} \neq \theta^*$ and $p_0(\hat{\theta}) = 1$.
-
-The agent chooses an action $a\in A$ and observes a noisy outcome $h$. 
-The outcome is a function of the agent's type, the state, and
-the action. In particular $h = h(\theta^*, \omega^*, a) + \varepsilon$ with $h(\cdot)$ increasing in both $\theta^*$ and $\omega^*$, 
-and such that conditional on a pair of parameters $(\theta, \omega)$, there is a unique optimal action. 
-additionally, $\varepsilon\sim N(0, \sigma)$ is noise in the output.
-
-After observing the outcome, the agent updates his beliefs about $\theta$ and $\omega$ using some algorithm and moves on to the next period.
-He repeats this process infinitely many times. I make the simplifying assumption that the agent is myopic and chooses the action 
-that maximizes the payoff in each period. This assumption simplifies the analysis and plays a role in whether an agent who updates
- their beliefs using Bayes rule would learn the truth or not, however, for the main theory discussed in this section, the results hold
- even when relaxing this assumption. The behavior of a forward-looking agent is further discussed in the conclusion.
-
-A key notion in this setting is that of a self-defeating equilibrium\footnote{This notion is an adaptation of the Berk-Nash equilibrium in 
-\citet{Esponda2016} to this setting with only one agent}. 
-A \emph{self-defeating equilibrium} is a belief and action pair such that the agent's belief about their type is misspecified and the 
-outcome generated by the action is consistent with the misspecified belief. This means that the average outcome under the true type and the true 
-state equals the average output the agent expects under the misspecified belief. The agent's belief is said to be 
-\emph{stable} when this happens.
-
-Within this framework, I consider two nested theories of belief updating: the first one is a dogmatic modeler from @Heidhues2018,
-The second one is a switcher, as in @Ba2023. The dogmatic modeler can be seen as a switcher with an infinitely sticky initial belief
-so the two theories are nested. However, outside of the limiting case, they produce different 
-predictions about the agent's behavior. I discuss each of them separately in what follows.
-
-### The Dogmatic Modeler
-
-Take the action space to be the same as the state space $\Omega$ and  $\Omega =A=[\underline{a}, \infty)$.
-
-A dogmatic agent does not update their beliefs about $\theta$, instead, he holds a degenerate belief that places probability on 
-$\hat{\theta}$, which is potentially misspecified. 
-In this case, no matter
-how much information he gathers against being of type $\hat{\theta}$, he will not update his beliefs about it. 
-Any discrepancies between the 
-observed outcomes and his believed type are incorporated using the Bayes rule to update his beliefs about $\omega$.
-@Heidhues2018 show that, under certain assumptions on the per-period utility,\footnote{The assumptions are that 
-$u$ is twice continuously differentiable with: (i)$u_{aa}<0$ and $u_a(\underline{a},  \theta, \omega)>0>u_a(\Bar{a}, \theta, \omega)$, 
-(ii) $u_{\theta}, u_{\omega}>0$ and (iii) $u_{a\theta}<0$ and $u_{a\omega}>0$. Where $\underline{a}$ is the
-minimal action and $\Bar{a}$ is the maximal one. 
- The direction of the derivatives is a normalization
-and the results would hold even when the signs are reversed.} 
-a dogmatic modeler will inevitably fall into a self-defeating equilibrium. The equilibrium will be such that
-the outcomes they observe reinforce their belief on $\omega$ in such a way that as $t\to\infty$ the agent will 
-be sure that
-the state is some $\omega^{'}$ consistent with their believed type and the observed data. In other words, 
-they will be in a self-defeating equilibrium with a stable belief that places probability one on the incorrect
-parameters $(\hat{\theta}, \omega_{\infty})$
-
-The mechanism by which the dogmatic agent falls into the self-defeating equilibrium is the following: Suppose the agent holds the 
-misspecified belief that they are type $\hat{\theta}>\theta^*$. For any prior over $\omega$, the agent will be disappointed by the outcome.
-He expected a gain of $h(\hat{\theta}, \mathbb{E}(\omega), a)$ but instead observes  $h(\hat{\theta}, \omega^*, a)$. 
-There are two 
-possible sources for the disappointment: the first is that the realized state is lower than the expected state; the second source is that the
-agent is of type $\theta^*$ and therefore, for all possible states, his gain will be lower than what he expected. Because the agent is dogmatic,
-he will not update his beliefs about $\theta$ and as a consequence will attribute the disappointment to the state being lower than expected.
-He will continue to update in this way until he converges to a belief about $\omega$ that is stable. Such a belief will 
-explain the observed utility perfectly and allow the agent to rationalize his dogmatic belief about $\theta$. 
-Under the assumptions of @Heidhues2018, there is a unique value of $\omega$ at which the belief is stable, I will refer to such value
-as $\omega_\infty$.
-This mechanism is illustrated in Example 1.
-
-**Example 1: ** 
-_Set $A = \Omega=[\underline{a}, \infty)$ and consider a student with intrinsic ability $\theta^*\geq 0$ who faces a grading procedure 
-$\omega^*$ that is unknown to them. 
-The student knows that a higher $\omega^*$ is more likely to yield a higher grade. In particular, she knows the grade is given by 
-$(\theta^*+a)\omega^*$._
-
-_The student must choose an effort level $a$, which determines her grade. For whatever the chosen effort level, 
-the student must pay a cost $c(a) = \frac{1}{2}a^2$ and observes a grade of $(\theta^*+a)\omega^*$. She repeats 
-this process for infinitely many periods. 
-Assume also that the student's prior is such that $\mathbb{E}[\omega]= \omega^*$ and she is dogmatic 
-about being of 
-type $\hat{\theta}>\theta^*$.\footnote{The example is illustrated for an overconfident student but 
-the results are symmetric for a dogmatic student who initially 
-places probability one on some $\tilde{\theta}<\theta^*$.}
-Therefore, the student's payoff in period $t$ is given by _
-
-\begin{equation}
-u_t(a_t; \theta^*, \omega^*) = (\theta^*+a_t)\omega^* - \frac{1}{2}a^2 + \varepsilon_t
-\end{equation}
-
-_Under this specification, the myopic optimal effort level is $a_t^* = \omega^*$. 
-Because the student does not know $\omega^*$,
-he will choose $a_t = \mathbb{E}_t(\omega)$ where the expectation is taken with respect to the 
-student's belief at the beginning of
-period $t$. If she does not revise his effort choice for $k$ periods, she will receive 
-an average utility of 
-$(\theta^*+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}$ but he was expecting an average utility of 
-$(\hat{\theta}+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}$. In response, she will apply Bayes 
-rule to update his beliefs about
-$\omega$ to get the posterior belief with 
-$\mathbb{E}_{t+k}[\omega] = \frac{(\theta^{*} + \omega^{*})\omega^{*}}{\hat{\theta} + \omega^{*}}$
-which is lower than the initial belief. This will cause the student to choose a lower effort at $t+k$. As a result, she will again
-receive an average utility that is lower than what he expected which will cause her belief to drift further down. This process will
-continue until the average utility equals her expected utility under the dogmatic belief that assigns probability 1 to $\hat{\theta}$. 
-At that point, the student will have reached a self-defeating equilibrium and she will continue to choose sub-optimal effort forever. _
-
-Although the model of a dogmatic modeler rationalizes the prevalence of overconfident (underconfident) beliefs, the
-assumption that the agent has a degenerate belief and no mechanism through which he can update such 
-belief is very restrictive. An
-alternative approach is proposed by @Ba2023. She proposes an extension of the dogmatic agent who 
-is able to swithch from one dogmatic 
-belief to another. By doing so, the agent can avoid the self-defeating equilibria and end up being dogmatic and correctly specified.
-
-### The Switcher
-
-An agent is a \emph{switcher} if they behave as a dogmatic, but are willing to entertain the possibility that they are of a different type.
-In particular, when they start off as a misspecified dogmatic, they are willing to switch to a different dogmatic belief if the data is
-convincing enough. Their prior is still degenerate and assigns probability one to a particular type, and zero to 
-all other types. This means that a Bayesian update on $\theta$ does not change their beliefs about the type.
-However, they are willing to entertain two such beliefs and have a mechanism by which they decide which belief to adopt at any period $t$.
-
-In order to abandon their initial dogmatic belief, the agent needs to observe a sequence of outcomes 
-that are sufficiently unlikely
-to have happened if they were of the type they initially believed. In order to evaluate if the evidence is convincing enough, 
-they keep track of the likelihood that each of the
-possible types generated the data. If the likelihood ratio is sufficiently large, the agent will switch to the alternative
-and behave as if they are dogmatic about the new type.
-
-In particular, for an agent that starts with a dogmatic belief that they are of type $\hat{\theta}$ but is willing to consider
-the alternative explanation that they are of type $\tilde{\theta}$, the agent will switch to the alternative if:
-
-$$\frac{p[h^t|\tilde{\theta}]}{p[h^t|\hat{\theta}]} > \alpha\geq 1$$
-
-Where $h^t$ is the history of outcomes up to time $t$ and $\alpha$ is the switching threshold.\footnote{Notice that if $\alpha \to \infty$, the behavior of the switcher will be indistinguishable from that of the Dogmatic modeler.
-In this sense, the switcher is a generalization of the dogmatic type.} By keeping track of the 
-likelihood ratio, the agent can perform a \emph{Bayesian hypothesis test} and adopt the Dogmatic belief that best fits 
-the data.\footnote{In a related problem \citet{Schwarstein2021} proposes a similar updating procedure which relies on the Bayesian 
-hypothesis test. However, in their model there is a sender who optimally chooses to propose a model that fits the data}
-
-By allowing the agent to keep track of the likelihoods and switching to an alternative type, the switcher can avoid the 
-self-confirming equilibria. However, if the prior belief on $omega$ is sufficiently tight around
-a self-defeating equilibrium, the switcher might look identical to the dogmatic even in a case where $\alpha$ is not too large.
-This happens because under the agent's prior, the likelihood ratio is unlikely to grow as fast as it is needed to escape 
-the self-defeating equilibrium. In such situations, we say that the misspecified belief is persistent.
-
-## Framework 2
-
-As in framework 1, the agent is of some type $\theta^* \in \Theta$ and the state is $\omega \sim F(\Omega)$. 
-In this case, the agent chooses an action 
-$a\in A$
-and observes a binary outcome that is either a success or a failure. Denote the outcome by $o \in \{s,f\}$. The probability of 
-observing a success is increasing in $\theta$ and in $\omega$. Whenever the agent observes a success, he gets a payoff $v>0$ and
-whenever the outcome is a failure, the payoff is 0.  In addition, the probability of success is such that for each state, 
-there is a unique optimal action that maximizes the agent's expected payoff. Therefore, the probability 
-of success can be seen as a monotone transformation of the utility from Framework 1.
-
-I focus on two nested theories that have been widely studied within this framework: Full Bayesian updating and self-serving attribution 
-bias. I explain each of these classical models of belief updating in what follows
-
-### The Bayesian
-
-A Bayesian agent simultaneously updates their beliefs about $\theta$ and $\omega$ by using Bayes' rule. 
-The posterior at period t+1 about $\theta$ after observing outcom $o$ is given by:
-$$
-p_{t+1}(\theta, \omega| h^t) = \frac{p[o|\theta, \omega]p_t(\theta, \omega)}{\sum_{(\theta', \omega')}p[o|\theta', \omega']p_t(\theta', \omega')}
-$$
-
-Where $p_{t}$ is the belief at the start of period $t+1$ and includes all the information gathered so far.
-
-Bayesian agents choose the effort level that maximizes their expected flow payoff by taking expectations over
-their prior beliefs about $\theta$ and $\omega$. Since agents are myopic, even though all the parameters 
-could be identified with enough variation in choices, there will be instances in which the Bayesian will not
-learn even with infinite amounts of data. This happens because, by being myopic, they do not internalize 
-the tradeoff between flow payoff
-and learning. This can result in too little experimentation to learn their true type. An alternative to this approach is given 
-by @Hestermann2021 and is discussed in the concluding remarks. Regardless, this approach is useful as a 
-benchamrk for the other theories discussed in this paper.
-
-Also notice that if a fully Bayesian agent has a dogmatic prior, they will never update their beliefs 
-about the parameter that they are dogmatic about. This will imply that they are prone to the same types 
-of errors as the dogmatic modeler in framework 1.
-
-### The Self-Serving Updater
-
-A Self-Serving Bayesian is an agent who uses a biased version of Bayes rule to update their beliefs. 
-They will update their beliefs 
-about the state $\omega$ and his type $\theta$ simultaneously
-by over-attributing successes to a high value of $\theta$ and under-estimating the role of higher $\omega$. Similarly,
-he will attribute failure to a low state to a greater degree than an unbiased agent would. 
-To model the self-serving attribution bias, I take the approach of @benjamin2019, where the posterior odds are given by:
-
-$$
-p_{t+1}(\theta, \omega| h^t) = \frac{p[h^t|\theta, \omega]^{c(\theta, \omega, o_t)}p_t(\theta, \omega)}{\sum_{(\theta', \omega')}p[h^t|\theta', \omega']^{c(\theta, \omega, o_t)}p_t(\theta', \omega')}
-$$
-
-with $c(\theta_H, \omega, o)<c(\theta_M, \omega, o)<c(\theta_L, \omega, o)\leq 1$
-and $c(\theta, \omega_L, o)<c(\theta, \omega_M, o)<c(\theta, \omega_H, o)\leq 1$.
-
-This formulation of the bias means that the agent will over-attribute successes to a high type and 
-under-attribute them to a low type Whereas they will over-attribute failures to a low state and
-under-attribute them to a high state. The bias is introduced by distorting the perceived likelihood 
-that the signal was generated by either high values of $\theta$ when it is a success, or by low 
-values of $\omega$ when it is a failure.  The parameter $c$ determines the degree of bias and imposes
-enough restrictions to ensure that the model is still falsifiable.
-
-# A Unifying Example
-
-In order to compare the predictions of the theories discussed above, I develop a unifying example that allows me to
-isolate the forces behind each of the theories. The example is a modification of the one in @Heidhues2018 and is adapted to 
-implementable in the lab.
-
-The agent can be of one of 3 types: $\theta \in \{\theta_L, \theta_M, \theta_H\}$  with $\theta_H > \theta_M > \theta_L$.
-They face an unknown exogenous success rate
-$\omega \in \{\omega_L, \omega_M, \omega_H\}$ with $\omega_H>\omega_M>\omega_L$. Each of the values of $\omega$ is realized with 
-equal probability. 
-The agent knows the distribution of $\omega$ but not its realized value.
-
-Denote the true type by $\theta^*$ and the true state by $\omega^*$. The agent holds some prior belief about 
-$\theta$\footnote{which is potentially misspecified as in the dogmatic and switcher cases discussed above} 
-and chooses a binary gamble $e in \{e_L, e_M, e_H\}$. The agent observes whether the gamble is a success or a failure and 
-gets a payoff of $1$ and if it is a success; they get $0$ otherwise.
-
-The probability of success is increasing in both $\theta$ and $\omega$ and is fully described by the Table \ref{tab:DGP}
-
-\begin{table}[htbp]
-\centering
-
-\begin{tabular}{ c|c|c|c|}
-
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
-  \cline{2-4}
-  $e_H$ & 50 & 20 & 2 \\
-  \cline{2-4}
-  $e_M$ & 45 & 30 & 7 \\
-  \cline{2-4}
-  $e_L$ & 40 & 25 & 20 \\
-
-  \cline{2-4}
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_L$} & \multicolumn{1}{c}{}\\
-\end{tabular}
-\hspace{.3cm} 
-\begin{tabular}{ c|c|c|c|}
-
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
-  \cline{2-4}
-  $e_H$ & 80 & 50 & 5 \\
-  \cline{2-4}
-  $e_M$ & 69 & 65 & 30 \\
-  \cline{2-4}
-  $e_L$ & 65 & 45 & 40 \\
-  \cline{2-4}
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_M$} & \multicolumn{1}{c}{}\\
-\end{tabular}
-\hspace{.3cm} 
-\begin{tabular}{ c|c|c|c|}
-
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
-  \cline{2-4}
-  $e_H$ & 98 & 65 & 25 \\
-  \cline{2-4}
-  $e_M$ & 80 & 69 & 35 \\
-  \cline{2-4}
-  $e_L$ & 75 & 55 & 45 \\
-  \cline{2-4}
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_H$} & \multicolumn{1}{c}{}\\
-\end{tabular}
-
-\caption{Probability of success for each type, gamble and effort level}
-\label{tab:DGP}
-\end{table}
-
-Conditional on a type, the agent's flow payoff is maximized by choosing the gamble that 
-matches the state. For example, if the value of $\omega$ is $\omega_H$, the agent's flow payoff is maximized by 
-choosing $e_H$ and if the state is $\omega_L$ the flow payoff is maximized by choosing gamble $e_L$, regardless of the value of $\theta$. 
-The agent myopically chooses gambles every period to maximize the flow payoff for $T<\infty$ periods.
-
-After observing the outcome of each gamble, the agent updates their beliefs using some procedure and moves on to the next period.
-
-Notice that both $\theta$ and $\omega$ can be identified from the outcomes if enough variation in the effort choices exists.
-This can be seen by confirming that there is no pair of $\theta$ and $\omega$ such that the probability of success is the same for all effort 
-choices. Thus, by changing the effort choice, the agent can learn both their type and the state if they observe enough outcomes.
-
-In this example, for an agent with a dogmatic belief about their type, a self-defeating equilibrium is one in which the agent 
-chooses an effort level that, under the true $\theta$, yields a frequency of success that is consistent with the agent's 
-misspecified belief. That is $P[\text{sucess}|\theta^*, e^*] = P[\text{sucess}|\hat{\theta}, e^*]$ where $e^*$ is the agent's 
-myopic optimal choice.
-
-In the data-generating process described above, there are five such equilibria. For example, if the agent is of type $\theta_M$  but
-mistakenly believes that he is of type $\hat{\theta}=\theta_H$ and the 
-and $\omega^* = \omega_M$, when the effort chosen is $e_L$, the agent will observe a success with 45% chance. Because the agent 
-dogmatically believes that their type is high, they will erroneously conclude that the rate is $\omega_L$. Under this belief,
-the optimal action is $e_L$ which will continue to generate successes with $45%$ probability, further reinforcing
-the incorrect belief. By doing so, the agent forgoes the payoff from gamble $e_M$ which would yield a success with $65\%$ chance.
-
-By including self-confirming equilibria, the example captures the forces from each of the updating mechanisms discussed in the 
-previous section and allows for the comparison of the main forces behind the theories. For realizations of $(\theta, \omega)$ for which there are 
-self-confirming equilibria, the dogmatic agent will fall into the 
-trap whereas the switcher will be able to escape it. Similarly, an agent with self-attribution bias will update their beliefs differently from an unbiased Bayesian, leading
-them to choose different gambles. I exploit such cases in order to test which model is a better fit for how subjects behave in a 
-laboratory experiment.\footnote{because the setting does not match that of @Heidhues2018, there will be situations for which the theory 
-does not provide a prediction. If such cases arise in the lab, they will not be used for the analysis. However, whether a misspecified 
-belief persists or not for the switcher, depends highly on the realized history of signals that he gets.} In what follows I explain 
-the details of how this example was implemented in the lab.
-
-# Experimental Design
-
-I recruited `r length(unique(updates$code))` undergraduate subjects from the CESS lab at NYU who participated in an in-person experiment. 
-Sessions lasted approximately 
-45 minutes and subjects earned an average payment of $\$22.6$. The experiment was programmed using oTree [@otree].
-
-The experiment consisted of 2 treatments: the \emph{ego-relevant} condition and the \emph{stereotype} condition. Subjects participated 
-in only one of the treatments. All subjects within a session participated in the same treatment and the 
-first 4 treatments were assigned the ego-relevant condition; the rest were assigned to the stereotype treatment. 
-The tasks were identical across treatments, 
-except for parameter $\theta$. In the ego-relevant condition $\theta$ is the subject's own performance in a quiz, while in the 
-stereotype condition, it is the performance of a randomly selected subject from another session.
-
-The experiment had 3 parts. In Part 1 subjects had 2 minutes to answer as many multiple-choice questions as they could from a 
-20-question quiz. They did this for quizzes on 6 different topics. The topics were: Math, Verbal 
-Reasoning, Pop-culture and Art, Science and Technology, US Geography, and Sports and Video Games. 
-In this part, they did not know how many questions were available and they were given no feedback.
-
-After taking all 6 quizzes, they proceeded to part 2 where they were asked to guess their score on each of them. 
-In the stereotype 
-treatment they were additionally asked to guess the score of a randomly drawn participant from a previous session. 
-All they knew about the other participant was their gender identity and whether they were US nationals or not.
-For each guess, they had three score options: Low-Score (5 or fewer correct answers), Mid-Score (between 6 and 15 correct answers), 
-High-Score (16 or more). Each of the score categories corresponded to $\theta_L$, $\theta_M$, and $\theta_H$ respectively. 
-They were also asked to say how confident they felt about their choices. They had 4 possible answers: "it was a random guess", 
-"there is another equally likely score", "I am pretty sure", "I am completely sure". 
-These 4 answers are mapped to priors that place probabilities 
-.33, .50, .75, and 1 to the chosen type. The remaining probability is split equally among the other two types. 
-Questions in Part 2
-were not incentivized, but subjects were told that providing an accurate answer would increase their chances of earning more money in 
-the last part of the experiment.
-
-The purpose of Part 2 is to classify subjects into overconfident, underconfident and correctly specified. If a subject 
-guesses their score to be in a higher (lower) category than their true score, they are overconfident (underconfident); if they 
-guess their score to be in the same category as their true score, they are correctly specified. 
-This classification is done for each of the 6 topics separately.
-
-Finally, in Part 3, subjects completed a belief updating task for each of the quizzes. Before starting the task they were reminded of their guess
-for the score. In the ego-relevant treatment, they were reminded of their guess about themselves and in the stereotype treatment they were reminded
-of their guess about the other participant. In the stereotype treatment, they were also reminded of the characteristics of the other participant.
-
-For one topic at a time and in random order,
-they were presented with the three gambles from the example above and were asked to choose one of them. 
-The probability of success was 
-determined by their own score in the ego-relevant condition, and by the score of the other participant in the stereotype condition. 
-Subjects had access to the three probability
-tables in the printout of the instructions at all times and the meaning of each cell was explained in detail.
-
-In the interphase, they had to choose which of the 3 tables they wanted to see before entering their choice in it. This was done as 
-an alternative to a belief elicitation in each round. I take their choice of table to be indicative of their beliefs about
-the underlying type. I chose not to elicit the beliefs at each round to stay true to the forces in framework 1.
-
-Once they have entered their choice, they observe a sample of 10 outcomes from the gamble they chose. After observing the outcomes, 
-they returned to the choice screen and entered a new choice. In the choice screen 
-subjects had access to the entire history of gambles and outcomes for that task as well as a summary of the outcomes so far. 
-Once they entered 11 gambles (and observed 110 outcomes), they moved on to 
-the next topic and repeated the same procedure. They all did this for all 6 topics.
-
-At the end of the experiment, one of the 6 topics was randomly selected to determine the payment. 
-They earned $\$0.20$ for each 
-correct answer in the quiz, and for each success in the task in Part 3 for the selected topic.
-
-Randomness is controlled throughout the experiment and sessions by setting a seed at the beginning of the
-first session. The seed was drawn at random and remained fixed for all sessions.\footnote{The seed that was drawn 
-at the beginning of session 1 was 3452. The same seed was used for all sessions. It is used both for drawing $\omega$ for each of 
-the tasks in the experiment, as well as for drawing the outcomes from the gambles.}
-By doing this I ensure that any two subjects who have the same type and face the same exogenous rate will observe
-the same outcomes. This feature allows me to identify differences across subjects in updating procedures since if they use the same 
-updating procedure, they should be choosing the same gambles.
-
-# Predictions
-
-In this section, I outline the behavior that is predicted by each of the theories discussed above.
-
-## Dogmatic Modeler
-
-Since the domain of the problem is discrete and finite in the example, the predictions of the original theory apply only to 
-the combinations of parameters and initial beliefs for which there is a self-defeating equilibrium. In the example, there are 5 such 
-combinations. For each of them, the dogmatic modeler predicts that the agent will fall into the self-defeating equilibrium and will 
-be able to sustain the misspecified belief forever.
-
-Table \ref{tab:table-dog} describes the 5 self-defeating equilibria and the effort choices that sustain them. The first columns describe the
-combination of parameters and initial beliefs. The last column describes the effort choice that the agent will make in the long run. It is 
-only for these combinations of parameter values and beliefs that the dogmatic model makes predictions within the Unifying example.
-
-**Prediction 1D:** _Whenever an agent is of a type $\theta^*$ but mistakenly believes that they are of a type $\hat{\theta}$, 
-and $(\theta^*, \omega^*, \hat{\theta})$ are such that there is s self-defeating equilibrium, the agent will fall into the
-trap and choose the effort level that sustains the misspecified belief forever._
-
-The model 
-does not make predictions about what happens in cases where there is no stable belief. I assume that because there is 
-no stable belief, the agent will eventually
-have to use some procedure to revise their belief about $\theta$. In such cases, I aim to determine which of the alternative 
-explanations provided by the other theories is a better fit for the data.
-
-\begin{table}[htbp]
-
-    \centering
-    \begin{tabular}{|c|c|c|c|c|}
-        \hline
-        \textbf{True Type ($\theta^*$)} & \textbf{True State ($\omega^*$)} & \textbf{Believed Type ($\hat{\theta}$)} & \textbf{Believed state ($\hat{\omega}$)} & \textbf{Effort} \\
-        \hline
-        \hline
-        $\theta_L$ & $\omega_H$ & $\theta_M$ & $\omega_L$ & $e_L$ \\
-        \hline
-        $\theta_M$ & $\omega_L$ & $\theta_L$ & $\omega_M$ & $e_M$ \\
-        \hline
-        $\theta_M$ & $\omega_M$ & $\theta_H$ & $\omega_L$ & $e_L$ \\
-        \hline
-        $\theta_M$ & $\omega_M$ & $\theta_L$ & $\omega_H$ & $e_H$ \\
-        \hline
-        $\theta_M$ & $\omega_H$ & $\theta_H$ & $\omega_M$ & $e_M$ \\
-        \hline
-
-    \end{tabular}
-    \caption{Stable beliefs and the effort choices that support them for the unifying example}
-    \label{tab:table-dog}
-\end{table}
-
-Although the dogmatic model does not apply to all possible parametrizations and beliefs, whether subjects
-fall into the self-defeating equilibria or not is still informative of the updating procedure that they are using.
-Understanding if the presence of traps is a key feature preventing subjects from learning the optimal action is important
-for understanding the prevalence of overconfidence. Similarly, gaining insight into what happens 
-when there are no traps is important for understanding what are the other reasons why overconfidence 
-might arise and prevail.
-
-## Switcher
-
-Since the switcher starts as the same dogmatic agent, the initial behavior of both types of agents is identical, 
-however, because the switcher is keeping track of the likelihood ratio, they will be able to escape the self-defeating
-equilibrium if the evidence is convincing enough. Therefore there is a positive probability that the switcher will
-adjust their initially misspecified belief about $\theta$ and learn the true state.
-
-**Prediction 1S:** With positive probability, the switcher will escape the self-defeating equilibrium and learn the true state.
-
-One caveat is that when the switcher and the dogmatic agent both start with a correctly specified belief, neither of them 
-will fall into the self-defeating equilibria and thus will look identical even in the long run. This means that
-in order to distinguish between the two theories, I need to look at cases where the agent starts with a misspecified belief.
-
-The probability that the switcher will escape the self-defeating equilibrium depends on the prior belief about $\omega$.
-If the prior is sufficiently tight around the self-defeating equilibrium, the likelihood ratio will not grow fast enough, however, 
-in the example above, the prior is uniform over the states and therefore, the likelihood ratio is more likely to grow fast enough.
-
-## Self-Attribution Bias
-
-The key feature of Self-attribution bias is the asymmetric treatment of good news and bad news. 
-In particular, the agent will over-attribute successes to a high type and under-attribute them to a low type.
-Similarly, they will over-attribute failures to a low state and under-attribute them to a high state.
-This implies that, after observing a failure, the agent will adjust their effort downwards by more than 
-what an unbiased Bayesian would have done. In contrast, after observing a success, the agent will adjust 
-their effort upwards by less than a Bayesian would have done and if the bias is large enough, it could
-be that the agent will not adjust their effort upwards at all, or even decrease their effort in response to a success.
-
-This is in stark contrast with what a Dogmatic modeler would do. A dogmatic modeler always attributes
-any variation in the outcome to the state and never updates their beliefs about $\theta$. Therefore,
-they will always increase their effort choices after a surprising success and decrease it after a failure.
-
-On the other hand, the biased behavior can be in line with the behavior of a switcher. In particular,
-if the agent starts with a misspecified belief on $\hat{\theta}$, and is willing to switch to a belief with 
-$\theta'>\hat{\theta}$, whenever the paradigm shift happens, it will likely be in response to a surprising 
-streak of successes. In this case, when they adjust their belief about $\theta$, they will also 
-adjust their effort choice. Since they were initially underconfident, they had been choosing an effort that was
-too high relative to the true state, and therefore, the effort is likely to fall in response to a 
-surprising streak of success.
-
-**Prediction 1A:** _After observing a failure, the agent will adjust their effort downwards by more than a Bayesian would have done.
-After observing a success, the agent will adjust their effort upwards by less than a Bayesian would have done. If the bias is large enough,
-the agent might not adjust their effort upwards at all, or even decrease their effort in response to a success._
-
-Prediction 1A helps distinguish between the self-attribution bias and the dogmatic modeler. However, it does not help distinguish between
-the self-attribution bias and the switcher. In order to do so, I need to look at cases where the agent starts with a correctly specified belief.
-In these cases, the switcher is very unlikely to switch to a different belief and therefore, the behavior of the switcher will mostly change
-in the same direction as the information he receives. \footnote{If they get a streak of failures they are likely to 
-adjust their effort downwards and if they get a streak of successes they are likely to adjust their effort upwards.} Instead, 
-the self-attribution bias will lead to a different behavior. In particular, even for agents who have a belief 
-that is correctly specified and place a lot of weight on the correct values of $\theta$, the bias will 
-cause these agents to become overconfident after a sequence of successes. This force is not present in the switcher or the dogmatic
-and it is the key feature that allows me to identify a biased updating procedure.
-
-**Prediction 2A:** _After observing a streak of successes, the agent will update their belief about $\theta$ upwards. This will lead to the 
-possibility of observing subjects who start correctly specified and become overconfident._
-
-## The Bayesian
-
-The Bayesian serves as the closest benchmark to a fully rational agent. However, as discussed above, 
-they are still vulnerable to falling into self-defeating equilibria, in which case, their long-run behavior
-will be identical to that of the dogmatic modeler. The main distinguishing feature is that when they do 
-fall into a self-defeating equilibrium, there is no bias in the direction of the misspecification that they 
-end up being trapped in. In contrast, the dogmatic modeler will always be trapped in a misspecified belief
-that they started with and the self-attribution updater will always become overconfident.
-
-**Prediction 1B:** _When an agent starts with a diffused prior and falls into a self-defeating equilibrium,
-they will be equally likely to fall into the underconfident trap as the overconfident trap._
-
-**Prediction 2B:** _Bayesian agents always update their effort choices in the same direction as the information they receive. 
-That is, if they see successes, they would only increase their effort; and if they see failures they would 
-only decrease their effort._
-
-# Stereotypes
-
-So far I have focused only on the case of overconfidence about an ego-relevant parameter. 
-However, each of the models can also be used to explain the prevalence
-of stereotypes. An agent can have a dogmatic belief about the ability of a particular group of people and either under or overestimate
-the associated parameter. Similarly, they can be willing to switch between two dogmatic beliefs about their ability as a switcher would.
-Finally, they can have a biased updating procedure in which they treat good news and bad news asymmetrically.
-
-As such, all the predictions discussed above apply to the case of Stereotypes as well. My analysis of 
-stereotypes will focus only on the degree to which ego-relevance of the type affects the updating procedure and not on the 
-motivations behind the bias. I am particularly interested in whether the explanatory power of the models 
-differs with the degree of ego-relevance of the type.
-
-# Results
-
-## Initial Beliefs and misspecifications
-
-As mentioned in the predictions section, the dogmatic modeler and the switcher are only distinguishable 
-when the agent starts with a misspecified belief. Figure \ref{fig:misspecification-hist} shows the 
-distribution of misspecifications by treatment. The histogram considers the difference between the subject's 
-true score in the quiz and their guess about their score. If their guess is in a higher category than their true score,
-they are overconfident; if it is in a lower category, they are underconfident; and if it is in the same category, 
-they are correctly specified. Overall, `r round(sum(updates$misspecification != 'correct')/nrow(updates), 2)` of the 
-guesses made in the questionnaire were misspecified. The rest of the guesses coincided with the true score. 
-And the distribution of misspecifications is similar across treatments.
-
-![Initial misspecifications by treatment](../figures/misspecification_hist.png){#fig:misspecification-hist}
-
-Although the overall distribution is similar for both treatments, the misspecifications arise for different 
-combinations of characteristics in each treatment. Figure \ref{fig:misspecification-by-treatment} shows a heatmap 
-of the misspecifications that arose in each treatment. In the stereotype treatment, subjects are most underconfident 
-about the performance 
-of other non-American females in Sports and Video Games. In contrast, they are most overconfident about the performance 
-of American men in Verbal Reasoning. In the ego-relevant treatment, subjects are most underconfident about their own
-performance in pop culture and art, while most overconfident about their performance in Verbal Reasoning.
-
-![Initial misspecifications by treatment and characteristics](../figures/misspecifications_characteristics_treatment.png){#fig:misspecification-by-treatment}
-
-Having widespread misspecifications in both treatments is important for the analysis because it allows me to distinguish between the
-dogmatic modeler and the switcher. If there were no misspecifications, the two models would be indistinguishable.
-
-## Learning
-
-In this section, I analyze the learning behavior of subjects in the experiment. There are two parameters 
-that subjects can be learning about: the exogenous parameter $\omega$ and the type $\theta$. 
-Their belief about the exogenous parameter is tracked by their choice of effort, while their belief about the 
-type is tracked by their choice of a matrix in which to enter their effort.
-
-### Learning about the state
-
-In order to analyze the learning about the state, I look at the share of optimal choices that are made at each round.
-I find that although subjects seem to be improving in their choices overall, the last choice coincided 
-with the true state only in 52% of the choices in the last round of each task. This is statistically 
-greater than the initial share of optimal choices ($p<0.01$). However, it is still far from 
-complete learning. It is also important to note that learning is similar across treatments. The 
-share of choices that were consistent with the true state for each round is reported in panel A of 
-Figure \ref{fig:learning-by-groups}.
-
-A closer look at whether people learned or not reveals that there is a good amount of heterogeneity in the
-sample. Panel B of Figure \ref{fig:learning-by-groups} shows the share of optimal choices by round for 
-subjects that chose an effort that matched the state in 3 out of the last 4 rounds. It also shows the 
-share of optimal choices for subjects who chose an effort that matched the state in fewer than 3 out of 
-the last 4 rounds. I label the former as learners and the latter as non-learners, with learners making up
-`r round(sum(updates$learned)/nrow(updates), 2)*100`% of the sample.
-
-![Share of optimal choices by round for subjects who learned (their effort in at least 3 out of tha last 4 choices matched the state), and subjects who did not learn](../figures/learning_groups.png){#fig:learning-by-groups}
-
-In what follows I will try to disentangle the reasons for the lack of learning. I will argue that 
-it is not due to the presence of traps, but rather due to biased updating. According to the theories, 
-the main reason why subjects might not learn is that they have an incorrect belief about the type or 
-they develop an incorrect belief about the type.
-
-### Learning about the type
-
-![Matrix choices by round](../figures/last_button_consistency.png){#fig:matrix-choices-by-round}
-
-Since the elicitation of the belief about the type was not incentivized and not elicited in a standard way, 
-I first need to confirm that subjects were not just randomly choosing a matrix in which to enter their effort.
-The left panel of Figure \ref{fig:matrix-choices-by-round} shows the share of subjects who chose a matrix 
-consistent with their initial reported belief. In round 1, `r round(nrow(updates[round_number == 1 & last_button_consistent == 1])/ nrow(updates[round_number==1]), 2)*100`% 
-of the subjects chose a matrix that was consistent with their initial belief. This indicates that subjects
-were not just randomly choosing a matrix in which to enter their effort. From round 2 onwards, the share
-steadily declines, but still not as far as to indicate a random choice of matrices. This is consistent with
-the subjects moving away from their starting belief through some updating procedure.
-
-On the right panel of Figure \ref{fig:matrix-choices-by-round} I show the share of subjects who chose a matrix
-that is consistent with their true type. Unlike the left panel, there is no clear trend, which indicates that
-although they are moving away from their initial belief, they are not moving towards their true type, which 
-means that overall, misspecification is not decreasing. A closer look at the data reveals a good amount of
-heterogeneity in the underlying behavior.
-
-Figure \ref{fig:transitions} shows the transition matrix for subjects who started in each of the 
-3 possible starting specifications and the specifications that they ended up in at the end of the updating task.
-The two things to note are that the initial belief is the most likely end belief. This is consistent with 
-some degree of stickiness of the misspecifications as the switcher and dogmatic models would predict. However, 
-the data also presents a lot of subjects who started with a correct belief of the type and ended up 
-overestimating it. This is consistent only with the self-attribution bias. Lastly, the subjects who
-initially overestimate the score, are the least likely to learn their true type.
-
-![Transition matrix for subjects who started in each of the 3 possible starting specifications and the specification that they ended up in at the end of the updating task](../figures/misspecification_transitions.png){#fig:transitions}
-
-The transition matrix points towards the presence of self-attribution bias in the data. However, it is
-still possible that there is heterogeneity in the updating procedure across subjects. In the next section
-I will look at the role of self-defeating equilibria in preventing learning. I find that the presence of
-self-defeating equilibria does not seem to be the main deterrent to learning.
-
-## Learning traps
-
-As described above, the presence of stable misspecified beliefs act as learning traps. If an agent falls 
-into one of these traps, bayesian updating will lead them to choose the same effort forever. These self-defeating 
-equilibria allow me to distinguish between the dogmatic modeler and the switcher. If the agent falls into a
-trap and stays there forever, they are more likely to be a dogmatic modeler. If they escape the trap, they
-are more likely to be a switcher or to be updating with some attribution bias.
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-numerator <- length(unique(updates$player_code[updates$trap == 1 & updates$learned == 1]))
-
-# Calculate the denominator
-denominator <- length(unique(updates$player_code[updates$trap == 1]))
-
-# Calculate the ratio
-share_learned <- round(numerator / denominator, 2)
-
-numerator <- length(unique(updates$player_code[updates$trap == 1 & updates$trapped == 1]))
-
-# Calculate the denominator
-denominator <- length(unique(updates$player_code[updates$trap == 1]))
-
-# Calculate the ratio
-share_trapped <- round(numerator / denominator, 2)
-```
-
-Overall, it does not seem to be the presence of traps that is preventing learning. Panel A of Figure \ref{fig:traps-choice}
-shows that the share of subjects who learned in cases where there was a trap is larger than the share of
-subjects who learned in cases where there was no trap. This is true for both treatments. This indicates
-that even in the presence of traps, `r share_learned*100`% of subjects learn. From the share that 
-did not learn when there was a trap. A remaining `r share_trapped*100`% can be accounted for as being 
-trapped.\footnote{A subject is considered trapped when 3 out of their last 4 choices are consistent with 
-a self-defeating equilibrium.} 
-While the rest of the subjects neither learned nor were trapped.
-
-A closer look at the behavior of only the cases in which there were traps reveals that among those who did not
-learn, the choices that support stable beliefs were chosen much more often than among subjects who learned. 
-Figure \ref{fig:traps-choice} shows the share of choices that were consistent with a stable belief for the
-learners and the non-learners. The difference is statistically significant ($p<0.01$). Thus, although the 
-presence of self-defeating equilibria is not the main deterrent to learning, it does seem to be a factor
-in the behavior of those who do not learn.
-
-![Panel A: Share of subjects who learned in cases where there was a trap and in cases where there was no trap.
-Panel B: Share of choices that were consistent with a stable belief for the learners, those who are in a trap and others](../figures/trap_choice.png){#fig:traps-choice}
-
-So far I have accounted for `r round(sum(updates$trapped)/nrow(updates), 2)*100`% subjects as being trapped, and 
-`r round(sum(updates$learned)/nrow(updates), 2)*100`%
-having learned the state correctly. From the remaining `r (1 - round(sum(updates$trapped)/nrow(updates), 2) - round(sum(updates$learned)/nrow(updates), 2))*100`%, 
-`r round(sum(updates$categorized=='neither' & updates$trap==1)/sum(updates$categorized=='neither'), 2)*100`% were prone to traps
-but did not fall into them, therefore they could not have been dogmatic modelers. Alternative explanations
-are that they were switchers who considered an incorrect alternative model, or that they were updating with a bias so large that their effort
-choices were far from optimal. Behavior that is not consistent with either of these falls outside of the 
-scope of the theories discussed above.
-
-My results are consistent with the findings of @Hestermann2021. In a laboratory experiment that
-stays true to Framework 1, they test the predictions of the dogmatic modeler. They find that the average
-pattern in behavior is in the direction of the dogmatic modeler, however, subjects do not fully act as dogmatics as
-their actions do not go as far as to fully support the self-defeating equilibrium. A lot of 
-the differences between the observed behavior in their experiment and the model can be attributed 
-to subjects avoiding the self-defeating equilibria and learning the true state. In contrast to their study, I can 
-provide more insight into the reasons why subjects avoid the self-defeating equilibria.
-
-## Reactions to good and bad news
-
-One of the key features of the self-attribution bias is that the agent will react differently to good news and bad news.
-In particular, they will overreact to bad news and underreact to good news. I define good news to be any sample of outcomes
-for which the realized number of successes is greater than the average number of successes so far. Similarly, I define bad news to be
-any sample of outcomes for which the realized number of successes is smaller than the average number of successes so far.
-In addition, I calculate the difference between the realized number of successes and the average number of successes so far and
-call it the news differential.
-Figure \ref{fig:reaction-news} shows the correlation between change in effort and the news differential, separately for 
-good and bad news.
-
-The overall pattern is that bad news are associated with a decrease in effort, and a 
-more negative news differential is associated with a larger decrease in effort. On the contrary, good news are associated with 
-a small decrease in effort. As mentioned in the predictions section, this is consistent with the self-attribution bias as well
-as with a change of paradigm. It is not consistent with the dogmatic modeler or the Bayesian. Because 
-I do not directly elicit beliefs, it is not possible to distinguish between the self-attribution bias and the change of 
-paradigm with this data alone.
-Nevertheless, the fact that about a third of the subjects started with a correctly specified belief and ended up overconfident
-is consistent only with the self-attribution bias. this points towards the fact that 
-misattribution bias is the most likely explanation for the behavior of the subjects in the experiment.
-
-![Change in effort by news differential](../figures/effort_change_news.png){#fig:reaction-news}
-
-A regression analysis of this same data reveals that indeed, the slopes are different for godd and bad
-news and that the difference is statistically significant.\footnote{I run a robustness check where I define
-good news to be a net-positive sample (half or more of the outcomes observed in the sample received in that round
-were successful) and bad news to be net-negative sample. I find the same pattern in this alternative regression model
-and the results are reported in the appendix.} 
-The regression results are reported in Table \ref{tab:regression}.
-columns 2 and 3 of the table consider the model for each treatment separately. I find no significant differences in 
-the parameters across treatment. This is consistent with the fact that the bias is not driven by the ego-relevance 
-of $\theta$.\footnote{The ego-relevance of $\theta$ is the motivation behind the self-attribution bias, 
-however, the bias itself is due to an incorrect updating procedure in response to good and bad news. The presence of 
-asymmetric updating in the stereotype condition can be due to self-censoring of the subjects. In particular, subjects 
-who initially underestimated the performance of the other participant might have realized their mistake and 
-by overestimating it after good news. This is consistent with the data presented here as well as with 
-the data observed in the transition matrix for stereotypes which is reported in the Appendix}
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE }
-reg <- lm(effort_change ~ good_news + news_diff + news_diff:good_news, data=updates[round_number>1,])
-robust_se <- sqrt(diag(vcovHC(reg)))
-
-# Attach the robust standard errors to the coefficient estimates
-coefs <- coef(reg)
-coefs <- cbind(coefs, robust_se)
-```
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-# run the regression only for treatment  = ego
-reg_ego <- lm(effort_change ~ good_news + news_diff + news_diff:good_news, data=updates[round_number>1 & treatment == 'ego',])
-
-# Attach the robust standard errors to the coefficient estimates
-coefs_ego <- coef(reg_ego)
-coefs_ego <- cbind(coefs_ego, robust_se)
-
-# run the regression only for treatment  = stereotype
-reg_stereotype <- lm(effort_change ~ good_news + news_diff + news_diff:good_news, data=updates[round_number>1 & treatment == 'stereotype',])
-
-# Attach the robust standard errors to the coefficient estimates
-coefs_stereotype <- coef(reg_stereotype)
-coefs_stereotype <- cbind(coefs_stereotype, robust_se)
-```
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-
-bayesian <- updates[, .(round_number, good_news_bay, signal_bay_diff, effort_change_bay)]
-
-setnames(bayesian, c('good_news_bay', 'signal_bay_diff', 'effort_change_bay'), c('good_news', 'news_diff', 'effort_change'))
-
-# run the regression for the bayesian simulation
-reg_bayesian <- lm(effort_change ~ good_news + news_diff + news_diff:good_news, data=bayesian[round_number>1])
-
-# Attach the robust standard errors to the coefficient estimates
-coefs_bayesian <- coef(reg_bayesian)
-coefs_bayesian <- cbind(coefs_bayesian, robust_se)
-```
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-dogmatic <- updates[, .(round_number, good_news_dogmatic, signal_dogmatic_diff, effort_change_dogmatic)]
-setnames(dogmatic, c('good_news_dogmatic', 'signal_dogmatic_diff', 'effort_change_dogmatic'), c('good_news', 'news_diff', 'effort_change'))
-
-# run the regression for the dogmatic simulation
-reg_dogmatic <- lm(effort_change ~ good_news + news_diff + news_diff:good_news, data=dogmatic[round_number>1])
-
-# Attach the robust standard errors to the coefficient estimates
-coefs_dogmatic <- coef(reg_dogmatic)
-coefs_dogmatic <- cbind(coefs_dogmatic, robust_se)
-
-```
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-# report reg, reg_ego, reg_stereotype in different columns using stargazer
-
-stargazer(reg, reg_ego, reg_stereotype, reg_bayesian, reg_dogmatic,  
-          title='Regression of effort change on news difference with robust standard errors', 
-          dep.var.labels='Change in effort', 
-          covariate.labels=c('Good news', 'News difference', 'News difference * Good news'),
-          column.labels=c('All', 'Ego-relevant', 'Stereotype', 'Bayesian Simulation', 'Dogmatic Simulation'), 
-          omit.stat=c('f', 'ser'), 
-          digits=2, 
-          label='tab:regression', 
-          header=FALSE,
-          float.env='sidewaystable', 
-          se = list(coefs[, 2], coefs_ego[, 2], coefs_stereotype[, 2], coefs_bayesian[, 2], coefs_dogmatic[, 2]))
-
-```
-
-More convincing evidence against the Switching model is the lack of inverse or attenuated correlation between 
-the change in effort and the news differential. In particular, if the switcher were the underlying model,
-I would expect overconfident subjects who start with an overestimation of $\theta$ to increase their effort
-in response to surprising bad news. This would flatten the slope of the regression line 
-for bad news relative to what a Bayesian would do. \ref{tab:regression} shows that the slope for bad news for
-the simulation\footnote{The details on how the data was simulated are explained in the Appendix} 
-of the Bayesian updates is much flatter than the slope in the data.
-
-## Stereotypes and ego-relevance
-
-Throughout the experiment, there is little difference in the behavior of subjects across treatments.
-Two of the main differences are that subjects in the ego-relevant treatment are more likely to become 
-overconfident when they start with a correct belief. And that subjects in the stereotype treatment are
-more likely to overreact to good news when they start by underestimating the performance of the other
-participant.
-
-These two differences present as consistent with the self-attribution bias. However, the pattern in the
-stereotype treatment could also be due to self-censoring of the subjects. In particular, subjects who
-initially underestimated the performance of the other participant might have realized their mistake and
-over-compensated their mistake by overestimating it after good news. This is consistent with the data
-and offers a more intuitive explanation for why this pattern arises in the stereotype treatment.
-
-Furthermore, I find no evidence of confirmation bias which is something that has been suggested in the
-literature of biased udating.\footnote{See \citet{benjamin2019} for a review of the literature in this and 
-other biases.} In particular, I find no evidence that subjects who overestimate the score of the other 
-participant are more likely to over-attribute successes to a high type and under-attribute them to a low type.
-Symmetrically, I find no evidence that subjects who underestimate the score of the other participant are
-more likely to over-attribute failures to a low type and under-attribute them to a high type. This is 
-consistent with what @Mobius2022 find in their experiment in a less complex updating task.
-
-# Structural estimation
-I have discussed two models that are consistent with the data: the self-attribution bias and the switcher.
-Although the data seems to point more convincingly towards the self-attribution bias, I cannot rule out
-the possibility that the switcher is the underlying model. In this section, I estimate the structural
-parameters of the two models and try to classify subjects into each of the models to assess how 
-much of the data is explained by each of the two likely theories.
-
-## Estimation of the switching threshold
-
-The switching threshold is the parameter that determines the likelihood ratio at which the switcher
-abandons the status quo paradigm and adopts the alternative. In order to estimate this parameter, I
-assume that all subjects are switchers and look at the rounds in which they chose to reveal a probability
-matrix that was different from the one they revealed in the previous round. I then calculate the likelihood
-ratio for the alternative paradigm to the status quo. I average across all such 
-likelihood ratios and use the average as an estimate of the switching threshold.
-
-In detail, Let $b_{t}^\theta$ be the belief about $\theta$ in period $t$.\footnote{in the experimental data, 
-I use the revealed matrix as a proxy for the belief. I take the matrix revealed in the previous period 
-to be the status-quo and the matrix revealed in period $t$ to be the alternative}. 
-And consider a subject for whom $b_{\tau-1}^\theta \neq b_{\tau}^\theta$, 
-where $b_{t}^\theta$. That is, in period $\tau-1$ they chose to reveal a matrix that was different from the one they
-revealed in period $\tau$. The matrix revealed in period $\tau-1$ is the status quo paradigm and the matrix revealed in
-period $\tau$ is the alternative paradigm. The likelihood ratio for the alternative paradigm to the status quo is
-$$
-\ell = \frac{L(\theta | b_{\tau}^\theta)}{L(\theta | b_{\tau-1}^\theta)}=\frac{p_\tau(o_t|b_{\tau}^\theta)}{p_{\tau}(o_t|b_{\tau-1}^\theta)} 
-$$
-
-where $p_\tau(o_t|b_{\tau}^\theta)$ is the probability of observing the signal $o_t$ when the agent is of type $b_{\tau}^\theta$.
-
-The estimate of the switching threshold, $\alpha$, is the average of the likelihood ratios across all subjects who switched
-in the experiment, which is given by
-
-$$\hat{\alpha} = \frac{1}{N}\sum_{i=1}^N \ell_{i\tau}$$
-
-Where $N$ is the number of switches observed in the experiment.
-
-Because the feedback that subjects receive is the equivalent of 10 signal realizations, the estimate 
-of the parameter is an upper bound of the true parameter. A lower bound would be given by the
-average likelihood ratio in the round before the switch happens. I choose to estimate the upper bound
-to impose a harsher test on the theory.
-
-Because the likelihood ratio is a function of the signal, it depends on the sequence of signals that 
-subjects observe. This means that in some cases, the likelihood ratio increases by a large amount from 
-one period to another. Although such cases are not common\footnote{In the data, only 1.8% of the 
-observations have a likelihood ratio that exceeds 5.}, a few very large values can skew the average. 
-To avoid a biased parameter, I restrict my sample to those observations for which the likelihood ratio
-is less than 5.\footnote{The full distribution of likelihood ratios is reported in the appendix}
-Under these assumptions, the estimate of the switching threshold is `r round(mean(updates[lr < 5 & change_indicator==1, lr]), 2)`.
-
-This means that the evidence supporting the alternative paradigm needs to be approximately 10% more
-compelling than the evidence supporting the status quo paradigm in order for the agent to switch.
-The estimation treatment by treatment is slightly larger for the Ego condition than for the Stereotype
-condition. However, the difference is not statistically significant (p-value=0.96).
-
-I then use this estimate to simulate the behavior of the switcher to assess the fit of the model.
-Which is discussed in the next section.
-
-## Estimation of the self-attribution bias
-
-Estimation of the parameters of the self-attribution bias is more involved than estimation of the switching
-threshold. In this case, there is no obvious identification strategy that provides a simple estimate 
-of the parameters. Instead, I use the simulated method of moments to estimate the parameters of the model.
-
-In particular, I simulate the behavior of the self-attribution bias for each possible prior and over 
-a grid of parameters. I make the simplifying assumption that the distortion is symmetric across good and bad news.
-That is, I assume that $c(\theta_H, \omega, \text{good news})=c(\theta, \omega_L, \text{bad news})=:c_g$ and that 
-$c(\theta_M, \omega, \text{bad news})=c(\theta, \omega_M, \text{good news})=:c_b$. In addition, I normalize the 
-remaining cases to be equal to 1. This leaves me with only 2 parameters to estimate.
-
-The moments that I match in the data are the reaction to good news and the reaction to bad news. In particular,
-I match the average change in effort in response to good news and the average change in effort in response to bad news.
-That is I match the following moments:
-
-$$
-\bar{G} = \frac{1}{N}\sum_{i=1}^N \frac{1}{T}\sum_{t=1}^T \mathbb{I}\{o_t > \bar{o}\} \cdot (e_t - e_{t-1}) 
-$$
-$$
-\bar{B} = \frac{1}{N}\sum_{i=1}^N \frac{1}{T}\sum_{t=1}^T \mathbb{I}\{o_t < \bar{o}\} \cdot (e_t - e_{t-1})
-$$
-where $N$ is the number of subjects in the sample, $T$ is the number of rounds in the experiment.
-
-I then use the simulated method of moments to estimate the parameters of the model. In particular, I
-simulate the behavior of the model for each possible prior and over a grid of parameters. I then
-calculate the average change in effort in response to good news and the average change in effort in
-response to bad news for each possible prior and over the grid of parameters and across $I$ simulated 
-indiviaduals. 
-I then minimize the objective function given by the sum of squared differences between the simulated
-moments and the empirical moments. That is, I solve the following problem
-
-# Model fit
-
-# Conclusion
-
-I  designed a setting in which I can distinguish between the forces of dogmatism, paradigm shifts, and optimal expectations.
-Through a laboratory experiment, I collected data on behavior and infer beliefs from it. I find that 
-the behavior of the subjects is consistent with the self-attribution bias. In particular, I find that 
-subjects decrease their effort in response to bad news as well as to bad news, although the latter decrease 
-is smaller. This is consistent with the self-attribution bias as well as with a change of paradigm. However,
-I also observe that about a third of the subjects started with a correctly specified belief and ended up
-overconfident. This is consistent only with the self-attribution bias. Therefore, I conclude that the
-model that best explains the data is that of optimal expectations.
-
-I have small or no effects throughout on the ego-relevance of the type. Although the motivation behind the 
-theories does not directly apply to the case of stereotypes, the lack of stark differences suggests that 
-biases arise due to an incorrect updating procedure and not necessarily due to the self-serving motivation 
-behind the bias. The lack of differences in the behavior of the subjects across treatments could also 
-be due to self-censoring of the subjects. In particular, subjects might be initially reluctant to 
-express their true belief about a particular group of people. In addition, as they learn and realize 
-that their beliefs might be incorrect, they might overreact to signals to try to compensate for the initial 
-bias. Such an updating procedure would be consistent with the self-attribution bias for the case of stereotypes.
-I remain agnostic about whether that is truly the case or whether the lack of differences is due to other 
-factors.
-
-Another bias that has been studied and suggested in the literature is the confirmation bias. In particular,
-it has been suggested that subjects who are overestimate $\theta$ in their prior, will over-attribute 
-successes to a high type and under-attribute them to a low type. Symmetrically, subjects who initially 
-underestimate $\theta$ will over-attribute failures to a low type and under-attribute them to a high type.
-I do not find evidence of such a bias in the data. This is consistent with what @Mobius2022 find in their
-experiment.
-
-I further investigate possible heterogeneity in the underlying models being used by estimating the 
-structural parameters of the models.
-
-\newpage
-\appendix
-
-# appendix
-## Transition matrix by treatment
-
-Figure \ref{fig:transitions-treatment} shows the transition matrix for each of the treatments separately.
-It shows that initial misspecifications are more sticky in the ego treatment and that subjects who 
-underestimate the score of the other participant in the stereotype treatment are more likely to end up 
-overestimating it than in the ego treatment. This may signal some sort of self-censoring or overreaction 
-in the stereotype treatment.
-
-![Transition matrix for subjects who started in each of the 3 possible starting specifications and the specification that they ended up in at the end of the updating task](../figures/misspecification_transitions_treatment.png){#fig:transitions-treatment}
-
-## Full distribution of likelihood ratios
-The likelihood ratios at rounds in which I observe a change in the belief about $\theta$ presents a
-long right-tail. In particular, 1.8% of the observations have a likelihood ratio that exceeds 5 
-which would mean that the agent requires evidence that is 5 times more compelling in favor 
-of the alternative paradigm in order to switch. Figure \ref{fig:lr-hist} shows the distribution of
-likelihood ratios for all observations.
-
-![Distribution of likelihood ratios for all observed belief changes](../figures/lr_hist.png){#fig:lr-hist}
-
-## Model simulation
-
-In order to simulate the data for each of the models and asses their fit, I simulated the path that each
-type of agent would have taken given each possible realization of $(\theta, \omega)$. I fixed 
-the seed of the random number generator to 3452\footnote{this is the seed that was drawn at random for the experiment} and fixed the signals that would be shown in each round
-after each choice by drawing them before simulating. This way, the signals that the simulation 
-uses coincide exactly with the signals that a subject would have seen in the experiment. 
-I then use each of the algorithms defined by the models to simulate the path that the agent would have taken
-given the signal and given an initial belief. For the dogmatic modeler and the switcher, I use each possible
-dogmatic belief. For the Bayesian and the self-attribution bias, I use a uniform belief on theta.
-
-## Reaction to good and bad news (robustness check)
-
-I use an alternate definition for good and bad news and check whether the results are robust to this. 
-I define a signal to be a net positive if the number of successes is equal to or greater than the number of failures.
-I define a signal to be a net negative if the number of failures is greater than the number of successes.
-I now treat net positive signals as good news and net negative signals as bad news. I then rerun the regression 
-analysis and find that the results are robust to this alternative definition. In particular, net negative 
-signals are associated with a stark decrease in effort for both treatments. Net positive signals are
-associated with a small decrease in effort for both treatments. The results are reported in Table \ref{tab:regression-net}.
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE }
-reg2 <- lm(effort_change ~ positive_signal + signal_prev + signal_prev:positive_signal, data=updates[round_number>1,])
-robust_se <- sqrt(diag(vcovHC(reg)))
-
-# Attach the robust standard errors to the coefficient estimates
-coefs2 <- coef(reg2)
-coefs2 <- cbind(coefs2, robust_se)
-```
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-# run the regression only for treatment  = ego
-reg2_ego <- lm(effort_change ~ positive_signal + signal_prev + signal_prev:positive_signal, data=updates[round_number>1 & treatment == 'ego',])
-
-# Attach the robust standard errors to the coefficient estimates
-coefs2_ego <- coef(reg2_ego)
-coefs2_ego <- cbind(coefs2_ego, robust_se)
-```
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-# run the regression only for treatment  = stereotype
-reg2_stereotype <- lm(effort_change ~ positive_signal + signal_prev + signal_prev:positive_signal, data=updates[round_number>1 & treatment == 'stereotype',])
-
-# Attach the robust standard errors to the coefficient estimates
-coefs2_stereotype <- coef(reg2_stereotype)
-coefs2_stereotype <- cbind(coefs2_stereotype, robust_se)
-```
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-# report reg, reg_ego, reg_stereotype in different columns using stargazer
-
-stargazer(reg2, reg2_ego, reg2_stereotype,  
-          title='Regression of effort change on news difference with robust standard errors', 
-          dep.var.labels='Change in effort', 
-          covariate.labels=c('Net-positive signal', 'Signal value', 'Signal value * Net-Positive signal'),
-          column.labels=c('All', 'Ego-relevant', 'Stereotype'), 
-          omit.stat=c('f', 'ser'), 
-          digits=2, 
-          label='tab:regression-net', 
-          header=FALSE, 
-          se = list(coefs2[, 2], coefs2_ego[, 2], coefs2_stereotype[, 2]))
-
-```
-
-# Experimental Instructions
-
-You are about to participate in an experiment on decision-making.
-What you earn depends partly on your decisions and partly on chance.
-Please turn off cell phones and similar devices now.
-Please do not talk or in any way try to communicate with other participants.
-We will start with a brief instruction period. If you have any questions during this period, raise your hand, and your question will be answered so everyone can hear.
-
-**General Instructions**
-
-The experiment is separated into two parts. You will be given instructions for each part when it is reached.
-
-**Part 1:**
-
-In part 1, you will be asked to solve a series of quizzes.
-In each quiz, you will answer multiple choice questions on one of 6 topics: Math, Verbal Reasoning, US Geography, Science and Technology, Pop Culture, and Sports and Video Games.
-
-The order of the topics will be determined randomly.
-
-You will see only one question at a time. Select an answer and then click the “Next” button to move on to the following question.
-
-If you leave a question unanswered, it will be marked as incorrect. You will not be able to go back to that question once you click the “Next” button.
-
-You will have 2 minutes for each quiz. Once the time runs out, your answers will be submitted automatically.
-
-At the end of the experiment, the computer will randomly select one topic (each chosen with equal probability), and you will be paid $0.20 for each correct answer.
-
-Your score on the quizzes will also affect how much you earn in part 2. The higher your score, the more likely you will be to make more money.
-
-When you finish all six quizzes, there will be a short questionnaire that will not affect your payoff.
-Please answer all the questions as accurately as you can.
-You will have access to your answers from Part 1 when in Part 2, which can help you make better choices.
-
-We will move on to Part 2 once everyone completes Part 1.
-
- **Part 2 (Ego):**
-
-The task in this part will be repeated once for each topic from Part 1. For each task, you will make 11 choices.
-
-In this part, you will choose one of 3 gambles and see 10 outcomes for the one you choose.
-Each outcome will be either a success or a failure, and the probability with which each of them is a success is determined by 3 factors:
-
-Your score on the quiz for the corresponding topic,
-
-A randomly chosen success rate,
-
-Your choice of a gamble.
-
-Your score is either Low (if it is 5 or less), Mid (if it is between 6 and 15), or High (if it is 16 or more).
-You will not know your actual score, but you will be reminded of the guess you made in part 1.
-
-The success rate will be chosen randomly by the computer, and it can be Rate A, B, or C.
-Each is drawn with an equal chance (1⁄3 chance each), but you will not know which one was drawn.
-The rate is drawn once, at the beginning of the task, and stays fixed throughout.
-
-To maximize the chance of success, you should choose the gamble that matches the underlying success rate:
-- Gamble A maximizes the probability of a success when the rate is A,
-- Gamble B maximizes the probability of success when the rate is B and
-- Gamble C maximizes the probability of success when the rate is C.
-
-After 11 gamble choices, the task will change to the next topic. This means that the probability of success for this new task will be determined by the following:
-- The score you received on the quiz for the corresponding topic and 
-- a new draw of the rate (A, B, or C)
-
-At the end of the experiment, the computer will randomly pick one of the topics, and you will be paid $0.20 for each success.
-(For each topic, there will be 110 outcomes: 10 outcomes for each of the 11 choices you made).
-
-We will now go over the details of the probability of success. They are described by the tables in the back.
-
-Three tables describe the probabilities. Each table corresponds to one of the score levels: Low, Mid, and High.
-
-Each of the columns within the matrix corresponds to one of the success rates. You do not know which was drawn, but the gambles' outcomes can help you determine the rate.
-
-You will choose a Row.
-
-In order to enter your choice of a gamble, you will first need to choose which matrix you want to see.
-If you choose a matrix that does not correspond to your score, the probabilities in the table will not match the probabilities with which the outcomes are successful.
-
-The outcomes will be generated using:
-- your actual score (table), which you do not know for certain,
-- the gamble (row) that you chose, and
-- the rate (column), which you also don’t know.
-
-**Part 2 (stereotype):**
-
-The task in this part will be repeated once for each topic from Part 1. For each task, you will make 11 choices.
-
-In this part, you will choose one of 3 gambles and see 10 outcomes for the one you choose.
-Each outcome will be either a success or a failure, and the probability with which each of them is a success is determined by 3 factors:
-- The score of another participant on the quiz for the corresponding topic,
-- A randomly chosen success rate,
-- Your choice of a gamble.
-
-The other participant’s score is either Low (if it is 5 or less), Mid (if it is between 6 and 15), or High (if it is 16 or more).
-You will not know the score but will be reminded of your guess in part 1.
-
-The success rate will be chosen randomly by the computer, and it can be Rate A, B, or C.
-Each is drawn with an equal chance (1⁄3 chance each), but you will not know which one was drawn.
-The rate is drawn once, at the beginning of the task, and stays fixed throughout.
-
-To maximize the chance of success, you should choose the gamble that matches the underlying success rate:
-- Gamble A maximizes the probability of a success when the rate is A,
-- Gamble B maximizes the probability of success when the rate is B and
-- Gamble C maximizes the probability of success when the rate is C.
-
-After 11 gamble choices, the task will change to the next topic. This means that the probability of success for this new task will be determined by the following:
- - The score the other participant got on the quiz for the corresponding topic 
- - A new draw of the rate(A, B, or C)
-
-At the end of the experiment, the computer will randomly pick one of the topics, and you will be paid $0.20 for each success.
-(For each topic, there will be 110 outcomes: 10 outcomes for each of the 11 choices you made).
-
-We will now go over the details of the probability of success. They are described by the tables in the back.
-
-Three tables describe the probabilities. Each table corresponds to one of the score levels: Low, Mid, and High.
-
-Each of the columns within the matrix corresponds to one of the success rates. You do not know which one was drawn, but the gambles' outcomes can help you determine the rate.
-
-You will choose a Row.
-
-In order to enter your choice of a gamble, you will first need to choose which matrix you want to see.
-If you choose a matrix that does not correspond to the score, the probabilities in the table will not match the probabilities with which the outcomes are successful.
-
-Once you enter a choice, the 10 outcomes will be generated using the following:
-- the actual score (matrix), which you do not know for certain,
-- the gamble (row) that you chose, and
-- the rate (column), which you also don’t know.
-
-_The full data generating process is printed on the rear side of the instructions and always available to the subjects throughout part 2._
-_Each of the matrices is labeled with "if your/the other participant's score is..." depending on the treatment_
-
-**Screen walk-through script:**
-
-This is the screen where you will enter your choices of gambles.
-First, you must choose the matrix that you want to see. Whatever matrix you choose to see does not change the probabilities with which the gables are a success.
-Then, you must choose a gamble (which corresponds to a row).
-The computer will draw 10 outcomes for that gamble using the probability in the chosen row and the column corresponding to the rate for this task.
-On the right, you can choose to see either the total count of successes and failures for each gamble or the detailed history. That is the number of successes and failures for each of your choices.
-The rate will be drawn again for the next task, corresponding to the next quiz topic. And you will repeat this process.
-
-\newpage
-# References

### 2023-10-15 Paper/Intro.tex
Separate file with only intro

--- 2023-10-14 Paper/draft.tex
@@
 \usepackage[margin=2.5cm]{geometry}
-\usepackage{graphicx}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
 \setlength{\emergencystretch}{3em} % prevent overfull lines
@@
 \author{Jimena Galindo}
-\date{October 14, 2023}
+\date{October 15, 2023}
 
@@
 
-\hypertarget{theoretical-framework}{%
-\section{Theoretical Framework}\label{theoretical-framework}}
-
-The theories that I consider make predictions in two distinct
-frameworks. I first detail each theory within their original framework
-and then develop a unifying example that allows me to compare the
-predictions of all of them. In framework 1 I consider a setting in which
-the an agent observes a continuous output and infers the underlying
-state. In framework 2, the agent observes a binary outcome and infers
-the underlying probability of success. In both frameworks, I consider
-two nested theories of learning.
-
-\hypertarget{framework-1}{%
-\subsection{Framework 1}\label{framework-1}}
-
-An agent is of type \(\theta \in \Theta\) and faces an unknown exogenous
-state \(\omega\) drawn from some density \(f\) over \(\Omega\). The
-agent knows the distribution of \(\omega\) but not its realized value.
-His belief about the state, \(p_0(\omega)\), coincide with the true
-distribution, \(f\); and his belief about the type is \(p_0(\theta)\).
-Let the agent's true type be \(\theta^{*}\), and the realized state be
-\(\omega^{*}\).
-
-An agent's belief about the type is \emph{misspecified} if it assigns
-probability zero to their true type. Furthermore, the agent is
-\emph{dogmatic} if he holds a degenerate belief that places probability
-one on being of type \(\hat{\theta}\). An agent can be dogmatic and
-misspecified, in which case \(\hat{\theta} \neq \theta^*\) and
-\(p_0(\hat{\theta}) = 1\).
-
-The agent chooses an action \(a\in A\) and observes a noisy outcome
-\(h\). The outcome is a function of the agent's type, the state, and the
-action. In particular \(h = h(\theta^*, \omega^*, a) + \varepsilon\)
-with \(h(\cdot)\) increasing in both \(\theta^*\) and \(\omega^*\), and
-such that conditional on a pair of parameters \((\theta, \omega)\),
-there is a unique optimal action. additionally,
-\(\varepsilon\sim N(0, \sigma)\) is noise in the output.
-
-After observing the outcome, the agent updates his beliefs about
-\(\theta\) and \(\omega\) using some algorithm and moves on to the next
-period. He repeats this process infinitely many times. I make the
-simplifying assumption that the agent is myopic and chooses the action
-that maximizes the payoff in each period. This assumption simplifies the
-analysis and plays a role in whether an agent who updates their beliefs
-using Bayes rule would learn the truth or not, however, for the main
-theory discussed in this section, the results hold even when relaxing
-this assumption. The behavior of a forward-looking agent is further
-discussed in the conclusion.
-
-A key notion in this setting is that of a self-defeating
-equilibrium\footnote{This notion is an adaptation of the Berk-Nash equilibrium in 
-\citet{Esponda2016} to this setting with only one agent}. A
-\emph{self-defeating equilibrium} is a belief and action pair such that
-the agent's belief about their type is misspecified and the outcome
-generated by the action is consistent with the misspecified belief. This
-means that the average outcome under the true type and the true state
-equals the average output the agent expects under the misspecified
-belief. The agent's belief is said to be \emph{stable} when this
-happens.
-
-Within this framework, I consider two nested theories of belief
-updating: the first one is a dogmatic modeler from \citet{Heidhues2018},
-The second one is a switcher, as in \citet{Ba2023}. The dogmatic modeler
-can be seen as a switcher with an infinitely sticky initial belief so
-the two theories are nested. However, outside of the limiting case, they
-produce different predictions about the agent's behavior. I discuss each
-of them separately in what follows.
-
-\hypertarget{the-dogmatic-modeler}{%
-\subsubsection{The Dogmatic Modeler}\label{the-dogmatic-modeler}}
-
-Take the action space to be the same as the state space \(\Omega\) and
-\(\Omega =A=[\underline{a}, \infty)\).
-
-A dogmatic agent does not update their beliefs about \(\theta\),
-instead, he holds a degenerate belief that places probability on
-\(\hat{\theta}\), which is potentially misspecified. In this case, no
-matter how much information he gathers against being of type
-\(\hat{\theta}\), he will not update his beliefs about it. Any
-discrepancies between the observed outcomes and his believed type are
-incorporated using the Bayes rule to update his beliefs about
-\(\omega\). \citet{Heidhues2018} show that, under certain assumptions on
-the per-period utility,\footnote{The assumptions are that 
-$u$ is twice continuously differentiable with: (i)$u_{aa}<0$ and $u_a(\underline{a},  \theta, \omega)>0>u_a(\Bar{a}, \theta, \omega)$, 
-(ii) $u_{\theta}, u_{\omega}>0$ and (iii) $u_{a\theta}<0$ and $u_{a\omega}>0$. Where $\underline{a}$ is the
-minimal action and $\Bar{a}$ is the maximal one. 
- The direction of the derivatives is a normalization
-and the results would hold even when the signs are reversed.} a dogmatic
-modeler will inevitably fall into a self-defeating equilibrium. The
-equilibrium will be such that the outcomes they observe reinforce their
-belief on \(\omega\) in such a way that as \(t\to\infty\) the agent will
-be sure that the state is some \(\omega^{'}\) consistent with their
-believed type and the observed data. In other words, they will be in a
-self-defeating equilibrium with a stable belief that places probability
-one on the incorrect parameters \((\hat{\theta}, \omega_{\infty})\)
-
-The mechanism by which the dogmatic agent falls into the self-defeating
-equilibrium is the following: Suppose the agent holds the misspecified
-belief that they are type \(\hat{\theta}>\theta^*\). For any prior over
-\(\omega\), the agent will be disappointed by the outcome. He expected a
-gain of \(h(\hat{\theta}, \mathbb{E}(\omega), a)\) but instead observes
-\(h(\hat{\theta}, \omega^*, a)\). There are two possible sources for the
-disappointment: the first is that the realized state is lower than the
-expected state; the second source is that the agent is of type
-\(\theta^*\) and therefore, for all possible states, his gain will be
-lower than what he expected. Because the agent is dogmatic, he will not
-update his beliefs about \(\theta\) and as a consequence will attribute
-the disappointment to the state being lower than expected. He will
-continue to update in this way until he converges to a belief about
-\(\omega\) that is stable. Such a belief will explain the observed
-utility perfectly and allow the agent to rationalize his dogmatic belief
-about \(\theta\). Under the assumptions of \citet{Heidhues2018}, there
-is a unique value of \(\omega\) at which the belief is stable, I will
-refer to such value as \(\omega_\infty\). This mechanism is illustrated
-in Example 1.
-
-\textbf{Example 1: } \emph{Set \(A = \Omega=[\underline{a}, \infty)\)
-and consider a student with intrinsic ability \(\theta^*\geq 0\) who
-faces a grading procedure \(\omega^*\) that is unknown to them. The
-student knows that a higher \(\omega^*\) is more likely to yield a
-higher grade. In particular, she knows the grade is given by
-\((\theta^*+a)\omega^*\).}
-
-\emph{The student must choose an effort level \(a\), which determines
-her grade. For whatever the chosen effort level, the student must pay a
-cost \(c(a) = \frac{1}{2}a^2\) and observes a grade of
-\((\theta^*+a)\omega^*\). She repeats this process for infinitely many
-periods. Assume also that the student's prior is such that
-\(\mathbb{E}[\omega]= \omega^*\) and she is dogmatic about being of type
-\(\hat{\theta}>\theta^*\).\footnote{The example is illustrated for an overconfident student but 
-the results are symmetric for a dogmatic student who initially 
-places probability one on some $\tilde{\theta}<\theta^*$.} Therefore,
-the student's payoff in period \(t\) is given by }
-
-\begin{equation}
-u_t(a_t; \theta^*, \omega^*) = (\theta^*+a_t)\omega^* - \frac{1}{2}a^2 + \varepsilon_t
-\end{equation}
-
-\emph{Under this specification, the myopic optimal effort level is
-\(a_t^* = \omega^*\). Because the student does not know \(\omega^*\), he
-will choose \(a_t = \mathbb{E}_t(\omega)\) where the expectation is
-taken with respect to the student's belief at the beginning of period
-\(t\). If she does not revise his effort choice for \(k\) periods, she
-will receive an average utility of
-\((\theta^*+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}\) but he was expecting
-an average utility of
-\((\hat{\theta}+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}\). In response, she
-will apply Bayes rule to update his beliefs about \(\omega\) to get the
-posterior belief with
-\(\mathbb{E}_{t+k}[\omega] = \frac{(\theta^{*} + \omega^{*})\omega^{*}}{\hat{\theta} + \omega^{*}}\)
-which is lower than the initial belief. This will cause the student to
-choose a lower effort at \(t+k\). As a result, she will again receive an
-average utility that is lower than what he expected which will cause her
-belief to drift further down. This process will continue until the
-average utility equals her expected utility under the dogmatic belief
-that assigns probability 1 to \(\hat{\theta}\). At that point, the
-student will have reached a self-defeating equilibrium and she will
-continue to choose sub-optimal effort forever. }
-
-Although the model of a dogmatic modeler rationalizes the prevalence of
-overconfident (underconfident) beliefs, the assumption that the agent
-has a degenerate belief and no mechanism through which he can update
-such belief is very restrictive. An alternative approach is proposed by
-\citet{Ba2023}. She proposes an extension of the dogmatic agent who is
-able to swithch from one dogmatic belief to another. By doing so, the
-agent can avoid the self-defeating equilibria and end up being dogmatic
-and correctly specified.
-
-\hypertarget{the-switcher}{%
-\subsubsection{The Switcher}\label{the-switcher}}
-
-An agent is a \emph{switcher} if they behave as a dogmatic, but are
-willing to entertain the possibility that they are of a different type.
-In particular, when they start off as a misspecified dogmatic, they are
-willing to switch to a different dogmatic belief if the data is
-convincing enough. Their prior is still degenerate and assigns
-probability one to a particular type, and zero to all other types. This
-means that a Bayesian update on \(\theta\) does not change their beliefs
-about the type. However, they are willing to entertain two such beliefs
-and have a mechanism by which they decide which belief to adopt at any
-period \(t\).
-
-In order to abandon their initial dogmatic belief, the agent needs to
-observe a sequence of outcomes that are sufficiently unlikely to have
-happened if they were of the type they initially believed. In order to
-evaluate if the evidence is convincing enough, they keep track of the
-likelihood that each of the possible types generated the data. If the
-likelihood ratio is sufficiently large, the agent will switch to the
-alternative and behave as if they are dogmatic about the new type.
-
-In particular, for an agent that starts with a dogmatic belief that they
-are of type \(\hat{\theta}\) but is willing to consider the alternative
-explanation that they are of type \(\tilde{\theta}\), the agent will
-switch to the alternative if:
-
-\[\frac{p[h^t|\tilde{\theta}]}{p[h^t|\hat{\theta}]} > \alpha\geq 1\]
-
-Where \(h^t\) is the history of outcomes up to time \(t\) and \(\alpha\)
-is the switching
-threshold.\footnote{Notice that if $\alpha \to \infty$, the behavior of the switcher will be indistinguishable from that of the Dogmatic modeler. 
-In this sense, the switcher is a generalization of the dogmatic type.}
-By keeping track of the likelihood ratio, the agent can perform a
-\emph{Bayesian hypothesis test} and adopt the Dogmatic belief that best
-fits the
-data.\footnote{In a related problem \citet{Schwarstein2021} proposes a similar updating procedure which relies on the Bayesian 
-hypothesis test. However, in their model there is a sender who optimally chooses to propose a model that fits the data}
-
-By allowing the agent to keep track of the likelihoods and switching to
-an alternative type, the switcher can avoid the self-confirming
-equilibria. However, if the prior belief on \(omega\) is sufficiently
-tight around a self-defeating equilibrium, the switcher might look
-identical to the dogmatic even in a case where \(\alpha\) is not too
-large. This happens because under the agent's prior, the likelihood
-ratio is unlikely to grow as fast as it is needed to escape the
-self-defeating equilibrium. In such situations, we say that the
-misspecified belief is persistent.
-
-\hypertarget{framework-2}{%
-\subsection{Framework 2}\label{framework-2}}
-
-As in framework 1, the agent is of some type \(\theta^* \in \Theta\) and
-the state is \(\omega \sim F(\Omega)\). In this case, the agent chooses
-an action \(a\in A\) and observes a binary outcome that is either a
-success or a failure. Denote the outcome by \(o \in \{s,f\}\). The
-probability of observing a success is increasing in \(\theta\) and in
-\(\omega\). Whenever the agent observes a success, he gets a payoff
-\(v>0\) and whenever the outcome is a failure, the payoff is 0. In
-addition, the probability of success is such that for each state, there
-is a unique optimal action that maximizes the agent's expected payoff.
-Therefore, the probability of success can be seen as a monotone
-transformation of the utility from Framework 1.
-
-I focus on two nested theories that have been widely studied within this
-framework: Full Bayesian updating and self-serving attribution bias. I
-explain each of these classical models of belief updating in what
-follows
-
-\hypertarget{the-bayesian}{%
-\subsubsection{The Bayesian}\label{the-bayesian}}
-
-A Bayesian agent simultaneously updates their beliefs about \(\theta\)
-and \(\omega\) by using Bayes' rule. The posterior at period t+1 about
-\(\theta\) after observing outcom \(o\) is given by: \[
-p_{t+1}(\theta, \omega| h^t) = \frac{p[o|\theta, \omega]p_t(\theta, \omega)}{\sum_{(\theta', \omega')}p[o|\theta', \omega']p_t(\theta', \omega')}
-\]
-
-Where \(p_{t}\) is the belief at the start of period \(t+1\) and
-includes all the information gathered so far.
-
-Bayesian agents choose the effort level that maximizes their expected
-flow payoff by taking expectations over their prior beliefs about
-\(\theta\) and \(\omega\). Since agents are myopic, even though all the
-parameters could be identified with enough variation in choices, there
-will be instances in which the Bayesian will not learn even with
-infinite amounts of data. This happens because, by being myopic, they do
-not internalize the tradeoff between flow payoff and learning. This can
-result in too little experimentation to learn their true type. An
-alternative to this approach is given by \citet{Hestermann2021} and is
-discussed in the concluding remarks. Regardless, this approach is useful
-as a benchamrk for the other theories discussed in this paper.
-
-Also notice that if a fully Bayesian agent has a dogmatic prior, they
-will never update their beliefs about the parameter that they are
-dogmatic about. This will imply that they are prone to the same types of
-errors as the dogmatic modeler in framework 1.
-
-\hypertarget{the-self-serving-updater}{%
-\subsubsection{The Self-Serving
-Updater}\label{the-self-serving-updater}}
-
-A Self-Serving Bayesian is an agent who uses a biased version of Bayes
-rule to update their beliefs. They will update their beliefs about the
-state \(\omega\) and his type \(\theta\) simultaneously by
-over-attributing successes to a high value of \(\theta\) and
-under-estimating the role of higher \(\omega\). Similarly, he will
-attribute failure to a low state to a greater degree than an unbiased
-agent would. To model the self-serving attribution bias, I take the
-approach of \citet{benjamin2019}, where the posterior odds are given by:
-
-\[
-p_{t+1}(\theta, \omega| h^t) = \frac{p[h^t|\theta, \omega]^{c(\theta, \omega, o_t)}p_t(\theta, \omega)}{\sum_{(\theta', \omega')}p[h^t|\theta', \omega']^{c(\theta, \omega, o_t)}p_t(\theta', \omega')}
-\]
-
-with
-\(c(\theta_H, \omega, o)<c(\theta_M, \omega, o)<c(\theta_L, \omega, o)\leq 1\)
-and
-\(c(\theta, \omega_L, o)<c(\theta, \omega_M, o)<c(\theta, \omega_H, o)\leq 1\).
-
-This formulation of the bias means that the agent will over-attribute
-successes to a high type and under-attribute them to a low type Whereas
-they will over-attribute failures to a low state and under-attribute
-them to a high state. The bias is introduced by distorting the perceived
-likelihood that the signal was generated by either high values of
-\(\theta\) when it is a success, or by low values of \(\omega\) when it
-is a failure. The parameter \(c\) determines the degree of bias and
-imposes enough restrictions to ensure that the model is still
-falsifiable.
-
-\hypertarget{a-unifying-example}{%
-\section{A Unifying Example}\label{a-unifying-example}}
-
-In order to compare the predictions of the theories discussed above, I
-develop a unifying example that allows me to isolate the forces behind
-each of the theories. The example is a modification of the one in
-\citet{Heidhues2018} and is adapted to implementable in the lab.
-
-The agent can be of one of 3 types:
-\(\theta \in \{\theta_L, \theta_M, \theta_H\}\) with
-\(\theta_H > \theta_M > \theta_L\). They face an unknown exogenous
-success rate \(\omega \in \{\omega_L, \omega_M, \omega_H\}\) with
-\(\omega_H>\omega_M>\omega_L\). Each of the values of \(\omega\) is
-realized with equal probability. The agent knows the distribution of
-\(\omega\) but not its realized value.
-
-Denote the true type by \(\theta^*\) and the true state by \(\omega^*\).
-The agent holds some prior belief about
-\(\theta\)\footnote{which is potentially misspecified as in the dogmatic and switcher cases discussed above}
-and chooses a binary gamble \(e in \{e_L, e_M, e_H\}\). The agent
-observes whether the gamble is a success or a failure and gets a payoff
-of \(1\) and if it is a success; they get \(0\) otherwise.
-
-The probability of success is increasing in both \(\theta\) and
-\(\omega\) and is fully described by the Table \ref{tab:DGP}
-
-\begin{table}[htbp]
-\centering
-
-\begin{tabular}{ c|c|c|c|}
-
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
-  \cline{2-4}
-  $e_H$ & 50 & 20 & 2 \\
-  \cline{2-4}
-  $e_M$ & 45 & 30 & 7 \\
-  \cline{2-4}
-  $e_L$ & 40 & 25 & 20 \\
-
-  \cline{2-4}
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_L$} & \multicolumn{1}{c}{}\\
-\end{tabular}
-\hspace{.3cm} 
-\begin{tabular}{ c|c|c|c|}
-
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
-  \cline{2-4}
-  $e_H$ & 80 & 50 & 5 \\
-  \cline{2-4}
-  $e_M$ & 69 & 65 & 30 \\
-  \cline{2-4}
-  $e_L$ & 65 & 45 & 40 \\
-  \cline{2-4}
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_M$} & \multicolumn{1}{c}{}\\
-\end{tabular}
-\hspace{.3cm} 
-\begin{tabular}{ c|c|c|c|}
-
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\omega_H$} & \multicolumn{1}{c}{$\omega_M$} & \multicolumn{1}{c}{$\omega_L$}\\
-  \cline{2-4}
-  $e_H$ & 98 & 65 & 25 \\
-  \cline{2-4}
-  $e_M$ & 80 & 69 & 35 \\
-  \cline{2-4}
-  $e_L$ & 75 & 55 & 45 \\
-  \cline{2-4}
-  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{$\theta_H$} & \multicolumn{1}{c}{}\\
-\end{tabular}
-
-\caption{Probability of success for each type, gamble and effort level}
-\label{tab:DGP}
-\end{table}
-
-Conditional on a type, the agent's flow payoff is maximized by choosing
-the gamble that matches the state. For example, if the value of
-\(\omega\) is \(\omega_H\), the agent's flow payoff is maximized by
-choosing \(e_H\) and if the state is \(\omega_L\) the flow payoff is
-maximized by choosing gamble \(e_L\), regardless of the value of
-\(\theta\). The agent myopically chooses gambles every period to
-maximize the flow payoff for \(T<\infty\) periods.
-
-After observing the outcome of each gamble, the agent updates their
-beliefs using some procedure and moves on to the next period.
-
-Notice that both \(\theta\) and \(\omega\) can be identified from the
-outcomes if enough variation in the effort choices exists. This can be
-seen by confirming that there is no pair of \(\theta\) and \(\omega\)
-such that the probability of success is the same for all effort choices.
-Thus, by changing the effort choice, the agent can learn both their type
-and the state if they observe enough outcomes.
-
-In this example, for an agent with a dogmatic belief about their type, a
-self-defeating equilibrium is one in which the agent chooses an effort
-level that, under the true \(\theta\), yields a frequency of success
-that is consistent with the agent's misspecified belief. That is
-\(P[\text{sucess}|\theta^*, e^*] = P[\text{sucess}|\hat{\theta}, e^*]\)
-where \(e^*\) is the agent's myopic optimal choice.
-
-In the data-generating process described above, there are five such
-equilibria. For example, if the agent is of type \(\theta_M\) but
-mistakenly believes that he is of type \(\hat{\theta}=\theta_H\) and the
-and \(\omega^* = \omega_M\), when the effort chosen is \(e_L\), the
-agent will observe a success with 45\% chance. Because the agent
-dogmatically believes that their type is high, they will erroneously
-conclude that the rate is \(\omega_L\). Under this belief, the optimal
-action is \(e_L\) which will continue to generate successes with \(45%
-\) probability, further reinforcing the incorrect belief. By doing so,
-the agent forgoes the payoff from gamble \(e_M\) which would yield a
-success with \(65\%\) chance.
-
-By including self-confirming equilibria, the example captures the forces
-from each of the updating mechanisms discussed in the previous section
-and allows for the comparison of the main forces behind the theories.
-For realizations of \((\theta, \omega)\) for which there are
-self-confirming equilibria, the dogmatic agent will fall into the trap
-whereas the switcher will be able to escape it. Similarly, an agent with
-self-attribution bias will update their beliefs differently from an
-unbiased Bayesian, leading them to choose different gambles. I exploit
-such cases in order to test which model is a better fit for how subjects
-behave in a laboratory
-experiment.\footnote{because the setting does not match that of @Heidhues2018, there will be situations for which the theory 
-does not provide a prediction. If such cases arise in the lab, they will not be used for the analysis. However, whether a misspecified 
-belief persists or not for the switcher, depends highly on the realized history of signals that he gets.}
-In what follows I explain the details of how this example was
-implemented in the lab.
-
-\hypertarget{experimental-design}{%
-\section{Experimental Design}\label{experimental-design}}
-
-I recruited 78 undergraduate subjects from the CESS lab at NYU who
-participated in an in-person experiment. Sessions lasted approximately
-45 minutes and subjects earned an average payment of \(\$22.6\). The
-experiment was programmed using oTree \citep{otree}.
-
-The experiment consisted of 2 treatments: the \emph{ego-relevant}
-condition and the \emph{stereotype} condition. Subjects participated in
-only one of the treatments. All subjects within a session participated
-in the same treatment and the first 4 treatments were assigned the
-ego-relevant condition; the rest were assigned to the stereotype
-treatment. The tasks were identical across treatments, except for
-parameter \(\theta\). In the ego-relevant condition \(\theta\) is the
-subject's own performance in a quiz, while in the stereotype condition,
-it is the performance of a randomly selected subject from another
-session.
-
-The experiment had 3 parts. In Part 1 subjects had 2 minutes to answer
-as many multiple-choice questions as they could from a 20-question quiz.
-They did this for quizzes on 6 different topics. The topics were: Math,
-Verbal Reasoning, Pop-culture and Art, Science and Technology, US
-Geography, and Sports and Video Games. In this part, they did not know
-how many questions were available and they were given no feedback.
-
-After taking all 6 quizzes, they proceeded to part 2 where they were
-asked to guess their score on each of them. In the stereotype treatment
-they were additionally asked to guess the score of a randomly drawn
-participant from a previous session. All they knew about the other
-participant was their gender identity and whether they were US nationals
-or not. For each guess, they had three score options: Low-Score (5 or
-fewer correct answers), Mid-Score (between 6 and 15 correct answers),
-High-Score (16 or more). Each of the score categories corresponded to
-\(\theta_L\), \(\theta_M\), and \(\theta_H\) respectively. They were
-also asked to say how confident they felt about their choices. They had
-4 possible answers: ``it was a random guess'', ``there is another
-equally likely score'', ``I am pretty sure'', ``I am completely sure''.
-These 4 answers are mapped to priors that place probabilities .33, .50,
-.75, and 1 to the chosen type. The remaining probability is split
-equally among the other two types. Questions in Part 2 were not
-incentivized, but subjects were told that providing an accurate answer
-would increase their chances of earning more money in the last part of
-the experiment.
-
-The purpose of Part 2 is to classify subjects into overconfident,
-underconfident and correctly specified. If a subject guesses their score
-to be in a higher (lower) category than their true score, they are
-overconfident (underconfident); if they guess their score to be in the
-same category as their true score, they are correctly specified. This
-classification is done for each of the 6 topics separately.
-
-Finally, in Part 3, subjects completed a belief updating task for each
-of the quizzes. Before starting the task they were reminded of their
-guess for the score. In the ego-relevant treatment, they were reminded
-of their guess about themselves and in the stereotype treatment they
-were reminded of their guess about the other participant. In the
-stereotype treatment, they were also reminded of the characteristics of
-the other participant.
-
-For one topic at a time and in random order, they were presented with
-the three gambles from the example above and were asked to choose one of
-them. The probability of success was determined by their own score in
-the ego-relevant condition, and by the score of the other participant in
-the stereotype condition. Subjects had access to the three probability
-tables in the printout of the instructions at all times and the meaning
-of each cell was explained in detail.
-
-In the interphase, they had to choose which of the 3 tables they wanted
-to see before entering their choice in it. This was done as an
-alternative to a belief elicitation in each round. I take their choice
-of table to be indicative of their beliefs about the underlying type. I
-chose not to elicit the beliefs at each round to stay true to the forces
-in framework 1.
-
-Once they have entered their choice, they observe a sample of 10
-outcomes from the gamble they chose. After observing the outcomes, they
-returned to the choice screen and entered a new choice. In the choice
-screen subjects had access to the entire history of gambles and outcomes
-for that task as well as a summary of the outcomes so far. Once they
-entered 11 gambles (and observed 110 outcomes), they moved on to the
-next topic and repeated the same procedure. They all did this for all 6
-topics.
-
-At the end of the experiment, one of the 6 topics was randomly selected
-to determine the payment. They earned \(\$0.20\) for each correct answer
-in the quiz, and for each success in the task in Part 3 for the selected
-topic.
-
-Randomness is controlled throughout the experiment and sessions by
-setting a seed at the beginning of the first session. The seed was drawn
-at random and remained fixed for all
-sessions.\footnote{The seed that was drawn 
-at the beginning of session 1 was 3452. The same seed was used for all sessions. It is used both for drawing $\omega$ for each of 
-the tasks in the experiment, as well as for drawing the outcomes from the gambles.}
-By doing this I ensure that any two subjects who have the same type and
-face the same exogenous rate will observe the same outcomes. This
-feature allows me to identify differences across subjects in updating
-procedures since if they use the same updating procedure, they should be
-choosing the same gambles.
-
-\hypertarget{predictions}{%
-\section{Predictions}\label{predictions}}
-
-In this section, I outline the behavior that is predicted by each of the
-theories discussed above.
-
-\hypertarget{dogmatic-modeler}{%
-\subsection{Dogmatic Modeler}\label{dogmatic-modeler}}
-
-Since the domain of the problem is discrete and finite in the example,
-the predictions of the original theory apply only to the combinations of
-parameters and initial beliefs for which there is a self-defeating
-equilibrium. In the example, there are 5 such combinations. For each of
-them, the dogmatic modeler predicts that the agent will fall into the
-self-defeating equilibrium and will be able to sustain the misspecified
-belief forever.
-
-Table \ref{tab:table-dog} describes the 5 self-defeating equilibria and
-the effort choices that sustain them. The first columns describe the
-combination of parameters and initial beliefs. The last column describes
-the effort choice that the agent will make in the long run. It is only
-for these combinations of parameter values and beliefs that the dogmatic
-model makes predictions within the Unifying example.
-
-\textbf{Prediction 1D:} \emph{Whenever an agent is of a type
-\(\theta^*\) but mistakenly believes that they are of a type
-\(\hat{\theta}\), and \((\theta^*, \omega^*, \hat{\theta})\) are such
-that there is s self-defeating equilibrium, the agent will fall into the
-trap and choose the effort level that sustains the misspecified belief
-forever.}
-
-The model does not make predictions about what happens in cases where
-there is no stable belief. I assume that because there is no stable
-belief, the agent will eventually have to use some procedure to revise
-their belief about \(\theta\). In such cases, I aim to determine which
-of the alternative explanations provided by the other theories is a
-better fit for the data.
-
-\begin{table}[htbp]
-
-    \centering
-    \begin{tabular}{|c|c|c|c|c|}
-        \hline
-        \textbf{True Type ($\theta^*$)} & \textbf{True State ($\omega^*$)} & \textbf{Believed Type ($\hat{\theta}$)} & \textbf{Believed state ($\hat{\omega}$)} & \textbf{Effort} \\
-        \hline
-        \hline
-        $\theta_L$ & $\omega_H$ & $\theta_M$ & $\omega_L$ & $e_L$ \\
-        \hline
-        $\theta_M$ & $\omega_L$ & $\theta_L$ & $\omega_M$ & $e_M$ \\
-        \hline
-        $\theta_M$ & $\omega_M$ & $\theta_H$ & $\omega_L$ & $e_L$ \\
-        \hline
-        $\theta_M$ & $\omega_M$ & $\theta_L$ & $\omega_H$ & $e_H$ \\
-        \hline
-        $\theta_M$ & $\omega_H$ & $\theta_H$ & $\omega_M$ & $e_M$ \\
-        \hline
-
-    \end{tabular}
-    \caption{Stable beliefs and the effort choices that support them for the unifying example}
-    \label{tab:table-dog}
-\end{table}
-
-Although the dogmatic model does not apply to all possible
-parametrizations and beliefs, whether subjects fall into the
-self-defeating equilibria or not is still informative of the updating
-procedure that they are using. Understanding if the presence of traps is
-a key feature preventing subjects from learning the optimal action is
-important for understanding the prevalence of overconfidence. Similarly,
-gaining insight into what happens when there are no traps is important
-for understanding what are the other reasons why overconfidence might
-arise and prevail.
-
-\hypertarget{switcher}{%
-\subsection{Switcher}\label{switcher}}
-
-Since the switcher starts as the same dogmatic agent, the initial
-behavior of both types of agents is identical, however, because the
-switcher is keeping track of the likelihood ratio, they will be able to
-escape the self-defeating equilibrium if the evidence is convincing
-enough. Therefore there is a positive probability that the switcher will
-adjust their initially misspecified belief about \(\theta\) and learn
-the true state.
-
-\textbf{Prediction 1S:} With positive probability, the switcher will
-escape the self-defeating equilibrium and learn the true state.
-
-One caveat is that when the switcher and the dogmatic agent both start
-with a correctly specified belief, neither of them will fall into the
-self-defeating equilibria and thus will look identical even in the long
-run. This means that in order to distinguish between the two theories, I
-need to look at cases where the agent starts with a misspecified belief.
-
-The probability that the switcher will escape the self-defeating
-equilibrium depends on the prior belief about \(\omega\). If the prior
-is sufficiently tight around the self-defeating equilibrium, the
-likelihood ratio will not grow fast enough, however, in the example
-above, the prior is uniform over the states and therefore, the
-likelihood ratio is more likely to grow fast enough.
-
-\hypertarget{self-attribution-bias}{%
-\subsection{Self-Attribution Bias}\label{self-attribution-bias}}
-
-The key feature of Self-attribution bias is the asymmetric treatment of
-good news and bad news. In particular, the agent will over-attribute
-successes to a high type and under-attribute them to a low type.
-Similarly, they will over-attribute failures to a low state and
-under-attribute them to a high state. This implies that, after observing
-a failure, the agent will adjust their effort downwards by more than
-what an unbiased Bayesian would have done. In contrast, after observing
-a success, the agent will adjust their effort upwards by less than a
-Bayesian would have done and if the bias is large enough, it could be
-that the agent will not adjust their effort upwards at all, or even
-decrease their effort in response to a success.
-
-This is in stark contrast with what a Dogmatic modeler would do. A
-dogmatic modeler always attributes any variation in the outcome to the
-state and never updates their beliefs about \(\theta\). Therefore, they
-will always increase their effort choices after a surprising success and
-decrease it after a failure.
-
-On the other hand, the biased behavior can be in line with the behavior
-of a switcher. In particular, if the agent starts with a misspecified
-belief on \(\hat{\theta}\), and is willing to switch to a belief with
-\(\theta'>\hat{\theta}\), whenever the paradigm shift happens, it will
-likely be in response to a surprising streak of successes. In this case,
-when they adjust their belief about \(\theta\), they will also adjust
-their effort choice. Since they were initially underconfident, they had
-been choosing an effort that was too high relative to the true state,
-and therefore, the effort is likely to fall in response to a surprising
-streak of success.
-
-\textbf{Prediction 1A:} \emph{After observing a failure, the agent will
-adjust their effort downwards by more than a Bayesian would have done.
-After observing a success, the agent will adjust their effort upwards by
-less than a Bayesian would have done. If the bias is large enough, the
-agent might not adjust their effort upwards at all, or even decrease
-their effort in response to a success.}
-
-Prediction 1A helps distinguish between the self-attribution bias and
-the dogmatic modeler. However, it does not help distinguish between the
-self-attribution bias and the switcher. In order to do so, I need to
-look at cases where the agent starts with a correctly specified belief.
-In these cases, the switcher is very unlikely to switch to a different
-belief and therefore, the behavior of the switcher will mostly change in
-the same direction as the information he receives.
-\footnote{If they get a streak of failures they are likely to 
-adjust their effort downwards and if they get a streak of successes they are likely to adjust their effort upwards.}
-Instead, the self-attribution bias will lead to a different behavior. In
-particular, even for agents who have a belief that is correctly
-specified and place a lot of weight on the correct values of \(\theta\),
-the bias will cause these agents to become overconfident after a
-sequence of successes. This force is not present in the switcher or the
-dogmatic and it is the key feature that allows me to identify a biased
-updating procedure.
-
-\textbf{Prediction 2A:} \emph{After observing a streak of successes, the
-agent will update their belief about \(\theta\) upwards. This will lead
-to the possibility of observing subjects who start correctly specified
-and become overconfident.}
-
-\hypertarget{the-bayesian-1}{%
-\subsection{The Bayesian}\label{the-bayesian-1}}
-
-The Bayesian serves as the closest benchmark to a fully rational agent.
-However, as discussed above, they are still vulnerable to falling into
-self-defeating equilibria, in which case, their long-run behavior will
-be identical to that of the dogmatic modeler. The main distinguishing
-feature is that when they do fall into a self-defeating equilibrium,
-there is no bias in the direction of the misspecification that they end
-up being trapped in. In contrast, the dogmatic modeler will always be
-trapped in a misspecified belief that they started with and the
-self-attribution updater will always become overconfident.
-
-\textbf{Prediction 1B:} \emph{When an agent starts with a diffused prior
-and falls into a self-defeating equilibrium, they will be equally likely
-to fall into the underconfident trap as the overconfident trap.}
-
-\textbf{Prediction 2B:} \emph{Bayesian agents always update their effort
-choices in the same direction as the information they receive. That is,
-if they see successes, they would only increase their effort; and if
-they see failures they would only decrease their effort.}
-
-\hypertarget{stereotypes}{%
-\section{Stereotypes}\label{stereotypes}}
-
-So far I have focused only on the case of overconfidence about an
-ego-relevant parameter. However, each of the models can also be used to
-explain the prevalence of stereotypes. An agent can have a dogmatic
-belief about the ability of a particular group of people and either
-under or overestimate the associated parameter. Similarly, they can be
-willing to switch between two dogmatic beliefs about their ability as a
-switcher would. Finally, they can have a biased updating procedure in
-which they treat good news and bad news asymmetrically.
-
-As such, all the predictions discussed above apply to the case of
-Stereotypes as well. My analysis of stereotypes will focus only on the
-degree to which ego-relevance of the type affects the updating procedure
-and not on the motivations behind the bias. I am particularly interested
-in whether the explanatory power of the models differs with the degree
-of ego-relevance of the type.
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-\hypertarget{initial-beliefs-and-misspecifications}{%
-\subsection{Initial Beliefs and
-misspecifications}\label{initial-beliefs-and-misspecifications}}
-
-As mentioned in the predictions section, the dogmatic modeler and the
-switcher are only distinguishable when the agent starts with a
-misspecified belief. Figure \ref{fig:misspecification-hist} shows the
-distribution of misspecifications by treatment. The histogram considers
-the difference between the subject's true score in the quiz and their
-guess about their score. If their guess is in a higher category than
-their true score, they are overconfident; if it is in a lower category,
-they are underconfident; and if it is in the same category, they are
-correctly specified. Overall, 0.43 of the guesses made in the
-questionnaire were misspecified. The rest of the guesses coincided with
-the true score. And the distribution of misspecifications is similar
-across treatments.
-
-\begin{figure}
-\hypertarget{fig:misspecification-hist}{%
-\centering
-\includegraphics{../figures/misspecification_hist.png}
-\caption{Initial misspecifications by
-treatment}\label{fig:misspecification-hist}
-}
-\end{figure}
-
-Although the overall distribution is similar for both treatments, the
-misspecifications arise for different combinations of characteristics in
-each treatment. Figure \ref{fig:misspecification-by-treatment} shows a
-heatmap of the misspecifications that arose in each treatment. In the
-stereotype treatment, subjects are most underconfident about the
-performance of other non-American females in Sports and Video Games. In
-contrast, they are most overconfident about the performance of American
-men in Verbal Reasoning. In the ego-relevant treatment, subjects are
-most underconfident about their own performance in pop culture and art,
-while most overconfident about their performance in Verbal Reasoning.
-
-\begin{figure}
-\hypertarget{fig:misspecification-by-treatment}{%
-\centering
-\includegraphics{../figures/misspecifications_characteristics_treatment.png}
-\caption{Initial misspecifications by treatment and
-characteristics}\label{fig:misspecification-by-treatment}
-}
-\end{figure}
-
-Having widespread misspecifications in both treatments is important for
-the analysis because it allows me to distinguish between the dogmatic
-modeler and the switcher. If there were no misspecifications, the two
-models would be indistinguishable.
-
-\hypertarget{learning}{%
-\subsection{Learning}\label{learning}}
-
-In this section, I analyze the learning behavior of subjects in the
-experiment. There are two parameters that subjects can be learning
-about: the exogenous parameter \(\omega\) and the type \(\theta\). Their
-belief about the exogenous parameter is tracked by their choice of
-effort, while their belief about the type is tracked by their choice of
-a matrix in which to enter their effort.
-
-\hypertarget{learning-about-the-state}{%
-\subsubsection{Learning about the
-state}\label{learning-about-the-state}}
-
-In order to analyze the learning about the state, I look at the share of
-optimal choices that are made at each round. I find that although
-subjects seem to be improving in their choices overall, the last choice
-coincided with the true state only in 52\% of the choices in the last
-round of each task. This is statistically greater than the initial share
-of optimal choices (\(p<0.01\)). However, it is still far from complete
-learning. It is also important to note that learning is similar across
-treatments. The share of choices that were consistent with the true
-state for each round is reported in panel A of Figure
-\ref{fig:learning-by-groups}.
-
-A closer look at whether people learned or not reveals that there is a
-good amount of heterogeneity in the sample. Panel B of Figure
-\ref{fig:learning-by-groups} shows the share of optimal choices by round
-for subjects that chose an effort that matched the state in 3 out of the
-last 4 rounds. It also shows the share of optimal choices for subjects
-who chose an effort that matched the state in fewer than 3 out of the
-last 4 rounds. I label the former as learners and the latter as
-non-learners, with learners making up 39\% of the sample.
-
-\begin{figure}
-\hypertarget{fig:learning-by-groups}{%
-\centering
-\includegraphics{../figures/learning_groups.png}
-\caption{Share of optimal choices by round for subjects who learned
-(their effort in at least 3 out of tha last 4 choices matched the
-state), and subjects who did not learn}\label{fig:learning-by-groups}
-}
-\end{figure}
-
-In what follows I will try to disentangle the reasons for the lack of
-learning. I will argue that it is not due to the presence of traps, but
-rather due to biased updating. According to the theories, the main
-reason why subjects might not learn is that they have an incorrect
-belief about the type or they develop an incorrect belief about the
-type.
-
-\hypertarget{learning-about-the-type}{%
-\subsubsection{Learning about the type}\label{learning-about-the-type}}
-
-\begin{figure}
-\hypertarget{fig:matrix-choices-by-round}{%
-\centering
-\includegraphics{../figures/last_button_consistency.png}
-\caption{Matrix choices by round}\label{fig:matrix-choices-by-round}
-}
-\end{figure}
-
-Since the elicitation of the belief about the type was not incentivized
-and not elicited in a standard way, I first need to confirm that
-subjects were not just randomly choosing a matrix in which to enter
-their effort. The left panel of Figure \ref{fig:matrix-choices-by-round}
-shows the share of subjects who chose a matrix consistent with their
-initial reported belief. In round 1, 71\% of the subjects chose a matrix
-that was consistent with their initial belief. This indicates that
-subjects were not just randomly choosing a matrix in which to enter
-their effort. From round 2 onwards, the share steadily declines, but
-still not as far as to indicate a random choice of matrices. This is
-consistent with the subjects moving away from their starting belief
-through some updating procedure.
-
-On the right panel of Figure \ref{fig:matrix-choices-by-round} I show
-the share of subjects who chose a matrix that is consistent with their
-true type. Unlike the left panel, there is no clear trend, which
-indicates that although they are moving away from their initial belief,
-they are not moving towards their true type, which means that overall,
-misspecification is not decreasing. A closer look at the data reveals a
-good amount of heterogeneity in the underlying behavior.
-
-Figure \ref{fig:transitions} shows the transition matrix for subjects
-who started in each of the 3 possible starting specifications and the
-specifications that they ended up in at the end of the updating task.
-The two things to note are that the initial belief is the most likely
-end belief. This is consistent with some degree of stickiness of the
-misspecifications as the switcher and dogmatic models would predict.
-However, the data also presents a lot of subjects who started with a
-correct belief of the type and ended up overestimating it. This is
-consistent only with the self-attribution bias. Lastly, the subjects who
-initially overestimate the score, are the least likely to learn their
-true type.
-
-\begin{figure}
-\hypertarget{fig:transitions}{%
-\centering
-\includegraphics{../figures/misspecification_transitions.png}
-\caption{Transition matrix for subjects who started in each of the 3
-possible starting specifications and the specification that they ended
-up in at the end of the updating task}\label{fig:transitions}
-}
-\end{figure}
-
-The transition matrix points towards the presence of self-attribution
-bias in the data. However, it is still possible that there is
-heterogeneity in the updating procedure across subjects. In the next
-section I will look at the role of self-defeating equilibria in
-preventing learning. I find that the presence of self-defeating
-equilibria does not seem to be the main deterrent to learning.
-
-\hypertarget{learning-traps}{%
-\subsection{Learning traps}\label{learning-traps}}
-
-As described above, the presence of stable misspecified beliefs act as
-learning traps. If an agent falls into one of these traps, bayesian
-updating will lead them to choose the same effort forever. These
-self-defeating equilibria allow me to distinguish between the dogmatic
-modeler and the switcher. If the agent falls into a trap and stays there
-forever, they are more likely to be a dogmatic modeler. If they escape
-the trap, they are more likely to be a switcher or to be updating with
-some attribution bias.
-
-Overall, it does not seem to be the presence of traps that is preventing
-learning. Panel A of Figure \ref{fig:traps-choice} shows that the share
-of subjects who learned in cases where there was a trap is larger than
-the share of subjects who learned in cases where there was no trap. This
-is true for both treatments. This indicates that even in the presence of
-traps, 44\% of subjects learn. From the share that did not learn when
-there was a trap. A remaining 21\% can be accounted for as being
-trapped.\footnote{A subject is considered trapped when 3 out of their last 4 choices are consistent with 
-a self-defeating equilibrium.} While the rest of the subjects neither
-learned nor were trapped.
-
-A closer look at the behavior of only the cases in which there were
-traps reveals that among those who did not learn, the choices that
-support stable beliefs were chosen much more often than among subjects
-who learned. Figure \ref{fig:traps-choice} shows the share of choices
-that were consistent with a stable belief for the learners and the
-non-learners. The difference is statistically significant (\(p<0.01\)).
-Thus, although the presence of self-defeating equilibria is not the main
-deterrent to learning, it does seem to be a factor in the behavior of
-those who do not learn.
-
-\begin{figure}
-\hypertarget{fig:traps-choice}{%
-\centering
-\includegraphics{../figures/trap_choice.png}
-\caption{Panel A: Share of subjects who learned in cases where there was
-a trap and in cases where there was no trap. Panel B: Share of choices
-that were consistent with a stable belief for the learners, those who
-are in a trap and others}\label{fig:traps-choice}
-}
-\end{figure}
-
-So far I have accounted for 16\% subjects as being trapped, and 39\%
-having learned the state correctly. From the remaining 45\%, 60\% were
-prone to traps but did not fall into them, therefore they could not have
-been dogmatic modelers. Alternative explanations are that they were
-switchers who considered an incorrect alternative model, or that they
-were updating with a bias so large that their effort choices were far
-from optimal. Behavior that is not consistent with either of these falls
-outside of the scope of the theories discussed above.
-
-My results are consistent with the findings of \citet{Hestermann2021}.
-In a laboratory experiment that stays true to Framework 1, they test the
-predictions of the dogmatic modeler. They find that the average pattern
-in behavior is in the direction of the dogmatic modeler, however,
-subjects do not fully act as dogmatics as their actions do not go as far
-as to fully support the self-defeating equilibrium. A lot of the
-differences between the observed behavior in their experiment and the
-model can be attributed to subjects avoiding the self-defeating
-equilibria and learning the true state. In contrast to their study, I
-can provide more insight into the reasons why subjects avoid the
-self-defeating equilibria.
-
-\hypertarget{reactions-to-good-and-bad-news}{%
-\subsection{Reactions to good and bad
-news}\label{reactions-to-good-and-bad-news}}
-
-One of the key features of the self-attribution bias is that the agent
-will react differently to good news and bad news. In particular, they
-will overreact to bad news and underreact to good news. I define good
-news to be any sample of outcomes for which the realized number of
-successes is greater than the average number of successes so far.
-Similarly, I define bad news to be any sample of outcomes for which the
-realized number of successes is smaller than the average number of
-successes so far. In addition, I calculate the difference between the
-realized number of successes and the average number of successes so far
-and call it the news differential. Figure \ref{fig:reaction-news} shows
-the correlation between change in effort and the news differential,
-separately for good and bad news.
-
-The overall pattern is that bad news are associated with a decrease in
-effort, and a more negative news differential is associated with a
-larger decrease in effort. On the contrary, good news are associated
-with a small decrease in effort. As mentioned in the predictions
-section, this is consistent with the self-attribution bias as well as
-with a change of paradigm. It is not consistent with the dogmatic
-modeler or the Bayesian. Because I do not directly elicit beliefs, it is
-not possible to distinguish between the self-attribution bias and the
-change of paradigm with this data alone. Nevertheless, the fact that
-about a third of the subjects started with a correctly specified belief
-and ended up overconfident is consistent only with the self-attribution
-bias. this points towards the fact that misattribution bias is the most
-likely explanation for the behavior of the subjects in the experiment.
-
-\begin{figure}
-\hypertarget{fig:reaction-news}{%
-\centering
-\includegraphics{../figures/effort_change_news.png}
-\caption{Change in effort by news differential}\label{fig:reaction-news}
-}
-\end{figure}
-
-A regression analysis of this same data reveals that indeed, the slopes
-are different for godd and bad news and that the difference is
-statistically
-significant.\footnote{I run a robustness check where I define
-good news to be a net-positive sample (half or more of the outcomes observed in the sample received in that round
-were successful) and bad news to be net-negative sample. I find the same pattern in this alternative regression model
-and the results are reported in the appendix.} The regression results
-are reported in Table \ref{tab:regression}. columns 2 and 3 of the table
-consider the model for each treatment separately. I find no significant
-differences in the parameters across treatment. This is consistent with
-the fact that the bias is not driven by the ego-relevance of
-\(\theta\).\footnote{The ego-relevance of $\theta$ is the motivation behind the self-attribution bias, 
-however, the bias itself is due to an incorrect updating procedure in response to good and bad news. The presence of 
-asymmetric updating in the stereotype condition can be due to self-censoring of the subjects. In particular, subjects 
-who initially underestimated the performance of the other participant might have realized their mistake and 
-by overestimating it after good news. This is consistent with the data presented here as well as with 
-the data observed in the transition matrix for stereotypes which is reported in the Appendix}
-
-\begin{sidewaystable}[!htbp] \centering 
-  \caption{Regression of effort change on news difference with robust standard errors} 
-  \label{tab:regression} 
-\begin{tabular}{@{\extracolsep{5pt}}lccccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{5}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-6} 
-\\[-1.8ex] & \multicolumn{5}{c}{Change in effort} \\ 
- & All & Ego-relevant & Stereotype & Bayesian Simulation & Dogmatic Simulation \\ 
-\\[-1.8ex] & (1) & (2) & (3) & (4) & (5)\\ 
-\hline \\[-1.8ex] 
- Good news & $-$0.12$^{**}$ & $-$0.16$^{***}$ & $-$0.05 & 0.08 & $-$0.08 \\ 
-  & (0.05) & (0.05) & (0.05) & (0.05) & (0.05) \\ 
-  & & & & & \\ 
- News difference & 0.22$^{***}$ & 0.22$^{***}$ & 0.21$^{***}$ & 0.06$^{***}$ & 0.10$^{***}$ \\ 
-  & (0.02) & (0.02) & (0.02) & (0.02) & (0.02) \\ 
-  & & & & & \\ 
- News difference * Good news & $-$0.27$^{***}$ & $-$0.25$^{***}$ & $-$0.29$^{***}$ & $-$0.04 & $-$0.06$^{***}$ \\ 
-  & (0.02) & (0.02) & (0.02) & (0.02) & (0.02) \\ 
-  & & & & & \\ 
- Constant & 0.31$^{***}$ & 0.31$^{***}$ & 0.30$^{***}$ & $-$0.08$^{*}$ & 0.05 \\ 
-  & (0.04) & (0.04) & (0.04) & (0.04) & (0.04) \\ 
-  & & & & & \\ 
-\hline \\[-1.8ex] 
-Observations & 4,680 & 2,700 & 1,980 & 4,680 & 4,680 \\ 
-R$^{2}$ & 0.04 & 0.04 & 0.04 & 0.05 & 0.06 \\ 
-Adjusted R$^{2}$ & 0.04 & 0.04 & 0.04 & 0.05 & 0.06 \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{5}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-\end{sidewaystable}
-
-More convincing evidence against the Switching model is the lack of
-inverse or attenuated correlation between the change in effort and the
-news differential. In particular, if the switcher were the underlying
-model, I would expect overconfident subjects who start with an
-overestimation of \(\theta\) to increase their effort in response to
-surprising bad news. This would flatten the slope of the regression line
-for bad news relative to what a Bayesian would do. \ref{tab:regression}
-shows that the slope for bad news for the
-simulation\footnote{The details on how the data was simulated are explained in the Appendix}
-of the Bayesian updates is much flatter than the slope in the data.
-
-\hypertarget{stereotypes-and-ego-relevance}{%
-\subsection{Stereotypes and
-ego-relevance}\label{stereotypes-and-ego-relevance}}
-
-Throughout the experiment, there is little difference in the behavior of
-subjects across treatments. Two of the main differences are that
-subjects in the ego-relevant treatment are more likely to become
-overconfident when they start with a correct belief. And that subjects
-in the stereotype treatment are more likely to overreact to good news
-when they start by underestimating the performance of the other
-participant.
-
-These two differences present as consistent with the self-attribution
-bias. However, the pattern in the stereotype treatment could also be due
-to self-censoring of the subjects. In particular, subjects who initially
-underestimated the performance of the other participant might have
-realized their mistake and over-compensated their mistake by
-overestimating it after good news. This is consistent with the data and
-offers a more intuitive explanation for why this pattern arises in the
-stereotype treatment.
-
-Furthermore, I find no evidence of confirmation bias which is something
-that has been suggested in the literature of biased
-udating.\footnote{See \citet{benjamin2019} for a review of the literature in this and 
-other biases.} In particular, I find no evidence that subjects who
-overestimate the score of the other participant are more likely to
-over-attribute successes to a high type and under-attribute them to a
-low type. Symmetrically, I find no evidence that subjects who
-underestimate the score of the other participant are more likely to
-over-attribute failures to a low type and under-attribute them to a high
-type. This is consistent with what \citet{Mobius2022} find in their
-experiment in a less complex updating task.
-
-\hypertarget{structural-estimation}{%
-\section{Structural estimation}\label{structural-estimation}}
-
-I have discussed two models that are consistent with the data: the
-self-attribution bias and the switcher. Although the data seems to point
-more convincingly towards the self-attribution bias, I cannot rule out
-the possibility that the switcher is the underlying model. In this
-section, I estimate the structural parameters of the two models and try
-to classify subjects into each of the models to assess how much of the
-data is explained by each of the two likely theories.
-
-\hypertarget{estimation-of-the-switching-threshold}{%
-\subsection{Estimation of the switching
-threshold}\label{estimation-of-the-switching-threshold}}
-
-The switching threshold is the parameter that determines the likelihood
-ratio at which the switcher abandons the status quo paradigm and adopts
-the alternative. In order to estimate this parameter, I assume that all
-subjects are switchers and look at the rounds in which they chose to
-reveal a probability matrix that was different from the one they
-revealed in the previous round. I then calculate the likelihood ratio
-for the alternative paradigm to the status quo. I average across all
-such likelihood ratios and use the average as an estimate of the
-switching threshold.
-
-In detail, Let \(b_{t}^\theta\) be the belief about \(\theta\) in period
-\(t\).\footnote{in the experimental data, 
-I use the revealed matrix as a proxy for the belief. I take the matrix revealed in the previous period 
-to be the status-quo and the matrix revealed in period $t$ to be the alternative}.
-And consider a subject for whom
-\(b_{\tau-1}^\theta \neq b_{\tau}^\theta\), where \(b_{t}^\theta\). That
-is, in period \(\tau-1\) they chose to reveal a matrix that was
-different from the one they revealed in period \(\tau\). The matrix
-revealed in period \(\tau-1\) is the status quo paradigm and the matrix
-revealed in period \(\tau\) is the alternative paradigm. The likelihood
-ratio for the alternative paradigm to the status quo is \[
-\ell = \frac{L(\theta | b_{\tau}^\theta)}{L(\theta | b_{\tau-1}^\theta)}=\frac{p_\tau(o_t|b_{\tau}^\theta)}{p_{\tau}(o_t|b_{\tau-1}^\theta)} 
-\]
-
-where \(p_\tau(o_t|b_{\tau}^\theta)\) is the probability of observing
-the signal \(o_t\) when the agent is of type \(b_{\tau}^\theta\).
-
-The estimate of the switching threshold, \(\alpha\), is the average of
-the likelihood ratios across all subjects who switched in the
-experiment, which is given by
-
-\[\hat{\alpha} = \frac{1}{N}\sum_{i=1}^N \ell_{i\tau}\]
-
-Where \(N\) is the number of switches observed in the experiment.
-
-Because the feedback that subjects receive is the equivalent of 10
-signal realizations, the estimate of the parameter is an upper bound of
-the true parameter. A lower bound would be given by the average
-likelihood ratio in the round before the switch happens. I choose to
-estimate the upper bound to impose a harsher test on the theory.
-
-Because the likelihood ratio is a function of the signal, it depends on
-the sequence of signals that subjects observe. This means that in some
-cases, the likelihood ratio increases by a large amount from one period
-to another. Although such cases are not
-common\footnote{In the data, only 1.8% of the 
-observations have a likelihood ratio that exceeds 5.}, a few very large
-values can skew the average. To avoid a biased parameter, I restrict my
-sample to those observations for which the likelihood ratio is less than
-5.\footnote{The full distribution of likelihood ratios is reported in the appendix}
-Under these assumptions, the estimate of the switching threshold is
-1.09.
-
-This means that the evidence supporting the alternative paradigm needs
-to be approximately 10\% more compelling than the evidence supporting
-the status quo paradigm in order for the agent to switch. The estimation
-treatment by treatment is slightly larger for the Ego condition than for
-the Stereotype condition. However, the difference is not statistically
-significant (p-value=0.96).
-
-I then use this estimate to simulate the behavior of the switcher to
-assess the fit of the model. Which is discussed in the next section.
-
-\hypertarget{estimation-of-the-self-attribution-bias}{%
-\subsection{Estimation of the self-attribution
-bias}\label{estimation-of-the-self-attribution-bias}}
-
-Estimation of the parameters of the self-attribution bias is more
-involved than estimation of the switching threshold. In this case, there
-is no obvious identification strategy that provides a simple estimate of
-the parameters. Instead, I use the simulated method of moments to
-estimate the parameters of the model.
-
-In particular, I simulate the behavior of the self-attribution bias for
-each possible prior and over a grid of parameters. I make the
-simplifying assumption that the distortion is symmetric across good and
-bad news. That is, I assume that
-\(c(\theta_H, \omega, \text{good news})=c(\theta, \omega_L, \text{bad news})=:c_g\)
-and that
-\(c(\theta_M, \omega, \text{bad news})=c(\theta, \omega_M, \text{good news})=:c_b\).
-In addition, I normalize the remaining cases to be equal to 1. This
-leaves me with only 2 parameters to estimate.
-
-The moments that I match in the data are the reaction to good news and
-the reaction to bad news. In particular, I match the average change in
-effort in response to good news and the average change in effort in
-response to bad news. That is I match the following moments:
-
-\[
-\bar{G} = \frac{1}{N}\sum_{i=1}^N \frac{1}{T}\sum_{t=1}^T \mathbb{I}\{o_t > \bar{o}\} \cdot (e_t - e_{t-1}) 
-\] \[
-\bar{B} = \frac{1}{N}\sum_{i=1}^N \frac{1}{T}\sum_{t=1}^T \mathbb{I}\{o_t < \bar{o}\} \cdot (e_t - e_{t-1})
-\] where \(N\) is the number of subjects in the sample, \(T\) is the
-number of rounds in the experiment.
-
-I then use the simulated method of moments to estimate the parameters of
-the model. In particular, I simulate the behavior of the model for each
-possible prior and over a grid of parameters. I then calculate the
-average change in effort in response to good news and the average change
-in effort in response to bad news for each possible prior and over the
-grid of parameters and across \(I\) simulated indiviaduals. I then
-minimize the objective function given by the sum of squared differences
-between the simulated moments and the empirical moments. That is, I
-solve the following problem
-
-\hypertarget{model-fit}{%
-\section{Model fit}\label{model-fit}}
-
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
-
-I designed a setting in which I can distinguish between the forces of
-dogmatism, paradigm shifts, and optimal expectations. Through a
-laboratory experiment, I collected data on behavior and infer beliefs
-from it. I find that the behavior of the subjects is consistent with the
-self-attribution bias. In particular, I find that subjects decrease
-their effort in response to bad news as well as to bad news, although
-the latter decrease is smaller. This is consistent with the
-self-attribution bias as well as with a change of paradigm. However, I
-also observe that about a third of the subjects started with a correctly
-specified belief and ended up overconfident. This is consistent only
-with the self-attribution bias. Therefore, I conclude that the model
-that best explains the data is that of optimal expectations.
-
-I have small or no effects throughout on the ego-relevance of the type.
-Although the motivation behind the theories does not directly apply to
-the case of stereotypes, the lack of stark differences suggests that
-biases arise due to an incorrect updating procedure and not necessarily
-due to the self-serving motivation behind the bias. The lack of
-differences in the behavior of the subjects across treatments could also
-be due to self-censoring of the subjects. In particular, subjects might
-be initially reluctant to express their true belief about a particular
-group of people. In addition, as they learn and realize that their
-beliefs might be incorrect, they might overreact to signals to try to
-compensate for the initial bias. Such an updating procedure would be
-consistent with the self-attribution bias for the case of stereotypes. I
-remain agnostic about whether that is truly the case or whether the lack
-of differences is due to other factors.
-
-Another bias that has been studied and suggested in the literature is
-the confirmation bias. In particular, it has been suggested that
-subjects who are overestimate \(\theta\) in their prior, will
-over-attribute successes to a high type and under-attribute them to a
-low type. Symmetrically, subjects who initially underestimate \(\theta\)
-will over-attribute failures to a low type and under-attribute them to a
-high type. I do not find evidence of such a bias in the data. This is
-consistent with what \citet{Mobius2022} find in their experiment.
-
-I further investigate possible heterogeneity in the underlying models
-being used by estimating the structural parameters of the models.
-
-\newpage
-\appendix
-
-\hypertarget{appendix}{%
-\section{appendix}\label{appendix}}
-
-\hypertarget{transition-matrix-by-treatment}{%
-\subsection{Transition matrix by
-treatment}\label{transition-matrix-by-treatment}}
-
-Figure \ref{fig:transitions-treatment} shows the transition matrix for
-each of the treatments separately. It shows that initial
-misspecifications are more sticky in the ego treatment and that subjects
-who underestimate the score of the other participant in the stereotype
-treatment are more likely to end up overestimating it than in the ego
-treatment. This may signal some sort of self-censoring or overreaction
-in the stereotype treatment.
-
-\begin{figure}
-\hypertarget{fig:transitions-treatment}{%
-\centering
-\includegraphics{../figures/misspecification_transitions_treatment.png}
-\caption{Transition matrix for subjects who started in each of the 3
-possible starting specifications and the specification that they ended
-up in at the end of the updating task}\label{fig:transitions-treatment}
-}
-\end{figure}
-
-\hypertarget{full-distribution-of-likelihood-ratios}{%
-\subsection{Full distribution of likelihood
-ratios}\label{full-distribution-of-likelihood-ratios}}
-
-The likelihood ratios at rounds in which I observe a change in the
-belief about \(\theta\) presents a long right-tail. In particular, 1.8\%
-of the observations have a likelihood ratio that exceeds 5 which would
-mean that the agent requires evidence that is 5 times more compelling in
-favor of the alternative paradigm in order to switch. Figure
-\ref{fig:lr-hist} shows the distribution of likelihood ratios for all
-observations.
-
-\begin{figure}
-\hypertarget{fig:lr-hist}{%
-\centering
-\includegraphics{../figures/lr_hist.png}
-\caption{Distribution of likelihood ratios for all observed belief
-changes}\label{fig:lr-hist}
-}
-\end{figure}
-
-\hypertarget{model-simulation}{%
-\subsection{Model simulation}\label{model-simulation}}
-
-In order to simulate the data for each of the models and asses their
-fit, I simulated the path that each type of agent would have taken given
-each possible realization of \((\theta, \omega)\). I fixed the seed of
-the random number generator to
-3452\footnote{this is the seed that was drawn at random for the experiment}
-and fixed the signals that would be shown in each round after each
-choice by drawing them before simulating. This way, the signals that the
-simulation uses coincide exactly with the signals that a subject would
-have seen in the experiment. I then use each of the algorithms defined
-by the models to simulate the path that the agent would have taken given
-the signal and given an initial belief. For the dogmatic modeler and the
-switcher, I use each possible dogmatic belief. For the Bayesian and the
-self-attribution bias, I use a uniform belief on theta.
-
-\hypertarget{reaction-to-good-and-bad-news-robustness-check}{%
-\subsection{Reaction to good and bad news (robustness
-check)}\label{reaction-to-good-and-bad-news-robustness-check}}
-
-I use an alternate definition for good and bad news and check whether
-the results are robust to this. I define a signal to be a net positive
-if the number of successes is equal to or greater than the number of
-failures. I define a signal to be a net negative if the number of
-failures is greater than the number of successes. I now treat net
-positive signals as good news and net negative signals as bad news. I
-then rerun the regression analysis and find that the results are robust
-to this alternative definition. In particular, net negative signals are
-associated with a stark decrease in effort for both treatments. Net
-positive signals are associated with a small decrease in effort for both
-treatments. The results are reported in Table \ref{tab:regression-net}.
-
-\begin{table}[!htbp] \centering 
-  \caption{Regression of effort change on news difference with robust standard errors} 
-  \label{tab:regression-net} 
-\begin{tabular}{@{\extracolsep{5pt}}lccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-4} 
-\\[-1.8ex] & \multicolumn{3}{c}{Change in effort} \\ 
- & All & Ego-relevant & Stereotype \\ 
-\\[-1.8ex] & (1) & (2) & (3)\\ 
-\hline \\[-1.8ex] 
- Net-positive signal & 0.99$^{***}$ & 0.80$^{***}$ & 1.24$^{***}$ \\ 
-  & (0.05) & (0.05) & (0.05) \\ 
-  & & & \\ 
- Signal value & 0.21$^{***}$ & 0.22$^{***}$ & 0.21$^{***}$ \\ 
-  & (0.02) & (0.02) & (0.02) \\ 
-  & & & \\ 
- Signal value * Net-Positive signal & $-$0.28$^{***}$ & $-$0.26$^{***}$ & $-$0.31$^{***}$ \\ 
-  & (0.02) & (0.02) & (0.02) \\ 
-  & & & \\ 
- Constant & $-$0.49$^{***}$ & $-$0.48$^{***}$ & $-$0.50$^{***}$ \\ 
-  & (0.04) & (0.04) & (0.04) \\ 
-  & & & \\ 
-\hline \\[-1.8ex] 
-Observations & 4,680 & 2,700 & 1,980 \\ 
-R$^{2}$ & 0.05 & 0.05 & 0.05 \\ 
-Adjusted R$^{2}$ & 0.05 & 0.04 & 0.05 \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-\end{table}
-
-\hypertarget{experimental-instructions}{%
-\section{Experimental Instructions}\label{experimental-instructions}}
-
-You are about to participate in an experiment on decision-making. What
-you earn depends partly on your decisions and partly on chance. Please
-turn off cell phones and similar devices now. Please do not talk or in
-any way try to communicate with other participants. We will start with a
-brief instruction period. If you have any questions during this period,
-raise your hand, and your question will be answered so everyone can
-hear.
-
-\textbf{General Instructions}
-
-The experiment is separated into two parts. You will be given
-instructions for each part when it is reached.
-
-\textbf{Part 1:}
-
-In part 1, you will be asked to solve a series of quizzes. In each quiz,
-you will answer multiple choice questions on one of 6 topics: Math,
-Verbal Reasoning, US Geography, Science and Technology, Pop Culture, and
-Sports and Video Games.
-
-The order of the topics will be determined randomly.
-
-You will see only one question at a time. Select an answer and then
-click the ``Next'' button to move on to the following question.
-
-If you leave a question unanswered, it will be marked as incorrect. You
-will not be able to go back to that question once you click the ``Next''
-button.
-
-You will have 2 minutes for each quiz. Once the time runs out, your
-answers will be submitted automatically.
-
-At the end of the experiment, the computer will randomly select one
-topic (each chosen with equal probability), and you will be paid \$0.20
-for each correct answer.
-
-Your score on the quizzes will also affect how much you earn in part 2.
-The higher your score, the more likely you will be to make more money.
-
-When you finish all six quizzes, there will be a short questionnaire
-that will not affect your payoff. Please answer all the questions as
-accurately as you can. You will have access to your answers from Part 1
-when in Part 2, which can help you make better choices.
-
-We will move on to Part 2 once everyone completes Part 1.
-
-\textbf{Part 2 (Ego):}
-
-The task in this part will be repeated once for each topic from Part 1.
-For each task, you will make 11 choices.
-
-In this part, you will choose one of 3 gambles and see 10 outcomes for
-the one you choose. Each outcome will be either a success or a failure,
-and the probability with which each of them is a success is determined
-by 3 factors:
-
-Your score on the quiz for the corresponding topic,
-
-A randomly chosen success rate,
-
-Your choice of a gamble.
-
-Your score is either Low (if it is 5 or less), Mid (if it is between 6
-and 15), or High (if it is 16 or more). You will not know your actual
-score, but you will be reminded of the guess you made in part 1.
-
-The success rate will be chosen randomly by the computer, and it can be
-Rate A, B, or C. Each is drawn with an equal chance (1⁄3 chance each),
-but you will not know which one was drawn. The rate is drawn once, at
-the beginning of the task, and stays fixed throughout.
-
-To maximize the chance of success, you should choose the gamble that
-matches the underlying success rate: - Gamble A maximizes the
-probability of a success when the rate is A, - Gamble B maximizes the
-probability of success when the rate is B and - Gamble C maximizes the
-probability of success when the rate is C.
-
-After 11 gamble choices, the task will change to the next topic. This
-means that the probability of success for this new task will be
-determined by the following: - The score you received on the quiz for
-the corresponding topic and - a new draw of the rate (A, B, or C)
-
-At the end of the experiment, the computer will randomly pick one of the
-topics, and you will be paid \$0.20 for each success. (For each topic,
-there will be 110 outcomes: 10 outcomes for each of the 11 choices you
-made).
-
-We will now go over the details of the probability of success. They are
-described by the tables in the back.
-
-Three tables describe the probabilities. Each table corresponds to one
-of the score levels: Low, Mid, and High.
-
-Each of the columns within the matrix corresponds to one of the success
-rates. You do not know which was drawn, but the gambles' outcomes can
-help you determine the rate.
-
-You will choose a Row.
-
-In order to enter your choice of a gamble, you will first need to choose
-which matrix you want to see. If you choose a matrix that does not
-correspond to your score, the probabilities in the table will not match
-the probabilities with which the outcomes are successful.
-
-The outcomes will be generated using: - your actual score (table), which
-you do not know for certain, - the gamble (row) that you chose, and -
-the rate (column), which you also don't know.
-
-\textbf{Part 2 (stereotype):}
-
-The task in this part will be repeated once for each topic from Part 1.
-For each task, you will make 11 choices.
-
-In this part, you will choose one of 3 gambles and see 10 outcomes for
-the one you choose. Each outcome will be either a success or a failure,
-and the probability with which each of them is a success is determined
-by 3 factors: - The score of another participant on the quiz for the
-corresponding topic, - A randomly chosen success rate, - Your choice of
-a gamble.
-
-The other participant's score is either Low (if it is 5 or less), Mid
-(if it is between 6 and 15), or High (if it is 16 or more). You will not
-know the score but will be reminded of your guess in part 1.
-
-The success rate will be chosen randomly by the computer, and it can be
-Rate A, B, or C. Each is drawn with an equal chance (1⁄3 chance each),
-but you will not know which one was drawn. The rate is drawn once, at
-the beginning of the task, and stays fixed throughout.
-
-To maximize the chance of success, you should choose the gamble that
-matches the underlying success rate: - Gamble A maximizes the
-probability of a success when the rate is A, - Gamble B maximizes the
-probability of success when the rate is B and - Gamble C maximizes the
-probability of success when the rate is C.
-
-After 11 gamble choices, the task will change to the next topic. This
-means that the probability of success for this new task will be
-determined by the following: - The score the other participant got on
-the quiz for the corresponding topic - A new draw of the rate(A, B, or
-C)
-
-At the end of the experiment, the computer will randomly pick one of the
-topics, and you will be paid \$0.20 for each success. (For each topic,
-there will be 110 outcomes: 10 outcomes for each of the 11 choices you
-made).
-
-We will now go over the details of the probability of success. They are
-described by the tables in the back.
-
-Three tables describe the probabilities. Each table corresponds to one
-of the score levels: Low, Mid, and High.
-
-Each of the columns within the matrix corresponds to one of the success
-rates. You do not know which one was drawn, but the gambles' outcomes
-can help you determine the rate.
-
-You will choose a Row.
-
-In order to enter your choice of a gamble, you will first need to choose
-which matrix you want to see. If you choose a matrix that does not
-correspond to the score, the probabilities in the table will not match
-the probabilities with which the outcomes are successful.
-
-Once you enter a choice, the 10 outcomes will be generated using the
-following: - the actual score (matrix), which you do not know for
-certain, - the gamble (row) that you chose, and - the rate (column),
-which you also don't know.
-
-\emph{The full data generating process is printed on the rear side of
-the instructions and always available to the subjects throughout part
-2.} \emph{Each of the matrices is labeled with ``if your/the other
-participant's score is\ldots{}'' depending on the treatment}
-
-\textbf{Screen walk-through script:}
-
-This is the screen where you will enter your choices of gambles. First,
-you must choose the matrix that you want to see. Whatever matrix you
-choose to see does not change the probabilities with which the gables
-are a success. Then, you must choose a gamble (which corresponds to a
-row). The computer will draw 10 outcomes for that gamble using the
-probability in the chosen row and the column corresponding to the rate
-for this task. On the right, you can choose to see either the total
-count of successes and failures for each gamble or the detailed history.
-That is the number of successes and failures for each of your choices.
-The rate will be drawn again for the next task, corresponding to the
-next quiz topic. And you will repeat this process.
-
-\newpage
-
-\renewcommand\refname{References}
   \bibliography{references.bib}

### 2023-10-25 Paper/draft.Rmd
added last session

@@
 author: "Jimena Galindo"
-abstract: "I design a framework and a laboratory experiment that allows for the comparison of multiple theories of misspecified learning.
+abstract: "I design a framework and a laboratory experiment that allow for the comparison of multiple theories of misspecified learning.
 I focus on a framework with endogenous information and a data-generating process ruled by two fundamentals: an ego-relevant parameter and a state.
@@
 is limited in terms of the frameworks it considers. Most of the experimental evidence 
-documenting the bias is collected in settings where subject are passive learners.\footnote{
+documenting the bias is collected in settings where subjects are passive learners.\footnote{
 \citet{Gotte2022} and \citet{Ozyilmaz2022} are exceptions that study settings with endogenous information processes.} They 
@@
 a correctly specified model of learning, they will not be able to abandon their misspecified beliefs. 
-If, the agent is 
+If the agent is 
 dogmatic about their initial belief, @Heidhues2018 show that they will inevitably fall into a trap
@@
 @Ba2023 moves away from dogmatism and endows the agents with a mechanism through which 
-they can abandon incorrect beliefs; this allows them to avoid falling into learning traps. 
+they can abandon incorrect beliefs. This allows them to avoid falling into learning traps. 
 To do so agents perform Bayesian hypothesis tests that evaluate which is the more 
@@
 compare the predictions of all of them. In framework 1 I consider a setting in which the an agent observes
-a continuous output and infers the underlying state. In framework 2, the agent observes a binary 
-outcome and infers the underlying probability of success. In both frameworks, I consider two nested theories 
-of learning.
+a continuous output and infers the underlying parameters. In framework 2, the agent observes a binary 
+outcome and infers the underlying probability of success, which is related to the parameters. In both frameworks, I consider two nested theories of learning.
 
@@
 and such that conditional on a pair of parameters $(\theta, \omega)$, there is a unique optimal action. 
-additionally, $\varepsilon\sim N(0, \sigma)$ is noise in the output.
+Additionally, $\varepsilon\sim N(0, \sigma)$ is noise in the output.
 
@@
 He repeats this process infinitely many times. I make the simplifying assumption that the agent is myopic and chooses the action 
-that maximizes the payoff in each period. This assumption simplifies the analysis and plays a role in whether an agent who updates
- their beliefs using Bayes rule would learn the truth or not, however, for the main theory discussed in this section, the results hold
- even when relaxing this assumption. The behavior of a forward-looking agent is further discussed in the conclusion.
-
-A key notion in this setting is that of a self-defeating equilibrium\footnote{This notion is an adaptation of the Berk-Nash equilibrium in 
-\citet{Esponda2016} to this setting with only one agent}. 
-A \emph{self-defeating equilibrium} is a belief and action pair such that the agent's belief about their type is misspecified and the 
-outcome generated by the action is consistent with the misspecified belief. This means that the average outcome under the true type and the true 
-state equals the average output the agent expects under the misspecified belief. The agent's belief is said to be 
-\emph{stable} when this happens.
-
-Within this framework, I consider two nested theories of belief updating: the first one is a dogmatic modeler from @Heidhues2018,
-The second one is a switcher, as in @Ba2023. The dogmatic modeler can be seen as a switcher with an infinitely sticky initial belief
-so the two theories are nested. However, outside of the limiting case, they produce different 
+that maximizes the payoff in each period.
+This assumption simplifies the analysis and plays a role in whether an agent who updates their beliefs using Bayes rule would learn the truth or not, however, for the main theory discussed in this section, the results hold even when relaxing this assumption.
+
+A key notion in this setting is that of a self-defeating equilibrium\footnote{This notion is an adaptation of the Berk-Nash equilibrium in \citet{Esponda2016} to this setting with only one agent}. 
+A \emph{self-defeating equilibrium} is a belief and action pair, $(p, a)$, such that the agent's belief about their type is misspecified, and the outcome generated by the action is consistent with the misspecified belief.
+The agent's belief is said to be \emph{stable} when this happens and the average output is
+
+$$\bar{h}(a^*) = h(\hat{\theta}, \hat{\omega}, a)$$
+Where $\hat{\theta}$ and $\hat{\omega}$ is the type-state pair on which the misspecified belief places all probability.
+That is, the agents belief is $p(\hat{\theta}, \hat{\omega}) = 1$ and $p(\theta, \omega) = 0$ for all other values of the parameter.
+
+Within this framework, I consider two nested theories of belief updating: the first one is a dogmatic modeler adapted from @Heidhues2018,The second one is a switcher, as in @Ba2023.
+The dogmatic modeler can be seen as a switcher with an infinitely sticky initial belief so the two theories are nested.
+However, outside of the limiting case, they produce different
 predictions about the agent's behavior. I discuss each of them separately in what follows.
@@
 
-Take the action space to be the same as the state space $\Omega$ and  $\Omega =A=[\underline{a}, \infty)$.
-
-A dogmatic agent does not update their beliefs about $\theta$, instead, he holds a degenerate belief that places probability on 
-$\hat{\theta}$, which is potentially misspecified. 
-In this case, no matter
-how much information he gathers against being of type $\hat{\theta}$, he will not update his beliefs about it. 
-Any discrepancies between the 
-observed outcomes and his believed type are incorporated using the Bayes rule to update his beliefs about $\omega$.
-@Heidhues2018 show that, under certain assumptions on the per-period utility,\footnote{The assumptions are that 
-$u$ is twice continuously differentiable with: (i)$u_{aa}<0$ and $u_a(\underline{a},  \theta, \omega)>0>u_a(\Bar{a}, \theta, \omega)$, 
-(ii) $u_{\theta}, u_{\omega}>0$ and (iii) $u_{a\theta}<0$ and $u_{a\omega}>0$. Where $\underline{a}$ is the
-minimal action and $\Bar{a}$ is the maximal one. 
- The direction of the derivatives is a normalization
-and the results would hold even when the signs are reversed.} 
-a dogmatic modeler will inevitably fall into a self-defeating equilibrium. The equilibrium will be such that
-the outcomes they observe reinforce their belief on $\omega$ in such a way that as $t\to\infty$ the agent will 
-be sure that
-the state is some $\omega^{'}$ consistent with their believed type and the observed data. In other words, 
-they will be in a self-defeating equilibrium with a stable belief that places probability one on the incorrect
-parameters $(\hat{\theta}, \omega_{\infty})$
-
-The mechanism by which the dogmatic agent falls into the self-defeating equilibrium is the following: Suppose the agent holds the 
-misspecified belief that they are type $\hat{\theta}>\theta^*$. For any prior over $\omega$, the agent will be disappointed by the outcome.
-He expected a gain of $h(\hat{\theta}, \mathbb{E}(\omega), a)$ but instead observes  $h(\hat{\theta}, \omega^*, a)$. 
-There are two 
-possible sources for the disappointment: the first is that the realized state is lower than the expected state; the second source is that the
-agent is of type $\theta^*$ and therefore, for all possible states, his gain will be lower than what he expected. Because the agent is dogmatic,
-he will not update his beliefs about $\theta$ and as a consequence will attribute the disappointment to the state being lower than expected.
-He will continue to update in this way until he converges to a belief about $\omega$ that is stable. Such a belief will 
-explain the observed utility perfectly and allow the agent to rationalize his dogmatic belief about $\theta$. 
-Under the assumptions of @Heidhues2018, there is a unique value of $\omega$ at which the belief is stable, I will refer to such value
-as $\omega_\infty$.
+Take the action space to be the same as the state space $\Omega$ and let $\Omega=A:=[\underline{a}, \infty)$.
+
+A dogmatic agent is characterized by a learning model where he does not update their beliefs about $\theta$, instead, he holds a degenerate belief that places all probability on $\hat{\theta}$, which is potentially misspecified.
+In this case, no matter how much information he gathers against being of type $\hat{\theta}$, he will not update his beliefs about it. 
+Any discrepancies between the observed outcomes and his believed type are incorporated using the Bayes rule to update his beliefs about $\omega$.
+@Heidhues2018 show that, under certain assumptions on the per-period utility,\footnote{The assumptions are that $u$ is twice continuously differentiable with: (i)$u_{aa}<0$ and $u_a(\underline{a},  \theta, \omega)>0>u_a(\Bar{a}, \theta, \omega)$, (ii) $u_{\theta}, u_{\omega}>0$ and (iii) $u_{a\theta}<0$ and $u_{a\omega}>0$.
+Where $\underline{a}$ is the
+minimal action and $\Bar{a}$ is the maximal one. The direction of the derivatives is a normalization
+and the results would hold even when the signs are reversed.} a dogmatic modeler will inevitably fall into a self-defeating equilibrium.
+The equilibrium will be such that the outcomes they observe reinforce their belief on $\omega$ in such a way that as $t\to\infty$ the agent will be sure that the state is some $\omega^{'}$ consistent with their believed type and the observed data.
+In other words, they will be in a self-defeating equilibrium with a stable belief that places probability one on the incorrect parameters $(\hat{\theta}, \omega_{\infty})$
+
+The mechanism by which the dogmatic agent falls into the self-defeating equilibrium is the following: Suppose the agent holds the misspecified belief that they are type $\hat{\theta}>\theta^*$.
+For any prior over $\omega$, the agent will be disappointed by the outcome.
+That is:
+$$\bar{h}(\theta^*, \omega^*, a_t^*) := \frac{1}{T}\sum_t \left[h(\theta^*, \omega^*, a_t^*)+\varepsilon_t\right]<\frac{1}{T}\sum_t \left[h(\hat{\theta}, \mathbb{E}(\omega), a_t^*)+\varepsilon_t\right]$$
+Where the right-hand-side of the inequality represents the average outcome that the agent expected.
+
+There are two possible sources for the disappointment: the first is that the realized state is lower than the expected state; the second source is that the agent is of type $\theta^*$ and therefore, for all possible states, his gain will be lower than what he expected.
+
+Because the agent is dogmatic, he will not update his beliefs about $\theta$ and as a consequence will attribute the disappointment to the state being lower than expected.
+He will continue to update in this way until he converges to a belief about $\omega$ that is stable.
+Such a belief will explain the observed utility perfectly and allow the agent to rationalize his dogmatic belief about $\theta$.
+Under the assumptions of @Heidhues2018, there is a unique value of $\omega$ at which the belief is stable, I will refer to such value as $\omega_\infty$.
 This mechanism is illustrated in Example 1.
@@
 An agent is a \emph{switcher} if they behave as a dogmatic, but are willing to entertain the possibility that they are of a different type.
-In particular, when they start off as a misspecified dogmatic, they are willing to switch to a different dogmatic belief if the data is
-convincing enough. Their prior is still degenerate and assigns probability one to a particular type, and zero to 
-all other types. This means that a Bayesian update on $\theta$ does not change their beliefs about the type.
+In particular, when they start off as a misspecified dogmatic, they are willing to switch to a different dogmatic belief if the data is convincing enough.
+Their prior is still degenerate and assigns probability one to a particular type, and zero to all other types.
+This means that a Bayesian update on $\theta$ does not change their beliefs about the type.
 However, they are willing to entertain two such beliefs and have a mechanism by which they decide which belief to adopt at any period $t$.
 
-In order to abandon their initial dogmatic belief, the agent needs to observe a sequence of outcomes 
-that are sufficiently unlikely
-to have happened if they were of the type they initially believed. In order to evaluate if the evidence is convincing enough, 
-they keep track of the likelihood that each of the
-possible types generated the data. If the likelihood ratio is sufficiently large, the agent will switch to the alternative
-and behave as if they are dogmatic about the new type.
+In order to abandon their initial dogmatic belief, the agent needs to observe a sequence of outcomes that are sufficiently unlikely to have happened if they were of the type they initially believed.
+In order to evaluate if the evidence is convincing enough, they keep track of the likelihood that each of the possible types generated the data.
+If the likelihood ratio is sufficiently large, the agent will switch to the alternative and behave as if they are dogmatic about the new type.
 
@@
 
-Where $h^t$ is the history of outcomes up to time $t$ and $\alpha$ is the switching threshold.\footnote{Notice that if $\alpha \to \infty$, the behavior of the switcher will be indistinguishable from that of the Dogmatic modeler.
+Where $h^t$ is the history of outcomes up to time $t$, and $\alpha$ is the switching threshold.\footnote{Notice that if $\alpha \to \infty$, the behavior of the switcher will be indistinguishable from that of the Dogmatic modeler.
 In this sense, the switcher is a generalization of the dogmatic type.} By keeping track of the 
 likelihood ratio, the agent can perform a \emph{Bayesian hypothesis test} and adopt the Dogmatic belief that best fits 
-the data.\footnote{In a related problem \citet{Schwarstein2021} proposes a similar updating procedure which relies on the Bayesian 
-hypothesis test. However, in their model there is a sender who optimally chooses to propose a model that fits the data}
+the data.\footnote{In a related problem \citet{Schwarstein2021} proposes a similar updating procedure which relies on the Bayesian hypothesis test.
+However, in their model there is a sender who optimally chooses to propose a model that fits the data}
 
@@
 As in framework 1, the agent is of some type $\theta^* \in \Theta$ and the state is $\omega \sim F(\Omega)$.
-In this case, the agent chooses an action 
-$a\in A$
-and observes a binary outcome that is either a success or a failure. Denote the outcome by $o \in \{s,f\}$. The probability of 
-observing a success is increasing in $\theta$ and in $\omega$. Whenever the agent observes a success, he gets a payoff $v>0$ and
-whenever the outcome is a failure, the payoff is 0.  In addition, the probability of success is such that for each state, 
-there is a unique optimal action that maximizes the agent's expected payoff. Therefore, the probability 
-of success can be seen as a monotone transformation of the utility from Framework 1.
-
-I focus on two nested theories that have been widely studied within this framework: Full Bayesian updating and self-serving attribution 
-bias. I explain each of these classical models of belief updating in what follows
+In this case, the agent chooses an action $a\in A$ and observes a binary outcome that is either a success or a failure.
+Denote the outcome by $o \in \{s,f\}$.
+The probability of observing a success is increasing in $\theta$ and in $\omega$.
+Whenever the agent observes a success, he gets a payoff $v>0$ and whenever the outcome is a failure, the payoff is 0.
+In addition, the probability of success is such that for each state, there is a unique optimal action that maximizes the agent's expected payoff.
+Therefore, the probability of success can be seen as a monotone transformation of the utility from Framework 1.
+
+I focus on two nested theories that have been widely studied within this framework: Full Bayesian updating and self-serving attribution bias.
+I explain each of these classical models of belief updating in what follows
 
@@
 A Bayesian agent simultaneously updates their beliefs about $\theta$ and $\omega$ by using Bayes' rule. 
-The posterior at period t+1 about $\theta$ after observing outcom $o$ is given by:
+The posterior at period t+1 about $\theta$ after observing outcome $o$ is given by:
 $$
@@
 learn even with infinite amounts of data. This happens because, by being myopic, they do not internalize 
-the tradeoff between flow payoff
-and learning. This can result in too little experimentation to learn their true type. An alternative to this approach is given 
-by @Hestermann2021 and is discussed in the concluding remarks. Regardless, this approach is useful as a 
-benchamrk for the other theories discussed in this paper.
-
-Also notice that if a fully Bayesian agent has a dogmatic prior, they will never update their beliefs 
-about the parameter that they are dogmatic about. This will imply that they are prone to the same types 
-of errors as the dogmatic modeler in framework 1.
+the trade off between flow payoff and learning.
+This can result in too little experimentation to learn their true type.
+An alternative to this approach is given by @Hestermann2021 and is discussed in the concluding remarks.
+Regardless, this approach is useful as a benchmark for the other theories discussed in this paper.
+
+Also notice that if a fully Bayesian agent has a dogmatic prior, they will never update their beliefs about the parameter that they are dogmatic about.
+This will imply that they are prone to the same types of errors as the dogmatic modeler in framework 1.
 
@@
 A Self-Serving Bayesian is an agent who uses a biased version of Bayes rule to update their beliefs.
-They will update their beliefs 
-about the state $\omega$ and his type $\theta$ simultaneously
-by over-attributing successes to a high value of $\theta$ and under-estimating the role of higher $\omega$. Similarly,
-he will attribute failure to a low state to a greater degree than an unbiased agent would. 
-To model the self-serving attribution bias, I take the approach of @benjamin2019, where the posterior odds are given by:
+They will update their beliefs about the state $\omega$ and his type $\theta$ simultaneously by over-attributing successes to a high value of $\theta$ and under-estimating the role of higher $\omega$.
+Similarly, he will attribute failure to a low state to a greater degree than an unbiased agent would.
+This sort of biased updating is referred to as \emph{misattribution bias}.
+
+To model the misattribution bias, I take the approach of @benjamin2019, where the posterior odds are given by:
 
@@
 
-with $c(\theta_H, \omega, o)<c(\theta_M, \omega, o)<c(\theta_L, \omega, o)\leq 1$
-and $c(\theta, \omega_L, o)<c(\theta, \omega_M, o)<c(\theta, \omega_H, o)\leq 1$.
-
-This formulation of the bias means that the agent will over-attribute successes to a high type and 
-under-attribute them to a low type Whereas they will over-attribute failures to a low state and
-under-attribute them to a high state. The bias is introduced by distorting the perceived likelihood 
-that the signal was generated by either high values of $\theta$ when it is a success, or by low 
-values of $\omega$ when it is a failure.  The parameter $c$ determines the degree of bias and imposes
-enough restrictions to ensure that the model is still falsifiable.
+with $c(\theta_H, \omega, o)<c(\theta_M, \omega, o)<c(\theta_L, \omega, o)$
+and $c(\theta, \omega_L, o)<c(\theta, \omega_M, o)<c(\theta, \omega_H, o)$. And where $h_t$ is the history of signal realizations observed up to period t.
+
+This formulation of the bias means that the agent will over-attribute successes to a high type and under-attribute them to a low type Whereas they will over-attribute failures to a low state and under-attribute them to a high state.
+The bias is introduced by distorting the perceived likelihood that the signal was generated by either high values of $\theta$ when it is a success, or by low values of $\omega$ when it is a failure.
+The parameter $c$ determines the degree of bias and imposes enough restrictions to ensure that the model is still falsifiable.
+
+Define the distortion in the likelihood by $\Delta_c p(h^t|\theta, \omega) = p(h^t|\theta, \omega)^{c(\theta, \omega, o_t)} - p(h^t|\theta, \omega)$.
+Notice that because $p(h^t|\theta, \omega)<1$, if $c(\cdot)<1$, a smaller exponent $c$ implies a larger distortion upwards for fixed $h^t$, and fixed parameters $\theta$ and $omega$.
+While a $c(\cdot)>1$ implies a distortion downwards and it is larger when $c(\cdot)$ is larger.
 
@@
 
-In order to compare the predictions of the theories discussed above, I develop a unifying example that allows me to
-isolate the forces behind each of the theories. The example is a modification of the one in @Heidhues2018 and is adapted to 
-implementable in the lab.
+In order to compare the predictions of the theories discussed above, I develop a unifying example where the forces behind each of the theories can be isolated.
+The example is a modified from @Heidhues2018 and is adapted to be implementable in the lab.
 
@@
 They face an unknown exogenous success rate
-$\omega \in \{\omega_L, \omega_M, \omega_H\}$ with $\omega_H>\omega_M>\omega_L$. Each of the values of $\omega$ is realized with 
-equal probability. 
+$\omega \in \{\omega_L, \omega_M, \omega_H\}$ with $\omega_H>\omega_M>\omega_L$.
+Each of the values of $\omega$ is realized with equal probability.
 The agent knows the distribution of $\omega$ but not its realized value.
@@
 $\theta$\footnote{which is potentially misspecified as in the dogmatic and switcher cases discussed above} 
-and chooses a binary gamble $e in \{e_L, e_M, e_H\}$. The agent observes whether the gamble is a success or a failure and 
+and chooses gamble $e in \{e_L, e_M, e_H\}$. The agent observes whether the gamble is a success or a failure and 
 gets a payoff of $1$ and if it is a success; they get $0$ otherwise.
@@
 Notice that both $\theta$ and $\omega$ can be identified from the outcomes if enough variation in the effort choices exists.
-This can be seen by confirming that there is no pair of $\theta$ and $\omega$ such that the probability of success is the same for all effort 
-choices. Thus, by changing the effort choice, the agent can learn both their type and the state if they observe enough outcomes.
+This can be seen by confirming that there is no pair of $\theta$ and $\omega$ such that the probability of success is the same for all effort choices.
+Thus, by changing the effort choice, the agent can learn both their type and the state if they observe enough outcomes.
 
@@
 
-In the data-generating process described above, there are five such equilibria. For example, if the agent is of type $\theta_M$  but
-mistakenly believes that he is of type $\hat{\theta}=\theta_H$ and the 
-and $\omega^* = \omega_M$, when the effort chosen is $e_L$, the agent will observe a success with 45% chance. Because the agent 
-dogmatically believes that their type is high, they will erroneously conclude that the rate is $\omega_L$. Under this belief,
-the optimal action is $e_L$ which will continue to generate successes with $45%$ probability, further reinforcing
-the incorrect belief. By doing so, the agent forgoes the payoff from gamble $e_M$ which would yield a success with $65\%$ chance.
+In the data-generating process described above, there are five such equilibria.
+For example, if the agent is of type $\theta_M$ but mistakenly believes that he is of type $\hat{\theta}=\theta_H$ and the and $\omega^* = \omega_M$, when the effort chosen is $e_L$, the agent will observe a success with 45% chance.
+Because the agent dogmatically believes that their type is high, they will erroneously conclude that the rate is $\omega_L$.
+Under this belief, the optimal action is $e_L$ which will continue to generate successes with $45%$ probability, further reinforcing the incorrect belief.
+By doing so, the agent forgoes the payoff from gamble $e_M$ which would yield a success with $65\%$ chance.
 
 By including self-confirming equilibria, the example captures the forces from each of the updating mechanisms discussed in the 
-previous section and allows for the comparison of the main forces behind the theories. For realizations of $(\theta, \omega)$ for which there are 
-self-confirming equilibria, the dogmatic agent will fall into the 
-trap whereas the switcher will be able to escape it. Similarly, an agent with self-attribution bias will update their beliefs differently from an unbiased Bayesian, leading
-them to choose different gambles. I exploit such cases in order to test which model is a better fit for how subjects behave in a 
-laboratory experiment.\footnote{because the setting does not match that of @Heidhues2018, there will be situations for which the theory 
-does not provide a prediction. If such cases arise in the lab, they will not be used for the analysis. However, whether a misspecified 
-belief persists or not for the switcher, depends highly on the realized history of signals that he gets.} In what follows I explain 
-the details of how this example was implemented in the lab.
+previous section and allows for the comparison of the main forces behind the theories.
+For realizations of $(\theta, \omega)$ for which there are self-confirming equilibria, the dogmatic agent will fall into the trap whereas the switcher will be able to escape it.
+Similarly, an agent with self-attribution bias will update their beliefs differently from an unbiased Bayesian, leading them to choose different gambles.
+I exploit such cases in order to test which model is a better fit for how subjects behave in a laboratory experiment.\footnote{because the setting does not match that of @Heidhues2018, there will be situations for which the theory does not provide a prediction.
+If such cases arise in the lab, they will not be used for the analysis.
+However, whether a misspecified belief persists or not for the switcher, depends highly on the realized history of signals that he gets.} In what follows I explain the details of how this example was implemented in the lab.
 
@@
 In this section, I outline the behavior that is predicted by each of the theories discussed above.
+Some of the predictions are made relative to the Bayesian benchmark.
+In particular, the reaction to good and bad news is very informative of which model is most likely to be underlying the behavior.
+Define \emph{good news} to be a sample of signal realizations such that the number of successes in the sample is larger than the average number of successes observed so far.
+i.e.
+if
+
+$$ \sum_i \mathbb{I}\{o_{iT}=success\} \geq \frac{1}{T} \sum_{t=0}^T\sum_i \mathbb{I}\{o_{it}=success\}$$
+where T is the current period and $o_{t}=[o_{it}]_{i=1}^I$ is the sample observed at period $t$.
+\emph{Bad news} are any other kind of signal realization.
+Denote the set of good news at period t by $\mathcal{G}_t$ and let $s_t$ be the number of successes in $o_t$.
+
+Given the definition of good and bad news, the reaction of the agent to each kind of news is the change in their choice, conditional on the signal realization.
+Therefore, what we are interested are the coefficients of the following regression model, where the actions are those that a bayesian agent would choose:
+
+$$ \Delta a = \beta_0 + \beta_1\mathbb{I}\{o_t\in \mathcal{G}_t\} + \beta_2(s_{t} - s_{t-1}) + \beta_3\mathbb{I}\{o_t\in \mathcal{G}_t\}(s_{t} - s_{t-1})  $$
+
+Where $(s_{t} - s_{t-1})$ is the size of the surprise and $\Delta a$ is the change in action.
+$\beta_2$ is the reaction of the agent to bad news with surprise $(s_{t} - s_{t-1})$.
+And $\beta_2 + \beta_3$ is the reaction to good news with surprise $(s_{t} - s_{t-1})$.
+Notice that for a dogmatic modeler $\beta_2\geq0$ and $\beta_2+\beta_3\geq 0$ as more successes are always indicative of a better state.
 
@@
 
-The model 
-does not make predictions about what happens in cases where there is no stable belief. I assume that because there is 
-no stable belief, the agent will eventually
-have to use some procedure to revise their belief about $\theta$. In such cases, I aim to determine which of the alternative 
-explanations provided by the other theories is a better fit for the data.
+In term of the dogmatic's reagtion to good and bad news, let $\beta^D$ denote the coefficients of the regression model above when the actions are those predicted by the dogmatic model.
+
+**Prediction 2D:** _Before falling into a trap, the dogmatic modeler reacts more to good and bad news than the Bayesian would. i.e. $\beta_2^D>\beta_2$ and $\beta_3^D > \beta_3$._
+
+The model does not make predictions about what happens in cases where there is no stable belief.
+I assume that because there is no stable belief, the agent will eventually have to use some procedure to revise their belief about $\theta$.
+In such cases, I aim to determine which of the alternative explanations provided by the other theories is a better fit for the data.
 
@@
 
-**Prediction 1S:** With positive probability, the switcher will escape the self-defeating equilibrium and learn the true state.
+**Prediction 1S:** _With positive probability, the switcher will escape the self-defeating equilibrium and learn the true state._
+
+Let $\beta^S$ be the coefficients of the regresion model when the actions are those taken by a switcher.
+
+**Prediction 2S:** _When there is no change of paradigm, the switcher behaves as the dogmatic.
+When there is a change in paradigm, the reaction to good and bad news is attenuated or even in the opposite direction of what a Bayesian would have done.
+that is $\beta_2^S<\beta_2$ and $\beta_2^S + \beta_3^S<\beta_2+\beta_3$_
 
@@
 will fall into the self-defeating equilibria and thus will look identical even in the long run. This means that
-in order to distinguish between the two theories, I need to look at cases where the agent starts with a misspecified belief.
+in order to distinguish between the two theories, I need to look at cases where the agent starts with a misspecified belief and the switcher changes paradigm.
 
@@
 
+Let $\beta^A$ be the coefficients of the regression model when the agent updates with misattribution bias.
+
 **Prediction 1A:** _After observing a failure, the agent will adjust their effort downwards by more than a Bayesian would have done.
-After observing a success, the agent will adjust their effort upwards by less than a Bayesian would have done. If the bias is large enough,
-the agent might not adjust their effort upwards at all, or even decrease their effort in response to a success._
-
-Prediction 1A helps distinguish between the self-attribution bias and the dogmatic modeler. However, it does not help distinguish between
-the self-attribution bias and the switcher. In order to do so, I need to look at cases where the agent starts with a correctly specified belief.
-In these cases, the switcher is very unlikely to switch to a different belief and therefore, the behavior of the switcher will mostly change
-in the same direction as the information he receives. \footnote{If they get a streak of failures they are likely to 
-adjust their effort downwards and if they get a streak of successes they are likely to adjust their effort upwards.} Instead, 
-the self-attribution bias will lead to a different behavior. In particular, even for agents who have a belief 
-that is correctly specified and place a lot of weight on the correct values of $\theta$, the bias will 
-cause these agents to become overconfident after a sequence of successes. This force is not present in the switcher or the dogmatic
-and it is the key feature that allows me to identify a biased updating procedure.
-
-**Prediction 2A:** _After observing a streak of successes, the agent will update their belief about $\theta$ upwards. This will lead to the 
-possibility of observing subjects who start correctly specified and become overconfident._
-
-## The Bayesian
-
-The Bayesian serves as the closest benchmark to a fully rational agent. However, as discussed above, 
-they are still vulnerable to falling into self-defeating equilibria, in which case, their long-run behavior
-will be identical to that of the dogmatic modeler. The main distinguishing feature is that when they do 
-fall into a self-defeating equilibrium, there is no bias in the direction of the misspecification that they 
-end up being trapped in. In contrast, the dogmatic modeler will always be trapped in a misspecified belief
-that they started with and the self-attribution updater will always become overconfident.
-
-**Prediction 1B:** _When an agent starts with a diffused prior and falls into a self-defeating equilibrium,
-they will be equally likely to fall into the underconfident trap as the overconfident trap._
-
-**Prediction 2B:** _Bayesian agents always update their effort choices in the same direction as the information they receive. 
-That is, if they see successes, they would only increase their effort; and if they see failures they would 
-only decrease their effort._
+After observing a success, the agent will adjust their effort upwards by less than a Bayesian would have done.
+If the bias is large enough, the agent might not adjust their effort upwards at all, or even decrease their effort in response to a success.
+That is $\beta_2^A > \beta_2$ and $\beta_2^A + \beta_3^A<\beta_2 + \beta_3$_
+
+In addition to their behavior, there is an additional characteristic feature of misattribution bias that is not present in other models.
+This is the only model in which an agent could start off with a correct belief and become more overconfident.
+In the long-run.
+
+**Prediction 2A:** _After observing a streak of successes, the agent will update their belief about $\theta$ upwards.
+This will lead to the possibility of observing subjects who start correctly specified and become overconfident._
 
@@
 
-$$ arg\min_j \sum_k \frac{1}{T}\sum_t{\left[e_{ikt}-\tilde{e}_{t}(\theta, \omega, j)\right]} $$
-The histogram in Figure \ref{fig:best-models} shows the distribution of the best fitting models in the sample. The average fit of each model is reported in the Appendix.
+$$ arg\min_j \sum_k \frac{1}{T}\sum_t{\left[e_{ikt}-\tilde{e}_{t}(\theta, \omega, j)\right]^2} $$
+The histogram in Figure \ref{fig:best-models} shows the distribution of the best fitting models in the sample.
+The average fit of each model is reported in the Appendix.\footnote{The best fitting models are robust to different distance functions.
+In particular, the share of subjects best explained by misattribution bias is the same when using norm 1.}
 
@@
 
-Another bias that has been studied and suggested in the literature is the confirmation bias. In particular,
+A different bias that has been studied and suggested in the literature is the confirmation bias. In particular,
 it has been suggested that subjects who are overestimate $\theta$ in their prior, will over-attribute 
@@
 structural parameters of the models.
+I find that under the average parameters, most subjects are best explained by misattribution bias in both treatments.
+However, for the subjects for whom other models are a better explanation, those models have a better fit than the misattribution bias does for those better explained by it.
 

### 2023-10-25 Paper/draft.tex
added last session

@@
 \author{Jimena Galindo}
-\date{October 15, 2023}
+\date{October 24, 2023}
 
@@
 \begin{abstract}
-I design a framework and a laboratory experiment that allows for the
+I design a framework and a laboratory experiment that allow for the
 comparison of multiple theories of misspecified learning. I focus on a
@@
 experimental evidence documenting the bias is collected in settings
-where subject are passive learners.\footnote{
+where subjects are passive learners.\footnote{
 \citet{Gotte2022} and \citet{Ozyilmaz2022} are exceptions that study settings with endogenous information processes.}
@@
 learning, they will not be able to abandon their misspecified beliefs.
-If, the agent is dogmatic about their initial belief,
+If the agent is dogmatic about their initial belief,
 \citet{Heidhues2018} show that they will inevitably fall into a trap and
@@
 \citet{Ba2023} moves away from dogmatism and endows the agents with a
-mechanism through which they can abandon incorrect beliefs; this allows
+mechanism through which they can abandon incorrect beliefs. This allows
 them to avoid falling into learning traps. To do so agents perform
@@
 the an agent observes a continuous output and infers the underlying
-state. In framework 2, the agent observes a binary outcome and infers
-the underlying probability of success. In both frameworks, I consider
-two nested theories of learning.
+parameters. In framework 2, the agent observes a binary outcome and
+infers the underlying probability of success, which is related to the
+parameters. In both frameworks, I consider two nested theories of
+learning.
 
@@
 such that conditional on a pair of parameters \((\theta, \omega)\),
-there is a unique optimal action. additionally,
+there is a unique optimal action. Additionally,
 \(\varepsilon\sim N(0, \sigma)\) is noise in the output.
@@
 theory discussed in this section, the results hold even when relaxing
-this assumption. The behavior of a forward-looking agent is further
-discussed in the conclusion.
+this assumption.
 
 A key notion in this setting is that of a self-defeating
-equilibrium\footnote{This notion is an adaptation of the Berk-Nash equilibrium in 
-\citet{Esponda2016} to this setting with only one agent}. A
-\emph{self-defeating equilibrium} is a belief and action pair such that
-the agent's belief about their type is misspecified and the outcome
-generated by the action is consistent with the misspecified belief. This
-means that the average outcome under the true type and the true state
-equals the average output the agent expects under the misspecified
-belief. The agent's belief is said to be \emph{stable} when this
-happens.
+equilibrium\footnote{This notion is an adaptation of the Berk-Nash equilibrium in \citet{Esponda2016} to this setting with only one agent}.
+A \emph{self-defeating equilibrium} is a belief and action pair,
+\((p, a)\), such that the agent's belief about their type is
+misspecified, and the outcome generated by the action is consistent with
+the misspecified belief. The agent's belief is said to be \emph{stable}
+when this happens and the average output is
+
+\[\bar{h}(a^*) = h(\hat{\theta}, \hat{\omega}, a)\] Where
+\(\hat{\theta}\) and \(\hat{\omega}\) is the type-state pair on which
+the misspecified belief places all probability. That is, the agents
+belief is \(p(\hat{\theta}, \hat{\omega}) = 1\) and
+\(p(\theta, \omega) = 0\) for all other values of the parameter.
 
 Within this framework, I consider two nested theories of belief
-updating: the first one is a dogmatic modeler from \citet{Heidhues2018},
-The second one is a switcher, as in \citet{Ba2023}. The dogmatic modeler
-can be seen as a switcher with an infinitely sticky initial belief so
-the two theories are nested. However, outside of the limiting case, they
-produce different predictions about the agent's behavior. I discuss each
-of them separately in what follows.
+updating: the first one is a dogmatic modeler adapted from
+\citet{Heidhues2018},The second one is a switcher, as in \citet{Ba2023}.
+The dogmatic modeler can be seen as a switcher with an infinitely sticky
+initial belief so the two theories are nested. However, outside of the
+limiting case, they produce different predictions about the agent's
+behavior. I discuss each of them separately in what follows.
 
@@
 Take the action space to be the same as the state space \(\Omega\) and
-\(\Omega =A=[\underline{a}, \infty)\).
-
-A dogmatic agent does not update their beliefs about \(\theta\),
-instead, he holds a degenerate belief that places probability on
-\(\hat{\theta}\), which is potentially misspecified. In this case, no
-matter how much information he gathers against being of type
-\(\hat{\theta}\), he will not update his beliefs about it. Any
-discrepancies between the observed outcomes and his believed type are
-incorporated using the Bayes rule to update his beliefs about
-\(\omega\). \citet{Heidhues2018} show that, under certain assumptions on
-the per-period utility,\footnote{The assumptions are that 
-$u$ is twice continuously differentiable with: (i)$u_{aa}<0$ and $u_a(\underline{a},  \theta, \omega)>0>u_a(\Bar{a}, \theta, \omega)$, 
-(ii) $u_{\theta}, u_{\omega}>0$ and (iii) $u_{a\theta}<0$ and $u_{a\omega}>0$. Where $\underline{a}$ is the
-minimal action and $\Bar{a}$ is the maximal one. 
- The direction of the derivatives is a normalization
+let \(\Omega=A:=[\underline{a}, \infty)\).
+
+A dogmatic agent is characterized by a learning model where he does not
+update their beliefs about \(\theta\), instead, he holds a degenerate
+belief that places all probability on \(\hat{\theta}\), which is
+potentially misspecified. In this case, no matter how much information
+he gathers against being of type \(\hat{\theta}\), he will not update
+his beliefs about it. Any discrepancies between the observed outcomes
+and his believed type are incorporated using the Bayes rule to update
+his beliefs about \(\omega\). \citet{Heidhues2018} show that, under
+certain assumptions on the per-period
+utility,\footnote{The assumptions are that $u$ is twice continuously differentiable with: (i)$u_{aa}<0$ and $u_a(\underline{a},  \theta, \omega)>0>u_a(\Bar{a}, \theta, \omega)$, (ii) $u_{\theta}, u_{\omega}>0$ and (iii) $u_{a\theta}<0$ and $u_{a\omega}>0$.
+Where $\underline{a}$ is the
+minimal action and $\Bar{a}$ is the maximal one. The direction of the derivatives is a normalization
 and the results would hold even when the signs are reversed.} a dogmatic
@@
 belief that they are type \(\hat{\theta}>\theta^*\). For any prior over
-\(\omega\), the agent will be disappointed by the outcome. He expected a
-gain of \(h(\hat{\theta}, \mathbb{E}(\omega), a)\) but instead observes
-\(h(\hat{\theta}, \omega^*, a)\). There are two possible sources for the
-disappointment: the first is that the realized state is lower than the
-expected state; the second source is that the agent is of type
-\(\theta^*\) and therefore, for all possible states, his gain will be
-lower than what he expected. Because the agent is dogmatic, he will not
-update his beliefs about \(\theta\) and as a consequence will attribute
-the disappointment to the state being lower than expected. He will
-continue to update in this way until he converges to a belief about
-\(\omega\) that is stable. Such a belief will explain the observed
-utility perfectly and allow the agent to rationalize his dogmatic belief
-about \(\theta\). Under the assumptions of \citet{Heidhues2018}, there
-is a unique value of \(\omega\) at which the belief is stable, I will
-refer to such value as \(\omega_\infty\). This mechanism is illustrated
-in Example 1.
+\(\omega\), the agent will be disappointed by the outcome. That is:
+\[\bar{h}(\theta^*, \omega^*, a_t^*) := \frac{1}{T}\sum_t \left[h(\theta^*, \omega^*, a_t^*)+\varepsilon_t\right]<\frac{1}{T}\sum_t \left[h(\hat{\theta}, \mathbb{E}(\omega), a_t^*)+\varepsilon_t\right]\]
+Where the right-hand-side of the inequality represents the average
+outcome that the agent expected.
+
+There are two possible sources for the disappointment: the first is that
+the realized state is lower than the expected state; the second source
+is that the agent is of type \(\theta^*\) and therefore, for all
+possible states, his gain will be lower than what he expected.
+
+Because the agent is dogmatic, he will not update his beliefs about
+\(\theta\) and as a consequence will attribute the disappointment to the
+state being lower than expected. He will continue to update in this way
+until he converges to a belief about \(\omega\) that is stable. Such a
+belief will explain the observed utility perfectly and allow the agent
+to rationalize his dogmatic belief about \(\theta\). Under the
+assumptions of \citet{Heidhues2018}, there is a unique value of
+\(\omega\) at which the belief is stable, I will refer to such value as
+\(\omega_\infty\). This mechanism is illustrated in Example 1.
 
@@
 
-Where \(h^t\) is the history of outcomes up to time \(t\) and \(\alpha\)
-is the switching
+Where \(h^t\) is the history of outcomes up to time \(t\), and
+\(\alpha\) is the switching
 threshold.\footnote{Notice that if $\alpha \to \infty$, the behavior of the switcher will be indistinguishable from that of the Dogmatic modeler. 
@@
 fits the
-data.\footnote{In a related problem \citet{Schwarstein2021} proposes a similar updating procedure which relies on the Bayesian 
-hypothesis test. However, in their model there is a sender who optimally chooses to propose a model that fits the data}
+data.\footnote{In a related problem \citet{Schwarstein2021} proposes a similar updating procedure which relies on the Bayesian hypothesis test.
+However, in their model there is a sender who optimally chooses to propose a model that fits the data}
 
@@
 and \(\omega\) by using Bayes' rule. The posterior at period t+1 about
-\(\theta\) after observing outcom \(o\) is given by: \[
+\(\theta\) after observing outcome \(o\) is given by: \[
 p_{t+1}(\theta, \omega| h^t) = \frac{p[o|\theta, \omega]p_t(\theta, \omega)}{\sum_{(\theta', \omega')}p[o|\theta', \omega']p_t(\theta', \omega')}
@@
 infinite amounts of data. This happens because, by being myopic, they do
-not internalize the tradeoff between flow payoff and learning. This can
+not internalize the trade off between flow payoff and learning. This can
 result in too little experimentation to learn their true type. An
@@
 discussed in the concluding remarks. Regardless, this approach is useful
-as a benchamrk for the other theories discussed in this paper.
+as a benchmark for the other theories discussed in this paper.
 
@@
 attribute failure to a low state to a greater degree than an unbiased
-agent would. To model the self-serving attribution bias, I take the
-approach of \citet{benjamin2019}, where the posterior odds are given by:
+agent would. This sort of biased updating is referred to as
+\emph{misattribution bias}.
+
+To model the misattribution bias, I take the approach of
+\citet{benjamin2019}, where the posterior odds are given by:
 
@@
 with
-\(c(\theta_H, \omega, o)<c(\theta_M, \omega, o)<c(\theta_L, \omega, o)\leq 1\)
+\(c(\theta_H, \omega, o)<c(\theta_M, \omega, o)<c(\theta_L, \omega, o)\)
 and
-\(c(\theta, \omega_L, o)<c(\theta, \omega_M, o)<c(\theta, \omega_H, o)\leq 1\).
+\(c(\theta, \omega_L, o)<c(\theta, \omega_M, o)<c(\theta, \omega_H, o)\).
+And where \(h_t\) is the history of signal realizations observed up to
+period t.
 
@@
 
+Define the distortion in the likelihood by
+\(\Delta_c p(h^t|\theta, \omega) = p(h^t|\theta, \omega)^{c(\theta, \omega, o_t)} - p(h^t|\theta, \omega)\).
+Notice that because \(p(h^t|\theta, \omega)<1\), if \(c(\cdot)<1\), a
+smaller exponent \(c\) implies a larger distortion upwards for fixed
+\(h^t\), and fixed parameters \(\theta\) and \(omega\). While a
+\(c(\cdot)>1\) implies a distortion downwards and it is larger when
+\(c(\cdot)\) is larger.
+
 \hypertarget{a-unifying-example}{%
@@
 In order to compare the predictions of the theories discussed above, I
-develop a unifying example that allows me to isolate the forces behind
-each of the theories. The example is a modification of the one in
-\citet{Heidhues2018} and is adapted to implementable in the lab.
+develop a unifying example where the forces behind each of the theories
+can be isolated. The example is a modified from \citet{Heidhues2018} and
+is adapted to be implementable in the lab.
 
@@
 \(\theta\)\footnote{which is potentially misspecified as in the dogmatic and switcher cases discussed above}
-and chooses a binary gamble \(e in \{e_L, e_M, e_H\}\). The agent
-observes whether the gamble is a success or a failure and gets a payoff
-of \(1\) and if it is a success; they get \(0\) otherwise.
+and chooses gamble \(e in \{e_L, e_M, e_H\}\). The agent observes
+whether the gamble is a success or a failure and gets a payoff of \(1\)
+and if it is a success; they get \(0\) otherwise.
 
@@
 behave in a laboratory
-experiment.\footnote{because the setting does not match that of @Heidhues2018, there will be situations for which the theory 
-does not provide a prediction. If such cases arise in the lab, they will not be used for the analysis. However, whether a misspecified 
-belief persists or not for the switcher, depends highly on the realized history of signals that he gets.}
+experiment.\footnote{because the setting does not match that of @Heidhues2018, there will be situations for which the theory does not provide a prediction.
+If such cases arise in the lab, they will not be used for the analysis.
+However, whether a misspecified belief persists or not for the switcher, depends highly on the realized history of signals that he gets.}
 In what follows I explain the details of how this example was
@@
 
-I recruited 78 undergraduate subjects from the CESS lab at NYU who
+I recruited 86 undergraduate subjects from the CESS lab at NYU who
 participated in an in-person experiment. Sessions lasted approximately
@@
 In this section, I outline the behavior that is predicted by each of the
-theories discussed above.
+theories discussed above. Some of the predictions are made relative to
+the Bayesian benchmark. In particular, the reaction to good and bad news
+is very informative of which model is most likely to be underlying the
+behavior. Define \emph{good news} to be a sample of signal realizations
+such that the number of successes in the sample is larger than the
+average number of successes observed so far. i.e.~if
+
+\[ \sum_i \mathbb{I}\{o_{iT}=success\} \geq \frac{1}{T} \sum_{t=0}^T\sum_i \mathbb{I}\{o_{it}=success\}\]
+where T is the current period and \(o_{t}=[o_{it}]_{i=1}^I\) is the
+sample observed at period \(t\). \emph{Bad news} are any other kind of
+signal realization. Denote the set of good news at period t by
+\(\mathcal{G}_t\) and let \(s_t\) be the number of successes in \(o_t\).
+
+Given the definition of good and bad news, the reaction of the agent to
+each kind of news is the change in their choice, conditional on the
+signal realization. Therefore, what we are interested are the
+coefficients of the following regression model, where the actions are
+those that a bayesian agent would choose:
+
+\[ \Delta a = \beta_0 + \beta_1\mathbb{I}\{o_t\in \mathcal{G}_t\} + \beta_2(s_{t} - s_{t-1}) + \beta_3\mathbb{I}\{o_t\in \mathcal{G}_t\}(s_{t} - s_{t-1})  \]
+
+Where \((s_{t} - s_{t-1})\) is the size of the surprise and \(\Delta a\)
+is the change in action. \(\beta_2\) is the reaction of the agent to bad
+news with surprise \((s_{t} - s_{t-1})\). And \(\beta_2 + \beta_3\) is
+the reaction to good news with surprise \((s_{t} - s_{t-1})\). Notice
+that for a dogmatic modeler \(\beta_2\geq0\) and
+\(\beta_2+\beta_3\geq 0\) as more successes are always indicative of a
+better state.
 
@@
 forever.}
+
+In term of the dogmatic's reagtion to good and bad news, let \(\beta^D\)
+denote the coefficients of the regression model above when the actions
+are those predicted by the dogmatic model.
+
+\textbf{Prediction 2D:} \emph{Before falling into a trap, the dogmatic
+modeler reacts more to good and bad news than the Bayesian would.
+i.e.~\(\beta_2^D>\beta_2\) and \(\beta_3^D > \beta_3\).}
 
@@
 
-\textbf{Prediction 1S:} With positive probability, the switcher will
-escape the self-defeating equilibrium and learn the true state.
+\textbf{Prediction 1S:} \emph{With positive probability, the switcher
+will escape the self-defeating equilibrium and learn the true state.}
+
+Let \(\beta^S\) be the coefficients of the regresion model when the
+actions are those taken by a switcher.
+
+\textbf{Prediction 2S:} \emph{When there is no change of paradigm, the
+switcher behaves as the dogmatic. When there is a change in paradigm,
+the reaction to good and bad news is attenuated or even in the opposite
+direction of what a Bayesian would have done. that is
+\(\beta_2^S<\beta_2\) and \(\beta_2^S + \beta_3^S<\beta_2+\beta_3\)}
 
@@
 run. This means that in order to distinguish between the two theories, I
-need to look at cases where the agent starts with a misspecified belief.
+need to look at cases where the agent starts with a misspecified belief
+and the switcher changes paradigm.
 
@@
 
+Let \(\beta^A\) be the coefficients of the regression model when the
+agent updates with misattribution bias.
+
 \textbf{Prediction 1A:} \emph{After observing a failure, the agent will
@@
 agent might not adjust their effort upwards at all, or even decrease
-their effort in response to a success.}
-
-Prediction 1A helps distinguish between the self-attribution bias and
-the dogmatic modeler. However, it does not help distinguish between the
-self-attribution bias and the switcher. In order to do so, I need to
-look at cases where the agent starts with a correctly specified belief.
-In these cases, the switcher is very unlikely to switch to a different
-belief and therefore, the behavior of the switcher will mostly change in
-the same direction as the information he receives.
-\footnote{If they get a streak of failures they are likely to 
-adjust their effort downwards and if they get a streak of successes they are likely to adjust their effort upwards.}
-Instead, the self-attribution bias will lead to a different behavior. In
-particular, even for agents who have a belief that is correctly
-specified and place a lot of weight on the correct values of \(\theta\),
-the bias will cause these agents to become overconfident after a
-sequence of successes. This force is not present in the switcher or the
-dogmatic and it is the key feature that allows me to identify a biased
-updating procedure.
+their effort in response to a success. That is \(\beta_2^A > \beta_2\)
+and \(\beta_2^A + \beta_3^A<\beta_2 + \beta_3\)}
+
+In addition to their behavior, there is an additional characteristic
+feature of misattribution bias that is not present in other models. This
+is the only model in which an agent could start off with a correct
+belief and become more overconfident. In the long-run.
 
@@
 and become overconfident.}
-
-\hypertarget{the-bayesian-1}{%
-\subsection{The Bayesian}\label{the-bayesian-1}}
-
-The Bayesian serves as the closest benchmark to a fully rational agent.
-However, as discussed above, they are still vulnerable to falling into
-self-defeating equilibria, in which case, their long-run behavior will
-be identical to that of the dogmatic modeler. The main distinguishing
-feature is that when they do fall into a self-defeating equilibrium,
-there is no bias in the direction of the misspecification that they end
-up being trapped in. In contrast, the dogmatic modeler will always be
-trapped in a misspecified belief that they started with and the
-self-attribution updater will always become overconfident.
-
-\textbf{Prediction 1B:} \emph{When an agent starts with a diffused prior
-and falls into a self-defeating equilibrium, they will be equally likely
-to fall into the underconfident trap as the overconfident trap.}
-
-\textbf{Prediction 2B:} \emph{Bayesian agents always update their effort
-choices in the same direction as the information they receive. That is,
-if they see successes, they would only increase their effort; and if
-they see failures they would only decrease their effort.}
 
@@
 last 4 rounds. I label the former as learners and the latter as
-non-learners, with learners making up 39\% of the sample.
+non-learners, with learners making up 38\% of the sample.
 
@@
 shows the share of subjects who chose a matrix consistent with their
-initial reported belief. In round 1, 71\% of the subjects chose a matrix
+initial reported belief. In round 1, 69\% of the subjects chose a matrix
 that was consistent with their initial belief. This indicates that
@@
 is true for both treatments. This indicates that even in the presence of
-traps, 44\% of subjects learn. From the share that did not learn when
-there was a trap. A remaining 21\% can be accounted for as being
+traps, 43\% of subjects learn. From the share that did not learn when
+there was a trap. A remaining 22\% can be accounted for as being
 trapped.\footnote{A subject is considered trapped when 3 out of their last 4 choices are consistent with 
@@
 
-So far I have accounted for 16\% subjects as being trapped, and 39\%
+So far I have accounted for 17\% subjects as being trapped, and 38\%
 having learned the state correctly. From the remaining 45\%, 60\% were
@@
 \hline \\[-1.8ex] 
- Good news & $-$0.12$^{**}$ & $-$0.16$^{***}$ & $-$0.05 & 0.08 & $-$0.08 \\ 
+ Good news & $-$0.11$^{**}$ & $-$0.16$^{***}$ & $-$0.04 & 0.09$^{*}$ & $-$0.08 \\ 
   & (0.05) & (0.05) & (0.05) & (0.05) & (0.05) \\ 
@@
   & & & & & \\ 
- News difference * Good news & $-$0.27$^{***}$ & $-$0.25$^{***}$ & $-$0.29$^{***}$ & $-$0.04 & $-$0.06$^{***}$ \\ 
+ News difference * Good news & $-$0.27$^{***}$ & $-$0.25$^{***}$ & $-$0.29$^{***}$ & $-$0.03 & $-$0.06$^{***}$ \\ 
   & (0.02) & (0.02) & (0.02) & (0.02) & (0.02) \\ 
   & & & & & \\ 
- Constant & 0.31$^{***}$ & 0.31$^{***}$ & 0.30$^{***}$ & $-$0.08$^{*}$ & 0.05 \\ 
+ Constant & 0.31$^{***}$ & 0.31$^{***}$ & 0.30$^{***}$ & $-$0.09$^{**}$ & 0.06 \\ 
   & (0.04) & (0.04) & (0.04) & (0.04) & (0.04) \\ 
@@
 \hline \\[-1.8ex] 
-Observations & 4,680 & 2,700 & 1,980 & 4,680 & 4,680 \\ 
+Observations & 5,160 & 2,700 & 2,460 & 5,160 & 5,160 \\ 
 R$^{2}$ & 0.04 & 0.04 & 0.04 & 0.05 & 0.06 \\ 
@@
 optimal effort as predicted by the model. More details on the simulation
-can be found in the Appendix.
+can be found in the Appendix. While the estimated parameters are all
+interior solutions with \(\hat{c} = (0.4, 0.7, 1.5)\).
 
@@
 
-\[ arg\min_j \sum_k \frac{1}{T}\sum_t{\left[e_{ikt}-\tilde{e}_{t}(\theta, \omega, j)\right]} \]
+\[ arg\min_j \sum_k \frac{1}{T}\sum_t{\left[e_{ikt}-\tilde{e}_{t}(\theta, \omega, j)\right]^2} \]
 The histogram in Figure \ref{fig:best-models} shows the distribution of
 the best fitting models in the sample. The average fit of each model is
-reported in the Appendix.
+reported in the
+Appendix.\footnote{The best fitting models are robust to different distance functions. In particular, the share of subjects best explained by misattribution bias is the same when using norm 1.}
 
@@
 
-Another bias that has been studied and suggested in the literature is
-the confirmation bias. In particular, it has been suggested that
+A different bias that has been studied and suggested in the literature
+is the confirmation bias. In particular, it has been suggested that
 subjects who are overestimate \(\theta\) in their prior, will
@@
 I further investigate possible heterogeneity in the underlying models
-being used by estimating the structural parameters of the models.
+being used by estimating the structural parameters of the models. I find
+that under the average parameters, most subjects are best explained by
+misattribution bias in both treatments. However, for the subjects for
+whom other models are a better explanation, those models have a better
+fit than the misattribution bias does for those better explained by it.
 
@@
 simulated models for parameter vector \(c\) by \(\tilde{m}(c)\) and the
-sample moments by \(m\). The estimates of the parameters arw given by
+sample moments by \(m\). The estimates of the parameters are given by
 
@@
 observed signals that exists in the sample.
+
+To determine the parameters \(\theta\) and \(\omega\) in the simulated
+individuals, I draw from the empirical distribution.
 
@@
 \hline \\[-1.8ex] 
- Net-positive signal & 0.99$^{***}$ & 0.80$^{***}$ & 1.24$^{***}$ \\ 
+ Net-positive signal & 1.01$^{***}$ & 0.80$^{***}$ & 1.22$^{***}$ \\ 
   & (0.05) & (0.05) & (0.05) \\ 
   & & & \\ 
- Signal value & 0.21$^{***}$ & 0.22$^{***}$ & 0.21$^{***}$ \\ 
+ Signal value & 0.21$^{***}$ & 0.22$^{***}$ & 0.20$^{***}$ \\ 
   & (0.02) & (0.02) & (0.02) \\ 
@@
   & & & \\ 
- Constant & $-$0.49$^{***}$ & $-$0.48$^{***}$ & $-$0.50$^{***}$ \\ 
+ Constant & $-$0.48$^{***}$ & $-$0.48$^{***}$ & $-$0.49$^{***}$ \\ 
   & (0.04) & (0.04) & (0.04) \\ 
@@
 \hline \\[-1.8ex] 
-Observations & 4,680 & 2,700 & 1,980 \\ 
+Observations & 5,160 & 2,700 & 2,460 \\ 
 R$^{2}$ & 0.05 & 0.05 & 0.05 \\ 

### 2023-10-25 Analysis/SMM.py
smm script

@@ -1,0 +1,588 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+# In[1]:
+
+
+import csv
+import numpy as np
+import matplotlib.pyplot as plt
+import pandas as pd
+import scipy as sp
+import seaborn as sns
+import random
+import scipy.stats as stats
+import statsmodels.api as sm
+import statsmodels.formula.api as smf
+
+
+# In[2]:
+
+
+# the dgp
+# matrices: matrix[0] is the low type, matrix[2] is the high type. column 0 is low omega, row 0 is low effort
+ml = np.array([[.20, .25, .40], [.07, .30, .45], [.02, .20, .50]])
+mm = np.array([[.40, .45, .65], [.30, .65, .69], [.05, .50, .80]])
+mh = np.array([[.45, .55, .75], [.35, .69, .80], [.25, .65, .98]])
+
+msc = [ml, mm, mh]
+
+# number of periods
+T = 11
+
+# number of trials
+be_trials = 10
+
+seed = 3452
+
+
+# In[3]:
+
+
+# for each of the priors, simulate the choices under each of the parameterizations of the bias from attributions
+# where the attribution is [c_positive, c_negative, c_negative, c_positive] for each of the possible 
+# combinations of c_positive and c_negative
+
+# create a matrix of the possible combinations of c_positive and c_negative
+c_H = np.array([x for x in range(10, 100, 10)])/100
+c_M = np.array([x for x in range(10, 150, 10)])/100
+c_L = np.array([x for x in range(100, 200, 10)])/100
+
+grid_good_HML = np.array(np.meshgrid(c_H, c_M, c_L)).T.reshape(-1, 3)
+
+# turn into a dataframe
+grid_good_HML = pd.DataFrame(grid_good_HML, columns = ['c_H', 'c_M', 'c_L'])
+
+# keep only values for which c_H < c_M < c_L
+grid_good_HML = grid_good_HML[grid_good_HML['c_H'] < grid_good_HML['c_M']]
+grid_good_HML = grid_good_HML[grid_good_HML['c_M'] < grid_good_HML['c_L']]
+
+#turn back into an array
+grid_good_HML = np.array(grid_good_HML)
+
+
+# In[4]:
+
+
+# the list of possible prior beliefs on theta
+priors_theta = [[1/3, 1/3, 1/3], 
+                [1/2, 1/4, 1/4],
+                [3/4, 1/8, 1/8],
[…]

### 2023-10-27 Paper/draft.Rmd
draft edits

@@
 ---
-title: "Learning with Mental Models: the case of overestimation"  
+title: |
+  | Learning with Misspecified Models: The Case of Overestimation
+  | \href{https://jimena-galindo.github.io/fileRepo/draft.pdf}{\normalsize Click Here for the Latest Version}
+
 date: '`r format(Sys.time(), "%B %d, %Y")`'
@@
 geometry: margin=2.5cm
+link-citations: true
+linkcolor: mypink
+filecolor: myblue
+citecolor: mypink
+urlcolor: mypink
 
@@
 
-A growing body of literature in economics explores how people develop incorrect beliefs 
-about fundamentals. Most of this research centers on scenarios where agents 
-passively observe the world, and incorrectly integrate the received information into their 
-beliefs.\footnote{See \citet{benjamin2019} for a review of the literature on errors of 
-probabilistic thinking.}
-However, many real-world situations cast agents as active participants in the generation of 
-information. In these cases, the information they observe is influenced by their actions and 
-subsequent behavior is in turn determined by how they incorporate the information 
-into their beliefs.
-
-As an example consider a student who needs to decide how much effort to put into 
-studying for an exam. Their decision will depend on two factors: their belief about their intrinsic 
-ability, and their belief about how difficult the exam will be. The outcome 
-they observe will be affected by how much they decide to study. Imagine that the student 
-puts in a moderate amount of effort and gets a surprisingly good grade. Did they get a good grade because 
-they are smarter than they thought? Or because the exam was easier than they had anticipated? 
-Their future exam preparation strategy will depend fundamentally on which line of reasoning they 
-take. This feedback loop is referred to as an \emph{endogenous information 
-process} and is at the center of the forces I study.
-
-To understand what the main forces at play are, I compare a set of theories that model learning in settings with 
-endogenous information, and which can rationalize the persistence of misspecified beliefs. I develop a unifying framework that nests multiple 
-theories of learning and generates testable predictions for each of them. 
-Then I cast this framework in a laboratory experiment and test the predictions to identify which 
-of the theories are consistent with the behavior I observe in the lab.
-The experiment features an agent who needs to 
-learn two parameters: one that pertains their own characteristics 
-(an \emph{ego-relevant} parameter), 
-and an exogenously determined state---in the context of the student preparing for exams, 
-the two parameters  would be their intrinsic ability and the difficulty of the exam.
-
-Misspecified beliefs about an ego-relevant parameter are often referred to as overconfidence 
-(or underconfidence) and 
-have been documented by behavioral scientists\footnote{\citet{kelley1980} 
-provides a review of the psychology literature.} and economists\footnote{See \citet{benjamin2019} 
-for a review of the literature in economics.} in a variety of settings.  @Oster2013 find that 
-subjects who are at high risk of having Huntington's disease overestimate their probability of 
-being healthy and make retirement decisions as if they were healthy. @Hoffman2020 show that workers 
-overestimate the quality of their match to their 
-current employment and are unlikely to look for other opportunities. @Camerer1999 find that 
-entrepreneurs are overconfident about the quality of their enterprise, 
-which leads to excessive entry and early exit from markets.
-
-In all of these examples,
-holding an incorrect belief about a fundamental leads to suboptimal choices with 
-potentially high costs. In spite of the abundance of evidence, the scope of the existing research 
-is limited in terms of the frameworks it considers. Most of the experimental evidence 
-documenting the bias is collected in settings where subjects are passive learners.\footnote{
-\citet{Gotte2022} and \citet{Ozyilmaz2022} are exceptions that study settings with endogenous information processes.} They 
-observe a noisy signal and report their beliefs over subsequent rounds.\footnote{\citet{Bracha2012} and 
-\citet{Mobius2022} are some examples.} Although these studies provide important insights, they are 
-not flexible enough 
-to incorporate the richer theories that have been proposed more recently. In particular, they 
-do not allow the study of endogenous learning or for learning about multiple parameters at once.\footnote{\citet{Coutts2020} 
-studies an environment with an ego-relevant parameter and an exogenous state but does not 
+A growing body of literature in economics explores how people develop incorrect beliefs about fundamentals.
+Most of this research centers on scenarios where agents passively observe the world, and incorrectly integrate the received information into their beliefs.\footnote{See \citet{benjamin2019} for a review of the literature on errors of probabilistic thinking.} However, many real-world situations cast agents as active participants in the generation of information.
+In these cases, the information they observe is influenced by their actions and subsequent behavior is in turn determined by how they incorporate the information into their beliefs.
+
+As an example, consider a student who needs to decide how much effort to put into studying for an exam.
+Their decision will depend on two factors: their belief about their intrinsic ability and their belief about how difficult the exam will be.
+The outcome they observe will be affected by how much they decide to study.
+Imagine that the student exerts a moderate amount of effort and gets a surprisingly good grade.
+Did they get a good grade because they are smarter than they thought?
+Or because the exam was easier than they had anticipated?
+Their future exam-preparation strategy will depend fundamentally on which line of reasoning they take.
+This feedback loop is referred to as an \emph{endogenous information process} and is at the center of the forces I study.
+
+To understand what main forces are at play, I compare a set of theories that model learning in settings with 
+endogenous information and can rationalize the persistence of misspecified beliefs.
+I develop a unifying framework that nests multiple theories of learning and generates testable predictions for each of them.
+Then, I cast this framework in a laboratory experiment and test the predictions to identify which of the theories are consistent with the behavior I observe in the lab.
+The experiment features an agent who needs to learn two parameters: one that pertains to their own characteristics (an \emph{ego-relevant} parameter), and an exogenously determined state.
+In the context of the student preparing for exams, the two parameters  would be their intrinsic ability and the difficulty of the exam.
+
+Misspecified beliefs about an ego-relevant parameter are often referred to as overconfidence (or underconfidence) and have been documented by behavioral scientists\footnote{\citet{kelley1980} provides a review of the psychology literature.} and economists\footnote{See \citet{benjamin2019} for a review of the literature in economics.} in a variety of settings.
+@Oster2013 find subjects who are at high risk of having Huntington's disease overestimate their probability of being healthy, and they make retirement decisions as if they were healthy.
+@Hoffman2020 show workers overestimate the quality of their match to their current employment and are unlikely to look for other opportunities.
+@Camerer1999 find entrepreneurs are overconfident about the quality of their enterprise, which leads to excessive entry and early exit from markets.
+
+In all of these examples, holding an incorrect belief about a fundamental leads to suboptimal choices with potentially high costs.
+In spite of the abundance of evidence, the scope of the existing research is limited in terms of the frameworks it considers.
+Most of the experimental evidence documenting the bias is collected in settings where subjects are passive learners.\footnote{\citet{Gotte2022} and \citet{Ozyilmaz2022} are exceptions that study settings with endogenous information processes.} They observe a noisy signal and report their beliefs over subsequent rounds.\footnote{\citet{Bracha2012} and \citet{Mobius2022} are some examples.} Although these studies provide important insights, they are not flexible enough to incorporate the richer theories that have been proposed more recently.
+In particular, they do not allow the study of endogenous learning or for learning about multiple parameters at once.\footnote{\citet{Coutts2020} studies an environment with an ego-relevant parameter and an exogenous state but does not
 incorporate the endogenous information process.}
 
-In my experiment, I move away from the standard framework of passive learning to analyze a richer set of learning mechanisms. In particular, 
-the interaction between the two parameters together with an endogenous information process 
-gives rise to three possible mechanisms that allow
-for the persistence of incorrect beliefs: the presence of learning traps, incorrect initial beliefs, and misattribution bias.
+In my experiment, I move away from the standard framework of passive learning to analyze a richer set of learning mechanisms.
+In particular, the interaction between the two parameters together with an endogenous information process gives rise to three possible mechanisms that allow for the persistence of incorrect beliefs: the presence of learning traps, incorrect initial beliefs, and misattribution bias.
 The theories that I consider incorporate different combinations of these mechanisms.
 
-When the setting features learning traps, even an agent who incorporates all information correctly, 
-may fall into learning traps as outlined by @Hestermann2021. These traps are characterized by a 
-combination of an incorrect belief and an
-optimal action which produce information that confirms the incorrect belief. 
-Once an agent falls into a trap, the belief will be stable and even with 
-a correctly specified model of learning, they will not be able to abandon their misspecified beliefs. 
-If the agent is 
-dogmatic about their initial belief, @Heidhues2018 show that they will inevitably fall into a trap
-and thus will be able to rationalize and sustain their initial misspecification belief.\footnote{\citet{Gotte2022} study the case of agents with dogmatic initial beliefs in a 
+When the setting features learning traps, even an agent who incorporates all information correctly may fall into learning traps, as outlined by @Hestermann2021.
+These traps are characterized by a combination of an incorrect belief and an optimal action that produce information that confirms the incorrect belief.
+Once an agent falls into a trap, the belief will be stable and even with a correctly specified model of learning, they will not be able to abandon their misspecified beliefs.
+If the agent is dogmatic about their initial belief, @Heidhues2018 show they will inevitably fall into a trap and thus will be able to rationalize and sustain their initial misspecification belief.\footnote{\citet{Gotte2022} study the case of agents with dogmatic initial beliefs in a
 laboratory experiment.}
 
-@Ba2023 moves away from dogmatism and endows the agents with a mechanism through which 
-they can abandon incorrect beliefs. This allows them to avoid falling into learning traps. 
-To do so agents perform Bayesian hypothesis tests that evaluate which is the more 
-likely parameter out of two possibilities. By doing this, she characterizes the set of situations 
-in which, even agents who consider alternative paradigms, may become trapped.\footnote{A 
-similar mechanism is proposed by \citet{Schwarstein2021} in a setting with persuasion.}
-
-Lastly, misattribution bias is the more classical explanation and has been widely studied in 
-behavioral science.\footnote{See \citet{kelley1980} for a review.}
-Agents who suffer from misattribution bias will attribute successes to their own ability---the 
-ego-relevant parameter---and failures to bad luck---the state. 
-Under this model of learning, even an agent who initially has a correct initial 
-belief may become overconfident if they observe a sequence of successes. In this case, 
-the main driver of the bias is not an initial misspecification or the presence of learning traps, 
-it is the updating procedure itself.\footnote{A more general framework that can be used to model 
-this bias has also been proposed by \citet{Brunnermeier2005} and empirically studied by \citet{Bracha2012}.}
-
-These theories provide the main building blocks for a simplified framework that can be directly 
-implemented in a laboratory experiment.
+@Ba2023 moves away from dogmatism and endows the agents with a mechanism through which they can abandon incorrect beliefs.
+This allows them to avoid falling into learning traps.
+To do so, agents perform Bayesian hypothesis tests that evaluate which of two possible parameters is more likely.
+By doing so, she characterizes the set of situations in which even agents who consider alternative paradigms may become trapped.\footnote{A similar mechanism is proposed by \citet{Schwarstein2021} in a setting with persuasion.}
+
+Lastly, misattribution bias is the more classical explanation and has been widely studied in behavioral science.\footnote{See \citet{kelley1980} for a review.} Agents who suffer from misattribution bias will attribute successes to their own ability---the
+ego-relevant parameter---and their failures to bad luck---the state.
+Under this model of learning, even an agent who initially has a correct initial belief may become overconfident if they observe a sequence of successes.
+In this case, the main driver of the bias is not an initial misspecification or the presence of learning traps; it is the updating procedure itself.\footnote{A more general framework that can be used to model this bias has also been proposed by \citet{Brunnermeier2005} and empirically studied by \citet{Bracha2012}.}
+
+These theories provide the main building blocks for a simplified framework that can be directly implemented in a laboratory experiment.
 In the experiment subjects make choices and receive feedback that depends on their own ability, an exogenous parameter and the choice they made.
 I track their choices as well as their beliefs about their own ability.
-The goal is to
-identify which of the 3 forces---the presence of learning traps, misspecified initial beliefs, or misatribution 
-bias---better explains the observed behavior. To determine the fit of the models, I compare the behavior
-predicted by each theory to the benchmark given by the fully Bayesian updating procedure.
-
-I also study whether the learning mechanism is inherently linked to the ego-relevance of the parameters 
-or if it is a more general phenomenon. I vary the degree of ego-relevance by introducing a 
-treatment in which subjects learn about the ability of another participant.
-In this treatment, the participants know only the gender and nationality of the other, and thus can 
-induce stereotypes---a different type of misspecification.  
-If correct learning about the parameters happens at higher rates in the stereotype treatment, 
-it would suggest that the 
-bias is intrinsically linked to the ego-relevance of the parameter. In contrast, if similar 
-biased behavior arises in both treatments, it is more likely that the main driver of these types 
-of misspecified beliefs is the updating procedure itself or the endogenous information process.
-
-Although some agents do fall into learning traps, I find that the behavior of most 
-subjects is better explained by misattribution bias: good news are treated as signaling high ability, while bad news are attributed to a low state. I also find that misattribution is 
-no more prevalent in the ego-relevant than in the stereotype condition. This suggests 
-that the main driver of the misspecification is the updating procedure; however, the underlying 
-mechanism by which the bias is generated may be 
-different in both treatments: While in the ego-relevant condition subjects prefer to hold themselves in high esteem, in the stereotype condition
-updating seems to be driven by some sort of bias overcorrection---when subjects realize that they underestimated 
-the ability of another participant based on their gender and nationality, they compensate by
-overestimating their ability.
+The goal is to identify which of the three forces---the presence of learning traps, misspecified initial beliefs, or misatribution bias---better explains the observed behavior.
+To determine the fit of the models, I compare the behavior predicted by each theory with the benchmark given by the fully-Bayesian updating procedure.
+
+I also study whether the learning mechanism is inherently linked to the ego-relevance of the parameters or if it is a more general phenomenon.
+I vary the degree of ego-relevance by introducing a treatment in which subjects learn about the ability of another participant.
+In this treatment, the participants know only the gender and nationality of the other, and thus can induce stereotypes---a different type of misspecification.
+If correct learning about the parameters happens at higher rates in the stereotype treatment, this finding would suggest the bias is intrinsically linked to the ego-relevance of the parameter.
+By contrast, if similar biased behavior arises in both treatments,  the main driver of these types of misspecified beliefs is more likely to be the updating procedure itself or the endogenous information process.
+
+Although some agents do fall into learning traps, I find the behavior of most subjects is better explained by misattribution bias: good news are treated as signaling high ability, whereas bad news are attributed to a low state.
+I also find misattribution is no more prevalent in the ego-relevant than in the stereotype condition.
+This finding suggests the main driver of the misspecification is the updating procedure; however, the underlying mechanism by which the bias is generated may be different in both treatments.
+Whereas subjects in the ego-relevant condition prefer to hold themselves in high esteem, in the stereotype condition, updating seems to be driven by some sort of bias overcorrection---when subjects realize they underestimated
+the ability of another participant based on their gender and nationality, they compensate by overestimating their ability.
 
 Finally, I estimate the structural parameters of the models to study model-heterogeneity in the sample.
-I find that even at an individual level the behavior is better explained by a general model of 
-misattribution bias for most
-subjects. There is a smaller group of subjects that can be better explained through dogmatic beliefs
-and hypothesis testing and none of them behave in line with the fully Bayesian benchmark.
-
-In what follows I first discuss the theoretical framework and the predictions of each of the theories.
-Then I introduce a unifying example and my hypotheses. In section 4 I describe the experimental
-design and in section 5 I present the data and the results. Section 6 outlines the estimation of the parameters
-and the model fit analysis.
+I find that even at an individual level, the behavior is better explained by an average model of misattribution bias for most subjects.
+A smaller group of subjects exists that can be better explained through dogmatic beliefs and hypothesis testing, and very few of them behave in line with the fully Bayesian benchmark.
+
+In what follows, I first discuss the theoretical framework and the predictions of each of the theories.
+Then, I introduce a unifying example and my hypotheses.
+In section 4, I describe the experimental design, and in section 5, I present the data and the results.
+Section 6 outlines the estimation of the parameters and the model fit analysis.
 
@@
 
-The theories that I consider make predictions in two distinct frameworks. I first detail each theory 
+The theories I consider make predictions in two distinct frameworks. I first detail each theory 
 within their original framework and then develop a unifying example that allows me to
-compare the predictions of all of them. In framework 1 I consider a setting in which the an agent observes
+compare the predictions of all of them. In framework 1, I consider a setting in which an agent observes
 a continuous output and infers the underlying parameters. In framework 2, the agent observes a binary 
-outcome and infers the underlying probability of success, which is related to the parameters. In both frameworks, I consider two nested theories of learning.
+outcome and infers the underlying probability of success, which is related to the parameters.
 
@@
 
-An agent is of type $\theta \in \Theta$ and faces an unknown exogenous state $\omega$ drawn from some 
+An agent of type $\theta \in \Theta$ faces an unknown exogenous state $\omega$ drawn from 
 density $f$ over $\Omega$. The agent knows the 
-distribution of $\omega$ but not its realized value. His belief about the state, 
-$p_0(\omega)$, coincide with the true distribution, $f$; and his belief about the type is $p_0(\theta)$. 
+distribution of $\omega$ but not its realized value. His belief about the state $\omega\in\Omega$ is 
+$p_0(\omega)$ and coincides with the true distribution, $f$. His belief about the type 
+$\theta\in\Theta$ is $p_0(\theta)$. 
 Let the agent's true type be $\theta^{*}$,  and the realized state be $\omega^{*}$.
@@
 The outcome is a function of the agent's type, the state, and
-the action. In particular $h = h(\theta^*, \omega^*, a) + \varepsilon$ with $h(\cdot)$ increasing in both $\theta^*$ and $\omega^*$, 
+the action. In particular, $h = h(\theta^*, \omega^*, a) + \varepsilon$ with $h(\cdot)$ increasing in both $\theta^*$ and $\omega^*$, 
 and such that conditional on a pair of parameters $(\theta, \omega)$, there is a unique optimal action. 
-Additionally, $\varepsilon\sim N(0, \sigma)$ is noise in the output.
+Additionally, $\varepsilon\sim N(0, \sigma)$ is noise in the outcome.
 
 After observing the outcome, the agent updates his beliefs about $\theta$ and $\omega$ using some algorithm and moves on to the next period.
-He repeats this process infinitely many times. I make the simplifying assumption that the agent is myopic and chooses the action 
-that maximizes the payoff in each period.
-This assumption simplifies the analysis and plays a role in whether an agent who updates their beliefs using Bayes rule would learn the truth or not, however, for the main theory discussed in this section, the results hold even when relaxing this assumption.
+He repeats this process infinitely many times.
+I make the simplifying assumption that the agent is myopic and chooses the action that maximizes the payoff in each period.
+This assumption simplifies the analysis and plays a role in whether an agent who updates his beliefs using Bayes rule would learn the truth or not, however, for the main theory discussed in this section, the results hold even when relaxing this assumption as shown in @Heidhues2018.
 
 A key notion in this setting is that of a self-defeating equilibrium\footnote{This notion is an adaptation of the Berk-Nash equilibrium in \citet{Esponda2016} to this setting with only one agent}. 
-A \emph{self-defeating equilibrium} is a belief and action pair, $(p, a)$, such that the agent's belief about their type is misspecified, and the outcome generated by the action is consistent with the misspecified belief.
-The agent's belief is said to be \emph{stable} when this happens and the average output is
-
-$$\bar{h}(a^*) = h(\hat{\theta}, \hat{\omega}, a)$$
-Where $\hat{\theta}$ and $\hat{\omega}$ is the type-state pair on which the misspecified belief places all probability.
+A \emph{self-defeating equilibrium} is a belief and action pair, $(p, a^*)$, such that the agent's belief about his type is misspecified, and the outcome generated by the action is consistent with the misspecified belief.
+The agent's belief is said to be \emph{stable} when this happens.
+
+Given the choice that sustains the self-defeating equilibrium, they observe the \emph{average output} given by
+$$\bar{h}(a^*) =\frac{1}{T}\sum_t \left[h(\hat{\theta}, \hat{\omega}, a^*)+\varepsilon_t\right]$$ 
+where $\hat{\theta}$ and $\hat{\omega}$ is the type-state pair on which the misspecified belief places all probability.
 That is, the agents belief is $p(\hat{\theta}, \hat{\omega}) = 1$ and $p(\theta, \omega) = 0$ for all other values of the parameter.
 
-Within this framework, I consider two nested theories of belief updating: the first one is a dogmatic modeler adapted from @Heidhues2018,The second one is a switcher, as in @Ba2023.
+Within this framework, I consider two nested theories of belief updating: the first one is a dogmatic modeler adapted from @Heidhues2018.
+The second one is a switcher, as in @Ba2023.
 The dogmatic modeler can be seen as a switcher with an infinitely sticky initial belief so the two theories are nested.
@@
 
-A dogmatic agent is characterized by a learning model where he does not update their beliefs about $\theta$, instead, he holds a degenerate belief that places all probability on $\hat{\theta}$, which is potentially misspecified.
-In this case, no matter how much information he gathers against being of type $\hat{\theta}$, he will not update his beliefs about it. 
+A dogmatic agent is characterized by a learning model where he does not update his beliefs about $\theta$ and instead, holds a degenerate belief that places all probability on $\hat{\theta}$, which is potentially misspecified.
+In this case, no matter how much evidence he gathers against being of type $\hat{\theta}$, he will not update the beliefs about his type. 
 Any discrepancies between the observed outcomes and his believed type are incorporated using the Bayes rule to update his beliefs about $\omega$.
@@
 and the results would hold even when the signs are reversed.} a dogmatic modeler will inevitably fall into a self-defeating equilibrium.
-The equilibrium will be such that the outcomes they observe reinforce their belief on $\omega$ in such a way that as $t\to\infty$ the agent will be sure that the state is some $\omega^{'}$ consistent with their believed type and the observed data.
-In other words, they will be in a self-defeating equilibrium with a stable belief that places probability one on the incorrect parameters $(\hat{\theta}, \omega_{\infty})$
-
-The mechanism by which the dogmatic agent falls into the self-defeating equilibrium is the following: Suppose the agent holds the misspecified belief that they are type $\hat{\theta}>\theta^*$.
+The equilibrium will be such that the outcomes he observes reinforce his belief on $\omega$ in such a way that as $t\to\infty$ the agent will be sure that the state is some $\omega^{'}$ consistent with their believed type and the observed data.
+In other words, he will be in a self-defeating equilibrium with a stable belief that places probability one on the incorrect parameters $(\hat{\theta}, \omega_{\infty})$
+
+The mechanism by which the dogmatic agent falls into the self-defeating equilibrium is the following: suppose the agent holds the dogmatic and misspecified belief that they are type $\hat{\theta}>\theta^*$.
 For any prior over $\omega$, the agent will be disappointed by the outcome.
 That is:
-$$\bar{h}(\theta^*, \omega^*, a_t^*) := \frac{1}{T}\sum_t \left[h(\theta^*, \omega^*, a_t^*)+\varepsilon_t\right]<\frac{1}{T}\sum_t \left[h(\hat{\theta}, \mathbb{E}(\omega), a_t^*)+\varepsilon_t\right]$$
-Where the right-hand-side of the inequality represents the average outcome that the agent expected.
-
-There are two possible sources for the disappointment: the first is that the realized state is lower than the expected state; the second source is that the agent is of type $\theta^*$ and therefore, for all possible states, his gain will be lower than what he expected.
-
-Because the agent is dogmatic, he will not update his beliefs about $\theta$ and as a consequence will attribute the disappointment to the state being lower than expected.
+$$\frac{1}{T}\sum_t \left[{h}(\theta^*, \omega^*, a_t^*)+\varepsilon_t\right] <\mathbb{E_w} \left[h(\hat{\theta}, \omega, a_t^*)\right]$$
+where the right-hand-side of the inequality represents the average outcome that the agent expected given his beliefs about their type and the state. The left hand side is what they observed.
+
+There are two possible sources for the disappointment: the first is that the realized state $\omega^*$ is lower than what the agent expected, $\mathbb{E}[\omega]$; the second source is that the agent is of type $\theta^*$ and therefore, for all possible states, his gain will be lower than what he expected when the variance of the error term is low or $T$ is large.
+That is, when $\frac{1}{T}\sum_t\varepsilon_t$ is close to zero.
+
+Because the agent is dogmatic, he will not update his beliefs about $\theta$ and, as a consequence, will attribute the disappointment to the state being lower than expected.
 He will continue to update in this way until he converges to a belief about $\omega$ that is stable.
@@
 **Example 1: ** 
-_Set $A = \Omega=[\underline{a}, \infty)$ and consider a student with intrinsic ability $\theta^*\geq 0$ who faces a grading procedure 
-$\omega^*$ that is unknown to them. 
-The student knows that a higher $\omega^*$ is more likely to yield a higher grade. In particular, she knows the grade is given by 
-$(\theta^*+a)\omega^*$._
-
-_The student must choose an effort level $a$, which determines her grade. For whatever the chosen effort level, 
-the student must pay a cost $c(a) = \frac{1}{2}a^2$ and observes a grade of $(\theta^*+a)\omega^*$. She repeats 
-this process for infinitely many periods. 
-Assume also that the student's prior is such that $\mathbb{E}[\omega]= \omega^*$ and she is dogmatic 
-about being of 
-type $\hat{\theta}>\theta^*$.\footnote{The example is illustrated for an overconfident student but 
-the results are symmetric for a dogmatic student who initially 
-places probability one on some $\tilde{\theta}<\theta^*$.}
-Therefore, the student's payoff in period $t$ is given by _
+_Set $A = \Omega=[\underline{a}, \infty)$ and consider a student (she) with intrinsic ability $\theta^*\geq 0$ who faces a grading procedure $\omega^*$ that is unknown to her.
+The student knows that a higher $\omega^*$ is more likely to yield a higher grade.
+In particular, she knows the grade is given by $(\theta^*+a)\omega^*$._
+
+_The student must choose an effort level $a$, which determines her grade.
+For whatever the chosen effort level, the student must pay a cost $c(a) = \frac{1}{2}a^2$.
+She repeats this process for infinitely many periods.
+Assume also that the student's prior is such that $\mathbb{E}[\omega]= \omega^*$ and she is dogmatic about being of type $\hat{\theta}>\theta^*$.\footnote{The example is illustrated for an overconfident student but the results are symmetric for a dogmatic student who initially places probability one on some $\tilde{\theta}<\theta^*$.} Therefore, the student's payoff in period $t$ is given by _
 
@@
 
-_Under this specification, the myopic optimal effort level is $a_t^* = \omega^*$. 
-Because the student does not know $\omega^*$,
-he will choose $a_t = \mathbb{E}_t(\omega)$ where the expectation is taken with respect to the 
-student's belief at the beginning of
-period $t$. If she does not revise his effort choice for $k$ periods, she will receive 
-an average utility of 
-$(\theta^*+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}$ but he was expecting an average utility of 
-$(\hat{\theta}+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}$. In response, she will apply Bayes 
-rule to update his beliefs about
-$\omega$ to get the posterior belief with 
-$\mathbb{E}_{t+k}[\omega] = \frac{(\theta^{*} + \omega^{*})\omega^{*}}{\hat{\theta} + \omega^{*}}$
-which is lower than the initial belief. This will cause the student to choose a lower effort at $t+k$. As a result, she will again
-receive an average utility that is lower than what he expected which will cause her belief to drift further down. This process will
-continue until the average utility equals her expected utility under the dogmatic belief that assigns probability 1 to $\hat{\theta}$. 
-At that point, the student will have reached a self-defeating equilibrium and she will continue to choose sub-optimal effort forever. _
+_Under this specification, the myopic optimal effort level is $a_t^* = \omega^*$. Because the student does not know $\omega^*$,
+she will choose $a_t = \mathbb{E}_t(\omega)$ where the expectation is taken with respect to the student's belief at the beginning of
+period $t$.
+If she does not revise his effort choice for $k$ periods, she will receive an average utility of $(\theta^*+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}$ but was expecting an average utility of $(\hat{\theta}+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}$.
+In response, she will apply Bayes rule to update his beliefs about $\omega$ to get the posterior belief with $\mathbb{E}_{t+k}[\omega] = \frac{(\theta^{*} + \omega^{*})\omega^{*}}{\hat{\theta} + \omega^{*}}$ which is lower than the initial belief.
+This will cause the student to choose a lower effort at $t+k$.
+As a result, she will again receive an average utility that is lower than what he expected which will cause her belief to drift further down.
+This process will continue until the average utility equals her expected utility under the dogmatic belief that assigns probability 1 to $\hat{\theta}$.
+At that point, the student will have reached a self-defeating equilibrium and she will continue to choose sub-optimal effort forever._
 
 Although the model of a dogmatic modeler rationalizes the prevalence of overconfident (underconfident) beliefs, the
-assumption that the agent has a degenerate belief and no mechanism through which he can update such 
-belief is very restrictive. An
-alternative approach is proposed by @Ba2023. She proposes an extension of the dogmatic agent who 
-is able to swithch from one dogmatic 
+assumption that the agent has a degenerate belief and no mechanism through which he can update such belief is very restrictive.
+An alternative approach is proposed by @Ba2023.
+She proposes an extension of the dogmatic agent who is able to swithch from one dogmatic
 belief to another. By doing so, the agent can avoid the self-defeating equilibria and end up being dogmatic and correctly specified.
@@
 In particular, for an agent that starts with a dogmatic belief that they are of type $\hat{\theta}$ but is willing to consider
-the alternative explanation that they are of type $\tilde{\theta}$, the agent will switch to the alternative if:
+the alternative explanation that they are of type $\tilde{\theta}$, the agent will switch to the alternative if
 
@@
 
-Where $h^t$ is the history of outcomes up to time $t$, and $\alpha$ is the switching threshold.\footnote{Notice that if $\alpha \to \infty$, the behavior of the switcher will be indistinguishable from that of the Dogmatic modeler.
+where $h^t$ is the history of outcomes up to time $t$ and $\alpha$ is the switching threshold.\footnote{Notice that if $\alpha \to \infty$, the behavior of the switcher will be indistinguishable from that of the Dogmatic modeler.
 In this sense, the switcher is a generalization of the dogmatic type.} By keeping track of the 
@@
 By allowing the agent to keep track of the likelihoods and switching to an alternative type, the switcher can avoid the 
-self-confirming equilibria. However, if the prior belief on $omega$ is sufficiently tight around
+self-confirming equilibria. However, if the prior belief on $\omega$ is sufficiently tight around
 a self-defeating equilibrium, the switcher might look identical to the dogmatic even in a case where $\alpha$ is not too large.
 This happens because under the agent's prior, the likelihood ratio is unlikely to grow as fast as it is needed to escape 
-the self-defeating equilibrium. In such situations, we say that the misspecified belief is persistent.
+the self-defeating equilibrium. In such situations, we say that the misspecified belief about $\theta$ is \emph{persistent}.
 
@@
 
-As in framework 1, the agent is of some type $\theta^* \in \Theta$ and the state is $\omega \sim F(\Omega)$.
+As in framework 1, the agent is of some type $\theta^* \in \Theta$ and the state is $\omega$ is distributed according to  $F(\Omega)$.
 In this case, the agent chooses an action $a\in A$ and observes a binary outcome that is either a success or a failure.
@@
 In addition, the probability of success is such that for each state, there is a unique optimal action that maximizes the agent's expected payoff.
-Therefore, the probability of success can be seen as a monotone transformation of the utility from Framework 1.
-
-I focus on two nested theories that have been widely studied within this framework: Full Bayesian updating and self-serving attribution bias.
-I explain each of these classical models of belief updating in what follows
+Therefore, the probability of success can be seen as an order-preserving transformation of the utility from Framework 1.
+
+I focus on two nested theories that have been widely studied within this framework: full Bayesian updating and self-serving attribution bias.
+I explain each of these classical models of belief updating in what follows.
 
@@
 A Bayesian agent simultaneously updates their beliefs about $\theta$ and $\omega$ by using Bayes' rule. 
-The posterior at period t+1 about $\theta$ after observing outcome $o$ is given by:
+The posterior at period $t+1$ about $\theta$ after observing outcome $o$ is given by:
 $$
@@
 $$
-
-Where $p_{t}$ is the belief at the start of period $t+1$ and includes all the information gathered so far.
-
-Bayesian agents choose the effort level that maximizes their expected flow payoff by taking expectations over
-their prior beliefs about $\theta$ and $\omega$. Since agents are myopic, even though all the parameters 
-could be identified with enough variation in choices, there will be instances in which the Bayesian will not
-learn even with infinite amounts of data. This happens because, by being myopic, they do not internalize 
-the trade off between flow payoff and learning.
+where $p_{t}$ is the belief at the start of period $t+1$ and includes all the information gathered so far.
+
+Bayesian agents choose the effort level that maximizes their expected flow payoff by taking expectations over $(\theta, \omega)$ using their beliefs at period $t$.
+Since agents are myopic, there will be instances in which the Bayesian will not learn even with infinite amounts of data.
+This happens because myopic agents do not internalize the trade-off between flow payoff and learning.
 This can result in too little experimentation to learn their true type.
-An alternative to this approach is given by @Hestermann2021 and is discussed in the concluding remarks.
+An approach in which agents intentionally introduce variation in their choices is given by @Hestermann2021 and is discussed in the concluding remarks.
 Regardless, this approach is useful as a benchmark for the other theories discussed in this paper.
 
-Also notice that if a fully Bayesian agent has a dogmatic prior, they will never update their beliefs about the parameter that they are dogmatic about.
+Notice that if a fully Bayesian agent has a dogmatic prior, they will never update their beliefs about the parameter that they are dogmatic about.
 This will imply that they are prone to the same types of errors as the dogmatic modeler in framework 1.
@@
 
-A Self-Serving Bayesian is an agent who uses a biased version of Bayes rule to update their beliefs.
-They will update their beliefs about the state $\omega$ and his type $\theta$ simultaneously by over-attributing successes to a high value of $\theta$ and under-estimating the role of higher $\omega$.
+A Self-Serving Bayesian is an agent who uses a biased version of Bayes rule to update his beliefs.
+He will update his beliefs about the state $\omega$ and his type $\theta$ simultaneously by over-attributing successes to a high value of $\theta$ and under-estimating the role of higher $\omega$.
 Similarly, he will attribute failure to a low state to a greater degree than an unbiased agent would.
+For instance, if the student from the example attributed a high grade to being of high ability while attributing low grades to a harsh grading system.
 This sort of biased updating is referred to as \emph{misattribution bias}.
@@
 To model the misattribution bias, I take the approach of @benjamin2019, where the posterior odds are given by:
-
 $$
@@
 $$
-
-with $c(\theta_H, \omega, o)<c(\theta_M, \omega, o)<c(\theta_L, \omega, o)$
-and $c(\theta, \omega_L, o)<c(\theta, \omega_M, o)<c(\theta, \omega_H, o)$. And where $h_t$ is the history of signal realizations observed up to period t.
-
-This formulation of the bias means that the agent will over-attribute successes to a high type and under-attribute them to a low type Whereas they will over-attribute failures to a low state and under-attribute them to a high state.
-The bias is introduced by distorting the perceived likelihood that the signal was generated by either high values of $\theta$ when it is a success, or by low values of $\omega$ when it is a failure.
+with $c(\theta, \omega, o)$ decreasing in $\theta$ and increasing in $\omega$. $h_t$ is the history of signal realizations observed up to period $t$.
+
+This formulation allows the bias to be introduced by distorting the perceived likelihood that the signal was generated by either high values of $\theta$ when it is a success, or by low values of $\omega$ when it is a failure.
 The parameter $c$ determines the degree of bias and imposes enough restrictions to ensure that the model is still falsifiable.
@@
 Define the distortion in the likelihood by $\Delta_c p(h^t|\theta, \omega) = p(h^t|\theta, \omega)^{c(\theta, \omega, o_t)} - p(h^t|\theta, \omega)$.
-Notice that because $p(h^t|\theta, \omega)<1$, if $c(\cdot)<1$, a smaller exponent $c$ implies a larger distortion upwards for fixed $h^t$, and fixed parameters $\theta$ and $omega$.
-While a $c(\cdot)>1$ implies a distortion downwards and it is larger when $c(\cdot)$ is larger.
+Notice that because $p(h^t|\theta, \omega)<1$, if $c(\cdot)<1$, a smaller exponent $c$ implies a larger distortion upward for a fixed $h^t$, and fixed parameters $\theta$ and $\omega$.
+While a $c(\cdot)>1$ implies a distortion downward and it is larger when $c(\cdot)$ is larger.
 
@@
 In order to compare the predictions of the theories discussed above, I develop a unifying example where the forces behind each of the theories can be isolated.
-The example is a modified from @Heidhues2018 and is adapted to be implementable in the lab.
+The example is modified from @Heidhues2018 and is adapted to be implementable in the lab.
 
@@
 $\theta$\footnote{which is potentially misspecified as in the dogmatic and switcher cases discussed above} 
-and chooses gamble $e in \{e_L, e_M, e_H\}$. The agent observes whether the gamble is a success or a failure and 
-gets a payoff of $1$ and if it is a success; they get $0$ otherwise.
-
-The probability of success is increasing in both $\theta$ and $\omega$ and is fully described by the Table \ref{tab:DGP}
+and chooses gamble $e \in \{e_L, e_M, e_H\}$. The agent observes whether the gamble is a success or a failure and 
+gets a payoff of $1$ if it is a success; they get $0$ otherwise.
+
+The probability of success is increasing in both $\theta$ and $\omega$ and is fully described in Table \ref{tab:DGP}
 
@@
 
-\caption{Probability of success for each type, gamble and effort level}
+\caption{Probability of success for each type $\theta$, gamble $\omega$, and effort level $e$}
 \label{tab:DGP}
@@
 
-Conditional on a type, the agent's flow payoff is maximized by choosing the gamble that 
+For each type, the agent's flow payoff is maximized by choosing the gamble that 
 matches the state. For example, if the value of $\omega$ is $\omega_H$, the agent's flow payoff is maximized by 
@@
 Notice that both $\theta$ and $\omega$ can be identified from the outcomes if enough variation in the effort choices exists.
-This can be seen by confirming that there is no pair of $\theta$ and $\omega$ such that the probability of success is the same for all effort choices.
+This can be seen by confirming that there are no two pairs of $\theta$ and $\omega$ such that produce the same the probability of success for all effort choices.
 Thus, by changing the effort choice, the agent can learn both their type and the state if they observe enough outcomes.
@@
 chooses an effort level that, under the true $\theta$, yields a frequency of success that is consistent with the agent's 
-misspecified belief. That is $P[\text{sucess}|\theta^*, e^*] = P[\text{sucess}|\hat{\theta}, e^*]$ where $e^*$ is the agent's 
-myopic optimal choice.
+misspecified belief. That is $P[\text{sucess}|\theta^*, \omega^*, e^*] = P[\text{sucess}|\hat{\theta}, \hat{\omega}, e^*]$ where $e^*$ is the agent's myopic optimal choice.
 
 In the data-generating process described above, there are five such equilibria.
-For example, if the agent is of type $\theta_M$ but mistakenly believes that he is of type $\hat{\theta}=\theta_H$ and the and $\omega^* = \omega_M$, when the effort chosen is $e_L$, the agent will observe a success with 45% chance.
+For example, if the agent is of type $\theta_M$ but mistakenly believes that he is of type $\hat{\theta}=\theta_H$ and that $\omega^* = \omega_M$, when the effort chosen is $e_L$, the agent will observe a success with 45% chance.
 Because the agent dogmatically believes that their type is high, they will erroneously conclude that the rate is $\omega_L$.
-Under this belief, the optimal action is $e_L$ which will continue to generate successes with $45%$ probability, further reinforcing the incorrect belief.
+Under this belief, the optimal action is $e_L$ which will continue to generate successes with a $45%$ probability, further reinforcing the incorrect belief.
 By doing so, the agent forgoes the payoff from gamble $e_M$ which would yield a success with $65\%$ chance.
 
-By including self-confirming equilibria, the example captures the forces from each of the updating mechanisms discussed in the 
+By including self-defeating equilibria, the example captures the forces from each of the updating mechanisms discussed in the 
 previous section and allows for the comparison of the main forces behind the theories.
+This is because the self-defeating equilibria in a discretized setting acptures the main forces from the dogmatic and Switcher models.
+Furthermore, the data generating process has been designed to satisfy the main assumptions of both frameworks.
 For realizations of $(\theta, \omega)$ for which there are self-confirming equilibria, the dogmatic agent will fall into the trap whereas the switcher will be able to escape it.
 Similarly, an agent with self-attribution bias will update their beliefs differently from an unbiased Bayesian, leading them to choose different gambles.
-I exploit such cases in order to test which model is a better fit for how subjects behave in a laboratory experiment.\footnote{because the setting does not match that of @Heidhues2018, there will be situations for which the theory does not provide a prediction.
-If such cases arise in the lab, they will not be used for the analysis.
-However, whether a misspecified belief persists or not for the switcher, depends highly on the realized history of signals that he gets.} In what follows I explain the details of how this example was implemented in the lab.
+I exploit such cases in order to test which model is a better fit for how subjects behave in a laboratory experiment.
+In what follows I explain the details of how this example was implemented in the lab and the predictions that each model makes.
 
@@
 I recruited `r length(unique(updates$code))` undergraduate subjects from the CESS lab at NYU who participated in an in-person experiment.
-Sessions lasted approximately 
-45 minutes and subjects earned an average payment of $\$22.6$. The experiment was programmed using oTree [@otree].
-
-The experiment consisted of 2 treatments: the \emph{ego-relevant} condition and the \emph{stereotype} condition. Subjects participated 
-in only one of the treatments. All subjects within a session participated in the same treatment and the 
-first 4 treatments were assigned the ego-relevant condition; the rest were assigned to the stereotype treatment. 
-The tasks were identical across treatments, 
-except for parameter $\theta$. In the ego-relevant condition $\theta$ is the subject's own performance in a quiz, while in the 
-stereotype condition, it is the performance of a randomly selected subject from another session.
-
-The experiment had 3 parts. In Part 1 subjects had 2 minutes to answer as many multiple-choice questions as they could from a 
-20-question quiz. They did this for quizzes on 6 different topics. The topics were: Math, Verbal 
-Reasoning, Pop-culture and Art, Science and Technology, US Geography, and Sports and Video Games. 
+Sessions lasted approximately 45 minutes and subjects earned an average payment of $\$22.6$.
+The experiment was programmed using oTree [@otree].
+
+The experiment consisted of 2 treatments: the \emph{ego-relevant} condition and the \emph{stereotype} condition.
+Subjects participated in only one of the treatments.
+All subjects within a session participated in the same treatment and the first 4 sessions were assigned the ego-relevant condition; the rest were assigned to the stereotype treatment.
+The tasks were identical across treatments.
+In the ego-relevant condition, $\theta$ is the subject's own performance in a quiz.
+In the stereotype condition, it is the performance of a randomly selected subject from another session.
+
+The experiment had three parts.
+In Part 1 subjects had two minutes to answer as many multiple-choice questions as they could from a 20-question quiz.
+They did this for quizzes on 6 different topics.
+The topics were: Math, Verbal Reasoning, Pop-culture and Art, Science and Technology, US Geography, and Sports and Video Games.
 In this part, they did not know how many questions were available and they were given no feedback.
@@
 After taking all 6 quizzes, they proceeded to part 2 where they were asked to guess their score on each of them. 
-In the stereotype 
-treatment they were additionally asked to guess the score of a randomly drawn participant from a previous session. 
+In the stereotype treatment, they were additionally asked to guess the score of a randomly drawn participant from a previous session. 
 All they knew about the other participant was their gender identity and whether they were US nationals or not.
@@
 High-Score (16 or more). Each of the score categories corresponded to $\theta_L$, $\theta_M$, and $\theta_H$ respectively. 
-They were also asked to say how confident they felt about their choices. They had 4 possible answers: "it was a random guess", 
-"there is another equally likely score", "I am pretty sure", "I am completely sure". 
-These 4 answers are mapped to priors that place probabilities 
-.33, .50, .75, and 1 to the chosen type. The remaining probability is split equally among the other two types. 
-Questions in Part 2
-were not incentivized, but subjects were told that providing an accurate answer would increase their chances of earning more money in 
-the last part of the experiment.
+They were also asked to say how confident they felt about their choices. They had 4 possible answers: "it was a random guess," 
+"there is another equally likely score," "I am pretty sure," "I am completely sure."
+I mapped these four answers to priors that place probabilities .33, .50, .75, and 1 to the chosen type.
+The remaining probability is split equally among the other two types.
+Questions in Part 2 were not incentivized, but subjects were told that providing an accurate answer would increase their chances of earning more money in the last part of the experiment.
 
@@
 
-Finally, in Part 3, subjects completed a belief updating task for each of the quizzes. Before starting the task they were reminded of their guess
-for the score. In the ego-relevant treatment, they were reminded of their guess about themselves and in the stereotype treatment they were reminded
-of their guess about the other participant. In the stereotype treatment, they were also reminded of the characteristics of the other participant.
-
-For one topic at a time and in random order,
-they were presented with the three gambles from the example above and were asked to choose one of them. 
-The probability of success was 
-determined by their own score in the ego-relevant condition, and by the score of the other participant in the stereotype condition. 
-Subjects had access to the three probability
-tables in the printout of the instructions at all times and the meaning of each cell was explained in detail.
-
-In the interphase, they had to choose which of the 3 tables they wanted to see before entering their choice in it. This was done as 
+Finally, in Part 3, subjects completed a belief updating task for each of the quizzes.
+Before starting the task they were reminded of their guess for the score.
+In the ego-relevant treatment, they were reminded of their guess about themselves and in the stereotype treatment they were reminded of their guess about the other participant.
+In the stereotype treatment, they were also reminded of the characteristics of the other participant.
+
+For one topic at a time and in random order, they were presented with the three gambles from the unifying example and were asked to choose one of them.
+The probability of success was determined by their own score in the ego-relevant condition, and by the score of the other participant in the stereotype condition.
+Subjects had access to the three probability tables in the printout of the instructions at all times and the meaning of each cell was explained in detail.
+
+In the interfase, they had to choose which of the 3 tables they wanted to see before entering their choice in it. This was done as 
 an alternative to a belief elicitation in each round. I take their choice of table to be indicative of their beliefs about
-the underlying type. I chose not to elicit the beliefs at each round to stay true to the forces in framework 1.
+the underlying type.
+I chose not to elicit the beliefs at each round to stay true to the forces in framework 1.
+The agent's tas kin Framework 1 is to learn the exogenous parameter and match it with their choice.
+By eliciting the beliefs about their type in each round and rewarding it for it, I add an incentive to additionally learn their type correctly.
+This can lead them to take actions that  reveal their type when they wouldn's have done so in the case where there is no additional incentive.
 
 Once they have entered their choice, they observe a sample of 10 outcomes from the gamble they chose. After observing the outcomes, 
-they returned to the choice screen and entered a new choice. In the choice screen 
-subjects had access to the entire history of gambles and outcomes for that task as well as a summary of the outcomes so far. 
-Once they entered 11 gambles (and observed 110 outcomes), they moved on to 
-the next topic and repeated the same procedure. They all did this for all 6 topics.
-
-At the end of the experiment, one of the 6 topics was randomly selected to determine the payment. 
-They earned $\$0.20$ for each 
+they returned to the choice screen and entered a new choice.
+In the choice screen subjects had access to the entire history of gambles and outcomes for that task as well as a summary of the outcomes so far.
+Once they entered 11 gambles (and observed 110 outcomes), they moved on to the next topic and repeated the same procedure.
+They all did this for all 6 topics.
+
+At the end of the experiment, one of the 6 topics was randomly selected to determine the payment. They earned $\$0.20$ for each 
 correct answer in the quiz, and for each success in the task in Part 3 for the selected topic.
@@
 In particular, the reaction to good and bad news is very informative of which model is most likely to be underlying the behavior.
-Define \emph{good news} to be a sample of signal realizations such that the number of successes in the sample is larger than the average number of successes observed so far.
+Denote the sample size by $I$ and define \emph{good news} to be a sample of signal realizations such that the number of successes in the sample is larger than the average number of successes observed so far.
 i.e.
@@
 
-$$ \sum_i \mathbb{I}\{o_{iT}=success\} \geq \frac{1}{T} \sum_{t=0}^T\sum_i \mathbb{I}\{o_{it}=success\}$$
-where T is the current period and $o_{t}=[o_{it}]_{i=1}^I$ is the sample observed at period $t$.
-\emph{Bad news} are any other kind of signal realization.
-Denote the set of good news at period t by $\mathcal{G}_t$ and let $s_t$ be the number of successes in $o_t$.
-
-Given the definition of good and bad news, the reaction of the agent to each kind of news is the change in their choice, conditional on the signal realization.
-Therefore, what we are interested are the coefficients of the following regression model, where the actions are those that a bayesian agent would choose:
-
-$$ \Delta a = \beta_0 + \beta_1\mathbb{I}\{o_t\in \mathcal{G}_t\} + \beta_2(s_{t} - s_{t-1}) + \beta_3\mathbb{I}\{o_t\in \mathcal{G}_t\}(s_{t} - s_{t-1})  $$
-
-Where $(s_{t} - s_{t-1})$ is the size of the surprise and $\Delta a$ is the change in action.
+$$ \sum_{i=1}^I \mathbb{I}\{o_{iT}=success\} \geq \frac{1}{T} \sum_{t=0}^T\sum_{i=1}^I \mathbb{I}\{o_{it}=success\}$$
+where $T$ is the current period and $o_{t}=[o_{it}]_{i=1}^I$ is the sample observed at period $t$.
+Denote the set of good news at period t by $\mathcal{G}_t$ and let $s_t$ be the number of successes in $o_t$.\emph{Bad news} are any other kind of samples of signal realizations.
+
+Given the definition of good and bad news, the reaction of the agent to each kind of news is the change in their choice conditional on the signal realization.
+Therefore, what we are interested in are the coefficients of the following regression model
+
+$$ \Delta a = \beta_0 + \beta_1\mathbb{I}\{o_t\in \mathcal{G}_t\} + \beta_2(s_{t} - s_{t-1}) + \beta_3\mathbb{I}\{o_t\in \mathcal{G}_t\}(s_{t} - s_{t-1}) +\varepsilon_t $$
+where $(s_{t} - s_{t-1})$ is the size of the surprise\footnote{The surpries eis the difference between the number of successes in the sample observed at time t and the average number of successes in previous samples.} and $\Delta a = a_{t+1}-a_t$ is the change in action as a reaction after observing the latest sample.
 $\beta_2$ is the reaction of the agent to bad news with surprise $(s_{t} - s_{t-1})$.
 And $\beta_2 + \beta_3$ is the reaction to good news with surprise $(s_{t} - s_{t-1})$.
-Notice that for a dogmatic modeler $\beta_2\geq0$ and $\beta_2+\beta_3\geq 0$ as more successes are always indicative of a better state.
+$\varepsilon_t\sim N(0, \sigma)$ is variation in the action choices that is not explained by the sample of signal realizations.
+
+## Self-Attribution Bias
+
+The key feature of Self-attribution bias is the asymmetric treatment of good news and bad news. 
+In particular, the agent will over-attribute successes to a high type and under-attribute them to a low type.
+Similarly, they will over-attribute failures to a low state and under-attribute them to a high state.
+This implies that, after observing a failure, the agent will adjust their effort downwards by more than 
+what an unbiased Bayesian would have done. In contrast, after observing a success, the agent will adjust 
+their effort upwards by less than a Bayesian would have done and if the bias is large enough, it could
+be that the agent will not adjust their effort upwards at all, or even decrease their effort in response to a success.
+
+This is in stark contrast with what a Dogmatic modeler would do. A dogmatic modeler always attributes
+any variation in the outcome to the state and never updates their beliefs about $\theta$. Therefore,
+they will always increase their effort choices after a surprising success and decrease it after a failure.
+
+On the other hand, the biased behavior can be in line with the behavior of a switcher. In particular,
+if the agent starts with a misspecified belief on $\hat{\theta}$, and is willing to switch to a belief with 
+$\theta'>\hat{\theta}$, whenever the paradigm shift happens, it will likely be in response to a surprising 
+streak of successes. In this case, when they adjust their belief about $\theta$, they will also 
+adjust their effort choice. Since they were initially underconfident, they had been choosing an effort that was
+too high relative to the true state, and therefore, the effort is likely to fall in response to a 
+surprising streak of success.
+
+Let $\beta^A$ be the coefficients of the regression model when the agent updates with misattribution bias.
+Let $\beta^B$ be tha coefficients of the same regression model but when the agent is Bayesian.
+
+**Prediction 1A:** _After observing a failure, the agent will adjust their effort downwards by more than a Bayesian would have done.
+After observing a success, the agent will adjust their effort upwards by less than a Bayesian would have done.
+If the bias is large enough, the agent might not adjust their effort upwards at all, or even decrease their effort in response to a success.
+That is $\beta_2^A > \beta_2^B$ and $\beta_2^A + \beta_3^A<\beta_2^B + \beta_3^B$_
+
+In addition to their behavior, there is an additional characteristic feature of misattribution bias that is not present in other models.
+This is the only model in which an agent could start off with a correct belief and become more overconfident.
+In the long-run.
+
+**Prediction 2A:** _After observing a streak of successes, the agent will update their belief about $\theta$ upwards even when they started with a correct initial belief._
 
@@
 
-Since the domain of the problem is discrete and finite in the example, the predictions of the original theory apply only to 
-the combinations of parameters and initial beliefs for which there is a self-defeating equilibrium. In the example, there are 5 such 
-combinations. For each of them, the dogmatic modeler predicts that the agent will fall into the self-defeating equilibrium and will 
-be able to sustain the misspecified belief forever.
-
-Table \ref{tab:table-dog} describes the 5 self-defeating equilibria and the effort choices that sustain them. The first columns describe the
-combination of parameters and initial beliefs. The last column describes the effort choice that the agent will make in the long run. It is 
-only for these combinations of parameter values and beliefs that the dogmatic model makes predictions within the Unifying example.
+Since the domain of the problem is discrete and finite in the example, the predictions of the original theory of @Heidhues2018 apply only to the combinations of parameters and initial beliefs for which there is a self-defeating equilibrium.
+In the unifying example, there are 5 such combinations.
+For each of them, the dogmatic model predicts that the agent will fall into the self-defeating equilibrium and will be able to sustain the dogmatic misspecified belief forever.
+
+Table \ref{tab:table-dog} describes the 5 self-defeating equilibria and the effort choices that sustain them.
+The first columns describe the combination of parameters and initial beliefs.
+The last column describes the effort choice that the agent will make in the long run.
+It is only for these combinations of parameter values and beliefs that the dogmatic model makes predictions within the Unifying example.
+Otherwise, the agent is not able to sustain the dogmatic belief and  will be forced to use a different updating procedure to rationalize the signals that he observed.
 
 **Prediction 1D:** _Whenever an agent is of a type $\theta^*$ but mistakenly believes that they are of a type $\hat{\theta}$, 
-and $(\theta^*, \omega^*, \hat{\theta})$ are such that there is s self-defeating equilibrium, the agent will fall into the
-trap and choose the effort level that sustains the misspecified belief forever._
-
-In term of the dogmatic's reagtion to good and bad news, let $\beta^D$ denote the coefficients of the regression model above when the actions are those predicted by the dogmatic model.
+and $(\theta^*, \omega^*, \hat{\theta})$ are such that there is a self-defeating equilibrium, the agent will choose the effort level that sustains the misspecified belief forever._
+
+In term of the dogmatic's reaction to good and bad news, let $\beta^D$ denote the coefficients of the regression model above when the actions are those predicted by the dogmatic model.
 
 **Prediction 2D:** _Before falling into a trap, the dogmatic modeler reacts more to good and bad news than the Bayesian would. i.e. $\beta_2^D>\beta_2$ and $\beta_3^D > \beta_3$._
+
+**Prediction 3D:** _A dogmatic modeler never updates their belief about $\theta$._
 
@@
 for understanding the prevalence of overconfidence. Similarly, gaining insight into what happens 
-when there are no traps is important for understanding what are the other reasons why overconfidence 
+when there are no traps is important for understanding the other reasons why overconfidence 
 might arise and prevail.
@@
 
-Since the switcher starts as the same dogmatic agent, the initial behavior of both types of agents is identical, 
-however, because the switcher is keeping track of the likelihood ratio, they will be able to escape the self-defeating
-equilibrium if the evidence is convincing enough. Therefore there is a positive probability that the switcher will
+Since the switcher starts as the same dogmatic agent, the initial behavior of both types of agents is identical. 
+However, because the switcher keeps track of the likelihood ratio, they will be able to escape the self-defeating
+equilibria if the evidence is convincing enough. Therefore there is positive probability that the switcher will
 adjust their initially misspecified belief about $\theta$ and learn the true state.
 
-**Prediction 1S:** _With positive probability, the switcher will escape the self-defeating equilibrium and learn the true state._
+**Prediction 1S:** _With positive probability, the switcher will escape the self-defeating equilibria and learn the true state._
 
@@
 When there is a change in paradigm, the reaction to good and bad news is attenuated or even in the opposite direction of what a Bayesian would have done.
-that is $\beta_2^S<\beta_2$ and $\beta_2^S + \beta_3^S<\beta_2+\beta_3$_
+that is $\beta_2^S<\beta_2^B$ and $\beta_2^S + \beta_3^S<\beta_2^B+\beta_3^B$_
 
@@
 in order to distinguish between the two theories, I need to look at cases where the agent starts with a misspecified belief and the switcher changes paradigm.
-
-The probability that the switcher will escape the self-defeating equilibrium depends on the prior belief about $\omega$.
-If the prior is sufficiently tight around the self-defeating equilibrium, the likelihood ratio will not grow fast enough, however, 
-in the example above, the prior is uniform over the states and therefore, the likelihood ratio is more likely to grow fast enough.
-
-## Self-Attribution Bias
-
-The key feature of Self-attribution bias is the asymmetric treatment of good news and bad news. 
-In particular, the agent will over-attribute successes to a high type and under-attribute them to a low type.
-Similarly, they will over-attribute failures to a low state and under-attribute them to a high state.
-This implies that, after observing a failure, the agent will adjust their effort downwards by more than 
-what an unbiased Bayesian would have done. In contrast, after observing a success, the agent will adjust 
-their effort upwards by less than a Bayesian would have done and if the bias is large enough, it could
-be that the agent will not adjust their effort upwards at all, or even decrease their effort in response to a success.
-
-This is in stark contrast with what a Dogmatic modeler would do. A dogmatic modeler always attributes
-any variation in the outcome to the state and never updates their beliefs about $\theta$. Therefore,
-they will always increase their effort choices after a surprising success and decrease it after a failure.
-
-On the other hand, the biased behavior can be in line with the behavior of a switcher. In particular,
-if the agent starts with a misspecified belief on $\hat{\theta}$, and is willing to switch to a belief with 
-$\theta'>\hat{\theta}$, whenever the paradigm shift happens, it will likely be in response to a surprising 
-streak of successes. In this case, when they adjust their belief about $\theta$, they will also 
-adjust their effort choice. Since they were initially underconfident, they had been choosing an effort that was
-too high relative to the true state, and therefore, the effort is likely to fall in response to a 
-surprising streak of success.
-
-Let $\beta^A$ be the coefficients of the regression model when the agent updates with misattribution bias.
-
-**Prediction 1A:** _After observing a failure, the agent will adjust their effort downwards by more than a Bayesian would have done.
-After observing a success, the agent will adjust their effort upwards by less than a Bayesian would have done.
-If the bias is large enough, the agent might not adjust their effort upwards at all, or even decrease their effort in response to a success.
-That is $\beta_2^A > \beta_2$ and $\beta_2^A + \beta_3^A<\beta_2 + \beta_3$_
-
-In addition to their behavior, there is an additional characteristic feature of misattribution bias that is not present in other models.
-This is the only model in which an agent could start off with a correct belief and become more overconfident.
-In the long-run.
-
-**Prediction 2A:** _After observing a streak of successes, the agent will update their belief about $\theta$ upwards.
-This will lead to the possibility of observing subjects who start correctly specified and become overconfident._
+**Prediction 3S:** _Correctly specified switchers do not update their beliefs about $\theta$_
+
+The probability that the switcher will escape the self-defeating equilibria depends on the prior belief about $\omega$.
+If the prior is sufficiently tight around a self-defeating equilibrium, the likelihood ratio will not grow fast enough.
+In the unifying example, the prior is uniform over the states and therefore, the likelihood ratio is more likely to grow fast enough.
 
@@
 
-As such, all the predictions discussed above apply to the case of Stereotypes as well. My analysis of 
+All the predictions discussed above apply to the case of Stereotypes as well. My analysis of 
 stereotypes will focus only on the degree to which ego-relevance of the type affects the updating procedure and not on the 
@@
 they are overconfident; if it is in a lower category, they are underconfident; and if it is in the same category, 
-they are correctly specified. Overall, `r round(sum(updates$misspecification != 'correct')/nrow(updates), 2)` of the 
+they are correctly specified. Overall, `r round(sum(updates$misspecification != 'correct')/nrow(updates), 2)*100`% of the 
 guesses made in the questionnaire were misspecified. The rest of the guesses coincided with the true score. 
@@
 
-![Initial misspecifications by treatment](../figures/misspecification_hist.png){#fig:misspecification-hist}
+![Initial specifications by treatment](../figures/misspecification_hist.png){#fig:misspecification-hist}
 
@@
 combinations of characteristics in each treatment. Figure \ref{fig:misspecification-by-treatment} shows a heatmap 
-of the misspecifications that arose in each treatment. In the stereotype treatment, subjects are most underconfident 
+of the specifications that arose in each treatment. In the stereotype treatment, subjects are most underconfident 
 about the performance 
@@
 
-![Initial misspecifications by treatment and characteristics](../figures/misspecifications_characteristics_treatment.png){#fig:misspecification-by-treatment}
+![Initial misspecifications by treatment and characteristics.
+a -1 corresponds to all subjects being underconfident while 1 corresponds to all subjects being overconfidence.
+All subjects being correctly specified is assigned a value of zero.](../figures/misspecifications_characteristics_treatment.png){#fig:misspecification-by-treatment}
 
@@
 Since the elicitation of the belief about the type was not incentivized and not elicited in a standard way, 
-I first need to confirm that subjects were not just randomly choosing a matrix in which to enter their effort.
+I first need to confirm that subjects were not randomly choosing a matrix in which to enter their effort.
 The left panel of Figure \ref{fig:matrix-choices-by-round} shows the share of subjects who chose a matrix 
-consistent with their initial reported belief. In round 1, `r round(nrow(updates[round_number == 1 & last_button_consistent == 1])/ nrow(updates[round_number==1]), 2)*100`% 
-of the subjects chose a matrix that was consistent with their initial belief. This indicates that subjects
-were not just randomly choosing a matrix in which to enter their effort. From round 2 onwards, the share
-steadily declines, but still not as far as to indicate a random choice of matrices. This is consistent with
-the subjects moving away from their starting belief through some updating procedure.
+consistent with their initial reported belief.
+In round 1, `r round(nrow(updates[round_number == 1 & last_button_consistent == 1])/ nrow(updates[round_number==1]), 2)*100`% of the subjects chose a matrix that was consistent with their initial belief.
+This indicates that subjects were not randomly choosing a matrix in which to enter their effort.
+From round 2 onwards, the share declines, but not as far as to indicate a random choice of matrices.
+This is consistent with the subjects moving away from their starting belief through some updating procedure.
 
@@
 
-Figure \ref{fig:transitions} shows the transition matrix for subjects who started in each of the 
-3 possible starting specifications and the specifications that they ended up in at the end of the updating task.
-The two things to note are that the initial belief is the most likely end belief. This is consistent with 
-some degree of stickiness of the misspecifications as the switcher and dogmatic models would predict. However, 
-the data also presents a lot of subjects who started with a correct belief of the type and ended up 
-overestimating it. This is consistent only with the self-attribution bias. Lastly, the subjects who
-initially overestimate the score, are the least likely to learn their true type.
+Figure \ref{fig:transitions} shows the transition matrix for subjects who started in each of the three possible starting specifications and the specifications that they ended up in at the end of the updating task.
+The two things to note are that the initial belief is the most likely end belief.
+This is consistent with some degree of stickiness of the misspecifications as the switcher and dogmatic models would predict.
+However, the data also presents a lot of subjects who started with a correct belief of the type and ended up overestimating it.
+This is consistent only with self-attribution bias.
+Lastly, subjects who initially overestimate the score, are the least likely to learn their true type.
 
@@
 still possible that there is heterogeneity in the updating procedure across subjects. In the next section
-I will look at the role of self-defeating equilibria in preventing learning. I find that the presence of
-self-defeating equilibria does not seem to be the main deterrent to learning.
+I will look at the role of self-defeating equilibria in preventing learning.
 
@@
 
-As described above, the presence of stable misspecified beliefs act as learning traps. If an agent falls 
+As described in Framework 1, the presence of stable misspecified beliefs act as learning traps in this setting. If an agent falls 
 into one of these traps, bayesian updating will lead them to choose the same effort forever. These self-defeating 
@@
 that even in the presence of traps, `r share_learned*100`% of subjects learn. From the share that 
-did not learn when there was a trap. A remaining `r share_trapped*100`% can be accounted for as being 
+did not learn when there was a trap, `r share_trapped*100`% can be accounted for as being 
 trapped.\footnote{A subject is considered trapped when 3 out of their last 4 choices are consistent with 
@@
 choices were far from optimal. Behavior that is not consistent with either of these falls outside of the 
-scope of the theories discussed above.
-
-My results are consistent with the findings of @Hestermann2021. In a laboratory experiment that
+scope of the theories discussed here.
+
+My results are consistent with the findings of @Gotte2022. In a laboratory experiment that
 stays true to Framework 1, they test the predictions of the dogmatic modeler. They find that the average
-pattern in behavior is in the direction of the dogmatic modeler, however, subjects do not fully act as dogmatics as
+pattern in behavior is in the direction of the dogmatic modeler, however, subjects do not fully act as dogmatics since
 their actions do not go as far as to fully support the self-defeating equilibrium. A lot of 
@@
 In addition, I calculate the difference between the realized number of successes and the average number of successes so far and
-call it the news differential.
-Figure \ref{fig:reaction-news} shows the correlation between change in effort and the news differential, separately for 
-good and bad news.
-
-The overall pattern is that bad news are associated with a decrease in effort, and a 
-more negative news differential is associated with a larger decrease in effort. On the contrary, good news are associated with 
-a small decrease in effort. As mentioned in the predictions section, this is consistent with the self-attribution bias as well
-as with a change of paradigm. It is not consistent with the dogmatic modeler or the Bayesian. Because 
-I do not directly elicit beliefs, it is not possible to distinguish between the self-attribution bias and the change of 
-paradigm with this data alone.
-Nevertheless, the fact that about a third of the subjects started with a correctly specified belief and ended up overconfident
-is consistent only with the self-attribution bias. this points towards the fact that 
-misattribution bias is the most likely explanation for the behavior of the subjects in the experiment.
+call it the news differential but can be thought of as the "size'' of the surprise.
+Figure \ref{fig:reaction-news} shows the correlation between change in effort and the news differential, separately for good and bad news.
+
+The overall pattern is that bad news are associated with a decrease in effort, and a more negative news differential is associated with a larger decrease in effort.
+On the contrary, good news are associated with a small decrease in effort.
+As mentioned in the predictions section, this is consistent with the self-attribution bias as well as with a change of paradigm.
+It is not consistent with the dogmatic modeler or the Bayesian.
+In addition, the fact that about a third of the subjects started with a correctly specified belief and ended up overconfident is consistent only with the self-attribution bias.
+This points towards the fact that misattribution bias is the most likely explanation for the aggregate behavior of the subjects in the experiment.
 
@@
 
-A regression analysis of this same data reveals that indeed, the slopes are different for godd and bad
-news and that the difference is statistically significant.\footnote{I run a robustness check where I define
-good news to be a net-positive sample (half or more of the outcomes observed in the sample received in that round
-were successful) and bad news to be net-negative sample. I find the same pattern in this alternative regression model
-and the results are reported in the appendix.} 
+A regression analysis of this same data reveals that indeed, the slopes are different for good and bad news and that the difference is statistically significant.\footnote{I run a robustness check where I define good news to be a net-positive sample (half or more of the outcomes observed in the sample received in that round were successful) and bad news to be net-negative sample.
+I find the same pattern in this alternative regression model and the results are reported in the appendix.}
 The regression results are reported in Table \ref{tab:regression}.
-columns 2 and 3 of the table consider the model for each treatment separately. I find no significant differences in 
-the parameters across treatment. This is consistent with the fact that the bias is not driven by the ego-relevance 
-of $\theta$.\footnote{The ego-relevance of $\theta$ is the motivation behind the self-attribution bias, 
-however, the bias itself is due to an incorrect updating procedure in response to good and bad news. The presence of 
-asymmetric updating in the stereotype condition can be due to self-censoring of the subjects. In particular, subjects 
-who initially underestimated the performance of the other participant might have realized their mistake and 
-by overestimating it after good news. This is consistent with the data presented here as well as with 
-the data observed in the transition matrix for stereotypes which is reported in the Appendix}
+columns 2 and 3 of the table consider the model for each treatment separately.
+I find no significant differences in the parameters across treatment.
+This is consistent with the fact that the bias is not driven by the ego-relevance of $\theta$.\footnote{The ego-relevance of $\theta$ is the motivation behind the self-attribution bias, however, the bias itself is due to an incorrect updating procedure in response to good and bad news.
+The presence of asymmetric updating in the stereotype condition can be due to self-censoring of the subjects.
+In particular, subjects who initially underestimated the performance of the other participant might have realized their mistake and by overestimating it after good news.
+This is consistent with the data presented here as well as with the data observed in the transition matrix for stereotypes which is reported in the Appendix}
 
@@
 in response to surprising bad news. This would flatten the slope of the regression line 
-for bad news relative to what a Bayesian would do. \ref{tab:regression} shows that the slope for bad news for
+for bad news relative to what a Bayesian would do. Table \ref{tab:regression} shows that the slope for bad news for
 the simulation\footnote{The details on how the data was simulated are explained in the Appendix} 
@@
 Throughout the experiment, there is little difference in the behavior of subjects across treatments.
-Two of the main differences are that subjects in the ego-relevant treatment are more likely to become 
-overconfident when they start with a correct belief. And that subjects in the stereotype treatment are
+Two of the main differences are, first that subjects in the ego-relevant treatment are more likely to become 
+overconfident when they start with a correct belief; and second, that subjects in the stereotype treatment are
 more likely to overreact to good news when they start by underestimating the performance of the other
@@
 
-These two differences present as consistent with the self-attribution bias. However, the pattern in the
+These two differences present as consistent with the self-attribution bias, however, the pattern in the
 stereotype treatment could also be due to self-censoring of the subjects. In particular, subjects who
@@
 $$
-\ell = \frac{L(\theta | b_{\tau}^\theta)}{L(\theta | b_{\tau-1}^\theta)}=\frac{p_\tau(o_t|b_{\tau}^\theta)}{p_{\tau}(o_t|b_{\tau-1}^\theta)} 
+\ell = \frac{L(\theta | b_{\tau}^\theta)}{L(\theta | b_{\tau-1}^\theta)}=\frac{p_\tau(o_t|b_{\tau}^\theta)}{p_{\tau}(o_t|b_{\tau-1}^\theta)},
 $$
@@
 
-$$\hat{\alpha} = \frac{1}{N}\sum_{i=1}^N \ell_{i\tau}$$
-
-Where $N$ is the number of switches observed in the experiment.
+$$\hat{\alpha} = \frac{1}{N}\sum_{i=1}^N \ell_{i\tau},$$
+
+where $N$ is the number of switches observed in the experiment.
 
@@
 The sample moments are reported in \ref{tab:regression-net} and correspond to the following regression model:
-
-$$ \Delta effort_{it} = \beta_0 + \beta_1 signal_{i t-1} + \beta_2\mathbb{I}\{good \:news_{i t-1}\} + \beta_3{I}\{good\:news\}*signal_{i t-1} $$
+$$ \Delta effort_{it} = \beta_0 + \beta_1 signal_{i t-1} + \beta_2\mathbb{I}\{good \:news_{i t-1}\} + \beta_3{I}\{good\:news\}*signal_{i t-1}, $$
 where $i$ is an individual and task level index (each subject in each of the six tasks in the experiment represents a single observed path) and $t$ is a round_number index that ranges from 1 to 11.

### 2023-10-27 Paper/draft.tex
draft edits

@@
 \PassOptionsToPackage{hyphens}{url}
+\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
 %
@@
 \definecolor{myblue}{RGB}{31, 61, 122}
-\definecolor{mypink}{RGB}{204, 0, 82}
+\definecolor{mypink}{RGB}{50, 107, 31}
 \newtheorem{assumption}{Assumption}
@@
 \hypersetup{
-  pdftitle={Learning with Mental Models: the case of overestimation},
   pdfauthor={Jimena Galindo},
-  hidelinks,
+  colorlinks=true,
+  linkcolor={mypink},
+  filecolor={myblue},
+  citecolor={mypink},
+  urlcolor={mypink},
   pdfcreator={LaTeX via pandoc}}
 
-\title{Learning with Mental Models: the case of overestimation}
+\title{Learning with Misspecified Models: The Case of Overestimation\\
+\href{https://jimena-galindo.github.io/fileRepo/draft.pdf}{\normalsize Click Here for the Latest Version}}
 \author{Jimena Galindo}
-\date{October 24, 2023}
+\date{October 26, 2023}
 
@@
 integrate the received information into their
-beliefs.\footnote{See \citet{benjamin2019} for a review of the literature on errors of 
-probabilistic thinking.} However, many real-world situations cast agents
-as active participants in the generation of information. In these cases,
-the information they observe is influenced by their actions and
-subsequent behavior is in turn determined by how they incorporate the
-information into their beliefs.
-
-As an example consider a student who needs to decide how much effort to
+beliefs.\footnote{See \citet{benjamin2019} for a review of the literature on errors of probabilistic thinking.}
+However, many real-world situations cast agents as active participants
+in the generation of information. In these cases, the information they
+observe is influenced by their actions and subsequent behavior is in
+turn determined by how they incorporate the information into their
+beliefs.
+
+As an example, consider a student who needs to decide how much effort to
 put into studying for an exam. Their decision will depend on two
-factors: their belief about their intrinsic ability, and their belief
+factors: their belief about their intrinsic ability and their belief
 about how difficult the exam will be. The outcome they observe will be
-affected by how much they decide to study. Imagine that the student puts
-in a moderate amount of effort and gets a surprisingly good grade. Did
-they get a good grade because they are smarter than they thought? Or
-because the exam was easier than they had anticipated? Their future exam
-preparation strategy will depend fundamentally on which line of
+affected by how much they decide to study. Imagine that the student
+exerts a moderate amount of effort and gets a surprisingly good grade.
+Did they get a good grade because they are smarter than they thought? Or
+because the exam was easier than they had anticipated? Their future
+exam-preparation strategy will depend fundamentally on which line of
 reasoning they take. This feedback loop is referred to as an
-\emph{endogenous information 
-process} and is at the center of the forces I study.
-
-To understand what the main forces at play are, I compare a set of
-theories that model learning in settings with endogenous information,
-and which can rationalize the persistence of misspecified beliefs. I
-develop a unifying framework that nests multiple theories of learning
-and generates testable predictions for each of them. Then I cast this
+\emph{endogenous information process} and is at the center of the forces
+I study.
+
+To understand what main forces are at play, I compare a set of theories
+that model learning in settings with endogenous information and can
+rationalize the persistence of misspecified beliefs. I develop a
+unifying framework that nests multiple theories of learning and
+generates testable predictions for each of them. Then, I cast this
 framework in a laboratory experiment and test the predictions to
@@
 observe in the lab. The experiment features an agent who needs to learn
-two parameters: one that pertains their own characteristics (an
-\emph{ego-relevant} parameter), and an exogenously determined state---in
+two parameters: one that pertains to their own characteristics (an
+\emph{ego-relevant} parameter), and an exogenously determined state. In
 the context of the student preparing for exams, the two parameters would
@@
 to as overconfidence (or underconfidence) and have been documented by
-behavioral scientists\footnote{\citet{kelley1980} 
-provides a review of the psychology literature.} and
-economists\footnote{See \citet{benjamin2019} 
-for a review of the literature in economics.} in a variety of settings.
-\citet{Oster2013} find that subjects who are at high risk of having
-Huntington's disease overestimate their probability of being healthy and
-make retirement decisions as if they were healthy. \citet{Hoffman2020}
-show that workers overestimate the quality of their match to their
-current employment and are unlikely to look for other opportunities.
-\citet{Camerer1999} find that entrepreneurs are overconfident about the
-quality of their enterprise, which leads to excessive entry and early
-exit from markets.
+behavioral
+scientists\footnote{\citet{kelley1980} provides a review of the psychology literature.}
+and
+economists\footnote{See \citet{benjamin2019} for a review of the literature in economics.}
+in a variety of settings. \citet{Oster2013} find subjects who are at
+high risk of having Huntington's disease overestimate their probability
+of being healthy, and they make retirement decisions as if they were
+healthy. \citet{Hoffman2020} show workers overestimate the quality of
+their match to their current employment and are unlikely to look for
+other opportunities. \citet{Camerer1999} find entrepreneurs are
+overconfident about the quality of their enterprise, which leads to
+excessive entry and early exit from markets.
 
@@
 experimental evidence documenting the bias is collected in settings
-where subjects are passive learners.\footnote{
-\citet{Gotte2022} and \citet{Ozyilmaz2022} are exceptions that study settings with endogenous information processes.}
+where subjects are passive
+learners.\footnote{\citet{Gotte2022} and \citet{Ozyilmaz2022} are exceptions that study settings with endogenous information processes.}
 They observe a noisy signal and report their beliefs over subsequent
-rounds.\footnote{\citet{Bracha2012} and 
-\citet{Mobius2022} are some examples.} Although these studies provide
-important insights, they are not flexible enough to incorporate the
-richer theories that have been proposed more recently. In particular,
-they do not allow the study of endogenous learning or for learning about
-multiple parameters at once.\footnote{\citet{Coutts2020} 
-studies an environment with an ego-relevant parameter and an exogenous state but does not 
+rounds.\footnote{\citet{Bracha2012} and \citet{Mobius2022} are some examples.}
+Although these studies provide important insights, they are not flexible
+enough to incorporate the richer theories that have been proposed more
+recently. In particular, they do not allow the study of endogenous
+learning or for learning about multiple parameters at
+once.\footnote{\citet{Coutts2020} studies an environment with an ego-relevant parameter and an exogenous state but does not 
 incorporate the endogenous information process.}
@@
 When the setting features learning traps, even an agent who incorporates
-all information correctly, may fall into learning traps as outlined by
+all information correctly may fall into learning traps, as outlined by
 \citet{Hestermann2021}. These traps are characterized by a combination
-of an incorrect belief and an optimal action which produce information
+of an incorrect belief and an optimal action that produce information
 that confirms the incorrect belief. Once an agent falls into a trap, the
@@
 If the agent is dogmatic about their initial belief,
-\citet{Heidhues2018} show that they will inevitably fall into a trap and
-thus will be able to rationalize and sustain their initial
-misspecification
+\citet{Heidhues2018} show they will inevitably fall into a trap and thus
+will be able to rationalize and sustain their initial misspecification
 belief.\footnote{\citet{Gotte2022} study the case of agents with dogmatic initial beliefs in a 
@@
 mechanism through which they can abandon incorrect beliefs. This allows
-them to avoid falling into learning traps. To do so agents perform
-Bayesian hypothesis tests that evaluate which is the more likely
-parameter out of two possibilities. By doing this, she characterizes the
-set of situations in which, even agents who consider alternative
-paradigms, may become trapped.\footnote{A 
-similar mechanism is proposed by \citet{Schwarstein2021} in a setting with persuasion.}
+them to avoid falling into learning traps. To do so, agents perform
+Bayesian hypothesis tests that evaluate which of two possible parameters
+is more likely. By doing so, she characterizes the set of situations in
+which even agents who consider alternative paradigms may become
+trapped.\footnote{A similar mechanism is proposed by \citet{Schwarstein2021} in a setting with persuasion.}
 
@@
 suffer from misattribution bias will attribute successes to their own
-ability---the ego-relevant parameter---and failures to bad luck---the
-state. Under this model of learning, even an agent who initially has a
-correct initial belief may become overconfident if they observe a
-sequence of successes. In this case, the main driver of the bias is not
-an initial misspecification or the presence of learning traps, it is the
-updating procedure
-itself.\footnote{A more general framework that can be used to model 
-this bias has also been proposed by \citet{Brunnermeier2005} and empirically studied by \citet{Bracha2012}.}
+ability---the ego-relevant parameter---and their failures to bad
+luck---the state. Under this model of learning, even an agent who
+initially has a correct initial belief may become overconfident if they
+observe a sequence of successes. In this case, the main driver of the
+bias is not an initial misspecification or the presence of learning
+traps; it is the updating procedure
+itself.\footnote{A more general framework that can be used to model this bias has also been proposed by \citet{Brunnermeier2005} and empirically studied by \citet{Bracha2012}.}
 
@@
 made. I track their choices as well as their beliefs about their own
-ability. The goal is to identify which of the 3 forces---the presence of
-learning traps, misspecified initial beliefs, or misatribution
-bias---better explains the observed behavior. To determine the fit of
-the models, I compare the behavior predicted by each theory to the
-benchmark given by the fully Bayesian updating procedure.
+ability. The goal is to identify which of the three forces---the
+presence of learning traps, misspecified initial beliefs, or
+misatribution bias---better explains the observed behavior. To determine
+the fit of the models, I compare the behavior predicted by each theory
+with the benchmark given by the fully-Bayesian updating procedure.
 
@@
 other, and thus can induce stereotypes---a different type of
-misspecification.\\
-If correct learning about the parameters happens at higher rates in the
-stereotype treatment, it would suggest that the bias is intrinsically
-linked to the ego-relevance of the parameter. In contrast, if similar
-biased behavior arises in both treatments, it is more likely that the
-main driver of these types of misspecified beliefs is the updating
-procedure itself or the endogenous information process.
-
-Although some agents do fall into learning traps, I find that the
-behavior of most subjects is better explained by misattribution bias:
-good news are treated as signaling high ability, while bad news are
-attributed to a low state. I also find that misattribution is no more
-prevalent in the ego-relevant than in the stereotype condition. This
-suggests that the main driver of the misspecification is the updating
-procedure; however, the underlying mechanism by which the bias is
-generated may be different in both treatments: While in the ego-relevant
-condition subjects prefer to hold themselves in high esteem, in the
-stereotype condition updating seems to be driven by some sort of bias
-overcorrection---when subjects realize that they underestimated the
-ability of another participant based on their gender and nationality,
-they compensate by overestimating their ability.
+misspecification. If correct learning about the parameters happens at
+higher rates in the stereotype treatment, this finding would suggest the
+bias is intrinsically linked to the ego-relevance of the parameter. By
+contrast, if similar biased behavior arises in both treatments, the main
+driver of these types of misspecified beliefs is more likely to be the
+updating procedure itself or the endogenous information process.
+
+Although some agents do fall into learning traps, I find the behavior of
+most subjects is better explained by misattribution bias: good news are
+treated as signaling high ability, whereas bad news are attributed to a
+low state. I also find misattribution is no more prevalent in the
+ego-relevant than in the stereotype condition. This finding suggests the
+main driver of the misspecification is the updating procedure; however,
+the underlying mechanism by which the bias is generated may be different
+in both treatments. Whereas subjects in the ego-relevant condition
+prefer to hold themselves in high esteem, in the stereotype condition,
+updating seems to be driven by some sort of bias overcorrection---when
+subjects realize they underestimated the ability of another participant
+based on their gender and nationality, they compensate by overestimating
+their ability.
 
@@
 model-heterogeneity in the sample. I find that even at an individual
-level the behavior is better explained by a general model of
-misattribution bias for most subjects. There is a smaller group of
-subjects that can be better explained through dogmatic beliefs and
-hypothesis testing and none of them behave in line with the fully
+level, the behavior is better explained by an average model of
+misattribution bias for most subjects. A smaller group of subjects
+exists that can be better explained through dogmatic beliefs and
+hypothesis testing, and very few of them behave in line with the fully
 Bayesian benchmark.
 
-In what follows I first discuss the theoretical framework and the
-predictions of each of the theories. Then I introduce a unifying example
-and my hypotheses. In section 4 I describe the experimental design and
-in section 5 I present the data and the results. Section 6 outlines the
-estimation of the parameters and the model fit analysis.
+In what follows, I first discuss the theoretical framework and the
+predictions of each of the theories. Then, I introduce a unifying
+example and my hypotheses. In section 4, I describe the experimental
+design, and in section 5, I present the data and the results. Section 6
+outlines the estimation of the parameters and the model fit analysis.
 
@@
 
-The theories that I consider make predictions in two distinct
-frameworks. I first detail each theory within their original framework
-and then develop a unifying example that allows me to compare the
-predictions of all of them. In framework 1 I consider a setting in which
-the an agent observes a continuous output and infers the underlying
-parameters. In framework 2, the agent observes a binary outcome and
-infers the underlying probability of success, which is related to the
-parameters. In both frameworks, I consider two nested theories of
-learning.
+The theories I consider make predictions in two distinct frameworks. I
+first detail each theory within their original framework and then
+develop a unifying example that allows me to compare the predictions of
+all of them. In framework 1, I consider a setting in which an agent
+observes a continuous output and infers the underlying parameters. In
+framework 2, the agent observes a binary outcome and infers the
+underlying probability of success, which is related to the parameters.
 
@@
 
-An agent is of type \(\theta \in \Theta\) and faces an unknown exogenous
-state \(\omega\) drawn from some density \(f\) over \(\Omega\). The
-agent knows the distribution of \(\omega\) but not its realized value.
-His belief about the state, \(p_0(\omega)\), coincide with the true
-distribution, \(f\); and his belief about the type is \(p_0(\theta)\).
-Let the agent's true type be \(\theta^{*}\), and the realized state be
-\(\omega^{*}\).
+An agent of type \(\theta \in \Theta\) faces an unknown exogenous state
+\(\omega\) drawn from density \(f\) over \(\Omega\). The agent knows the
+distribution of \(\omega\) but not its realized value. His belief about
+the state \(\omega\in\Omega\) is \(p_0(\omega)\) and coincides with the
+true distribution, \(f\). His belief about the type \(\theta\in\Theta\)
+is \(p_0(\theta)\). Let the agent's true type be \(\theta^{*}\), and the
+realized state be \(\omega^{*}\).
 
@@
 \(h\). The outcome is a function of the agent's type, the state, and the
-action. In particular \(h = h(\theta^*, \omega^*, a) + \varepsilon\)
+action. In particular, \(h = h(\theta^*, \omega^*, a) + \varepsilon\)
 with \(h(\cdot)\) increasing in both \(\theta^*\) and \(\omega^*\), and
@@
 there is a unique optimal action. Additionally,
-\(\varepsilon\sim N(0, \sigma)\) is noise in the output.
+\(\varepsilon\sim N(0, \sigma)\) is noise in the outcome.
 
@@
 that maximizes the payoff in each period. This assumption simplifies the
-analysis and plays a role in whether an agent who updates their beliefs
+analysis and plays a role in whether an agent who updates his beliefs
 using Bayes rule would learn the truth or not, however, for the main
 theory discussed in this section, the results hold even when relaxing
-this assumption.
+this assumption as shown in \citet{Heidhues2018}.
 
@@
 A \emph{self-defeating equilibrium} is a belief and action pair,
-\((p, a)\), such that the agent's belief about their type is
+\((p, a^*)\), such that the agent's belief about his type is
 misspecified, and the outcome generated by the action is consistent with
 the misspecified belief. The agent's belief is said to be \emph{stable}
-when this happens and the average output is
-
-\[\bar{h}(a^*) = h(\hat{\theta}, \hat{\omega}, a)\] Where
-\(\hat{\theta}\) and \(\hat{\omega}\) is the type-state pair on which
-the misspecified belief places all probability. That is, the agents
-belief is \(p(\hat{\theta}, \hat{\omega}) = 1\) and
+when this happens.
+
+Given the choice that sustains the self-defeating equilibrium, they
+observe the \emph{average output} given by
+\[\bar{h}(a^*) =\frac{1}{T}\sum_t \left[h(\hat{\theta}, \hat{\omega}, a^*)+\varepsilon_t\right]\]
+where \(\hat{\theta}\) and \(\hat{\omega}\) is the type-state pair on
+which the misspecified belief places all probability. That is, the
+agents belief is \(p(\hat{\theta}, \hat{\omega}) = 1\) and
 \(p(\theta, \omega) = 0\) for all other values of the parameter.
@@
 updating: the first one is a dogmatic modeler adapted from
-\citet{Heidhues2018},The second one is a switcher, as in \citet{Ba2023}.
-The dogmatic modeler can be seen as a switcher with an infinitely sticky
-initial belief so the two theories are nested. However, outside of the
-limiting case, they produce different predictions about the agent's
-behavior. I discuss each of them separately in what follows.
+\citet{Heidhues2018}. The second one is a switcher, as in
+\citet{Ba2023}. The dogmatic modeler can be seen as a switcher with an
+infinitely sticky initial belief so the two theories are nested.
+However, outside of the limiting case, they produce different
+predictions about the agent's behavior. I discuss each of them
+separately in what follows.
 
@@
 A dogmatic agent is characterized by a learning model where he does not
-update their beliefs about \(\theta\), instead, he holds a degenerate
+update his beliefs about \(\theta\) and instead, holds a degenerate
 belief that places all probability on \(\hat{\theta}\), which is
-potentially misspecified. In this case, no matter how much information
-he gathers against being of type \(\hat{\theta}\), he will not update
-his beliefs about it. Any discrepancies between the observed outcomes
+potentially misspecified. In this case, no matter how much evidence he
+gathers against being of type \(\hat{\theta}\), he will not update the
+beliefs about his type. Any discrepancies between the observed outcomes
 and his believed type are incorporated using the Bayes rule to update
@@
 modeler will inevitably fall into a self-defeating equilibrium. The
-equilibrium will be such that the outcomes they observe reinforce their
+equilibrium will be such that the outcomes he observes reinforce his
 belief on \(\omega\) in such a way that as \(t\to\infty\) the agent will
 be sure that the state is some \(\omega^{'}\) consistent with their
-believed type and the observed data. In other words, they will be in a
+believed type and the observed data. In other words, he will be in a
 self-defeating equilibrium with a stable belief that places probability
@@
 The mechanism by which the dogmatic agent falls into the self-defeating
-equilibrium is the following: Suppose the agent holds the misspecified
-belief that they are type \(\hat{\theta}>\theta^*\). For any prior over
-\(\omega\), the agent will be disappointed by the outcome. That is:
-\[\bar{h}(\theta^*, \omega^*, a_t^*) := \frac{1}{T}\sum_t \left[h(\theta^*, \omega^*, a_t^*)+\varepsilon_t\right]<\frac{1}{T}\sum_t \left[h(\hat{\theta}, \mathbb{E}(\omega), a_t^*)+\varepsilon_t\right]\]
-Where the right-hand-side of the inequality represents the average
-outcome that the agent expected.
+equilibrium is the following: suppose the agent holds the dogmatic and
+misspecified belief that they are type \(\hat{\theta}>\theta^*\). For
+any prior over \(\omega\), the agent will be disappointed by the
+outcome. That is:
+\[\frac{1}{T}\sum_t \left[{h}(\theta^*, \omega^*, a_t^*)+\varepsilon_t\right] <\mathbb{E_w} \left[h(\hat{\theta}, \omega, a_t^*)\right]\]
+where the right-hand-side of the inequality represents the average
+outcome that the agent expected given his beliefs about their type and
+the state. The left hand side is what they observed.
 
 There are two possible sources for the disappointment: the first is that
-the realized state is lower than the expected state; the second source
-is that the agent is of type \(\theta^*\) and therefore, for all
-possible states, his gain will be lower than what he expected.
+the realized state \(\omega^*\) is lower than what the agent expected,
+\(\mathbb{E}[\omega]\); the second source is that the agent is of type
+\(\theta^*\) and therefore, for all possible states, his gain will be
+lower than what he expected when the variance of the error term is low
+or \(T\) is large. That is, when \(\frac{1}{T}\sum_t\varepsilon_t\) is
+close to zero.
 
 Because the agent is dogmatic, he will not update his beliefs about
-\(\theta\) and as a consequence will attribute the disappointment to the
-state being lower than expected. He will continue to update in this way
-until he converges to a belief about \(\omega\) that is stable. Such a
-belief will explain the observed utility perfectly and allow the agent
+\(\theta\) and, as a consequence, will attribute the disappointment to
+the state being lower than expected. He will continue to update in this
+way until he converges to a belief about \(\omega\) that is stable. Such
+a belief will explain the observed utility perfectly and allow the agent
 to rationalize his dogmatic belief about \(\theta\). Under the
@@
 \textbf{Example 1: } \emph{Set \(A = \Omega=[\underline{a}, \infty)\)
-and consider a student with intrinsic ability \(\theta^*\geq 0\) who
-faces a grading procedure \(\omega^*\) that is unknown to them. The
+and consider a student (she) with intrinsic ability \(\theta^*\geq 0\)
+who faces a grading procedure \(\omega^*\) that is unknown to her. The
 student knows that a higher \(\omega^*\) is more likely to yield a
@@
 her grade. For whatever the chosen effort level, the student must pay a
-cost \(c(a) = \frac{1}{2}a^2\) and observes a grade of
-\((\theta^*+a)\omega^*\). She repeats this process for infinitely many
-periods. Assume also that the student's prior is such that
+cost \(c(a) = \frac{1}{2}a^2\). She repeats this process for infinitely
+many periods. Assume also that the student's prior is such that
 \(\mathbb{E}[\omega]= \omega^*\) and she is dogmatic about being of type
-\(\hat{\theta}>\theta^*\).\footnote{The example is illustrated for an overconfident student but 
-the results are symmetric for a dogmatic student who initially 
-places probability one on some $\tilde{\theta}<\theta^*$.} Therefore,
-the student's payoff in period \(t\) is given by }
+\(\hat{\theta}>\theta^*\).\footnote{The example is illustrated for an overconfident student but the results are symmetric for a dogmatic student who initially places probability one on some $\tilde{\theta}<\theta^*$.}
+Therefore, the student's payoff in period \(t\) is given by }
 
@@
 \emph{Under this specification, the myopic optimal effort level is
-\(a_t^* = \omega^*\). Because the student does not know \(\omega^*\), he
-will choose \(a_t = \mathbb{E}_t(\omega)\) where the expectation is
+\(a_t^* = \omega^*\). Because the student does not know \(\omega^*\),
+she will choose \(a_t = \mathbb{E}_t(\omega)\) where the expectation is
 taken with respect to the student's belief at the beginning of period
@@
 will receive an average utility of
-\((\theta^*+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}\) but he was expecting
-an average utility of
+\((\theta^*+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}\) but was expecting an
+average utility of
 \((\hat{\theta}+a_t^*)\omega^* - \frac{1}{2}a_t^{*2}\). In response, she
@@
 student will have reached a self-defeating equilibrium and she will
-continue to choose sub-optimal effort forever. }
+continue to choose sub-optimal effort forever.}
 
@@
 explanation that they are of type \(\tilde{\theta}\), the agent will
-switch to the alternative if:
+switch to the alternative if
 
@@
 
-Where \(h^t\) is the history of outcomes up to time \(t\), and
-\(\alpha\) is the switching
+where \(h^t\) is the history of outcomes up to time \(t\) and \(\alpha\)
+is the switching
 threshold.\footnote{Notice that if $\alpha \to \infty$, the behavior of the switcher will be indistinguishable from that of the Dogmatic modeler. 
@@
 an alternative type, the switcher can avoid the self-confirming
-equilibria. However, if the prior belief on \(omega\) is sufficiently
+equilibria. However, if the prior belief on \(\omega\) is sufficiently
 tight around a self-defeating equilibrium, the switcher might look
@@
 self-defeating equilibrium. In such situations, we say that the
-misspecified belief is persistent.
+misspecified belief about \(\theta\) is \emph{persistent}.
 
@@
 As in framework 1, the agent is of some type \(\theta^* \in \Theta\) and
-the state is \(\omega \sim F(\Omega)\). In this case, the agent chooses
-an action \(a\in A\) and observes a binary outcome that is either a
-success or a failure. Denote the outcome by \(o \in \{s,f\}\). The
-probability of observing a success is increasing in \(\theta\) and in
-\(\omega\). Whenever the agent observes a success, he gets a payoff
-\(v>0\) and whenever the outcome is a failure, the payoff is 0. In
-addition, the probability of success is such that for each state, there
-is a unique optimal action that maximizes the agent's expected payoff.
-Therefore, the probability of success can be seen as a monotone
-transformation of the utility from Framework 1.
+the state is \(\omega\) is distributed according to \(F(\Omega)\). In
+this case, the agent chooses an action \(a\in A\) and observes a binary
+outcome that is either a success or a failure. Denote the outcome by
+\(o \in \{s,f\}\). The probability of observing a success is increasing
+in \(\theta\) and in \(\omega\). Whenever the agent observes a success,
+he gets a payoff \(v>0\) and whenever the outcome is a failure, the
+payoff is 0. In addition, the probability of success is such that for
+each state, there is a unique optimal action that maximizes the agent's
+expected payoff. Therefore, the probability of success can be seen as an
+order-preserving transformation of the utility from Framework 1.
 
 I focus on two nested theories that have been widely studied within this
-framework: Full Bayesian updating and self-serving attribution bias. I
+framework: full Bayesian updating and self-serving attribution bias. I
 explain each of these classical models of belief updating in what
-follows
+follows.
 
@@
 A Bayesian agent simultaneously updates their beliefs about \(\theta\)
-and \(\omega\) by using Bayes' rule. The posterior at period t+1 about
-\(\theta\) after observing outcome \(o\) is given by: \[
+and \(\omega\) by using Bayes' rule. The posterior at period \(t+1\)
+about \(\theta\) after observing outcome \(o\) is given by: \[
 p_{t+1}(\theta, \omega| h^t) = \frac{p[o|\theta, \omega]p_t(\theta, \omega)}{\sum_{(\theta', \omega')}p[o|\theta', \omega']p_t(\theta', \omega')}
-\]
-
-Where \(p_{t}\) is the belief at the start of period \(t+1\) and
+\] where \(p_{t}\) is the belief at the start of period \(t+1\) and
 includes all the information gathered so far.
@@
 Bayesian agents choose the effort level that maximizes their expected
-flow payoff by taking expectations over their prior beliefs about
-\(\theta\) and \(\omega\). Since agents are myopic, even though all the
-parameters could be identified with enough variation in choices, there
-will be instances in which the Bayesian will not learn even with
-infinite amounts of data. This happens because, by being myopic, they do
-not internalize the trade off between flow payoff and learning. This can
-result in too little experimentation to learn their true type. An
-alternative to this approach is given by \citet{Hestermann2021} and is
-discussed in the concluding remarks. Regardless, this approach is useful
-as a benchmark for the other theories discussed in this paper.
-
-Also notice that if a fully Bayesian agent has a dogmatic prior, they
-will never update their beliefs about the parameter that they are
-dogmatic about. This will imply that they are prone to the same types of
-errors as the dogmatic modeler in framework 1.
+flow payoff by taking expectations over \((\theta, \omega)\) using their
+beliefs at period \(t\). Since agents are myopic, there will be
+instances in which the Bayesian will not learn even with infinite
+amounts of data. This happens because myopic agents do not internalize
+the trade-off between flow payoff and learning. This can result in too
+little experimentation to learn their true type. An approach in which
+agents intentionally introduce variation in their choices is given by
+\citet{Hestermann2021} and is discussed in the concluding remarks.
+Regardless, this approach is useful as a benchmark for the other
+theories discussed in this paper.
+
+Notice that if a fully Bayesian agent has a dogmatic prior, they will
+never update their beliefs about the parameter that they are dogmatic
+about. This will imply that they are prone to the same types of errors
+as the dogmatic modeler in framework 1.
 
@@
 A Self-Serving Bayesian is an agent who uses a biased version of Bayes
-rule to update their beliefs. They will update their beliefs about the
-state \(\omega\) and his type \(\theta\) simultaneously by
-over-attributing successes to a high value of \(\theta\) and
-under-estimating the role of higher \(\omega\). Similarly, he will
-attribute failure to a low state to a greater degree than an unbiased
-agent would. This sort of biased updating is referred to as
-\emph{misattribution bias}.
+rule to update his beliefs. He will update his beliefs about the state
+\(\omega\) and his type \(\theta\) simultaneously by over-attributing
+successes to a high value of \(\theta\) and under-estimating the role of
+higher \(\omega\). Similarly, he will attribute failure to a low state
+to a greater degree than an unbiased agent would. For instance, if the
+student from the example attributed a high grade to being of high
+ability while attributing low grades to a harsh grading system. This
+sort of biased updating is referred to as \emph{misattribution bias}.
 
 To model the misattribution bias, I take the approach of
-\citet{benjamin2019}, where the posterior odds are given by:
-
-\[
+\citet{benjamin2019}, where the posterior odds are given by: \[
 p_{t+1}(\theta, \omega| h^t) = \frac{p[h^t|\theta, \omega]^{c(\theta, \omega, o_t)}p_t(\theta, \omega)}{\sum_{(\theta', \omega')}p[h^t|\theta', \omega']^{c(\theta, \omega, o_t)}p_t(\theta', \omega')}
-\]
-
-with
-\(c(\theta_H, \omega, o)<c(\theta_M, \omega, o)<c(\theta_L, \omega, o)\)
-and
-\(c(\theta, \omega_L, o)<c(\theta, \omega_M, o)<c(\theta, \omega_H, o)\).
-And where \(h_t\) is the history of signal realizations observed up to
-period t.
-
-This formulation of the bias means that the agent will over-attribute
-successes to a high type and under-attribute them to a low type Whereas
-they will over-attribute failures to a low state and under-attribute
-them to a high state. The bias is introduced by distorting the perceived
-likelihood that the signal was generated by either high values of
-\(\theta\) when it is a success, or by low values of \(\omega\) when it
-is a failure. The parameter \(c\) determines the degree of bias and
+\] with \(c(\theta, \omega, o)\) decreasing in \(\theta\) and increasing
+in \(\omega\). \(h_t\) is the history of signal realizations observed up
+to period \(t\).
+
+This formulation allows the bias to be introduced by distorting the
+perceived likelihood that the signal was generated by either high values
+of \(\theta\) when it is a success, or by low values of \(\omega\) when
+it is a failure. The parameter \(c\) determines the degree of bias and
 imposes enough restrictions to ensure that the model is still
@@
 Notice that because \(p(h^t|\theta, \omega)<1\), if \(c(\cdot)<1\), a
-smaller exponent \(c\) implies a larger distortion upwards for fixed
-\(h^t\), and fixed parameters \(\theta\) and \(omega\). While a
-\(c(\cdot)>1\) implies a distortion downwards and it is larger when
+smaller exponent \(c\) implies a larger distortion upward for a fixed
+\(h^t\), and fixed parameters \(\theta\) and \(\omega\). While a
+\(c(\cdot)>1\) implies a distortion downward and it is larger when
 \(c(\cdot)\) is larger.
@@
 develop a unifying example where the forces behind each of the theories
-can be isolated. The example is a modified from \citet{Heidhues2018} and
+can be isolated. The example is modified from \citet{Heidhues2018} and
 is adapted to be implementable in the lab.
@@
 \(\theta\)\footnote{which is potentially misspecified as in the dogmatic and switcher cases discussed above}
-and chooses gamble \(e in \{e_L, e_M, e_H\}\). The agent observes
+and chooses gamble \(e \in \{e_L, e_M, e_H\}\). The agent observes
 whether the gamble is a success or a failure and gets a payoff of \(1\)
-and if it is a success; they get \(0\) otherwise.
+if it is a success; they get \(0\) otherwise.
 
 The probability of success is increasing in both \(\theta\) and
-\(\omega\) and is fully described by the Table \ref{tab:DGP}
+\(\omega\) and is fully described in Table \ref{tab:DGP}
 
@@
 
-Conditional on a type, the agent's flow payoff is maximized by choosing
-the gamble that matches the state. For example, if the value of
-\(\omega\) is \(\omega_H\), the agent's flow payoff is maximized by
-choosing \(e_H\) and if the state is \(\omega_L\) the flow payoff is
-maximized by choosing gamble \(e_L\), regardless of the value of
-\(\theta\). The agent myopically chooses gambles every period to
-maximize the flow payoff for \(T<\infty\) periods.
+For each type, the agent's flow payoff is maximized by choosing the
+gamble that matches the state. For example, if the value of \(\omega\)
+is \(\omega_H\), the agent's flow payoff is maximized by choosing
+\(e_H\) and if the state is \(\omega_L\) the flow payoff is maximized by
+choosing gamble \(e_L\), regardless of the value of \(\theta\). The
+agent myopically chooses gambles every period to maximize the flow
+payoff for \(T<\infty\) periods.
 
@@
 outcomes if enough variation in the effort choices exists. This can be
-seen by confirming that there is no pair of \(\theta\) and \(\omega\)
-such that the probability of success is the same for all effort choices.
-Thus, by changing the effort choice, the agent can learn both their type
-and the state if they observe enough outcomes.
+seen by confirming that there are no two pairs of \(\theta\) and
+\(\omega\) such that produce the same the probability of success for all
+effort choices. Thus, by changing the effort choice, the agent can learn
+both their type and the state if they observe enough outcomes.
 
@@
 that is consistent with the agent's misspecified belief. That is
-\(P[\text{sucess}|\theta^*, e^*] = P[\text{sucess}|\hat{\theta}, e^*]\)
+\(P[\text{sucess}|\theta^*, \omega^*, e^*] = P[\text{sucess}|\hat{\theta}, \hat{\omega}, e^*]\)
 where \(e^*\) is the agent's myopic optimal choice.
@@
 equilibria. For example, if the agent is of type \(\theta_M\) but
-mistakenly believes that he is of type \(\hat{\theta}=\theta_H\) and the
-and \(\omega^* = \omega_M\), when the effort chosen is \(e_L\), the
+mistakenly believes that he is of type \(\hat{\theta}=\theta_H\) and
+that \(\omega^* = \omega_M\), when the effort chosen is \(e_L\), the
 agent will observe a success with 45\% chance. Because the agent
@@
 conclude that the rate is \(\omega_L\). Under this belief, the optimal
-action is \(e_L\) which will continue to generate successes with \(45%
+action is \(e_L\) which will continue to generate successes with a \(45%
 \) probability, further reinforcing the incorrect belief. By doing so,
@@
 
-By including self-confirming equilibria, the example captures the forces
+By including self-defeating equilibria, the example captures the forces
 from each of the updating mechanisms discussed in the previous section
 and allows for the comparison of the main forces behind the theories.
-For realizations of \((\theta, \omega)\) for which there are
-self-confirming equilibria, the dogmatic agent will fall into the trap
-whereas the switcher will be able to escape it. Similarly, an agent with
-self-attribution bias will update their beliefs differently from an
-unbiased Bayesian, leading them to choose different gambles. I exploit
-such cases in order to test which model is a better fit for how subjects
-behave in a laboratory
-experiment.\footnote{because the setting does not match that of @Heidhues2018, there will be situations for which the theory does not provide a prediction.
-If such cases arise in the lab, they will not be used for the analysis.
-However, whether a misspecified belief persists or not for the switcher, depends highly on the realized history of signals that he gets.}
-In what follows I explain the details of how this example was
-implemented in the lab.
+This is because the self-defeating equilibria in a discretized setting
+acptures the main forces from the dogmatic and Switcher models.
+Furthermore, the data generating process has been designed to satisfy
+the main assumptions of both frameworks. For realizations of
+\((\theta, \omega)\) for which there are self-confirming equilibria, the
+dogmatic agent will fall into the trap whereas the switcher will be able
+to escape it. Similarly, an agent with self-attribution bias will update
+their beliefs differently from an unbiased Bayesian, leading them to
+choose different gambles. I exploit such cases in order to test which
+model is a better fit for how subjects behave in a laboratory
+experiment. In what follows I explain the details of how this example
+was implemented in the lab and the predictions that each model makes.
 
@@
 only one of the treatments. All subjects within a session participated
-in the same treatment and the first 4 treatments were assigned the
+in the same treatment and the first 4 sessions were assigned the
 ego-relevant condition; the rest were assigned to the stereotype
-treatment. The tasks were identical across treatments, except for
-parameter \(\theta\). In the ego-relevant condition \(\theta\) is the
-subject's own performance in a quiz, while in the stereotype condition,
-it is the performance of a randomly selected subject from another
-session.
-
-The experiment had 3 parts. In Part 1 subjects had 2 minutes to answer
-as many multiple-choice questions as they could from a 20-question quiz.
-They did this for quizzes on 6 different topics. The topics were: Math,
-Verbal Reasoning, Pop-culture and Art, Science and Technology, US
-Geography, and Sports and Video Games. In this part, they did not know
-how many questions were available and they were given no feedback.
+treatment. The tasks were identical across treatments. In the
+ego-relevant condition, \(\theta\) is the subject's own performance in a
+quiz. In the stereotype condition, it is the performance of a randomly
+selected subject from another session.
+
+The experiment had three parts. In Part 1 subjects had two minutes to
+answer as many multiple-choice questions as they could from a
+20-question quiz. They did this for quizzes on 6 different topics. The
+topics were: Math, Verbal Reasoning, Pop-culture and Art, Science and
+Technology, US Geography, and Sports and Video Games. In this part, they
+did not know how many questions were available and they were given no
+feedback.
 
 After taking all 6 quizzes, they proceeded to part 2 where they were
-asked to guess their score on each of them. In the stereotype treatment
+asked to guess their score on each of them. In the stereotype treatment,
 they were additionally asked to guess the score of a randomly drawn
@@
 also asked to say how confident they felt about their choices. They had
-4 possible answers: ``it was a random guess'', ``there is another
-equally likely score'', ``I am pretty sure'', ``I am completely sure''.
-These 4 answers are mapped to priors that place probabilities .33, .50,
+4 possible answers: ``it was a random guess,'' ``there is another
+equally likely score,'' ``I am pretty sure,'' ``I am completely sure.''
+I mapped these four answers to priors that place probabilities .33, .50,
 .75, and 1 to the chosen type. The remaining probability is split
@@
 For one topic at a time and in random order, they were presented with
-the three gambles from the example above and were asked to choose one of
-them. The probability of success was determined by their own score in
+the three gambles from the unifying example and were asked to choose one
+of them. The probability of success was determined by their own score in
 the ego-relevant condition, and by the score of the other participant in
@@
 
-In the interphase, they had to choose which of the 3 tables they wanted
+In the interfase, they had to choose which of the 3 tables they wanted
 to see before entering their choice in it. This was done as an
@@
 chose not to elicit the beliefs at each round to stay true to the forces
-in framework 1.
+in framework 1. The agent's tas kin Framework 1 is to learn the
+exogenous parameter and match it with their choice. By eliciting the
+beliefs about their type in each round and rewarding it for it, I add an
+incentive to additionally learn their type correctly. This can lead them
+to take actions that reveal their type when they wouldn's have done so
+in the case where there is no additional incentive.
 
@@
 is very informative of which model is most likely to be underlying the
-behavior. Define \emph{good news} to be a sample of signal realizations
-such that the number of successes in the sample is larger than the
-average number of successes observed so far. i.e.~if
-
-\[ \sum_i \mathbb{I}\{o_{iT}=success\} \geq \frac{1}{T} \sum_{t=0}^T\sum_i \mathbb{I}\{o_{it}=success\}\]
-where T is the current period and \(o_{t}=[o_{it}]_{i=1}^I\) is the
-sample observed at period \(t\). \emph{Bad news} are any other kind of
-signal realization. Denote the set of good news at period t by
-\(\mathcal{G}_t\) and let \(s_t\) be the number of successes in \(o_t\).
+behavior. Denote the sample size by \(I\) and define \emph{good news} to
+be a sample of signal realizations such that the number of successes in
+the sample is larger than the average number of successes observed so
+far. i.e.~if
+
+\[ \sum_{i=1}^I \mathbb{I}\{o_{iT}=success\} \geq \frac{1}{T} \sum_{t=0}^T\sum_{i=1}^I \mathbb{I}\{o_{it}=success\}\]
+where \(T\) is the current period and \(o_{t}=[o_{it}]_{i=1}^I\) is the
+sample observed at period \(t\). Denote the set of good news at period t
+by \(\mathcal{G}_t\) and let \(s_t\) be the number of successes in
+\(o_t\).\emph{Bad news} are any other kind of samples of signal
+realizations.
 
 Given the definition of good and bad news, the reaction of the agent to
-each kind of news is the change in their choice, conditional on the
-signal realization. Therefore, what we are interested are the
-coefficients of the following regression model, where the actions are
-those that a bayesian agent would choose:
-
-\[ \Delta a = \beta_0 + \beta_1\mathbb{I}\{o_t\in \mathcal{G}_t\} + \beta_2(s_{t} - s_{t-1}) + \beta_3\mathbb{I}\{o_t\in \mathcal{G}_t\}(s_{t} - s_{t-1})  \]
-
-Where \((s_{t} - s_{t-1})\) is the size of the surprise and \(\Delta a\)
-is the change in action. \(\beta_2\) is the reaction of the agent to bad
-news with surprise \((s_{t} - s_{t-1})\). And \(\beta_2 + \beta_3\) is
-the reaction to good news with surprise \((s_{t} - s_{t-1})\). Notice
-that for a dogmatic modeler \(\beta_2\geq0\) and
-\(\beta_2+\beta_3\geq 0\) as more successes are always indicative of a
-better state.
+each kind of news is the change in their choice conditional on the
+signal realization. Therefore, what we are interested in are the
+coefficients of the following regression model
+
+\[ \Delta a = \beta_0 + \beta_1\mathbb{I}\{o_t\in \mathcal{G}_t\} + \beta_2(s_{t} - s_{t-1}) + \beta_3\mathbb{I}\{o_t\in \mathcal{G}_t\}(s_{t} - s_{t-1}) +\varepsilon_t \]
+where \((s_{t} - s_{t-1})\) is the size of the
+surprise\footnote{The surpries eis the difference between the number of successes in the sample observed at time t and the average number of successes in previous samples.}
+and \(\Delta a = a_{t+1}-a_t\) is the change in action as a reaction
+after observing the latest sample. \(\beta_2\) is the reaction of the
+agent to bad news with surprise \((s_{t} - s_{t-1})\). And
+\(\beta_2 + \beta_3\) is the reaction to good news with surprise
+\((s_{t} - s_{t-1})\). \(\varepsilon_t\sim N(0, \sigma)\) is variation
+in the action choices that is not explained by the sample of signal
+realizations.
+
+\hypertarget{self-attribution-bias}{%
+\subsection{Self-Attribution Bias}\label{self-attribution-bias}}
+
+The key feature of Self-attribution bias is the asymmetric treatment of
+good news and bad news. In particular, the agent will over-attribute
+successes to a high type and under-attribute them to a low type.
+Similarly, they will over-attribute failures to a low state and
+under-attribute them to a high state. This implies that, after observing
+a failure, the agent will adjust their effort downwards by more than
+what an unbiased Bayesian would have done. In contrast, after observing
+a success, the agent will adjust their effort upwards by less than a
+Bayesian would have done and if the bias is large enough, it could be
+that the agent will not adjust their effort upwards at all, or even
+decrease their effort in response to a success.
+
+This is in stark contrast with what a Dogmatic modeler would do. A
+dogmatic modeler always attributes any variation in the outcome to the
+state and never updates their beliefs about \(\theta\). Therefore, they
+will always increase their effort choices after a surprising success and
+decrease it after a failure.
+
+On the other hand, the biased behavior can be in line with the behavior
+of a switcher. In particular, if the agent starts with a misspecified
+belief on \(\hat{\theta}\), and is willing to switch to a belief with
+\(\theta'>\hat{\theta}\), whenever the paradigm shift happens, it will
+likely be in response to a surprising streak of successes. In this case,
+when they adjust their belief about \(\theta\), they will also adjust
+their effort choice. Since they were initially underconfident, they had
+been choosing an effort that was too high relative to the true state,
+and therefore, the effort is likely to fall in response to a surprising
+streak of success.
+
+Let \(\beta^A\) be the coefficients of the regression model when the
+agent updates with misattribution bias. Let \(\beta^B\) be tha
+coefficients of the same regression model but when the agent is
+Bayesian.
+
+\textbf{Prediction 1A:} \emph{After observing a failure, the agent will
+adjust their effort downwards by more than a Bayesian would have done.
+After observing a success, the agent will adjust their effort upwards by
+less than a Bayesian would have done. If the bias is large enough, the
+agent might not adjust their effort upwards at all, or even decrease
+their effort in response to a success. That is \(\beta_2^A > \beta_2^B\)
+and \(\beta_2^A + \beta_3^A<\beta_2^B + \beta_3^B\)}
+
+In addition to their behavior, there is an additional characteristic
+feature of misattribution bias that is not present in other models. This
+is the only model in which an agent could start off with a correct
+belief and become more overconfident. In the long-run.
+
+\textbf{Prediction 2A:} \emph{After observing a streak of successes, the
+agent will update their belief about \(\theta\) upwards even when they
+started with a correct initial belief.}
 
@@
 Since the domain of the problem is discrete and finite in the example,
-the predictions of the original theory apply only to the combinations of
-parameters and initial beliefs for which there is a self-defeating
-equilibrium. In the example, there are 5 such combinations. For each of
-them, the dogmatic modeler predicts that the agent will fall into the
-self-defeating equilibrium and will be able to sustain the misspecified
-belief forever.
+the predictions of the original theory of \citet{Heidhues2018} apply
+only to the combinations of parameters and initial beliefs for which
+there is a self-defeating equilibrium. In the unifying example, there
+are 5 such combinations. For each of them, the dogmatic model predicts
+that the agent will fall into the self-defeating equilibrium and will be
+able to sustain the dogmatic misspecified belief forever.
 
@@
 for these combinations of parameter values and beliefs that the dogmatic
-model makes predictions within the Unifying example.
+model makes predictions within the Unifying example. Otherwise, the
+agent is not able to sustain the dogmatic belief and will be forced to
+use a different updating procedure to rationalize the signals that he
+observed.
 
@@
 \(\hat{\theta}\), and \((\theta^*, \omega^*, \hat{\theta})\) are such
-that there is s self-defeating equilibrium, the agent will fall into the
-trap and choose the effort level that sustains the misspecified belief
-forever.}
-
-In term of the dogmatic's reagtion to good and bad news, let \(\beta^D\)
+that there is a self-defeating equilibrium, the agent will choose the
+effort level that sustains the misspecified belief forever.}
+
+In term of the dogmatic's reaction to good and bad news, let \(\beta^D\)
 denote the coefficients of the regression model above when the actions
@@
 i.e.~\(\beta_2^D>\beta_2\) and \(\beta_3^D > \beta_3\).}
+
+\textbf{Prediction 3D:} \emph{A dogmatic modeler never updates their
+belief about \(\theta\).}
 
@@
 gaining insight into what happens when there are no traps is important
-for understanding what are the other reasons why overconfidence might
-arise and prevail.
+for understanding the other reasons why overconfidence might arise and
+prevail.
 
@@
 Since the switcher starts as the same dogmatic agent, the initial
-behavior of both types of agents is identical, however, because the
-switcher is keeping track of the likelihood ratio, they will be able to
-escape the self-defeating equilibrium if the evidence is convincing
-enough. Therefore there is a positive probability that the switcher will
+behavior of both types of agents is identical. However, because the
+switcher keeps track of the likelihood ratio, they will be able to
+escape the self-defeating equilibria if the evidence is convincing
+enough. Therefore there is positive probability that the switcher will
 adjust their initially misspecified belief about \(\theta\) and learn
@@
 \textbf{Prediction 1S:} \emph{With positive probability, the switcher
-will escape the self-defeating equilibrium and learn the true state.}
+will escape the self-defeating equilibria and learn the true state.}
 
@@
 direction of what a Bayesian would have done. that is
-\(\beta_2^S<\beta_2\) and \(\beta_2^S + \beta_3^S<\beta_2+\beta_3\)}
+\(\beta_2^S<\beta_2^B\) and
+\(\beta_2^S + \beta_3^S<\beta_2^B+\beta_3^B\)}
 
@@
 need to look at cases where the agent starts with a misspecified belief
-and the switcher changes paradigm.
+and the switcher changes paradigm. \textbf{Prediction 3S:}
+\emph{Correctly specified switchers do not update their beliefs about
+\(\theta\)}
 
 The probability that the switcher will escape the self-defeating
-equilibrium depends on the prior belief about \(\omega\). If the prior
-is sufficiently tight around the self-defeating equilibrium, the
-likelihood ratio will not grow fast enough, however, in the example
-above, the prior is uniform over the states and therefore, the
-likelihood ratio is more likely to grow fast enough.
-
-\hypertarget{self-attribution-bias}{%
-\subsection{Self-Attribution Bias}\label{self-attribution-bias}}
-
-The key feature of Self-attribution bias is the asymmetric treatment of
-good news and bad news. In particular, the agent will over-attribute
-successes to a high type and under-attribute them to a low type.
-Similarly, they will over-attribute failures to a low state and
-under-attribute them to a high state. This implies that, after observing
-a failure, the agent will adjust their effort downwards by more than
-what an unbiased Bayesian would have done. In contrast, after observing
-a success, the agent will adjust their effort upwards by less than a
-Bayesian would have done and if the bias is large enough, it could be
-that the agent will not adjust their effort upwards at all, or even
-decrease their effort in response to a success.
-
-This is in stark contrast with what a Dogmatic modeler would do. A
-dogmatic modeler always attributes any variation in the outcome to the
-state and never updates their beliefs about \(\theta\). Therefore, they
-will always increase their effort choices after a surprising success and
-decrease it after a failure.
-
-On the other hand, the biased behavior can be in line with the behavior
-of a switcher. In particular, if the agent starts with a misspecified
-belief on \(\hat{\theta}\), and is willing to switch to a belief with
-\(\theta'>\hat{\theta}\), whenever the paradigm shift happens, it will
-likely be in response to a surprising streak of successes. In this case,
-when they adjust their belief about \(\theta\), they will also adjust
-their effort choice. Since they were initially underconfident, they had
-been choosing an effort that was too high relative to the true state,
-and therefore, the effort is likely to fall in response to a surprising
-streak of success.
-
-Let \(\beta^A\) be the coefficients of the regression model when the
-agent updates with misattribution bias.
-
-\textbf{Prediction 1A:} \emph{After observing a failure, the agent will
-adjust their effort downwards by more than a Bayesian would have done.
-After observing a success, the agent will adjust their effort upwards by
-less than a Bayesian would have done. If the bias is large enough, the
-agent might not adjust their effort upwards at all, or even decrease
-their effort in response to a success. That is \(\beta_2^A > \beta_2\)
-and \(\beta_2^A + \beta_3^A<\beta_2 + \beta_3\)}
-
-In addition to their behavior, there is an additional characteristic
-feature of misattribution bias that is not present in other models. This
-is the only model in which an agent could start off with a correct
-belief and become more overconfident. In the long-run.
-
-\textbf{Prediction 2A:} \emph{After observing a streak of successes, the
-agent will update their belief about \(\theta\) upwards. This will lead
-to the possibility of observing subjects who start correctly specified
-and become overconfident.}
+equilibria depends on the prior belief about \(\omega\). If the prior is
+sufficiently tight around a self-defeating equilibrium, the likelihood
+ratio will not grow fast enough. In the unifying example, the prior is
+uniform over the states and therefore, the likelihood ratio is more
+likely to grow fast enough.
 
@@
 
-As such, all the predictions discussed above apply to the case of
-Stereotypes as well. My analysis of stereotypes will focus only on the
-degree to which ego-relevance of the type affects the updating procedure
-and not on the motivations behind the bias. I am particularly interested
-in whether the explanatory power of the models differs with the degree
-of ego-relevance of the type.
+All the predictions discussed above apply to the case of Stereotypes as
+well. My analysis of stereotypes will focus only on the degree to which
+ego-relevance of the type affects the updating procedure and not on the
+motivations behind the bias. I am particularly interested in whether the
+explanatory power of the models differs with the degree of ego-relevance
+of the type.
 
@@
 they are underconfident; and if it is in the same category, they are
-correctly specified. Overall, 0.43 of the guesses made in the
+correctly specified. Overall, 43\% of the guesses made in the
 questionnaire were misspecified. The rest of the guesses coincided with
@@
 \includegraphics{../figures/misspecification_hist.png}
-\caption{Initial misspecifications by
+\caption{Initial specifications by
 treatment}\label{fig:misspecification-hist}
@@
 each treatment. Figure \ref{fig:misspecification-by-treatment} shows a
-heatmap of the misspecifications that arose in each treatment. In the
+heatmap of the specifications that arose in each treatment. In the
 stereotype treatment, subjects are most underconfident about the
@@
 \includegraphics{../figures/misspecifications_characteristics_treatment.png}
-\caption{Initial misspecifications by treatment and
-characteristics}\label{fig:misspecification-by-treatment}
+\caption{Initial misspecifications by treatment and characteristics. a
+-1 corresponds to all subjects being underconfident while 1 corresponds
+to all subjects being overconfidence. All subjects being correctly
+specified is assigned a value of
+zero.}\label{fig:misspecification-by-treatment}
 }
@@
 and not elicited in a standard way, I first need to confirm that
-subjects were not just randomly choosing a matrix in which to enter
-their effort. The left panel of Figure \ref{fig:matrix-choices-by-round}
-shows the share of subjects who chose a matrix consistent with their
-initial reported belief. In round 1, 69\% of the subjects chose a matrix
-that was consistent with their initial belief. This indicates that
-subjects were not just randomly choosing a matrix in which to enter
-their effort. From round 2 onwards, the share steadily declines, but
-still not as far as to indicate a random choice of matrices. This is
-consistent with the subjects moving away from their starting belief
-through some updating procedure.
+subjects were not randomly choosing a matrix in which to enter their
+effort. The left panel of Figure \ref{fig:matrix-choices-by-round} shows
+the share of subjects who chose a matrix consistent with their initial
+reported belief. In round 1, 69\% of the subjects chose a matrix that
+was consistent with their initial belief. This indicates that subjects
+were not randomly choosing a matrix in which to enter their effort. From
+round 2 onwards, the share declines, but not as far as to indicate a
+random choice of matrices. This is consistent with the subjects moving
+away from their starting belief through some updating procedure.
 
@@
 Figure \ref{fig:transitions} shows the transition matrix for subjects
-who started in each of the 3 possible starting specifications and the
-specifications that they ended up in at the end of the updating task.
-The two things to note are that the initial belief is the most likely
-end belief. This is consistent with some degree of stickiness of the
-misspecifications as the switcher and dogmatic models would predict.
+who started in each of the three possible starting specifications and
+the specifications that they ended up in at the end of the updating
+task. The two things to note are that the initial belief is the most
+likely end belief. This is consistent with some degree of stickiness of
+the misspecifications as the switcher and dogmatic models would predict.
 However, the data also presents a lot of subjects who started with a
 correct belief of the type and ended up overestimating it. This is
-consistent only with the self-attribution bias. Lastly, the subjects who
+consistent only with self-attribution bias. Lastly, subjects who
 initially overestimate the score, are the least likely to learn their
@@
 section I will look at the role of self-defeating equilibria in
-preventing learning. I find that the presence of self-defeating
-equilibria does not seem to be the main deterrent to learning.
+preventing learning.
 
@@
 
-As described above, the presence of stable misspecified beliefs act as
-learning traps. If an agent falls into one of these traps, bayesian
-updating will lead them to choose the same effort forever. These
-self-defeating equilibria allow me to distinguish between the dogmatic
-modeler and the switcher. If the agent falls into a trap and stays there
-forever, they are more likely to be a dogmatic modeler. If they escape
-the trap, they are more likely to be a switcher or to be updating with
-some attribution bias.
+As described in Framework 1, the presence of stable misspecified beliefs
+act as learning traps in this setting. If an agent falls into one of
+these traps, bayesian updating will lead them to choose the same effort
+forever. These self-defeating equilibria allow me to distinguish between
+the dogmatic modeler and the switcher. If the agent falls into a trap
+and stays there forever, they are more likely to be a dogmatic modeler.
+If they escape the trap, they are more likely to be a switcher or to be
+updating with some attribution bias.
 
@@
 traps, 43\% of subjects learn. From the share that did not learn when
-there was a trap. A remaining 22\% can be accounted for as being
+there was a trap, 22\% can be accounted for as being
 trapped.\footnote{A subject is considered trapped when 3 out of their last 4 choices are consistent with 
@@
 from optimal. Behavior that is not consistent with either of these falls
-outside of the scope of the theories discussed above.
-
-My results are consistent with the findings of \citet{Hestermann2021}.
-In a laboratory experiment that stays true to Framework 1, they test the
+outside of the scope of the theories discussed here.
+
+My results are consistent with the findings of \citet{Gotte2022}. In a
+laboratory experiment that stays true to Framework 1, they test the
 predictions of the dogmatic modeler. They find that the average pattern
 in behavior is in the direction of the dogmatic modeler, however,
-subjects do not fully act as dogmatics as their actions do not go as far
-as to fully support the self-defeating equilibrium. A lot of the
+subjects do not fully act as dogmatics since their actions do not go as
+far as to fully support the self-defeating equilibrium. A lot of the
 differences between the observed behavior in their experiment and the
@@
 realized number of successes and the average number of successes so far
-and call it the news differential. Figure \ref{fig:reaction-news} shows
-the correlation between change in effort and the news differential,
+and call it the news differential but can be thought of as the
+``size'\,' of the surprise. Figure \ref{fig:reaction-news} shows the
+correlation between change in effort and the news differential,
 separately for good and bad news.
@@
 with a change of paradigm. It is not consistent with the dogmatic
-modeler or the Bayesian. Because I do not directly elicit beliefs, it is
-not possible to distinguish between the self-attribution bias and the
-change of paradigm with this data alone. Nevertheless, the fact that
-about a third of the subjects started with a correctly specified belief
-and ended up overconfident is consistent only with the self-attribution
-bias. this points towards the fact that misattribution bias is the most
-likely explanation for the behavior of the subjects in the experiment.
+modeler or the Bayesian. In addition, the fact that about a third of the
+subjects started with a correctly specified belief and ended up
+overconfident is consistent only with the self-attribution bias. This
+points towards the fact that misattribution bias is the most likely
+explanation for the aggregate behavior of the subjects in the
+experiment.
 
@@
 A regression analysis of this same data reveals that indeed, the slopes
-are different for godd and bad news and that the difference is
+are different for good and bad news and that the difference is
 statistically
-significant.\footnote{I run a robustness check where I define
-good news to be a net-positive sample (half or more of the outcomes observed in the sample received in that round
-were successful) and bad news to be net-negative sample. I find the same pattern in this alternative regression model
-and the results are reported in the appendix.} The regression results
-are reported in Table \ref{tab:regression}. columns 2 and 3 of the table
-consider the model for each treatment separately. I find no significant
-differences in the parameters across treatment. This is consistent with
-the fact that the bias is not driven by the ego-relevance of
-\(\theta\).\footnote{The ego-relevance of $\theta$ is the motivation behind the self-attribution bias, 
-however, the bias itself is due to an incorrect updating procedure in response to good and bad news. The presence of 
-asymmetric updating in the stereotype condition can be due to self-censoring of the subjects. In particular, subjects 
-who initially underestimated the performance of the other participant might have realized their mistake and 
-by overestimating it after good news. This is consistent with the data presented here as well as with 
-the data observed in the transition matrix for stereotypes which is reported in the Appendix}
+significant.\footnote{I run a robustness check where I define good news to be a net-positive sample (half or more of the outcomes observed in the sample received in that round were successful) and bad news to be net-negative sample.
+I find the same pattern in this alternative regression model and the results are reported in the appendix.}
+The regression results are reported in Table \ref{tab:regression}.
+columns 2 and 3 of the table consider the model for each treatment
+separately. I find no significant differences in the parameters across
+treatment. This is consistent with the fact that the bias is not driven
+by the ego-relevance of
+\(\theta\).\footnote{The ego-relevance of $\theta$ is the motivation behind the self-attribution bias, however, the bias itself is due to an incorrect updating procedure in response to good and bad news.
+The presence of asymmetric updating in the stereotype condition can be due to self-censoring of the subjects.
+In particular, subjects who initially underestimated the performance of the other participant might have realized their mistake and by overestimating it after good news.
+This is consistent with the data presented here as well as with the data observed in the transition matrix for stereotypes which is reported in the Appendix}
 
@@
 surprising bad news. This would flatten the slope of the regression line
-for bad news relative to what a Bayesian would do. \ref{tab:regression}
-shows that the slope for bad news for the
+for bad news relative to what a Bayesian would do. Table
+\ref{tab:regression} shows that the slope for bad news for the
 simulation\footnote{The details on how the data was simulated are explained in the Appendix}
@@
 Throughout the experiment, there is little difference in the behavior of
-subjects across treatments. Two of the main differences are that
+subjects across treatments. Two of the main differences are, first that
 subjects in the ego-relevant treatment are more likely to become
-overconfident when they start with a correct belief. And that subjects
-in the stereotype treatment are more likely to overreact to good news
-when they start by underestimating the performance of the other
-participant.
+overconfident when they start with a correct belief; and second, that
+subjects in the stereotype treatment are more likely to overreact to
+good news when they start by underestimating the performance of the
+other participant.
 
 These two differences present as consistent with the self-attribution
-bias. However, the pattern in the stereotype treatment could also be due
+bias, however, the pattern in the stereotype treatment could also be due
 to self-censoring of the subjects. In particular, subjects who initially
@@
 ratio for the alternative paradigm to the status quo is \[
-\ell = \frac{L(\theta | b_{\tau}^\theta)}{L(\theta | b_{\tau-1}^\theta)}=\frac{p_\tau(o_t|b_{\tau}^\theta)}{p_{\tau}(o_t|b_{\tau-1}^\theta)} 
+\ell = \frac{L(\theta | b_{\tau}^\theta)}{L(\theta | b_{\tau-1}^\theta)}=\frac{p_\tau(o_t|b_{\tau}^\theta)}{p_{\tau}(o_t|b_{\tau-1}^\theta)},
 \]
@@
 
-\[\hat{\alpha} = \frac{1}{N}\sum_{i=1}^N \ell_{i\tau}\]
-
-Where \(N\) is the number of switches observed in the experiment.
+\[\hat{\alpha} = \frac{1}{N}\sum_{i=1}^N \ell_{i\tau},\]
+
+where \(N\) is the number of switches observed in the experiment.
 
@@
 to the following regression model:
-
-\[ \Delta effort_{it} = \beta_0 + \beta_1 signal_{i t-1} + \beta_2\mathbb{I}\{good \:news_{i t-1}\} + \beta_3{I}\{good\:news\}*signal_{i t-1} \]
+\[ \Delta effort_{it} = \beta_0 + \beta_1 signal_{i t-1} + \beta_2\mathbb{I}\{good \:news_{i t-1}\} + \beta_3{I}\{good\:news\}*signal_{i t-1}, \]
 where \(i\) is an individual and task level index (each subject in each

### 2023-11-09 Paper/draft.Rmd
Added references to paper

@@
 To do so, agents perform Bayesian hypothesis tests that evaluate which of two possible parameters is more likely.
-By doing so, she characterizes the set of situations in which even agents who consider alternative paradigms may become trapped.\footnote{A similar mechanism is proposed by \citet{Schwarstein2021} in a setting with persuasion.}
+By doing so, she characterizes the set of situations in which even agents who consider alternative paradigms may become trapped.\footnote{A similar mechanism is proposed by \citet{Schwarstein2021} in a setting with persuasion.} A more general model in this spirit is also illustrated by @Ortoleva2012, where the agent has a prior over priors and acts according to the most likely belief.
 
@@
 the self-defeating equilibrium. In such situations, we say that the misspecified belief about $\theta$ is \emph{persistent}.
+
+A more general model that can be considered here is that of @Ortoleva2012.
+In his model agents have a prior over priors and choose a single prior to act according to.
+If this prior over priors only considers degenerate beliefs, the model will essentially reduce to the setting described here.
+The main difference is that in order to determine if there is a paradigm shift, the agent does not compare the likelihoods of two models, he simply looks at the likelihood of the current model and decides to switch paradigms if the likelihood is below a certain threshold.
+In this model the agent thus considers all possible theories and has a more flexible rule for that allows for paradigm shifts.
 
@@
 The overall pattern is that bad news are associated with a decrease in effort, and a more negative news differential is associated with a larger decrease in effort.
-On the contrary, good news are associated with a small decrease in effort.
-As mentioned in the predictions section, this is consistent with the self-attribution bias as well as with a change of paradigm.
+On the contrary, good news are associated with a small decrease in effort.\footnote{This asymmetric treatment of good and bad news has also been recently documented by \citet{Coutts2019} and @Barron2021} As mentioned in the predictions section, this is consistent with the self-attribution bias as well as with a change of paradigm.
 It is not consistent with the dogmatic modeler or the Bayesian.
@@
 and offers a more intuitive explanation for why this pattern arises in the stereotype treatment.
+It is also consistent with the findings of @Bohren2019, where they find that subjects initially underestimate the ability of women, however, after a sequence of good news for a woman, the attitude reverts and subjects evaluate that particlar woman to be better than men.
 

### 2023-11-09 Paper/draft.tex
Added references to paper

@@
 \author{Jimena Galindo}
-\date{October 26, 2023}
+\date{November 08, 2023}
 
@@
 trapped.\footnote{A similar mechanism is proposed by \citet{Schwarstein2021} in a setting with persuasion.}
+A more general model in this spirit is also illustrated by
+\citet{Ortoleva2012}, where the agent has a prior over priors and acts
+according to the most likely belief.
 
@@
 
+A more general model that can be considered here is that of
+\citet{Ortoleva2012}. In his model agents have a prior over priors and
+choose a single prior to act according to. If this prior over priors
+only considers degenerate beliefs, the model will essentially reduce to
+the setting described here. The main difference is that in order to
+determine if there is a paradigm shift, the agent does not compare the
+likelihoods of two models, he simply looks at the likelihood of the
+current model and decides to switch paradigms if the likelihood is below
+a certain threshold. In this model the agent thus considers all possible
+theories and has a more flexible rule for that allows for paradigm
+shifts.
+
 \hypertarget{framework-2}{%
@@
 larger decrease in effort. On the contrary, good news are associated
-with a small decrease in effort. As mentioned in the predictions
-section, this is consistent with the self-attribution bias as well as
-with a change of paradigm. It is not consistent with the dogmatic
-modeler or the Bayesian. In addition, the fact that about a third of the
-subjects started with a correctly specified belief and ended up
-overconfident is consistent only with the self-attribution bias. This
-points towards the fact that misattribution bias is the most likely
-explanation for the aggregate behavior of the subjects in the
-experiment.
+with a small decrease in
+effort.\footnote{This asymmetric treatment of good and bad news has also been recently documented by \citet{Coutts2019} and @Barron2021}
+As mentioned in the predictions section, this is consistent with the
+self-attribution bias as well as with a change of paradigm. It is not
+consistent with the dogmatic modeler or the Bayesian. In addition, the
+fact that about a third of the subjects started with a correctly
+specified belief and ended up overconfident is consistent only with the
+self-attribution bias. This points towards the fact that misattribution
+bias is the most likely explanation for the aggregate behavior of the
+subjects in the experiment.
 
@@
 offers a more intuitive explanation for why this pattern arises in the
-stereotype treatment.
+stereotype treatment. It is also consistent with the findings of
+\citet{Bohren2019}, where they find that subjects initially
+underestimate the ability of women, however, after a sequence of good
+news for a woman, the attitude reverts and subjects evaluate that
+particlar woman to be better than men.
 
